% Chapter: Kapitel 35
\section{Kapitel 35}


QUANTUM PHENOMENA EXPLAINED
DVFT interprets quantum mechanics as the behavior of vacuum-phase and vacuum-amplitude fields. This
chapter provides a unified explanation for twelve major unsolved quantum phenomena, including collapse,
entanglement, zero point energy, decoherence and delayed-choice experiments. DVFT clarifies these
phenomena by grounding them in the physical fields Φ = \rho e^{i\theta}.
1. Wavefunction Collapse
In DVFT, collapse is not a postulate. It occurs when vacuum-phase coherence (\theta) is disrupted by
macroscopic interactions. Measurement destroys \theta-coherence, forcing \psi to localize.
2. Wave–Particle Duality
Waves correspond to coherent vacuum-phase patterns, while particles correspond to localized vacuumamplitude excitations. Duality becomes a property of Φ, not a paradox.
3. Entanglement
Entanglement arises from shared vacuum-phase coherence between separated systems. Global coherence
of \theta allows nonlocal correlations without signaling.
4. Zero-Point Energy
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 78
Dynamic vacuum field gives finite, physical zero-point energy \epsilon_vac = \rho₀² (d\theta/dt)², connecting vacuum
energy to cosmological acceleration.
5. Delayed Choice \& Quantum Eraser
Interference depends on \theta-coherence. Which-path detectors scramble \theta; erasure restores it. DVFT removes
retrocausality by explaining phase re-coherence.
6. Decoherence
Decoherence is vacuum-phase scrambling. Macroscopic systems distort \theta-fields and eliminate
interference patterns physically, not abstractly.
7. Quantum Randomness
Randomness arises from unavoidable vacuum-phase fluctuations: \Delta\theta · \DeltaE \geq ħ/2 produces inherent phase
jitter in Φ.
8. Atomic Quantization
Energy quantization corresponds to \theta-field circulation conditions: ∮ \nabla\theta · dl = 2\pin. Atomic spectra reflect
dynamic vacuum field waves.
Conclusion
DVFT unifies gravity and quantum mechanics by grounding quantum behavior in vacuum-phase
properties. Interference, collapse, entanglement, and decoherence all follow naturally from Φ = \rho e^{i\theta}.
