\documentclass[12pt,a4paper]{article}

% Use shared T0 preamble
\input{../../../../T0_preamble_shared_De}

\title{Kapitel 26}
\author{}
\date{}

\begin{document}
\maketitle


SOLUTION TO THE BARYONIC ASYMMETRY
1. Introduction
The observed universe contains far more matter than antimatter, quantified by the baryon-to-photon ratio:
η_B \approx 6 \times 10⁻¹⁰.
The Standard Model cannot explain this value. Its allowed sources of baryon number violation and CP
violation are far too small by orders of magnitude.
DVFT (Dynamic vacuum field Curvature Theory) provides a clean, unified explanation because baryon
number, CP violation, and non-equilibrium dynamics all arise naturally from the structure of the vacuum
field:
\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)},
with amplitude \rho controlling inertia and gravitational stiffness and phase \theta controlling quantum behavior,
internal symmetries, and charge structure.
2. Sakharov Conditions in the DVFT Framework
Any successful theory of baryogenesis must satisfy Sakharov’s three conditions:
1. Baryon number violation
2. C and CP violation
3. Departure from thermal equilibrium
DVFT satisfies all three using the single vacuum field \Phi = \rho e^{i\theta}, without introducing extra fields, new
particles, or arbitrary CP phases. The conditions emerge naturally from the dynamical behavior of the
vacuum during the early dynamic vacuum field epoch.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 59
3. Baryon Number as Topological Winding in DVFT
In DVFT, baryons correspond to localized topological excitations of the vacuum phase \theta:
• baryons \rightarrow positive winding number of \theta
• antibaryons \rightarrow negative winding number of \theta
Thus baryon number is:
B ∼ winding number of \theta in internal phase space.
When the vacuum phase undergoes topological transitions (such as unwinding, knot-decay, or domain
merging),
B can change by integer amounts. This gives:
• natural baryon-number violation
• no need for sphalerons or beyond-Standard-Model operators
Baryon number violation comes directly from the microphysics of \theta(x,t).
4. CP Violation from Vacuum Phase Dynamics
In DVFT, CP violation is built into the dynamics of \theta.
If the vacuum's phase evolution is not symmetric under:
\theta \rightarrow −\theta (charge conjugation)
x \rightarrow −x (parity),
then the vacuum itself contains a CP-odd bias. This implies:
• different energy costs for +B and −B topological domains
• asymmetric decay of baryon vs antibaryon-like structures
• a preferred direction for phase unwinding
This CP bias is not an arbitrary input (as in the CKM matrix), but emerges from the structure of the
vacuum-phase Lagrangian. A general vacuum Lagrangian may include CP-odd terms such as:
L ⊃ \alpha · \partialₜ\theta + \beta · (\nabla\theta ⋅ P_odd),
which directly generate CP-violating evolution.
5. Non-Equilibrium from DVFT Early Dynamic vacuum field
The early universe in DVFT undergoes a transition from a highly coherent vacuum phase (large \rho, uniform
\theta) to a broken-phase state with rich amplitude and phase structure. This process is rapid and cannot be
adiabatic.
During this epoch:
• \rho varies rapidly
• \theta develops domains and defects
• particle masses change dynamically
• vacuum stiffness evolves in time
This means the universe is automatically out of thermal equilibrium, satisfying Sakharov's third condition
without requiring an inflation, reheating, or ad hoc transitions.
6. DVFT Mechanism of Baryogenesis
The DVFT baryogenesis mechanism proceeds in five stages:
1. Early uniform vacuum: \theta is nearly constant, \rho is high.
2. Dynamic vacuum field: \theta fractures into domains with different local winding numbers.
3. CP bias: the dynamics favor survival of domains with +B over those with −B.
4. Topological relaxation: as the vacuum transitions, domain walls collapse, knots unwind, changing
B.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 60
5. Freezing: once \rho stabilizes near \rho_0, baryon-number-changing processes shut off.
Because the CP-odd terms bias the relaxation, the random walk in baryon number becomes biased.
As the universe cools, this generates a net positive baryon asymmetry:
B_final > 0.
7. Predicting the Baryon-to-Photon Ratio
To calculate the observed ratio η_B \approx 6 \times 10⁻¹⁰, DVFT requires:
• Explicit CP-odd terms in the \theta-Lagrangian
• Vacuum stiffness parameters A, B, κ, \lambda
• Dynamics of domain-wall collapse rates
• Evolution of the dynamic vacuum field scale
The baryon asymmetry emerges from the imbalance in domain decay:
η_B ∼ (ΔE_CP / T_dynamic vacuum field).
DVFT uniquely provides a physical meaning to ΔE_CP as the energy bias between opposite-winding
phase domains. This makes η_B calculable once the vacuum potential is fully specified.
8. Distinction Between DVFT and Standard Approaches
Standard Model baryogenesis fails because:
• Sphaleron transitions are too weak
• CKM CP violation is too small
• No natural out-of-equilibrium period exists
Leptogenesis works only by adding massive particles whose masses and couplings remain unmeasured.
DVFT differs sharply:
• All Sakharov conditions emerge from \Phi = \rho e^{i\theta}.
• Baryon number is topological, not accidental.
• CP violation arises from dynamics, not arbitrary phases.
• Non-equilibrium is inherent to early dynamic vacuum field.
• No new fields or heavy particles are needed.
This produces a conceptually clean and physically transparent framework for baryogenesis.
9. Observational Consequences and Tests
DVFT predicts:
1. Residual vacuum-phase textures may survive as cosmological signatures.
2. Gravitational waves from domain-wall collapse in the early universe.
3. A specific scale for CP-odd vacuum terms, constrained by η_B.
4. Possible correlations between baryogenesis parameters and dark energy scale.
5. A unified explanation of matter genesis and gravitational vacuum structure.
These predictions allow DVFT to be tested against cosmology, gravitational wave astronomy, and
laboratory searches for CP violation.
Conclusion
DVFT provides a natural, unified, and physically grounded solution to baryonic asymmetry:
• baryon number as topological phase winding
• CP violation from intrinsic vacuum phase bias
• non-equilibrium from early dynamic vacuum field dynamics
• net baryon asymmetry from biased topological relaxation
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 61
What the Standard Model inserts artificially, DVFT derives inevitably.
DVFT therefore offers one of the cleanest and most compelling paths toward a complete theory of
baryogenesis and the origin of matter in the universe.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 62

\end{document}
