\documentclass[12pt,a4paper]{article}

% Use shared T0 preamble
\input{../../../../T0_preamble_shared_De}

\title{Kapitel 29}
\author{}
\date{}

\begin{document}
\maketitle


DELAYED CHOICE QUANTUM ERASER EXPERIMENT
The Delayed Choice Quantum Eraser (DCQE) experiment is one of the most misunderstood
demonstrations in quantum physics. It appears to suggest that the future can change the past or that the
photon ‘knows’ whether interference will be observed. In this chapter, the experiment is fully analyzed in
the framework of the Dynamic Vacuum Field Theory(DVFT). The DVFT interpretation removes the
mystery completely by showing that the key phenomenon is vacuum-phase coherence. DCQE involves
how vacuum-phase information is preserved, erased, or restored—not retrocausality. DVFT provides a
physically intuitive mechanism while remaining consistent with all observed results.
1. Introduction
The DCQE experiment challenges classical logic because it produces interference only when path
information is erased—even if the erasure occurs “after” the photon is detected. Standard interpretations
lean on abstract wavefunction collapse, nonlocality, or delayed information. DVFT provides a clearer
mechanism: interference depends on the coherence of the vacuum-phase field \Phi = \rho e^{i\theta}. When whichpath information is created, phase coherence is disrupted. When it is erased, the coherence is restored in
the correlated subset of events. This chapter explains how this arises naturally in DVFT.
2. Vacuum Field Structure Under DVFT
In DVFT, the quantum state of a photon is not a mysterious probability wave. It is a configuration of the
vacuum field \Phi(x), with:
• \rho(x): vacuum amplitude
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 67
• \theta(x): vacuum phase
Interference patterns arise from the relative phase between two vacuum-field paths. The detection pattern
depends on:
I(x) = |\Phi_1(x) + \Phi_2(x)|^2
When the two paths maintain a stable phase difference, interference appears. If the phase is randomized
or tagged by measurement, interference disappears.
3. What Happens After the Slits
After the photon encounters the slits or beam splitter, the vacuum field splits into two coherent branches:
\Phi = \Phi_1 + \Phi_2
This coherence is not a mathematical trick—it reflects real structure in the vacuum phase \theta(x). The
interference pattern emerges when:
Δ\theta = \theta_1 − \theta_2 = constant
Thus, interference is fundamentally a “phase-coherence phenomenon” in the vacuum, not a property of a
photon.
4. Which-Path Information as Phase Decoherence
When which-path detectors are inserted, the vacuum field branches become entangled with a macroscopic
system and lose coherence:
• \theta_1 \rightarrow \theta_1 + \delta\theta_1
• \theta_2 \rightarrow \theta_2 + \delta\theta_2
• \delta\theta_1 \neq \delta\theta_2
Now Δ\theta is no longer well defined. This is physical: the vacuum field's phase was perturbed by
measurement. Interference disappears because the phase gradients no longer match.
5. The Quantum Eraser Restores Phase Coherence
The 'eraser' does not change the past. Instead, it changes the vacuum-phase boundary conditions by
removing which-path information stored in entanglement. This restores:
Δ\theta = constant
But only for a specific subset of correlated events. Thus, interference appears only in the coincidence
counts.
6. Why Delayed Choice Does Not Imply Retrocausality
DCQE appears to imply future choices affect past events, but in DVFT:
• The vacuum field \Phi spans the entire apparatus.
• Phase coherence or decoherence is global, not local.
• The final coincidence sorting groups events by their vacuum-phase relationships.
No signal travels backward in time. No photon changes its past. The vacuum-phase field already contains
all correlations. The delayed-choice simply selects a subset consistent with restored coherence.
7. DVFT Equation for Interference and Decoherence
Full interference:
I(x) = |\Phi_1(x) + \Phi_2(x)|^2
Decoherence from which-path:
\Phi \rightarrow (\Phi_1 e^{i\delta\theta_1}) + (\Phi_2 e^{i\delta\theta_2})
Δ\theta = \theta_1 − \theta_2 + (\delta\theta_1 − \delta\theta_2) \rightarrow undefined
Eraser restores coherence:
\delta\theta_1 = \delta\theta_2 ⇒ Δ\theta = constant
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 68
Therefore, interference reappears only in the selected coincidence channel.
8. Photon Behavior Under DVFT
In DVFT:
• A photon is a localized excitation riding on the vacuum field.
• Its trajectory is not determined by classical paths but by vacuum-phase geometry.
• Which-path detection modifies the vacuum phase, not the photon itself.
• Erasure restores the phase structure, enabling interference to reappear.
This interpretation avoids the paradoxes of retrocausal or consciousness-based explanations.
9. Why DVFT Explains DCQE Better Than Standard QM
Standard QM says: 'Wavefunction collapse depends on whether information is available.'
But it does not explain *how* or *why* this information physically affects the photon.
DVFT explains DCQE through:
• Vacuum-phase coherence
• Vacuum-phase decoherence
• Entanglement-induced phase tagging
• Erasure-induced re-coherence
Everything occurs in the vacuum field \Phi, which is real, continuous, and causal.
Conclusion
The Delayed Choice Quantum Eraser experiment does not require retrocausality or paradoxical reasoning.
DVFT provides a physically intuitive explanation: the vacuum field’s phase determines whether
interference appears, not the photon's knowledge or future choices. Which-path information disrupts
vacuum-phase coherence. Eraser actions restore it. The delayed-choice affects how events are *classified*,
not how they occur. DVFT thus unifies DCQE with classical intuition while preserving quantum
predictions exactly.

\end{document}
