\section*{Abstract}

The T0 theory postulates neither the parameter $\xi$ nor the minimal length scale $L_0 = \xi \cdot \lP$. Both emerge as necessary consequences of the self-consistency of the T0 Lagrangian. This document presents the complete derivation chain in five steps: (1) Lagrangian structure with time-mass duality, (2) self-consistency condition and $10^{-4}$ scaling, (3) uniqueness of $\xi$ from the e-p-$\mu$ system, (4) gravitational constant $G$ from $\xi$, (5) minimal length scale $L_0 = \xi \cdot \lP$.

\section{Step 1: The T0 Lagrangian}

\subsection{Standard Model Starting Point}

The Standard Model Lagrangian for a lepton $\psi_\ell$ reads:
\begin{equation}
	\Lag_{\text{SM}} = -\frac{1}{4} F_{\mu\nu}F^{\mu\nu} + \bar{\psi}_\ell(i\gamma^\mu D_\mu - m_\ell)\psi_\ell
\end{equation}
with $D_\mu = \partial_\mu + ieA_\mu$ and constant $m_\ell$.

\subsection{Time-Mass Duality as Fundamental Principle}

In T0 theory the fundamental relation holds:
\begin{equation}
	\tilde{T}(x,t) \cdot m(x,t) = 1
\end{equation}
This is not an additional postulate but a structural condition: every mass carries an intrinsic time field. This necessarily implies a dynamic mass field:
\begin{equation}
	m(x,t) = m_0 + \Delta m(x,t)
\end{equation}

\subsection{Complete T0 Lagrangian}

\begin{keyresult}[Complete T0 Lagrangian]
\begin{equation}
	\Lag_{\text{T0}} = -\frac{1}{4} F_{\mu\nu}F^{\mu\nu}
	+ \bar{\psi}_\ell(i\gamma^\mu D_\mu - m_\ell)\psi_\ell
	+ \frac{1}{2}(\partial_\mu \Delta m)(\partial^\mu \Delta m)
	- \frac{1}{2} m_T^2 \Delta m^2
	+ \xipar \, m_\ell \,\bar{\psi}_\ell \psi_\ell \, \Delta m
\end{equation}
\end{keyresult}

\subsection{The Three Key Formulae}

\textbf{Coupling strength} (mass-proportional):
\begin{equation}
	\boxed{g_T^\ell = \xipar \cdot m_\ell}
\end{equation}

\textbf{Time field mass:}
\begin{equation}
	m_T = \frac{\lambda}{\xipar}
\end{equation}

\textbf{Vertex factor:}
\begin{equation}
	\bar{\psi}_\ell \psi_\ell \Delta m \longrightarrow -i\,\xipar\, m_\ell
\end{equation}

\textbf{Time field propagator:}
\begin{equation}
	\Delta m(k) \longrightarrow \frac{i}{k^2 - m_T^2 + i\epsilon}
\end{equation}

\section{Step 2: Self-Consistency Condition}

\subsection{Why the Lagrangian Forces \texorpdfstring{$\xi$}{xi}}

The coupling term $g_T^\ell = \xipar \cdot m_\ell$ is not freely choosable. The self-consistency of the Lagrangian requires:
\begin{itemize}
	\item The theory remains free of divergences at high energies.
	\item The known particle masses are reproduced.
	\item The mass hierarchy between generations is geometrically describable.
\end{itemize}

\subsection{The \texorpdfstring{$10^{-4}$}{10\^(-4)} Factor from QFT Loop Structure}

The loop suppression in four spacetime dimensions yields:
\begin{equation}
	\frac{1}{16\pi^3} \approx 2{.}01 \times 10^{-3}
\end{equation}
Combined with the Higgs parameters from the T0 Lagrangian:
\begin{equation}
	(\lambda_h)^2 \cdot \frac{v^2}{m_h^2} = (0{.}129)^2 \times \frac{(246{.}2)^2}{(125{.}1)^2} \approx 0{.}0647
\end{equation}

\begin{keyresult}[\texorpdfstring{$10^{-4}$}{10\^(-4)} from Spacetime Dimensionality]
\begin{equation}
	\xipar_4 \sim (10^{-1})^4 = 10^{-4}
\end{equation}
This factor is not postulated — it follows from the dimensionality of spacetime.
\end{keyresult}

\subsection{The 4/3 Factor from Tetrahedral Geometry}

The factor $4/3$ emerges from the harmonic structure of three-dimensional space:
\begin{equation}
	\frac{4 \text{ vertices}}{3 \text{ edges per vertex}} = \frac{4}{3} \quad \text{(perfect fourth)}
\end{equation}
The tetrahedron contains both fundamental harmonic intervals:
\begin{equation}
	\frac{3}{2} \times \frac{4}{3} = 2 \quad \text{(octave)}
\end{equation}

\section{Step 3: Uniqueness of \texorpdfstring{$\xi$}{xi}}

\subsection{The e-p-\texorpdfstring{$\mu$}{mu} System as Uniqueness Proof}

From the three fundamental mass ratios:
\begin{align}
	R_{pe} &= \frac{m_p}{m_e} = 1836{.}15267343 \\
	R_{\mu e} &= \frac{m_{\mu}}{m_e} = 206{.}7682830 \\
	R_{p\mu} &= \frac{m_p}{m_{\mu}} = 8{.}880
\end{align}
With the mass scaling $m_p / m_e = 245 \times (4/3)^\kappa$ it follows:
\begin{equation}
	\kappa = \frac{\ln(R_{pe}/245)}{\ln(4/3)} = \frac{\ln(1836{.}15/245)}{\ln(1{.}3333)} \approx 7{.}000
\end{equation}

\subsection{\texorpdfstring{$\kappa = 7$}{kappa = 7} is the Only Consistent Solution}

\begin{table}[h]
\centering
\begin{tabular}{lccr}
\toprule
\textbf{Exponent $\kappa$} & \textbf{$R_{pe}$ prediction} & \textbf{Consistent} & \textbf{Error} \\
\midrule
$\kappa = 6$ & $245 \times (4/3)^6 = 1376{.}6$ & \texttimes & $25{.}0\%$ \\
$\kappa = 7$ & $245 \times (4/3)^7 = 1835{.}4$ & \checkmark & $0{.}04\%$ \\
$\kappa = 8$ & $245 \times (4/3)^8 = 2447{.}2$ & \texttimes & $33{.}3\%$ \\
\bottomrule
\end{tabular}
\caption{$\kappa = 7$ is the only consistent solution}
\end{table}

\begin{keyresult}[\texorpdfstring{$\xi$}{xi} as Emergent Constant]
\begin{equation}
	\boxed{\xipar = \frac{4}{30000} = \frac{4}{3} \times 10^{-4} = 1{.}333 \times 10^{-4}}
\end{equation}
$\xi$ is not a postulate — it is the only self-consistent solution of the e-p-$\mu$ system.
\end{keyresult}

\section{Step 4: Gravitational Constant \texorpdfstring{$G$}{G} from \texorpdfstring{$\xi$}{xi}}

\subsection{Fundamental T0 Gravitational Relation}

The T0 Lagrangian implies the fundamental geometric relation:
\begin{equation}
	\xipar = 2\sqrt{G \cdot m_{\text{char}}}
	\quad \Rightarrow \quad
	G = \frac{\xipar^2}{4\, m_{\text{char}}} \quad \text{(T0 natural units)}
\end{equation}

The complete SI value requires explicit dimensional and unit conversion factors (Document 012):
\begin{equation}
	\boxed{G_{\text{SI}} = \frac{\xipar^2}{4\, m_e} \times C_{\text{dim}} \times C_{\text{conv}} \times \Kfrak}
\end{equation}
where $C_{\text{dim}}$ is the dimensional correction for the transition from T0 natural to physical units, $C_{\text{conv}}$ the SI conversion factor, and $\Kfrak$ the fractal correction. Numerically:
\begin{equation}
	G_{\text{SI}} \approx 6{.}674 \times 10^{-11}\,\text{N\,m}^2/\text{kg}^2
\end{equation}
Deviation from CODATA-2018: $< 0{.}01\%$. The complete derivation of all factors is in Document 012.

\section{Step 5: Minimal Length Scale \texorpdfstring{$L_0$}{L0}}

\subsection{Planck Length from \texorpdfstring{$G$}{G} and \texorpdfstring{$\xi$}{xi}}

\begin{equation}
	\lP = \sqrt{\frac{\hbar G}{c^3}} = 1{.}616 \times 10^{-35}\,\text{m}
\end{equation}
Since $G$ is derived from $\xi$, $\lP$ follows completely from $\xi$.

\subsection{\texorpdfstring{$L_0$}{L0} as Sub-Planck Scale}

The time-energy duality $r_0(E) \leftrightarrow E$ in natural units requires a minimal length scale. The coupling term $g_T^\ell = \xipar \cdot m_\ell$ scales with $\xipar$ — below $L_0$ the concept of ``distance'' loses its physical meaning, because the time field fluctuations $\Delta m$ dissolve the spacetime structure itself.

\begin{keyresult}[Minimal Length Scale]
\begin{equation}
	\boxed{L_0 = \xipar \cdot \lP = \frac{4}{30000} \times 1{.}616 \times 10^{-35}\,\text{m} = 2{.}155 \times 10^{-39}\,\text{m}}
\end{equation}
\end{keyresult}

\subsection{Physical Meaning of \texorpdfstring{$L_0$}{L0}}

$L_0$ marks the scale where T0 geometric effects become dominant. Below $L_0$:
\begin{itemize}
	\item All vacuum fluctuations are fully effective (Casimir effect).
	\item The perturbative expansion loses its validity.
	\item The fractal correction $\Kfrak$ becomes structurally necessary.
\end{itemize}

\section{Summary: Complete Derivation Chain}

\begin{keyresult}[Derivation Chain without Postulates]
\begin{align}
	&\text{Lagrangian structure} \; (\tilde{T} \cdot m = 1) \notag \\
	&\quad\Downarrow \notag \\
	&\text{Self-consistency requires} \; g_T = \xipar \cdot m \notag \\
	&\quad\Downarrow \notag \\
	&10^{-4}\text{ factor from 4D spacetime},\quad 4/3\text{ factor from tetrahedral geometry} \notag \\
	&\quad\Downarrow \notag \\
	&\kappa = 7 \text{ only solution of the e-p-}\mu\text{ system} \notag \\
	&\quad\Downarrow \notag \\
	&\boxed{\xipar = 4/30000} \quad \text{(not a postulate — emergent constant)} \notag \\
	&\quad\Downarrow \notag \\
	&G_{\text{SI}} = \frac{\xipar^2}{4m_e} \times C_{\text{dim}} \times C_{\text{conv}} \times \Kfrak \quad\Rightarrow\quad \lP = \sqrt{\hbar G/c^3} \notag \\
	&\quad\Downarrow \notag \\
	&\boxed{L_0 = \xipar \cdot \lP = 2{.}155 \times 10^{-39}\,\text{m}}
\end{align}
\end{keyresult}

\section{Connection to the SI System}

\subsection{The Unavoidable Circularity}

All results in this document — and in the companion documents 181 and 182 — are initially \textbf{ratio-based}: $\xipar$ is dimensionless, $L_0/\lP = \xipar$ is a pure ratio, $G = \xipar^2/(4m_e)$ holds in natural units. As soon as one wishes to state absolute SI values — i.e.\ $L_0 = 2{.}155 \times 10^{-39}\,\text{m}$ rather than just $L_0 = \xipar \cdot \lP$ — at least \textbf{one} external connection to the SI system is required.

\begin{important}[Apparent Circularity is Unavoidable]
It is not possible to derive absolute SI values from a purely dimensionless parameter like $\xipar$ without establishing somewhere a connection to the SI unit definition. This connection is not a weakness of the theory — it is an epistemological necessity of every physical theory.
\end{important}

\subsection{Possible Entry Points into the SI System}

The connection can be established via various quantities, all of which are equivalent:

\begin{itemize}
	\item \textbf{Via $\alpha$}: The fine-structure constant $\alpha = \xipar \cdot E_0^2 / (1\,\text{MeV})^2$ is dimensionless and experimentally very well known. It provides via $E_0 = \sqrt{m_e \cdot m_\mu}$ the connection to the lepton masses in MeV.
	\item \textbf{Via $m_{\text{char}}$ or $m_e$}: The electron mass $m_e = 0{.}511\,\text{MeV}$ is experimentally defined and links $\xipar$ to SI units via $G = \xipar^2/(4m_e) \times C_{\text{dim}} \times C_{\text{conv}} \times \Kfrak$.
	\item \textbf{Via $\lP$}: The Planck length $\lP = \sqrt{\hbar G/c^3}$ is experimentally accessible and gives directly $L_0 = \xipar \cdot \lP$ in metres.
\end{itemize}

\subsection{Which Entry is Fundamental?}

In T0/FFGFT the most natural entry is via $\alpha$, because:
\begin{itemize}
	\item $\alpha$ is itself derived from $\xipar$: $\alpha = \xipar \cdot E_0^2 / (1\,\text{MeV})^2$
	\item $\alpha$ is dimensionless — the transition to SI units occurs only through the choice of unit scale (MeV)
	\item The 2019 SI reform implemented exactly this calibration, which is consistent with the T0 geometry (Document 013)
\end{itemize}

\begin{keyresult}[Epistemological Classification]
The derivation chain in this document is internally consistent and free of postulates. The only external input is the choice of an SI unit scale — for example via $m_e$ in MeV or $\lP$ in metres. This input is not a circularity of the theory, but the necessary calibration of every physical theory to the world of measurement. Treated in detail in Document 056 (Universal Derivation) and Document 101 (Circularity of Constants).
\end{keyresult}
