% ==============================================================================
% T0 Theory / FFGFT: Document 185 (Chapter Content)
% Title: Time as the Embedding Price of Mathematics:
%        Factorisation, Quantum Computers, and the Physical Limit of RSA Decomposition
% Author: Johann Pascher
% Date: April 2026
% References:
%   Doc. 075: T0-Shor algorithm and precision barrier
%   Doc. 076: Empirical factorisation tests
%   Doc. 057: Relational number system, primes as irreducible ratios
%   Doc. 183: Willow, T_rev, recursion and time
% ==============================================================================

\section*{Abstract}

Factorisation is a timeless identity in pure mathematics: $N = p \cdot q$ exists
without process, without runtime, without error. As soon as this identity is
physically realised — whether on a quantum processor, a classical server, or the
vacuum field itself — information must flow. Flow requires time. And time, defined
in FFGFT by the fundamental revolution time $T_\text{rev} = \xipar \cdot \ell_P / c$,
accumulates phase errors.

This document shows: it is not insufficient qubit count or poor hardware that
limits RSA decomposition by quantum computers, but the intrinsic time-phase coupling
of physical spacetime. There is a scaling limit beyond which even the best future
quantum computer fails — geometrically forced, not technically circumventable.

At the same time, the same geometry yields a positive result: error correction can
be massively improved when one accounts for the fact that the vacuum field has
preferred resonance points. These are not artefacts — they are the stable torus
modes to which the physical system naturally returns.

\clearpage

\section{The Paradox of Timelessness}

\subsection{Two Worlds: Mathematics and Physics}

In pure mathematics, factorisation $N = p \cdot q$ is a \textbf{timeless identity}.
There is no process — only a static fact, simultaneously and always true. The prime
$p$ does not need to be searched; it is already contained in $N$ without ever having
been ``placed'' there.

In physical reality this is different. Whether on Google's Willow processor, a
classical server, or the human brain: every computation requires that information
flows from one place to another. Flow means time. Time means phase drift.

\begin{keypoint}[The Central Distinction]
\textbf{Mathematics:} $N = p \cdot q$ — timeless, error-free, without process.

\textbf{Physics:} To \emph{extract} $p$ and $q$ from $N$, a measurement must
take place — a period $r$ must be found in the feedback $f(x) = a^x \bmod N$.
This requires runtime $t = n \cdot T_\text{rev}$.
Runtime accumulates phase errors. Beyond a critical $N$, the error exceeds the
coherence threshold before the resonance is found.
\end{keypoint}

\subsection{Static Knowledge vs. Dynamic Process}

An important distinction: known prime numbers do not need to be searched again.
They exist as already identified, stable resonance points — entered in tables,
stored in databases. This \textbf{knowledge} is static: retrieving a known prime
costs no runtime.

But the \emph{use} of these known primes to decompose a new, unknown number $N$
is not a static comparison — it is a \textbf{dynamic process}. Using known primes
shortens the search, but verifying the phase coincidence between a candidate and $N$
requires physical runtime.

\begin{technical}[Knowledge vs. Process in FFGFT Language]
In the language of torus resonances (Doc.~183):

\textbf{Known prime $p$:} Stored winding number — a topologically stable node
that exists without further effort.

\textbf{Factorising $N$:} Checking whether the winding number of $N$ can be
written as the product of two known winding numbers $p \cdot q$. This check
requires the quantum processor to physically establish the phase coincidence
between $p$, $q$, and $N$ — in real time, with accumulated phase error.
\end{technical}


\section{Factorisation as Resonance Search in Time}

\subsection{Period Finding as a Physical Process}

Shor's algorithm (and T0-Shor, Doc.~075) solve factorisation through
\textbf{period finding}: one searches for the period $r$ of the function
$f(x) = a^x \bmod N$. This period encodes the prime factors:
\begin{equation}
    a^r \equiv 1 \pmod{N}
    \;\Rightarrow\;
    a^r - 1 = (a^{r/2} - 1)(a^{r/2} + 1) \equiv 0 \pmod{N}
\end{equation}
The sought resonance frequency is $\nu_r = 1/r$. The required resolution is
(Doc.~075):
\begin{equation}
    \Delta f_\text{required} \approx \frac{f_0}{r^2}
\end{equation}
For cryptographically relevant numbers with $r \approx N$:

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Key length} & \textbf{Required precision $\epsilon$} & \textbf{Status} \\
\hline
27-bit & $\epsilon \approx 10^{-16}$ & 64-bit hardware sufficient \\
\hline
56-bit & $\epsilon \approx 10^{-34}$ & 128-bit hardware sufficient \\
\hline
RSA-1024 & $\epsilon \approx 10^{-617}$ & physically impossible \\
\hline
RSA-2048 & $\epsilon \approx 10^{-1234}$ & physically impossible \\
\hline
\end{tabular}
\caption{Precision barrier for factorisation (after Doc.~075)}
\end{table}

\subsection{Why Runtime Accumulation Is Unavoidable}

In FFGFT, time is not an external clock but the accumulated travel time of the
field through its own geometry — measured in multiples of $T_\text{rev}$ (Doc.~183):
\begin{equation}
    T_\text{rev} = \frac{\xipar \cdot \ell_P}{c} \approx 7.2 \times 10^{-48}\,\text{s}
\end{equation}
To find the period $r$, the system must complete $r$ revolutions — a total runtime
of $t = r \cdot T_\text{rev}$. At each revolution a phase error $\varepsilon$
accumulates. After $r$ cycles the total error is $r \cdot \varepsilon$.

Coherence collapses as soon as the phase error exceeds $\pi/2$:
\begin{equation}
    r_\text{crit} \approx \frac{\pi}{2\varepsilon}
\end{equation}
For RSA keys, $r \approx N$ is enormous. The required precision per step scales as
$\varepsilon \lesssim \pi/(2N)$ — which for RSA-1024 demands the physically
impossible precision $\epsilon \approx 10^{-617}$.

\begin{foundation}[Runtime Accumulation as a Law of Nature]
This is not a technical constraint that better hardware can overcome.
It is a consequence of the structure of physical reality:

\begin{equation}
    \Psi(t) = G\!\left(\Psi(t - T_\text{rev}),\; \xipar\right)
\end{equation}

Every computational step is one revolution on the torus. Every revolution
accumulates $\Delta\phi = 2\pi \cdot \xipar$. For $r \approx N$ revolutions
at RSA key lengths, the accumulated error $r \cdot \Delta\phi \approx N \cdot
2\pi \cdot \xipar$ is far beyond the coherence threshold.
\end{foundation}


\section{Why the Quantum Computer Still Fails}

\subsection{The Threshold Theorem and Its Limits}

Standard quantum information theory appeals to the \textbf{threshold theorem}:
when the error rate per gate falls below a critical threshold, quantum error
correction (QEC) can correct errors faster than they arise. The logical state
then lives theoretically indefinitely.

FFGFT reveals a fundamental limit to this argument:

\begin{important}[QEC Is Itself a Recursive Process]
QEC requires runtime — every error correction is itself a sequence of gate
operations that costs $T_\text{rev}$. The correction adds new phase errors
to the system, which must themselves be corrected.

For small $N$ (short periods, few cycles) the correction outweighs the error
— the threshold theorem holds. For large $N$ (RSA keys) the correction itself
becomes part of the problem: the recursion depth of error correction is so
large that its phase error assumes the same character as the original noise.
\end{important}

The standard literature's argument — ``error correction defeats time'' — holds
in the regime of short periods. In the RSA regime with $r \approx 10^{308}$
(RSA-1024), it fails in principle.

\subsection{RSA as a Geometric Shield}

In the FFGFT perspective, the difficulty of RSA factorisation is not a lack of
computing power but a \textbf{shield of spacetime geometry}:

Large primes generate such long-period resonances in the feedback system
$a^x \bmod N$ that no physical system — which is itself part of this spacetime and
itself described by $T_\text{rev}$ and $\xipar$ — can maintain the necessary phase
stability over the runtime $r \cdot T_\text{rev}$.

\begin{conclusionBox}[The Wall Between Mathematics and Physics]
Mathematics says: $N = p \cdot q$ is trivially true.

Physics says: To \emph{discover} this truth, a system must sustain coherence for a
period of $r \approx N$ cycles. For RSA-1024 this means $r \approx 10^{308}$ cycles
at precision $\epsilon \approx 10^{-617}$ per cycle.

That is the wall. Not made of metal — made of time and phase.
\end{conclusionBox}


\section{The Positive Result: Resonance Points Improve Error Correction}

\subsection{Preferred Resonance Points in the Torus Spectrum}

From the same geometry that limits RSA decomposition follows a positive result for
quantum error correction. The torus spectrum is not uniform: modes contribute as
$1/n^2$, and prime modes are the irreducible resonance nodes. This means there are
\textbf{preferred, geometrically stable positions} in the state space of the quantum
computer.

Standard correction (threshold theorem) treats all errors statistically and projects
onto an arbitrary target state. FFGFT-informed error correction recognises that
certain states are \textbf{geometrically preferred} — they correspond to stable
torus modes to which the system naturally returns.

\subsection{Resonance Correction Instead of Statistical Correction}

Rather than correcting every error independently, one can interpret errors as
\textbf{drifting from stable resonance points}. Correction then consists of actively
returning the system to the nearest stable resonance node — not to an arbitrary
codeword state.

\begin{keyresult}[Improvement Potential Through Resonance Correction]
When error correction is geometrically informed — using preferred torus modes as
anchor points — it can correct errors more efficiently than the statistical method.
The rate at which errors accumulate remains the same; but the rate at which they
are corrected increases, because the corrective moves point toward natural attractors
of the system.

This is not a contradiction of the fundamental runtime barrier: for small $N$,
resonance correction helps considerably. For RSA key lengths, the period $r$ exceeds
the reach of any correction.
\end{keyresult}

\subsection{Practical Consequences for Willow and Successors}

Google's Willow demonstrates exponential error suppression with growing code distance
$d$ (Doc.~183) — this is experimental evidence that topologically stable modes are
accessible. The FFGFT perspective says:

\begin{itemize}
    \item \textbf{What Willow already does:} Projection onto topologically stable
    torus modes — implicitly, without knowing the geometric structure.
    \item \textbf{What resonance correction could achieve:} Explicit use of the
    $1/n^2$ structure of the torus spectrum to direct corrections toward the most
    stable modes.
    \item \textbf{What remains in principle impossible:} Breaking RSA keys in the
    cryptographically relevant range — because the period $r \approx N$ exceeds the
    coherence time of any physical hardware.
\end{itemize}


\section{Counter-Arguments and FFGFT Responses}

\begin{table}[ht]
\centering
\begin{tabular}{|p{5cm}|p{7.5cm}|}
\hline
\textbf{Standard Argument} & \textbf{FFGFT Response} \\
\hline
Threshold theorem: QEC defeats time & QEC is itself a recursive process with
runtime. For $r \approx 10^{308}$, correction becomes part of the noise. \\
\hline
Shor is polynomial: $O((\log N)^3)$ steps & Polynomiality holds for logical
complexity. Phase precision $\epsilon \sim 1/N^2$ grows exponentially —
physically, not logically. \\
\hline
Better hardware $\Rightarrow$ smaller $\epsilon$ & There is no $\epsilon = 0$.
All hardware is embedded in spacetime, thus described by $T_\text{rev}$ and
$\xipar$. Geometric phase drift is intrinsic. \\
\hline
Topological qubits solve the problem & Topological qubits improve error rates —
they do not eliminate runtime accumulation. For RSA-1024, even $\epsilon \to 10^{-16}$
is insufficient; one would need $10^{-617}$. \\
\hline
\end{tabular}
\caption{Standard arguments of quantum information theory and FFGFT responses}
\end{table}


\section{Summary}

Time is the toll paid when mathematics is brought into physical reality. For small
numbers this toll is affordable — quantum computers can and will break short-key
cryptography. For RSA keys of present and future cryptography the toll is
astronomical.

\begin{foundation}[Three Statements of This Document]
\begin{enumerate}
    \item \textbf{Physical limit:} RSA-1024 and larger remains protected from
    quantum computers by the runtime accumulation of spacetime geometry ($T_\text{rev}$,
    $\xipar$) — not by technical deficiencies, but by laws of nature.

    \item \textbf{Static knowledge vs.\ dynamic process:} Known primes cost no
    runtime. Applying them to a new number $N$ requires a physical phase coincidence —
    and that costs $r \cdot T_\text{rev}$.

    \item \textbf{Positive result:} Error correction can be considerably improved
    through geometrically informed resonance correction (using preferred torus modes)
    — for small $N$, short periods, and practical quantum algorithms in the reachable
    range.
\end{enumerate}
\end{foundation}

\vspace{0.8cm}
\noindent
\textit{Draft. The statement on the physical impossibility of RSA decomposition at
large key lengths is qualitatively motivated from FFGFT dynamics. A quantitative
derivation of the precise scaling limit requires further formalisation of the
connection between $T_\text{rev}$, $\xipar$, and the threshold condition of Shor's
algorithm.}

\begin{thebibliography}{9}

\bibitem{Dok075}
J.~Pascher, \textit{T0-Shor Algorithm: Energy Field Formulation and Precision
Barrier}, T0 Document~075 (2025).

\bibitem{Dok076}
J.~Pascher, \textit{Empirical Factorisation Tests}, T0 Document~076 (2025).

\bibitem{Dok057}
J.~Pascher, \textit{Relational Number System: Primes as Irreducible Ratios},
T0 Document~057 (2025).

\bibitem{Dok183}
J.~Pascher, \textit{Google Willow and the Physics of Self-Measurement:
$T_\text{rev}$ as Fundamental Revolution Time}, T0 Document~183 (2026).

\bibitem{Shor1997}
P.~W.~Shor, \textit{Polynomial-Time Algorithms for Prime Factorization and
Discrete Logarithms on a Quantum Computer}, SIAM J.\ Comput.\ \textbf{26}
(1997), 1484--1509.

\bibitem{GoogleWillow2024}
Google Quantum AI, \textit{Quantum error correction below the surface code
threshold}, Nature (2024), DOI: 10.1038/s41586-024-08449-y.

\end{thebibliography}
