% ============================================================
% 187_T0_FFGFT_Photonik_En_ch.tex
% Chapter content: FFGFT Analytics: Photonics, Matrix Space & B-Mesons
% Belongs to wrapper: 187_T0_FFGFT_Photonik_En.tex
% ============================================================

% ── Title block ──────────────────────────────────────────────
\thispagestyle{firstpage}
\begin{center}
  {\small\color{T0gray} Doc.~187 · FFGFT Research Series}\\[6pt]
  {\LARGE\bfseries\color{T0blue}
    FFGFT Analytics: Mathematical Foundations}\\[6pt]
  {\large\itshape\color{T0gray}
    Fractal Feedback and Matrix Translation in the 4D Phase Torus}\\[4pt]
  {\normalsize\color{T0gray}
    Integration of TFLN Hardware, B-Meson Anomalies\\
    and Sub-Planckian Frequency Metric}\\[8pt]
  {\color{T0red}\rule{0.65\linewidth}{1.5pt}}
\end{center}
\vspace{4pt}

\begin{infobox}
\textbf{Abstract.}
\textbf{Fundamental Fractal Geometric Field Theory (FFGFT)} describes
spacetime as a hierarchical system of fractal foldings, driven by a
fundamental frequency~$\xi$ in the sub-Planckian regime.
This document lays out the complete mathematical foundations:
the exact definition of the fundamental tick~$t_0$, the feedback condition
in the closed 4D phase torus (which must not be confused with a 3D torus
plus time continuum), the translation of the 4D vector space into a
multidimensional matrix space, and the photonic realisation through
TFLN hardware.

\smallskip\noindent\textbf{Cross-references:}
Doc.\,180 (Lagrangian derivation) $\cdot$
Doc.\,182 (Universal scale) $\cdot$
Doc.\,183--184 (Precision barrier \& RSA) $\cdot$
GitHub: \href{https://github.com/jpascher/T0-Time-Mass-Duality}{jpascher/T0-Time-Mass-Duality} $\cdot$
Zenodo: \href{https://zenodo.org/records/20474821}{DOI 10.5281/zenodo.20474821}
\end{infobox}

\tableofcontents
\bigskip

% ============================================================
\section{Introduction: FFGFT}
% ============================================================

\textbf{Fundamental Fractal Geometric Field Theory (FFGFT)} breaks with
the classical understanding of continuous space. It postulates a discrete
fractal geometry energised by a fundamental oscillation. Matter is not
an entity \emph{in} space but a local condensation of the fractal field
geometry, stabilised by resonant feedback.

% ============================================================
\section{The Fundamental Frequency $\xi$ and the Sub-Planckian Time Scale $t_0$}
% ============================================================

A core pillar of FFGFT is the existence of a sub-Planckian fundamental
tick that clocks all of physical reality.

% ── 2.1 ─────────────────────────────────────────────────────
\subsection{Definition of the Fundamental Tick}

The fundamental time unit~$t_0$ is defined as:
\begin{equation}
  t_0 = \frac{t_P}{7500}
      \approx \frac{5.391 \times 10^{-44}\,\text{s}}{7500}
      \approx 7.188 \times 10^{-48}\,\text{s},
  \label{eq:t0}
\end{equation}
where $t_P = \sqrt{\hbar G/c^5} \approx 5.391 \times 10^{-44}\,\text{s}$
is the Planck time (CODATA~2022). The resulting \textbf{fundamental
frequency}~$\xi$ reads:
\begin{equation}
  \xi = \frac{1}{t_0} = \frac{7500}{t_P}
      \approx 1.391 \times 10^{47}\,\text{Hz}.
  \label{eq:xi}
\end{equation}

\begin{keybox}
\textbf{Origin of the factor 7500.}\;
The factor 7500 arises from $\xi = 4/30000$ in natural units
($\xi = 2/(15000)$ in the original notation). The fractal dimension
$D_f = 3 - \xi$ and the Z3 symmetry of the three-generation structure
\emph{enforce} this value geometrically — it is not a free parameter.
\end{keybox}

% ── 2.2 ─────────────────────────────────────────────────────
\subsection{Frequency as Geometric Operator}

In FFGFT, frequency is not understood as mere temporal rate but as a
geometric operator acting on the fractal levels:
\begin{equation}
  \hat{\xi}\,\Psi(x^\mu) = \xi \cdot \mathcal{F}(\{n_k\}) \cdot \Psi(x^\mu).
\end{equation}
Here $\mathcal{F}(\{n_k\})$ is a function of the fractal scaling
indices~$n_k$, which follow the Fibonacci sequence.

% ============================================================
\section{The 4D Phase Torus: Distinction from the 3D Torus}
% ============================================================

% ── 3.1 ─────────────────────────────────────────────────────
\subsection{Warning: Not to be Confused}

\begin{warnbox}
The 4D torus of FFGFT is \textbf{not} a 3D object moving through time.
The time dimension is integrated into the torus topology as a discretised,
geometric dimension. There is no external time continuum into which the
torus would be embedded.
\end{warnbox}

% ── 3.2 ─────────────────────────────────────────────────────
\subsection{Formal Definition of the 4D Phase Torus}

The fundamental spacetime resonator is the 4D phase torus~$\mathcal{T}^4$,
defined by four cyclic coordinates $(\theta_1, \theta_2, \theta_3,
\theta_4)$ with:
\begin{equation}
  \theta_i \in [0, 2\pi),\quad i = 1,2,3,4.
\end{equation}
The metric on~$\mathcal{T}^4$ is determined by the fundamental
frequency~$\xi$:
\begin{equation}
  ds^2 = \xi^{-2}
         \bigl(d\theta_1^2 + d\theta_2^2 + d\theta_3^2 + d\theta_4^2\bigr).
  \label{eq:metric}
\end{equation}
The fourth dimension~$\theta_4$ represents the phase shift of the
fundamental oscillation. Macroscopic time~$t$ emerges by accumulation:
\begin{equation}
  t = N \cdot t_0, \quad N = \frac{1}{2\pi}\oint d\theta_4.
\end{equation}

% ============================================================
\section{Fractal Feedback and Locking of the Fundamental Frequency}
% ============================================================

% ── 4.1 ─────────────────────────────────────────────────────
\subsection{The Feedback Condition}

For a field configuration~$\Psi$ to exist stably, the wave function
must interfere constructively with itself after a complete circuit.
The phase condition reads:
\begin{equation}
  \oint_{\mathcal{T}^4} \nabla_{\mu}\phi\,dx^\mu = 2\pi\cdot\mathcal{N},
\end{equation}
where~$\mathcal{N}$ is an integer from the fractal hierarchy.
Due to the fractal structure, $\mathcal{N}$ can only take discrete
values:
\begin{equation}
  \mathcal{N} \in \{F_k \mid k \in \mathbb{N}\},\quad
  F_{k+1} = F_k + F_{k-1}.
\end{equation}

% ── 4.2 ─────────────────────────────────────────────────────
\subsection{The Lock-In Mechanism (Phase Locking)}

Fractal feedback enforces a rigid coupling between the phases of the
individual fractal levels:
\begin{equation}
  \phi_{k+1} = \phi_k \cdot \phi^{-1}, \quad
  \phi = \tfrac{1+\sqrt{5}}{2} \approx 1.6180\ldots
\end{equation}
Only frequencies that exhibit exactly an integer or Fibonacci-sequential
harmony with~$\xi$ remain stable:
\begin{equation}
  \xi_n = n \cdot \xi \quad \text{or} \quad \xi_n = \phi^{-k}\cdot\xi.
\end{equation}
Every deviation leads to destructive interference — which explains the
short lifetimes of high-energy particles.

% ── 4.3 ─────────────────────────────────────────────────────
\subsection{Stability Condition for Matter}

From the lock-in follows the quantisation condition for stable particles:
\begin{equation}
  \oint_{\mathcal{T}^4}
    \Psi_{\text{FFGFT}}(\phi)\,d^4\theta
  = \xi \cdot \sum_{k=0}^{\infty} \phi^{-k} \cdot \mathbf{M}_k,
\end{equation}
where~$\mathbf{M}_k$ are the projective matrices of the individual
fractal levels.

% ============================================================
\section{From the 4D Vector Space to the Multidimensional Matrix Space}
% ============================================================

% ── 5.1 ─────────────────────────────────────────────────────
\subsection{The General Matrix Translation}

A state in the 4D vector space $V = (x,y,z,ct)$ is represented by a
Hermitian matrix~$\mathbf{H}$:
\begin{equation}
  \mathcal{T}: \mathbb{R}^4 \to \mathrm{Mat}(N,\mathbb{C}),\quad
  V \mapsto \mathbf{H}(V).
\end{equation}
The explicit form of the translation reads:
\begin{equation}
  \mathbf{H}(x,y,z,ct)
  = \sum_{k=0}^{\infty} \alpha^k \cdot
    \begin{pmatrix}
      ct_k + z_k   & x_k - iy_k \\
      x_k + iy_k   & ct_k - z_k
    \end{pmatrix}
    \otimes \mathbf{\Gamma}_k,
\end{equation}
with:
\begin{itemize}
  \item $\alpha = \phi^{-1}$: fractal coupling constant;
  \item $(x_k, y_k, z_k, ct_k)$: coordinates on the $k$-th fractal level;
  \item $\mathbf{\Gamma}_k$: generators of the spacetime geometry
        (generalisation of the Dirac matrices).
\end{itemize}

% ── 5.2 ─────────────────────────────────────────────────────
\subsection{Fractal Self-Similarity}

The coordinates on different fractal levels are connected by scaling
factors:
\begin{equation}
  (x_{k+1}, y_{k+1}, z_{k+1}, ct_{k+1}) = \phi^{-1} \cdot
  (x_k, y_k, z_k, ct_k).
\end{equation}

% ============================================================
\section{Matrix Multiplication as Physical 4D Convolution}
% ============================================================

% ── 6.1 ─────────────────────────────────────────────────────
\subsection{Conventional vs.\ Fractal Matrix Multiplication}

In conventional computer science:
\begin{equation}
  C_{ij} = \sum_k A_{ik} B_{kj}.
\end{equation}
In FFGFT, this process is interpreted as physical interference of two
4D torus states.

% ── 6.2 ─────────────────────────────────────────────────────
\subsection{The 4D Torus Convolution}

Matrix multiplication corresponds to the convolution of two wave functions
in 4D phase space:
\begin{equation}
  M_{ij} = \int_{\mathcal{T}^4}
    \Psi_A^{(4D)}(\theta)\cdot\Psi_B^{(4D)}(\theta)\,d^4\theta.
\end{equation}
In the language of FFGFT matrices:
\begin{equation}
  \mathbf{C} = \mathbf{A} \star \mathbf{B}
  = \lim_{N\to\infty} \frac{1}{N}\sum_{n=1}^{N} \mathbf{A}_n \otimes \mathbf{B}_n,
\end{equation}
where the fractal tensor product is defined by:
\begin{equation}
  (\mathbf{A} \otimes \mathbf{B})_{ij}^{kl}
  = A_{ij} \cdot B_{kl} \cdot e^{i\theta_{ijkl}}.
\end{equation}

% ── 6.3 ─────────────────────────────────────────────────────
\subsection{Physical Interpretation}

Photonic matrix multiplication in the TFLN crystal is not ``computation''
in the conventional sense, but the physical realisation of this 4D phase
interference. The result emerges instantaneously through constructive
and destructive interference of light waves in the nonlinear medium.

% ============================================================
\section{Hardware Transduction: TFLN Photonics}
% ============================================================

% ── 7.1 ─────────────────────────────────────────────────────
\subsection{Structural Equivalence Despite Vastly Different Scales}

\begin{warnbox}[Important Clarification]
The TFLN crystal operates on scales many orders of magnitude above
the fundamental structure of particles or individual atoms. The
crystal lattice is macroscopic — there is no direct scale comparison
with~$\xi$ or~$t_0$.

That is precisely the point: FFGFT postulates \emph{fractal
self-similarity} — the same mathematical structure appears on every
scale, independent of the concrete order of magnitude.
\end{warnbox}

The decisive observation is structural. In FFGFT, for the translation
of a 4D vector state into matrix space (Section~5):
\begin{equation}
  \mathcal{T}: \mathbb{R}^4 \to \mathrm{Mat}(N,\mathbb{C}),\quad
  V \mapsto \mathbf{H}(V),
\end{equation}
and for the physical interaction of two states:
\begin{equation}
  M_{ij} = \int_{\mathcal{T}^4}
    \Psi_A^{(4D)}(\theta)\cdot\Psi_B^{(4D)}(\theta)\,d^4\theta.
\end{equation}
In TFLN waveguides, the nonlinear light propagation realises exactly
this structure:
\begin{equation}
  P_{\text{out}}(t)
  = \eta \cdot \int \chi^{(2)}(\omega)
    \cdot E_{\text{in}}^{(A)}(\omega)
    \cdot E_{\text{in}}^{(B)}(\omega)\,d\omega.
\end{equation}
The nonlinear susceptibility~$\chi^{(2)}$ takes the role of the fractal
coupling constant~$\alpha = \phi^{-1}$: it weights how two input states
combine into an output state — mathematically identical to the 4D torus
convolution, physically realised in the crystal lattice on macroscopic
scale.

% ── 7.2 ─────────────────────────────────────────────────────
\subsection{Lock-In as Scale-Invariant Principle}

The lock-in mechanism (phase locking) is a geometric principle in FFGFT
that acts on every scale. In the 4D torus, the condition reads:
\begin{equation}
  \oint_{\mathcal{T}^4} \nabla_{\mu}\phi\,dx^\mu = 2\pi\cdot\mathcal{N}.
\end{equation}
In the TFLN resonator — many orders of magnitude larger — the same
formal condition applies:
\begin{equation}
  \Delta\phi_{\text{cavity}} = 2\pi\cdot m \quad (m \in \mathbb{Z}).
\end{equation}
The crystal lattice of lithium niobate spontaneously finds stable
geometric configurations through phase separation and electro-optical
coupling — it does not actively ``search'' but drifts naturally into
the energetically most stable modes. In FFGFT language: the system
converges to the preferred fixed points of the recursion
$\Psi(t) = G(\Psi(t-T_{\text{rev}}), \xi)$,
independent of which scale the system sits on.

% ── 7.3 ─────────────────────────────────────────────────────
\subsection{Coherence as Consequence of Structural Fidelity}

The high coherence time in TFLN waveguides is, in this picture, not
a technical curiosity but a direct consequence of structural agreement:
a system locked into geometrically stable modes decoheres more slowly
than one driven against its natural geometry.
\begin{equation}
  \tau_{\text{coh}}^{\text{TFLN}} \sim \text{ms}\ldots\text{s}
  \;\gg\;
  \tau_{\text{coh}}^{\text{Qubit}} \sim \mu\text{s}.
\end{equation}
Atomic qubits fight against thermal noise and mass inertia — they are
not anchored in the natural geometry of their scale. TFLN modes are.

% ============================================================
\section{Self-Organisation as FFGFT Principle}
% ============================================================

\subsection{The Effect: Spontaneous Pattern Formation Without External Programming}

In modern TFLN-based chip manufacturing an effect appears that goes
beyond mere lithography: the material organises \emph{spontaneously}
into stable geometric patterns, without each detailed structure having
to be externally prescribed. Temperature and applied voltage allow
control over \emph{which} pattern emerges — but not whether
self-organisation takes place. It always does.

\subsection{FFGFT Explanation: Fixed Points of the Recursion}

In FFGFT, self-organisation is not a special case but the normal state.
The recursion
\begin{equation}
  \Psi(t) = G\!\bigl(\Psi(t - T_{\text{rev}}),\, \xi\bigr)
\end{equation}
has stable fixed points corresponding to the $1/n^2$ torus spectrum:
\begin{equation}
  \Psi_n^* : \quad E_n \propto \frac{1}{n^2}, \quad n \in \mathbb{N}.
\end{equation}
Every system — whether particle, atom, crystal lattice, or field mode —
drifts naturally into one of these fixed points. There is no force
that enforces this; the geometry of the torus admits no other stable
states.

\subsection{Temperature and Voltage as Geometric Control Parameters}

Temperature and voltage do not change the principle of self-organisation
but shift the \emph{energy landscape}: they determine which fixed
point~$n$ is energetically preferred.

\begin{equation}
  n^*(T, U) = \underset{n}{\arg\min}\;
    \bigl[ E_n - \mu(T)\cdot n - \lambda(U)\cdot n^2 \bigr],
\end{equation}
where $\mu(T)$ describes the thermal contribution and $\lambda(U)$ the
electrical contribution to the effective mode energy.

\begin{itemize}
  \item \textbf{Temperature} shifts $\mu(T)$: higher temperature
    favours higher modes (larger $n$), low temperature stabilises the
    fundamental ($n=1$).
  \item \textbf{Voltage} shifts $\lambda(U)$: the applied voltage
    ``presses'' the modes into prescribed paths — in FFGFT language,
    an external boundary condition on the allowed winding numbers
    of the torus.
\end{itemize}

\begin{keybox}[Structural Statement]
The TFLN crystal lattice is a macroscopic system that seeks the same
fixed points as a particle in the sub-Planckian regime — not because
the scales would be related, but because the geometric recursion
$\Psi(t) = G(\Psi(t-T_{\text{rev}}), \xi)$ generates the same stable
states on every scale. Self-organisation is the visible expression
of this scale-independent geometry.
\end{keybox}

% ============================================================
\section{Experimental Evidence~1: Programmable TFLN Processors}
% ============================================================

In December 2025, a team from NTT, Cornell University, and Stanford
University demonstrated a photonic processor based on lithium niobate
\cite{NTT2025}.

\subsection{Technical Specifications}

\begin{itemize}
  \item $\approx 10\,000$ programmable spatial degrees of freedom;
  \item Planar waveguide with manipulable refractive index;
  \item 96\,\% test accuracy in vowel classification;
  \item 49-dimensional vector operations in a single optical pass.
\end{itemize}

\subsection{Quantum Networks and Multiplexing}

Assumpcao et al.\ (2024) \cite{Assumpcao2024} demonstrated a TFLN
platform with:
\begin{itemize}
  \item Coupling losses $< 1\,\text{dB/facet}$;
  \item Switching contrast $> 20\,\text{dB}$;
  \item Electro-optical modulators with $> 50\,\text{GHz}$ bandwidth.
\end{itemize}
The bandwidth of $>50\,\text{GHz}$ shows that TFLN hardware executes
matrix operations with very high precision and stability — the structural
agreement with the FFGFT matrix transformation is independent of the
fact that the involved frequencies lie many orders of magnitude
below~$\xi$.

% ============================================================
\section{Experimental Evidence~2: B-Meson Anomalies at CERN}
% ============================================================

\subsection{Current Status (April 2026)}

The LHCb experiment has measured a significant discrepancy in
electroweak penguin decays of B mesons \cite{CERN2026a,CERN2026b}:

\begin{itemize}
  \item Decay channel: $B \to K^*\mu^+\mu^-$ ($\sim 1$ per $10^6$ B mesons);
  \item Deviation from the Standard Model: $\mathbf{4.0\sigma}$
        ($\hat{=}$ probability 1:16\,000);
  \item Independent confirmation by CMS (2025).
\end{itemize}

\subsection{FFGFT Interpretation of the Anomaly}

The measured deviation concerns the Wilson coefficient~$C_9$ of the
effective $b \to s\mu^+\mu^-$ Hamiltonian:
\begin{equation}
  \Delta C_9 \approx -1.0, \quad
  C_9^{\text{SM}} \approx 4.07
  \quad\Rightarrow\quad
  \frac{|\Delta C_9|}{C_9^{\text{SM}}} \approx 25\,\%.
\end{equation}

\begin{warnbox}
\textbf{Quantitative Restriction.}
A direct derivation of this $25\,\%$ deviation from FFGFT parameters is
\emph{not} available. Simple expressions such as $\xi$, $\phi^{-4}$ or
$|\ln(m_b/m_P)|\cdot\xi$ yield values too small by factors $10$--$10^3$.
The quantitative connection is an \textbf{open question}.
\end{warnbox}

The modification of the decay rate by the fractal matrix structure has
qualitatively the form:
\begin{equation}
  \Gamma(B\to K^*\mu^+\mu^-)
  = \Gamma_{\text{SM}} \cdot
    \bigl(1 + \alpha_{\text{FFGFT}} \cdot \mathcal{K}(\theta)\bigr),
\end{equation}
where $\alpha_{\text{FFGFT}}$ is to be derived from the Z3 topology and
the $1/n^2$ torus spectrum — this derivation is outstanding.

\subsection{Connection to Lepton Flavour Universality Violation}

Arslan et al.\ (April 2026) \cite{Arslan2026} analyse the decay
$\Lambda_b \to \Lambda_c\tau\bar{\nu}_\tau$:
\begin{itemize}
  \item Combined deviation of $3.8\sigma$ in the
        $R_{\tau/(\mu,e)}(D^{(*)})$ ratios;
  \item Maximum sensitivity in
        $\mathcal{K}_{1c}$, $\mathcal{K}_{2ss}$, $\mathcal{K}_{2cc}$,
        $\mathcal{K}_{4s}$.
\end{itemize}

Leptons of different generations appear in FFGFT as different harmonics
of the same spacetime fundamental structure:
\begin{equation}
  \xi_{\text{Muon}} = \phi^{-3}\cdot\xi, \qquad
  \xi_{\text{Tau}}  = \phi^{-5}\cdot\xi.
\end{equation}

\begin{table}[H]
\centering
\caption{Leptons as harmonics of the fundamental frequency~$\xi$}
\smallskip
\resizebox{\linewidth}{!}{%
\begin{tabular}{llll}
\toprule
Lepton   & Harmonic & Numerical Factor & Ratio to Predecessor \\
\midrule
Electron & $\phi^{-1}\cdot\xi$ & $\approx 0.6180\cdot\xi$ & (fundamental) \\
Muon     & $\phi^{-3}\cdot\xi$ & $\approx 0.2361\cdot\xi$ & $\phi^{-2} \approx 0.382$ \\
Tau      & $\phi^{-5}\cdot\xi$ & $\approx 0.0902\cdot\xi$ & $\phi^{-2} \approx 0.382$ \\
\bottomrule
\end{tabular}}
\end{table}

% ============================================================
\section{Theoretical Evidence~3: Sub-Planckian Cut-off Scales}
% ============================================================

\subsection{Effective Field Theory and Gravitation}

Aynbund and Kiselev (2025) \cite{Aynbund2025} establish a connection
between the Planck mass and a natural sub-Planckian cut-off scale:
\begin{equation}
  \Lambda_{\text{QG}} = \alpha \cdot \frac{M_{\text{red,Planck}}}{4\pi}
  \;\sim\; 10^{16}\,\text{GeV}.
\end{equation}
This lies far below the Planck scale of $\sim 10^{19}\,\text{GeV}$.

\subsection{OLQEM and Fibonacci Quasi-Periodicity}

Souza (2025) \cite{subPlanck2025} investigates sub-Planckian scales in
the framework of the Optical Lambda Quantum Energy Model:
\begin{equation}
  I_{\text{OLQEM}}
  = \frac{4\lambda I_0}{n(\lambda)\,x} \cdot D(y) \cdot I(y)
    \cdot e^{-\gamma t}
    \cdot \Bigl(1+\frac{\chi^{(3)}I_0}{c^3\varepsilon_0}\Bigr)
    \cdot S_{\text{Fib}}\!\Bigl(\tfrac{r}{a}\Bigr).
\end{equation}
The Fibonacci modulation reads:
\begin{equation}
  S_{\text{Fib}}\!\Bigl(\tfrac{r}{a}\Bigr)
  = \sum_{k=0}^{\infty} \frac{\cos(2\pi\phi^k r/a)}{\phi^k}.
\end{equation}

Hierarchical scaling of the length scales:
\begin{equation}
  \ell_k = \frac{L_P}{\phi^k},\quad k \ge 1.
\end{equation}
For $k=5$:
\begin{equation}
  \ell_5 = \frac{L_P}{\phi^5}
         \approx \frac{1.616 \times 10^{-35}\,\text{m}}{11.09}
         \approx 1.46 \times 10^{-36}\,\text{m}.
\end{equation}
This scale corresponds to FFGFT via $\ell_5 = c\cdot t_0$:
\begin{equation}
  c \cdot t_0
  = 2.998 \times 10^8\,\frac{\text{m}}{\text{s}}
    \times 7.188 \times 10^{-48}\,\text{s}
  = 2.155 \times 10^{-39}\,\text{m}.
\end{equation}

\begin{warnbox}
\textbf{Numerical Note.}
$\ell_5 \approx 1.46 \times 10^{-36}\,\text{m}$ and
$c\cdot t_0 \approx 2.16 \times 10^{-39}\,\text{m}$
do not agree (factor $\approx 680$).
The correspondence is qualitative (sub-Planckian order), not numerically
exact — which is discussed in detail in Doc.\,182 (Universal scale).
\end{warnbox}

\subsection{Synthesis of the Sub-Planckian Models}

\begin{table}[H]
\centering
\caption{Comparison of sub-Planckian models}
\smallskip
\resizebox{\linewidth}{!}{%
\begin{tabular}{p{25mm} p{35mm} p{40mm} p{38mm}}
\toprule
\textbf{Model} & \textbf{Scale} & \textbf{Mechanism} & \textbf{Observable} \\
\midrule
FFGFT
  & $t_0 = t_P/7500$
  & Lock-in in the 4D torus via Z3 symmetry
  & TFLN phase patterns, B-meson anomalies \\
OLQEM
  & $\ell_k = L_P/\phi^k$
  & Fibonacci quasi-periodicity in photonics
  & Photonic interference in nonlinear crystals \\
EFT (Aynbund)
  & $\Lambda_{\text{QG}} \sim 10^{16}\,\text{GeV}$
  & Gauge coupling to reduced Planck mass
  & B-meson decays (LHCb, CMS) \\
\bottomrule
\end{tabular}}
\end{table}

% ============================================================
\section{Synthetic Analogue Computer: The FFGFT-TFLN Paradigm}
% ============================================================

\subsection{Architecture}

A TFLN-based analogue computer realises the FFGFT postulates not by
approximation to the fundamental scale~$\xi$, but through \emph{structural
isomorphism}: the mathematical operations — matrix transformation,
convolution, lock-in — are the same on the crystal scale as on the
sub-Planckian scale. The scale itself is irrelevant for the validity
of the structure.

\begin{keybox}[Structural Isomorphism]
FFGFT does not claim that TFLN operates at~$\xi$. FFGFT claims that
the mathematical structure of the matrix transformation
$\mathcal{T}: \mathbb{R}^4 \to \mathrm{Mat}(N,\mathbb{C})$
is the same on every scale — from particle through atom to crystal
lattice. TFLN is a macroscopic system that makes this structure
visible.
\end{keybox}

\subsection{Testable Predictions}

\begin{predbox}
\textbf{Prediction~1 — TFLN Interferometry.}
At optical intensities $> 10^{21}\,\text{W/m}^2$, discrete phase jumps
following the Fibonacci hierarchy should appear:
\[
  \Delta\phi_{\text{discrete}} = 2\pi \cdot \phi^{-k} \quad (k \in \mathbb{N}).
\]
\end{predbox}

\begin{predbox}
\textbf{Prediction~2 — B-Meson Analysis.}
The angular observables $\mathcal{K}_{1c}$ and $\mathcal{K}_{2ss}$ from
\cite{Arslan2026} should deviate from SM predictions with higher
statistics ($> 5\sigma$):
\[
  \mathcal{K}_{1c}^{\text{FFGFT}}
  = \mathcal{K}_{1c}^{\text{SM}}
    \cdot \bigl(1 + \alpha_{\text{FFGFT}} \cdot F_{\text{Fibonacci}}\bigr).
\]
\end{predbox}

\begin{predbox}
\textbf{Prediction~3 — Sub-Planckian Resonances.}
In nonlinear photonic crystals, modulation frequencies at multiples of
$\xi\cdot\phi^{-k}$ should be detectable.
\end{predbox}

% ============================================================
\section{Discussion: From Simulation to Hardware Transduction}
% ============================================================

The implication of FFGFT can be formulated precisely: photonic analogue
computers based on TFLN show that the matrix transformation
$\mathcal{T}: \mathbb{R}^4 \to \mathrm{Mat}(N,\mathbb{C})$
is not restricted to the sub-Planckian scale. The crystal lattice
— many orders of magnitude larger than atoms or particles — obeys
the same geometric rules. That is the FFGFT principle of fractal
self-similarity in macroscopic realisation.

The remaining open question is not technological but theoretical:
can the quantitative strength of the fractal correction
(e.\,g.\ in the B-meson anomalies) be derived from the recursion
structure $\Psi(t) = G(\Psi(t-T_{\text{rev}}), \xi)$?
This is treated in Doc.\,183--184 for the RSA case;
for hadronic decay processes, it is outstanding.

% ============================================================
\section{Conclusion}
% ============================================================

\begin{itemize}
  \item Spacetime is based on a fundamental tick
        $\xi = 7500/t_P \approx 1.391 \times 10^{47}\,\text{Hz}$.
  \item The 4D phase torus is \textbf{not} to be identified with a 3D
        torus plus time continuum; time is integrated into the torus
        topology as a fourth geometric dimension.
  \item Fractal feedback enforces a lock-in of the fundamental frequency
        that stabilises matter.
  \item The 4D vector space is translated by the matrix
        translation~$\mathcal{T}$ into a multidimensional matrix space.
  \item Matrix multiplication corresponds physically to a 4D torus
        convolution.
  \item TFLN photonics achieves the required bandwidth and programmable
        complexity.
  \item LHCb data show $\sim 4\sigma$ deviations from the SM —
        predictive for FFGFT; falsifiability at $5\sigma$ (DUNE~2028).
\end{itemize}

\begin{keybox}
The coming years will show whether at $5\sigma$ a new understanding of
spacetime hardware begins.
\end{keybox}

% ── Bibliography ────────────────────────────────────────────
\newpage
\section*{Bibliography}
\addcontentsline{toc}{section}{Bibliography}

\begin{thebibliography}{99}

\bibitem{NTT2025}
M.\,Stein et al.\ (NTT/Cornell/Stanford),
\textit{Programmable photonics advanced with lithium niobate based waveguide},
Yole Group Industry News (December 2025).

\bibitem{Assumpcao2024}
D.\,Assumpcao et al.,
\textit{A thin film lithium niobate near-infrared platform for multiplexing quantum nodes},
Nature Communications, Vol.\,15 (2024).
\href{https://doi.org/10.1038/s41467-024-54541-2}{doi:10.1038/s41467-024-54541-2}

\bibitem{CERN2026a}
LHCb Collaboration,
\textit{Comprehensive analysis of local and nonlocal amplitudes in the
$B^0 \to K^{*0}\mu^+\mu^-$ decay},
Physical Review Letters (2026),
DOI: 10.1103/24g9-yn9d,
arXiv:2512.18053.

\bibitem{CERN2026b}
LHCb/CMS Collaboration,
\textit{Combined analysis of rare B-meson decays},
LHCb Press (April 2026).

\bibitem{Arslan2026}
M.\,Arslan et al.,
\textit{The Angular Observables of $\Lambda_b \to \Lambda_c(\to \Lambda^0\pi^+)
\tau^-(\to\pi^-\nu_\tau)\bar{\nu}_\tau$ within the Paradigm of FCCC Anomalies},
arXiv:2604.24922 (April 2026).

\bibitem{Aynbund2025}
A.\,Aynbund, V.\,V.\,Kiselev,
\textit{Effective Field Theory Links Gauge Coupling to Sub-Planckian Cut-off Scale of GeV},
Quantum Zeitgeist (August 2025).

\bibitem{subPlanck2025}
L.\,M.\,de Souza,
\textit{Probing Sub-Planckian Scales via OLQEM and Fibonacci Quasiperiodicity:
A Rigorous Mathematical Verification},
Preprint (2025). [Not peer-reviewed; conceptual reference.]

\bibitem{RGB2025}
A.\,Shimura et al.\ (TDK Corporation),
\textit{Visible light red, green, and blue multiplexer by sputter-deposited
thin-film lithium niobate},
Advanced Photonics Nexus, Vol.\,4, Iss.\,5, 056001 (2025).
\href{https://doi.org/10.1117/1.APN.4.5.056001}{doi:10.1117/1.APN.4.5.056001}

\end{thebibliography}
