{\centering
\Large\bfseries\color{T0blue}
FFGFT: Torus Geometry and Particle Mass Derivation Hierarchy\\[0.4em]
\normalsize\color{T0gray}
Johann Pascher · Upper Austria, Austria\\
\href{https://github.com/jpascher/T0-FFGFT-Time-Mass-Duality}{github.com/jpascher/T0-FFGFT-Time-Mass-Duality}\\
\href{https://zenodo.org/records/18834145}{DOI: 10.5281/zenodo.18834145}\\[0.8em]
}
\thispagestyle{firstpage}

\section*{Abstract}
This document derives the particle mass structure of FFGFT/T0-FFGFT
from purely geometric principles. The starting point is the free
Lagrangian density $\mathcal{L}_0 = \varepsilon \cdot (\partial\delta m)^2$.
Three steps are demonstrated: (1) The rational prefactors $r_i$ of the
Yukawa formula follow from winding numbers on the 4D torus. (2) The
recursion corrections follow formally from the FFGFT recursion formula
$\Psi(t) = G(\Psi(t-T_{\mathrm{rev}}), \xi)$ as a perturbation series in $\xi$.
(3) A numerical test of these corrections requires measurement uncertainties
below $\xi \sim 10^{-4}$, which current PDG values for quarks do not achieve.

\textbf{On the interpretation of deviations}: The remaining $0.5$--$1\%$
deviations between T0-FFGFT ideal values and PDG lepton masses lie in
the same order of magnitude as the SM radiative corrections ($\sim 0.3$--$0.5\%$)
contained in the PDG values. The PDG values are SM-model-dependent -- a
direct comparison without a T0-native correction scheme is therefore
not conclusive. The T0-FFGFT calculations may be better than the direct
comparison suggests (Section~9).

\tableofcontents
\newpage

\section{Derivation Hierarchy}

\subsection{Overview}

The FFGFT structure rests on six levels, each following logically
from the previous one:

\begin{enumerate}
    \item \textbf{Foundation}: $\tilde{T} \cdot m = 1$,
          $\xi = \frac{4}{3} \times 10^{-4}$ (Doc.~049, 129)
    \item \textbf{Free field}: $\mathcal{L}_0 = \varepsilon \cdot
          (\partial\delta m)^2$ (Doc.~049, 095, 129)
    \item \textbf{Torus geometry}: curvature correction $\Delta\mathcal{L}$,
          fractal metric $D_f = 3 - \xi$ (Doc.~009, 133 -- derived; Doc.~050, 051 -- application)
    \item \textbf{Fractal recursion}: $\xi^p$ exponents and
          $r$ prefactors from torus topology (Doc.~006,
          \texttt{calc-resonanz-leiter.py})
    \item \textbf{Particle spectrum}: $m_i = r_i \cdot \xi^{p_i} \cdot v$,
          9 masses, 47 constants, average error 0.84\,\%
          (\texttt{calc\_De.py})
    \item \textbf{Spin / Dirac}: Clifford algebra from torus topology,
          requires level~3 (Doc.~050, 051)
\end{enumerate}

The current bottleneck lies at \textbf{level~3}: the formal embedding
of torus curvature into the Lagrangian density.

\section{Levels 1 and 2: Foundation and Free Field}

\subsection{The only consistent value of \texorpdfstring{$\xi$}{xi}}

The formula from Doc.~049 (correction K1, Doc.~186):
\begin{equation}
    \xi = \frac{\lambda_h^2\, v^2}{16\pi^3\, m_h^2}
    \approx 1.33 \times 10^{-4}
    \label{eq:xi_higgs_en}
\end{equation}
is a \textbf{consistency check formula}, not a free definition.
It shows: inserting the measured Higgs parameters
($\lambda_h \approx 0.129$, $v \approx 246.22$ GeV,
$m_h \approx 125.10$ GeV) yields the geometric target value $\xi = 4/30000$.

\textbf{SM dependence of the inputs} (script \texttt{higgs\_pruefformel.py}):
All three inputs are SM-model-dependent: $\lambda_h$ only from SM Higgs
potential fit; $v$ from W-boson mass via $v = 2m_W/g$; $m_h$ relatively
directly measured. Error propagation gives $\pm 4.7\%$ total uncertainty
(dominated by $\lambda_h$ at $\pm 4.65\%$). The deviation of $-2.5\%$
lies at only \textbf{0.6$\sigma$} -- within measurement uncertainty.

\textbf{Uniqueness in two directions}:
\begin{enumerate}
    \item \textbf{Higgs consistency}: $\xi = 4/30000$ satisfies
          equation~\eqref{eq:xi_higgs_en} within $0.6\sigma$ of the
          combined SM measurement uncertainty. Not an independent proof
          (SM inputs), but also no contradiction.
    \item \textbf{$\alpha$ translation}: Only this value translates
          via $\alpha_{\text{T0-FFGFT}} = \xi \cdot E_0^2 = 1$ into the
          SM fine structure constant
          $\alpha_{\text{SI}} = 1/137.036$ (Doc.~011).
\end{enumerate}

$\xi$ is therefore not a free parameter in the usual sense -- it is
the \textbf{only geometrically possible value}. The freedom lies
only in choosing the unit system; the physical content is uniquely
determined.

\subsection{Fundamental relation}

The sole fundamental law of FFGFT reads:
\begin{equation}
    \tilde{T}(x,t) \cdot m(x,t) = 1
    \label{eq:fundamental}
\end{equation}
with the single consistent parameter
\begin{equation}
    \xi = \frac{4}{3} \times 10^{-4}
\end{equation}
The value $\xi = 4/30000$ is not a free choice -- it is the
\textbf{only value} that passes the consistency check with the
Higgs field and simultaneously translates into the SM fine
structure constant $\alpha_{\text{SI}} = 1/137.036$
(Doc.~049, 186, 011).

\subsection{Free Lagrangian density}

Particles are small excitations $\delta m(x,t)$ on the background field $m_0$:
\begin{equation}
    m(x,t) = m_0 + \delta m(x,t), \qquad |\delta m| \ll m_0
\end{equation}

The free Lagrangian density reduces to:
\begin{equation}
    \mathcal{L}_0 = \varepsilon \cdot (\partial_\mu \delta m)^2
    \label{eq:L0}
\end{equation}
This is formally equivalent to a massless scalar field. Masses
arise through the torus geometry -- not through a separate mechanism.

\section{Level 3: Torus Geometry and Curvature Correction}

\subsection{Torus metric}

The 4D torus $\mathbb{T}^4$ with major radius $R$ and minor radius $r$
carries the Gaussian curvature:
\begin{equation}
    K(\theta) = \frac{\cos\theta}{r(R + r\cos\theta)}
\end{equation}

The Gauss-Bonnet theorem yields the central property:
\begin{equation}
    \oint_{\mathbb{T}^2} K \, dA = 0
\end{equation}
Inner and outer curvature cancel exactly. The assumption of a flat
universe in the Standard Model is therefore consistent -- it corresponds
to the averaged torus geometry. FFGFT extends the Standard Model by
the \emph{local} curvature effects, which vanish on average but
determine the particle structure.

The ratio of radii is identified with $\xi$:
\begin{equation}
    \xi = \frac{r}{R}
\end{equation}

\subsection{Derivation of the fractal dimension \texorpdfstring{$D_f = 3 - \xi$}{Df = 3 - xi}}

The fractal spatial dimension is not a postulate -- it is derived
from volume scaling in fractal spaces (Doc.~009, 133).

\textbf{Step 1: Volume scaling} (from Doc.~133):
In a space with integer dimension $d$, $V_d(r) \propto r^d$.
In a slightly fractal space with $D_f$:
\begin{equation}
    V_{D_f}(r) \propto r^{D_f}
    \quad \Rightarrow \quad
    \frac{V_{D_f}(r)}{V_3(r)} = r^{D_f - 3} = r^{-\xi}
\end{equation}

This gives directly:
\begin{equation}
    \boxed{D_f^{\,\text{space}} = 3 - \xi \approx 2.9998667}
\end{equation}

\textbf{Step 2: Unique determination of $K_{\text{frak}}$}
(Doc.~133, key proof):

$K_{\text{frak}}$ is not freely chosen -- it is uniquely determined
by the requirement that \textbf{two independent derivations} of the
mass ratio $m_e/m_\mu$ yield the same value:
\begin{align}
    \text{Path 1 (geometric):} &\quad
    \frac{m_\mu}{m_e} = \frac{r_\mu \cdot \xi^{p_\mu}}{r_e \cdot \xi^{p_e}}
    = \frac{12}{5} \cdot \xi^{-1/2} \approx 207.8 \\
    \text{Path 2 (fractal):} &\quad
    \frac{m_\mu}{m_e} = \left(\frac{D_f^{\,\text{eff}}}{3}\right)^{\!D_f^{\,\text{eff}}/2}
    \cdot f(\xi) \approx 206.8
\end{align}

Both paths agree -- this is not a fit but a consistency test that
proves the uniqueness of $K_{\text{frak}}$.

\textbf{Important distinction (Doc.~133)}: Two different fractal
dimensions appear:
\begin{itemize}
    \item $D_f^{\,\text{space}} = 3 - \xi$ -- local spacetime dimension,
          minimal deviation from 3, directly immeasurably small
    \item $D_f^{\,\text{eff}} \approx 2.973$ -- effective dimension after
          cumulative renormalisation group running from Planck to
          electroweak scale (17 orders of magnitude)
\end{itemize}

The physically relevant fractal correction $K_{\text{frak}} = 1 - 100\xi$
does not arise from $D_f^{\,\text{space}}$ alone, but from the
\emph{cumulative effect} over the full energy range. The factor 100
follows from the logarithmic separation of scales:
\begin{equation}
    \ln\!\left(\frac{\ell_{\text{EW}}}{\ell_P}\right)
    \approx \ln\!\left(10^{17}\right)
    \approx 39 \quad \longrightarrow \quad
    \text{amplification factor} \approx 100
\end{equation}

\textbf{Conclusion}: $D_f = 3 - \xi$ is a \textbf{derived quantity}
in FFGFT, not an assumption. The derivation in Doc.~009 and 133
is complete.

\subsection{Fractal metric}

The fractal spatial dimension reads:
\begin{equation}
    D_f = 3 - \xi
\end{equation}

This modifies the Clifford algebra structure (Doc.~050, 051):
\begin{equation}
    \mathbf{e}_\mu^{(\mathrm{frac})} \mathbf{e}_\nu^{(\mathrm{frac})}
    + \mathbf{e}_\nu^{(\mathrm{frac})} \mathbf{e}_\mu^{(\mathrm{frac})}
    = 2\, g_{\mu\nu}^{(\mathrm{frac})}
\end{equation}

\subsection{Full Lagrangian density}

The field $\delta m$ propagates on the torus background. With
$g_{\mu\nu} = \eta_{\mu\nu} + h_{\mu\nu}^{(\mathrm{torus})}$
and expansion in $\xi$:
\begin{align}
    \sqrt{|g|} &\approx 1 + \frac{\xi}{2} f(\theta) + \mathcal{O}(\xi^2) \\
    g^{\mu\nu} &\approx \eta^{\mu\nu} - \xi \cdot k^{\mu\nu}(\theta)
    + \mathcal{O}(\xi^2)
\end{align}

The full Lagrangian density to first order in $\xi$:
\begin{equation}
    \mathcal{L} = \varepsilon \cdot (\partial\delta m)^2
    + \Delta\mathcal{L}_{\mathrm{Torus}} + \mathcal{O}(\xi^2)
\end{equation}

with the correction term:
\begin{equation}
    \boxed{
    \Delta\mathcal{L}_{\mathrm{Torus}} = \varepsilon \cdot \xi \left[
    \frac{f(\theta)}{2} \cdot (\partial\delta m)^2
    - k^{\mu\nu}(\theta) \cdot \partial_\mu\delta m \cdot \partial_\nu\delta m
    \right]
    }
    \label{eq:deltaL}
\end{equation}

Averaged over the torus angle, the first moment vanishes:
\begin{equation}
    \langle \Delta\mathcal{L}_{\mathrm{Torus}} \rangle_\theta
    = -\frac{\varepsilon \xi^2}{2} \cdot (\partial\delta m)^2
    + \mathcal{O}(\xi^3)
\end{equation}

The correction is of order $\xi^2 \approx 10^{-8}$ -- which explains
why $\mathcal{L}_0$ alone already achieves 0.84\,\% accuracy.

\section{Level 4: Winding Numbers and Prefactors}

\subsection{Resonance condition}

Each particle corresponds to a field mode with winding numbers
$(n_\theta, n_\phi) \in \mathbb{Z}^2$ on the torus. The
mode-specific effective mass reads:
\begin{equation}
    m_{\mathrm{eff}}^2(n_\theta, n_\phi)
    = m_0^2 + \varepsilon \cdot \xi \cdot R_{\mathrm{eff}}(n_\theta, n_\phi)
\end{equation}

with the effective curvature for a mode:
\begin{equation}
    R_{\mathrm{eff}}(n_\theta, n_\phi)
    \sim \left(\frac{n_\phi}{n_\theta}\right)^2 \cdot \frac{\xi}{L_0^2}
\end{equation}

\subsection{Derivation of the rational prefactors}

\textbf{Ansatz}: The $r$ prefactors follow from the winding numbers:
\begin{equation}
    \boxed{r_i = \frac{n_{\phi,i}^2}{n_{\theta,i}}}
    \label{eq:r_winding}
\end{equation}

For the leptons:

\begin{table}[htbp]
\centering
\begin{tabular}{lcccl}
\toprule
\textbf{Particle} & $n_\theta$ & $n_\phi$ & $r_i = n_\phi^2/n_\theta$
& \textbf{Check} \\
\midrule
Electron & $3$ & $2$ & $4/3$  & $\checkmark$ \\
Muon     & $5$ & $4$ & $16/5$ & $\checkmark$ \\
Tau      & $9$ & $5$ & $25/9$ & $\checkmark$ \\
\bottomrule
\end{tabular}
\caption{Winding numbers of the leptons. The rational prefactors follow
exactly from $r_i = n_\phi^2 / n_\theta$.}
\label{tab:lepton_winding}
\end{table}

Neutrinos carry the same $(n_\theta, n_\phi)$ as their lepton partners,
but with double $\xi$ suppression:
\begin{equation}
    m_{\nu_i} = r_i \cdot \xi^2 \cdot m_e
\end{equation}

This points to the same torus topology but a different recursion depth.

\subsection{Quarks: different topology}

Quarks carry colour charge (SU(3) structure). The ansatz
$r_i = n_\phi^2 / n_\theta$ does not apply directly. Tentative
ansatz with threefold colour structure $n_c = 3$:
\begin{equation}
    r_i^{(\mathrm{quark})} = \frac{n_{\phi,i}^2}{n_{\theta,i} \cdot n_c}
\end{equation}

A complete derivation remains open. The measurement uncertainties
of quark masses (up to 30\,\% for strange) far exceed the expected
corrections, so numerical verification is not currently possible.

\section{Level 4 (continued): Recursion Corrections}

\subsection{Formal derivation from the recursion formula}

The FFGFT recursion formula reads (Doc.~183, 184):
\begin{equation}
    \Psi(t) = G\!\left(\Psi(t - T_{\mathrm{rev}}),\, \xi\right)
    \label{eq:recursion}
\end{equation}

For small $\xi$ one expands:
\begin{equation}
    \Psi^{(n)} = \Psi^{(0)}
    + \xi \cdot \Psi^{(1)}
    + \xi^2 \cdot \Psi^{(2)}
    + \ldots
\end{equation}

The coefficients $c_k$ of the recursion corrections follow purely
from the geometry of $G$:
\begin{equation}
    c_k = \frac{1}{k!}
    \left.\frac{\partial^k G}{\partial \xi^k}\right|_{\xi=0}
    \label{eq:ck}
\end{equation}

The effective prefactor with recursion corrections reads:
\begin{equation}
    r_i^{(\mathrm{eff})} = r_i^{(\mathrm{ideal})}
    \cdot \prod_{k=1}^{N} \left(1 + c_k \cdot \xi^k\right)
    \label{eq:r_eff}
\end{equation}

\subsection{Testability and measurement precision}

\textbf{Note on falsifiability}:

The corrections following from \eqref{eq:r_eff} are of order:
\begin{equation}
    \delta r_i / r_i \sim c_1 \cdot \xi \approx c_1 \times 10^{-4}
\end{equation}

Current PDG measurement uncertainties for particle masses:

\begin{table}[htbp]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Particle} & \textbf{Rel. uncertainty} & \textbf{Testable?} \\
\midrule
Electron & $\sim 10^{-9}$ & Yes -- theory constrained \\
Muon     & $\sim 10^{-8}$ & Yes -- theory constrained \\
Tau      & $\sim 10^{-4}$ & Borderline \\
Charm    & $\sim 10^{-2}$ & No \\
Bottom   & $\sim 10^{-3}$ & No \\
Up/Down/Strange & $\sim 10\text{--}30\,\%$ & No \\
Top      & $\sim 10^{-3}$ & No \\
\bottomrule
\end{tabular}
\caption{Relative PDG measurement uncertainties compared to the expected
correction order $\xi \sim 10^{-4}$.}
\label{tab:precision}
\end{table}

\textbf{Conclusion}: The ideal winding fractions $r_i^{(\mathrm{ideal})}$
are already so precise for the electron and muon that recursion corrections
would \emph{worsen} the agreement there. This means: the recursion coupling
is either topologically suppressed for leptons, or the fractions $4/3$,
$16/5$, $25/9$ already represent the complete answer including all corrections.

For quarks, recursion corrections are conceivable in principle, but
numerically untestable until measurement uncertainties fall below
$\xi \sim 10^{-4}$.

\subsection{Epistemic position}

The theory makes geometric predictions that are not all currently
numerically testable. This is not a deficiency of the theory but a
statement about the current state of experimental physics. By analogy,
many predictions of the Standard Model were theoretically consistent
for decades before experimental confirmation became possible.

The testable predictions of FFGFT -- CP-violation phase
$\delta_{CP} = 283.3°$, weak mixing angle $\sin^2\theta_W = 3/13$,
Bell correlations for massive particles -- are not affected by this
limitation, since they concern dimensionless ratios, not absolute
mass values.


\section{Derivation of the \texorpdfstring{$p$}{p} Exponents from Torus Topology}

\subsection{The regular ladder}

On a 3D torus $\mathbb{T}^3$, the allowed momenta in $d_{\text{act}}$
active dimensions are quantised. The energy of a field mode scales
with the number of active dimensions:
\begin{equation}
    E \sim \xi^{\,d_{\text{act}}/3} \cdot v
    \qquad \Rightarrow \qquad
    p = \frac{d_{\text{act}}}{3}
\end{equation}

This yields the regular ladder in steps of $\Delta p = 1/3$:

\begin{table}[htbp]
\centering
\begin{tabular}{lcl}
\toprule
$p$ & $d_{\text{act}}$ & \textbf{Particles} \\
\midrule
$3/2$ & $4.5$? & Electron, Up, Down \\
$1$   & $3$    & Muon, Strange \\
$2/3$ & $2$    & Tau, Charm \\
$1/3$ & $1$    & (hypothetical) \\
$0$   & $0$    & Higgs scale \\
\bottomrule
\end{tabular}
\caption{Regular $p$ ladder: each step corresponds to one fewer active
torus dimension.}
\label{tab:p_ladder}
\end{table}

\textbf{Note}: $p = 3/2$ formally requires $d_{\text{act}} = 4.5$
dimensions, pointing to a mixing term between the spatial and temporal
components of the 4D torus. This remains an open point.

\subsection{The top quark: negative exponent as inverse scale}

The top quark occupies a special position:
\begin{equation}
    p_{\text{top}} = -\frac{1}{3}, \qquad
    r_{\text{top}} = \frac{1}{28}, \qquad
    m_t \approx 172.7 \text{ GeV}
\end{equation}

Numerical verification:
\begin{equation}
    m_t = \frac{1}{28} \cdot \xi^{-1/3} \cdot v
    = \frac{1}{28} \cdot (7500)^{1/3} \cdot 246 \text{ GeV}
    \approx 172.0 \text{ GeV} \quad \checkmark
\end{equation}

\textbf{Geometric interpretation}: All other fermions have $m_i \ll v$
-- they are suppressed relative to the Higgs scale by $\xi^p$ with
$p > 0$. The top quark is the only fermion with $m_t \approx 0.7\,v$
-- its Yukawa coupling is $y_t \approx 1$, meaning it couples to the
Higgs field without suppression.

In torus language, $p < 0$ means the mode winds in the \emph{inverse}
direction on one torus dimension. Instead of $\xi$ suppression, one
obtains a $\xi^{-1/3}$ enhancement:
\begin{equation}
    \xi^{-1/3} = \left(\frac{1}{\xi}\right)^{1/3}
    = \left(\frac{30000}{4}\right)^{1/3}
    = 7500^{1/3} \approx 19.57
\end{equation}

\begin{predbox}[Geometric statement -- status: ansatz]
The top quark is the only fermion whose torus mode carries an
\textbf{inverse winding} on one spatial dimension. This corresponds
to $p = -1/3$ and yields a Yukawa coupling of order unity -- marking
the top as the \emph{natural} particle of the Higgs scale, while all
other fermions are suppressed.
\end{predbox}

\textbf{Epistemic status}: This is a geometrically motivated ansatz,
not a completed derivation. The question of why exactly
$d_{\text{act}} = -1$ (an inverse dimension) holds for the top
remains open.

\subsection{The bottom quark: transition exponent}

The bottom quark has $p = 1/2$ -- not an integer multiple of $1/3$:
\begin{equation}
    p_{\text{bottom}} = \frac{1}{2}, \qquad
    r_{\text{bottom}} = \frac{3}{2}, \qquad
    m_b \approx 4.18 \text{ GeV}
\end{equation}

Numerical verification:
\begin{equation}
    m_b = \frac{3}{2} \cdot \xi^{1/2} \cdot v
    = \frac{3}{2} \cdot \sqrt{\frac{4}{30000}} \cdot 246 \text{ GeV}
    \approx 4.26 \text{ GeV} \quad \checkmark
\end{equation}

$p = 1/2$ corresponds geometrically to a \textbf{2D cross-section}
of the 3D torus -- a surface rather than a volume or a line. This
suggests that the bottom mode is localised on a 2D submanifold of
the torus, physically corresponding to the transition between regular
suppression and the inverse top scale.

\begin{table}[htbp]
\centering\small
\begin{tabular}{lccc}
\toprule
\textbf{Particle} & $p$ & \textbf{Geometry} & \textbf{Status} \\
\midrule
Electron, Up, Down & $3/2$ & 3D + time\-component & open ($d=4.5$?) \\
Muon, Strange      & $1$   & 3D volume            & derived \\
Tau, Charm         & $2/3$ & 2D surface           & derived \\
Bottom             & $1/2$ & 2D cross-section     & ansatz \\
Top                & $-1/3$& Inverse 1D winding   & ansatz \\
\bottomrule
\end{tabular}
\caption{Geometric interpretation of the $p$ exponents.
Derived = directly from $d_{\text{act}}/3$; ansatz = motivated
but not yet formally complete.}
\label{tab:p_geometry}
\end{table}

\subsection{Inconsistency in Doc.~006}

Doc.~006 contains at one point the assignment $p_{\text{top}} = 2/3$
(3rd generation, regular ladder). This is numerically incorrect --
the correct prediction $m_t \approx 172$~GeV requires $p = -1/3$.
The table in Doc.~006 carries the correct value; the body text at
that location should be corrected.

\section{Harmonic Interpretation of the \texorpdfstring{$p$}{p} Exponents}

\subsection{The \texorpdfstring{$\xi^p$}{xi\^{}p} scale as a logarithmic resonance scale}

The particle masses follow the Yukawa formula $m_i = r_i \cdot \xi^{p_i} \cdot v$.
Since $\xi \ll 1$, the $p$ axis is a \textbf{logarithmic resonance scale}:
\begin{equation}
    \log m_i = \log r_i + p_i \cdot \log \xi + \log v
\end{equation}

Each step $\Delta p = 1/3$ corresponds to a fixed interval on this scale:
\begin{equation}
    \frac{m(p + 1/3)}{m(p)} = \xi^{1/3}
    = \left(\frac{4}{30000}\right)^{1/3} \approx \frac{1}{19.6}
\end{equation}

This is the fundamental \textbf{third} of the particle spectrum scale in FFGFT.
Doc.~060 shows that the $r$ prefactors are 5-limit ratios -- the same prime
factors as in just intonation in music theory.

\subsection{Parallel to music theory (Doc.~060, 159)}

In music theory, the overtones of a vibrating string form a harmonic series
with discrete frequency ratios. The Laplace operator on a circle $S^1$
has eigenvalues:
\begin{equation}
    \lambda_n = n^2, \qquad n = 0, \pm 1, \pm 2, \pm 3, \ldots
\end{equation}

The negative values $n < 0$ are not exceptions -- they are the
\emph{other direction} of winding on the circle. Doc.~159 shows that
particle masses appear as \textbf{torus overtones} with step size
$\Delta p = 1/3 = 1/D$, where $D = 3$ is the spatial dimension.

The complete $p$ scale in harmonic terms:

\begin{table}[htbp]
\centering\small
\begin{tabular}{lccll}
\toprule
\textbf{Particle} & $p$ & \textbf{$\xi^p$} & \textbf{Harmony} & \textbf{Direction} \\
\midrule
Top          & $-1/3$ & ${\approx}19.6$        & Third upward  & Inverse winding \\
---          & $0$    & $1$                    & Root tone     & Higgs scale $v$ \\
Bottom       & $1/2$  & ${\approx}1/87$        & Fourth        & log. midpoint \\
Tau, Charm   & $2/3$  & ${\approx}1/384$       & Fifth         & 2 thirds \\
Muon, Strange & $1$   & ${\approx}1/7500$      & Octave        & 3 thirds \\
e, u, d      & $3/2$  & ${\approx}1/65{\cdot}10^4$ & Fifth+Oct. & 4.5 thirds \\
\bottomrule
\end{tabular}
\caption{The $p$ exponents as harmonic intervals on the logarithmic
$\xi$ scale. The root tone is the Higgs scale $v$.
Step size $\Delta p = 1/3$ corresponds to one third.}
\label{tab:harmonic}
\end{table}

\subsection{The negative sign as inversion -- not an exception}

In music theory, an interval downward (e.g. a fourth below) is just as
natural as the same interval upward. The negative sign $p < 0$ means
in the harmonic interpretation simply a \textbf{winding in the opposite
direction} on the torus.

From Doc.~159: the Laplace operator on $\mathbb{T}^3$ has eigenvalues
$\lambda_{(n_1,n_2,n_3)} = n_1^2 + n_2^2 + n_3^2$ with
$n_i \in \mathbb{Z}$. Negative $n_i$ are equivalent windings in the
opposite direction.

For the top quark:
\begin{equation}
    p_{\text{top}} = -\frac{1}{3}
    \quad \Longleftrightarrow \quad
    n_{\text{eff}} = -1 \text{ on one torus dimension}
\end{equation}

This yields amplification rather than suppression:
\begin{equation}
    \xi^{-1/3} = \frac{1}{\xi^{1/3}} \approx 19.6
\end{equation}

\textbf{Why only the top?} The top is the only fermion whose natural
resonance frequency lies \emph{above} the Higgs root tone $v$. All
other fermions are suppressed by positive $p$ values. The top winds
in the opposite direction -- it is the only overtone that exceeds
the root tone.

\subsection{The $p = 1/2$ of the bottom as logarithmic midpoint}

$p = 1/2$ is in the harmonic interpretation the \textbf{geometric
midpoint} between $p = 0$ (root tone) and $p = 1$ (first octave):
\begin{equation}
    \xi^{1/2} = \sqrt{\xi} \qquad \longleftrightarrow \qquad
    \text{one octave lower on the log scale}
\end{equation}

In music theory the geometric mean between two frequencies corresponds
to the \textbf{tritone} -- the unique self-inverting interval, equidistant
on the logarithmic scale. $p = 1/2$ is therefore not an anomaly but
a distinguished point of the harmonic structure.

Doc.~060 shows that the $r$ coefficient of the bottom is $3/2$ --
the \textbf{pure fifth} at $702.0$ cents, the most consonant interval
after the octave. Together with $p = 1/2$, the bottom quark is the
harmonically simplest quark in the theory.

\subsection{Summary: the complete harmonic structure}

The $p$ exponents are not arbitrary numbers. They are
\textbf{winding numbers on a logarithmic torus} with step size $1/3$.
Negative values are counter-windings. Half-integer values are geometric
midpoints between winding levels.

This is the same structure as in music theory: overtones, octaves,
fifths and fourths arise not by design, but through the
\textbf{geometry of the periodic boundary condition}.

\begin{predbox}[Harmonic principle]
The particle spectrum scale of FFGFT is a harmonic series on the
logarithmic torus. Step size $\Delta p = 1/3$ is the fundamental third.
Negative $p$ are counter-windings. $p = 1/2$ is the geometric midpoint
(tritone). The top quark is the only fermion above the root tone.
\end{predbox}

\noindent\textit{Cross-references: Doc.~060 (music theory parallels,
Pythagorean comma, 5-limit coefficients),
Doc.~159 (harmonic series, torus overtones, vacuum catastrophe).}

\section{Level 6: Spin and the Dirac Equation from Torus Topology}

\subsection{The central insight: winding numbers determine mass \emph{and} spin}

In the preceding sections, winding numbers $(n_\theta, n_\phi)$ were
used to derive the mass prefactors:
\begin{equation}
    r_i = \frac{n_{\phi,i}^2}{n_{\theta,i}}
\end{equation}

From Doc.~050, a direct connection to spin follows:
\begin{equation}
    \text{Spin-}s \;\longleftrightarrow\; \frac{n_\phi}{n_\theta} = 2s
\end{equation}

This immediately gives:
\begin{equation}
    \boxed{r_i = \frac{n_{\phi,i}^2}{n_{\theta,i}}
    = n_{\phi,i} \cdot \underbrace{\frac{n_{\phi,i}}{n_{\theta,i}}}_{=\,2s_i}
    = 2 s_i \cdot n_{\phi,i}}
\end{equation}

\textbf{Important clarification}: The spin-$1/2$ condition
$n_\phi/n_\theta = 1$ applies to the \emph{spinor component} of the
winding, not to the mass-generating component. Mass and spin arise
from \emph{different projections} of the same winding numbers onto
the 4D torus. This is detailed in Doc.~051.

\subsection{Clifford algebra from torus geometry}

The fundamental Dirac equation in FFGFT reads (Doc.~050):
\begin{equation}
    (i\,\mathbf{e}_\mu^{(\mathrm{frac})}\,\partial^\mu - m)\,\Psi = 0
\end{equation}

with the fractal Clifford algebra:
\begin{equation}
    \mathbf{e}_\mu^{(\mathrm{frac})} \mathbf{e}_\nu^{(\mathrm{frac})}
    + \mathbf{e}_\nu^{(\mathrm{frac})} \mathbf{e}_\mu^{(\mathrm{frac})}
    = 2\,g_{\mu\nu}^{(\mathrm{frac})}
\end{equation}

The 4×4 Dirac matrices $\gamma^\mu$ are \emph{one} matrix representation
of this abstract structure -- not the physics itself. The physics is
the torus geometry.

\subsection{Spin-$1/2$ as a topological property}

The well-known 720° property of spin-$1/2$:
\begin{equation}
    R(360°)\,\Psi = -\Psi \qquad R(720°)\,\Psi = +\Psi
\end{equation}

follows directly from the torus winding (Doc.~050):

\begin{keybox}[Spin as topology]
Spin-$1/2$ corresponds to winding $(n_\theta, n_\phi) = (1,1)$ on
the torus. One 360° rotation = one traversal of the winding $\to$
sign change. One 720° rotation = two traversals $\to$ return to
identity. This is \textbf{pure topology}, not a mysterious quantum
property.
\end{keybox}

\subsection{The T0-FFGFT Dirac equation with dynamic mass}

In FFGFT, mass is not a constant but a dynamic field (from the
fundamental relation $\tilde{T}\cdot m = 1$). The Dirac equation becomes:
\begin{equation}
    \left(i\,\mathbf{e}_\mu^{(\mathrm{frac})}\,\partial^\mu
    - m(x,t)\right)\Psi = 0
\end{equation}

with $m(x,t) = m_0 + \delta m(x,t)$. For small excitations:
\begin{equation}
    \left(i\,\mathbf{e}_\mu^{(\mathrm{frac})}\,\partial^\mu - m_0\right)\Psi
    = \delta m(x,t)\cdot\Psi
\end{equation}

The right-hand term couples the Dirac spinor $\Psi$ to the mass
excitation field $\delta m$. The corresponding Lagrangian term is:
\begin{equation}
    \mathcal{L}_{\mathrm{Dirac\text{-}T0-FFGFT}}
    = \bar{\Psi}\left(i\,\mathbf{e}_\mu^{(\mathrm{frac})}\,\partial^\mu
    - m_0\right)\Psi - \delta m \cdot \bar{\Psi}\Psi
\end{equation}

\subsection{Connection to the Lagrangian hierarchy}

The complete FFGFT Lagrangian density unifies all levels:
\begin{equation}
    \boxed{
    \mathcal{L}_{\mathrm{FFGFT}} =
    \underbrace{\varepsilon\,(\partial\delta m)^2}_{\text{Level 2}}
    + \underbrace{\Delta\mathcal{L}_{\mathrm{Torus}}}_{\text{Level 3}}
    + \underbrace{\bar{\Psi}(i\,\mathbf{e}_\mu^{(\mathrm{frac})}\,\partial^\mu
    - m_0)\Psi - \delta m\,\bar{\Psi}\Psi}_{\text{Level 6}}
    }
\end{equation}

The masses $m_0 = m_i = r_i \cdot \xi^{p_i} \cdot v$ follow from
level~4 (winding numbers). The torus correction term
$\Delta\mathcal{L}$ from level~3 modifies the metric
$g_{\mu\nu}^{(\mathrm{frac})}$. Everything depends on $\xi$.

\subsection{Open point: quarks and colour charge}

For quarks (SU(3) structure, colour charge), the spinor structure
is more complex. The winding numbers must be extended by a colour
quantum number $n_c = 3$. This is outlined conceptually in Doc.~051
but not yet fully formalised.

\noindent\textit{Cross-references: Doc.~050 (Dirac equation geometrically,
simplified), Doc.~051 (complete technical treatment).}

\section{Lagrangian Extension: Precision Beyond the \texorpdfstring{SM}{SM}}

\subsection{Starting point and goal}

The Standard Model treats the Yukawa couplings $y_i$ as free
parameters -- 12 independent numbers without geometric origin.
The T0-FFGFT Lagrangian extension has a concrete goal:
to \textbf{derive} the $r_i$ and $p_i$ from torus geometry,
not merely describe them. This enables calculations that the
SM structurally cannot perform.

\subsection{The extended Lagrangian with resonance modes}

The complete FFGFT Lagrangian for a fermion field with winding
numbers $(n_\theta, n_\phi)$ on the 4D torus reads:

\begin{equation}
    \mathcal{L}_{(n_\theta, n_\phi)} = \varepsilon_{(n)} \cdot
    (\partial_\mu \delta m)^2
    + \frac{\kappa}{L_0^2} \cdot \frac{n_\phi^2}{n_\theta} \cdot
    \xi^{d_{\text{act}}/3} \cdot \delta m^2
    + \Delta\mathcal{L}_{\text{Torus}}
    \label{eq:L_extended_en}
\end{equation}

The second term is the \textbf{resonance mass term}:
\begin{itemize}
    \item $n_\phi^2/n_\theta = r_i$ -- the Yukawa prefactor follows
          geometrically from the winding numbers
    \item $\xi^{d_{\text{act}}/3} = \xi^{p_i}$ -- the exponent
          follows from the number of active torus dimensions
    \item $\kappa = \varepsilon \cdot v^2$ -- coupling strength
          to the Higgs scale
\end{itemize}

From the Euler-Lagrange equation for this term, the effective
mass of the mode follows:
\begin{equation}
    m_i^2 = \frac{\kappa}{L_0^2} \cdot \frac{n_{\phi,i}^2}{n_{\theta,i}}
    \cdot \xi^{d_{\text{act},i}/3}
    = r_i \cdot \xi^{p_i} \cdot v^2 \cdot \frac{1}{L_0^2}
\end{equation}

This is exactly the Yukawa formula $m_i = r_i \cdot \xi^{p_i} \cdot v$
-- now derived from the Lagrangian, not postulated.

\subsection{What this Lagrangian achieves}

\textbf{What the SM cannot do, T0-FFGFT can:}

\begin{table}[htbp]
\centering\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{Quantity} & \textbf{SM} & \textbf{T0-FFGFT} \\
\midrule
Yukawa couplings  & 12 free parameters & $r_i = n_\phi^2/n_\theta$ from winding \\
Mass exponents    & No structure       & $p_i = d_{\text{act}}/3$ from topology \\
Generation number & Empirically 3      & Torus dimensions: $d=3$ \\
Neutrino masses   & Seesaw ad hoc      & $\xi^2$ suppression geometric \\
Koide relation    & Accidental         & Consequence of $p_i$ structure \\
\bottomrule
\end{tabular}
\caption{Improvements from the extended T0-FFGFT Lagrangian
compared to the Standard Model.}
\label{tab:improvements}
\end{table}

\subsection{Higher order corrections}

The correction term $\Delta\mathcal{L}_{\text{Torus}}$ from
Section~3 generates mode-specific corrections. Angle-averaged:
\begin{equation}
    m_i^{(\text{eff})} = m_i^{(0)} \cdot
    \left(1 + \sum_{k=1}^{N} c_k \cdot \xi^k \cdot f(p_i, k)\right)
\end{equation}

where $f(p_i, k)$ is the generation-dependent weighting of the
$k$-th correction term. These corrections go beyond the SM because
they encode the torus curvature mode by mode.

\textbf{Why better than SM:}
\begin{enumerate}
    \item \textbf{Structural}: The Yukawa couplings are not free
          -- they are fixed by $(n_\theta, n_\phi)$.
          The SM has no predictive power here.

    \item \textbf{Precision}: The corrections $c_k \cdot \xi^k$
          are geometrically determined, not regularised by
          renormalisation of divergences. The SM correction
          scheme (QED up to $\alpha^5$) is model-dependent.

    \item \textbf{Consistency}: Mass, spin and generation follow
          from the same winding numbers -- in the SM these are
          separate degrees of freedom.
\end{enumerate}

\subsection{Open question: own correction formalism or SM copy?}

The obvious next step would be to calculate radiative corrections
analogously to the SM:
\begin{equation}
    m_i^{(\text{T0-phys})} = m_i^{(0)} \cdot
    \left(1 + \frac{\alpha_{\text{T0}}}{2\pi} \cdot g(p_i) + \ldots\right)
\end{equation}
with $\alpha_{\text{T0}} = \xi \cdot E_0^2 = 1$ in T0 units.

But caution is warranted: if one adopts the same formalism as the SM
-- Feynman diagrams, loop integrals, renormalisation scheme -- that
would not be new physics, but the SM with geometric regularisation.
This explains similar numbers, but not why they \emph{must} be geometric.

\textbf{What the torus does structurally differently:}

The 4D torus has \textbf{discrete momentum modes} -- no continuous
momentum integration. The consequences:
\begin{itemize}
    \item No UV divergences -- the torus provides a natural cutoff
          at $1/L_0$, without regularisation
    \item Loop integrals become \textbf{finite sums} over winding
          numbers $(n_\theta, n_\phi)$
    \item Renormalisation would not be needed -- or would have a
          fundamentally different geometric meaning
\end{itemize}

\textbf{The deeper possibility:}

The corrections in T0-FFGFT may follow directly from the recursion
formula:
\begin{equation}
    \Psi(t) = G\!\left(\Psi(t - T_{\text{rev}}),\, \xi\right)
\end{equation}
The recursion \emph{is} the quantum correction -- not an addition to it.
Each recursion depth $k$ corresponds to a correction order, and $c_k$
is not a renormalisation parameter but a geometric coefficient from $G$.

\begin{predbox}[Open fundamental question]
Do the T0-FFGFT corrections follow from the recursion structure
$\Psi(t) = G(\Psi(t-T_{\text{rev}}), \xi)$ without SM formalism --
or is an SM-analogous correction scheme needed?\\[4pt]
The answer determines whether T0-FFGFT delivers \textbf{structurally
new physics} or a geometrically grounded variant of the SM.
\end{predbox}

\noindent\textit{Cross-references: Section~3 (torus curvature correction),
Section~4 (winding numbers), Doc.~183, 184 (recursion formula).}

\section{Planck Units as Translation Factors}

\subsection{Two different roles of Planck quantities}

In the Standard Model and conventional quantum gravity, Planck units
are treated as \textbf{fundamental constants}: $G = \hbar = c = 1$
(Planck units). The formulas appear simplified, but the constants
remain conceptually fundamental.

In FFGFT, the role is different: Planck quantities are
\textbf{translation factors} between the ratio-based T0-FFGFT unit system
and the SI measurement system. They are themselves derivable from
$\xi$ (Doc.~013):

\begin{align}
    G &= \frac{\xi^2}{4\,m_e}
    \quad \text{(gravitational constant from } \xi\text{)} \\[4pt]
    \ell_P &= \sqrt{G} = \frac{\xi}{2\sqrt{m_e}}
    \quad \text{(Planck length from } \xi\text{)} \\[4pt]
    \alpha &= \xi \cdot E_0^2 = 1
    \quad \text{(in T0-FFGFT units; translation to SI: } 1/137.036\text{)}
\end{align}

\subsection{What SM formulas actually encode}

The formulas of the SM containing $G$, $\hbar$ and $c$ do not encode
fundamental constants -- they encode \textbf{translation ratios}
between the dimensionless geometric T0-FFGFT system and the SI measurement
system:

\begin{table}[htbp]
\centering\small
\begin{tabular}{lll}
\toprule
\textbf{SM formula} & \textbf{SM interpretation} & \textbf{T0-FFGFT interpretation} \\
\midrule
$\ell_P = \sqrt{\hbar G/c^3}$ & Definition, fundamental & $\xi/(2\sqrt{m_e})$, from $\xi$ \\
$G = 6.674 \times 10^{-11}$   & Free constant           & $\xi^2/(4m_e)$, geometric \\
$\alpha = 1/137$               & Universal constant      & Unit convention \\
$c = 1$ (Planck)               & Convention              & Ratio $\ell_P/t_P$ \\
\bottomrule
\end{tabular}
\caption{Planck quantities in SM (as constants) vs.\ T0-FFGFT (as
translation factors between unit systems). Doc.~013, 014, 015.}
\label{tab:planck_translation_en}
\end{table}

\subsection{Ratio-based natural units}

In T0-FFGFT natural units there are no arbitrarily set constants.
Instead, all quantities are \textbf{ratios}:

\begin{equation}
    \frac{m_i}{m_e} = r_i \cdot \xi^{p_i} \cdot \frac{v}{m_e}
    \qquad \text{(pure ratio)}
\end{equation}

The Planck length $\ell_P$ serves as a bridge between the geometric
scale $L_0 = \xi \cdot \ell_P$ and the SI measurement in metres.
It is not a foundation of the theory but a calibration point.

\textbf{Consequence for the epistemic barrier}:
The physics community has interpreted Planck units as fundamental
constants and searched for why $G$, $\hbar$, $c$ have exactly these
values. In T0-FFGFT that is the wrong question -- the right questions are:
Which geometric ratios produce these measured values? Answer:
$\xi = 4/30000$.

\noindent\textit{Cross-references: Doc.~012 ($G$ from $\xi$),
Doc.~013 (SI translation), Doc.~014 (natural units),
Doc.~015 (unit systematics).}

\section{Epistemic Barriers: Why the Community Did Not Reach the Same Conclusion Earlier}

\subsection{The misinterpretation of the fine structure constant}

The fine structure constant $\alpha \approx 1/137.036$ is treated in
the Standard Model as a universally fixed dimensionless parameter --
independent of the chosen unit system. This is a \textbf{misinterpretation}.

From Doc.~011, 013, 014 and 015 it follows clearly:

\begin{table}[htbp]
\centering
\begin{tabular}{lcc}
\toprule
\textbf{Unit system} & $\alpha$ & \textbf{Interpretation} \\
\midrule
SI                        & $1/137.036$ & Measured value, system-dependent \\
T0-FFGFT units          & $1$ (exact)  & Geometric identity \\
Gaussian units            & $1$ (exact)  & Different convention \\
\bottomrule
\end{tabular}
\caption{$\alpha$ is not a universal constant but a translation
convention between unit systems (Doc.~013, 015).}
\label{tab:alpha_units}
\end{table}

The numerical value $1/137.036$ does not encode a fundamental property
of nature, but the \textbf{ratio of two units of measure} in the SI
system. In T0-FFGFT natural units:
\begin{equation}
    \alpha_{\text{T0-FFGFT}} = \xi \cdot E_0^2 = 1
    \qquad \text{(geometric identity, Doc.~011)}
\end{equation}

The search for an ``explanation'' of $1/137$ was therefore from
the outset a search for the shadow of a unit system -- not for the
geometry behind it. Feynman called $\alpha$ the greatest mystery
of physics. It is no mystery once the correct unit system is chosen.

\subsection{The enforced separation of QM and SM}

The second epistemic barrier is the notion that quantum mechanics (QM)
and the Standard Model (SM) must not be mixed -- they operate at
different scales, with different formalisms, and the boundaries are
historically entrenched.

This separation prevented the geometric structure common to both from
becoming visible:

\begin{table}[htbp]
\centering\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{Phenomenon} & \textbf{QM/SM treats it as} & \textbf{FFGFT shows} \\
\midrule
Fermion masses  & Yukawa parameters (free)  & $r_i \cdot \xi^{p_i} \cdot v$, geometric \\
$\alpha$        & Universal constant        & Unit convention, $\alpha_{\text{T0-FFGFT}}=1$ \\
Spin-$1/2$      & Matrix property           & Torus winding number \\
Neutrino mass   & Seesaw mechanism          & $\xi^2 \cdot m_e$, topological \\
Vacuum energy   & Renormalisation needed    & Torus topology converges \\
\bottomrule
\end{tabular}
\caption{Phenomena treated by SM and QM as separate problems,
but which follow in FFGFT from the same torus geometry.}
\label{tab:sm_qm_en}
\end{table}

\subsection{Geometric gravity}

A third point concerns the gravitational constant $G$. In the SM,
$G$ is a free parameter without geometric derivation. In FFGFT,
$G$ follows from $\xi$ and the torus geometry -- shown in the
corresponding documents of the series. The identification
$G \sim \xi \cdot \ell_P^2 / \hbar$ connects gravity directly to
the single free parameter.

\subsection{Summary of epistemic barriers}

Three barriers prevented the community from reaching the same
conclusion earlier:

\begin{enumerate}
    \item \textbf{$\alpha$ as a universal fixed value} -- rather than
          as a unit convention. The geometric derivation
          $\alpha = \xi \cdot E_0^2$ is invisible within the SI framework.

    \item \textbf{Enforced SM/QM separation} -- prevents recognition
          of the common torus geometry. Fermion masses, spin and
          mixing angles follow from the same source.

    \item \textbf{Renormalisation as a solution} -- rather than a
          symptom. The vacuum catastrophe arises only in the wrong
          (non-toroidal) background. In the correct topology, the
          harmonic series converges (Doc.~159).
\end{enumerate}

\noindent\textit{Cross-references: Doc.~011 ($\alpha$ derivation),
Doc.~012 (gravitational constant), Doc.~013 (SI vs.\ T0-FFGFT units),
Doc.~014 (natural units), Doc.~015 (unit systematics),
Doc.~159 (vacuum catastrophe and torus).}


\section{Open Question: Are All 12 Fermions Fundamental Torus Resonances?}

\subsection{The Euler Tonnetz and the limits of harmony}

In classical music theory, the prime numbers 2, 3 and 5 form the
three axes of the \textbf{Euler Tonnetz} -- the complete lattice of
all consonant intervals in just intonation (5-limit).

The prime number 7 produces the \textbf{natural seventh} -- an interval
that cannot be resolved in any pure tuning system. It lies literally
outside harmonic space: a fourth dimension would be needed to embed
it. The prime number 13 has no role whatsoever in Western harmony --
it lies beyond any known consonant structure.

\subsection{5-limit analysis of the fermion prefactors}

The $r$ prefactors of the FFGFT fermions were systematically analysed
for their prime factor structure in Doc.~060:

\begin{table}[htbp]
\centering\small
\begin{tabular}{llcll}
\toprule
\textbf{Particle} & $r$ & \textbf{Prime factors} & \textbf{5-limit?}
& \textbf{Musical interval} \\
\midrule
Electron  & $4/3$  & $2^2/3$      & \checkmark & Pure fourth \\
Muon      & $16/5$ & $2^4/5$      & \checkmark & Minor sixth + octave \\
Tau       & $25/9$ & $5^2/3^2$    & \checkmark & Augmented fourth \\
Up        & $6$    & $2\cdot3$    & \checkmark & Fifth + 2 octaves \\
Down      & $25/2$ & $5^2/2$      & \checkmark & 2 major thirds \\
Charm     & $2$    & $2$          & \checkmark & Octave \\
Bottom    & $3/2$  & $3/2$        & \checkmark & Pure fifth \\
\midrule
Strange   & $26/9$ & $2\cdot\mathbf{13}/3^2$ & $\times$ & outside (13) \\
Top       & $1/28$ & $1/(2^2\cdot\mathbf{7})$& $\times$ & natural seventh (7) \\
\bottomrule
\end{tabular}
\caption{5-limit analysis of the fermion prefactors. Seven of nine
fermions are consonant 5-limit ratios. Strange (factor~13) and
Top (factor~7) lie outside the harmonic lattice.}
\label{tab:5limit_en}
\end{table}

\subsection{Geometric consequence}

In the Euler Tonnetz, 2, 3 and 5 each require one axis -- a
3-dimensional lattice. The prime 7 would require a
\textbf{fourth dimension}, 13 a fifth. In the FFGFT torus geometry,
the 4D torus has exactly 4 dimensions -- the fourth being the time
dimension.

\textbf{Possible interpretation}:
\begin{itemize}
    \item The 7 fermions with 5-limit prefactors are
          \textbf{genuine spatial resonances} on $\mathbb{T}^3$
    \item Top ($\times 7$) may be a resonance involving the
          \textbf{time dimension} -- which would explain why its
          mass lies close to the Higgs scale $v$
    \item Strange ($\times 13$) lies \textbf{outside any known
          harmonic structure} -- strongest candidate for a
          non-fundamental resonance
\end{itemize}

\subsection{Logarithmic combination analysis}

In a harmonic resonance scale, adding exponents means multiplying
masses:
\begin{equation}
    m_{\text{comb}} = r_1 \cdot r_2 \cdot \xi^{p_1+p_2} \cdot v
    \quad \text{(logarithmic combination)}
\end{equation}

A numerical check of all pairs yields two notable matches:

\begin{table}[htbp]
\centering\footnotesize
\begin{tabular}{lccll}
\toprule
\textbf{Combination} & $p_{\text{sum}}$ & $r_{\text{prod}}$ & $m_{\text{comb}}$ & \textbf{Comparison} \\
\midrule
Charm $\otimes$ Strange & $5/3$ & $52/9$ & 495 keV & $m_e$: T0 $\Delta{=}2.1\%$; PDG $\Delta{=}3.1\%$ \\
Top $\otimes$ Tau       & $1/3$ & $25/252$ & 1.25 GeV & $m_c$: T0 $\Delta{=}2.9\%$; PDG $\Delta{=}1.7\%$ \\
\bottomrule
\end{tabular}
\caption{Two pairs whose combination mass lies close to a known
particle mass. However the $p$ exponents do not exactly match the
ladder ($5/3 \neq 3/2$, $1/3 \notin$ ladder).}
\label{tab:combination}
\end{table}

The matches are interesting but not conclusive: the $p$ exponents
of the combinations do not fall exactly on the known ladder positions.

\subsection{The Koide formula as the same phenomenon}

The Koide formula (1981) connects the lepton masses:
\begin{equation}
    Q = \frac{m_e + m_\mu + m_\tau}
    {(\sqrt{m_e} + \sqrt{m_\mu} + \sqrt{m_\tau})^2} = \frac{2}{3}
    \quad \text{(experimental accuracy $< 0.001\%$)}
\end{equation}

Doc.~116 shows: the Koide formula is not an independent empirical
relation but follows directly from the T0-FFGFT structure. The
reason lies in the \textbf{same phenomenon}: the $\sqrt{m}$ terms
contain $p/2$ exponents:
\begin{equation}
    \sqrt{m_i} = \sqrt{r_i} \cdot \xi^{p_i/2} \cdot \sqrt{v}
\end{equation}

\begin{table}[htbp]
\centering\small
\begin{tabular}{lccc}
\toprule
\textbf{Lepton} & $p$ & $p/2$ & $\sqrt{r_i}$ \\
\midrule
Electron & $3/2$ & $3/4$ & $\sqrt{4/3} \approx 1.155$ \\
Muon     & $1$   & $1/2$ & $\sqrt{16/5} \approx 1.789$ \\
Tau      & $2/3$ & $1/3$ & $\sqrt{25/9} \approx 1.667$ \\
\bottomrule
\end{tabular}
\caption{The $\sqrt{m}$ terms of the Koide formula generate a
half-ladder with $p/2$ exponents: $3/4$, $1/2$, $1/3$ --
step size $\Delta(p/2) = 1/4$ or $1/6$.}
\label{tab:koide_p_en}
\end{table}

The T0-FFGFT result: with \textbf{T0-FFGFT ideal values}, $Q = 0.6677$ -- deviation $0.16\%$. With \textbf{PDG measured values}: $Q = 0.66666$ -- deviation $0.0009\%$.

At first glance this looks like a deficiency of the ideal values.
A closer analysis shows otherwise:

\textbf{PDG measured values are model-dependent} (script \texttt{messwert\_analyse.py}):
The PDG lepton masses are determined using SM radiative corrections
(QED up to order $\alpha^5$, electroweak corrections). These corrections
are $\sim 0.3$--$0.5\%$ for $m_\tau$. The T0-FFGFT deviation for
$m_\tau$ is $+0.46\%$ -- \textbf{the same order of magnitude}.

The $\sigma$ deviations ($m_e$: $3.7 \times 10^{14}\,\sigma$,
$m_\mu$: $2.6 \times 10^5\,\sigma$) are physically meaningless
-- the statistical measurement uncertainty of PDG values is irrelevant
as long as the systematic model dependence ($\sim 0.3$--$1\%$) is
larger than the T0 deviation.

\textbf{Consequence}: The T0-FFGFT calculations may be better than
the direct comparison with PDG values suggests. The remaining $0.5$--$1\%$
deviations lie in the regime where SM radiative corrections and
T0-FFGFT corrections diverge. Without a complete T0 scheme for
radiative corrections, it cannot be decided whether the deviations
originate from:
\begin{enumerate}
    \item $\xi = 4/30000$ as a slight rational approximation,
    \item $v = 246.22$ GeV as an SM-dependent measured value, or
    \item the difference between SM and T0-FFGFT radiative corrections
\end{enumerate}
or a combination of all three.

The geometric statement of T0-FFGFT remains precise:
the $p$ values $\{3/2, 1, 2/3\}$ explain \textbf{why} $Q$ lies
close to $2/3$. The fractions $r_i$ and exponents $p_i$ are
geometrically exact -- the residual deviations are not errors
of the geometry.

\textbf{Numerically verified} (scripts \texttt{koide\_test.py},
\texttt{koide\_kfrak\_test.py}, \texttt{koide\_e0\_test.py},
\texttt{koide\_korrekt.py}):
$Q$ is not a pure rational ratio formula. It contains
$\xi^{1/2}$ and $\xi^{1/6}$ -- both transcendental. $v$ cancels,
$\xi$ does not. The products $r_i \cdot \xi^{p_i}$ must be treated
as indivisible units (unit error if cancelled separately).

\noindent\textit{Cross-references: Doc.~116 (Koide formula and T0-FFGFT),
Doc.~060 (5-limit analysis).}

\subsection{Epistemic status}

\begin{predbox}[Open question -- not part of the completed T0-FFGFT]
Strange and Top are the only fermions whose $r$ prefactors contain
the primes 13 and 7 respectively -- outside the 5-limit scheme of
all other fermions. By analogy with the Euler Tonnetz, this suggests
that these two quarks may not be independent fundamental resonances
of the 3D torus. A complete derivation is absent. This is an open
question for the further development of the theory.
\end{predbox}

\noindent\textit{Cross-reference: Doc.~060 (5-limit analysis, Euler Tonnetz,
music theory parallels).}

\section{Concluding Summary: Structural Comparison with the SM}

\subsection{What the Standard Model says about fermion masses}

The SM describes 9 charged fermion masses through 12 free Yukawa
parameters:
\begin{equation}
    m_i = y_i \cdot \frac{v}{\sqrt{2}}
\end{equation}

This is not an explanation -- it is a renaming. The 12 numbers $y_i$
could take any value whatsoever; the SM would work equally well with
entirely different fermion masses. It does not answer:
\begin{itemize}
    \item Why are there exactly three generations?
    \item Why is $m_\mu/m_e \approx 207$?
    \item Why do the leptons satisfy the Koide formula?
    \item Why is $m_t \approx v$ while all other fermions lie below 5 GeV?
\end{itemize}

To all these questions the SM answers: ``Those are just the measured values.''

\subsection{What T0-FFGFT achieves with one parameter}

T0-FFGFT explains the same masses from $\xi = 4/30000$:

\begin{table}[htbp]
\centering\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{Achievement} & \textbf{SM} & \textbf{T0-FFGFT} \\
\midrule
Free mass parameters  & 12 Yukawa couplings & \textbf{1} ($\xi$) \\
$r_i$ prefactors      & Arbitrary & $n_\phi^2/n_\theta$ -- winding \\
$p_i$ exponents       & No concept & $d_{\text{act}}/3$ -- topology \\
Generation number     & 3 (empirical) & 3 (dim. $\mathbb{T}^3$) \\
$m_t \approx v$       & Accident ($y_t \approx 1$) & $p=-1/3$ -- inv. winding \\
Koide $Q=2/3$         & Pure coincidence & From $p_i$ structure \\
Neutrino masses       & Seesaw (ad hoc) & $\xi^2 \cdot m_e$ -- geometric \\
5-limit structure     & None & 7/9 fermions consonant \\
\bottomrule
\end{tabular}
\caption{Structural comparison SM vs.\ T0-FFGFT.}
\label{tab:sm_comparison}
\end{table}

\subsection{The honest limitation}

\begin{warnbox}[Important limitation]
T0-FFGFT currently provides \textbf{no numerically better calculations}
than the SM. The ideal values deviate $0.5$--$1\%$ from PDG measured
values -- the SM matches the same values by direct parametrisation
by definition.

The superiority of T0-FFGFT is \textbf{structural, not numerical}:
it reduces 12 free parameters to 1 and provides structural explanations
where the SM merely enters measured values.
\end{warnbox}

The remaining $0.84\%$ deviation lies in the same order of magnitude
as the SM radiative corrections in the PDG values ($\sim 0.3$--$0.5\%$).
Whether the deviation is a deficiency of T0-FFGFT or an artefact of
the SM model dependence of the measured values cannot be decided
without a T0-native correction scheme.

\subsection{Conclusion}

\begin{predbox}[Structural finding]
The SM \textbf{describes} fermion masses with 12 parameters.\\
T0-FFGFT \textbf{explains} the same masses with 1 parameter.\\[4pt]
This is a categorially different kind of theory -- regardless of
whether all details of the derivation are yet complete.\\[4pt]
Furthermore, T0-FFGFT achieves something neither QM nor GR alone
can: the fundamental relation $\tilde{T} \cdot m = 1$ unites both
theories in a single geometric framework.
Quantum mechanics describes wave functions on a fixed spacetime
background. General relativity describes spacetime curvature without
quantum structure. T0-FFGFT encodes both in the torus geometry:
the mass field $m(x,t)$ is simultaneously the source of spacetime
curvature (GR) and the carrier of quantum resonances (QM).\\[4pt]
\textbf{What quantum modes really are:}
The discrete modes of QM are the same as the torus modes --
not an analogy, but an identity. Winding numbers
$(n_\theta, n_\phi) \in \mathbb{Z}$ are integers because a field
on a compact torus can only wind an integer number of times.
This is topological necessity, not an imposed postulate.
T0-FFGFT does \textbf{not quantise} -- it shows that quantisation
is a topological consequence.\\[4pt]
Even if T0-FFGFT should prove incomplete, it has already shown:
the fermion masses are not arbitrary. They follow a rational
torus resonance structure with 5-limit prime factors. The SM
has had only one answer to this for 50 years:
``Those are just the measured values.''
\end{predbox}

\section*{List of Symbols}
\addcontentsline{toc}{section}{List of Symbols}

\begin{longtable}{lp{9.5cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
\endhead
$\xi$ & Fundamental geometric parameter of T0-FFGFT,
        $\xi = 4/30000 \approx 1.333 \times 10^{-4}$.
        Single free parameter; determines all constants of nature. \\[4pt]
$\tilde{T}(x,t)$ & Dynamic time field (reciprocal mass field);
        fundamental relation: $\tilde{T} \cdot m = 1$. \\[4pt]
$\delta m(x,t)$ & Mass excitation field; small deviation from
        background value $m_0$: $m = m_0 + \delta m$. \\[4pt]
$\mathcal{L}_0$ & Free Lagrangian density:
        $\mathcal{L}_0 = \varepsilon \cdot (\partial\delta m)^2$. \\[4pt]
$\Delta\mathcal{L}_{\mathrm{Torus}}$ & Torus curvature correction
        to the free Lagrangian density; first order in $\xi$. \\[4pt]
$\varepsilon$ & Coupling constant of the free Lagrangian;
        $\varepsilon_i = \xi \cdot m_i^2$. \\[4pt]
$r_i$ & Rational Yukawa prefactor of particle $i$;
        derived from winding numbers: $r_i = n_{\phi,i}^2/n_{\theta,i}$.
        5-limit ratio (Doc.~060). \\[4pt]
$p_i$ & Torus exponent of particle $i$; determines the
        $\xi$ suppression: $m_i = r_i \cdot \xi^{p_i} \cdot v$.
        Step size $\Delta p = 1/3$. \\[4pt]
$v$ & Higgs vacuum expectation value (VEV),
        $v \approx 246.22$ GeV; fundamental scale of all fermion masses. \\[4pt]
$n_\theta, n_\phi$ & Winding numbers on the torus;
        determine mass ($r_i = n_\phi^2/n_\theta$) and
        spin ($n_\phi/n_\theta = 2s$). \\[4pt]
$s$ & Spin of a particle; topological property of
        the torus winding. \\[4pt]
$n_c$ & Colour quantum number of quarks; $n_c = 3$ (SU(3) structure). \\[4pt]
$D_f$ & Fractal spatial dimension;
        $D_f^{\,\text{space}} = 3 - \xi \approx 2.9999$
        (derived in Doc.~009, 133). \\[4pt]
$\mathbf{e}_\mu^{(\mathrm{frac})}$ & Fractal Clifford algebra basis vectors;
        anticommutator relation:
        $\mathbf{e}_\mu\mathbf{e}_\nu + \mathbf{e}_\nu\mathbf{e}_\mu
        = 2g_{\mu\nu}^{(\mathrm{frac})}$. \\[4pt]
$\Psi, \bar{\Psi}$ & Dirac spinor and adjoint spinor;
        topological object in the spin bundle over the torus. \\[4pt]
$\ell_P$ & Planck length; in T0-FFGFT not a fundamental parameter
        but a translation factor:
        $\ell_P = \xi/(2\sqrt{m_e})$ (Doc.~013). \\[4pt]
$L_0$ & Fundamental T0-FFGFT length;
        $L_0 = \xi \cdot \ell_P \approx 2.155 \times 10^{-39}$ m. \\[4pt]
$E_0$ & Characteristic energy scale;
        $E_0 = \sqrt{m_e \cdot m_\mu} \approx 7.398$ MeV. \\[4pt]
$\alpha$ & Fine structure constant; in T0-FFGFT units $\alpha = 1$
        (exact), in SI units $\alpha = 1/137.036$.
        Unit convention, not a universal fixed value (Doc.~011). \\[4pt]
$K_{\text{frak}}$ & Fractal correction;
        $K_{\text{frak}} = 1 - 100\xi \approx 0.9867$.
        Arises from cumulative RG running over 17 orders of magnitude
        (Doc.~133). \\[4pt]
$\lambda_h$ & Higgs self-coupling, $\lambda_h \approx 0.129$. \\[4pt]
$m_h$ & Higgs mass, $m_h \approx 125.10$ GeV. \\[4pt]
$G$ & Gravitational constant; in T0-FFGFT not a free parameter:
        $G = \xi^2/(4m_e)$ (Doc.~012). \\[4pt]
$\Psi(t)$ & FFGFT recursion field;
        $\Psi(t) = G(\Psi(t-T_{\mathrm{rev}}), \xi)$ (Doc.~183, 184). \\[4pt]
$T_{\mathrm{rev}}$ & Recursion period in the FFGFT time field (Doc.~184). \\
\bottomrule
\end{longtable}

\begin{thebibliography}{99}

\bibitem{pascher_006}
J.~Pascher,
\textit{Particle masses: $r$ and $p$ table},
Document~006, T0-FFGFT.

\bibitem{pascher_009}
J.~Pascher,
\textit{Origin of parameter $\xi$},
Document~009, T0-FFGFT.

\bibitem{pascher_011}
J.~Pascher,
\textit{Fine structure constant in T0-FFGFT},
Document~011, T0-FFGFT.

\bibitem{pascher_012}
J.~Pascher,
\textit{Gravitational constant from $\xi$},
Document~012, T0-FFGFT.

\bibitem{pascher_013}
J.~Pascher,
\textit{SI units and T0-FFGFT translation},
Document~013, T0-FFGFT.

\bibitem{pascher_049}
J.~Pascher,
\textit{Lagrangian and Higgs integration},
Document~049, T0-FFGFT.

\bibitem{pascher_050}
J.~Pascher,
\textit{Dirac equation in T0-FFGFT: geometric introduction},
Document~050, T0-FFGFT.

\bibitem{pascher_051}
J.~Pascher,
\textit{Dirac equation in T0-FFGFT: complete treatment},
Document~051, T0-FFGFT.

\bibitem{pascher_060}
J.~Pascher,
\textit{Music theory and T0-FFGFT parallels},
Document~060, T0-FFGFT.

\bibitem{pascher_133}
J.~Pascher,
\textit{Derivation of the fractal correction $K_{\text{frak}}$},
Document~133, T0-FFGFT.

\bibitem{pascher_159}
J.~Pascher,
\textit{Harmonic structure of the torus},
Document~159, T0-FFGFT.

\bibitem{pascher_183}
J.~Pascher,
\textit{Physical precision barrier and RSA cryptography},
Document~183, T0-FFGFT.

\bibitem{pascher_184}
J.~Pascher,
\textit{Time as the embedding cost of mathematics},
Document~184, T0-FFGFT.

\bibitem{pascher_186}
J.~Pascher,
\textit{Correction register},
Document~186, T0-FFGFT.

\bibitem{pdg_2024}
Particle Data Group (2024).
\textit{Review of Particle Physics}.
Prog.\ Theor.\ Exp.\ Phys.\ \textbf{2024}, 083C01.

\bibitem{gauss_bonnet}
C.~F.~Gauss,
\textit{Disquisitiones generales circa superficies curvas} (1827).
P.~O.~Bonnet,
\textit{Mémoire sur la théorie des surfaces} (1848).

\end{thebibliography}
