% ============================================================
% 190_T0_Korrekturen_En_ch.tex
% Errata and Refinements - FFGFT / T0 Time-Mass Duality
% Older documents remain unchanged; this document records
% corrections and refinements.
% Status: 5 May 2026 (with C7, C8: Terminology "Renormalization")
% ============================================================

\section*{Preliminary Note}

This document lists corrections and refinements for previously
published documents in the FFGFT series. Older documents are
\emph{not} modified. Where a contradiction exists between an older and
a newer document, the version recorded here is binding.

Each entry contains: affected document and location, the erroneous
expression, the correct expression, and a brief justification.

% ============================================================
\section{\texorpdfstring{Correction~1: Prefactor in the Higgs derivation of $\xi$}{Correction 1: Prefactor in the Higgs derivation of xi}}
% ============================================================

\subsection*{Affected Document}

Doc.~049 (T0 Lagrangian and Higgs Integration), HTML draft version
and earlier working versions.

\subsection*{Erroneous Expression}

\begin{equation}
  \xi \;=\; \frac{\lambda_h^2\, v^2}{64\pi^4\, m_h^2}
  \;\approx\; 1.0 \times 10^{-5}
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct Expression}

\begin{equation}
  \boxed{
    \xi \;=\; \frac{\lambda_h^2\, v^2}{16\pi^3\, m_h^2}
    \;\approx\; 1.33 \times 10^{-4}
  }
  \tag{190.1}
\end{equation}

with the experimental inputs:
\begin{align*}
  m_h      &= 125.25\,\text{GeV} \quad \text{(Higgs mass)}, \\
  v        &= 246.22\,\text{GeV} \quad \text{(vacuum expectation value)}, \\
  \lambda_h &= \frac{m_h^2}{2v^2} \approx 0.129
               \quad \text{(Higgs self-coupling)}.
\end{align*}

\subsection*{Justification}

The prefactor $64\pi^4$ originated as a typo in the early
HTML visualization. It yields $\xi \approx 10^{-5}$, which deviates by
an order of magnitude from the geometrically derived value
$\xi = 4/3 \cdot 10^{-4}$ and does not reproduce the natural constants.
The correct prefactor $16\pi^3$ yields
$\xi \approx 1.33 \times 10^{-4}$, consistent with the value
independently determined from the proton-electron mass ratio (Doc.~009).

% ============================================================
\section{\texorpdfstring{Correction~2: Tau-Yukawa prefactor $r_\tau$}{Correction 2: Tau-Yukawa prefactor r-tau}}
% ============================================================

\subsection*{Affected Document}

Doc.~116 (Koide formula as a consequence of T0 theory), table of
Yukawa coefficients.

\subsection*{Erroneous Expression}

\begin{equation}
  r_\tau \;=\; \frac{8}{3} \;\approx\; 2.667
  \quad \Rightarrow \quad
  m_\tau \approx 1712\,\text{MeV} \quad (-3.6\,\% \text{ dev.})
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct Expression}

\begin{equation}
  \boxed{r_\tau \;=\; \frac{25}{9} \;\approx\; 2.778}
  \quad \Rightarrow \quad
  m_\tau \approx 1783\,\text{MeV} \quad (+0.4\,\% \text{ dev.})
  \tag{190.2}
\end{equation}

The lepton masses are generally given by:
\begin{equation}
  m_\ell \;=\; r_\ell \cdot \xi^{p_\ell} \cdot v
  \tag{190.3}
\end{equation}
with exponents $p_e = 3/2$, $p_\mu = 1$, $p_\tau = 2/3$
(step size $\Delta p = 1/3$) and the vacuum expectation value $v$.

\subsection*{Justification}

$r_\tau = 8/3$ was a remnant from an earlier iteration stage.
Doc.~158 (Koide-to-g-2 bridge) already uses $r_\tau = 25/9$, which
agrees numerically with the tau mass. Furthermore, $25/9 = (5/3)^2$
has a geometric interpretation as the square of the pure sixth in the
natural overtone series, consistent with the musical resonance analogy
(Doc.~060).

\subsubsection*{Complete Corrected Prefactor Table}

\begin{center}
{\footnotesize
\begin{tabular}{lccc}
\hline
\textbf{Lepton} & \textbf{Exponent $p$} & \textbf{Prefactor $r$} & \textbf{$m$ [MeV]}\\
\hline
Electron   & $3/2$  & $4/3$   & $0.511$ \\
Muon       & $1$    & $16/5$  & $105.7$ \\
Tau        & $2/3$  & $25/9$  & $1783$  \\
\hline
\end{tabular}
} % footnotesize
\end{center}

% ============================================================
\section{\texorpdfstring{Correction~3: Base formula for $g$-$2$ of the electron}{Correction 3: Base formula for g-2 of the electron}}
% ============================================================

\subsection*{Affected Document}

T0 Explorer (HTML visualization), first version; earlier draft versions
of Doc.~018.

\subsection*{Erroneous Expression}

\begin{equation}
  a_e \;=\; \frac{4\pi}{f \cdot k_{\text{geom}}}
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct Expression}

\begin{equation}
  \boxed{
    a_e \;=\; \frac{S_3}{f \cdot k_{\text{geom}}}
    \;=\; \frac{2\pi^2}{f \cdot k_{\text{geom}}}
  }
  \tag{190.4}
\end{equation}

with $f = 1/\xi \approx 7500$, $k_{\text{geom}} = (2/\sqrt{\varphi})\cdot\sqrt{2} \approx 2.224$
and $S_3 = 2\pi^2 \approx 19.74$ (surface area of the 4D unit sphere,
i.e.\ the 3D boundary of the torus).

\subsection*{Justification}

The earlier prefactor $4\pi$ corresponds to the surface area of the 2D sphere
in 3D space, not the geometrically correct 3D surface of the 4D torus.
$S_3 = 2\pi^2$ is the correct value from torus geometry. The
fractal corrections for muon and tau still use $4\pi$:

\begin{align}
  \Delta a_\mu  &= \frac{4\pi}{f^{5/3}}, \tag{190.5}\\
  \Delta a_\tau &= \frac{4\pi}{f^{4/3}}. \tag{190.6}
\end{align}

% ============================================================
\section{Refinement~1: Accuracy of the Koide formula}
% ============================================================

\subsection*{Affected Documents}

Doc.~116 (abstract, line~14): $\Delta Q < 0.00003\,\%$ \\
Doc.~158 (abstract): \enquote{experimentally confirmed to $0.001\,\%$}

\subsection*{Correct Interpretation}

The Koide relation
\begin{equation}
  Q \;=\; \frac{m_e + m_\mu + m_\tau}
               {(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2}
  \;=\; \frac{2}{3}
  \tag{190.7}
\end{equation}
is experimentally confirmed to better than $0.001\,\%$
(PDG values 2022). The figure $< 0.00003\,\%$ in Doc.~116 refers
to the internal consistency of the T0 formulas, not the
experimental measurement uncertainty. Both statements are
substantively correct but refer to different quantities. In external
communications, $0.001\,\%$ is the appropriate figure.

\subsection*{Note}

The individual T0 masses agree with experiment to within $\sim 1\,\%$;
the high precision of $Q = 2/3$ arises from the specific
algebraic structure of the Koide combination, not from individual
mass accuracy.

% ============================================================
\section{\texorpdfstring{Refinement~2: $\hbar$ from the Higgs field -- derivation chain}{Refinement 2: hbar from the Higgs field -- derivation chain}}
% ============================================================

\subsection*{Context}

Planck's constant $\hbar$ is derived differently in various documents.
The complete, consistent derivation chain is fixed here.

\subsection*{Binding Derivation Chain}

\begin{equation}
  \xi \;=\; \frac{\lambda_h^2 v^2}{16\pi^3 m_h^2}
  \;\longrightarrow\;
  L_0 \;=\; \xi \cdot \ell_P
  \;\longrightarrow\;
  \hbar \;\sim\; \sqrt{\xi}\cdot \ell_P \cdot c
  \tag{190.8}
\end{equation}

The time-mass binding condition provides the physical justification:
\begin{equation}
  T(x,t)\cdot m(x,t) \;=\; 1
  \quad\Longrightarrow\quad
  T \;=\; \frac{\hbar}{m\, c^2}
  \quad\Longrightarrow\quad
  E \;=\; \hbar\omega.
  \tag{190.9}
\end{equation}

$h = 2\pi\hbar$ is therefore \emph{not} a free constant but a
geometric consequence of $\xi$ and $\ell_P$. The numerical SI value
$h \approx 6.626 \times 10^{-34}\,\text{J·s}$ is the
calibration of this relation onto the SI base units.

% ============================================================
\section{\texorpdfstring{Refinement~3: Two $\xi$ parameters -- two distinct spaces}{Refinement 3: Two xi parameters -- two distinct spaces}}
% ============================================================

\subsection*{Context}

In Documents 173--176 (quantum dots, spin qubits, qubit state spaces,
Shor algorithm), two numerically different $\xi$ values appear.
Earlier documents did not separate these consistently, which can
cause confusion.

\subsection*{Binding Distinction}

\begin{center}
{\footnotesize
\begin{tabular}{p{2.4cm}p{2.0cm}p{2.4cm}p{3.0cm}}
\toprule
\textbf{Parameter} & \textbf{Value} & \textbf{Domain} & \textbf{Meaning} \\
\midrule
$\xi_0$ \newline (geometric) &
$\dfrac{4}{30000}$ \newline $\approx 1.33 \times 10^{-4}$ &
3D geometric space &
Length hierarchy of the torus; valid in physical position space \\[6pt]
$\xi_{\text{Higgs}}$ \newline (algebraic) &
$\approx 1.04 \times 10^{-5}$ &
Number / quantum state space &
Algebraic field corrections; Higgs sector; decoherence rates \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection*{Justification}

$\xi_0 = 4/30000$ follows from the torus geometry of physical space
(geometric derivation, independent of SI measurements).
$\xi_{\text{Higgs}}$ follows from the algebraic Higgs field structure
and appears in coupling formulas between quantum states (e.g.\ Bell
correlations, $T_2$ hierarchy).

\textbf{The two $\xi$ values are not a contradiction}; they describe
complementary aspects: geometry of space ($\xi_0$) vs.\ algebra of
state space ($\xi_{\text{Higgs}}$). External communications must always
specify which parameter is meant.

% ============================================================
\section{\texorpdfstring{Refinement~4: $L_0$ and the Schwarzschild interpretation}{Refinement 4: L0 and the Schwarzschild interpretation}}
% ============================================================

\subsection*{Affected Documents}

Earlier versions of Doc.~180--182 (Lagrangian derivation, torus geometry,
maximum cosmological scale).

\subsection*{Erroneous Approach}

Earlier versions interpreted $L_0 = \xi_0 \cdot \ell_P$ as the
Schwarzschild radius of a fundamental minimal object. This
interpretation was explicitly discarded in Doc.~182 (2026 revision).

\subsection*{Correct Interpretation}

$L_0$ is exclusively the \textbf{geometric fundamental length} of the
FFGFT torus:
\begin{equation}
  L_0 \;=\; \xi_0 \cdot \ell_P \;\approx\; 2.15 \times 10^{-39}\,\text{m}.
  \tag{190.10}
\end{equation}
It defines the lowest scale stage of the $\xi$ hierarchy and has
\emph{no} Schwarzschild interpretation. The cosmological Hubble radius
$R_H$ is the system-specific upper limit of the cosmological sector --
not a universal maximum scale. Each scale has its own
system-specific upper limit.

\subsection*{Note: Schwarzschild as Consistency Check}

The Schwarzschild connection remains valid as an
\textbf{internal consistency check}: an object of mass
$M_0 = \xi_0 \cdot m_P / 2$ would have a Schwarzschild radius
exactly equal to $L_0$ -- with no free parameter. If $M_0$ matches a
scale stage of the $\xi$ hierarchy, that is a non-trivial
self-consistency test. The connection is \emph{a probe, not a derivation}.

% ============================================================
\section{Refinement~5: Scope and reach of the mass formulas}
% ============================================================

\subsection*{Context}

Several FFGFT documents describe mass derivations for leptons
and other particles. The scope of these derivations must be
communicated clearly.

\subsection*{Binding Formulation}

The FFGFT mass formulas (e.g.\ $m_\ell = r_\ell \cdot \xi^{p_\ell} \cdot v$)
yield values that agree with experiment to $\sim 1\,\%$.
This is \textbf{not a precision calculation} but a structural proof:

\begin{itemize}
  \item The mass formulas \emph{follow geometrically} from $\xi$ and $v$
    -- they are not fitted.
  \item The remaining $\sim 1\,\%$ deviations reflect
    measurement uncertainties and approximations, not errors in the
    structure.
  \item Numerical accuracy beyond the Standard Model is
    \emph{not} claimed.
\end{itemize}

To be avoided in external texts: \enquote{FFGFT calculates the masses exactly.}
The correct statement is: \enquote{FFGFT \emph{derives} the mass structure from
a single parameter $\xi$ and reproduces the orders of magnitude to $\sim 1\,\%$.}

% ============================================================
\section{Refinement~6: Koide formula only with original values}
% ============================================================

\subsection*{Binding Rule}

The Koide relation
\begin{equation}
  Q = \frac{m_e + m_\mu + m_\tau}{(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2} = \frac{2}{3}
  \tag{190.11}
\end{equation}
must be evaluated only with experimentally measured masses (PDG values).

\textbf{Not permitted:} substituting the symbolic FFGFT terms
$r_\ell \cdot \xi^{p_\ell} \cdot v$ directly into the formula. The
$\sqrt{m_i}$ operation generates cross-terms with mixed $\xi$ powers
that are foreign to the torus structure space. Any such substitution
yields $Q \approx 0.6677 \neq 2/3$ and is not a contradiction to the
theory but a category error.

\textbf{Permitted:} evaluating FFGFT terms numerically
(e.g.\ $m_\tau = 1783\,\text{MeV}$) and inserting that result
into the Koide formula like a measured value.

\textbf{Mathematical background:} The $r_\ell$ terms are
geometric invariants of their torus modes. The set of admissible
pairs $(r_i, p_i)$ is not closed under multiplication:
$r_e \cdot r_\mu = 64/15$ does not belong to any torus mode.
This is the Non-Closure Theorem (Doc.~193).
The general analysis of composition limits is found in Doc.~192.

% ============================================================
\section{\texorpdfstring{Refinement~7: Terminology \enquote{renormalization group} and scale structure}{Refinement 7: Terminology renormalization group and scale structure}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~005 (T0 tm-extension): \enquote{RG flow},
        \enquote{renormalization group factor},
        \enquote{renormalization group invariance},
        subsection \enquote{renormalization group treatment}.
  \item Doc.~008 ($\xi$ and $e$): subsection \enquote{modified
        renormalization group equations}.
  \item Doc.~019 (T0 Lagrangian, earlier version):
        subsection \enquote{renormalization group equations}.
  \item Doc.~086 (document overview): \enquote{renormalization group as flow
        in parameter space}.
  \item Doc.~189 (torus derivation): \enquote{cumulative
        renormalization group running}.
  \item Doc.~202 (FFGFT comprehensive field theory), \S 18:
        section title \enquote{The renormalization group}.
\end{itemize}

\subsection*{Previous Formulation}

In the documents listed, the $\xi_0$-modified scale running of the
coupling
\begin{equation}
  \frac{d\alpha}{d\ln\mu}
  = \beta_0\,\alpha^2\!\left(1 + \xi_0\,\ln\tfrac{\mu}{E_0}\right)
  \tag{old -- imprecise}
\end{equation}
and the corresponding scale dependence are designated as the
\emph{renormalization group}, sometimes adjacent to statements
explicitly characterizing $\xi_0$ as a topologically fixed
geometric constant.

\subsection*{Refined Formulation}

In FFGFT, the scale dependence of the coupling is \emph{not} a result
of a renormalization procedure but a direct consequence of the
recursion $\mathcal{R}$ (Doc.~203) on the fractal torus geometry.
The correct designation is therefore:

\begin{equation}
  \boxed{\;
  \begin{aligned}
    &\text{Scale structure from recursion} \\
    &\quad\equiv\; \text{recursive $\alpha$ running via $\mathcal{R}$}
  \end{aligned}
  \;}
  \tag{190.12}
\end{equation}

Specifically:
\begin{itemize}
  \item The term $\xi_0\,\ln(\mu/E_0)$ arises from the iterated
        application of the recursion $\mathcal{R}$ to the mode
        structure, not from a counter-term subtraction.
  \item $\xi_0$ is \emph{not} a fixed point of a $\beta$ function
        but a topologically fixed constant
        ($\xi_0 = 4/30000$, Doc.~180).
  \item Stability, scale flow, and UV finiteness are three aspects
        of \emph{the same} recursive structure -- not separate
        mechanisms.
\end{itemize}

\subsubsection*{Language Convention}

\begin{center}
{\footnotesize
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Avoid} & \textbf{Use} \\
\midrule
Renormalization group \newline
{\scriptsize(implies QFT procedure)} &
  Scale structure from recursion \\[6pt]
RG flow / RG running &
  Recursive $\alpha$ running; \newline
  $\mathcal{R}$-induced scale correction \\[6pt]
Renormalization group equations &
  Scale equations from $\mathcal{R}$ \\[6pt]
Renormalization group invariance &
  Recursive scale invariance \\[6pt]
Renormalization group fixed point &
  Recursion fixed point: \newline
  $\mathcal{R}(\Phi_*) = \Phi_*$ \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection*{Justification}

The designation \enquote{renormalization group} imports a tool
of standard quantum field theory based on a fundamentally different
principle: there UV divergences are absorbed by a procedure, and
parameters \emph{run} under a formal scale transformation.
In FFGFT neither the divergence problem (cf.\ Doc.~159,
\enquote{without artificial renormalization}) nor a free scale parameter to
be absorbed exists. The scale dependence is a \emph{structural
property} of the recursion, not a subsequent adjustment step.

The FFGFT-native view is already correctly formulated in Doc.~159
(\enquote{renormalization as symptom, not as solution}) and Doc.~189
(\enquote{geometrically determined, not by renormalization}); this
clarification serves to unify the terminology across the older
Lagrangian and $\xi$-derivation series (Doc.~005, 008, 019) and across
Doc.~202.

The underlying mechanism is developed in Doc.~203
(recursion operator $\mathcal{R}$) and Doc.~204
(fractal boundary condition).

% ============================================================
\section{\texorpdfstring{Refinement~8: Terminology \enquote{fractal renormalization}}{Refinement 8: Terminology fractal renormalization}}
% ============================================================

\subsection*{Affected Documents}

Doc.~005, 008, 012, 014 (with 19 occurrences the most frequent source),
041, 060, 133, 141, 159, 181.

\subsection*{Previous Formulation}

\enquote{Fractal renormalization} is used as an FFGFT-internal term for
the geometric correction factors in the conversion between
natural and SI units, and for scale-dependent corrections
on the fractal torus.

\subsection*{Refined Formulation}

Since the word \enquote{renormalization} -- even in compound form --
carries the QFT connotation of a subtraction or adjustment procedure,
the term is replaced by context-specific alternatives:

\begin{center}
{\footnotesize
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Context} & \textbf{Binding designation} \\
\midrule
Unit conversion \newline
natural $\leftrightarrow$ SI \newline
{\scriptsize(esp.\ Doc.~014)} &
  Geometric scale adjustment \\[8pt]
Scale-dependent corrections \newline on the fractal torus \newline
{\scriptsize(Doc.~133, 159, 181)} &
  Fractal correction \newline
  {\scriptsize (matches title of Doc.~133)} \\[8pt]
General scale transformation \newline by recursion &
  $\mathcal{R}$-induced \newline
  scale correction \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection*{Justification}

The proprietary term \enquote{fractal renormalization} was meant to
distinguish the procedure clearly from QFT renormalization, but it
adopts the central word and unavoidably with it the connotation of a
\emph{correction procedure}. In FFGFT this is not a procedure but
the direct numerical manifestation of the fractal geometry.
The proposed alternatives avoid this misunderstanding without
requiring new vocabulary -- both phrases are already established
in the corpus (Doc.~133 \enquote{fractal correction}; \enquote{geometric scale
adjustment} in the same semantic field as Doc.~014).

% ============================================================
\section{\texorpdfstring{Refinement~9: Column \enquote{Symmetry} and the term \enquote{color charge} in the fermion tables}{Refinement 9: Column Symmetry and the term color charge in the fermion tables}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~006 (T0 particle masses), \enquote{universal fermion table},
        column \enquote{Symmetry}.
  \item Doc.~046 (Particle Masses, English parallel version), same
        table, column \enquote{Color}.
  \item Doc.~042 ($\xi$ parameter and particles), table
        \enquote{spatial field patterns}, entry
        \enquote{Quarks: multi-node bound clusters, confined, color charge}.
  \item Doc.~005 (T0 tm-extension), Method~2 \enquote{extended fractal
        method with QCD integration}: use of $N_c = 3$,
        $\alpha_s$, $\Lambda_{\text{QCD}}$ as external inputs.
\end{itemize}

\subsection*{Previous Formulation}

In the fermion tables of Doc.~006/046 each row carries a column
\enquote{Symmetry} with the following entries:
\begin{center}
{\footnotesize
\begin{tabular}{ll}
\toprule
\textbf{Particle} & \textbf{Entry under \enquote{Symmetry}} \\
\midrule
Electron, Muon, Tau                  & Lepton number \\
$\nu_e$, $\nu_\mu$, $\nu_\tau$       & Double-$\xi$ \\
Up, Charm, Strange, Top, Bottom      & Color \\
Down                                  & Color + Isospin \\
\bottomrule
\end{tabular}
}
\end{center}

This mixture combines four different concepts in one column:
an FFGFT scaling class (\enquote{Double-$\xi$}), an SM conserved
quantity (\enquote{lepton number}), an SM gauge symmetry
(\enquote{color}), and an SM quantum number (\enquote{isospin}).
In addition, the entry \enquote{color charge} in Doc.~042 and
$N_c = 3$ in Doc.~005 suggest that the SM color symmetry $SU(3)_C$
is an independent component of FFGFT.

\subsection*{Refined Formulation}

In FFGFT neither the gauge group $SU(3)_C$ nor a color quantum number
exists. Quark masses follow, just like lepton masses, exclusively
from the Yukawa resonance formula
\begin{equation}
  m_f \;=\; r_f \cdot \xi^{p_f} \cdot v
  \tag{190.13}
\end{equation}
with $r_f$ a rational prefactor and $p_f$ a rational exponent
(step size $\Delta p = 1/3$). This is verified numerically by
the script \texttt{calc-resonanz-leiter.py}: all six quarks
hit their PDG masses to $\sim 0.3\text{--}3.4\,\%$
\emph{without} use of $N_c$, $\alpha_s$, $\Lambda_{\text{QCD}}$,
or any color quantum number.

\subsubsection*{Corrected column structure of the fermion table}

The old column \enquote{Symmetry} is replaced by two clearly
separated columns:

\begin{center}
{\footnotesize
\begin{tabular}{p{2.4cm}p{3.6cm}p{4.0cm}}
\toprule
\textbf{Particle} & \textbf{FFGFT scaling class}
                  & \textbf{SM correspondence \newline (informational)} \\
\midrule
Electron, Muon, Tau              & Single-$\xi$  & Lepton number \\
$\nu_e$, $\nu_\mu$, $\nu_\tau$   & Double-$\xi$  & Lepton number, lepton mixing \\
Up, Charm, Top                   & Cluster-$\xi$ & Up-type, $T_3 = +1/2$ \\
Down, Strange, Bottom            & Cluster-$\xi$ & Down-type, $T_3 = -1/2$ \\
\bottomrule
\end{tabular}
}
\end{center}

\textbf{Meaning of the classes:}
\begin{itemize}
  \item \emph{Single-$\xi$}: $m = r\,\xi^p\,v$ with $p \in \{2/3, 1, 3/2\}$.
  \item \emph{Double-$\xi$}: $m_\nu = r_\nu\,\xi^2\,m_e$
        (additional $\xi$ suppression relative to the charged leptons).
  \item \emph{Cluster-$\xi$}: $m = r\,\xi^p\,v$ with the same exponents
        $p \in \{-1/3, 1/2, 2/3, 1, 3/2\}$ as for the leptons, but with
        multi-node binding in the sense of Doc.~049 (cubic
        self-interaction $\lambda_s\,(\delta m_q)^3$).
\end{itemize}

\subsubsection*{Language convention for quarks}

\begin{center}
{\footnotesize
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Avoid} & \textbf{Use} \\
\midrule
\enquote{color charge}\newline
{\scriptsize(implies SU(3)$_C$ quantum number)} &
  Multi-node binding \\[6pt]
\enquote{three colors red/green/blue}\newline
{\scriptsize(SM gauge index)} &
  Triple-node cluster \newline
  {\scriptsize (the triplet is geometric, not an $SU(3)$ index)} \\[6pt]
\enquote{$N_c = 3$ colors} &
  $N_{\text{cluster}} = 3$ \newline
  {\scriptsize (geometric node count in the baryon)} \\[6pt]
\enquote{color confinement} &
  Cluster binding \newline
  {\scriptsize (cubic self-interaction)} \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection*{Status of Doc.~005, Method~2}

Doc.~005 contains two calculation methods:
\begin{itemize}
  \item \emph{Method~1: Direct geometric method.} Yukawa form
        according to Eq.~(190.13); parameter-free; accuracy $\sim 1\,\%$
        for all fermions. \textbf{This is the FFGFT method.}
  \item \emph{Method~2: Extended fractal method with QCD
        integration.} Uses $N_c$, $\alpha_s$, $\Lambda_{\text{QCD}}$,
        lattice-QCD calibration and ML.
        \textbf{This is a phenomenological bridge construction}
        for connecting to the lattice-QCD literature, not part
        of the parameter-free FFGFT.
\end{itemize}

In external communication Method~1 is to be cited. Method~2 may
be used if explicitly labelled as \enquote{bridge to lattice QCD}
or \enquote{ML-calibrated extension}.

\subsection*{Justification}

The designations \enquote{color}, \enquote{color charge}, \enquote{$N_c$}
import a concept from standard quantum field theory ($SU(3)_C$ as
gauge symmetry, three colors, eight gluons, color confinement as a
non-perturbative property). Doc.~049 explicitly states that FFGFT
contains none of these elements: \enquote{what we call ,color' becomes
high-energy node binding patterns} (Doc.~049, §3.7), with a single
cubic interaction term $\lambda_s\,(\delta m_q)^3$ instead of eight
gluon fields.

The script validation (\texttt{calc-resonanz-leiter.py},
\texttt{calc\_De.py}) shows: all quark masses follow from the same
Yukawa formula as the leptons. The column \enquote{Symmetry} of the
fermion table, however, suggests that $SU(3)_C$ is a distinguishing
property of quarks within FFGFT -- which is not the case.

The corrected column structure separates what is FFGFT-proper
(\emph{scaling class}) from informational SM correspondence
(\emph{SM correspondence}), in parallel with the separation of
\enquote{recursive $\alpha$ running} and \enquote{renormalization
group} in Refinement~7.

% ============================================================
\section{\texorpdfstring{Refinement~10: Logical status of $K = 245$ and the factor $1.314$ in Doc.~009}{Refinement 10: Logical status of K = 245 and the factor 1.314 in Doc. 009}}
% ============================================================

\subsection*{Affected Document}

Doc.~009 (Origin of $\xi$), Section \enquote{Why $K = 245$ is fundamental},
subsection \enquote{Geometric meaning}.

\subsection*{Misleading Presentation}

Doc.~009 lists the following derivation chain for $K = 245$:
\begin{itemize}
  \item $\varphi^{12} = 321.996$
  \item Correction by fractal structure: $(1-\xi)^2 \approx 0.999733$
  \item Result: $321.996 \times 0.999733 \approx 321.87$
  \item \enquote{Scaling to mass range}: $321.87 / 1.314 \approx 245$
\end{itemize}
The factor $1.314$ appears here without derivation or independent
physical justification.

\subsection*{Correct Logical Order}

$K = 245$ is not derived from $\varphi^{12}$ and $1.314$.
The correct logical order is the reverse:

\begin{equation}
  K \;=\; \frac{R_{pe}}{(4/3)^\kappa}
    \;=\; \frac{1836.153}{(4/3)^7}
    \;\approx\; 245.097
  \tag{190.14}
\end{equation}

$K$ is fixed by the observed proton-electron mass ratio $R_{pe}$ and
the exponent $\kappa = 7$. It is an \emph{empirical anchor}, not a
first-principles result. The factor $1.314$ is implicitly defined as
$\varphi^{12} / 245 \approx 1.314$ and does not constitute an
independent derivation of $K$.

\subsection*{What remains non-trivial}

The exponent $\kappa = 7$ is the \emph{unique integer} for which the
complete e-p-$\mu$ triangle closes simultaneously:
\begin{center}
{\footnotesize
\begin{tabular}{lcc}
\toprule
$\kappa$ & $K \times (4/3)^\kappa$ & Agreement with $R_{pe}$ \\
\midrule
6 & 1376.6 & $-25\,\%$ \\
7 & 1835.4 & $\checkmark\; 0.04\,\%$ \\
8 & 2447.2 & $+33\,\%$ \\
\bottomrule
\end{tabular}
}
\end{center}
This uniqueness is a genuine constraint, not a tautology.
$K = 245$ then follows from $\kappa = 7$ and the empirical $R_{pe}$.

\subsection*{Corrected claim for external communication}

\begin{itemize}
  \item \textbf{Avoid:} \enquote{$K = 245$ is derived from first
        principles; no free parameters.}
  \item \textbf{Use:} \enquote{One empirical anchor: $K = 245$,
        fixed by $R_{pe}$ and $\kappa = 7$. From this anchor,
        five mass ratios follow with ${<}\,0.04\,\%$ accuracy.
        The $\varphi^{12}$ observation is a numerological
        consistency note, not a derivation.}
\end{itemize}

% ============================================================
\section{\texorpdfstring{Refinement~11: $T_\text{CMB}$ correction factor and $K_\text{frak}$ disambiguation}{Refinement 11: T\_CMB correction factor and K\_frak disambiguation}}
% ============================================================

\subsection*{Affected Documents}

Doc.~025 (Cosmology), Doc.~003 (Foundations), Doc.~133 (Fractal Correction Derivation).

\subsection*{Issue A: $K_\text{frak}$ does not close the $T_\text{CMB}$ gap}

Doc.~025 derives:
\begin{equation}
  T_\text{CMB} \;=\; \tfrac{16}{9}\,\xi \;=\; \tfrac{4}{16875}\;\text{eV}
  \;\approx\; 2.7507\;\text{K}
  \tag{190.15}
\end{equation}
The observed value is $T_\text{CMB} = 2.72548\,\text{K}$ (Planck 2018).
The gap is $\approx 0.925\,\%$.

$K_\text{frak} = 1 - 100\xi = 74/75$ (Doc.~133) does \emph{not} close this
gap. Numerically:
\begin{equation}
  \tfrac{16}{9}\,\xi \times K_\text{frak} \;=\; 2.714\;\text{K}
  \quad (0.42\,\% \text{ below target, worse})
  \tag{190.16}
\end{equation}
The required correction factor is $0.99083$, which satisfies:
\begin{equation}
  \boxed{
    T_\text{CMB} \;=\; \tfrac{16}{9}\,\xi\,\Bigl(1 - \tfrac{275}{4}\,\xi\Bigr)
    \;=\; 2.725486\;\text{K}
  }
  \tag{190.17}
\end{equation}
Agreement with observation: $\Delta = 0.0002\,\%$.

The coefficient $275/4 = 68.75$ is close to the tetrahedral number $68 = 72 - 4$
(Doc.~003, Section~0.5) but its derivation as a second-order correction is not
yet formally established. \textbf{This is an open point:} a geometric derivation
of $275/4$ is required. The formula above is a numerically verified
result pending full justification.

\subsection*{Issue B: Two inconsistent $K_\text{frak}$ definitions}

Doc.~003 gives:
\begin{equation}
  K_\text{frak}^\text{(003)} \;=\; 1 - \frac{D_\text{frak} - 2}{68}
  \;=\; 1 - \frac{0.94}{68} \;\approx\; 0.98530
  \tag{190.18}
\end{equation}
where $D_\text{frak} = 2.94$ is stated without derivation from $\xi$.

Doc.~133 gives:
\begin{equation}
  K_\text{frak}^\text{(133)} \;=\; 1 - 100\xi \;=\; \tfrac{74}{75}
  \;\approx\; 0.98667
  \tag{190.19}
\end{equation}
derived from the cumulative RG run with $D_f = 3 - \xi$.

These differ by $1.37 \times 10^{-3}$ and cannot both be correct.
The \textbf{primary definition} is Doc.~133: $K_\text{frak} = 1 - 100\xi = 74/75$.
The value $D_\text{frak} = 2.94$ in Doc.~003 is an independent approximation
not derived from $\xi$; it uses a different (tetrahedral) model.
Doc.~003 should be understood as a heuristic motivation, not as the
defining formula.

\subsection*{Corrected claim for $T_\text{CMB}$}

\begin{itemize}
  \item \textbf{Avoid:} \enquote{$K_\text{frak}$ closes the $T_\text{CMB}$ gap.}
  \item \textbf{Use:} \enquote{$T_\text{CMB}$ requires a second-order correction
        $(1 - 275/4\cdot\xi)$, giving $0.0002\,\%$ agreement.
        The geometric origin of $275/4$ is an open derivation.}
\end{itemize}

% ============================================================
\section*{Updated Summary}
% ============================================================

\begin{center}
{\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{0.5cm}p{2.4cm}p{4.4cm}p{4.4cm}}
\toprule
\textbf{No.} & \textbf{Doc.} & \textbf{Erroneous / unclear} & \textbf{Correct / refined} \\
\midrule
C1 & 049 (HTML) &
  $\xi = \lambda_h^2 v^2/(64\pi^4 m_h^2)$ &
  $\xi = \lambda_h^2 v^2/(16\pi^3 m_h^2)$ \\[3pt]
C2 & 116 (table) &
  $r_\tau = 8/3$ &
  $r_\tau = 25/9$ \\[3pt]
C3 & 018 (Explorer) &
  $a_e = 4\pi/(f \cdot k)$ &
  $a_e = 2\pi^2/(f \cdot k)$ \\[3pt]
R1 & 116 / 158 &
  $\Delta Q < 0.00003\,\%$ vs.\ $0.001\,\%$ &
  Both correct; $0.001\,\%$ for external use \\[3pt]
R2 & several &
  $\hbar$ as a postulate &
  $\hbar$ follows from $\xi$ via $L_0 = \xi\cdot\ell_P$ \\[3pt]
R3 & 173--176 &
  A single $\xi$ value &
  Two parameters: $\xi_0$ (geom.) and $\xi_{\text{Higgs}}$ (alg.) \\[3pt]
R4 & 180--182 &
  $L_0$ as Schwarzschild radius &
  $L_0$ = geom.\ fundamental length \\[3pt]
R5 & several &
  \enquote{FFGFT calculates masses exactly} &
  Mass structure from $\xi$; $\sim 1\,\%$ agreement \\[3pt]
R6 & 116 / 158 &
  Koide with FFGFT symbolic terms &
  Koide only with numerical values (non-closure, Doc.~193) \\[3pt]
R7 & 005, 008, 019, \newline 086, 189, 202 &
  \enquote{Renormalization group} as FFGFT tool &
  Scale structure from recursion $\mathcal{R}$ \\[3pt]
R8 & 005, 008, 012, \newline 014, 041, 060, \newline 133, 141, 159, 181 &
  \enquote{Fractal renormalization} as proprietary term &
  Geometric scale adjustment / fractal correction \\
R9 & 005, 006, 042, \newline 046 &
  Column \enquote{Symmetry} with \enquote{Color}; \newline
  $N_c = 3$ as external SM input &
  Columns \enquote{Scaling class} + \enquote{SM correspondence}; \newline
  quarks via $m = r\,\xi^p\,v$ \\[3pt]
R10 & 009 &
  $K = 245$ derived from $\varphi^{12}/1.314$; \newline
  \enquote{no free parameters} &
  $K = R_{pe}/(4/3)^7$: one empirical anchor; \newline
  factor $1.314$ implicitly defined, not derived \\[3pt]
R11 & 025, 003, 133 &
  $K_\text{frak}$ closes $T_\text{CMB}$ gap; \newline
  one definition of $K_\text{frak}$ &
  Correct: $(1-275/4\cdot\xi)$, $\Delta=0.0002\,\%$; \newline
  Doc.~003 and Doc.~133 use different models \\
\bottomrule
\end{tabular}
}
}
\end{center}
