% ============================================================
% 070_T0_Mathematische_Struktur_En_ch.tex
% On the Mathematical Structure of T0 Theory
% Why Products of Different r_i Are Structurally Meaningless
% Johann Pascher — May 2026
% ============================================================

\section*{Preliminary note}

The operations discussed below are \textbf{algebraically correct}.
The restrictions are not arithmetic rules but
\textbf{consistency conditions of the FFGFT model}:
products of different $r_i$ are algebraically defined
but structurally meaningless --- they correspond to no state in the model.

%------------------------------------------------------------
\section{Prefactors as Geometric Invariants}
%------------------------------------------------------------

In FFGFT, for every particle $i$:
\begin{equation}
  m_i = r_i \cdot \xi_0^{p_i} \cdot v,
  \qquad r_i = f(\mathcal{T}_i), \quad p_i = g(\mathcal{T}_i)
\end{equation}
where $\mathcal{T}_i = (n_i, l_i, j_i)$ is the torus quantum number of the particle.

The functions $f$ and $g$ are \textbf{injective} on the set of admissible
torus modes: from $(r_i, p_i)$ one can uniquely reconstruct $\mathcal{T}_i$.

The prefactors $r_i$ are \textbf{not free parameters} but
\textbf{geometric invariants} of the respective particle ---
fully determined by its quantum numbers $(n,l,j)$.

For electron and muon (Doc.~006):
\begin{align}
  m_e &= \frac{4}{3} \cdot \xi_0^{3/2} \cdot v \label{eq:me}\\
  m_\mu &= \frac{16}{5} \cdot \xi_0^{1} \cdot v \label{eq:mmu}
\end{align}

%------------------------------------------------------------
\section{The Key Insight: The Set of Pairs \texorpdfstring{\texorpdfstring{$(r_i,p_i)$}{(ri,pi)}}{(ri,pi)} Is Not Closed Under Multiplication}
%------------------------------------------------------------

\subsection{Torus quantisation}

The admissible torus modes generate $r_i$ and $p_i$ through specific geometric
rules (Doc.~006). The admissible pairs $(r,p)$ are discrete and finite:

\begin{center}
{\footnotesize
\begin{tabular}{lcccc}
\toprule
\textbf{Particle} & \textbf{$(n,l,j)$} & \textbf{$r_i$} & \textbf{$p_i$} \\
\midrule
Electron & $(1,0,\nicefrac{1}{2})$ & $4/3$ & $3/2$ \\
Muon     & $(2,1,\nicefrac{1}{2})$ & $16/5$ & $1$ \\
Tau      & $(3,2,\nicefrac{1}{2})$ & $25/9$ & $2/3$ \\
\bottomrule
\end{tabular}
}
\end{center}

\subsection{The non-closure theorem}

Forming the product $r_e \cdot r_\mu$:
\[
  r_e \cdot r_\mu = \frac{4}{3} \cdot \frac{16}{5} = \frac{64}{15},
  \qquad p_e + p_\mu = \frac{3}{2} + 1 = \frac{5}{2}
\]

The model asks:
\begin{center}
  \emph{Is there a particle $X$ with $r_X = 64/15$ and $p_X = 5/2$?}
\end{center}

\textbf{Answer: No.} In the quantum number table, $64/15$ appears for
no $p$, and $p=5/2$ appears for no $r$.

This is not coincidence. The set of admissible pairs $\mathcal{P}$
is \textbf{not closed} under multiplication:
\[
  \forall\, i \neq j:\; (r_i \cdot r_j,\; p_i + p_j) \notin \mathcal{P}
\]
where $\mathcal{P}$ is the set of all pairs occurring in FFGFT.

\subsection{Why is this so?}

The admissible torus modes have separate, non-multiplicative generation rules for $r$:
\[
  r(n,l) = \frac{(l+1)^2}{n^2 - l(l+1)} \cdot \text{(spin factor)}
\]
(simplified). The product of two such fractions is \textbf{never} again
a fraction of the same form with two quantum numbers.

The $r_i$ are therefore not numbers in a field, but
\textbf{labels of a discrete geometric space with its own composition} ---
and this composition is not field multiplication.

%------------------------------------------------------------
\section{Algebraically Correct but Structurally Meaningless}
%------------------------------------------------------------

\subsection{The cross-product problem}

Inserting \eqref{eq:me} and \eqref{eq:mmu} symbolically into
$E_0 = \sqrt{m_e \cdot m_\mu}$:
\begin{equation}
  E_0^2 = m_e \cdot m_\mu
        = \underbrace{\frac{4}{3} \cdot \frac{16}{5}}_{r_e \cdot r_\mu}
          \cdot \xi_0^{3/2+1} \cdot v^2
        = \frac{64}{15} \cdot \xi_0^{5/2} \cdot v^2
  \label{eq:cross}
\end{equation}

The result is \textbf{algebraically correct}. But because
$(64/15,\;5/2) \notin \mathcal{P}$, this expression corresponds to
\textbf{no FFGFT particle} --- it is structurally uninterpretable.

\subsection{Analogy: different algebraic spaces}

Each particle $i$ lives in the state space spanned by its torus mode $\mathcal{T}_i$.
The $r_i$ are coefficients in \emph{different spaces}.
Their product corresponds to a tensor product:
\[
  r_e \cdot r_\mu \;\leftrightarrow\; \mathbf{v}_e \otimes \mathbf{v}_\mu
\]
This yields a tensor-product state --- \textbf{not} a state in the original
single-particle space. In a single-particle theory (mass formulas), such
a state is meaningless.

\subsection{Further substitution worsens the result}

Inserting \eqref{eq:cross} into $\alpha = \xi_0 \cdot (E_0/\text{MeV})^2$:
\begin{equation}
  \alpha \stackrel{\text{structurally wrong}}{=}
  \frac{64}{15} \cdot \xi_0^{7/2} \cdot \frac{v^2}{\text{MeV}^2}
\end{equation}
Exponent $7/2$ and factor $64/15$ appear nowhere in the basic equations.
Additionally $K_{\text{frak}}$ is missing and units are covertly mixed.
In practice: instead of $-1.35\,\%$, one gets $-3.15\,\%$ deviation.

%------------------------------------------------------------
\section{What Is Permitted and Why}
%------------------------------------------------------------

\subsection{Numerical evaluation: transition to $\mathbb{R}$}

Numbers live in $\mathbb{R}$, where multiplication is always permitted.
Once $r_e$ and $r_\mu$ have been evaluated to numbers, they have
\textbf{no memory} of their origin from different particles:

\begin{align*}
  m_e &\approx 0.511\,\text{MeV}, \quad
  m_\mu \approx 105.66\,\text{MeV} \\
  E_0 &= \sqrt{0.511 \cdot 105.66}\,\text{MeV} = 7.348\,\text{MeV} \\
  \alpha &= \xi_0 \cdot (7.348)^2 \approx 0.00720 \quad (-1.35\,\%)
\end{align*}

\subsection{Division: respecting the separate spaces}

In ratios, $v$ and $K_{\text{frak}}$ cancel, and the quantum number
structures \emph{remain separate}:
\[
  \frac{m_\mu}{m_e}
  = \frac{r_\mu}{r_e} \cdot \xi_0^{p_\mu - p_e}
  = \frac{12}{5} \cdot \xi_0^{-1/2}
  \approx 207.9 \quad (0.5\,\%)
\]
The result $12/5$ is interpretable --- no cross-product.
Division \textbf{respects} the separate quantum number spaces.

\begin{tcolorbox}[colback=blue!5, colframe=blue!60!black, boxrule=0.5pt,
  arc=2pt, left=3mm, right=3mm, fontupper=\small,
  title={Basic rule --- The non-closure condition}]
The set of admissible pairs $(r_i, p_i)$ is not closed under multiplication:
\[
  \boxed{\forall\, i \neq j:\; (r_i \cdot r_j,\; p_i + p_j) \notin \mathcal{P}}
\]
Therefore: products of different $r_i$ are algebraically defined
but correspond to no particle in the model.
Only numerical evaluation (transition to $\mathbb{R}$) permits
free combination.
\end{tcolorbox}

%------------------------------------------------------------
\section{Connection to Other Results}
%------------------------------------------------------------

The same principle applies to the Koide relation (Doc.~192):
there too, symbolic insertion of mass terms generates cross-terms
with exponents belonging to no particle.

The rule is not arbitrary, but a \textbf{necessary consequence of
torus quantisation} and the injectivity of $f$ and $g$.

%------------------------------------------------------------
\section*{Summary}
%------------------------------------------------------------

\begin{quote}
\emph{The prefactors $r_i$ are not free parameters but geometric
invariants of torus modes with fixed quantum numbers. The set of admissible
pairs $(r_i, p_i)$ is not closed under multiplication --- a product
$r_i \cdot r_j$ with $i \neq j$ is algebraically defined but belongs
to no torus mode and is therefore meaningless in the model. Combinations
are only permitted after numerical evaluation in $\mathbb{R}$.}
\end{quote}

%------------------------------------------------------------
\section*{Legend}
%------------------------------------------------------------

\begin{center}
{\footnotesize
\begin{tabular}{ll}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$\mathcal{T}_i = (n_i, l_i, j_i)$ & Torus mode of particle $i$: principal, orbital, spin quantum number \\
$r_i = f(\mathcal{T}_i)$ & Geometric prefactor (injective from quantum numbers) \\
$p_i = g(\mathcal{T}_i)$ & Exponent in the mass formula \\
$\mathcal{P}$ & Set of all admissible pairs $(r_i, p_i)$ in FFGFT \\
$v = 246\,\text{GeV}$ & Higgs vacuum expectation value (scale factor) \\
$\xi_0 = 4/30000$ & Geometric base parameter \\
$K_{\text{frak}}$ & Fractal correction ($\approx 0.986$) \\
$\mathbb{R}$ & Real numbers (measured values without structural memory) \\
$\mathbf{v}_e \otimes \mathbf{v}_\mu$ & Tensor-product state (meaningless in single-particle theory) \\
$(64/15,\;5/2)$ & Cross-product pair --- not in $\mathcal{P}$, no FFGFT particle \\
\bottomrule
\end{tabular}
}
\end{center}


\medskip\noindent
\textbf{References:} Doc.~006 (quantum numbers), Doc.~043, Doc.~011,
Doc.~044 ($\alpha$), Doc.~192 (Koide, general principle).
