% ============================================================
% 210_T0_Korrekturen_Wicklung_En_ch.tex
% Errata Register II – FFGFT / T0 Time-Mass Duality
% Topic: Winding numbers, torus modes, ambiguity of (n,l,j)
% Date: 10 May 2026
% Intended for later merge with Doc. 190.
% ============================================================

\section*{Preliminary Note}

This document supplements the errata register Doc.~190 with
clarifications that exclusively concern the \textbf{winding-number
structure of the particles on the fractal torus}. It is kept as a
separate document so that the winding question can be treated as a
closed unit; later merge with Doc.~190 is intended.

The statements recorded here override conflicting readings in the
older documents. Older documents are \emph{not} modified.

\bigskip

\textbf{Core statement.} Each fermion in FFGFT carries three
\emph{distinct} winding-number layers, which in the older documents
appear under the same symbols $(n,l,j)$ or \enquote{winding}, but
have different geometric meanings:

\begin{itemize}
  \item a universal base winding number $f = 1/(4\xi) = 7500$
        (the same for all particles),
  \item a spin winding $(n_\theta, n_\phi)$ on the inner spin
        fibration of the 4D torus $T^4$,
  \item a generation winding as fractal branching with
        Hausdorff dimension $p_{g\!-\!2}$.
\end{itemize}

The space-time mode of each particle lives on the \textbf{4D torus}
$T^4$ and carries four integer winding numbers $(k_x, k_y, k_z, k_t)$.
These four layers are clearly separated in what follows. A fifth
refinement (W5) additionally clarifies the bridge formula between the
direct geometric and the Yukawa mass formula and resolves the
ambiguity of the symbol $f_i$ in the older documents.

% ============================================================
\section{\texorpdfstring{Refinement~W1: Universal base winding number $f = 7500$}{Refinement W1: Universal base winding number f = 7500}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~060 (Music parallels) §\enquote{Circle of fifths
        $\leftrightarrow$ torus topology}: \enquote{$f = 7500$ windings}.
  \item Doc.~018 (Anomalous g-2) §\enquote{The real sub-Planck factor
        $f = 7500$}.
  \item Doc.~149 (FFGFT torsion) §\enquote{The ideal anchor number}:
        $f = 1/(4\xi) = 30000/4 = 7500$.
\end{itemize}

\subsection*{Binding Reading}

\begin{equation}
  \boxed{\;f \;=\; \frac{1}{4\xi} \;=\; \frac{30000}{4} \;=\; 7500\;}
  \tag{210.1}
\end{equation}

$f$ is the \emph{winding density of the universal 4D torus} and is
\textbf{not particle-specific}. All particles are modes on the same
torus with the same base winding. Where older documents speak of
\enquote{the winding number of a particle}, this does not refer to
$f$, but to one of the subordinate windings from W2 or W3.

\subsection*{Justification}

The constant $f = 7500$ is the geometric inverse of $4\xi$, hence
directly derived from the geometry parameter $\xi_0 = 4/30000$
(Doc.~180, 182). Its prime factorization
$7500 = 2^2 \cdot 3 \cdot 5^4$ (Doc.~149 §65) reflects the tetrahedral
symmetry ($3$), the spatial dimensionality ($2^2$), and the pentagonal
projection ($5^4$) -- all universal structural features, not
particle-specific ones.

% ============================================================
\section{Torus Geometry: Symbol Reference}
% ============================================================

For the winding designations in W1--W4 to be unambiguous, here first
the torus geometry and the symbol legend.

\subsection*{What \enquote{4D torus} means here}

The FFGFT torus is a \textbf{four-dimensional torus} $T^4$.
Important: time is not a separate, linear coordinate $\mathbb{R}$
\emph{next to} the torus, but \textbf{the fourth compact circle
direction} \emph{within} the torus itself. This is the geometric
expression of the time-mass duality $\tilde T \cdot m = 1$: time and
the three spatial directions are circles of equal status, all four
cyclically closed.

\begin{equation}
  T^4 \;=\; S^1_x \,\times\, S^1_y \,\times\, S^1_z \,\times\, S^1_t
  \tag{210.0}
\end{equation}

Hence \emph{every} mode of the universe carries four integer winding
numbers $(k_x, k_y, k_z, k_t)$ -- three spatial and one temporal.

\textbf{Note on older formulations:} where Doc.~202 §116 writes the
support manifold as $T^3 \times \mathbb{R}$, the low-energy
approximation is meant in which the temporal circle direction
appears unrolled to $\mathbb{R}$. Binding is the full 4D torus
structure $T^4$.

\subsection*{Anatomy of a Torus -- Section View}

Since $T^4$ is four-dimensional, it cannot be drawn directly. The
following sketch shows a \textbf{2D cross-section} through two
selected circle directions -- e.g.\ $(x, t)$ or $(\theta, \phi)$.
The other two circle directions are orthogonal and treated separately.

\begin{center}
\begin{tikzpicture}[scale=0.95,
  poloidal/.style={thick, T0red,    -{Latex[length=2mm]}},
  toroidal/.style={thick, T0blue,   -{Latex[length=2mm]}}]

  \draw[ultra thick, T0gray!50] (0,0) ellipse (2.6cm and 1.2cm);
  \draw[ultra thick, T0gray!50] (0,0) ellipse (0.85cm and 0.45cm);

  \draw[toroidal]
    (1.7,-0.92) arc[start angle=-25, end angle=235, x radius=1.7cm, y radius=0.82cm];

  \begin{scope}[shift={(2.05,0)}]
    \draw[ultra thick, T0red!30] (0,0) ellipse (0.45cm and 0.45cm);
    \draw[poloidal]
      (0,0.45) arc[start angle=90, end angle=-200, radius=0.45cm];
  \end{scope}

  \draw[ultra thick, T0orange, smooth, tension=0.8]
    plot coordinates {
      (2.05,0.45) (1.5,0.6) (0.8,0.75) (0,0.85) (-0.8,0.75)
      (-1.5,0.6) (-2.2,0.4) (-2.55,0.0) (-2.2,-0.4)
      (-1.5,-0.6) (-0.8,-0.75) (0,-0.85) (0.8,-0.75)
      (1.5,-0.6) (2.05,-0.45) (2.55,0.0) (2.05,0.45)
    };

  \node[T0blue, font=\bfseries\small, align=center] (lblPhi) at (-2.2,2.0)
    {big circle\\(one direction)};
  \draw[->, T0blue, thick] (lblPhi) -- (-1.4,1.0);

  \node[T0red, font=\bfseries\small, align=center] (lblTheta) at (2.2,2.0)
    {small circle\\(other direction)};
  \draw[->, T0red, thick] (lblTheta) -- (2.05,0.45);

  \node[T0gray, font=\footnotesize] at (0,0) {hole};

  \node[T0orange, font=\bfseries\small] at (0,-1.7)
    {$(1,1)$ winding in cross-section};

\end{tikzpicture}
\end{center}

\textbf{Reading aid for the sketch:} the gray double-ellipse is the
top view of a cross-section torus -- the tube seen from above, with
the hole in the middle. The red arrow on the right shows one circle
traversed once (cross-section of the tube). The blue arrow shows the
other circle traversed once (around the hole). The orange path is a
$(1,1)$ winding: a single simultaneous traversal of both circles.

On the 4D torus, every mode lives with \emph{four} such winding
numbers simultaneously. The sketch shows only two of them.

\subsection*{Symbol Legend}

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{>{\raggedright\arraybackslash}p{2.6cm}>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{7.4cm}}
\toprule
\textbf{Symbol} & \textbf{Designation} & \textbf{Geometric meaning} \\
\midrule
$T^4$ &
  4D space-time torus &
  Support manifold of FFGFT. $T^4 = S^1_x \times S^1_y \times S^1_z \times S^1_t$ -- four cyclic circle directions, three spatial and one temporal. All four have the same topological status. \\
$S^1_x, S^1_y, S^1_z$ &
  Spatial circle directions &
  The three spatial dimensions, each rolled into a circle of base period $L_0$. \\
$S^1_t$ &
  Temporal circle direction &
  Time as the fourth circle direction. Period $\tilde T_0 = L_0/c$. \emph{Not} a separate $\mathbb{R}$ line; time-mass duality $\tilde T \cdot m = 1$ is geometrically visible here. \\
$(k_x, k_y, k_z, k_t)$ &
  Wave-vector winding numbers &
  Four integer winding numbers of a mode on $T^4$. Each counts how often the mode wraps around the corresponding circle direction. \\
$\theta, \phi$ &
  Poloidal / toroidal angle &
  In the \emph{cross-section} representation of the torus through two circle directions, the cross-section circle (\enquote{small circle}) is denoted $\theta$, the loop around the hole (\enquote{big circle}) is denoted $\phi$. \\
$(n_\theta, n_\phi)$ &
  Spin winding &
  Pair of winding numbers specifically for the spin property of a particle. Encodes not the space-time mode, but the inner spin structure (W2). \\
$L_0$ &
  Base period &
  Length scale $L_0 = \ell_P/\xi$ of the universal torus (Doc.~182). Defines the size of \emph{all four} circle directions together with $c$. \\
$f$ &
  Winding density &
  $f = 1/(4\xi) = 7500$. Number of base periods $L_0$ that fit into the Hubble distance; \emph{not} a winding number of individual particles. The factor $4$ in $1/(4\xi)$ comes directly from the four-dimensionality of $T^4$. \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{Space-time mode vs.\ spin winding}

On the 4D torus $T^4$, every mode carries \emph{two distinct sets}
of winding numbers, independent of each other:

\begin{center}
\renewcommand{\arraystretch}{1.4}
\setlength{\tabcolsep}{8pt}
\begin{tabular}{>{\raggedright\arraybackslash}p{3.0cm}>{\raggedright\arraybackslash}p{4.6cm}>{\raggedright\arraybackslash}p{4.8cm}}
\toprule
 & \textbf{Space-time mode} & \textbf{Spin winding} \\
\midrule
Lives on &
  All four circles of $T^4$ &
  Inner spin fibration over $T^4$ \\
Winding numbers &
  $(k_x, k_y, k_z, k_t)$ &
  $(n_\theta, n_\phi)$ \\
What they encode &
  Space-time motion of the mode, generation, particle identity (W4) &
  Spin (W2) \\
Characterizes &
  Generation and identity of the particle &
  Spin class: fermion / boson / Higgs \\
\bottomrule
\end{tabular}
\setlength{\tabcolsep}{6pt}
\renewcommand{\arraystretch}{1.0}
\end{center}

\textbf{Both winding sets exist simultaneously.} An electron sits
with space-time wave vector $(k_x,k_y,k_z,k_t)$ on $T^4$ \emph{and}
additionally carries the spin winding $(1,1)$ on the inner fibration.

% ============================================================
\section{\texorpdfstring{Refinement~W2: Spin winding $(n_\theta, n_\phi)$}{Refinement W2: Spin winding}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~051 (Dirac, FFGFT) §\enquote{Topological interpretation},
        §\enquote{Winding numbers on the torus}.
  \item Doc.~202 §\enquote{Quantum numbers of the modes} \S 7.4
        (spin structure).
\end{itemize}

\subsection*{Binding Reading}

The \textbf{spin winding} is a property on the inner spin fibration
over the 4D torus $T^4$, with two independent winding numbers
$(n_\theta, n_\phi)$:

\begin{equation}
  \text{Spin-}s \;\longleftrightarrow\;
  (n_\theta, n_\phi)\ \text{with}\ \frac{n_\phi}{n_\theta} = 2s
  \tag{210.2}
\end{equation}

\begin{center}
{\footnotesize
\begin{tabular}{lcl}
\toprule
\textbf{Particle class} & \textbf{Spin $s$} & \textbf{$(n_\theta, n_\phi)$} \\
\midrule
All fermions (e, $\mu$, $\tau$, $\nu$, q) & $1/2$ & $(1,1)$ \\
Gauge bosons ($\gamma$, $W^\pm$, $Z$, $g$) & $1$  & $(1,2)$ \\
Higgs boson                                 & $0$  & $(1,0)$ \\
Hypothetical graviton                       & $2$  & $(1,4)$ \\
\bottomrule
\end{tabular}
}
\end{center}

\textbf{Geometric reading of the fermion's $(1,1)$ winding:}
The orange path in the sketch above shows what it means to wind
$(1,1)$. Traversing the path goes \emph{once around the small circle}
($n_\theta = 1$) and \emph{once around the big circle} ($n_\phi = 1$).
Only after \emph{two} such traversals does a point with the same
phase return to itself -- this is the topological origin of the 720°
periodicity of spin-$\tfrac12$.

\textbf{Important:} the spin winding does \emph{not} distinguish the
twelve fermions from one another -- they all carry $(1,1)$. It only
distinguishes spin classes.

\subsection*{Justification}

The topological interpretation of spin as a winding number is
explicitly developed in Doc.~051 and supported by the Clifford-algebra
structure (Doc.~050, 051). It is independent of the generation
hierarchy of masses and applies universally to all
spin-$\tfrac12$ fermions.

% ============================================================
\section{\texorpdfstring{Refinement~W3: Generation winding as fractal branching}{Refinement W3: Generation winding as fractal branching}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~018 (anomalous g-2 v12) §\enquote{Muon: fractal extra
        winding}, §\enquote{Tau: more complex fractal structure}.
  \item Doc.~149 (FFGFT torsion) Abstract.
\end{itemize}

\subsection*{Binding Reading}

The generations differ by \textbf{fractal branchings} of the base
winding with characteristic Hausdorff dimension $p_{g\!-\!2}$:

\begin{equation}
  a_\ell \;=\; a_e^{\text{base}} \;+\; \frac{4\pi}{f^{\,p_{\ell}}}
  \tag{210.3}
\end{equation}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\footnotesize
\begin{tabular}{lc>{\raggedright\arraybackslash}p{6.5cm}l}
\toprule
\textbf{Particle} & \textbf{$p_{g\!-\!2}$} & \textbf{Geometric meaning} & \textbf{Source} \\
\midrule
Electron & --   & Base winding (tetrahedral projection) & Doc.~018 §6 \\
Muon     & $5/3$ & Brownian motion in 2D (\enquote{partially branched winding}) & Doc.~018 §7 \\
Tau      & $4/3$ & Box-counting of the Koch curve (stronger branching) & Doc.~018 §8 \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\textbf{Key property:} higher generation $\Rightarrow$ \emph{lower}
Hausdorff dimension $\Rightarrow$ stronger fractal branching
$\Rightarrow$ larger contribution to the anomalous magnetic moment.

\subsection*{Justification}

The Hausdorff dimensions $5/3$ and $4/3$ are explicitly introduced in
Doc.~018 §215--290 and traced to known fractal structures (2D Brownian
motion, Koch curve). Formula~(210.3) reproduces $a_e$ and $a_\mu$ with
fractal correction $K_{\text{frak}}^{3/2}$ to $0.014\,\%$ and
$0.15\,\%$ accuracy, respectively (Doc.~018 §211, §268).

% ============================================================
\section{\texorpdfstring{Refinement~W4: Three meanings of $(n,l,j)$ -- clean separation}{Refinement W4: Three meanings of (n,l,j)}}
% ============================================================

\subsection*{Problem Statement}

In the older documents the symbol triple $(n,l,j)$ appears in
\emph{three} different meanings:

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{>{\raggedright\arraybackslash}p{3.4cm}>{\raggedright\arraybackslash}p{4.5cm}>{\raggedright\arraybackslash}p{4.8cm}}
\toprule
\textbf{Source} & \textbf{Meaning} & \textbf{Values for electron, muon, tau} \\
\midrule
Doc.~005, 006, 042 &
  Hydrogen-like generation indices &
  $(1,0,\tfrac12)$, $(2,1,\tfrac12)$, $(3,2,\tfrac12)$ \\
Doc.~005 §153 (fractal method) &
  Three independent indices $(n_1, n_2, n_3)$, $n_{\text{eff}} = n_1+n_2+n_3$ &
  $(1,0,0)$, $(2,1,0)$, $(3,2,0)$ \\
Doc.~202 §72--88 &
  Wave-vector components $n = k_x^2 + k_y^2 + k_z^2$, $l^2 = k_x^2 + k_y^2$ &
  $\mathbf{k} = (1,0,0)$, $(1,1,0)$, $(1,1,1)$; hence $n = 1, 2, 3$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

The first two tables assign values to the triple labels without
specifying a geometric construction; Doc.~202 derives $n$
\emph{retrospectively} from the wave vector.

\subsection*{Binding Reading}

Binding is the wave-vector definition on the 4D torus $T^4$. The
space-time mode carries a \emph{four-dimensional} wave vector:

\begin{equation}
  \boxed{\;\mathbf{k} \;=\; \frac{2\pi}{L_0}(k_x,k_y,k_z,k_t),
  \quad k_x,k_y,k_z,k_t \in \mathbb{Z}\;}
  \tag{210.4}
\end{equation}

with $n$, $l$, $j$ as derived quantities from the three
\emph{spatial} components:

\begin{align}
  n &\;=\; k_x^2 + k_y^2 + k_z^2
       \quad\text{(principal quantum number, spatial part)} \tag{210.5}\\
  l &\;=\; \text{orbital angular momentum from spherical harmonics}
       \;Y_{l,m}(\theta,\phi) \tag{210.6}\\
  j &\;=\; l \pm \tfrac12
       \quad\text{(spin-orbit coupling, spin winding from W2)} \tag{210.7}
\end{align}

The temporal winding number $k_t$, after \emph{Wick rotation} or
low-energy unrolling, gives the mass energy of the mode:
\begin{equation}
  E_t \;=\; \frac{2\pi\, k_t}{\tilde T_0} \;=\; \frac{2\pi\,k_t\,c}{L_0}
  \tag{210.7a}
\end{equation}
In the low-energy limit $k_t \to 0$ the temporal circle direction
unrolls onto $\mathbb{R}$ -- this is the form in which Doc.~202 §116
writes the manifold as $T^3 \times \mathbb{R}$.

\textbf{Note:} the notation $l = \sqrt{k_x^2+k_y^2}$ in Doc.~202 §85--90
is to be understood as a \emph{scaling relation} and does not replace
the exact quantization $l(l+1) = \langle k_x^2+k_y^2 \rangle$. The
integer values $(0,1,2)$ for $l$ in the lepton table are the
corresponding orbital angular momentum eigenvalues, not the result of
direct square root extraction.

\subsection*{Language Convention for Future Documents}

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{>{\raggedright\arraybackslash}p{6.0cm}>{\raggedright\arraybackslash}p{6.5cm}}
\toprule
\textbf{When meaning is} & \textbf{Designation to use} \\
\midrule
Wave-vector winding &
  $(k_x, k_y, k_z, k_t) \in \mathbb{Z}^4$ \\
Hydrogen quantum numbers &
  $(n,l,j)$ \\
Spin winding &
  $(n_\theta, n_\phi)$ \\
Hausdorff branching exponent (g-2 anomaly) &
  $p_{g\!-\!2}$ \\
Yukawa mass exponent &
  $p_{\text{Yuk}}$ or simply $p$ in the form $m = r\,\xi^p\,v$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\textbf{Important:} the symbols $p_{g\!-\!2}$ and $p_{\text{Yuk}}$
denote \emph{different} quantities with different values:

\begin{center}
{\footnotesize
\begin{tabular}{lcc}
\toprule
\textbf{Particle} & \textbf{$p_{\text{Yuk}}$} (mass formula) & \textbf{$p_{g\!-\!2}$} (Hausdorff) \\
\midrule
Electron & $3/2$  & --\,(base) \\
Muon     & $1$    & $5/3$ \\
Tau      & $2/3$  & $4/3$ \\
\bottomrule
\end{tabular}
}
\end{center}

% ============================================================
\section{\texorpdfstring{Refinement~W5: Bridge formula between direct and Yukawa method}{Refinement W5: Bridge formula between direct and Yukawa method}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}
  \item Doc.~Teilchenmassen\_De (older version), §\enquote{Complete
        quark analysis with both methods} and §\enquote{Corrected
        interpretation of mathematical equivalence}.
  \item Doc.~005 (T0-tm-Extension), §\enquote{Method 1: Direct
        geometric resonance (lepton basis)}: values $f_\mu = 207$,
        $f_\tau = 12.3$.
  \item Doc.~006 (T0-Particle Masses), §\enquote{Universal table}:
        three different readings of the same symbol $f_i$.
  \item Doc.~T0\_Teilchenmassen\_De (Z.~384), §\enquote{Mathematical
        proof of equivalence}: identity claim
        $K_{\text{frak}}/(\xi_0 f_i)\cdot C_{\text{conv}}
        = r_i\,\xi_0^{p_i}\,v$
        without explicit resolution of the bridge formula.
\end{itemize}

\subsection*{Problem Statement}

In the older documents the symbol $f_i$ is used in \emph{three}
different meanings, often not clearly separated:

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\footnotesize
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{4.6cm}>{\raggedright\arraybackslash}p{5.0cm}}
\toprule
\textbf{Meaning} & \textbf{Definition} & \textbf{Values for e, $\mu$, $\tau$} \\
\midrule
$f_i^{\,(\text{cluster})}$ &
  Geometric cluster label in $\xi_i = \xi_0\cdot f_i$ &
  $1,\;16/5,\;25/9$ (rational fractions, identical with $r_i$) \\
$f_i^{\,(\text{bridge})}$ &
  Inverse frequency size $f_i = 1/(\xi_0 \cdot m_i)$ &
  $1.47\!\cdot\!10^7$, $7.10\!\cdot\!10^4$, $4.22\!\cdot\!10^3$ (orders of magnitude $10^3$--$10^7$) \\
$f_i^{\,(\text{ratio})}$ &
  Mass ratio $m_i/m_e$ (in Doc.~005 erroneously entered as $f$) &
  $1,\;207,\;3477$ resp.\ $1,\;207,\;12.3$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

The three meanings are \emph{not} equivalent. The use of the same
letter for three distinct quantities is a main source of confusion
in the discussion of the \enquote{two methods}.

\subsection*{Binding Reading}

FFGFT uses as its canonical mass formula the Yukawa form
(Doc.~006 §161):

\begin{equation}
  \boxed{\;m_i \;=\; r_i \cdot \xi_0^{\,p_i} \cdot v\;}
  \tag{210.9}
\end{equation}

with $r_i, p_i \in \mathbb{Q}$ from the consolidated table (above).

The direct geometric form
\begin{equation}
  m_i \;=\; \frac{1}{\xi_0 \cdot f_i^{\,(\text{bridge})}}
  \tag{210.10}
\end{equation}
is linked to (210.9) by the \textbf{bridge formula}
(Doc.~Teilchenmassen\_De Z.~649):

\begin{equation}
  \boxed{\;f_i^{\,(\text{bridge})}
  \;=\; \frac{1}{r_i \cdot \xi_0^{\,p_i+1} \cdot v}\;}
  \tag{210.11}
\end{equation}

Hence the direct and Yukawa forms are \textbf{not two independent
paths}, but \emph{one and the same formula in two notations},
mutually convertible by the identity (210.11).

\subsection*{Character of the Equivalence}

The older version (Doc.~Teilchenmassen\_De Z.~640) states this
plainly:

\begin{quote}
\enquote{The mathematical equivalence of both methods is given
\emph{by definition}, when the parameters ($r_i$ or $f_i$) are
determined from the same experimental masses. The equivalence is
not a proof for the theory, but a consistency property of the
mathematical structure.}
\end{quote}

Binding: statements like \enquote{the two methods confirm each other
to $0.2\%$ accuracy} (Doc.~032 §70) are \emph{tautological} -- both
methods \emph{must} agree numerically because they are identical by
construction via (210.11).

\subsection*{Numerical Verification of the Bridge Formula}

With $\xi_0 = 4/30000$, $v = 246\,\text{GeV}$ and the Yukawa values
from the consolidated table:

\begin{center}
{\footnotesize
\begin{tabular}{lcccc}
\toprule
\textbf{Particle} & \textbf{$r_i$} & \textbf{$p_i$} &
  \textbf{$f_i^{\,(\text{bridge})}$ from (210.11)} &
  \textbf{$f_i$ in old table} \\
\midrule
Electron & $4/3$  & $3/2$ & $1.485 \cdot 10^7$ & $1.468 \cdot 10^7$ \\
Muon     & $16/5$ & $1$   & $7.146 \cdot 10^4$ & $7.099 \cdot 10^4$ \\
Tau      & $25/9$ & $2/3$ & $4.205 \cdot 10^3$ & $4.221 \cdot 10^3$ \\
\bottomrule
\end{tabular}
}
\end{center}

Agreement to $\sim 1\%$ (residual loss from rounding of the input
values). Hence (210.11) is numerically confirmed.

\subsection*{Maximal Formula: Connection to the Fine-Structure Constant}

The bridge formula (210.11) extends to the \textbf{maximal formula}
that links masses and the fine-structure constant in one expression
(Doc.~Mathematische\_struktur\_De Z.~1019):

\begin{equation}
  \boxed{\;\alpha \;=\; c_e \cdot c_\mu \cdot \xi_0^{11/2}\;}
  \tag{210.12}
\end{equation}

with the geometric coefficients (Doc.~Mathematische\_struktur\_De
Z.~1034):

\begin{equation}
  c_e \;=\; \frac{3\sqrt{3}}{2\pi\,\alpha^{1/2}},
  \qquad
  c_\mu \;=\; \frac{9}{4\pi\alpha},
  \qquad
  c_e \cdot c_\mu \;=\; \frac{27\sqrt{3}}{8\pi^2\,\alpha^{3/2}}
  \tag{210.13}
\end{equation}

Solved for $\alpha$ in closed form
(Doc.~Mathematische\_struktur\_De Z.~526):

\begin{equation}
  \boxed{\;\alpha \;=\; \left(\frac{27\sqrt{3}}{8\pi^2}\right)^{2/5}
  \cdot \xi_0^{\,11/5} \cdot K_{\text{frak}}\;}
  \tag{210.14}
\end{equation}

Numerically: $\alpha^{-1} \approx 137.04$ -- consistent with CODATA
to $0.013\%$.

\textbf{Reading:} the fractions $4/3$, $16/5$, $25/9$ in the
Yukawa form are \emph{not} simple rational numbers, but disguised
expressions in $\alpha, \pi, \sqrt{3}$
(Doc.~Mathematische\_struktur\_De §25.3.1). Reducing the fractions
directly destroys this structure. The maximal formula (210.14)
shows that the seemingly two independent constants $\alpha$ and
$\xi_0$ are in fact \textbf{not independent}, but follow both from
the same fractal geometry.

\subsection*{Recommendation for Future Communication}

\begin{itemize}
  \item Use exclusively the Yukawa form $m_i = r_i\,\xi_0^{p_i}\,v$
        as the canonical mass formula.
  \item When the direct form is needed (e.g.\ for connection to older
        documents), cite the bridge formula (210.11) explicitly,
        rather than writing \enquote{$f_i$} without specification.
  \item Avoid the phrasing \enquote{the two methods confirm each
        other}; say instead \enquote{the Yukawa form and the direct
        form are identical by construction via (210.11)}.
  \item For deeper geometric discussion, cite
        Doc.~Mathematische\_struktur\_De §25 (maximal formula), where
        the fractions $r_i$ are decomposed into their
        $\alpha$-$\pi$-$\sqrt{3}$ structure.
\end{itemize}

% ============================================================
\section{\texorpdfstring{Consolidated Winding Table of the Twelve Fermions}{Consolidated Winding Table of the Twelve Fermions}}
% ============================================================

The following table lists, for each of the twelve Standard Model
fermions, all four winding layers synchronously. It replaces the
scattered and partly conflicting tables in Doc.~005, 006, 042, 202.

\begin{center}
{\scriptsize
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{1.6cm}ccccccc}
\toprule
\textbf{Particle} &
  \textbf{Spin}\newline$(n_\theta,n_\phi)$ &
  \textbf{Space wind.}\newline$(k_x,k_y,k_z)$ &
  \textbf{Time w.}\newline$k_t$ &
  \textbf{$n$} &
  \textbf{$p_{\text{Yuk}}$} &
  \textbf{$r_i$} &
  \textbf{$p_{g\!-\!2}$} \\
\midrule
\multicolumn{8}{l}{\textit{Charged leptons}} \\
\midrule
Electron & $(1,1)$ & $(1,0,0)$ & (mass) & $1$ & $3/2$ & $4/3$  & base \\
Muon     & $(1,1)$ & $(1,1,0)$ & (mass) & $2$ & $1$   & $16/5$ & $5/3$ \\
Tau      & $(1,1)$ & $(1,1,1)$ & (mass) & $3$ & $2/3$ & $25/9$ & $4/3$ \\
\midrule
\multicolumn{8}{l}{\textit{Neutrinos (double-$\xi$, $m_\nu = r_\nu \xi^2 m_e$)}} \\
\midrule
$\nu_e$    & $(1,1)$ & $(1,0,0)$ & (mass) & $1$ & --    & $1$    & -- \\
$\nu_\mu$  & $(1,1)$ & $(1,1,0)$ & (mass) & $2$ & --    & $16/5$ & -- \\
$\nu_\tau$ & $(1,1)$ & $(1,1,1)$ & (mass) & $3$ & --    & $25/9$ & -- \\
\midrule
\multicolumn{8}{l}{\textit{Up-type quarks ($T_3 = +1/2$)}} \\
\midrule
Up    & $(1,1)$ & $(1,0,0)$ & (mass) & $1$ & $3/2$  & $6$    & -- \\
Charm & $(1,1)$ & $(1,1,0)$ & (mass) & $2$ & $2/3$  & $2$    & -- \\
Top   & $(1,1)$ & $(1,1,1)$ & (mass) & $3$ & $-1/3$ & $1/28$ & -- \\
\midrule
\multicolumn{8}{l}{\textit{Down-type quarks ($T_3 = -1/2$)}} \\
\midrule
Down    & $(1,1)$ & $(1,0,0)$ & (mass) & $1$ & $3/2$ & $25/2$ & -- \\
Strange & $(1,1)$ & $(1,1,0)$ & (mass) & $2$ & $1$   & $26/9$ & -- \\
Bottom  & $(1,1)$ & $(1,1,1)$ & (mass) & $3$ & $1/2$ & $3/2$  & -- \\
\bottomrule
\end{tabular}}
}
\end{center}

\textbf{Note on the column \enquote{Time w.}:} the temporal winding
number $k_t$ is linked via (210.7a) to the mass energy of the mode:
$E_t = 2\pi k_t c / L_0$. \enquote{(mass)} here means \enquote{set
by the mass energy}; the corresponding value of $k_t$ is not 0 or 1,
but the quantization number of the particle state on the temporal
circle direction -- in the low-energy unrolling this number appears
as the mass $m$ of the particle.

\textbf{How to read this table:}
\begin{itemize}
  \item Column \enquote{Spin}: all fermions carry $(1,1)$ -- the spin
        winding only separates bosons from fermions, not generations.
  \item Columns \enquote{Space wind.} and $n$: identical within a
        generation; they distinguish generations, not particle types
        within a generation.
  \item Column \enquote{Time w.}: carries the mass energy of the mode
        via (210.7a). For \emph{different} particles in the same
        generation (e.g.\ Up vs.\ Down vs.\ Charm vs.\ Strange) the
        spatial winding is the same, but $k_t$ differs -- this is
        how the temporal circle direction distinguishes the masses.
  \item Columns $p_{\text{Yuk}}$ and $r_i$: distinguish all twelve
        fermions from each other; they carry the same information as
        $k_t$, in practical low-energy notation.
  \item Column $p_{g\!-\!2}$: only geometrically well-defined for
        the charged leptons. For quarks, the anomalous magnetic
        moment $g\!-\!2$ is not a direct observable (hadronic
        distribution functions are measured instead); neutrinos
        carry no electromagnetic $g\!-\!2$ contribution.
        \enquote{--} therefore means \enquote{not applicable}, not
        \enquote{open}.
\end{itemize}

\subsection*{Relation to the Yukawa Form}

The Yukawa mass formula $m = r\,\xi^p\,v$ from Doc.~006 is the
\emph{compact} notation; it is equivalent to the direct geometric form
of Doc.~070, where the seemingly simple fractions $r$ are
\emph{structured} expressions:

\begin{equation}
  \frac{4}{3} \;=\; \frac{3\sqrt{3}}{2\pi\,\alpha^{1/2}},
  \qquad
  \frac{16}{5} \;=\; \frac{9}{4\pi\alpha},
  \qquad
  \frac{25}{9} \;=\; \frac{27\sqrt{3}}{8\pi\,\alpha^{3/2}}
  \tag{210.8}
\end{equation}

(Doc.~070 §25.3.1 -- \enquote{numerical fractions must not be reduced
directly}). The table above uses the Yukawa form as a practical
notation; when communicating to readers expected to be familiar with
the underlying geometric structure, reference Doc.~070.

% ============================================================
\section{\texorpdfstring{Precision~W6: Lepton exponents as a geometric sequence}{Precision W6: Lepton exponents as a geometric sequence}}
% ============================================================

\subsection*{Affected Documents}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Doc.~116 (Koide formula) §3 \enquote{Geometric structure of
        the exponents}.
  \item Doc.~158 (Koide-to-g-2) §1, §3.2 \enquote{$1/3$ step size}.
  \item Doc.~203 (R-operator) §3 \enquote{Step size $\Delta p = 1/3$}.
  \item Doc.~202 (Field theory overview) §22.1.
\end{itemize}

\subsection*{Problem}

In several documents the lepton-exponent sequence
$(p_e, p_\mu, p_\tau) = (3/2, 1, 2/3)$ is described as an arithmetic
sequence with constant step size $\Delta p = 1/3 = 1/D$ (three spatial
dimensions). This characterisation is not satisfied arithmetically:
\begin{equation}
  p_e - p_\mu \;=\; \tfrac{3}{2} - 1 \;=\; \tfrac{1}{2},
  \qquad
  p_\mu - p_\tau \;=\; 1 - \tfrac{2}{3} \;=\; \tfrac{1}{3}.
\end{equation}
The steps differ ($1/2$ vs.\ $1/3$); the claim
\enquote{$\Delta p = 1/D$} holds literally only for the
$p_\mu \to p_\tau$ step.

Doc.~158 (g-2 bridge formula) builds the prediction
$\Delta a(\tau{-}e) = (144/125) \cdot (m_\tau/m_\mu) \cdot \Delta a(\mu{-}e)$
on the assumption of a canonical $1/3$ step size. The bridge formula
is numerically correct -- but the justification needs to be reformulated.

\subsection*{Binding Reading}

The lepton exponents form a \textbf{geometric sequence with ratio
$q = 2/3$}:
\begin{equation}
  p_{n+1} \;=\; \tfrac{2}{3}\, p_n,
  \qquad
  \bigl(p_e,\, p_\mu,\, p_\tau\bigr)
  \;=\; \bigl(\tfrac{3}{2},\;1,\;\tfrac{2}{3}\bigr).
  \label{eq:w6-lepton-sequence}
\end{equation}
The ratio $2/3$ is the inverse of the tetrahedral factor $3/2$ of
$\xi_0 = (4/3) \cdot 10^{-4}$ (Doc.~180). The non-constant
differences $1/2$ and $1/3$ are \emph{consequences} of this geometric
sequence:
\begin{equation}
  p_n - p_{n+1} \;=\; p_n \cdot (1 - q) \;=\; p_n \cdot \tfrac{1}{3}.
\end{equation}
Specifically: $p_\mu \cdot 1/3 = 1/3$ (for the $\mu \to \tau$ step),
$p_e \cdot 1/3 = 1/2$ (for the $e \to \mu$ step).

\subsection*{Connection to Koide $Q = 2/3$}

The value $Q = 2/3$ of the Koide relation
\begin{equation}
  Q \;=\; \frac{m_e + m_\mu + m_\tau}{(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2}
  \;=\; \tfrac{2}{3}
\end{equation}
is \emph{numerically identical} to the sequence ratio $q = 2/3$ from
(\ref{eq:w6-lepton-sequence}). This match is not coincidental:
inserting an arithmetic sequence with constant step (e.g.\
$p = 3/2,\,1,\,1/2$ as for the down-type quarks) gives Koide
$Q \approx 0.80$; with the geometric sequence $(3/2,\,1,\,2/3)$ one
obtains $Q = 2/3$. The specific ratio $2/3$ thus appears in two
layers of the theory:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item as ratio $q$ of the lepton-exponent sequence,
  \item as value $Q$ of the Koide symmetry.
\end{itemize}

\subsection*{Consequences for Doc.~158 (g-2 bridge)}

The bridge formula
$\Delta a(\tau{-}e)/\Delta a(\mu{-}e) = (144/125) \cdot m_\tau/m_\mu$
remains numerically valid. The justification is to be reformulated:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item The $1/3$ difference in the $p_\mu \to p_\tau$ step arises
        from $p_\mu \cdot (1 - 2/3) = 1/3$, not from $1/D$.
  \item The factor $144/125$ comes from the ratio
        $(r_\tau/r_\mu)$ of the specific rational prefactors.
  \item The bridge uses only the $\mu \to \tau$ step (which is why
        it works without the full sequence structure).
\end{itemize}

\subsection*{Summary}

The characterisation \enquote{$\Delta p = 1/3 = 1/D$} used in
Doc.~203 §3 and Doc.~158 §1 is to be replaced by the geometric
sequence $p_{n+1} = (2/3)\,p_n$. Statements that build on this
sequence (Koide $Q$, g-2 bridge) remain valid. What is corrected is
the geometric justification: not \enquote{step size $1/D$ from three
spatial dimensions}, but \enquote{geometric ratio $2/3$, inverse of
the tetrahedral factor}.

% ============================================================
\section*{Updated Summary}
% ============================================================

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\footnotesize
\begin{tabular}{>{\raggedright\arraybackslash}p{0.7cm}>{\raggedright\arraybackslash}p{2.7cm}>{\raggedright\arraybackslash}p{5.0cm}>{\raggedright\arraybackslash}p{5.6cm}}
\toprule
\textbf{No.} & \textbf{Doc.} & \textbf{Unclear / ambiguous} & \textbf{Binding} \\
\midrule
W1 & Doc.~060, 018, 149 &
  \enquote{Winding number of a particle} ambiguous &
  $f = 1/(4\xi) = 7500$ is the universal base winding density, not particle-specific \\
W2 & Doc.~051, 202 &
  \enquote{Winding} without specification &
  $(n_\theta, n_\phi)$ encodes only spin; all fermions carry $(1,1)$ \\
W3 & Doc.~018, 149 &
  Generation hierarchy without winding picture &
  Generations = fractal branchings with Hausdorff dim.\ $p_{g\!-\!2} \in \{-, 5/3, 4/3\}$ \\
W4 & Doc.~005, 006, 042, 202 &
  Symbol $(n,l,j)$ in three meanings &
  Wave vector $(k_x,k_y,k_z,k_t)$ on $T^4$ is primary; $(n,l,j)$ is derived via $n = k_x^2+k_y^2+k_z^2$ \\
W5 & Doc.~005, 006, 032 &
  Symbol $f_i$ in three meanings; \enquote{two methods} presented as independent &
  Yukawa form $m=r\,\xi^p\,v$ is canonical; direct form $m = 1/(\xi_0\,f_i)$ identical via bridge formula (210.11) \\
W6 & Doc.~116, 158, 203 &
  Lepton exponents as arithmetic sequence with \enquote{$\Delta p = 1/3 = 1/D$} &
  Geometric sequence $p_{n+1} = (2/3)\,p_n$; ratio $q = 2/3$ identical with Koide $Q = 2/3$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\textbf{Consolidated winding table for all twelve fermions:} see
\S\,\enquote{Consolidated Winding Table of the Twelve Fermions} above.
