% ==============================================================================
% T0/FFGFT Theory: Document 231
% Title: Extensions of the Hilbert-space formalism for full FFGFT
% Author: Johann Pascher
% Date: May 2026
% References: Documents 175 (Qubit state spaces), 174 (Spin qubit), 210 (Windings),
%             202 (Field theory), 230 (Hilbert-space translation)
% ==============================================================================

\section*{Preamble}

Document~230 showed how FFGFT statements can be \emph{translated into
the standard Hilbert space} -- with reductions losing information at
each stage. This document reverses the question:

\begin{quote}
\itshape
\enquote{What additional mathematical structures must be added to
the standard Hilbert space so that it can carry the full FFGFT
geometry \textbf{natively} -- without reduction?}
\end{quote}

The answer has a notable property: each required extension
corresponds to an \emph{established mathematical structure} from
other areas of theoretical physics. FFGFT does not \enquote{invent}
new mathematics; it is the specific combination of established
extensions that delivers all Standard-Model constants
parameter-free.

% ==============================================================================
\section*{Notation}
% ==============================================================================

\subsection*{Geometric spaces and Hilbert spaces}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$\mathbb{R}$ & real numbers \\
$\mathbb{C}$ & complex numbers \\
$\mathbb{C}^2$ & standard qubit Hilbert space \\
$\mathbb{Z}$ & integers (winding index) \\
$\aleph_0$ & countably infinite (Hilbert-space dimension after extension 2) \\
$S^1, S^2$ & circle, 2-sphere \\
$T^n$ & $n$-torus, $n$ compact loops \\
$L^2(M, S)$ & sections of spinor bundle $S$ over manifold $M$ \\
$\mathcal{H}_{\text{std}}$ & standard Hilbert space \\
$\mathcal{H}^{T^n}_{\text{FFGFT}}$ & FFGFT Hilbert space on $T^n$ \\
$\bigoplus_n$ & direct sum over index $n$ \\
$\bigotimes$ & tensor product \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{Algebraic structures}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$SU(2)$ & special unitary group (standard) \\
$SU_q(2)$ & $q$-deformed quantum group (Drinfeld-Jimbo) \\
$q$ & deformation parameter, $q = e^{i\pi(1-K_{\text{frak}})} = e^{i\pi/75}$ \\
$[n]_q$ & $q$-deformed number, $[n]_q = (q^n - q^{-n})/(q - q^{-1})$ \\
$\sigma_x, \sigma_y, \sigma_z$ & Pauli matrices \\
$\sigma_x^{\text{FFGFT}}$ & FFGFT-modified $\sigma_x = K_{\text{frak}} \sigma_x$ \\
$[A, B]$ & commutator $AB - BA$ \\
$\{A, B\}$ & anticommutator $AB + BA$ \\
$\mathbb{1}$ & identity matrix \\
$\delta_{ij}, \epsilon_{ijk}$ & Kronecker delta, Levi-Civita tensor \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{FFGFT geometry parameters}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$\xi_0 = 4/30000$ & dimensionless FFGFT geometry parameter \\
$\xi$ & alternative notation for $\xi_0$ \\
$D_f = 2.999867$ & fractal spacetime dimension \\
$K_{\text{frak}}$ & fractal correction, $K_{\text{frak}} = 1 - 100\xi_0 \approx 0.9867$ \\
$1 - K_{\text{frak}}$ & deformation phase, $\approx 0.0133$ \\
$v$ & Higgs vacuum expectation value, $\approx 246$ GeV \\
$\hbar, c$ & Planck constant, speed of light \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{Winding structure (extensions 2 and 4)}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$n \in \mathbb{Z}$ & cyclic winding quantum number (loop) \\
$|\psi; n\rangle$ & state with winding number $n$ \\
$\mathbb{C}^2_n$ & qubit Hilbert space in $n$-winding sector \\
$E_n$ & energy of $n$-th winding excitation \\
$R$ & loop radius (major radius of torus) \\
$a^\dagger, a$ & creation and annihilation operators for winding excitations \\
$k_t \in \mathbb{Z}$ & temporal winding quantum number \\
$f(k_t)$ & periodic energy function of $k_t$ winding \\
$(n_x, n_y, n_z)$ & spatial winding quantum numbers \\
$(n_\theta, n_\phi)$ & spin winding quantum numbers \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{Fiber bundle operators (extension 3)}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$\vec L$ & orbital angular momentum operator \\
$\vec S$ & spin operator \\
$L_i, S_j$ & components of $\vec L, \vec S$ \\
$H_{\text{SO}}$ & spin-orbit coupling Hamiltonian \\
$\xi(r)$ & radial spin-orbit coupling function \\
$Z$ & atomic number \\
$S$ & spinor bundle over $T^3$ or $T^4$ \\
$\mathcal{D}_{T^4}$ & Dirac-like operator on $T^4$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection*{Standard QM quantities}

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{2.8cm}>{\raggedright\arraybackslash}p{8.2cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
$|\psi\rangle$ & quantum state \\
$|0\rangle, |1\rangle$ & computational basis states \\
$\alpha, \beta$ & complex amplitudes \\
$\psi(x,y,z)$ & position wavefunction \\
$\omega = 2\pi/T$ & angular frequency \\
$E$ & energy \\
$m, m_i$ & mass, mass of fermion $i$ \\
$\alpha$ & fine-structure constant \\
$\nabla^2$ & Laplace operator \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

% ==============================================================================
\section*{The four required extensions}
% ==============================================================================

From Doc.~230 we know: the Hilbert-space translation of a single
qubit takes place on the Bloch sphere ($S^2$), reached through two
reductions from the full FFGFT geometry
($T^4 \to T^3 \to T^2 \to \text{cylinder} \to S^2$). Each reduction
corresponds to the loss of a structural layer. To reconstruct full
FFGFT, we must restore four extensions.

\textbf{Overview:}

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{1.7cm}>{\raggedright\arraybackslash}p{4.0cm}>{\raggedright\arraybackslash}p{4.3cm}}
\toprule
\textbf{Step} & \textbf{Extension} & \textbf{Mathematical model} \\
\midrule
$S^2 \to$ cylinder
  & deformed $SU(2)$ algebra
  & quantum groups $SU_q(2)$ \\[4pt]
cyl.\ $\to T^2$
  & additional cyclic quantum number
  & Kac-Moody algebras, winding states \\[4pt]
$T^2 \to T^3$
  & bundle structure instead of tensor product
  & fiber bundles, Kaluza-Klein \\[4pt]
$T^3 \to T^4$
  & temporal winding dimension
  & Kaluza-Klein, compact extra dimensions \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

% ==============================================================================
\section{Extension 1: deformed $SU(2)$ algebra}
% ==============================================================================

\subsection{Standard Pauli algebra}

The Pauli matrices $\sigma_x, \sigma_y, \sigma_z$ generate the
isotropic $SU(2)$ algebra:
\begin{equation}
  [\sigma_i, \sigma_j] = 2i\epsilon_{ijk}\sigma_k,
  \qquad
  \{\sigma_i, \sigma_j\} = 2\delta_{ij}\mathbb{1}.
\end{equation}
\enquote{Isotropic} means: all three axes $x, y, z$ are on equal
footing; a rotation around $\sigma_x$ is exactly equivalent to a
rotation around $\sigma_z$ after an appropriate basis change.

\subsection{FFGFT anisotropy}

In FFGFT there is a \emph{distinguished prefactor} for the $\sigma_x$
rotation:
\begin{equation}
  \sigma_x^{\text{FFGFT}} = K_{\text{frak}} \cdot \sigma_x,
  \qquad
  K_{\text{frak}} = 1 - 100\xi_0 \approx 0.9867.
\end{equation}
The $\sigma_y$ and $\sigma_z$ rotations are unmodified. Hence the
algebra is no longer isotropic: $\sigma_x$ is distinguished.

\subsection{Mathematical identification: $SU_q(2)$}

The $SU_q(2)$ quantum group (Drinfeld-Jimbo, 1985) is the
$q$-deformation of $SU(2)$, with modified commutation relations.
In the limit $q \to 1$ it becomes standard $SU(2)$. The FFGFT
anisotropy corresponds to the identification:
\begin{equation}
  \boxed{
    q = e^{i\pi(1 - K_{\text{frak}})}
      = e^{i\pi \cdot 100\xi_0}
      = e^{i\pi/75}
      \approx 0.999 + 0.042i.
  }
\end{equation}

The $q$-phase is small ($\pi/75 \approx 0.042$ rad) but
structurally significant: it breaks the spherically symmetric
$SU(2)$ algebra into an anisotropic, axis-distinguished algebra. The
anisotropy is the mathematical memory of the cylinder of its
toroidal origin.

\subsection{What this extension costs}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Hilbert space remains $\mathbb{C}^2$ -- no dimensional
        extension.
  \item Operators remain $2\times 2$ matrices -- no matrix
        extension.
  \item What changes: the structure constants of the algebra
        (Casimir operators, multipliers).
  \item Consequence: all $\pi$-gates deviate systematically by
        $0.013\,\%$ from the ideal value (Doc.~175 §3, testable in
        high-precision quantum gate experiments).
\end{itemize}

% ==============================================================================
\section{Extension 2: cyclic quantum number}
% ==============================================================================

\subsection{What is missing on the cylinder}

The cylinder $\mathbb{R} \times S^1$ has \emph{one} compact loop
(the phase $\theta$) and \emph{one} linear axis ($z$). On the
2-torus $T^2 = S^1 \times S^1$, \emph{both} axes are compact -- so
$z = +1$ and $z = -1$ are connected by a second loop. In the
Bloch-sphere limit (all poles contracted) and even in the cylinder
limit (one loop pulled apart), this connection is lost.

\subsection{Hilbert-space extension}

To represent the second loop, the Hilbert space must carry an
additional \emph{winding quantum number} $n \in \mathbb{Z}$. Instead
of
\begin{equation}
  |\psi\rangle = \alpha|0\rangle + \beta|1\rangle \in \mathbb{C}^2
\end{equation}
the state becomes
\begin{equation}
  |\psi; n\rangle = \alpha|0; n\rangle + \beta|1; n\rangle,
\end{equation}
where $n$ specifies how often the mode configuration wraps around
the second loop of $T^2$. The Hilbert space becomes:
\begin{equation}
  \boxed{
    \mathcal{H}^{T^2}_{\text{FFGFT}}
    = \bigoplus_{n \in \mathbb{Z}} \mathbb{C}^2_n.
  }
\end{equation}
This is a \emph{countably infinite-dimensional} Hilbert space, no
longer 2-dimensional.

\subsection{Low-energy limit: why this is normally invisible}

Higher winding excitations ($n \neq 0$) have higher energy:
\begin{equation}
  E_n \sim n^2 \cdot \frac{\hbar^2}{m R^2},
\end{equation}
where $R$ is the loop radius. At low energies only $n = 0$ is
populated, and the Hilbert space effectively reduces to $\mathbb{C}^2$
-- the standard Bloch sphere. Higher $n$-excitations become
rapidly invisible at macroscopic $R$.

\subsection{Mathematical model}

The structure $\bigoplus_n \mathbb{C}^2_n$ is exactly what appears
in string theory as \emph{winding states of compact dimensions},
and in Kac-Moody algebras as \emph{levels}. Here too the mathematics
is known -- FFGFT imports it with a specific geometric meaning.

\subsection{What this extension costs}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Hilbert-space dimension becomes $\aleph_0$ instead of $2$.
  \item Operators become infinite-dimensional, but block-diagonal:
        within each $n$-sector they are $2\times 2$.
  \item Additional operators $a^\dagger, a$ propagate between
        winding sectors ($n \to n \pm 1$).
  \item Irrelevant at low energies; required in the full theory
        (e.g.\ for vacuum Casimir effects between the poles, Doc.~091/220).
\end{itemize}

% ==============================================================================
\section{Extension 3: bundle structure instead of tensor product}
% ==============================================================================

\subsection{Standard QM for a particle with spin}

A spin-$\tfrac{1}{2}$ particle in space has, in standard QM, the
Hilbert space:
\begin{equation}
  \mathcal{H}_{\text{std}} = L^2(\mathbb{R}^3) \otimes \mathbb{C}^2.
\end{equation}
The \emph{tensor product} means: position space and spin space are
\textbf{independent} Hilbert spaces. Operators on one factor commute
with operators on the other:
\begin{equation}
  [L_i, S_j] = 0
  \qquad \text{(orbital and spin angular momentum commute)}.
\end{equation}
Spin-orbit coupling must be introduced as an \emph{additional
Hamiltonian term}:
\begin{equation}
  H_{\text{SO}} = \xi(r)\, \vec L \cdot \vec S,
\end{equation}
where the \enquote{spin-orbit constant} $\xi(r)$ is a free parameter
(typically $\sim Z^4 \alpha^2$ for a hydrogen-like atom).

\subsection{FFGFT: spin and position on the same $T^3$}

In FFGFT both \enquote{position} and \enquote{spin} arise from
windings on the same 3-torus $T^3$ (Doc.~210):
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item spatial windings $(n_x, n_y, n_z)$: mode-space position,
  \item spin windings $(n_\theta, n_\phi)$: 3-1 spin index.
\end{itemize}
Both sets of winding numbers live on the same compact manifold.
They are not independent.

\subsection{Hilbert space as spinor bundle}

Mathematically the FFGFT Hilbert space for a particle with spin on
$T^3$ is \emph{not} a tensor product, but the space of sections of a
spinor bundle:
\begin{equation}
  \boxed{
    \mathcal{H}^{T^3}_{\text{FFGFT}}
    = L^2(T^3, S),
  }
\end{equation}
where $S$ is the spinor bundle over $T^3$. In this structure orbital
and spin operators are \emph{no longer independent}:
\begin{equation}
  [L_i, S_j] \neq 0
  \qquad \text{with corrections} \sim \xi.
\end{equation}

\subsection{Consequence: geometric spin-orbit coupling}

Spin-orbit coupling in FFGFT is \emph{not} an additional Hamiltonian
term, but a \textbf{geometric property of the bundle}. The
\enquote{spin-orbit constant} $\xi(r)$ is not a free parameter, but
follows from the winding geometry. In particular: the behaviour
$\xi(r) \propto Z^4 \alpha^2$ in heavy atoms follows from the
specific winding topology (Doc.~174).

\subsection{Mathematical model}

The bundle structure is standard differential geometry -- every
modern differential geometry textbook treats spinor bundles. The
specific FFGFT step is the geometric identification:
\enquote{spin and position are not two Hilbert spaces, but two
aspects of the same winding structure on a compact manifold.}

\subsection{What this extension costs}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Hilbert space is \emph{no longer} a tensor product -- the
        algebraic structure differs.
  \item Pauli principle becomes geometric: two fermions cannot
        occupy the same winding state because the bundle geometry
        forbids it (Doc.~174 §3).
  \item Angular momentum algebra is intertwined with translation
        algebra.
  \item Consequence: all phenomenological \enquote{spin-orbit
        constants} of atomic physics are derivable from FFGFT -- they
        are not free.
\end{itemize}

% ==============================================================================
\section{\texorpdfstring{Extension 4: temporal winding $k_t$}{Extension 4: temporal winding k_t}}
% ==============================================================================

\subsection{What standard QM does with time}

In standard QM, time is a \emph{continuous, linear} axis $\mathbb{R}$.
The Schrödinger equation:
\begin{equation}
  i\hbar \frac{\partial \psi}{\partial t} = H \psi,
  \qquad
  E = \hbar \omega
  \qquad \text{(standard dispersion)}.
\end{equation}
Energy is linear in the frequency $\omega = 2\pi/T$.

\subsection{FFGFT: time on $S^1$}

In FFGFT, time is a \emph{compact} winding direction with quantum
number $k_t \in \mathbb{Z}$ (Doc.~210). The energy becomes:
\begin{equation}
  \boxed{
    E = \hbar f(k_t),
  }
\end{equation}
where $f$ is a periodic function. In the lowest winding sector this
reduces to $E \approx \hbar \omega$, but the winding structure is
real and carries physical meaning.

\subsection{Mass from winding}

The central FFGFT statement: \textbf{the mass of a mode is the
$k_t$-winding energy}:
\begin{equation}
  m_i c^2 = \hbar f(k_t^{(i)})
  \qquad \text{for mode $i$}.
\end{equation}
Combined with the Yukawa form (Doc.~006):
\begin{equation}
  m_i = r_i \cdot \xi_0^{p_i} \cdot v,
\end{equation}
all 12 Standard-Model fermion masses follow from the tuples
$(n_x, n_y, n_z, k_t^{(i)})$ without free parameters.

\subsection{Hilbert-space extension}

Instead of $\mathcal{H} = L^2(\mathbb{R}^3) \otimes \mathbb{C}^2$ and
time as a continuous parameter, the full FFGFT Hilbert space becomes:
\begin{equation}
  \mathcal{H}^{T^4}_{\text{FFGFT}} = L^2(T^4, S),
\end{equation}
with sections of a spinor bundle over the 4-torus. The Schrödinger
equation becomes a \emph{mode equation} on $T^4$:
\begin{equation}
  i\hbar \frac{\partial \varphi_{n,l,j}}{\partial t}
  = \mathcal{D}_{T^4} \varphi_{n,l,j},
\end{equation}
where $\mathcal{D}_{T^4}$ is a Dirac-like operator on the 4-torus.
At low energies this reduces to the standard Schrödinger equation
with fixed mass.

\subsection{Mathematical model}

Compact extra dimensions have been an established framework since
Kaluza (1921) and Klein (1926). FFGFT uses this structure with two
modifications:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item The extra dimension is \emph{temporal}, not spatial.
  \item The winding quantum number $k_t$ is not free, but fixed by
        geometry and Higgs matching.
\end{itemize}

\subsection{What this extension costs}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item The Schrödinger equation itself is modified.
  \item Masses are no longer external parameters.
  \item The standard QFT construction (Lagrangian densities with
        Yukawa terms) is a \emph{low-energy approximation} of the
        full FFGFT mode theory.
  \item Consequence: all 12 fermion masses, the fine-structure
        constant, and the Higgs self-coupling follow parameter-free
        from the 4D winding geometry.
\end{itemize}

% ==============================================================================
\section{The structural point: known mathematics, new combination}
% ==============================================================================

Each of the four extensions corresponds to a mathematically
\emph{well-established} structure:

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{1.0cm}>{\raggedright\arraybackslash}p{3.5cm}>{\raggedright\arraybackslash}p{5.5cm}}
\toprule
\textbf{Ext.} & \textbf{Mathematics} & \textbf{Established since} \\
\midrule
1 & quantum groups $SU_q(2)$ & Drinfeld/Jimbo 1985 \\
2 & winding excitations & string theory, Kac-Moody (1980s) \\
3 & spinor bundles & differential geometry 1950s \\
4 & compact extra dimension & Kaluza 1921, Klein 1926 \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

None of these structures is new. What makes FFGFT \emph{specific} is
the \textbf{combination}: all four extensions together, with a
single geometric justification.

\textbf{What no other theory does:}
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Quantum groups are studied in mathematics, but not motivated
        by geometry from a spacetime dimension.
  \item String theory has winding excitations, but requires 10 or
        11 dimensions and does not deliver Standard-Model masses
        parameter-free.
  \item Spinor bundles are standard geometry, but typical QFT
        applications take spin and position as a tensor product.
  \item Kaluza-Klein theories exist in numerous variants, but none
        delivers all 12 SM masses from a single compact dimension.
\end{itemize}

FFGFT is the \emph{convergence} of these four extensions with a
common geometric source ($T^4$ and $\xi_0$).

% ==============================================================================
\section{What a Hilbert-space-extended formulation achieves}
% ==============================================================================

If one equips the standard Hilbert space with all four extensions, one
obtains a complete FFGFT-equivalent formulation accessible to
mathematicians and QM practitioners:

\begin{equation}
  \mathcal{H}^{\text{FFGFT}}
  = L^2(T^4, S) \;\bigotimes\; \text{(deformed $SU_q(2)$ algebra)},
\end{equation}
with an additional winding quantum number $n$ per spin rotational
degree of freedom and a modified mode equation
$\mathcal{D}_{T^4}\varphi = E \varphi$ instead of the Schrödinger
equation.

In this formulation all FFGFT predictions are derivable directly
from the Hilbert-space algebra:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item masses from the $k_t$ windings,
  \item fine-structure constant from the $SU_q(2)$ Casimir,
  \item spin-orbit coupling from the bundle structure,
  \item $K_{\text{frak}}$ corrections from the quantum-group
        deformation,
  \item Casimir effect and cosmological energy loss from the winding
        vacuum structures.
\end{itemize}

\textbf{Methodological consequence:} FFGFT can be \emph{fully
formulated in Hilbert-space language}, provided one accepts the four
extensions. Those wishing to extend the standard Hilbert space
minimally can begin with stage 1 ($SU_q(2)$), then stage 2 (winding
quantum number), and so on -- each stage brings a further class of
FFGFT statements into the Hilbert-space vocabulary.

% ==============================================================================
\section{Summary}
% ==============================================================================

The standard Hilbert space ($\mathbb{C}^2$ per qubit, $L^2(\mathbb{R}^3)$
per particle, tensor product for composite systems) must be supplemented
by \textbf{four extensions} to capture full FFGFT:

\begin{enumerate}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item \textbf{Deformed algebra} $SU_q(2)$ with
        $q = e^{i\pi(1-K_{\text{frak}})}$.
  \item \textbf{Cyclic winding quantum number} $n \in \mathbb{Z}$ for
        each compact dimension; Hilbert space becomes
        $\bigoplus_n \mathbb{C}^2_n$.
  \item \textbf{Bundle structure} instead of tensor product between
        position and spin: $L^2(T^3, S)$ with coupled operators.
  \item \textbf{Temporal winding dimension} $k_t$ with energy
        $E = \hbar f(k_t)$ instead of $E = \hbar\omega$; masses from
        $k_t$ windings.
\end{enumerate}

Each extension corresponds to an established mathematical structure
(quantum groups, string-theory windings, differential geometry,
Kaluza-Klein). FFGFT is the specific, geometrically motivated
combination of these four structures, delivering all
Standard-Model constants parameter-free.

\textbf{Methodological position:}
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item FFGFT \emph{integrates} into the Hilbert-space formalism,
        provided it is appropriately extended.
  \item The extensions are \emph{not ad hoc}, but follow from the
        specific geometric structure of $T^4$.
  \item Mathematicians and QM practitioners can adopt FFGFT
        \emph{stage by stage} -- each extension turns one further
        class of previously external parameters into derivable
        quantities.
\end{itemize}

\textbf{Connection to Doc.~230:} while Doc.~230 described the
\enquote{downward translation} (FFGFT into the standard Hilbert
space, with reductions), this document formulates the
\enquote{upward translation} (Hilbert-space extensions, to carry
FFGFT natively). Both directions are necessary to fully understand
the structural connection.
