% ==============================================================================
% 251_FFGFT_Vopson_Vergleich_En_ch.tex
% FFGFT and Vopson's Computational Universe -- Parallels and Differences
% Author: Johann Pascher · May 2026
% ==============================================================================

\section*{Abstract}

This document compares FFGFT (Fundamental Fractal Geometric Field Theory,
T0 Time-Mass Duality) with Vopson's Computational Universe hypothesis and
Second Law of Infodynamics. Both approaches start from different primitives ---
FFGFT from 4D torus geometry~$T^4$, Vopson from Shannon's information theory
and Landauer's principle --- and arrive at structurally very similar conclusions.
The agreements are numerous and substantial; the essential difference lies in
the direction of derivation and in a structural disagreement about whether an
outside perspective on the system is possible.

\tableofcontents
\newpage

% ------------------------------------------------------------------------------
\section{Introduction: Two Paths to the Same Destination}

Melvin Vopson has been developing the \emph{Computational Universe} hypothesis
and the \emph{Second Law of Infodynamics}: information is a physical quantity,
information entropy stays the same or decreases, and gravity and symmetry can
be derived from information-theoretic minimisation principles
\cite{Vopson2022,Vopson2023,Vopson2024}.

FFGFT begins at a different point: the conviction that no fundamental
contradiction can exist between quantum mechanics and relativity, because both
work too well. The search for the common geometric structure led to the 4D
identification torus~$T^4$ with the single dimensionless parameter
$\xipar = 4/3 \times 10^{-4}$ and the foundational relation $\tilde{T} \cdot m = 1$.

As the following analysis shows, the conclusions of both approaches are
structurally identical in central respects. This is not coincidence: two
independent paths arriving at the same place suggest that something is there.

% ------------------------------------------------------------------------------
\section{Parallel 1: The Minimisation Principle}

\subsection{Vopson's Second Law of Infodynamics}

Vopson formulates: the information entropy in a closed system stays the same
or decreases over time. This stands in contrast to the second law of
thermodynamics (physical entropy increases). Empirical evidence: virus
mutations reduce genome entropy; atoms occupy orbitals with lowest information
entropy (Hund's rules) \cite{Vopson2023}.

\subsection{FFGFT: Resonant Stability as Geometric Minimisation}

In FFGFT, only winding configurations with integer winding numbers
$(n_\theta, n_\varphi, n_3, n_4)$ are stable --- closed trajectories on~$T^4$
resonate, open ones decay. The $\xipar$-recursion ladder selects stable levels:
only configurations satisfying the geometric resonance condition persist.

This is a geometric minimisation principle: the universe tends toward
configurations that are topologically sustainable. Vopson calls this
information entropy minimisation. FFGFT calls it resonant stability. The
outcome is the same.

\begin{erkenntnis}
Vopson's Second Law of Infodynamics and FFGFT's resonant stability on~$T^4$
describe the same structural preference: the system tends toward the
geometrically/information-theoretically minimal stable configurations.
\end{erkenntnis}

% ------------------------------------------------------------------------------
\section{Parallel 2: Symmetry as Emergent Parsimony}

\subsection{Vopson}

Symmetric structures contain less information and ``save computational power''.
This explains why the universe prefers symmetry over asymmetry \cite{Vopson2024}.

\subsection{FFGFT}

Symmetric configurations on~$T^4$ correspond to closed winding trajectories ---
they minimise the geometric action and are stable fixed points of the
$\xipar$-recursion. Asymmetric configurations are either metastable or unstable.

Both conclusions: symmetry is not a coincidence but a structural preference of
the underlying system.

% ------------------------------------------------------------------------------
\section{Parallel 3: Gravity as an Emergent Phenomenon}

\subsection{Vopson}

Vopson derives Newton's law of gravity from infodynamics: objects attract each
other to minimise their shared information footprint. The universe is
computationally more efficient with few large objects than with billions of
individual particles \cite{Vopson2022}.

\subsection{FFGFT}

FFGFT derives gravity from $\tilde{T} \cdot m = 1$: the T-field couples mass
to the local time structure, producing gravitational effects without a separate
graviton or geometrically separately introduced curvature. The gravitational
potential follows from the T-field geometry on~$T^4$.

Two independent derivations, the same empirical law. That is the kind of
convergence that is significant.

% ------------------------------------------------------------------------------
\section{Parallel 4: A Non-Directly Observable Field Explains Dark Matter Effects}

\subsection{Vopson}

Dark matter is the stored information of the universe --- the actual
``program code'' of reality. Not directly observable as matter, but
gravitationally active and structure-bearing \cite{Vopson2024}.

\subsection{FFGFT}

The T-field in FFGFT: not directly observable as matter, permeates all of
space, influences gravitational dynamics via $\tilde{T} \cdot m = 1$, carries
topological information through winding configurations. FFGFT does not need
a separate dark matter substance because the T-field already accounts for the
observed effects.

Whether one calls this ``stored information'' (Vopson) or ``T-field from
$T^4$ geometry'' (FFGFT) --- the functional description is the same.

\begin{erkenntnis}
Vopson's ``dark matter as information'' and FFGFT's T-field fulfil
structurally the same role: a non-directly-observable field that explains
gravity and structure.
\end{erkenntnis}

% ------------------------------------------------------------------------------
\section{Parallel 5: Information and Consciousness as Conserved Quantities}

\subsection{Vopson}

Through the conservation laws of physics (energy and information cannot be
destroyed), Vopson concludes that consciousness --- or the information of a
living being --- persists in some form after physical death \cite{Vopson2024}.

\subsection{FFGFT}

Topological invariants (winding numbers) are structurally preserved in FFGFT ---
even in extreme configurations such as black holes. The topological fundamental
information (``Grundinformation'' in the sense of Dok.~250) is not lost; it
may become inaccessible to an external observer (access problem), but it
continues to exist geometrically.

The conclusion is the same: information does not disappear.

% ------------------------------------------------------------------------------
\section{Parallel 6: Information Capacity of the Universe}

\subsection{Vopson's Bit Count}

Vopson calculates the total information of the observable universe from the
number of elementary particles (~$10^{80}$) times bits per particle.
Result: ~$10^{80}$ to $10^{90}$ bits (depending on the paper) \cite{Vopson2023}.
These are the actually \emph{occupied} bits.

\subsection{FFGFT: Maximum Geometric Capacity}

In FFGFT there is a natural upper bound via $L_0$:

\begin{align}
  L_0 &= \xipar \cdot \ell_P \approx 2.2 \times 10^{-39}\,\text{m} \\
  N_\text{max}^\text{(3D)} &= \frac{V_\text{universe}}{L_0^3}
    \approx \frac{4 \times 10^{80}\,\text{m}^3}{(2.2 \times 10^{-39})^3\,\text{m}^3}
    \approx 10^{195}\,\text{bits} \\
  N_\text{max}^\text{(4D)} &= \frac{V_{4D}}{L_0^4}
    \approx 10^{260}\,\text{bits}
\end{align}

\begin{longtable}{lll}
\toprule
Quantity & Value & Meaning \\
\midrule
Vopson (occupied bits) & $10^{80}$--$10^{90}$ & Actually occupied information \\
FFGFT (max.\ capacity 3D) & $\sim 10^{195}$ & Geometric upper bound \\
FFGFT (max.\ capacity 4D) & $\sim 10^{260}$ & T⁴ capacity \\
Fill rate (3D) & $\sim 10^{-115}$ & Universe is almost empty \\
\bottomrule
\end{longtable}

No contradiction: Vopson counts the \emph{contents}, FFGFT gives the
\emph{container size}. The universe uses a vanishingly small fraction of its
geometric information capacity --- consistent with the observed cosmic void.

% ------------------------------------------------------------------------------
\section{The Starting Point: Reversed Direction}

The most important difference is not the result but the direction:

\begin{longtable}{>{\bfseries}p{3cm} p{5cm} p{5cm}}
\toprule
 & Vopson & FFGFT \\
\midrule
Primitive & Shannon information (physical) & $T^4$ geometry + $\xipar$ \\
Direction & Information $\rightarrow$ geometry emerges & Geometry $\rightarrow$ information is projection \\
Starting point & Landauer principle, Shannon & QM/RT unification, music theory \\
Gravity & From information minimisation & From $\tilde{T} \cdot m = 1$ \\
Dark matter & Stored information & T-field from $T^4$ \\
\bottomrule
\end{longtable}

Both arrive at structurally very similar places because they describe a common
deeper reality --- approached from different sides.

This matches the pattern of other converging approaches in the history of
science: Maxwell and Faraday arrived at electrodynamics from different sides;
Heisenberg and Schrödinger developed equivalent formulations of quantum
mechanics. The convergence itself is a signal.

% ------------------------------------------------------------------------------
\section{The Dissent: Is There an Outside?}

\subsection{Vopson's Position}

If one discovered and understood the code of reality, one could theoretically
``hack'' it --- teleportation, overcoming the speed of light, ``godlike powers''
\cite{Vopson2024}. The simulation hypothesis leaves an outside open: the
universe might be running on something else.

\subsection{FFGFT: Structural Exclusion}

In FFGFT there is no outside to~$T^4$. Every attempt to ``hack'' the code is
itself a process within~$T^4$. This is not a practical limitation --- it is a
geometric one. The analogy to Gödel's incompleteness theorem (Dok.~248, §9.4)
is direct: a system cannot prove its own completeness from its own axioms, and
there is no standpoint outside the system from which to fully describe it.

Questions like ``What lies before~$T^4$?'' or ``Who chose~$\xipar$?'' are not
well-formed in FFGFT --- not because they have not yet been answered, but
because they presuppose an outside perspective that structurally does not exist
(cf.\ Dok.~248, §9).

\begin{wichtig}
The simulation hypothesis presupposes that an ``outside'' exists from which
the universe is simulated. FFGFT structurally excludes this: $T^4$ is not
embedded in a larger space. ``What lies outside?'' is not an answerable
question --- analogous to ``What lies north of the North Pole?''
\end{wichtig}

% ------------------------------------------------------------------------------
\section{Torus Resonances as Consciousness Selection Mechanism}

A further point of contact: Vopson sees the universe as an information-processing
system; consciousness is part of it. In FFGFT, torus resonances are already a
built-in selection mechanism:

\begin{itemize}
  \item Only integer winding numbers are stable --- resonant configurations
    persist, non-resonant ones decay.
  \item This is a geometric selection mechanism operating at all scales ---
    from elementary particles to complex systems.
  \item Consciousness emerges in FFGFT terms from the recursive feedback loop
    (sensor → memory → movement correlation) that builds on the same
    topological basis.
\end{itemize}

Rudimentary forms of this self-referentiality exist already in simple
$T^4$ configurations --- analogous to Vopson's view that information is
inherent in every physical structure.

% ------------------------------------------------------------------------------
\section*{Summary}

\begin{longtable}{>{\bfseries}p{5cm} p{4.5cm} p{4.5cm}}
\toprule
Aspect & Vopson & FFGFT \\
\midrule
Primitive & Information (physical) & $T^4$ geometry + $\xipar$ \\
Minimisation principle & 2nd Law of Infodynamics & $\xipar$-resonant stability \\
Symmetry & Information-minimal & Geometrically minimal \\
Gravity & From information minimisation & From $\tilde{T} \cdot m = 1$ \\
Dark matter & Stored information & T-field \\
Information conservation & Yes & Yes (topological invariants) \\
Consciousness & Information preserved & Topological charge preserved \\
Universe bits & $10^{80}$--$10^{90}$ (occupied) & $10^{195}$ (max.\ capacity) \\
Outside perspective & Open (simulation possible) & Structurally excluded \\
Hackability & Theoretically possible & No --- no outside \\
\bottomrule
\end{longtable}
