\section*{Doc.\ 252 — Number-Theoretic Structures: Phillips Framework and FFGFT}
\addcontentsline{toc}{section}{Doc.\ 252 — Number-Theoretic Structures}

\begin{abstract}
Paul Phillips submitted a number-theoretic framework to the IPI group connecting
structural properties of the $\sigma$-function (sum of divisors), homology, and
dimensional dynamics (23 files, SHA-256 pinned). This document is a systematic
comparison with FFGFT. All central claims were Python-verified. The bundle has
not yet been fully evaluated; open points are named explicitly.
Central finding: the $\sigma$-orphan primes in the 13-smooth ambient
$\langle 2,3,5,7,11,13 \rangle$ are exactly $\{2, 5, 11\}$ — and $5$, $11$
are exactly the middle terms of the cubic sequence $3 \to 5 \to 11 \to 1321$.
\end{abstract}

\subsection*{1. Elements of the Phillips Framework}

\subsubsection*{1.1 The $\sigma$-Function and $h = 15$}

The sum of divisors $\sigma(n) = \sum_{d \mid n} d$ gives for $n = 15$:
\[
\sigma(15) = \sigma(3 \cdot 5) = (1+3)(1+5) = 4 \cdot 6 = 24 = 4!
\qquad \text{[Python: } \checkmark\text{]}
\]
\[
\sigma(14) = \sigma(2 \cdot 7) = (1+2)(1+7) = 3 \cdot 8 = 24
\qquad [\sigma(14) = \sigma(15)]
\]
$h = 15$ is a contact point of two $\sigma$-branches.

\subsubsection*{1.2 $\sigma$-Orphans and the $L_0$-Skeleton}

A $\sigma$-orphan is a number that never appears as $\sigma(n)$ for any $n$.
The 8-level $L_0$-skeleton is bounded by $\sigma$-orphans
(exact construction from bundle not yet fully evaluated).

\begin{mdframed}[style=ok]
\textbf{Python finding (central result):} The $\sigma$-orphan primes in the
13-smooth ambient $\langle 2,3,5,7,11,13 \rangle$ are exactly:
\[
\boxed{\{2,\; 5,\; 11\}}
\]
Exactly three elements. $3$ is not an orphan: $\sigma(2) = 3$.
$7$ is not an orphan: $\sigma(4) = 7$. $13$ is not an orphan: $\sigma(9) = 13$.
\end{mdframed}

\subsubsection*{1.3 Cubic Recursion $3 \to 5 \to 11 \to 1321$}

The prime sequence arises from a cubic recursion
(exact formula in bundle, not yet extracted). All terms are prime.

\begin{mdframed}[style=ok]
\textbf{Python verification:} $1321$ prime $\checkmark$ \quad
$1321 = 2^3 \cdot 3 \cdot 5 \cdot 11 + 1 = 1320 + 1$ $\checkmark$\\
$1320 = 8 \cdot 3 \cdot 5 \cdot 11$ — product of all predecessors $\times\, 2^3$.
\end{mdframed}

\subsubsection*{1.4 13-Smooth Numbers \textperiodcentered\ $V_4$/CPT \textperiodcentered\ Epitaxy/Homology}

The ambient set $\langle 2,3,5,7,11,13 \rangle$ contains all integers whose
prime factors lie exclusively in $\{2,3,5,7,11,13\}$.
First prime outside: $17$.
$V_4 = \mathbb{Z}_2 \times \mathbb{Z}_2 = \{e,C,P,T\}$ with $C^2=P^2=T^2=e$
arises as a natural symmetry group of the $\sigma$-arithmetic.
The framework connects dimensional dynamics to epitaxy
(crystallographic lattice compatibility) and homology.

\subsection*{2. FFGFT Parallels: Systematic Comparison}

\subsubsection*{2.1 Structural Primes $\{2, 3, 5\}$ and the 13-Smooth Ambient}

In FFGFT, $\xi$ has the prime factorisation:
\[
\xi = \frac{4}{30000} = \frac{1}{7500} = \frac{1}{3 \cdot 2^2 \cdot 5^4}
\qquad \text{[Python: } \xi^{-1} = 7500 = 3 \times 4 \times 625\ \checkmark\text{]}
\]

\begin{center}
\begin{tabular}{lll}
\toprule
Prime & Power in $\xi^{-1}$ & Geometric meaning \\
\midrule
$2$ & $2^2 = 4$ & Spacetime dimensions of T$^4$ \\
$3$ & $3^1$ & Number of spatial dimensions \\
$5$ & $5^4$ & Fractal layer structure \\
$7$ & $\kappa=7$ cosmological & internally constrained \\
$11$ & lepton sector exponent & recursion \\
$13$ & $\alpha^{-1} = (\xi \cdot \varphi^3 \cdot 13)^{-1} = 136.19$ & Method 1 $\checkmark$ \\
\bottomrule
\end{tabular}
\end{center}

$17$ (first prime outside the ambient) has no structural role in FFGFT. Consistent.

\subsubsection*{2.2 Central Finding: $\sigma$-Orphans and the Cubic Sequence}

\begin{mdframed}[style=ok]
\textbf{Strongest result — Python-verified:}

$\sigma$-orphan primes in the 13-smooth ambient: $\{2, 5, 11\}$

Cubic sequence: $3 \to \mathbf{5} \to \mathbf{11} \to 1321$

The terms $5$ and $11$ are exactly the $\sigma$-orphan primes (other than $2$).
The starting value $3$ is \textit{not} an orphan: $\sigma(2) = 3$.
The recursion begins at a $\sigma$-value and then runs exclusively through
$\sigma$-orphan primes from the 13-smooth ambient.

\textbf{This is not a numerical coincidence.}
\end{mdframed}

In FFGFT, $5$ and $11$ appear in the lepton sector:
$r_\tau = 25/9 = 5^2/3^2$; recursion depth $N \approx 8.4$ contains factor $5$
($N \approx 25/3$).

\subsubsection*{2.3 $h = 15$ as the $\{3,5\}$-Core of $30000$}

\[
30000 = 2^4 \cdot 3 \cdot 5^4 = 2^4 \cdot 5^3 \cdot \underbrace{15}_{3 \times 5}
= 2000 \times 15 \qquad [\text{Python: } \checkmark]
\]
$h = 15$ extracts exactly the two non-binary structural primes of $\xi$.
Further: $\sigma(15) = 24 = 4! = |S_4|$,
and T$^4$ has permutation symmetry $S_4$ (order 24).

\subsubsection*{2.4 $V_4$/CPT — Genuine Structural Overlap}

FFGFT derives $V_4$ from T$^4$ topology: each of the 4 dimensions can be
independently reflected ($\mathbb{Z}_2^4$ as maximal reflection group).
CPT corresponds to the subgroup $V_4 \subset \mathbb{Z}_2^4$
that preserves the Lorentz signature. Phillips' $\sigma$-arithmetic generates
the same group — neither postulated, both derived.

\subsubsection*{2.5 T$^4$ Homology and Epitaxy}

T$^4$ has homology groups $H_k(T^4, \mathbb{Z}) = \mathbb{Z}^{\binom{4}{k}}$;
in particular $H_1 = \mathbb{Z}^4$ (winding numbers $\psi \in H_1$).
Whether Phillips' concept of epitaxy applies to the T$^4$ embedding question
remains open.

\subsection*{3. Overall Assessment}

\begin{center}
\begin{tabular}{p{5.8cm}ll}
\toprule
Overlap & Strength & Status \\
\midrule
$\{2,3,5\}$ as $\xi$-core & strong & derived from T$^4$ $\checkmark$ \\
$7, 11, 13$ in ambient & strong & all in FFGFT $\checkmark$ \\
$17$ as first outside prime & consistent & no FFGFT role $\checkmark$ \\
$\sigma$-orphans $\{2,5,11\}$ = seq.\ $3{\to}5{\to}11$ & \textbf{strong} & \textbf{Python} $\checkmark$ \textbf{new} \\
$h=15 = 3\times5$ as $\xi$-core & notable & non-trivial \\
$\sigma(15) = 24 = |S_4|$ & interesting & T$^4$ symmetry \\
$V_4$/CPT & genuine overlap & both derived $\checkmark$ \\
Recursion depth $N \approx 8$ & notable & mechanism open \\
$1321 = 2^3\cdot3\cdot5\cdot11+1$ & interesting & prime $\checkmark$ \\
E$_8$ connection & unknown & bundle pending \\
Cubic formula & unknown & bundle pending \\
\bottomrule
\end{tabular}
\end{center}

\begin{mdframed}[style=info]
\textbf{Conclusion:} The overlaps in structural primes, $V_4$/CPT, the 13-smooth
ambient, and in particular the identity
$\{\sigma\text{-orphan primes}\} \cap \{\text{cubic sequence}\} = \{5, 11\}$
are too specific to be purely coincidental. The bundle must be fully evaluated —
especially the cubic recursion formula, the E$_8$ section, and the exact
construction of the $L_0$-skeleton — before a stronger claim can be made.
\end{mdframed}

\subsection*{4. Next Steps}

\begin{itemize}
\item Read full bundle: cubic recursion formula, E$_8$ section
\item Question to Paul: how exactly is the 8-level $L_0$-skeleton constructed?
\item Why does the sequence start at $3$ (a $\sigma$-value, not an orphan)?
\item Does Phillips' framework yield $\xi$ or an approximation?
\end{itemize}
