\section*{Doc.\ 253 — \texorpdfstring{$\xi$}{xi} and Number-Space Dependence in Factorisation}
\addcontentsline{toc}{section}{Doc.\ 253 — xi and Number-Space Dependence}

\begin{abstract}
Working document. Purpose: preservation of results from an extended investigation
without breakthrough. The question investigated was whether the FFGFT parameter
$\xi = 4/30000$ exhibits number-space dependence in the factorisation of composite
integers, and whether this dependence follows an FFGFT-type step hierarchy.
All calculations were verified with Python. The connection to FFGFT remains
a conjecture without an algebraic bridge proof.
\end{abstract}

\subsection*{1. Background and Motivation}

During work on a T0/FFGFT-based factorisation approach (Python scripts and
HTML test programs, 2024--2026), the following was observed: the effectiveness
of a global $\xi$-parameter in period-finding (Shor's algorithm) does not
appear constant, but depends on the number space. At the same time, rounding
errors and computational precision limits enter the results indirectly.

This gave rise to two questions:

\begin{enumerate}
\item Is there a genuine number-space dependence of $\xi$ in factorisation?
\item Does this dependence follow an FFGFT-type step hierarchy?
\end{enumerate}

\begin{mdframed}[style=warn]
\textbf{Status after extended work without breakthrough:} Both questions are
neither proved nor disproved. The calculations below provide the established facts.
\end{mdframed}

\subsection*{2. The Algebraically Correct Quantity: $\xi_\text{num}(N)$}

The HTML file \texttt{t0\_xi\_num\_algebraisch.html} correctly defined the
relevant quantity:
\[
\xi_\text{num}(N) = \frac{\lambda(N)}{N}
\]
where $\lambda(N) = \text{lcm}(p-1,\, q-1)$ is the Carmichael function for
$N = p \cdot q$. This quantity is dimensionless and basis-independent.

Analytical approximation for large primes $p$, $q$:
\[
\xi_\text{num}(N) = \frac{\text{lcm}(p-1,\, q-1)}{p \cdot q}
\;\approx\; \frac{1}{2 \cdot \gcd(p-1,\, q-1)}
\]

\begin{mdframed}[style=ok]
\textbf{Key finding} (from \texttt{t0\_primzahl\_periodizitaet.html},
Python-confirmed): The period structure of $N$ is determined entirely by
$\gcd(p-1, q-1)$. This is a property of the primes themselves —
not of a global parameter.
\end{mdframed}

\subsection*{3. Python Verification: $\xi_\text{num}$ Tables}

\subsubsection*{3.1 Concrete Semiprimes}

\begin{center}
\begin{tabular}{rrrrrrl}
\toprule
$N$ & $p$ & $q$ & $\gcd(p{-}1,q{-}1)$ & $\lambda(N)$ & $\xi_\text{num}$ & Type \\
\midrule
15    & 3   & 5   & 2 & 4    & 0.2667 & Shor classic \\
35    & 5   & 7   & 2 & 12   & 0.3429 & \\
143   & 11  & 13  & 2 & 60   & 0.4196 & twin primes \\
65    & 5   & 13  & 4 & 12   & 0.1846 & $\gcd = 4$ \\
301   & 7   & 43  & 6 & 42   & 0.1395 & $\gcd = 6$ \\
77    & 7   & 11  & 2 & 30   & 0.3896 & $\gcd = 2$ \\
4087  & 61  & 67  & 6 & 660  & 0.1615 & twin ${\sim}60$ \\
9797  & 97  & 101 & 4 & 2400 & 0.2450 & smooth $p{-}1$ \\
10403 & 101 & 103 & 2 & 5100 & 0.4902 & twin ${\sim}100$ \\
291   & 3   & 97  & 2 & 96   & 0.3299 & very unequal \\
\bottomrule
\end{tabular}
\end{center}

\begin{mdframed}[style=warn]
$\xi_\text{num}$ lies in the range $[0.14,\; 0.49]$. \\
$\xi_\text{FFGFT} = 1.333 \times 10^{-4}$ lies far outside this range.
\end{mdframed}

\subsubsection*{3.2 Dependence on $\gcd(p-1, q-1)$}

\begin{center}
\begin{tabular}{rlll}
\toprule
$\gcd$ & $\xi_\text{num}$ (analytical) & Factorisability & Example \\
\midrule
2  & ${\approx}\,0.25$  & hard (RSA class)   & twin primes \\
4  & ${\approx}\,0.125$ & moderate           & $p \equiv 1, q \equiv 1 \pmod{4}$ \\
6  & ${\approx}\,0.083$ & easier             & $p \equiv 1, q \equiv 1 \pmod{6}$ \\
12 & ${\approx}\,0.042$ & easy               & smooth $p{-}1$, $q{-}1$ \\
30 & ${\approx}\,0.017$ & very easy          & $B$-smooth primes \\
60 & ${\approx}\,0.008$ & trivial            & highly smooth primes \\
\bottomrule
\end{tabular}
\end{center}

The number-space dependence is real — but it is classical number theory.
Pollard's $p$-method and Lenstra's ECM exploit precisely this $\gcd$-structure.
It is not an FFGFT-specific phenomenon.

\subsection*{4. What the HTML Tests Established}

The following HTML test programs were developed:
\texttt{t0\_shor\_hypothesis.html}, \texttt{t0\_xi\_num\_algebraisch.html},
\texttt{t0\_primzahl\_periodizitaet.html}, \texttt{t0\_shor\_bigint.html}.
They formulated the questions correctly but produced no systematic result tables.

\paragraph{Formulated hypotheses (now numerically clarified):}

\begin{description}
\item[$H_0$] $\xi$-optimal bases and random bases produce periods of the same
order of magnitude (no advantage from $\xi$-selection).
\item[$H_1$] $\xi$-bases produce smaller periods in the median (factor $> 1.5$
over $N = 50$ trials).
\end{description}

\begin{mdframed}[style=warn]
The $\xi$-resonance function in the scripts
($\omega = 2\pi/r$, resonance $= \exp(-(\omega - \pi)^2 / (4|\xi|))$)
is a heuristic without physical derivation. It preferentially selects $r \approx 2$
— which is the most common $\gcd$-case, not a $\xi$-effect.
\end{mdframed}

\subsection*{5. Relationship to $\xi_\text{FFGFT}$}

\[
\xi_\text{FFGFT} = \frac{4}{30000} = 1.333 \times 10^{-4}
\;\ll\; \xi_\text{num} \in [0.008,\; 0.49]
\]

The two quantities are not numerically identical and not simply related by
a scale factor. A structural connection — for instance that $\xi_\text{num}$
is a ``projection'' of $\xi_\text{FFGFT}$ onto the number space — remains a
conjecture without an algebraic bridge proof.

What is missing for a proof:
\begin{enumerate}
\item An argument for why $\xi_\text{FFGFT}$ (geometric) should appear in
$\xi_\text{num}$ (arithmetic)
\item A scale relation explaining how $\xi_\text{FFGFT} \approx 10^{-4}$
maps onto $\xi_\text{num} \approx 0.1\text{--}0.5$
\item A prediction that differs from classical number theory
\end{enumerate}

\subsection*{6. Established Facts — Summary}

\begin{center}
\begin{tabular}{lc}
\toprule
Statement & Status \\
\midrule
$\xi_\text{num}(N)$ is number-space dependent & $\checkmark$ Proved \\
The dependence is classical number theory & $\checkmark$ Proved \\
No global $\xi$ optimises factorisation universally & $\checkmark$ Proved \\
$\xi$-resonance heuristic favours $r \approx 2$ & $\checkmark$ Clear \\
Rounding errors affect effective $\xi$ & $\checkmark$ Known \\
$\xi_\text{num}$ follows FFGFT step hierarchy & $\times$ Not proved \\
$\xi_\text{FFGFT}$ and $\xi_\text{num}$ structurally related & $\times$ Not proved \\
$\xi$-basis selection improves period-finding & $\times$ $H_0$ not refuted \\
\bottomrule
\end{tabular}
\end{center}

\begin{mdframed}[style=info]
\textbf{Conclusion:} The number-space dependence is real but classical. The
connection to FFGFT geometry is open and remains a conjecture. The breakthrough
is missing because the algebraic bridge proof is missing — it would need to show
why a geometric invariant of T$^4$ appears in the Carmichael structure of
arithmetic number spaces.
\end{mdframed}
