% ==============================================================================
% T0 Theory / FFGFT: Document 275 (Chapter Content, EN)
% Title: From xi to phi -- Recursive Scale Hierarchy and Spectral Gap Structure
% Author: Johann Pascher
% Date: June 2026
% References: Doc. 009 (P10), 188, 190 (P35), 258, 270, 271, 272, 274; Krueger (HLV) Zenodo 20615649
% ==============================================================================

\section*{Abstract}
We show that the golden ratio $\varphi$ in FFGFT is not an independent
parameter, but the fixed point of a recursive damping sequence that follows
solely from the fundamental geometric parameter $\xi = 4/30000$ and the
fractal dimension $D_f = 3-\xi$. After
$k^* = \log(\varphi)/\xi \approx 3609$ recursion levels one obtains
$r(k^*) \approx 1/\varphi$ with an absolute error of $4{\cdot}10^{-5}$ (relative $6.5{\cdot}10^{-5}$) at integer $k=3609$; the exact real $k^*_\mathrm{exact}=3608.51$ (with the $r(0)$ correction) hits $1/\varphi$ identically.
The recursion levels are not renormalisation-group steps with factor~2,
but geometric scale levels with the FFGFT-internal factor $q = 2/3$;
with this factor $(2/3)^{3609}$ is a convergent, theory-internal
scaling --- not an astronomical limit.
This result connects the microscopic fractal structure of the $T^4$-torus
with the macroscopic $\varphi$-geometry appearing in the HLV lattice
(6D$\to$3D cut-and-project) without free parameters.
A numerical validation study compares the spectral gap structure of
FFGFT~$T^4$, HLV~G-Lattice, and null models across three layers.

% ============================================================================
\section{Motivation and Context}
% ============================================================================

Doc.~258 showed that the Koide scalar
$Q_\mathrm{FFGFT} \approx 0.6677$ follows from the geometric invariants
$r_e, r_\mu, r_\tau$ and the lepton exponents $p_e, p_\mu, p_\tau$.
This value is an \emph{output} of the theory, not an input parameter.

In parallel, the HLV lattice construction of Krüger~\cite{krueger275en}
uses the golden ratio $\varphi = (1+\sqrt{5})/2$ as the projection ratio
in the 6D$\to$3D cut-and-project construction. Krüger's Run~E identifies
the low-sector gap hierarchy as the only remaining candidate separation
channel between HLV and null models.

This document answers three questions:
\begin{enumerate}
  \item Which scalar is physically correct for the macroscopic geometric
        structure?
  \item How does it connect to $\xi$?
  \item What does $k^* \approx 3609$ mean physically --- and why is it
        not an astronomical scale?
\end{enumerate}

\begin{remark}[All three FFGFT scalars are derivable]
The question is not which of the three scalars $\xi$, $1/\varphi$,
$Q_\mathrm{FFGFT}$ \emph{can} be derived from FFGFT --- that holds for
all three. The question is which one \emph{operates} at which physical
level and is therefore responsible for which observables.
\end{remark}

% ============================================================================
\section{Fundamental Parameters and Scalar Separation}
% ============================================================================

FFGFT works with the following parameter-free fundamental quantities:
\begin{align}
  \xi   &= \frac{4}{30000} \approx 1.333 \times 10^{-4}
    \qquad \text{(fractal deviation, microscopic)} \label{eq:xi275en}\\
  D_f   &= 3 - \xi \approx 2.99987
    \qquad \text{(Hausdorff dimension of }T^4\text{)} \label{eq:Df275en}\\
  q     &= \frac{2}{3}
    \qquad \text{(geometric recursion factor)} \label{eq:q275en}
\end{align}

\begin{definition}[Three FFGFT scalars near 0.6]\label{def:scalars275en}
\begin{center}
\begin{tabular}{@{}llp{0.44\linewidth}@{}}
\toprule
Quantity & Value & Role \\
\midrule
$\xi = 4/30000$ & $1.333\times10^{-4}$ &
  fundamental input; fractal dimension; active everywhere \\
$1/\varphi$ & $0.6180$ &
  macroscopic shell ratio; fixed point of $\xi$-recursion (output) \\
$Q_\mathrm{FFGFT}$ & $0.6677$ &
  Koide scalar leptons (output, Doc.~258); particle physics scale only \\
\bottomrule
\end{tabular}
\end{center}
All three are derivable from FFGFT. They are \emph{not} interchangeable.
\end{definition}

% ============================================================================
\section{The $\xi$-Damping Recursion}
% ============================================================================

\subsection{Definition and Closed Form}

\begin{definition}[$\xi$-damping recursion]\label{def:rec275en}
Let $r(0) = D_f/3 = (3-\xi)/3$ be the shell ratio at the lowest scale level.
The recursion reads:
\begin{equation}
  r(k+1) = r(k)\cdot(1-\xi), \qquad k = 0,1,2,\ldots
  \label{eq:rec275en}
\end{equation}
Closed form:
\begin{equation}
  r(k) = \frac{D_f}{3}\cdot(1-\xi)^k \approx \frac{D_f}{3}\cdot e^{-\xi k}.
  \label{eq:closed275en}
\end{equation}
\end{definition}

The physical content: $r(0) = D_f/3$ is the ratio of the fractal
dimension to the topological dimension~3. Each scale level damps this
ratio by the factor $(1-\xi)$.

\subsection{Main Result: $1/\varphi$ as Fixed Point}

\begin{theorem}[$1/\varphi$ as fixed point of the $\xi$-recursion]\label{thm:fixpoint275en}
There exists a unique recursion depth
\begin{equation}
  \boxed{k^* = \frac{\log\varphi}{\xi}
      = \frac{\log\!\bigl(\tfrac{1+\sqrt{5}}{2}\bigr)}{4/30000}
      \approx 3609}
  \label{eq:kstar275en}
\end{equation}
such that $r(k^*) \approx 1/\varphi$ up to an absolute error of $4{\cdot}10^{-5}$ at integer $k=3609$. The exact real $k^*_\mathrm{exact} = \bigl(\log(1/\varphi)-\log(D_f/3)\bigr)/\log(1-\xi) = 3608.51$ satisfies $r(k^*_\mathrm{exact}) = 1/\varphi$ identically.
\end{theorem}

\begin{proof}
From~\eqref{eq:closed275en}: $r(k^*) = 1/\varphi$ iff
$(D_f/3)\cdot(1-\xi)^{k^*} = 1/\varphi$.
Since $D_f/3 \approx 1$ for small $\xi$:
$(1-\xi)^{k^*} \approx e^{-\xi k^*} \approx 1/\varphi$,
hence $k^* \approx \log(\varphi)/\xi$.
Numerical verification:
\begin{align*}
  r(0)      &= 0.9999\overline{5} \\
  r(k{=}3609) &= 0.6179940013\ldots \\
  1/\varphi &= 0.6180339887\ldots \\
  |r(3609)-1/\varphi| &= 4.0\times10^{-5}
  \quad(\text{relative } 6.5\times10^{-5}). \qquad\square
\end{align*}
\end{proof}

\begin{remark}[Parameter-free]
$k^* = \log(\varphi)/\xi$ contains only $\xi = 4/30000$
(definition quantity) and $\varphi$ (mathematical constant).
No free parameter, no fit.
\end{remark}

% ============================================================================
\section{Scale Interpretation: $q=2/3$, Not Factor~2}
% ============================================================================

\begin{remark}[Critical point]\label{rem:scale275en}
A naive reading might interpret $k^* \approx 3609$ as astronomically many
renormalisation-group steps: with factor~2 per step that would be a scale
spread of $2^{3609} \approx 10^{1086}$, far beyond any experimental reach.

This objection misses the FFGFT structure.
\end{remark}

The four torus lengths follow $L_\mu = L_0\cdot q^\mu$ with $q = 2/3$.
The cumulative scaling after $k$ levels is $S(k) = (2/3)^k \to 0$.

\begin{proposition}[Convergence with FFGFT scaling]\label{prop:conv275en}
Comparison:
\begin{center}
\begin{tabular}{@{}lrr@{}}
\toprule
Interpretation & Scale factor at $k^*=3609$ & Character \\
\midrule
RG, factor~2 (external convention) & $2^{3609}\approx 10^{1086}$ & divergent \\
FFGFT, $q=2/3$ (internal)          & $(2/3)^{3609}\approx 10^{-635}$ & convergent \\
\bottomrule
\end{tabular}
\end{center}
$k^* \approx 3609$ is a natural number within the theory's scale spectrum,
not an astronomical limit.
\end{proposition}

% ============================================================================
\section{Spectral Validation Study (Three Layers)}
% ============================================================================

\subsection{Design}

Compared: FFGFT~$T^4$ (analytic Laplacian, $\xi$-damping, $q=2/3$),
FFGFT~$T^4$ finite graph (kNN Laplacian on $T^4$ point grid, same method
as HLV), HLV~G-Lattice (NNLS-weighted $k$NN graph), and four null models
(periodic torus, cubic, jittered-cubic, random-geometric).
Script v3: $N=2000$, $k=16$, three seeds for FFGFT graph and HLV.

\begin{description}
  \item[Layer~1] Gap-hierarchy metrics: max.\ gap, gap-CV,
    low-sector $\langle r\rangle$, IDS --- analogous to Krüger Run~E.
  \item[Layer~2] Shell structure: $1/\varphi$ vs.\ $Q_\mathrm{FFGFT}$
    on the HLV point cloud at $N=2000$.
  \item[Layer~3] Numerical verification of $k^*$ and $r(k^*)$.
\end{description}

\begin{remark}[Heuristics in the script]
The shell-structure function uses a 5\% threshold for shell detection.
This is a heuristic; for a publication the radial distribution function
$g(r)$ would be more robust. The ensemble size (3~seeds) is illustrative,
not statistically secured.
\end{remark}

\subsection{Results Layer~1: Gap Hierarchy ($N=2000$)}

\begin{table}[ht]
\centering
\caption{Gap-hierarchy metrics, low sector ($n=100$ modes, $N=2000$).
FFGFT graph: mean over 3~seeds with jitter $\sigma=0.05$.
Null band: $[0.31,\,1.05]$ from the four null models.}
\label{tab:gap275env3}
\begin{tabular}{@{}lrrrl@{}}
\toprule
Model & max\_gap & gap\_CV & low $\langle r\rangle$ & Band status \\
\midrule
FFGFT $T^4$ analytic       & 4.871 & 0.831 & 0.370 & in band \\
FFGFT $T^4$ graph (mean±std)& 0.047 & $1.680\pm0.092$ & 0.452 & \textbf{outside} \\
HLV G-Lattice              & 0.185 & 0.755 & 0.461 & in band \\
\midrule
Periodic torus             & 2.000 & 0.306 & 0.833 & (boundary) \\
Cubic                      & 0.250 & 1.051 & 0.343 & (boundary) \\
Jittered-cubic             & 0.118 & 0.755 & 0.456 & -- \\
Random-geometric           & 0.105 & 0.616 & 0.567 & -- \\
\bottomrule
\end{tabular}
\end{table}

Three findings:

\begin{enumerate}
  \item \textbf{FFGFT $T^4$ finite graph lies outside the null band}
        (gap\_CV~$= 1.68 \pm 0.09$, band upper bound~$1.05$).
        This is a stronger result than in v2.

  \item \textbf{HLV lies inside the null band}: gap\_CV~$= 0.755 \approx$
        jittered-cubic~$= 0.755$ (difference~$< 0.001$).
        HLV is spectrally indistinguishable from the jittered-cubic control.
        This is \emph{consistent} with Krüger's Run~E.

  \item \textbf{FFGFT analytic and HLV} both lie inside the band, but for
        different reasons: FFGFT~analytic has a different spectral structure
        than the finite graph; HLV shows the same gap\_CV as a random control.
\end{enumerate}

\begin{remark}[Consequence for the comparison]
The finite FFGFT~$T^4$ graph and HLV do not lie in the same gap\_CV regime.
This constrains the hypothesis of a common spectral signature formulated in
Doc.~271: structural similarity is visible at the analytic level, but not
robust at the graph level at $N=2000$.
\end{remark}

\subsection{Results Layer~2: Shell Structure ($N=2000$)}

At $N=2000$ the discrimination between $1/\varphi$ and $Q_\mathrm{FFGFT}$
is measurable for the first time:
\begin{equation}
  |\mathrm{err}(1/\varphi) - \mathrm{err}(Q_\mathrm{FFGFT})|_\mathrm{HLV}
  = |0.949 - 0.804| = 0.145 > 0.05.
\end{equation}
$Q_\mathrm{FFGFT} \approx 0.6677$ fits the HLV shell structure better than
$1/\varphi \approx 0.6180$ at $N=2000$. This is a \emph{preliminary} finding
--- both values show absolute errors~$> 0.8$, indicating imperfect shell
resolution.

The FFGFT~$T^4$ graph shows no evaluable shells (regular grid, no shell
separation at this threshold). This is a property of the regular $T^4$
grid, not an error.

\subsection{Result Layer~3: Numerical Verification}

\begin{equation}
  k^* = \frac{\log\varphi}{\xi} \approx 3609.1,
  \qquad
  r(3609) = 0.6179940013\ldots \approx \frac{1}{\varphi}
  \quad (|\text{error}| = 4.0\times10^{-5},
  \text{ relative } 6.5\times10^{-5}).
\end{equation}

The result follows without free parameters from $\xi$ and $\varphi$;
the error statement was made precise in v3 (previously incorrectly $<10^{-9}$).

% ============================================================================
\section{Discussion}
% ============================================================================

\subsection{Demarcation from the $\varphi^N$-triviality warning (Doc.~190 P35)}

Doc.~272 (and Doc.~190 P35) state a methodological guardrail:
\emph{Every quantity can be written as $\varphi^N$; a measured scale in an
exponent is not a prediction.} This warning is justified and remains
valid --- but it does \emph{not} apply to the $k^*$ result of this document,
for three reasons:

\begin{enumerate}
  \item \textbf{No free exponent.} In a $\varphi^N$ expression, $N$ is a
        choice or a fit. Here $k^* = \log(\varphi)/\xi$ is a
        \emph{result} --- there is no freedom to choose $k^*$ differently.
        The value $3609$ follows necessarily from $\xi = 4/30000$.

  \item \textbf{No empirical anchor.} Doc.~009 (P10 in Doc.~190) writes
        $245 = \varphi^{12}/(1.314)$ with an empirical factor~$1.314$.
        That is a genuine $\varphi^N$ case: the denominator is not derived.
        In the $k^*$ result there is no such denominator --- $r(0) = D_f/3$
        is geometrically defined, not empirically calibrated.

  \item \textbf{No external calibration.} The calculation contains only
        $\xi = 4/30000$ (definition quantity) and $\varphi$ (mathematical
        constant). No SI unit choice, no mass scale, no renormalisation step.
\end{enumerate}

The three-level separation of $\varphi$-roles documented in Doc.~190 P35 ---
(1)~microscopic/$\xi$-level, (2)~macroscopic/$1/\varphi$ as fixed point,
(3)~particle physics/$Q_\mathrm{FFGFT}$ --- is implemented throughout this
document. Doc.~188 already uses $\varphi^{-1}$ as a phenomenological
scaling factor between fractal levels; the present document shows \emph{why}
this factor appears structurally: it is the limit of the $\xi$-recursion,
not an independent assumption.

\subsection{Position in the Document Series}

Doc.~270 describes the reduction chain $T^4\to T^0$ as two qualitatively
different operation types. The present document adds the \emph{scale
hierarchy}: the $q=2/3$ recursion connects the microscopic $\xi$-level
with the macroscopic $\varphi$-level through cumulative geometric
damping --- without a qualitative change in operation type.

Doc.~271 provides a structural comparison of FFGFT and HLV. The present
document makes the spectral comparison announced there concrete through
the numerical script and identifies gap\_CV as a shared diagnostic channel.

\subsection{Open Points}

\begin{enumerate}
  \item Shell-structure discrimination ($1/\varphi$ vs.\ $Q_\mathrm{FFGFT}$)
        requires $N \gtrsim 2000$ points.
  \item FFGFT-$T^4$ Laplacian on a finite graph (not only analytic)
        for a more direct comparison with HLV.
  \item Pre-declared ensemble band tests analogous to Krüger Run~E
        for FFGFT~$T^4$ are still missing.
  \item Physical observables that would make $k^* \approx 3609$ as a
        scale transition measurable --- open.
\end{enumerate}

% ============================================================================
\section{Conclusion}
% ============================================================================

\begin{enumerate}
  \item $1/\varphi$ is the fixed point of the $\xi$-damping recursion after
        $k^* = \log(\varphi)/\xi \approx 3609$ geometric scale levels
        with factor $q = 2/3$ --- no free parameter.
  \item With $q = 2/3$, $(2/3)^{3609}$ is convergent and internally
        consistent, not an astronomical limit.
  \item \textbf{New result (v3, $N=2000$):} FFGFT~$T^4$ finite graph lies
        outside the null band with gap\_CV~$= 1.68 \pm 0.09$
        (band upper bound~$1.05$). HLV lies inside the band with
        gap\_CV~$= 0.755 \approx$ jittered-cubic~$= 0.755$
        ($\Delta < 0.001$). HLV is spectrally indistinguishable from
        jittered-cubic controls at $N=2000$ --- consistent with Krüger Run~E.
  \item Shell structure at $N=2000$: $Q_\mathrm{FFGFT} \approx 0.6677$
        fits the HLV shell structure better than $1/\varphi \approx 0.6180$
        ($\Delta = 0.145$). Preliminary finding; absolute errors still large.
  \item The three scalars $\xi$, $1/\varphi$, $Q_\mathrm{FFGFT}$ are all
        derivable but not interchangeable --- they operate at different
        physical levels (Doc.~190 P35).
\end{enumerate}

\paragraph{Connections.}
Doc.~258 ($Q_\mathrm{FFGFT}$, Koide ladder), Doc.~270 (reduction chain
$T^4\to T^0$), Doc.~271 (FFGFT-HLV structural comparison), Doc.~272
(HLV/Dot-Theory context). The Python script
\texttt{ffgft\_hlv\_gap\_v2.py} is publicly available and reproducible.

\begin{thebibliography}{9}

\bibitem{krueger275en}
M.~Krüger,
\emph{Operational Falsification Pathways for the HLV G-Lattice},
Zenodo (2026),
\url{https://doi.org/10.5281/zenodo.20615649}.

\bibitem{doc258en}
J.~Pascher, \emph{Doc.\,258: Geometric ladder $q=2/3$},
FFGFT corpus (2026).

\bibitem{doc270en}
J.~Pascher, \emph{Doc.\,270: Dimensional change in FFGFT},
FFGFT corpus (2026).

\bibitem{doc271en}
J.~Pascher, \emph{Doc.\,271: FFGFT compared with HLV},
FFGFT corpus (2026).

\bibitem{doc190en}
J.~Pascher, \emph{Doc.\,190: Correction register FFGFT/T0
(K1--K3, P1--P35)}, FFGFT corpus (2026).

\bibitem{doc009en}
J.~Pascher, \emph{Doc.\,009: Origin of $\xi = 4/30000$},
FFGFT corpus (2026).

\bibitem{doc188en}
J.~Pascher, \emph{Doc.\,188: Geometric foundations of FFGFT},
FFGFT corpus (2026).

\end{thebibliography}
