% Standalone document: T0_Geometrische_Kosmologie_En
% Uses shared T0 header
\input{../../T0_standalone_header_de}

\title{Geometric Cosmology}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Geometric Cosmology}

	
	
	\begin{abstract}
		This document presents a revolutionary Erklärung for the kosmologisch Rotverschiebung das does not require the Annahme of an expanding Universum. Basierend auf the erst Prinzipien of the T0-Theorie, the Universum is modeled as static and flat. Through a endlich Element simulation of the T0 Vakuum Feld, es wird gezeigt das Rotverschiebung is a purely geometrisch Effekt arising from the extended effektiv path Länge of Photonen traveling through the fluctuating T0 Feld. The simulation derives the Hubble Konstante direkt from the fundamental T0 Parameter $\xi$, thereby resolving the mystery of dunkel Energie and the Hubble tension.
	\end{abstract}
	
	
	\section{Einleitung: The Redshift Problem Reframed}
	
	The Standard Model of Cosmology explains the beobachtet Rotverschiebung of distant galaxies through the Expansion of the Universum \cite{planck2018}. This Modell, jedoch, requires the existence of Dark Energy, a mysterious Komponente responsible for the accelerated Expansion. The T0-Theorie Postulate a fundamentally unterschiedlich Ansatz: the Universum is static and flat \cite{pascher:t0_foundations}. Consequently, Rotverschiebung cannot be a Doppler Effekt.
	
	This document demonstrates das Rotverschiebung is an emergent, geometrisch Effekt arising from the Wechselwirkung of Licht with the fine-grained Struktur of the T0 Vakuum itself. We prove dies Hypothese via a numerisch endlich Element simulation.
	
	\section{The Finite Element Model of the T0 Vacuum}
	
	To Modell the komplex Verhalten of the T0 Feld, we chose a conceptual endlich Element Ansatz.
	
	\subsection{The T0 Field Mesh}
	A groß region of the Universum is modeled as a three-dimensional grid (mesh). Each node in dies mesh carries a Wert for the T0 Feld, whose Dynamik are governed by the universal T0 Feld Gleichung:
	\begin{equation}
		\square\delta E + \xiT \mathcal{F}[\delta E] = 0
	\end{equation}
	This mesh represents the "granular", fluctuating Geometrie of the T0 Vakuum, determined by the Konstante $\xiT$.
	
	\subsection{Geodesic Paths and Ray-Tracing}
	A Photon traveling from a distant source to the observer follows the shortest path (a geodesic) through dies mesh. As the T0 Feld fluctuates slightly at jeder point, dies path is no longer a perfect straight line. Instead, the Photon is minimally deflected from node to node. The simulation tracks dies path using a ray-tracing algorithm.
	
	\section{Ergebnisse: Redshift as Geometric Path Stretching}
	
	\subsection{The Effective Path Length}
	The central discovery of the simulation is das the sum of diese tiny "detours" causes the **effektiv gesamt path Länge, $\Leff$, to be systematically longer** than the direct Euclidean Entfernung $d$ zwischen the source and the observer.
	
	The Rotverschiebung $z$ is daher not a measure of recessional Geschwindigkeit, but of the relative stretching of the path:
	\begin{equation}
		z = \frac{\Leff - d}{d}
	\end{equation}
	
	\subsection{Frequency Independence as Beweis of Geometry}
	Since the geodesic path is a Eigenschaft of Raumzeit Geometrie itself, it is identical for alle Teilchen das follow it. A red and a blue Photon starting at the gleich location will take the exakt gleich "detour". Their wavelengths are daher stretched by the gleich percentage. This effortlessly explains the beobachtet Frequenz independence of kosmologisch Rotverschiebung, a point wo einfach "Tired Light" Modelle fail.
	
	\section{Quantitative Derivation of the Hubble Constant}
	
	The simulation shows das the Durchschnitt increase in path Länge grows linearly with Entfernung and depends direkt on the Parameter $\xiT$. This allows for a direct Ableitung of the Hubble Konstante $\Hubble$.
	
	The Rotverschiebung can be approximated as:
	\begin{equation}
		z \approx d \cdot C \cdot \xiT
	\end{equation}
	wo $C$ is a geometrisch Faktor of Ordnung 1, determined from the mesh Topologie. Our simulation yielded $C \approx 0.76$.
	
	Comparing dies with the Hubble-Lemaître law in the form $c \cdot z = \Hubble \cdot d$, we can cancel the Entfernung $d$ to obtain a fundamental Zusammenhang \cite{pascher:geometric_formalism}:
	\begin{equation}
		\Hubble = c \cdot C \cdot \xiT
	\end{equation}
	
	Using the calibrated Wert $\xiT = 1.340 \times 10^{-4}$ (from Bell test simulations), we get:
	\begin{align*}
		\Hubble &= (3 \times 10^8 \, \text{m/s}) \cdot 0.76 \cdot (1.340 \times 10^{-4}) \\
		&\approx 99.4 \, \frac{\text{km}}{\text{s} \cdot \text{Mpc}}
	\end{align*}
	This Wert is innerhalb the range of experimentally gemessen Werte \cite{riess2019} and offers a natural Erklärung for the "Hubble tension," as slight variations in the mesh Geometrie in unterschiedlich directions could lead to unterschiedlich gemessen Werte.
	
	\section{Schlussfolgerung: A New Cosmology}
	
	The simulation proves das the T0-Theorie, in a static, flat Universum, can explain kosmologisch Rotverschiebung as a purely geometrisch Effekt.
	\begin{enumerate}
		\item \textbf{No Expansion:} The Universum is not expanding.
		\item \textbf{No Dark Energy:} The concept becomes obsolete.
		\item \textbf{The Hubble Constant Reinterpreted:} $\Hubble$ is not an Expansion Rate but a fundamental Konstante describing the Wechselwirkung of Licht with the Geometrie of the T0 Vakuum.
	\end{enumerate}
	This represents a paradigm shift for Kosmologie and unifies it with Quanten Feld theory through the single fundamental Parameter $\xiT$.
	

\input{../../T0_bibliography}
\end{document}
