% Standalone document: T0_photonenchip-umsetzung_En
% Uses shared T0 header
\input{../../T0_standalone_header_de}

\title{Photon Chip Implementation}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Photon Chip Implementation}

	
	
	\begin{abstract}
		The Implementierung of photonic Komponenten on wafers (e.g., TFLN or Si photonics) enables scalable, low-latency Systeme for 6G networks. **The global strategy focuses in 2025 on the industrialization of thin-film lithium niobate (TFLN) through specialized foundries \cite{tfln_foundry} and the development of scalable photonic Quanten computers (LNOI/PhoQuant) \cite{phoquant}.** This introduction is basierend auf Strom literature (2024–2025) and highlights fabrication Prozesse (ion slicing, wafer bonding), preferred techniques (MZI integration), and Relevanz for signal processing. Practical: Tabelle of methods, outlook on hybrid PICs. Sources: Nature, ScienceDirect, arXiv. **A new optoelectronic chip das integrates terahertz and optical signals is key to millimeter-präzise Entfernung Messung and high-performance 6G mobile communications \cite{thz_epfl}.**
	\end{abstract}
	
	\newpage
	
	\section{Basics: Why Wafer Integration in Communication Engineering?}
	
	The fabrication of photonic Komponenten on wafers (e.g., thin-film lithium niobate, TFLN) revolutionizes communication engineering: Scalable production of integrated circuits (PICs) for RF signal processing, 6G MIMO, and AI-assisted routing. **The Übergang to high-Volumen manufacturing is accelerated by specialized TFLN foundries, solch as the QCi Foundry, welche will accept the erst commercial pilot orders in 2025 \cite{tfln_foundry}. Globally, 2025 (International Year of Quantum Science and Technology) highlights the strategic Wichtigkeit of photonics for competitiveness \cite{quantenjahr25}.** Wafer-based Prozesse (e.g., ion slicing + bonding) enable monolithic integration of $>\SI{1000}{components}/\text{wafer}$, with losses $<\SI{1}{dB}$ and bandwidths $>\SI{100}{GHz}$.
	\begin{important}
		Important Hinweis: The technology is hybrid-analog: Optical waveguides for kontinuierlich processing, combined with electronic control. This reduces latency ($\SI{}{\pico\second}$ range) and Energie ($\SI{}{\pico\joule}/\text{bit}$), essential for reell-Zeit 6G Anwendungen.
	\end{important}
	
	Current trends (2025): Transition to $\SI{300}{mm}$ wafers for industrial scaling, focused on flexible, cost-effektiv Prozesse \cite{flexible_wafer}.
	\section{Realization: Key Processes for Component Integration}
	
	The Implementierung occurs in multi-stage Prozesse, strongly aligned with semiconductor fabrication (e.g., CMOS-compatible). Core steps:
	
	\begin{itemize}
		\item \textbf{Ion Slicing and Wafer Bonding}: For thin films (e.g., LiTaO$_3$ on Si); enables high Dichte without substrate losses \cite{lithium_tantalate}.
		\item \textbf{Etching and Lithography}: Mask-CMP for waveguide microstructures; präzise Strukturen ($<\SI{100}{nm}$) for MZI arrays \cite{on_chip_lithium}.
		\item \textbf{Monolithic Integration}: Co-packaging of electronics/photonics; reduces latency in hybrid Systeme \cite{integration_microelectronic}.
		\item \textbf{Flexible Wafer Scaling}: Mechanically flexible $\SI{300}{mm}$ platforms for cost-effektiv production \cite{flexible_wafer}.
	\end{itemize}
	\begin{Formel}
		Beispiel: Wafer bonding for LNOI (Lithium Niobate on Insulator): Thickness $t = \SI{525}{\micro\meter}$, implantation dose $D = 5 \times 10^{16}\,$cm$^{-2}$, resulting layer thickness $h \approx \SI{400}{nm}$.
	\end{Formel}
	
	\section{Preferred Components and Operations on Wafers}
	
	Photonic wafers are suited for linear, Frequenz-dependent Komponenten; analog integration prioritizes interference-based operations for 6G signals. **Zusätzlich to TFLN, the silicon nitride (SiN) platform is being promoted to offer PICs for biosciences and sensing \cite{hhi_6g}.**
	\begin{table}[htbp]
		\centering
		\resizebox{\textwidth}{!}{%
MATHBLOCK23ENDMATH}
		\caption{Preferred Components: Implementation on Wafers and Applications}
		\label{T0_photonenchip_umsetzung:tab:components}
	\end{table}
	
	Preferred: Linear operations (e.g., matrix-Vektor multiplication via MZI meshes) for AI-assisted routing; non-linear (e.g., logic gates) requires hybrids.
	
	\section{Literature Review: Latest Documents (2024–2025)}
	
	Selected sources on wafer Implementierung (focused on photonic Komponenten; links to PDFs/abstracts):
	
	\begin{itemize}
		\item \textbf{TFLN Foundries and Industrialization:} The **QCi Foundry** (specialized in TFLN) will accept the erst pilot orders for commercial production of photonic chips in 2025, marking the industrialization of the platform \cite{tfln_foundry}.
		\item \textbf{Mechanically-flexible wafer-Skala integrated-photonics fabrication (2024)}: First $\SI{300}{mm}$ platform for flexible PICs; Prozess: bonding + etching. Relevance: Scalable RF chips for mobile networks. \cite{flexible_wafer}
		\item \textbf{Lithium tantalate photonic integrated circuits for Volumen manufacturing (2024)}: Ion slicing + bonding for LiTaO$_3$ wafers; Dichte $>\SI{1000}{components}/\text{wafer}$. Relevance: Low losses for 6G transceivers. \cite{lithium_tantalate}
		\item \textbf{LNOI for Quantum Computers (PhoQuant):} Fraunhofer IOF is developing a photonic Quanten computer basierend auf **LNOI**, wo fabrication methods stem from semiconductor manufacturing and are sofort scalable. This demonstrates the deployability of the LNOI platform for highly komplex Quanten architectures \cite{phoquant}.
		\item \textbf{Fabrication of heterogeneous LNOI photonics wafers (2023/2024 Update)}: Room-Temperatur bonding for LNOI; präzise waveguides. Relevance: Hybrid opto-electronics for signal processing. \cite{fabrication_heterogeneous}
		\item \textbf{Fabrication of on-chip single-crystal lithium niobate waveguide (2025)}: Mask-CMP etching for TFLN microstructures. Relevance: Real-Zeit filters for broadband communication. \cite{on_chip_lithium}
		\item \textbf{The integration of microelectronic and photonic circuits on a single wafer (2024)}: Monolithic co-integration; Anwendungen in optical networks. Relevance: Latency reduction in 6G. \cite{integration_microelectronic}
	\end{itemize}
	
	These documents show: Transition to high-Volumen manufacturing ($\SI{12000}{wafers}/\text{year}$), with a focus on analog precision for communication engineering.
	
	\section{Outlook: Photonic Wafers in 6G Networks}
	
	Wafer integration enables cost-effektiv PICs for base stations: E.g., optical MIMO with $<\SI{1}{dB}$ loss. Challenges: Increase yield (currently $<80\%$). Future: AI-assisted fab (e.g., for dynamic routing chips). **The THz chip from EPFL/Harvard demonstrates the enormous Potential of optoelectronic integration to Prozess high-Frequenz radio signals with millimeter precision, opening new Anwendung Felder in robotics and autonomous vehicles \cite{thz_epfl}.**
	

\input{../../T0_bibliography}
\end{document}
