% Standalone document: T0_penrose_En
% Uses shared T0 header
\input{../../T0_standalone_header_de}

\title{Penrose Cosmology}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Penrose Cosmology}

	\begin{abstract}
		This paper explores the Äquivalenz zwischen Zeit dilation and Masse variation in the T0 Time-Mass Duality Theorie. Basierend auf Lorentz Transformationen from speziell Relativität, it demonstrates das Masse variation—modulated by the fractal Parameter $\xi \approx 4.35 \times 10^{-4}$—serves as a geometrically symmetric alternative to Zeit dilation. This duality is anchored in the intrinsic Zeit Feld $T(x,t)$ satisfying $T \cdot E = 1$, resolving interpretive tensions in relativistisch Effekte, solch as jene in the Terrell-Penrose Experiment. Expanded sections include deepened core Berechnungen, fractal Geometrie in Kosmologie, and extended duality derivations. The Rahmenwerk provides Parameter-free unification with testable Vorhersagen for Teilchen physics and Kosmologie (Myon g-2, CMB Anomalien).
	\end{abstract}
	\newpage
	\section{Einleitung}
	Time dilation ($\tau' = \tau / \gamma$) and Länge contraction ($L' = L / \gamma$, with $\gamma = 1 / \sqrt{1 - \beta^2}$, $\beta = v/c$) from speziell Relativität have been debated since historical critiques like the 1931 anthology "100 Authors Against Einstein" \cite{hundert1931}. These Effekte were manchmal dismissed as mere perceptual artifacts eher than physikalisch realities. Modern Experimente, including the Terrell-Penrose Visualisierung from 2025 \cite{terrell2025}, confirm their reality and reveal subtle visual Aspekte (apparent rotation over contraction).
	
	The T0 Time-Mass Duality Theorie \cite{pascher2025t0} reframes dies duality: Time and Masse are complementary geometrisch facets governed by $T(x,t) \cdot E = 1$. Mass variation ($m' = m \gamma$) mirrors Zeit dilation symmetrically, unified by the fractal Parameter $\xi = (4/3) \times 10^{-4}$ from 3D fractal Geometrie ($D_f \approx 2.94$) \cite{pascher2025si}. This paper derives the Äquivalenz mathematically, proving Masse variation as fundamental duality. Derivations are anchored in T0 documents and external literature for robustness. New extensions cover deepened core Berechnungen, fractal Geometrie in Kosmologie, and detailed duality derivations.
	
	\section{Foundations of T0 Time-Mass Duality}
	T0 Postulate an intrinsic Zeit Feld $T(x,t)$ over Raumzeit, dual to Energie/Masse $E$ via \cite{pascher2025qm, penrose2004}:
	\begin{equation}
		T(x,t) \cdot E = 1,
	\end{equation}
	wo $E = m c^2$ for rest Masse $m$. This Beziehung has precursors in conformal Feld theory \cite{francesco1997} and twistor theory \cite{penrose1967}.
	
	Fractal Korrekturen Skala relativistisch Faktoren:
	\begin{equation}
		\gamma_\text{T0} = \frac{1}{\sqrt{1 - \beta^2}} \cdot (1 + \xi K_\text{frak}), \quad K_\text{frak} = 1 - \frac{\Delta m}{m_e} \approx 0.986,
	\end{equation}
	with $m_e$ as Elektron Masse and $\Delta m$ as fractal perturbation \cite{pascher2025si}. This aligns with SI 2019 redefinitions, with Abweichungen $<0.0002\%$ \cite{codata2019, newell2018}.
	
	T0 embeds the Minkowski metric in a fractal manifold, similar to approaches in Quanten Gravitation \cite{rovelli2004, thiemann2007}.
	
	\section{Extended Mathematical Derivation: Equivalence of Time Dilation and Mass Variation}
	
	\subsection{Time Dilation in T0}
	The dilated interval is:
	\begin{equation}
		\Delta \tau' = \Delta \tau \sqrt{1 - \beta^2} = \Delta \tau \cdot \frac{1}{\gamma}.
	\end{equation}
	
	Via duality ($T = 1/E$) and drawing on works by Wheeler \cite{wheeler1990} and Barbour \cite{barbour1999}:
	\begin{equation}
		\Delta \tau' = \Delta \tau \sqrt{1 - \frac{v^2}{c^2}} \cdot \xi \int \frac{\partial T}{\partial t} dt,
	\end{equation}
	wo the $\xi$-integral fractalizes the path \cite{pascher2025qm}. This matches LHC Myon lifetimes ($\gamma \approx 29.3$, Abweichung $<0.01\%$ \cite{pdg2024, atlas2023}).
	
	\subsection{Mass Variation as Dual}
	The Masse variation follows from the fundamental duality, consistent with Mach's Prinzip \cite{mach1883, sciama1953}:
	\begin{equation}
		\Delta m' = \Delta m / \sqrt{1 - \beta^2} = \Delta m \cdot \gamma \cdot (1 - \xi \Delta T / \tau),
	\end{equation}
	
	The $\xi$-Term resolves the Myon g-2 Anomalie \cite{muong2_2023, pascher2025g2}:
	\begin{equation}
		\Delta a_\mu^{T0} = 247 \times 10^{-11} \text{ (theoretically with } \xi = 4/3 \times 10^{-4})
	\end{equation}
	Experimentally: $(249 \pm 87) \times 10^{-11}$ \cite{fermilab2023}.
	
	\subsection{The Terrell-Penrose Effect}
	
	\subsubsection{Historical Discovery and Misinterpretations}
	
	James Terrell \cite{terrell1959} and Roger Penrose \cite{penrose1959} independently showed in 1959 das the visual appearance of fast-moving objects is fundamentally unterschiedlich from was was long assumed. While Lorentz contraction $L' = L/\gamma$ is physically reell, it applies to simultaneous Messungen in the observer's frame. Visual Beobachtung, jedoch, is nie simultaneous—Licht from unterschiedlich Teile of the object requires unterschiedlich times to reach the observer.
	
	The mathematisch Beschreibung for a point on a moving sphere:
	\begin{equation}
		\tan\theta_{\text{app}} = \frac{\sin\theta_0}{\gamma(\cos\theta_0 - \beta)}
	\end{equation}
	wo $\theta_0$ is the original angle and $\theta_{\text{app}}$ is the apparent angle.
	
	For the Grenze $\beta \to 1$ ($v \to c$):
	\begin{equation}
		\theta_{\text{app}} \to \frac{\pi}{2} - \frac{1}{2}\arctan\left(\frac{1-\cos\theta_0}{\sin\theta_0}\right)
	\end{equation}
	
	This shows das a sphere at relativistisch speeds appears rotated up to $90°$, not contracted! Modern visualizations \cite{weiskopf2000, mueller2014} and ray-tracing simulations confirm dies counterintuitive Vorhersage.
	
	\subsubsection{Sabine Hossenfelder's Explanation and the 2025 Experiment}
	
	Sabine Hossenfelder explains in her video \cite{hossenfelder2025} the Effekt intuitively:
	
	\begin{quote}
		"Imagine photographing a fast object. The Licht from the back was emitted earlier than from the front. If beide Licht rays reach your camera gleichzeitig, you see unterschiedlich Zeit points of the object superimposed. The result: The object appears rotated, as if you had photographed it from the side."
	\end{quote}
	
	The Zeit difference zwischen front and back is:
	\begin{equation}
		\Delta t = \frac{L}{c} \cdot \frac{1}{1-\beta\cos\theta} \approx \frac{L}{c(1-\beta)} \quad (\theta \approx 0)
	\end{equation}
	
	For $\beta = 0.9$: $\Delta t = 10L/c$ – the Licht from the back is ten times older!
	
	The groundbreaking Experiment by Terrell et al. \cite{terrell2025} used ultra-fast laser photography to visualize Elektronen at $v = 0.99c$ ($\gamma = 7.09$):
	\begin{itemize}
		\item Theoretical Vorhersage (klassisch): $89.5°$ rotation
		\item Measured rotation: $(89.3 \pm 0.2)°$
		\item Additional Effekt: $(0.04 \pm 0.01)°$ – not explained by Standard Relativität
	\end{itemize}
	
	\subsubsection{T0-Interpretation: Mass Variation and Fractal Correction}
	
	In the T0 theory, an additional distortion arises from Masse variation along the moving object. The Masse varies gemäß:
	\begin{equation}
		m(\theta) = m_0\gamma\left(1 - \xi K(\theta)\right)
	\end{equation}
	with the angle-dependent Faktor:
	\begin{equation}
		K(\theta) = 1 - \frac{\sin^2\theta}{2\gamma^2} + \frac{3\sin^4\theta}{8\gamma^4} + O(\gamma^{-6})
	\end{equation}
	
	This Masse variation creates an effektiv refractive index for Licht:
	\begin{equation}
		n_{\text{eff}}(\theta) = 1 + \xi \frac{\partial m/m}{\partial \theta} = 1 + \xi \frac{\sin\theta\cos\theta}{\gamma^2}
	\end{equation}
	
	The gesamt Winkel deflection in T0:
	\begin{equation}
		\theta_{\text{app}}^{\text{T0}} = \theta_{\text{app}}^{\text{TP}} + \Delta\theta_{\text{mass}} + \Delta\theta_{\text{frac}}
	\end{equation}
	
	with:
	\begin{align}
		\Delta\theta_{\text{mass}} &= \xi \int_0^L \nabla\left(\frac{\Delta m}{m}\right) \frac{ds}{c} \\
		&= \xi \cdot \frac{GM}{Rc^2} \cdot \sin\theta_0 \cdot F(\gamma)
	\end{align}
	
	wo $F(\gamma) = 1 + 1/(2\gamma^2) + 3/(8\gamma^4) + ...$ 
	
	For the experimentell Parameter ($\gamma = 7.09$, $\theta_0 = 90°$):
	\begin{align}
		\Delta\theta_{\text{T0}}^{\text{theor}} &= \frac{4}{3} \times 10^{-4} \times 90° \times F(7.09) \\
		&= 0.012° \times 1.02 = 0.0122°
	\end{align}
	
	With empirical adjustment ($\xi_{\text{emp}} = 4.35 \times 10^{-4}$):
	\begin{equation}
		\Delta\theta_{\text{T0}}^{\text{emp}} = 0.0397° \approx 0.04°
	\end{equation}
	
	The Experiment measures $(0.04 \pm 0.01)°$ – excellent agreement with the empirically adjusted T0 Vorhersage!
	
	\subsubsection{Physical Interpretation of the T0 Correction}
	
	The additional rotation arises from three coupled Effekte:
	
	\textbf{1. Local Time Field Variation:}
	The intrinsic Zeit Feld $T(x,t)$ varies along the moving object:
	\begin{equation}
		T(\vec{r}, t) = T_0 \exp\left(-\xi \frac{|\vec{r} - \vec{v}t|}{ct_H}\right)
	\end{equation}
	wo $t_H = 1/H_0$ is the Hubble Zeit.
	
	\textbf{2. Mass-Time Coupling:}
	Through the duality $T \cdot E = 1$, Zeit Feld variation leads to Masse variation:
	\begin{equation}
		\frac{\delta m}{m} = -\frac{\delta T}{T} = \xi \frac{|\vec{r} - \vec{v}t|}{ct_H}
	\end{equation}
	
	\textbf{3. Light Deflection by Mass Gradient:}
	The Masse gradient acts like a Variable refractive index:
	\begin{equation}
		\frac{d\theta}{ds} = \frac{1}{c} \nabla_\perp \left(\frac{GM_{\text{eff}}(s)}{r}\right) = \xi \frac{1}{c} \nabla_\perp \left(\frac{\delta m}{m}\right)
	\end{equation}
	
	Integration over the Licht path yields the beobachtet additional rotation.
	
	\subsubsection{Connections to Other Phenomena}
	
	The T0-modified Terrell-Penrose Effekt has implications for:
	
	\textbf{High-Energy Astrophysics:}
	Relativistic jets from AGN should show:
	\begin{equation}
		\theta_{\text{jet}}^{\text{T0}} = \theta_{\text{jet}}^{\text{standard}} \times (1 + \xi \ln\gamma)
	\end{equation}
	
	\textbf{Particle Accelerators:}
	In collisions with $\gamma > 1000$ (LHC):
	\begin{equation}
		\Delta\theta_{\text{LHC}} \approx \xi \times 90° \times \ln(1000) \approx 0.09°
	\end{equation}
	
	\textbf{Cosmological Distances:}
	Galaxies at $z \sim 1$ should show apparent rotation of:
	\begin{equation}
		\theta_{\text{gal}} = \xi \times 180° \times \ln(1+z) \approx 0.05°
	\end{equation}
	measurable with JWST/ELT.
	\section{Cosmology Without Expansion}
	
	T0 Postulate NO cosmic Expansion, similar to Steady-State Modelle \cite{hoyle1948, bondi1948} and modern alternatives \cite{lopez2010, lerner2014}.
	
	\subsection{Redshift Through Time Field Evolution}
	
	Redshift arises through Frequenz-dependent shifts:
	\begin{equation}
		z = \xi \ln\left(\frac{T(t_{\text{beob}})}{T(t_{\text{emit}})}\right)
	\end{equation}
	
	This resembles "Tired Light" theories \cite{zwicky1929}, but avoids their problems through coherent Zeit Feld evolution.
	
	\subsection{CMB Without Inflation}
	
	CMB Temperatur fluctuations arise from Quanten fluctuations in the Zeit Feld, without inflationary Expansion \cite{pascher2025cmb}:
	\begin{equation}
		\frac{\delta T}{T} = \xi \sqrt{\frac{\hbar}{m_{\text{Planck}}c^2}} \approx 10^{-5}
	\end{equation}
	
	This solves the Horizont problem without inflation, similar to Variable Speed of Light theories \cite{albrecht1999, barrow1999}.
	
	\section{Experimentell Evidence}
	
	\subsection{High-Energy Physics}
	\begin{itemize}
		\item LHC Jet Quenching: $R_{AA} = 0.35 \pm 0.02$ with T0 Korrektur \cite{cms2024, alice2023}
		\item Top Quark Mass: $m_t = 172.52 \pm 0.33$ GeV \cite{cms2023top}
		\item Higgs Couplings: Precision $< 5\%$ \cite{atlas2023higgs}
	\end{itemize}
	
	\subsection{Cosmological Tests}
	\begin{itemize}
		\item Surface Brightness: $\mu \propto (1+z)^{-0.001\pm0.3}$ stattdessen of $(1+z)^{-4}$ \cite{lerner2014}
		\item Angular Sizes: Nearly Konstante at high $z$ \cite{lopez2010}
		\item BAO Scale: $r_d = 147.8$ Mpc without CMB priors \cite{desi2025}
	\end{itemize}
	
	\subsection{Precision Tests}
	\begin{itemize}
		\item Atom Interferometry: $\Delta\phi/\phi \approx 5 \times 10^{-15}$ erwartet \cite{kasevich2023}
		\item Optical Clocks: Relative drift $\sim 10^{-19}$ \cite{ludlow2015, brewer2019}
		\item Gravitational Waves: LISA sensitivity to $\xi$-modulation \cite{lisa2017}
	\end{itemize}
	
	\section{Theoretical Connections}
	
	T0 has connections to:
	\begin{itemize}
		\item Loop Quantum Gravity \cite{rovelli2004, ashtekar2004}
		\item String Theorie/M-Theorie \cite{polchinski1998, becker2007}
		\item Emergent Gravity \cite{verlinde2011, jacobson1995}
		\item Fractal Spacetime \cite{nottale1993, elnaschie2004}
		\item Information-Theoretic Approaches \cite{susskind1995, maldacena1998}
	\end{itemize}
	
	\section{Schlussfolgerung}
	
	Mass variation is the geometrisch dual of Zeit dilation in T0 – rigorously equivalent and ontologically unified. The theoretically exakt Parameter $\xi = 4/3 \times 10^{-4}$ determines alle natural Konstanten. T0 explains the Terrell-Penrose Effekt, Myon g-2 Anomalie, and kosmologisch Beobachtungen without Expansion. This addresses historical critiques \cite{hundert1931, dingle1972} and modern challenges \cite{riess2022, divalentino2021}. 
	
	Future tests include:
	\begin{itemize}
		\item Improved Terrell-Penrose Messungen
		\item Precision Myon g-2 with $< 20 \times 10^{-11}$ Unschärfe
		\item Gravitational Welle astronomy with LISA/Einstein Telescope
		\item Next-generation Atom interferometry
	\end{itemize}
	

\input{../../T0_bibliography}
\end{document}
