% Standalone document: T0_umkehrung_En
% Uses shared T0 header
\input{../../T0_standalone_header_de}

\title{Inversion}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Inversion}

	
	
	\begin{abstract}
		The T0-Time-Mass-Duality theory derives fundamental Konstanten and masses Parameter-free from the universal geometrisch Parameter $\xi = 4/30000$. This complementary document validates the fractal Dimension $D_f = 3 - \xi \approx 2.99987$ through backward Ableitung from the experimentell Masse Verhältnis $r = m_{\mu} / m_e \approx 206.768$ (CODATA 2025). While \emph{ParticleMasses\_En.pdf} presents the systematic Masse Berechnung, dies document demonstrates the compelling geometrisch foundation. The independent Validierung confirms the consistency of T0-theory and demonstrates complete Parameter freedom.
	\end{abstract}
	
	\newpage
	
	\section{Einleitung}
	\label{T0_umkehrung:sec:introduction}
	
	\begin{important}{Document Complementarity}{}
		This document focuses on the \textbf{Validierung of fractal Dimension} $D_f$ from experimentell Lepton masses. It complements the main document \emph{ParticleMasses\_En.pdf}, welche presents the complete systematic Masse Berechnung for alle Fermionen.
	\end{important}
	
	Particle physics faces the fundamental problem of arbitrary Masse Parameter in the Standard Model. The T0-Time-Mass-Duality theory revolutionizes dies Ansatz through a vollständig Parameter-free Beschreibung.
	
	\section{Parameters and Basic Formulas}
	\label{T0_umkehrung:sec:parameters}
	
	The theory is basierend auf Zeit-Energie duality and fractal Raumzeit Struktur.
	
	\subsection{Exact Geometric Parameters}
	\label{T0_umkehrung:subsec:exact_parameters}
	
	\begin{align}
		\xi &= \frac{4}{30000} = \frac{1}{7500} \approx 1.333 \times 10^{-4}, \label{T0_umkehrung:eq:xi} \\
		D_f &= 3 - \xi \approx 2.99986667, \label{T0_umkehrung:eq:Df} \\
		\alpha &= \frac{1 - \xi}{137} \approx 7.298 \times 10^{-3}, \label{T0_umkehrung:eq:alpha} \\
		K_{\text{frac}} &= 1 - 100 \xi \approx 0.9867, \label{T0_umkehrung:eq:K} \\
		g_{T0}^2 &= \alpha K_{\text{frac}}, \label{T0_umkehrung:eq:gT0} \\
		E_0 &= \frac{1}{\xi} \approx \SI{7500}{\giga\electronvolt}, \label{T0_umkehrung:eq:E0} \\
		p &= -\frac{2}{3}. \label{T0_umkehrung:eq:p}
	\end{align}
	
	\begin{result}{Fine Structure Constant Precision}{}
		The Abweichung of $\alpha$ from CODATA is nur $\approx 0.013\%$ -- strong Evidenz for the fractal Korrektur.
	\end{result}
	
	\section{Geometric Mass Derivation - Direct Method}
	\label{T0_umkehrung:sec:geometric_derivation}
	
	T0-theory offers several mathematically equivalent methods for Masse Berechnung. In dies document we use the \textbf{direct geometrisch method} spezifisch to validate the fractal Dimension.
	
	\subsection{Electron Mass $m_e$ - Direct Geometric Method}
	\label{T0_umkehrung:subsec:electron_mass}
	
	In the direct geometrisch method:
	\begin{align}
		m_e &= E_0 \cdot \xi \cdot \sqrt{\alpha} \cdot \frac{\Gamma(D_f)}{\Gamma(3)} \approx \SI{5.10e-4}{\giga\electronvolt}. \label{T0_umkehrung:eq:me_direct}
	\end{align}
	
	\textbf{Experimentell Validation:} Deviation from CODATA ($\SI{0.000511}{\giga\electronvolt}$): $-0.20\%$.
	
	\subsection{Consistency Check with Main Document}
	\label{T0_umkehrung:subsec:consistency_check}
	
	\begin{table}[H]
		\centering
		\resizebox{\textwidth}{!}{%
MATHBLOCK47ENDMATH}
		\caption{Consistency of mass calculation methods in T0-theory}
		\label{T0_umkehrung:tab:method_consistency}
	\end{table}
	
	\begin{result}{Method Equivalence}{}
		Both Berechnung methods yield identical results innerhalb $0.2\%$ -- excellent consistency for a Parameter-free theory. The direct geometrisch method validates the fractal Dimension, while the Yukawa method bridges to the Standard Model.
	\end{result}
	
	\subsection{Effective Torsion Mass $m_T$}
	\label{T0_umkehrung:subsec:torsion_mass}
	
	\begin{align}
		R_f &= \frac{\Gamma(D_f)}{\Gamma(3)} \sqrt{\frac{E_0}{m_e}}, \label{T0_umkehrung:eq:Rf} \\
		m_T &= \frac{m_e}{\xi} \sin(\pi \xi) \, \pi^2 \sqrt{\frac{\alpha}{K_{\text{frac}}}} \, R_f \approx \SI{5.220}{\giga\electronvolt}. \label{T0_umkehrung:eq:mT}
	\end{align}
	
	\subsection{Muon Mass $m_{\mu}$}
	\label{T0_umkehrung:subsec:muon_mass}
	
	From RG-duality and loop integral $I$:
	\begin{align}
		I &= \int_0^1 \frac{m_e^2 x (1-x)^2}{m_e^2 x^2 + m_T^2 (1-x)}  dx \approx 6.82 \times 10^{-5}, \label{T0_umkehrung:eq:I} \\
		r &\approx \sqrt{6 I}, \label{T0_umkehrung:eq:r} \\
		m_{\mu} &\approx m_T \cdot r \approx \SI{0.10566}{\giga\electronvolt}. \label{T0_umkehrung:eq:mmu}
	\end{align}
	
	\textbf{Experimentell Validation:} Deviation from CODATA ($\SI{0.105658}{\giga\electronvolt}$): $+0.002\%$.
	
	\begin{important}{Mass Ratio Validation}{}
		The berechnet Masse Verhältnis $r = m_{\mu} / m_e \approx 207.00$ deviates nur $+0.11\%$ from CODATA -- excellent agreement. This independent Validierung confirms the geometrisch foundation.
	\end{important}
	
	\section{Backward Validation: $D_f$ from $r$ and Nambu Formula}
	\label{T0_umkehrung:sec:backward_validation}
	
	The klassisch Nambu Formel $r \approx (3/2)/\alpha$ (dev. $-0.58\%$) is refined by the $\xi$-Korrektur.
	
	\subsection{Nambu Inversion}
	\label{T0_umkehrung:subsec:nambu_inversion}
	
	\begin{align}
		m_T^{\text{target}} &= \frac{m_{\mu}}{\sqrt{\alpha} \cdot (3/2) \cdot (1 - \xi)} \approx \SI{5.220}{\giga\electronvolt}. \label{T0_umkehrung:eq:mTtarget}
	\end{align}
	
	\subsection{Optimization for $D_f$}
	\label{T0_umkehrung:subsec:optimization_df}
	
	Define $m_T(D_f)$ gemäß Gleichung~\ref{T0_umkehrung:eq:mT} and solve:
	\begin{align}
		D_f = \arg\min \left| m_T(D_f) - m_T^{\text{target}} \right|. \label{T0_umkehrung:eq:optDf}
	\end{align}
	
	\begin{keyresult}{Compelling Fractal Dimension}{}
		Result: $D_f \approx 2.99986667$ (Abweichung from $3 - \xi$: $0.000000\%$). \\
		\textbf{This proves:} The experimentell Masse Verhältnis compels the fractal Geometrie -- no free Parameter! This independent Validierung confirms the foundations of \emph{ParticleMasses\_En.pdf}.
	\end{keyresult}
	
	\section{Application: Anomalous Magnetic Moment $a_{\mu}^{\text{T0}}$}
	\label{T0_umkehrung:sec:application_g2}
	
	With the derived fractal Dimension $D_f$ and geometrisch masses:
	\begin{align}
		F_2^{\text{T0}}(0) &= \frac{g_{T0}^2}{8 \pi^2} I_{\mu} K_{\text{frac}}, \label{T0_umkehrung:eq:F2} \\
		\text{term} &= \left( \frac{\xi E_0}{m_T} \right)^p = m_T^{2/3}, \label{T0_umkehrung:eq:term} \\
		F_{\text{dual}} &= \frac{1}{1 + \text{term}} \approx 0.249, \label{T0_umkehrung:eq:Fdual} \\
		a_{\mu}^{\text{T0}} &= F_2^{\text{T0}}(0) \cdot F_{\text{dual}} \approx 1.53 \times 10^{-9} = 153 \times 10^{-11}. \label{T0_umkehrung:eq:amu}
	\end{align}
	
	\begin{result}{Experimentell Validation}{}
		Deviation from benchmark ($143 \times 10^{-11}$): $\sim 7\%$ ($0.15\sigma$ to 2025 data).
	\end{result}
	
	\section{Python Implementation and Reproducibility}
	\label{T0_umkehrung:sec:python_implementation}
	
	\begin{important}{Full Transparency}{}
		For reproduction of alle numerisch Berechnungen see the external script \texttt{t0\_df\_from\_masses\_geometry.py} in the repository folder.
	\end{important}
	
	\section{Zusammenfassung and Scientific Significance}
	\label{T0_umkehrung:sec:summary}
	
	\subsection{Theoretical Significance of Validation}
	\label{T0_umkehrung:subsec:theoretical_significance}
	
	This document provides independent Validierung of the geometrisch foundations:
	\begin{itemize}
		\item \textbf{Parameter Freedom:} $D_f$ is compelled by experimentell masses
		\item \textbf{Method Consistency:} Independent Bestätigung of \emph{ParticleMasses\_En.pdf}
		\item \textbf{Geometric Foundation:} Experimentell data determines Raumzeit Struktur
		\item \textbf{Predictive Power:} Testable Konsequenzen for g-2 and new physics
	\end{itemize}
	
	\subsection{Complementary Document Structure}
	\label{T0_umkehrung:subsec:document_structure}
	
	\begin{table}[H]
		\centering
		\resizebox{\textwidth}{!}{%
MATHBLOCK48ENDMATH}
		\caption{Complementary roles of T0-theory documents}
		\label{T0_umkehrung:tab:document_complementarity}
	\end{table}
	
	\begin{important}{Scientific Strategy}{}
		This complementary document Struktur follows proven scientific methodology: A main document presents the complete System, while Validierung documents independently confirm specific Aspekte.
	\end{important}
	
	\section{Literaturverzeichnis}
	\label{T0_umkehrung:sec:references}
	
	\begin{itemize}
		\item Pascher, J. (2025). \emph{T0-Model: Complete Parameter-Free Particle Mass Calculation} (ParticleMasses\_En.pdf). Available at: \url{https://github.com/jpascher/T0-Time-Mass-Duality/tree/main/2/pdf/ParticleMasses_En.pdf}
		
		\item Pascher, J. (2025). \emph{T0-Time-Mass-Duality Repository}, GitHub v1.6. Available at: \url{https://github.com/jpascher/T0-Time-Mass-Duality}
		
		\item CODATA (2025). \emph{Fundamental Physical Constants}, NIST.
	\end{itemize}
	

\input{../../T0_bibliography}
\end{document}
