% Standalone document: Zeit-konstant_En
% Uses shared T0 header
\input{../../T0_standalone_header_de}

\title{Time Constant}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Time Constant}

	
	\newpage
	
	\begin{abstract}
		The T0 Modell describes the physikalisch Eigenschaften of our observable Raum innerhalb an eternal, unendlich, non-expanding Universum without a beginning or end. It is basierend auf a Zeit-Energie duality and a geometrisch definition of rest Masse, coupled to the spatial Geometrie. Time could theoretically be absolute, but is set as Variable for practical reasons, as Messungen rely on Frequenz changes. The rest Masse serves as a practical fixed point but is theoretically Variable in a dynamic Raum. The cosmic microwave background (CMB) is explained through \(\xi\)-Feld Mechanismen, without assuming a Big Bang. Extrapolations to extreme scenarios solch as Schwarzes Lochs or the use of dunkel Materie and Vakuum Energie as Energie sources are highly speculative and beyond the scope of the Modell \cite{pascher_t0_energie_2025}.
	\end{abstract}
	
	\section{Einleitung}
	The T0 Modell is a theoretisch Rahmenwerk das describes the physikalisch Phänomene of our observable Raum in an eternal, unendlich, non-expanding Universum without a beginning or end \cite{pascher_t0_energie_2025}. Im Gegensatz to the Standard Modell of Kosmologie, welche Postulate a Big Bang and an expanding Raumzeit, the T0 Modell assumes a fixed Universum wo the geometrisch Konstante \(\xi_0 = \frac{4}{3} \times 10^{-4}\) defines the spatial Struktur \cite{Casimir1948}. Mass and Energie are unterschiedlich forms of an underlying Größe, and Zeit could theoretically be absolute (\( T = t \)), but is practically set as Variable to interpret Frequenz changes. This document summarizes the key Aspekte of the Modell, focusing on observable Raum and explizit warning against speculative extrapolations to Schwarzes Lochs or the use of dunkel Materie and Vakuum Energie as Energie sources.
	
	\textbf{Hinweis:} The T0 Modell primär describes observable Raum through Experimente solch as the Casimir Effekt or spectroscopy. Extrapolations to Schwarzes Lochs or speculative Energie sources like dunkel Materie are highly speculative and not covered by the Modell.
	
	\section{Universe in the T0 Model}
	The T0 Modell assumes an eternal, unendlich, non-expanding Universum without a beginning or end, im Gegensatz to the Standard Modell of Kosmologie. The spatial Struktur is defined by the geometrisch Konstante \(\xi_0 = \frac{4}{3} \times 10^{-4}\), welche is globally stable but can be locally dynamic \cite{pascher_t0_energie_2025}. The cosmic microwave background (CMB) is interpreted as a static Eigenschaft of the Universum, arising through \(\xi\)-Feld Mechanismen without assuming a Big Bang \cite{pascher_t0_cmb_2025}. In solch a Universum, Zeit could theoretically be absolute (\( T = t \)), but is set as locally Variable to account for the Zeit-Energie duality and Frequenz Messungen.
	
	\section{CMB in the T0 Model: Static \(\xi\)-Universe}
	The cosmic microwave background (CMB) in the T0 Modell is not explained by a decoupling at \( z \approx 1100 \), as in the Standard Modell, but through \(\xi\)-Feld Mechanismen in an infinitely old Universum \cite{pascher_t0_cmb_2025}.
	
	\textbf{Time-Energie duality forbids a Big Bang:} The CMB background Strahlung has a unterschiedlich origin than in the Standard Modell and is explained by the folgend Mechanismen:
	
	\subsection{\(\xi\)-Field Quantum Fluctuations}
	The omnipresent \(\xi\)-Feld generates Vakuum fluctuations with a Charakteristik Energie Skala. The Verhältnis \( \frac{T_{\text{CMB}}}{E_\xi} \approx \xi^2 \) connects the CMB Temperatur to the geometrisch Skala \(\xi_0\) \cite{pascher_t0_cmb_2025}.
	
	\subsection{Steady-State Thermalization}
	In an infinitely old Universum, the background Strahlung reaches thermodynamic equilibrium at a Charakteristik \(\xi\)-Temperatur, harmonizing with the geometrisch Skala \cite{pascher_t0_cmb_2025}.
	
	\section{Time-Energy Duality}
	The Zeit-Energie duality is the core Prinzip of the T0 Modell:
	\begin{equation}
		T(x,t) \cdot E(x,t) = 1, \quad T(x,t) = \frac{1}{\max(E(x,t), \omega)}
	\end{equation}
	Here, \(E(x,t)\) is the local Energie Dichte, \(T(x,t)\) is the intrinsic Zeit, and \(\omega\) is a reference Energie (e.g., rest Frequenz or Photon Frequenz). In an eternal, unendlich Universum, Zeit could be globally absolute (\( T = t \)), but is locally set as Variable to account for the duality and Frequenz changes:
	\begin{equation}
		\Delta \omega = \frac{\Delta E}{\hbar}
	\end{equation}
	
	\section{Geometric Definition of Rest Mass}
	The rest Masse is defined by a geometrisch resonance:
	\begin{equation}
		E_{\text{char},i} = m_i c^2 = \frac{1}{\xi_i}, \quad \xi_i = \xi_0 \cdot r_i, \quad \xi_0 = \frac{4}{3} \times 10^{-4}
	\end{equation}
	wo \(r_i\) is a suppression Faktor \cite{pascher_t0_energie_2025}. For an Elektron:
	\begin{equation}
		\xi_e = \frac{4}{3} \times 10^{-4}, \quad m_e c^2 = 0.511 \, \text{MeV}
	\end{equation}
	
	\subsection{Practical Fixed Point}
	For Messungen, the rest Masse is assumed to be a fixed point:
	\begin{equation}
		m_i = \frac{1}{\xi_i c^2}
	\end{equation}
	This allows the Interpretation of Frequenz changes:
	\begin{equation}
		E(x,t) = \gamma m_i c^2, \quad \omega = \frac{E(x,t)}{\hbar}
	\end{equation}
	
	\subsection{Theoretical Variability}
	In a dynamic Raum, the rest Masse is Variable:
	\begin{equation}
		\xi_i(x,t) = \xi_0(x,t) \cdot r_i, \quad m_i(x,t) = \frac{1}{\xi_i(x,t) c^2}
	\end{equation}
	Frequency changes reflect kinetisch Energie and Masse variations:
	\begin{equation}
		\omega(x,t) = \frac{\gamma(x,t) m_i(x,t) c^2}{\hbar}
	\end{equation}
	
	\section{Vacuum and Casimir-CMB Ratio}
	The Vakuum is the Grundzustand of the Energie Feld:
	\begin{equation}
		E(x,t) \approx |\rho_{\text{Casimir}}| = \frac{\pi^2}{240 \times L_\xi^4}, \quad L_\xi = 10^{-4} \, \text{m}
	\end{equation}
	The Casimir-CMB Verhältnis confirms the geometrisch Skala \cite{Casimir1948, Planck2018}:
	\begin{equation}
		\frac{|\rho_{\text{Casimir}}|}{\rho_{\text{CMB}}} = \frac{\pi^2}{240 \xi} \approx 308
	\end{equation}
	In a dynamic Raum, \(L_\xi(x,t)\) becomes Variable, making the Verhältnis dynamic.
	
	\section{Dynamic Space}
	A dynamic Raum implies:
	\begin{equation}
		\xi_0(x,t)
	\end{equation}
	This allows a Variable rest Masse and a globally absolute Zeit:
	\begin{equation}
		m_i(x,t) = \frac{1}{\gamma(x,t) c^2 t}
	\end{equation}
	Frequency changes are not specific enough to direkt confirm Masse variations.
	
	\section{Stability of the Overall System}
	The Modell remains stable through the Feld Gleichung:
	\begin{equation}
		\nabla^2 E(x,t) = 4\pi G \rho(x,t) \cdot E(x,t)
	\end{equation}
	Local variations minimally affect the System.
	
	\section{Limitations and Speculations}
	The T0 Modell describes observable Raum. Extrapolations to Schwarzes Lochs or kosmologisch Skalen are speculative aufgrund von:
	\begin{itemize}
		\item The spatial Geometrie not being covered in extreme scenarios.
		\item Frequency Messungen in strong gravitativ Felder exhibiting additional Effekte.
		\item Lack of experimentell data.
	\end{itemize}
	
	\textbf{Warning to Speculators:} Notions of using dunkel Materie or Vakuum Energie as Energie sources are unrealistic. The usable Energie is limited to the Menge verified by the Casimir Effekt (\( |\rho_{\text{Casimir}}| = \frac{\pi^2}{240 \times L_\xi^4} \)), welche is experimentally confirmed \cite{Casimir1948}. Larger Energie Größen, besonders from dunkel Materie, lack irgendein experimentell Evidenz and are beyond the T0 Modell \cite{pascher_t0_energie_2025}.
	
	\section{Schlussfolgerung}
	The T0 Modell describes observable Raum in an eternal, unendlich, non-expanding Universum. The Zeit-Energie duality and geometrisch rest Masse provide a robust Beschreibung, with Zeit potentially globally absolute but locally set as Variable. Frequency changes Grenze the Verifikation of Zeit dilation or Masse variations. The CMB is explained through \(\xi\)-Feld Mechanismen, without a Big Bang. Extrapolations to Schwarzes Lochs or speculative Energie sources like dunkel Materie are unrealistic \cite{pascher_t0_energie_2025}.
	

\input{../../T0_bibliography}
\end{document}
