% R62 — Register entry for Doc. 190 (correction register, append-only)
% To be inserted as the next table row after R61.
% Author: Johann Pascher, 23 July 2026

 R62 & 005 \S{}Baryon worked example (proton) \newline (cf.\ R50, P35) &
   The printed proton calculation
   $m_p = m_\mu \cdot K_\text{corr} \cdot QZ \cdot RG \cdot D_\text{baryon} \cdot f_\text{NN}$
   with the printed values $0.105658 \cdot 0.985 \cdot 0.532 \cdot 1.00007 \cdot 0.363 \cdot 1.00002$
   yields $0.0201$~GeV, not the stated result $0.9381$~GeV
   (missing factor $46.672$). The formula line is moreover dimensionally
   open ($m_\mu$ in GeV, $D_\text{baryon}$ in GeV $\Rightarrow$ GeV$^2$). &
   \textbf{The anchor of the formula line is $\pi^2/2$, not $m_\mu$.}
   \emph{(i) Diagnosis.} The missing factor identifies the error as a
   single symbol: $(\pi^2/2)/m_\mu = 46.705$ hits the missing factor to
   $0.07\,\%$. \emph{(ii) Repair.} With
   $m_p = (\pi^2/2)\cdot K_\text{corr}\cdot QZ\cdot RG\cdot
   D_\text{baryon}\cdot f_\text{NN}$ --- $\pi^2/2$ dimensionless,
   $D_\text{baryon}$ (contains $0.5\,\Lambda_\text{QCD}$) the sole
   dimensionful carrier --- the dimensional balance closes, and the
   \emph{unchanged} printed values give $0.93878$~GeV against PDG
   $0.93827$ ($\Delta = +0.05\,\%$) resp.\ against the printed result
   $0.93810$ ($\Delta = +0.07\,\%$). The printed values were internally
   consistent with the $\pi^2/2$ anchor; only the symbol $m_\mu$ in the
   formula line was erroneous. \emph{(iii) Structural note.}
   $\pi^2/2 = \text{Vol}(B^4)$ is T$^4$-native;
   $(\pi^2/2)\cdot(16/\pi^2) = 8$ links the anchor to the reciprocal of
   the D4 packing density (A270). Further structure (the split
   $QZ\cdot K_\text{corr}$ underdetermined; geometric candidate $\pi/6$
   for the product; $\pi^3/12$ link to the Higgs formula via the Weyl
   number 192) is kept independently in A155 \S{}Baryon Candidate.
   \emph{(iv) Secondary finding.} The printed value
   $K_\text{corr} = 0.985$ does not match the printed formula
   $K_\text{frak}^{D_f(1-(\xi/4)n_\text{eff})} = 0.9605$
   ($\Delta = 2.5\,\%$); the worked example closes only with $0.985$.
   Which value is correct is decided by the pending derivation.
   \emph{(v) Untouched.} $f_\text{NN}$ is an ML calibration factor
   (numerically $\approx 1$). The meson formula of Doc.~005 is not
   affected by this entry; self-contained A-series successors are A155
   (meson and baryon candidate) and A270 (sector structure).
   \emph{Verification script:} \texttt{python/Dok190\_Skripte/r62\_baryon\_anker.py}.
   \textbf{The source documents are not revised}
   (append-only; cf.\ R50). \emph{Declared 23~July 2026} \\
