\documentclass[11pt,a4paper,openany]{book}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[ngerman]{babel}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage[unicode,pdfencoding=auto]{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{siunitx}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{tikz}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{adjustbox}
\usepackage{xcolor}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\pagestyle{fancy}

\newcommand{\checkmarkx}{\checkmark}
\newcommand{\warningx}{\textbf{!}}

\title{T0 Zeit--Masse Dualität\\Vereinigtes Deutsches Buch}
\author{J. Pascher}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

%==============================
% Automatisch generierte Kapitel:

% Kapitel können hier eingefügt werden

%==============================
% Globales Literaturverzeichnis
\chapter*{Literaturverzeichnis}
\addcontentsline{toc}{chapter}{Literaturverzeichnis}
\begin{thebibliography}{99}
		
		\bibitem{pdg2024}
		Particle Data Group Collaboration (2024). 
		\textit{Review of Particle Physics}. 
		Progress of Theoretical and Experimental Physics, 2024(8), 083C01.
		\url{https://pdg.lbl.gov}
		
		\bibitem{flag2024}
		Aoki, Y., et al. (FLAG Collaboration) (2024). 
		\textit{FLAG Review 2024 of Lattice Results for Low-Energy Constants}. 
		arXiv:2411.04268.
		\url{https://arxiv.org/abs/2411.04268}
		
		\bibitem{fermilab_muon_g2}
		Abi, B., et al. (Muon g-2 Collaboration) (2021). 
		\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
		Physical Review Letters, 126, 141801.
		
		\bibitem{peskin_schroeder}
		Peskin, M. E., \& Schroeder, D. V. (1995). 
		\textit{An Introduction to Quantum Field Theory}. 
		Addison-Wesley.
		
		\bibitem{weinberg_qft}
		Weinberg, S. (1995). 
		\textit{The Quantum Theory of Fields, Vol. I--III}. 
		Cambridge University Press.
		
		\bibitem{griffiths_particle}
		Griffiths, D. (2008). 
		\textit{Introduction to Elementary Particles (2nd ed.)}. 
		Wiley-VCH.
		
\end{thebibliography}

\end{document}
