% Chapter 15
% Auto-reconstructed from FFGFT_Xi_Narrative_Master_En_print.pdf
% RAW source: 2\narrative\xi_En_chapters_raw\Kapitel_15_Xi_En_raw.txt
% English translation

\chapter{Sources and Further Reading}


This chapter lists the most important external sources cited in the Xi narrative and refers to supplementary T0 documents in the repository.

\section*{Bibliography}

\begin{description}
	\item[Modesto (2008)] L. Modesto, ``Fractal Structure of Loop Quantum Gravity,'' \textit{Class. Quantum Grav.} \textbf{26} (2009) 242002, arXiv:0812.2214 [gr-qc].
	
	\item[Modesto (2009)] L. Modesto, ``Fractal Quantum Space-Time,'' arXiv:0905.1665 [gr-qc].
	
	\item[Calcagni (2010)] G. Calcagni, ``Fractal universe and quantum gravity,'' \textit{Phys. Rev. Lett.} \textbf{104} (2010) 251301, arXiv:0912.3142 [hep-th].
	
	\item[Calcagni (2010b)] G. Calcagni, ``Quantum field theory, gravity and cosmology in a fractal universe,'' \textit{JHEP} \textbf{03} (2010) 120, arXiv:1001.0571 [hep-th].
	
	\item[Calcagni (2012)] G. Calcagni, ``Introduction to multifractional spacetimes,'' \textit{AIP Conf. Proc.} \textbf{1483} (2012) 31, arXiv:1209.1110 [hep-th].
	
	\item[Hořava (2009)] P. Hořava, ``Spectral Dimension of the Universe in Quantum Gravity at a Lifshitz Point,'' \textit{Phys. Rev. Lett.} \textbf{102} (2009) 161301, arXiv:0902.3657 [hep-th].
	
	\item[Thürigen (2015)] J. Thürigen, ``Discrete Quantum Geometries,'' arXiv:1511.08737 [gr-qc].
	
	\item[Jiang et al. (2024)] W.-C. Jiang, M.-C. Zhong, Y.-K. Fang, S. Donsa, I. Březinová, L.-Y. Peng, J. Burgdörfer, ``Time Delays as Attosecond Probe of Interelectronic Coherence and Entanglement,'' \textit{Phys. Rev. Lett.} \textbf{133} (2024) 163201, doi:10.1103/PhysRevLett.133.163201.
	
	\item[NASA Space News (2026)] NASA Space News, ``Scientists Measure Quantum Entanglement Speed – And It Breaks Physics,'' YouTube video, 14 January 2026, \href{https://www.youtube.com/watch?v=t3wjY95zvNM}{https://www.youtube.com/watch?v=t3wjY95zvNM} (accessed 15 January 2026).
	
	\item[Pascher (2026a)] J. Pascher, ``Fractal Spacetime and Its Implications in Quantum Gravity,'' internal T0 document \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/141_Renormierung_En.pdf}{141\_Renormierung\_En.pdf} (2026).
	
	\item[Pascher (2026b)] J. Pascher, ``Attosecond Prediction on the Generation of Quantum Entanglement as Evidence for the T0-Time-Mass-Duality Theory,'' internal T0 document \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/142_Experimet-verschränkung_En.pdf}{142\_Experimet-verschränkung\_En.pdf} (2026).
	
	\item[Pascher (2025a)] J. Pascher, ``T0 Particle Masses and Lepton Hierarchy,'' internal T0 document \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/006_T0_Teilchenmassen_En.pdf}{006\_T0\_Teilchenmassen\_En.pdf} (2025).
	
	\item[Pascher (2025b)] J. Pascher, ``Fine-Structure Constant and Fractal Geometry,'' internal T0 documents \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/044_Feinstrukturkonstante_En.pdf}{044\_Feinstrukturkonstante\_En.pdf} and \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/043_ResolvingTheConstantsAlfa_En.pdf}{043\_ResolvingTheConstantsAlfa\_En.pdf} (2025).
	
	\item[Pascher (2025c)] J. Pascher, ``Natural Units and Their Systematics,'' internal T0 document \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/015_NatEinheitenSystematik_En.pdf}{015\_NatEinheitenSystematik\_En.pdf} (2025).
	
	\item[Pascher (2025d)] J. Pascher, ``T0, Natural Units, and SI,'' internal T0 documents \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/014_T0_nat-si_En.pdf}{014\_T0\_nat-si\_En.pdf} and \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/013_T0_SI_En.pdf}{013\_T0\_SI\_En.pdf} (2025).
	
	\item[Pascher (2025e)] J. Pascher, ``T0 Cosmology and Fractal Geometry,'' internal T0 documents \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/026_T0_Geometrische_Kosmologie_En.pdf}{026\_T0\_Geometrische\_Kosmologie\_En.pdf} and \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/025_T0_Kosmologie_En.pdf}{025\_T0\_Kosmologie\_En.pdf} (2025).
\end{description}


