\chapter{\textbf{Ontological Hierarchy of Energy Reduction}

\section*{Abstract}
		This work examines the ontological hierarchy of T0 theory under the paradigm of natural units, where through time-mass duality $T \cdot m = 1$ all physical quantities can be reduced to energy. The central insight: There exist \textbf{five ontological levels of reduction}, ranging from the most fundamental (universal energy field) to observable physics. Each level emerges from the underlying one through mathematical necessity. The analysis shows: (1) \textbf{Level 0 -- Absolute Foundation}: The universal energy field $E_{\text{Field}}(x,t)$ with wave equation $\square E = 0$. (2) \textbf{Level 1 -- Time-Mass Duality}: $T(x,t) \cdot m(x,t) = 1$ in natural units. (3) \textbf{Level 2 -- Geometric Parameters}: $\xi = 4/30000$ and 4D torsion structure. (4) \textbf{Level 3 -- Effective Field Theory}: Modified laws with $\sim$1--2\% corrections. (5) \textbf{Level 4 -- SI Units Physics}: Classical observation level with $c, \hbar, G$ as separate constants. Narrative integration occurs through upward propagation: From the fundamental energy field emerges duality, from that geometry, from that effective laws, from that classical physics.

	\newpage
	
	\section{Introduction: The Reduction Program}
	
	\subsection{The Central Question}
	
	\begin{important}[Fundamental Question]
		If in natural units ($\hbar = c = 1$) through time-mass duality everything can be reduced to energy, which ontological levels exist, and how do they organize themselves hierarchically?
		
		Put differently: What are the \textbf{depths of reality} when we systematically descend from human conventions (SI units) to fundamental structures (energy field)?
	\end{important}
	
	\subsection{The Dimensional Reduction}
	
	In natural units:
	\begin{equation}
		\hbar = c = 1 \quad \Rightarrow \quad [L] = [T] = [E^{-1}], \quad [M] = [E]
	\end{equation}
	
	\textbf{Consequence}: All physical quantities are reduced to \textbf{one dimension} -- energy!
	
	\begin{table}[H]
		\centering
		\begin{tabular}{lcc}
			\toprule
			\textbf{Quantity} & \textbf{SI Units} & \textbf{Natural Units} \\
			\midrule
			Length & m & $E^{-1}$ \\
			Time & s & $E^{-1}$ \\
			Mass & kg & $E$ \\
			Temperature & K & $E$ \\
			Charge & C & dimensionless \\
			Energy & J & $E$ \\
			\bottomrule
		\end{tabular}
		\caption{Dimensional reduction in natural units}
	\end{table}
	
	\section{The Five Ontological Levels}
	
	\subsection{Hierarchy Overview}
	
	\begin{center}
		\begin{tikzpicture}[node distance=1.8cm]
			\tikzstyle{level} = [rectangle, rounded corners, minimum width=6cm, minimum height=1.2cm, draw, font=\small, align=center]
			
			\node[level, fill=gold!30] (L0) {\textbf{LEVEL 0: ABSOLUTE FOUNDATION}\\Universal Energy Field $E_{\text{Field}}(x,t)$};
			
			\node[level, fill=red!20, below of=L0] (L1) {\textbf{LEVEL 1: TIME-MASS DUALITY}\\$T(x,t) \cdot m(x,t) = 1$};
			
			\node[level, fill=orange!20, below of=L1] (L2) {\textbf{LEVEL 2: GEOMETRIC STRUCTURE}\\$\xi = 4/30000$, 4D Torsion Crystal};
			
			\node[level, fill=yellow!20, below of=L2] (L3) {\textbf{LEVEL 3: EFFECTIVE FIELD THEORY}\\Modified Laws, $\sim$1--2\% Corrections};
			
			\node[level, fill=green!20, below of=L3] (L4) {\textbf{LEVEL 4: SI UNITS PHYSICS}\\Classical Observation Level};
			
			\draw[->, ultra thick] (L0) -- (L1) node[midway, right, text width=2.5cm, font=\tiny] {Duality\\emerges};
			\draw[->, ultra thick] (L1) -- (L2) node[midway, right, text width=2.5cm, font=\tiny] {Geometry\\manifests};
			\draw[->, ultra thick] (L2) -- (L3) node[midway, right, text width=2.5cm, font=\tiny] {Effects\\scale};
			\draw[->, ultra thick] (L3) -- (L4) node[midway, right, text width=2.5cm, font=\tiny] {Conventions\\arise};
			
			\node[right of=L0, xshift=3.5cm, text width=3cm, font=\scriptsize] {\textcolor{gold!80!black}{\textbf{Purely ontological}}};
			\node[right of=L1, xshift=3.5cm, text width=3cm, font=\scriptsize] {\textcolor{red!80!black}{Fundamental\\Principle}};
			\node[right of=L2, xshift=3.5cm, text width=3cm, font=\scriptsize] {\textcolor{orange!80!black}{Structural\\Reality}};
			\node[right of=L3, xshift=3.5cm, text width=3cm, font=\scriptsize] {\textcolor{yellow!80!black}{Phenomenological}};
			\node[right of=L4, xshift=3.5cm, text width=3cm, font=\scriptsize] {\textcolor{green!50!black}{Conventional}};
		\end{tikzpicture}
	\end{center}
	
	\section{Level 0: The Absolute Foundation}
	
	\subsection{Ontological Description}
	
	\begin{keyresult}[The Most Fundamental Reality]
		\textbf{At the deepest level exists:}
		
		\begin{center}
			\Large A Universal Energy Field $E_{\text{Field}}(x,t)$
		\end{center}
		
		\vspace{0.3cm}
		
		This field is:
		\begin{itemize}
			\item \textbf{Non-dual}: No separation into space/time/mass
			\item \textbf{Self-evident}: Requires no further concepts
			\item \textbf{Dynamic}: Obeys the wave equation
			\item \textbf{Universal}: Permeates the entire universe
		\end{itemize}
	\end{keyresult}
	
	\subsection{The Fundamental Equation}
	
	\begin{equation}
		\boxed{\square E_{\text{Field}}(x,t) = 0}
	\end{equation}
	
	where $\square = \frac{\partial^2}{\partial t^2} - \nabla^2$ is the d'Alembert operator.
	
	\textbf{Physical meaning}:
	\begin{itemize}
		\item Energy propagates as wave
		\item No sources or sinks at fundamental level
		\item Completely deterministic
		\item Local in space and time
	\end{itemize}
	
	\subsection{Why is this fundamental?}
	
	\begin{philosophical}[Justification of Fundamentality]
		The energy field is fundamental because:
		
		\textbf{1. Minimal assumptions}:
		\begin{itemize}
			\item Only one field
			\item Only one equation
			\item No free parameters (in natural units)
		\end{itemize}
		
		\textbf{2. Maximal explanatory power}:
		\begin{itemize}
			\item All other concepts emerge from it
			\item Space = configuration space of the field
			\item Time = evolution of the field
			\item Mass = field excitation
		\end{itemize}
		
		\textbf{3. Mathematical elegance}:
		\begin{itemize}
			\item Linear (superposition valid)
			\item Lorentz invariant
			\item Energy conserving
		\end{itemize}
	\end{philosophical}
	
	\subsection{Ontological Status}
	
	\textbf{What exists}:
	\begin{itemize}
		\item The energy field $E_{\text{Field}}(x,t)$
		\item Its configuration at each time
		\item Its evolution dynamics
	\end{itemize}
	
	\textbf{What doesn't exist} (at this level):
	\begin{itemize}
		\item Separate time as independent entity
		\item Separate mass as substance
		\item Particles as fundamental objects
		\item Space as empty container
	\end{itemize}
	
	\section{Level 1: Time-Mass Duality}
	
	\subsection{Emergence of Duality}
	
	From the fundamental energy field emerges the first structuring:
	
	\begin{keyresult}[Time-Mass Duality]
		In natural units holds the fundamental relationship:
		
		\begin{equation}
			\boxed{T(x,t) \cdot m(x,t) = 1}
		\end{equation}
		
		This is equivalent to:
		\begin{equation}
			T(x,t) = \frac{1}{m(x,t)} = \frac{1}{E(x,t)}
		\end{equation}
	\end{keyresult}
	
	\subsection{Mathematical Derivation}
	
	From the Heisenberg uncertainty principle:
	\begin{equation}
		\Delta E \cdot \Delta t \geq \frac{\hbar}{2}
	\end{equation}
	
	In natural units ($\hbar = 1$):
	\begin{equation}
		\Delta E \cdot \Delta t \geq \frac{1}{2}
	\end{equation}
	
	In the limit $\Delta \to 0$:
	\begin{equation}
		E \cdot T = 1 \quad \Leftrightarrow \quad m \cdot T = 1
	\end{equation}
	
	\subsection{The Intrinsic Time Field}
	
	The duality manifests as a field:
	
	\begin{equation}
		\boxed{T(x,t) = \frac{1}{\max(m(x,t), \omega)}}
	\end{equation}
	
	\textbf{Dimensional verification}:
	\begin{align}
		[T(x,t)] &= [E^{-1}] \\
		[m(x,t)] &= [E] \\
		[T \cdot m] &= [E^{-1}] \cdot [E] = [1] \quad \checkmark
	\end{align}
	
	\subsection{Ontological Status}
	
	\textbf{At this level exist}:
	\begin{itemize}
		\item Time as \textbf{field quantity} $T(x,t)$ (not as parameter)
		\item Mass as \textbf{field quantity} $m(x,t)$ (not as substance)
		\item Their reciprocal relationship as \textbf{fundamental law}
	\end{itemize}
	
	\textbf{Physical meaning}:
	\begin{itemize}
		\item Time varies with energy: $T \propto 1/E$
		\item Mass varies with energy: $m \propto E$
		\item Both are \textbf{aspects of the energy field}
	\end{itemize}
	
	\subsection{Reduction to Energy}
	
	In natural units:
	\begin{align}
		E = m \quad &\text{(Energy = Mass)} \\
		E = \omega \quad &\text{(Energy = Frequency)} \\
		E = 1/T \quad &\text{(Energy = inverse time)} \\
		E = 1/L \quad &\text{(Energy = inverse length)}
	\end{align}
	
	\textbf{Everything is energy in various manifestations!}
	
	\section{Level 2: Geometric Structure}
	
	\subsection{Emergence of Geometry}
	
	From time-mass duality emerges geometric structure:
	
	\begin{keyresult}[Geometric Manifestation]
		The duality manifests geometrically as:
		
		\begin{itemize}
			\item \textbf{Parameter}: $\xi = \frac{4}{30000} = 1.333 \times 10^{-4}$
			\item \textbf{Structure}: 4D torsion crystal
			\item \textbf{Scale}: Sub-Planck granulation $\Lambda_0 = \xi \cdot \ell_P$
			\item \textbf{Symmetry}: Pentagonal breaking via golden ratio $\varphi$
		\end{itemize}
	\end{keyresult}
	
	\subsection{The Field Equation}
	
	The time-mass field obeys:
	
	\begin{equation}
		\boxed{\nabla^2 m(x,t) = 4\pi G \rho(x,t) \cdot m(x,t)}
	\end{equation}
	
	\textbf{Dimensional verification} (natural units):
	\begin{align}
		[\nabla^2 m] &= [E^2] \cdot [E] = [E^3] \\
		[4\pi G \rho m] &= [1] \cdot [E^{-2}] \cdot [E^4] \cdot [E] = [E^3] \quad \checkmark
	\end{align}
	
	\subsection{Geometric Parameters}
	
	From the field equation follow:
	
	\begin{align}
		\beta &= \frac{2Gm}{r} = \frac{2m}{r} \quad \text{(in nat. units with } G=1\text{)} \\
		\xi_{\text{geom}} &= 2\sqrt{G} \cdot m = 2m \quad \text{(geometric parameter)}
	\end{align}
	
	\subsection{The 4D Torsion Structure}
	
	\textbf{Topology}:
	\begin{equation}
		\mathcal{M}_{\text{fund}} = \mathbb{R}^3 \times S^1_{\text{comp}}
	\end{equation}
	
	where:
	\begin{itemize}
		\item $\mathbb{R}^3$ = observable 3D space
		\item $S^1_{\text{comp}}$ = compactified 4th dimension with radius $r_4 = \xi \cdot \ell_P$
	\end{itemize}
	
	\subsection{Ontological Status}
	
	\textbf{At this level exist}:
	\begin{itemize}
		\item Geometric structure as \textbf{emergent property} of duality
		\item Parameter $\xi$ as \textbf{manifestation} of 4D structure
		\item Torsion as \textbf{twisting} of compact dimension
	\end{itemize}
	
	\textbf{Not yet existent} (only higher levels):
	\begin{itemize}
		\item Separate constants $c, \hbar, G$
		\item Particles as distinct objects
		\item Classical trajectories
	\end{itemize}
	
	\section{Level 3: Effective Field Theory}
	
	\subsection{Emergence of Phenomenological Laws}
	
	From geometric structure emerge measurable effects:
	
	\begin{keyresult}[Effective Description]
		At measurable scales ($\ell \gg \Lambda_0$) we see:
		
		\begin{itemize}
			\item Modified force laws with $\xi$-corrections
			\item Fractal dimension $D_f = 3-\xi$
			\item Anomalous moments with $\sim$2\% deviation
			\item Geometric constant predictions
		\end{itemize}
	\end{keyresult}
	
	\subsection{Modified Laws}
	
	\textbf{Coulomb's law}:
	\begin{equation}
		F_{\text{Coulomb}} \propto \frac{1}{r^{1+\xi}} \approx \frac{1}{r^2} \left(1 - \xi \ln\frac{r}{\ell_P}\right)
	\end{equation}
	
	\textbf{Gravitational potential}:
	\begin{equation}
		\Phi(r) = -\frac{Gm}{r}(1 + \kappa r)
	\end{equation}
	
	\textbf{Fine structure constant}:
	\begin{equation}
		\alpha^{-1} = \pi^4 \cdot \sqrt{2} \approx 137.76
	\end{equation}
	
	\subsection{Correction Factors}
	
	Over many orders of magnitude, $\xi$ accumulates:
	
	\begin{equation}
		K_{\text{frak}} = 1 - 100\xi \approx 0.9867
	\end{equation}
	
	This leads to $\sim$1.33\% corrections in observables.
	
	\subsection{Ontological Status}
	
	\textbf{At this level exist}:
	\begin{itemize}
		\item Effective laws as \textbf{approximations} of geometry
		\item Measurable deviations from Standard Model
		\item Phenomenological parameters (not yet $c, \hbar, G$ separate)
	\end{itemize}
	
	\textbf{Characteristics}:
	\begin{itemize}
		\item \textbf{Not fundamental}, but practically relevant
		\item \textbf{Emergent} from deeper levels
		\item \textbf{Approximative} with defined accuracy
	\end{itemize}
	
	\section{Level 4: SI Units Physics}
	
	\subsection{Emergence of Conventions}
	
	From effective theory emerge human conventions:
	
	\begin{keyresult}[Conventional Physics]
		For practical purposes we introduce:
		
		\begin{itemize}
			\item Separate constants: $c = 299\,792\,458$ m/s, $\hbar = 1.055 \times 10^{-34}$ Js
			\item Separate units: Meter, kilogram, second
			\item Separate quantities: Energy $\neq$ mass $\neq$ time
		\end{itemize}
		
		\textbf{This is the level of human measurements!}
	\end{keyresult}
	
	\subsection{Back Translation}
	
	From natural to SI units:
	
	\begin{align}
		E \text{ (nat.)} &\to E \text{ (SI)} = E \cdot (\hbar c) \\
		m \text{ (nat.)} &\to m \text{ (SI)} = m \cdot \frac{\hbar}{c^2} \\
		T \text{ (nat.)} &\to T \text{ (SI)} = T \cdot \frac{\hbar}{c^2}
	\end{align}
	
	\subsection{Ontological Status}
	
	\textbf{At this level exist}:
	\begin{itemize}
		\item Human conventions as \textbf{measurement tools}
		\item Separate concepts for practical applications
		\item Classical approximations for everyday physics
	\end{itemize}
	
	\textbf{Characteristics}:
	\begin{itemize}
		\item \textbf{Not fundamental}, but conventional
		\item \textbf{Useful} for technology and experiments
		\item \textbf{Obscures} the deeper unity of physics
	\end{itemize}
	
	\section{Narrative Integration}
	
	\subsection{Bottom-Up: The Emergence Narrative}
	
	\begin{revolutionary}[The Story of Reality]
		\textbf{LEVEL 0 -- In the beginning was the field}:
		
		There exists a universal energy field $E_{\text{Field}}(x,t)$ that obeys the wave equation $\square E = 0$. Nothing else exists -- only this one field.
		
		\vspace{0.3cm}
		
		$\Downarrow$
		
		\vspace{0.3cm}
		
		\textbf{LEVEL 1 -- Duality emerges}:
		
		From the quantum nature of the field ($\Delta E \cdot \Delta t \geq \hbar/2$) emerges time-mass duality: $T \cdot m = 1$. Time is no longer parameter, but field!
		
		\vspace{0.3cm}
		
		$\Downarrow$
		
		\vspace{0.3cm}
		
		\textbf{LEVEL 2 -- Geometry manifests}:
		
		The duality manifests geometrically: 4D torsion crystal with parameter $\xi = 4/30000$, compact 4th dimension at sub-Planck scale.
		
		\vspace{0.3cm}
		
		$\Downarrow$
		
		\vspace{0.3cm}
		
		\textbf{LEVEL 3 -- Effects scale}:
		
		At measurable scales we see modified laws: Coulomb $\propto 1/r^{1+\xi}$, anomalous moments with $\sim$2\% deviation, geometric constants.
		
		\vspace{0.3cm}
		
		$\Downarrow$
		
		\vspace{0.3cm}
		
		\textbf{LEVEL 4 -- Conventions arise}:
		
		Humans introduce SI units: meter, kilogram, second. They artificially separate $c, \hbar, G$. The deeper unity is obscured.
	\end{revolutionary}
	
	\subsection{Top-Down: The Reduction Narrative}
	
	\begin{philosophical}[The Path to Fundamentality]
		\textbf{START: SI Physics (Level 4)}
		
		We begin with separate concepts: energy, mass, time, length. We have many constants: $c, \hbar, G, k_B, \ldots$
		
		\vspace{0.3cm}
		
		$\Downarrow$ \textit{Simplification}
		
		\vspace{0.3cm}
		
		\textbf{Natural Units (Level 3)}
		
		We set $c = \hbar = 1$. Suddenly: energy = mass, time = inverse energy. Everything becomes simpler!
		
		\vspace{0.3cm}
		
		$\Downarrow$ \textit{Deeper analysis}
		
		\vspace{0.3cm}
		
		\textbf{Geometric Structure (Level 2)}
		
		We recognize: The simplicity comes from 4D geometry. Parameter $\xi$ encodes everything. Torsion explains mass!
		
		\vspace{0.3cm}
		
		$\Downarrow$ \textit{Ultimate reduction}
		
		\vspace{0.3cm}
		
		\textbf{Time-Mass Duality (Level 1)}
		
		We understand: Time and mass are dual, $T \cdot m = 1$. Both are aspects of energy!
		
		\vspace{0.3cm}
		
		$\Downarrow$ \textit{Fundamental truth}
		
		\vspace{0.3cm}
		
		\textbf{Universal Energy Field (Level 0)}
		
		At the foundation: One field, one equation. Everything else emerges.
	\end{philosophical}
	
	\section{Comparison of Both Descriptions}
	
	\subsection{4D Torsion Crystal vs. Energy Reduction}
	
	\begin{table}[H]
		\centering
		\small
		\begin{tabular}{p{5cm}|p{5cm}}
			\toprule
			\textbf{4D Torsion Crystal (Level 2)} & \textbf{Energy Reduction (Level 0--1)} \\
			\midrule
			Geometric perspective & Field-theoretic perspective \\
			Intuitive: Twisting & Abstract: Duality \\
			4 dimensions topological & 1 dimension (energy) reductive \\
			Torsion as cause & Field excitation as cause \\
			Sub-Planck structure primary & Wave equation primary \\
			\midrule
			\multicolumn{2}{c}{\textbf{BOTH describe the same reality!}} \\
			\midrule
			Level 2 in hierarchy & Level 0--1 in hierarchy \\
			Emerges from Level 1 & Fundamental for Level 2 \\
			Geometrically manifest & Energetically fundamental \\
			\bottomrule
		\end{tabular}
		\caption{Complementary descriptions}
	\end{table}
	
	\subsection{Ontological Classification}
	
	\begin{keyresult}[How do both fit in?]
		\textbf{Energy Reduction (Level 0--1)}:
		\begin{itemize}
			\item \textbf{More fundamental} -- goes deeper
			\item \textbf{More abstract} -- less intuitive
			\item \textbf{More universal} -- holds without restrictions
		\end{itemize}
		
		\vspace{0.3cm}
		
		\textbf{4D Torsion Crystal (Level 2)}:
		\begin{itemize}
			\item \textbf{Emergent} -- follows from Level 1
			\item \textbf{More intuitive} -- geometrically visualizable
			\item \textbf{Structural} -- manifests duality
		\end{itemize}
		
		\vspace{0.3cm}
		
		\textbf{Relationship}:
		\begin{center}
			Energy Field (Level 0) $\xrightarrow{\text{creates}}$ Duality (Level 1) $\xrightarrow{\text{manifests}}$ Geometry (Level 2)
		\end{center}
	\end{keyresult}
	
	\subsection{Why Both Descriptions Coexist}
	
	\begin{philosophical}[Complementarity]
		Analogous to wave-particle duality in quantum mechanics:
		
		\textbf{Energy Reduction}:
		\begin{itemize}
			\item Like wave description
			\item Fundamental, but abstract
			\item Mathematically elegant
			\item Hard to visualize
		\end{itemize}
		
		\textbf{4D Geometry}:
		\begin{itemize}
			\item Like particle description
			\item Emergent, but intuitive
			\item Geometrically intuitive
			\item Practically useful
		\end{itemize}
		
		\vspace{0.3cm}
		
		\textbf{Both are valid}, describing different aspects of the same reality!
	\end{philosophical}
	
	\section{Practical Consequences}
	
	\subsection{For Calculations}
	
	\begin{important}[Which level to choose?]
		\textbf{Level 0--1 (Energy Reduction)}:
		\begin{itemize}
			\item Theoretical derivations
			\item Fundamental principles
			\item Symmetry arguments
			\item Conceptual clarity
		\end{itemize}
		
		\textbf{Level 2 (Geometry)}:
		\begin{itemize}
			\item Visual explanations
			\item Particle masses
			\item Structural predictions
			\item Narrative presentations
		\end{itemize}
		
		\textbf{Level 3 (Effective)}:
		\begin{itemize}
			\item Experimental predictions
			\item Comparison with data
			\item Phenomenology
		\end{itemize}
		
		\textbf{Level 4 (SI)}:
		\begin{itemize}
			\item Practical measurements
			\item Technology
			\item Everyday applications
		\end{itemize}
	\end{important}
	
	\subsection{For Communication}
	
	\begin{table}[H]
		\centering
		\begin{tabular}{lll}
			\toprule
			\textbf{Target Audience} & \textbf{Preferred Level} & \textbf{Reason} \\
			\midrule
			Laypeople & Level 4 (SI) & Familiar \\
			Students & Level 3 (Effective) & Learnable \\
			Physicists & Level 2 (Geometry) & Intuitive \\
			Theorists & Level 1 (Duality) & Fundamental \\
			Philosophers & Level 0 (Field) & Ontological \\
			\bottomrule
		\end{tabular}
		\caption{Level choice by target audience}
	\end{table}
	