\section{Use of AI Tools}

This document series was created with the assistance of AI tools. The
notice appears at the front, not in small print, and belongs as its own
section in every document of the series.

The division of labour is clear. The questions, the theoretical stipulations,
the geometric ideas, and all substantive decisions come from the author. The
AI tools are tools in the literal sense: they formulate, compute, check for
contradiction, create verification scripts, find inconsistencies between
documents, and translate between representations. They make no substantive
decisions and generate no theses.

This separation is not merely an attribution but is methodologically
essential. A language model generates plausible-sounding text even where
there is no substance -- exactly the type of error that the layer marking
of the following section is designed to counter. Therefore, throughout this
series: every computational statement has a verification script that can be
independently checked; every number has a tolerance standard; every
derivation step has a layer marker. What does not pass this test does not
appear as a result in the text.

Responsibility for content and errors rests entirely with the author.


\section{What Is Not Part of the A-Series}

Two areas are explicitly excluded.

\textbf{The cosmological sector.} The A-series does not include it. The
corresponding documents from the legacy corpus remain and retain their numbers,
but are not carried into the new structure. The reason is a difference in
standards: the geometric core derives results from $\xi$; the cosmological
sector works throughout with imported scales and declared calibrations. Mixing
both in one series would obscure precisely the separation that motivates the
new structure.

\textbf{Predictions beyond the fundamental quantities.} The only quantities
carried as predictions are those that follow directly from the apparatus and
at which the theory can fail: the tau mass, the $\xi$-order of the CHSH
deviation, the fractal dimension $D_f$, and the fundamental length $L_0$.
Everything else that appeared as a prediction in earlier documents appears
here as a structural statement, or not at all.

\section{Why a New Series}

The existing FFGFT document series grew historically. Its numbers follow the
order of creation, not the subject matter. Over roughly three years, more than
two hundred German-language documents accumulated -- individually comprehensible,
but collectively exhibiting four properties that harm the whole.

\textbf{First, reference decay.} A substantial portion of the early documents
is rarely cited by the later ones. The content has not become wrong, but it is
presented more completely and precisely elsewhere. The old number persists and
continues to be found.

\textbf{Second, corrections sit outside the texts.} A separate correction
register amends documents from the outside instead of modifying them; it records
corrections, refinements, and revisions as dated entries. A reader of a single
old document therefore reads the uncorrected state. The working rule of not
modifying older documents was methodologically correct -- it keeps the
development history honest -- but it shifts the burden onto the reader.

\textbf{Third, multiple coverage.} The mass sector appears in at least five
documents, the concept of time in seven, the information question in six. Each
of these presentations has its occasion, but there is no single place that says:
\emph{this} is the current state.

\textbf{Fourth, layers are typographically invisible.} A statement derived
from $\xi$, an algebraically proved translation, and a plausibility sketch
appear in the same typeface side by side. This is the most dangerous of the four
properties, because it inflates the theory's apparent claim.

\textbf{[STIPULATION]} The A-series addresses all four points with the same
measure: subject order instead of chronological order, corrections integrated
instead of appended, one topic in one place, layer status declared per
statement.

\section{Introductory Reading Before the A-Series}

A reader entering the A-series encounters stipulations, layer markers, and
geometric structures from A020 onward. Two documents in the legacy corpus
prepare for this -- in different ways.

\textbf{``The Journey'' (legacy corpus, popular science)} describes the T0
theory in everyday language -- with analogies, without formulas, without
requiring a physics background. A reader who reads it before A010 arrives
with a picture in mind: why a single number $\xi$ might suffice, what
time-mass duality means, what is different about this approach from
established theories.

\textbf{``FFGFT in Plain Language'' (legacy corpus, narrative-technical)} is
the narrative introduction to the Lagrangian core. It translates the central
Lagrangian formulations into accessible language -- using images from
acoustics (vibrating string, resonator, Pythagorean comma) that appear in
FFGFT itself as structural parallels, not arbitrary metaphors. Every
statement is anchored in the formal documents. A reader who wants to
understand how the theory computes before seeing the computations should
read this document.

Both documents are not part of the A-series and are not superseded by it.
They are independent and remain so.

\section{What the A-Series Is Not}

\textbf{[STIPULATION]} It is \emph{not} a revision in the sense of
reappraisal. Nothing is retracted that has not already been retracted in the
correction register. The content is the same; the order is new.

It does not physically replace the old documents. The legacy corpus is fully
preserved, unchanged, under its old numbers. It is the development history
and remains citable. The A-series is the version to read when one wants to
know what the theory claims -- not how it got there.

And it is not an abridgment. Where an old text is more detailed than the
corresponding A-section, the latter refers to it. What is to be lost is
redundancy, not substance.

\section{The Three Layers}

FFGFT has always had three methodological layers. What is new is that they
are marked in the A-series -- per statement, not per document.

\begin{description}
  \item[{[K]} Core.] Derived from the geometry and the single parameter $\xi$.
    Example: the Koide relation $Q = 2/3$ as operator condition $r = \sqrt{2}$;
    the non-closure of the recursion; $D_f = 3-\xi$.
  \item[{[B]} Bridge.] Algebraically proved translation between two
    representations. Example: the bijection $\mathcal{H} = L^2(T^4)\otimes
    \mathbb{C}^3$; the DFT diagonalisation of the $Z_3$ circulant. A bridge
    carries everything established on one side, and proves nothing that was
    not already there.
  \item[{[S]} Sketch.] Plausibility, analogy, candidate. Example: the
    neutrino sector; $N_0 \approx 38{.}6$; the fine value of the refraction
    strength $\delta$.
\end{description}

A fourth marker is added that is not a layer but a booking category:

\begin{description}
  \item[{[STIPULATION]}] Declared, not derived. Example: $\tilde T\cdot m = 1$;
    the choice of $T^4$; the numerical value $\xi = 4/30000$; the reference
    point $m_\mu/m_e$.
\end{description}

\textbf{[B]} The purpose of the markers is not modesty but testability. A
theory that names its stipulations can be measured by how few it needs. A
theory that conceals them cannot.

\section{The Tolerance Standard}

Every numerical statement in the A-series names the standard against which
it is tested. This is a consequence of an experience older than the theory:
a measuring instrument is always less capable than the reality it measures.
Exact agreement on the last digit is therefore neither achievable nor the goal.

\textbf{[STIPULATION]} Completeness in the A-series means: \emph{no residual
remains that exceeds the tolerances and can only be closed by a free parameter.}
A residual within the determination tolerance is not a deficiency but the
normal case. A residual that exceeds the tolerance is a statement -- and is
booked as such, not rounded away.

In practice: at every deviation, three quantities appear together -- the
value, the measurement precision of the comparison quantity, and the
determination tolerance of the theoretical quantity. Only the ratio of these
three decides whether a deviation is meaningful.

\section{Citation Policy}

\textbf{[STIPULATION]} The A-series carries no reference lists. The rule:

\textbf{Standard physics without source.} Textbook knowledge -- constants,
standard formulas, established results (Dirac equation, Casimir formula,
CHSH bound, Koide relation, Landauer principle) -- is used without citation.
Name references (Bell, Tsirelson, Weyl) are concept labels, not literature
references.

\textbf{Specific external measurements with inline source.} Where a concrete,
dated measurement by a third party with error bars is claimed, the source
appears in parentheses directly at the number.

\textbf{Own measurements with reference to the measurement protocol.}
Hardware runs and own measurement campaigns refer to raw data and evaluation
scripts in the corpus, so that the claim is independently verifiable.

\section{Structure and Numbering}

The series has four blocks.

\textbf{Block 0 (A010--A090): Foundation.} Stipulations, geometry, fractal
correction, recursion, time, Hilbert space, field theory, units, projection
chain. A reader who has worked through this block knows the apparatus
completely -- without a single result. Current documents: A010, A015, A020,
A030, A040, A050, A060, A070, A075, A080, A085, A090.

\textbf{Block 1 (A100--A190): Sectors.} Leptons, Koide relation,
$\theta = 2/9$, fine-structure constant, $g$-2, gravitation, gravitational
constant, quarks and neutrinos, Bell and hardware, information, Standard
Model. The results appear here, each referred back to the apparatus from
Block~0. Current documents: A100, A105, A110, A120, A130, A135, A138, A140,
A142, A145, A150, A160, A165, A180, A190.

\textbf{Block 2 (A200--A250): Methodology and assessment.} The distinction
of law, norm, and stipulation; the test quantities; the tolerance standard;
the open questions; the demarcation from external frameworks; the index.
Current documents: A200, A210, A220, A230, A240, A250.

\textbf{Block 3 (A260--): Extensions.} Topics without back-reference from
earlier blocks -- self-contained units that supplement the core but are not
embedded in the main flow. Current documents: A260 (Casimir effect), A261
(scale hierarchy), A262 ($c$-convention and $E=m$), A263 (Dirac complete),
A264 (asymmetry and CP), A265 (spectral shift and SI anchor), A266 (unit
test and SI back-computation), A267 ($\alpha=1$ as stipulation).

\textbf{Methodological status of Block~3.} A260--A264 and A265 are physics
result documents without back-reference from Block~0/1. A266 (unit test)
and A267 ($\alpha=1$ convention) are convention and methodology documents --
they contain computational tools, not new theoretical results. This does not
change their place in Block~3, but the reader should know that the claim
differs.

\textbf{[STIPULATION]} Numbers within blocks increase in steps of ten.
Intermediate numbers (A015, A075, A138, A142, etc.) are assigned when a
later document refers back to an earlier one and the ordering requires it.
A document without back-reference from the existing block goes to the end --
in Block~3, not as an intermediate number. That is the rule guiding the
decision: not the topic, but the reference.

\section{Sources}

Every A-document names in its closing section the old numbers whose content
it subsumes. This is not a reference list but a replacement declaration:
a reader who has read the A-document need not read the listed old documents
to know the current state.

The reverse direction -- from each old number to its A-successor -- is
collected in A250. There it is also recorded which entries of the correction
register are incorporated where, and which old documents deliberately have
no successor because their content is outdated or purely historical.

\section{Language Status}

The A-series is initially produced in German only. This is a deliberate
departure from the previous rule of keeping every change bilingual. The
reason is practical: the structure must settle first. An English version
is produced when a block is complete and stable -- then in one pass from the
finished German state, not change by change.

Until then, the bilingual legacy series remains the reference for external
correspondence.

\section{Symbol Glossary of the A-Series}

The following table explains the symbols used consistently throughout the
entire A-series. Symbols that appear only in a single document are introduced
there at their first occurrence.

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\setlength\tabcolsep{5pt}
\begin{tabular}{lp{10cm}}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
\multicolumn{2}{l}{\textit{Fundamental constants and parameters}} \\
$\xi = 4/30000$ & Geometric fundamental constant of FFGFT;
  $\xi = 4/3\times10^{-4}$ \\
$\ell_P$ & Planck length, $\ell_P = \sqrt{\hbar G/c^3}
  \approx 1{.}616\times10^{-35}\,$m \\
$\hbar$ & Reduced Planck constant \\
$c$ & Speed of light (in natural units: $c=1$) \\
$\alpha$ & Fine-structure constant, $\alpha\approx1/137{.}036$ \\
$\varphi$ & Golden ratio, $\varphi=(1+\sqrt5)/2\approx1{.}618$ \\
\midrule
\multicolumn{2}{l}{\textit{FFGFT-specific quantities}} \\
$D_f = 3-\xi$ & Fractal dimension of the FFGFT torus \\
$L_0 = \xi\cdot\ell_P$ & Minimal length scale (sub-Planck),
  $L_0\approx2{.}15\times10^{-39}\,$m \\
$L_T = \ell_P/\xi$ & Torus fundamental period, $L_T\approx7500\,\ell_P$ \\
$\tau_0 = \xi\cdot t_P$ & Minimal time scale; by $c=1$ the same quantity
  as $L_0$ in time dress (four-dress principle, A080) \\
$K_\text{frak} = 1-100\xi$ & Fractal correction factor,
  $K_\text{frak}\approx0{.}9867$ \\
$E_0 = \sqrt{m_e m_\mu}$ & Characteristic energy,
  $E_0\approx7{.}398\,$MeV \\
$\tilde T\cdot m = 1$ & Time-mass duality (stipulation); $\tilde T$ is the
  intrinsic time field \\
$v = 246\,$GeV & Higgs vacuum expectation value (energy unit) \\
\midrule
\multicolumn{2}{l}{\textit{Layer markers}} \\
\textbf{[STIPULATION]} & Axiom of the theory; not further derived \\
\textbf{[B]} & Bridge; algebraically proved \\
\textbf{[K]} & Core; numerically verified derivation \\
\textbf{[S]} & Sketch; plausible but not fully worked out \\
\midrule
\multicolumn{2}{l}{\textit{Mathematical structures}} \\
$T^4/\mathbb{Z}_3$ & Compact 4-torus with $\mathbb{Z}_3$ orbifold structure \\
$\mathcal{H} = L^2(T^4)\otimes\mathbb{C}^3$ & Hilbert space of the theory \\
$\pi_1(T^4)\cong\mathbb{Z}^4$ & First homotopy group of the 4-torus \\
$P_i = |\mathbf{e}_i\rangle\langle\mathbf{e}_i|$ & Projector onto mode $i$ \\
$\Phi = \sum_i m_i P_i$ & Mode operator (field operator) \\
\midrule
\multicolumn{2}{l}{\textit{Masses and ratios}} \\
$m_e, m_\mu, m_\tau$ & Electron, muon, tau mass \\
$m_i = r_i\cdot\xi^{p_i}\cdot v$ & FFGFT mass formula; $r_i\in\mathbb{Q}$
  rational prefactor, $p_i\in\mathbb{Q}$ exponent \\
$(n, l, j)$ & Quantum numbers: principal, angular momentum, spin \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Independent Documents of the Legacy Corpus}

\textbf{[STIPULATION]} The A-series subsumes 102 documents of the legacy corpus.
The remainder -- more than 200 numbers -- stands independently. This section lists
the main thematic groups of these independent documents, so the reader knows where
the legacy corpus ends and where the A-series begins. Complete mapping: A250.

\textbf{Cosmological sector (excluded, Dok.~036, 063, 064, 140 et al.).}
Hubble constant, cosmic microwave background, vacuum field at galactic scales,
$\Lambda_\text{cosmo}$. This sector is not wrong -- it is of a different ambition:
it works throughout with imported scales and calibrations that the A-series cannot
reproduce. Excluded, not superseded.

\textbf{Gauge sector and QFT extensions (Dok.~186, 192, 281 et al.).}
Complete Feynman rules, renormalisation group beyond $\xi$-corrections, Yang-Mills
formulation. These documents treat topics declared as open points in the A-series
(A190, A240). They remain independent because the projection mapping is still missing.

\textbf{IPI framework comparisons (Dok.~246, 251, 252, 265, 267, 269, 271, 272,
274, 283, 285, 294, 297, 299 et al.).} Structural comparisons with HLV
(Helix-Light-Vortex), RA/PMT, Dot Theory, SICC, and other works from the IPI
community. These documents are explicitly not FFGFT statements but comparison
documents: they investigate where external frameworks and FFGFT share points of
contact. The A-series takes over none of these comparisons (A240 names the contact
points without carrying them).

\textbf{Quantum hardware and photonic systems (Dok.~083--085, 161, 167,
173--176, 183 et al.).} Photonic chips in communications technology, quantum dots,
Shor's algorithm on photonic platforms, Google Willow analysis, Ising machines.
These documents apply FFGFT ideas to concrete hardware systems. The application is
independent and not back-anchored in the A-series core.

\textbf{Popular and narrative introductions (Dok.~002, 004, 185, 191 et al.).}
``The Journey'' (narrative introduction without formulas), FFGFT for communications
engineers, video scripts. These documents are deliberately not part of the A-series
-- they are the access point for readers without physics prerequisites and remain
so. They are not superseded; they are complementary.

\textbf{AI and consciousness (Dok.~100, 207 et al.).} T0 theory and consciousness;
consciousness and bridges. These documents treat a topic that does not appear in
the A-series. They are independent philosophical works, not an appendix to the
physics.

\textbf{Methodological and diagnostic documents (Dok.~241, 242, 244, 247, 248,
250, 262, 277, 281, 284, 287, 288, 303--305 et al.).} Hawking information paradox,
ratio vs.\ absolute-value pedagogy, document structure maps, embedding protocols.
These documents are working materials that arose during the development of the
corpus. They are important for following the development history, but are not part
of the canonical state.

\textbf{Physics extensions in the narrow sense (Dok.~021--024, 027--034,
037--040, 054--068, 075--081, 089, 095, 105, 114, 124, 129, 137, 145--170,
172, 178, 179, 182, 184, 187, 192, 206 et al.).} Earlier formulations of the mass
formula, alternative parametrisations, intermediate stages of the theory, individual
calculations that have been absorbed into A-documents or deliberately not taken over.
This block is the largest and most heterogeneous: it contains early correct
calculations alongside superseded approaches, independent side-lines alongside
already-subsumed substance. The correction register (Dok.~190) books the relevant
corrections; the A-documents name what they take over. What appears in neither the
register nor an A-document is historical record.


\section{Open Questions}

This section appears in every document of the A-series and names what the
document does \emph{not} accomplish. The rule is adopted from outside: a
completed step that does not name its residual silently claims jurisdiction
beyond what it has shown.

For this document, four points remain open.

\textbf{First, the series does not cover the entire corpus.} It orders the
geometric core, the unit and constant structure, and the fermion sector;
the gauge sector and the dynamic field theory remain in the legacy corpus,
as does the early cosmology sector excluded from the series (A240, A250).
The commitment to back every computational statement with a verification
script has not yet been fulfilled for the series as a whole.

\textbf{Second, the replacement claim is untested.} The blueprint assigns
each A-document a set of old numbers whose content it is to subsume. Whether
this assignment is complete -- whether nothing from the legacy corpus falls
through -- can only be decided at the finished index A250, not before. Until
then, ``supersedes'' is an intention, not a finding.

\textbf{Third, the boundary of the cosmological exclusion is not sharp.} The
exclusion is justified by a difference in standard, not by topic. At three
points -- the correction factor $K_\text{frak}$, the bridge constants, the
projection chain -- the legacy corpus historically carries cosmological
anchors. Whether these points remain valid without such anchors is an open
substantive question, not answered by the exclusion decision.

\textbf{Fourth, the tolerance standard is here only formulated, not applied.}
The demand to compare every numerical statement against measurement precision
and determination tolerance is easy to state. Whether it can be sustained
consistently is decided only where numbers appear -- that is, from A100 onward.

\section{Supersedes}

The correction register referred to is Dok.~190 (entries K1--K6, P1--P43,
R1--R56); the winding-number corrections are in Dok.~210.

This document subsumes the framework and overview sections of: Dok.~086
(document overview), Dok.~201 (FFGFT-all, outline section), Dok.~205
(narrative, framework sections). The narrative part of Dok.~205 remains
independently worth reading and is not superseded.
