\section{Why the Stipulations Come First}

\textbf{[STIPULATION]} This document stands at the beginning of the content
section because a theory is measured by the number and nature of its
stipulations, not by the number of its results.

FFGFT claims to derive the constants of the Standard Model from a single
dimensionless parameter. This claim is worth only as much as the list of
what is additionally assumed is short and open. If the list is concealed,
the one-parameter claim is worthless, because any amount of information
can be hidden in an unstated assumption.

There are three stipulations. They are stated here in full, before any
result is mentioned.

\section{First Stipulation: Time-Mass Duality}

\textbf{[STIPULATION]} For the intrinsic time scale $\tilde T$ and the
mass $m$ of an object:
\[
  \tilde T \cdot m = 1 .
\]

This is not a definition of mass and not a definition of time. It is the
statement that both quantities are two readings of the same thing: a small
mass is a long intrinsic time, a large mass a short one. The equation is
reciprocal, hence symmetric -- neither side is the explanatory one.

In communications engineering terms, this is the Fourier duality between
time and frequency, translated into physical language. That is precisely
where it came from: the duality was the starting point of the theory,
not its result.

\textbf{[B]} From this single equation it follows immediately that time is
not an additional independent quantity. An object with mass carries its
time scale with it; it needs no externally imposed clock. This is why the
geometry manages with four and not five circles (A030), and why time sits
inside the state space and not beside it (A060).

\textbf{What is stipulated and not shown here:} that the reciprocity holds
exactly and not merely approximately; and that the constant on the right-hand
side equals one. The one is a choice of units -- any other value could be
absorbed into the scales -- but the exactness of the reciprocity is a
substantive claim that is stipulated, not proved.

This stipulation is also why the theory cannot place itself as a norm above
other frameworks: $\tilde T\cdot m = 1$ is a commitment, not a discovered
law. One who does not share it makes no error but works in a different
framework. The distinction between law, norm, and stipulation is developed
in A200; it begins here.

\section{Second Stipulation: The Compact Geometry}

\textbf{[STIPULATION]} The underlying space is a four-dimensional compact
torus with a $Z_3$ identification, written $T^4/Z_3$.

Three sub-decisions are embedded here, to be assessed separately.

\textbf{Compact instead of infinite.} This is the actual stipulation. It has
an immediate consequence: a compact space has a discrete spectrum. It follows
that masses appear as eigenvalues and need not be inserted as free parameters.
This consequence is the entire reason for the stipulation -- and it is
simultaneously the point at which the stipulation can fail.

\textbf{Torus instead of sphere.} \textbf{[B]} This choice is not free: the
torus has a non-trivial fundamental group, $\pi_1(T^4) \cong \mathbb{Z}^4$,
the sphere does not. Winding numbers -- the discrete, integer, coordinate-free
quantities on which the entire information concept of the theory rests (A180)
-- do not exist on the sphere. Replacing the torus by a simply connected
surface loses not a detail but the load-bearing element.

\textbf{Four dimensions.} The accounting here is uncomfortable, and should
remain so. That there are \emph{four} and not five follows from the first
stipulation: because $\tilde T\cdot m = 1$ binds time to mass, no separate
fifth circle for time is needed. In this sense the four is derived. But that
the experienced structure is precisely $3+1$ -- three spatial directions and
one time -- is \textbf{empirical input} and is not derived by the theory.
Earlier formulations in the corpus were too strong at this point; the
correction is recorded in the register as P34 and incorporated here.

\textbf{The $Z_3$ identification.} \textbf{[STIPULATION]} The tripling is
stipulated. It delivers the three-element fibre on which the three generations
appear as the spectrum of a cyclic operator (A110). \textbf{[B]} What can be
shown: tripling is crystallographically permitted, fivefold symmetry is not --
the condition $2\cos(2\pi/n) \in \mathbb{Z}$ permits $n \in \{1,2,3,4,6\}$.
This does not explain why three must be realised; but it excludes an entire
class of alternatives.

\textbf{[STIPULATION]} The direction is to be noted: $n=3$ is \emph{fixed} not
by symmetry but by the observed number of generations -- the observation
selects the symmetry, not the other way around. $Z_3$ is stipulated, motivated
by the economy of the three-point configuration and consistent with the
generation count. The reversal -- ``three generations are not free parameters
but the three permitted $Z_3$ fixed points'' -- reads the observation as a
consequence of the symmetry and is to be avoided. A stipulation does not become
a derivation by the presence of reasons.

\section{Third Stipulation: The Numerical Value}

\textbf{[STIPULATION]} The parameter is
\[
  \xi = \frac{4}{30000} = \frac{1}{3\cdot 2^2\cdot 5^4}
  \approx 1{.}333\cdot 10^{-4}.
\]

This stipulation is the most vulnerable of the three, and it decomposes into
two parts with quite different status. The separation is important enough to
make explicit -- earlier presentations in the corpus treated both parts jointly
as derived, which was not sustainable (register P33).

\textbf{The form is structural.} \textbf{[B]} The factors $4/3$, the $3$, and
the $2^2$ have a geometric origin: they come from the dimension structure and
the tripling. In this respect the shape of the expression is not chosen.

\textbf{The order of magnitude is not.} The factor $5^4$ -- the question of
why $\xi$ sits at $10^{-4}$ and not at $10^{-2}$ or $10^{-6}$ -- is
\emph{not} derived forward. It is justified in two ways, and both are honestly
to be named for what they are: intuitively via harmonic ratio structures, and
empirically via the Higgs sector. Neither justification is a derivation from
the geometry.

\textbf{[STIPULATION]} Therefore: the numerical value of $\xi$ is an input.
The theory does not claim to generate it; it claims that everything else
follows from it.

A warning belongs at the same place, because it concerns the most common
error of reasoning. Every dimensionless quantity can be written as a power
of $\xi$ if one is free to choose the exponent. An expression of the form
$X = \xi^N$ is in itself \emph{vacuous}. It becomes a statement only when
the exponent is fixed independently -- by the geometry, by a count, by a
recursion depth. Where this is not possible in this series, it will be said.

\section{What Follows from the Three Stipulations}

\textbf{[B]} The three stipulations together fix: a compact space with
discrete spectrum, a three-element fibre, a scale. Nothing more. Everything
further in this series is either derived from these three, or explicitly
marked as a further stipulation.

The test is the count itself. If in the course of the series a fourth or
fifth stipulation becomes necessary, it stands at its place with the marker
\textbf{[STIPULATION]} -- and it must then enter the balance of A230. A
theory with three openly declared stipulations is better than one with a
concealed one; one with seven openly declared would be worse than one with
three. The accounting decides, not the rhetoric.

\section{The Tolerance Standard at This Point}

This document deliberately contains not a single comparison number. The
reason is methodological: stipulations have no measurement precision. It is
meaningless to ask whether $\tilde T\cdot m = 1$ holds to six places --
the equation is stipulated, not measured.

Stipulations are testable only indirectly, through their consequences, and
there the standard from A010 applies: a consequence is considered supported
when its residual stays within the determination tolerance and need not be
closed by a free parameter. The first such numbers appear in A100.

\section{Verification Scripts}

Two statements of this document are computational and therefore backed by
scripts:

\begin{itemize}
  \item the crystallographic restriction $2\cos(2\pi/n)\in\mathbb{Z}$ with
    the result $n\in\{1,2,3,4,6\}$ and the exclusion of fivefold symmetry:
    \texttt{python/A\_Serie\_Skripte/a020\_kristallographie.py}
  \item the vacuousness of $X=\xi^N$ with a free exponent -- shown on
    arbitrarily chosen target quantities for which a matching $N$ can always
    be found: \texttt{python/A\_Serie\_Skripte/a020\_xi\_potenz\_trivialitaet.py}
\end{itemize}

\section{Open Questions}

\textbf{First, the number three is not proved minimal.} That exactly these
three stipulations are needed is a claim about the economy of the construction.
It has not been shown that none of them can be obtained from the others, nor
that two would suffice.

\textbf{Second, the tripling is permitted but not explained.} The crystallographic
restriction excludes fivefold symmetry and permits $\{1,2,3,4,6\}$. Why of
the permitted values precisely three is realised, the geometry does not say.

\textbf{Third, the order of magnitude of $\xi$ is justified but not yet
derived within the A-series.} The exponent $-4$ follows from $D_f=3-\xi$ and
the four-dimensionality of the universe; $\kappa=7$ emerges as the unique
consistent solution of the e-p-$\mu$ system; the factor $4/3$ is independently
confirmed by the Casimir effect. This derivation is in A015. What \emph{still}
lacks: a derivation of the order of magnitude from the three stipulations
themselves, without recourse to measured masses as input. Until then, the
quantitative side carries a measured anchor.

\textbf{Fourth, $3+1$ is an input.} It is marked as such and will not be
silently upgraded to a derivation in any later document of the series.
Whether this is maintained, the audit script checks.

\section{Supersedes}

This document subsumes: Dok.~003 (foundations), Dok.~008 ($\xi$ and $e$),
Dok.~009 ($\xi$-origin), Dok.~041 (parameter derivation), Dok.~042 ($\xi$
parameter particles), Dok.~253 ($\xi$ number space). Incorporated register
entries: P33 (status of the magnitude), P34 (dimension structure), P35
($\xi^N$ triviality), R56 ($Z_3$ as stipulation; direction observation$\to$symmetry,
not the reverse).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
the theoretical stipulations, and all substantive decisions come from the
author; the tools formulate, compute, check for contradiction, and create
verification scripts. They make no substantive decisions.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
