\section{Purpose}

The geometry of A030 is described as smooth, but not intended to be smooth.
FFGFT assumes that the effective structure carries a dimension deficit: it
does not behave like an exactly three-dimensional object, but like one with
\[
  D_f = 3 - \xi .
\]

This document states what follows from this, and -- the actual purpose --
traces the correction factor $K_\text{frak}$ back to a purely internal reason.

\textbf{Why both forms appear here:} the closure comma gives the \emph{internal}
reading of the factor $100$, the scale flow its \emph{derivation} (below). Both
describe the same number; the first shows where it sits in the geometry, the
second why it is exactly $100$.

\section{The Conformal Form of the Correction}

\textbf{[STIPULATION]} The correction acts conformally on the metric:
\[
  g_{\mu\nu}^{(\text{frak})} = \eta_{\mu\nu}\,\bigl(1 + \xi f\bigr),
\]
with a bounded function $f$ on the torus.

\textbf{[B]} Two properties follow immediately from this form.

First, the intervention is \emph{metric}, not topological. A bounded, $\xi$-small
modulation of the prefactor does not tear a manifold; it changes distances, not
connections. Winding numbers and spectral structure remain untouched. This is
why the fractal correction leaves everything from A030 in place.

Second, the correction is \emph{small of order} $\xi$. In the limit $\xi\to 0$
it vanishes and the smooth description is exact. The idealised smooth structure
is therefore not wrong, but the limiting case.

\textbf{[B]} Explicitly: fractal here does not mean discrete. The structure
remains an uncountable continuum; it is simply not smoothly affine. One who
concludes from $D_f<3$ to a granularity in the sense of smallest building blocks
has used a different concept.

\section{The Correction Factor from the Closure Comma}

\textbf{[B]} The recursion (A050) closes in the frozen case after exactly
$75$ circuits, where
\[
  75 = \frac{1}{100\,\xi}, \qquad \xi = \frac{4}{30000}.
\]

Requiring that $75$ rotations each shortened by $\varepsilon$ close \emph{exactly}, i.e.\
\[
  75\,(1-\varepsilon) = 74 ,
\]
it follows that
\[
  \varepsilon = \frac{1}{75} = 100\,\xi ,
\]
and therefore
\[
  K_\text{frak} = 1 - 100\,\xi = \frac{74}{75} = 0{.}98\overline{6}.
\]

This is the internal form: the correction factor is the ratio between the
unrolled and the projected rotation. It is not a fitted value but the closure
comma of a winding that falls one rotation short.

The closure comma re-expresses $100\xi$; it is the \emph{internal} reading of
the factor, not its derivation. The actual derivation of the factor $100$ runs
through the scale flow.

\section{Why the Factor 100}

\textbf{[K]} The factor $100$ is not stipulated but follows from the cumulative
action of the sub-dimensionality $D_f = 3-\xi$ over the entire renormalisation
group run. The local deviation from dimension $3$ is tiny ($\sim 0{.}003\,\%$);
it becomes physically effective only \emph{cumulatively} over the path from
the Planck to the electroweak scale:
\[
  \ln\!\left(\frac{\ell_\text{EW}}{\ell_P}\right) \approx \ln(10^{17}) \approx 39 .
\]
From this run and geometric averaging over scales, an effective amplification
factor of around $100$ emerges: the cumulative fractal correction is not $\xi$,
but $100\xi \approx 1{.}3\,\%$.

\textbf{[K]} The equivalent power form confirms this:
\[
  K_\text{frak} = \Bigl(\frac{D_f^\text{eff}}{3}\Bigr)^{D_f^\text{eff}/2}
  = 1-100\xi, \qquad D_f^\text{eff} \approx 2{.}973 .
\]
The effective dimension $D_f^\text{eff}\approx 2{.}973$ is \emph{not} the local
$D_f^\text{space}=2{.}9999$; it describes the cumulative action over the RG run.
Substituting gives $0{.}98665$ versus $1-100\xi = 0{.}98667$.

\textbf{[K]} And $D_f^\text{eff}$ itself is uniquely determined, not free: it
is the only value for which two independent derivations of the ratio $m_e/m_\mu$
-- the fractal and the directly-geometric ($5\sqrt3/18\cdot10^{-2}$) -- agree.
From this consistency condition $D_f^\text{eff}\approx 2{.}973$ follows, and
thereby $K_\text{frak}=1-100\xi$ necessarily. The factor $100$ is therefore a
derived quantity.

\section{Where the Factor Appears and Where It Does Not}

\textbf{[B]} $K_\text{frak}$ concerns exclusively \emph{absolute} values, never
ratios. A ratio of two quantities at the same level is unaffected by the
correction, because it cancels.

This is a sharp and testable separation, and simultaneously the most important
statement of this document for everything that follows: the dimensionless ratios
of the theory are independent of the fractal correction. Deviations attributable
to $K_\text{frak}$ can therefore only appear in the conversion to absolute values
(A080), not in the geometric core.

\textbf{[B]} The value $74/75$ is moreover not only derived but independently
\emph{confirmed}. In the fine-structure sector (A130) there are two separate
paths to the characteristic energy $E_0$, neither of which uses $K_\text{frak}$;
their difference is exactly $K_\text{frak}^{-1/2}$ and pins the factor to
around $10^{-4}$ at the same value that follows here from the scale run. Two
derivations that know nothing of each other hit the same number -- this is the
strongest support for $74/75$ not being freely chosen.

\section{The Limit of Resolution}

\textbf{[B]} The dimension deficit is a deficit, not a volume-preserving
ripple. The difference is computationally accessible: for a volume-preserving
modulation, the mean of $f$ over the torus vanishes; for a deficit, it does not.

This decides with what power of $\xi$ the correction enters first-order
perturbation calculations -- with nonvanishing mean as $\xi^1$, otherwise only
as $\xi^2$. The verification script computes both cases and shows the exponents
numerically.

\section{Verification Scripts}

\begin{itemize}
  \item Closure comma: $75(1-\varepsilon)=74 \Rightarrow \varepsilon = 1/75 = 100\xi$,
    with explicit countercheck that the computation assumes rather than produces
    the $100$:
    \texttt{python/A\_Serie\_Skripte/a040\_schliessungskomma.py}
  \item Deficit versus volume-preserving ripple: numerical determination of
    the $\xi$-power in both cases:
    \texttt{python/A\_Serie\_Skripte/a040\_dimensionsdefizit.py}
\end{itemize}

\section{Open Questions}

\textbf{First, the closure comma shows consistency, not necessity.} The
cumulative RG run derives $K_\text{frak}=1-100\xi$ from the accumulated effect
of $D_f=3-\xi$ over 17 orders of magnitude; the factor 100 emerges as a
logarithmic scale ratio. The closure comma ($1-100\xi$ hits exactly the
empirical value) confirms the construction but does not prove it: a geometric
derivation showing that exactly $100$ follows and no other factor still stands.
This remainder is explicitly smaller than the point as previously formulated.

\textbf{Second, $f$ is not determined.} The form of the correction is stipulated,
the function itself is not. Everything depending on details of $f$ -- notably
the phase of its harmonics -- is thereby open.

\textbf{Third, $K_\text{frak}$ is a single, generation-independent factor.}
There are indications that the correction should act generation-dependently on
the mass ladder; a constant factor does not close these deviations. The point
belongs substantively in A100 and is treated there.

\section{Supersedes}

This document subsumes: Dok.~132 (fractal duality), Dok.~133 (fractal correction
derivation), Dok.~300 (two roles of $K_\text{frak}$), Dok.~210 (winding-number
corrections, insofar as they concern the factor). Incorporated: K1--K6 from the
correction register, insofar as they concern the correction form.

\section{Use of AI Tools}

This document was created with the assistance of AI tools.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
