\section{The Separation That Everything Depends On}

\textbf{[K]} The theory predicts ratios, not absolute values.

This sentence is the most important methodological statement of the entire
block, and it cuts the error discussion into two halves that have nothing to
do with each other.

A dimensionless ratio of two quantities at the same level is intrinsic: it
depends on the geometry and nothing else. It needs no unit, no bridge constant,
no correction factor -- these cancel (A040).

An absolute value, by contrast -- a mass in megaelectronvolts, a length in
metres -- additionally requires a conversion, and this conversion is not part
of the geometry.

\textbf{[B]} From this follows a sharp diagnostic rule: \emph{every deviation
between theory and measurement must first be examined as to whether it sits in
the geometric core or in the translation layer.} Treating both the same obscures
the statement.

\section{What the Physical Constants Are Here}

\textbf{[STIPULATION]} In the natural system of the theory, $\hbar$, $c$, and
$k_B$ equal one. They are not physical quantities but unit bridges.

The word bookkeeping, which appears in the corpus for this, is regularly
misunderstood as dismissive. The opposite is meant. Bookkeeping here means
\emph{necessary}, not \emph{dispensable}:

\begin{itemize}
  \item $c$ is the bridge between units of space and time,
  \item $\hbar$ the bridge between units of mass and time,
  \item $k_B$ the bridge between temperature and energy.
\end{itemize}

\textbf{[B]} The SI separates metres, seconds, kilograms, and kelvins into
distinct units. As soon as \emph{computation} is performed in this system, the
conversion factors are indispensable -- without $k_B$ an energy in kelvins would
result. Ontologically they are secondary; operationally indispensable.

\section{The Four Dresses}

\textbf{[K]} A single quantity appears in four guises:
\[
  m_0 c^2 \;=\; E_0 \;=\; k_B T_0 \;=\; \hbar/\tilde T .
\]

Dividing by $c^2$ gives a mass; by $\hbar$, a time; by $k_B$, a temperature.
These are four expressions of the same fact, not four quantities. This identity
is \emph{exact} -- it is the definition of the conversion, and it contains no
approximation.

\textbf{[B]} $E_0$ itself is an empirical bridge: $E_0=\sqrt{m_em_\mu}
\approx7{.}398\,\text{MeV}$ follows from measured lepton masses, not from $\xi$
alone. The geometric derivation is in A130; the unit check in A085. A reader
of only this document must know: $E_0$ is treated here as a given bridge
constant, not as a derived quantity.

\textbf{[B]} Where then do deviations arise? Not in this identity. They arise
where a theoretically determined dimensionless number is held against a measured
quantity -- and there they sit in the dress, not in the conversion.

\section{Bridge Constants}

\textbf{[STIPULATION]} To state absolute values, the theory needs at least one
quantity with dimension. This bridge constant is a declared input.

This is not a weakness of the approach, but a necessity of any theory that
seeks to generate absolute numbers from dimensionless structures: from pure
numbers no mass in kilograms follows. What matters solely is that the number of
bridge constants is stated openly and remains small.

\textbf{[B]} At the same time: choosing a bridge constant is a calibration,
not a test. An agreement produced by the choice of bridge must not be counted
as confirmation. This rule is applied in A130 at a concrete case, where it
makes the difference between a success and a self-confirmation.

\section{The Tolerance Standard in Units}

\textbf{[B]} From the separation follows how to read a deviation. Three
quantities belong together: the value, the measurement precision of the
comparison quantity, and the determination tolerance of the theoretical quantity.

A deviation of one percent can be meaningless if the theoretical quantity is
determined only to two places -- and it can be devastating if both sides are
fixed to eight places. The percentage alone says nothing. This rule is applied
consistently from A100 onward.

\section{Verification Scripts}

\begin{itemize}
  \item Exactness of the four-dress identity $m_0c^2=E_0=k_BT_0=\hbar/\tilde T$
    in SI numbers, with display of the relative deviation (expected: zero up to
    rounding): \texttt{python/A\_Serie\_Skripte/a080\_vier\_kleidungen.py}
  \item Invariance of ratios under change of bridge constant, against the
    non-invariance of absolute values:
    \texttt{python/A\_Serie\_Skripte/a080\_verhaeltnis\_invarianz.py}
\end{itemize}

\section{Open Questions}

\textbf{First, the number of bridge constants is not tallied here.} It belongs
in the overall balance A230, not here -- but it must appear there, otherwise
the one-parameter claim of the theory is not testable.

\textbf{Second, it is not shown that the bridge constant could follow from the
geometry.} As long as it is declared, the absolute scale remains an input.
This is consistent with A020, where the same holds for the order of magnitude
of $\xi$, and it is the same gap in a different guise.

\section{Supersedes}

This document subsumes: Dok.~013 (SI), Dok.~014 (natural/SI), Dok.~015
(systematics of natural units), Dok.~122 (ratio and absolute), Dok.~134
(unit conventions), Dok.~261 (static natural units). Incorporated: P40
(ratios exact, deviations at the conversion).

\section{Use of AI Tools}

This document was created with the assistance of AI tools.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
