\section{What $N_0$ Is}

\textbf{[B]} A100 showed that the rough $\xi$-ladder of the lepton masses carries
a small, generation-dependent correction. Writing the correction required per rung
as an effective factor $N_g$ via $K = 1 - N_g\,\xi$, the three factors stand in
the ratio
\[
  N_1 : N_2 : N_3 \;=\; 1 : 1{.}981 : 2{.}971 \;\approx\; 1 : 2 : 3 .
\]
The correction thus grows \emph{linearly with generation number},
\[
  \boxed{\,N_g \approx g \cdot N_0\,}, \qquad
  N_0 \approx 38{.}5 ,
\]
and the three individual estimates $N_1$, $N_2/2$, $N_3/3$ lie at $38{.}89$,
$38{.}53$, $38{.}52$ -- consistent with each other to under one per cent. That is
the core: $N_0$ is \emph{not a fixed constant of the theory} but the \emph{ladder
step per generation}. At $g=2$ it is already $77$, at $g=3$ about $116$.

\textbf{[K]} This triple consistency is, however, weaker than it looks: only
\emph{two} of the three estimates are independent. Because a consistently
multiplicative correction $K^{p_3} = K^{p_1}K^{p_2}$ and hence $p_3 = p_1 + p_2$
forces $N_3 \approx N_1 + N_2$ arithmetically (checked: $115{.}95$ vs.\ $115{.}55$,
difference $0{.}35\,\%$, second order in $\xi$) -- in the ratio $1{:}1{.}981{:}2{.}971$
only $1{.}981$ is measured, the third number is fixed as $1 + 1{.}981$. The
generation-linear law therefore rests on \emph{one} observation (the $\mu/e$ rung),
not three; it is a candidate on one measurement, not a triply supported regularity.
The standard from A220 -- ``do not count dependent as independent'' -- applies
immediately here.

\textbf{[K]} Two things follow immediately. First, $N_0$ is to be sharply
separated from the fixed number $100$ in $K_\text{frak} = 1 - 100\xi$ (A040):
the $100$ is the \emph{one} RG scale of a corpus-wide constant, $N_0$ is a
generation counter in a different sector. That both lie near powers of ten does
not make them the same quantity. Second, with the generation-linear law the real
question is not the \emph{value} of $N_0$ but why the ladder is corrected in a
\emph{generation-counting} way at all. A closed form for the base alone would
leave this law untouched.

\section{The Right Standard: Determination Tolerance Instead of Last Digit}

\textbf{[K]} $N_0$ is not known to arbitrary precision. In the referenced mode
its value follows solely from the two $\tau$ rungs, and their precision is limited
by the $\tau$ mass ($\pm 0{.}12$ MeV). Propagating that gives
\[
  N_0 = 38{.}52 \pm 0{.}21 ,
\]
a relative determination uncertainty of about half a per cent. From this follows
the standard against which every candidate expression is to be measured: not
whether it hits $38{.}5$ to the last decimal -- that is in principle unreachable
-- but whether it \emph{falls within this interval}.

\textbf{[K]} This standard has a converse that carries the whole section:
\emph{the band is wide enough that many expressions fall into it}. Hitting a
$\pm 0{.}21$ window is easy. Hence bare compatibility with the band \emph{cannot}
be the test that turns a candidate into a derivation. Compatibility says the
number fits; it does not say the number \emph{follows}.

\section{The Candidates}

\textbf{[K]} Three expressions lie in or near the band and are to be recorded as
\emph{permissible, unrefuted} candidates -- none is a derivation:

\begin{center}
\begin{tabular}{lrr}
\hline
Expression & Value & Distance \\
\hline
$100/\varphi^2$                 & $38{.}20$ & $-1{.}5\,\sigma$ \\
$3\cdot(\pi^2/2)\cdot\varphi^2$ & $38{.}76$ & $+1{.}1\,\sigma$ \\
$\ln(M_\text{Pl}/v)$            & $38{.}44$ & $-0{.}4\,\sigma$ \\
\hline
$100/e$                         & $36{.}79$ & $-8{.}3\,\sigma$ \\
\hline
\end{tabular}
\end{center}

with $\varphi = \tfrac{1+\sqrt5}{2}$ and $V_{S^4} = \pi^2/2$ the volume of the
unit 4-ball. The first three are compatible; $100/e$ lies far outside and is
excluded. The middle expression $3 \cdot (\pi^2/2) \cdot \varphi^2$ lies even
closer to the centre than $100/\varphi^2$.

\textbf{[K]} And here the standard from the previous section applies: that three
seemingly well-motivated expressions fall into the band is precisely the diagnosis.
A fourth would do the same. Band hits do not separate candidates because the band
is wide.

\section{Why None of Them Is a Derivation}

\textbf{[K]} The objection falls equally on all three expressions, and it concerns
not the \emph{value} but the \emph{form}. For none is there a justification of
why precisely this form should be the form of $N_0$: why the 4-ball volume
$\pi^2/2$, why $\varphi^2$, why the factor $3$ and not $9$. What is missing is a
chain that begins at the $T^4/Z_3$ geometry and has this structure \emph{as output
at the end} -- rather than an expression assembled backwards to hit an already
known value.

\textbf{[K]} The role of $\varphi$ is to be precisely stated, because $\varphi$
is not foreign to the mass sector. In A120 $\varphi$ appears \emph{forward and
parameter-free} as an eigenvalue of a named construction -- the golden inflation
$\varphi^2 = \varphi + 1$ in the icosahedral redistribution. In \emph{this} role
$\varphi$ is permissible and derived. Strictly to be separated from this is
$\varphi$ as a \emph{power inserted into an expression to hit a scale} --
$\varphi^N$ as a fitting base. That is exactly the warning example: it carries no
forward content. Both $100/\varphi^2$ and $3\cdot(\pi^2/2)\cdot\varphi^2$ are of
the second kind -- $\varphi^2$ assembled, not produced by a construction. That is
why both remain candidates and do not become derivations, even though $\varphi$
itself is at home in the theory when it appears as output of a named symmetry.

\section{A Warning Example: Target First, Justification After}

\textbf{[K]} How easily a fit dresses itself as a derivation is shown by a
concrete case. To the expression $3\cdot(\pi^2/2)\cdot\varphi^2 = 38{.}76$,
which lies $+1{.}1\sigma$ above the centre, an ``anomaly'' term $\Delta$ was
subsequently added to close the residual. Its value:
\[
  \Delta = \frac{3}{4\pi} = 0{.}2387 ,
\]
and the gap to be closed is $38{.}758 - 38{.}52 = 0{.}238$ -- the same number to
three figures. The correction was therefore not derived and then found to fit; the
gap was known first, and a term of the right size was \emph{subsequently} given a
name. Two physical features confirm this independently of the coincidence: a
one-loop contribution would carry the factor $1/(4\pi)^2$, not linear $1/(4\pi)$;
and a genuine localised anomaly would be \emph{quantised} -- an integer index, not
a fractional $0{.}2387$. The physical dress does not fit the number underneath it.
That does not refute $38{.}52$ as a candidate; it only shows that the anomaly
narrative is not the reason why the value sits there.

\textbf{[K]} From this follows the test rule that A220 records generally and that
applies particularly here: a derivation is not to be assumed in prose but to be
written as a script that begins at the geometry, contains \emph{no target value},
and one checks what number it prints. Prose can hide a fitted step behind a secure
sentence; code cannot. A value hitting the centre of a $\pm 0{.}21$ band to the
last digit is not a triumph but a warning: nothing fundamental lands exactly on
the mean of a measurement unless it was built to do so.

\section{Verification Script}

\begin{itemize}
  \item The tolerance $N_0 = 38{.}52 \pm 0{.}21$, the $\sigma$ distances of the
    four candidates, the target back-computation $\Delta = 3/(4\pi)$ vs.\ the gap,
    and the generation run $N_g = g\,N_0$:
    \texttt{python/A\_Serie\_Skripte/a105\_n0.py}
\end{itemize}

\section{Symbol Glossary}

Symbols used throughout the entire A-series are explained in A010.
Specific to this document:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\begin{tabular}{lp{9cm}}
\toprule
Symbol & Meaning \\
\midrule
$N_0$ & Recursion limit; value at which the iteration converges \\
$\delta$ & Refraction strength; deviation from ideal torus lattice \\
$\Delta_\text{rec}$ & Recursion deficit; difference to next closure \\
\bottomrule
\end{tabular}}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Open Questions}

\textbf{First, $N_0$ is open.} It is well bounded as a value within its tolerance,
but not derived from the geometry. No expression presented so far is more than a
permissible candidate.

\textbf{Second, the standard is named.} The question is closed by a construction
that begins at the $T^4/Z_3$ geometry, fixes invariant, exponent, and scales, and
delivers $N_0$ at the end -- a construction that could have missed and did not --,
not by another well-looking expression that falls into the band.

\textbf{Third, the generation law remains the deeper task.} Even a perfect closed
form for the base does not explain why the correction $N_g = g\,N_0$ runs
generation-counting. That is the real open question, and it lies beneath the
question of the numerical value.

\section{Supersedes}

This document subsumes: Dok.~292 (generation-linear coupling, $N_g=g\,N_0$,
tolerance $N_0=38{.}52\pm0{.}21$, candidates $100/\varphi^2$, $100/e$), Dok.~190
(R54/R55: $N_0$ open, separation $K_\text{frak}$-$100$ / $N_0$; P35). Incorporated:
the external candidate $3\cdot(\pi^2/2)\cdot\varphi^2$ and the $\Delta=3/(4\pi)$
target back-computation from the IPI correspondence (July 2026), booked as
permissible-but-not-derived candidate and as warning example respectively.

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
