\section{The Question}

$\theta = 2/9$ is empirically confirmed to seven figures (A110). This document
shows three things: \emph{where} the value resides (solely in the dynamic phase
channel, not in the magnitude), \emph{that} it follows exactly and parameter-free
from the icosahedral doubling geometry, and \emph{what} remains open as a
derivation step (the bridge to the mass ratios).

The central finding is positive: two mutually independent paths -- the
phenomenological Koide angle from the measured masses and the purely geometric
redistribution of modes -- hit exactly the same rational number $2/9$, without
knowing about each other.

\section{The Magnitude Channel Is Blind}

\textbf{[K]} With amplitudes $a_k(\theta) = 1 + \sqrt2\cos(\theta+2\pi k/3)$
the Koide invariant is
\[
  Q(\theta) = \frac{\sum_k a_k^2}{\bigl(\sum_k a_k\bigr)^2} = \frac{6}{9} = \frac23
  \qquad\text{for \emph{every} } \theta .
\]

The proof is two lines: three cosines offset by $120°$ sum to zero, hence
$\sum_k a_k = 3$; and with $\sum_k\cos^2 = 3/2$ it follows that $\sum_k a_k^2 = 6$.

\textbf{[K]} From this follows a statement to be recorded, because it limits the
reach of A110: \emph{the Koide relation says nothing about $\theta$}. $Q=2/3$
holds for every angle. The value $2/9 = 0{.}2222$ also lies \emph{below} the
range $[1/3,1]$ that $Q$ traverses for positive masses -- $2/9$ is therefore
neither a limit, nor an extremum, nor a fixed point of the symmetric functional.

In the magnitude channel $2/9$ is completely invisible.

\section{The Elimination Chain}

\textbf{[K]} Systematically checked where $\theta$ does \emph{not} live. The
orbit members $\{1/9,\,2/9,\,4/9\}$ are to be distinguished; the question is
which quantity achieves this.

\begin{center}
\begin{tabular}{lll}
\hline
Channel & Behaviour & Distinguishes? \\
\hline
Magnitude $|B_\theta|$ & $=1$ to $10^{-15}$ for all $\theta$ & no \\
Winding number & $=3$ exactly for all $\theta$ & no \\
Symmetric functional & identical for all $\theta$ & no \\
Continuous phase profile & $0{.}093$ / $0{.}171$ / $0{.}249$ & \textbf{yes} \\
\hline
\end{tabular}
\end{center}

\textbf{[K]} Noteworthy is the second row. The integer winding -- precisely the
topological quantity that, according to A030, carries the information concept of
the theory -- does \emph{not separate $2/9$} from $1/9$ and $4/9$. The reason is
that $2/(9\pi)$ is irrational; $\theta$ is not a flat topological invariant.

\textbf{[K]} Exactly one channel remains: the continuous, dynamic phase profile.
There and only there is $2/9$ distinguishable from its orbit companions.

\section{Forced or Contingent}

\textbf{[K]} This raises the decisive question: is $2/9$ forced like the speed of
light, or contingent?

The test is the variational behaviour. Coupling a second triplet with strength
$\delta$, the extremum moves away from the $Z_3$ point: $\theta^*$ rises smoothly
and monotonically from $0{.}099$ at $\delta = 0{.}10$ through $0{.}223$ at
$\delta = 0{.}24$ to $0{.}501$ at $\delta = 1{.}0$. The achieved range
$[0{.}05;\,0{.}52]$ contains $2/9$ \emph{in the interior and undistinguished}.

\textbf{[K]} This test sets $\delta$ as a \emph{free} coupling parameter. Under
this assumption $2/9$ would lie undistinguished in the achieved range and the
value would be contingent. But the assumption is not that of the theory: the
icosahedral geometry fixes $\delta$ (next section). Once $\delta$ is no longer
free but the total leak $(7-3\varphi)/9$ of the same redistribution that also
carries $\theta$, the contingency falls away. The variation test therefore shows
that $\theta$ \emph{lives in the dynamic channel} -- it does not decide
forced/contingent, because it assumes $\delta$ to be free, which the geometry
does not.

\section{The Geometric Source: $C_3$ in $A_5$}

\textbf{[B]} The dynamic channel has a geometric source. The three lepton modes
are the Fourier eigenmodes of the $Z_3$ circulant: the trivial mode
$v_0 = \tfrac{1}{\sqrt3}(1,1,1)$ and two non-trivial, Galois-conjugate modes.
The doubling places the $C_3$ structure into the icosahedral group $A_5$; its
fivefold generator is a rotation $R_5$ by $72°$ about an icosahedral fivefold
axis. Because the threefold and fivefold axes are differently oriented, $R_5$
mixes the $C_3$ modes.

\textbf{[B]} The complete redistribution of the electron mode has weights
$p_j = |\langle v_j\,|\,R_5\,v_e\rangle|^2$:
\[
  \underbrace{p_0 = \tfrac29}_{\text{trivial}},\qquad
  p_2 = \tfrac{5-3\varphi}{9},\qquad
  p_1 = \tfrac{2+3\varphi}{9},\qquad
  p_0+p_1+p_2 = 1,
\]
with $\varphi = \tfrac{1+\sqrt5}{2}$. \emph{All three weights carry the denominator
$9 = 3^2$} -- the same $Z_3$ structure in which $2/9$ sits as orbit address. The
fraction that transitions into the trivial mode under the fivefold rotation is
\[
  p_0 = \bigl|\langle v_0\,|\,R_5\,v_e\rangle\bigr|^2 = \frac29
\]
exactly and parameter-free (numerically confirmed to 40 places). No mass ratio,
no Koide parametrisation, and no $2/9$ input enters this value.

\textbf{[K]} The value is icosahedron-\emph{specific}, not generic:
\begin{itemize}
  \item $200$ random rotation axes at $72°$ give the leak in the range
    $[0{.}036;\,0{.}452]$; \emph{not one} hits $2/9$. Only the icosahedral
    fivefold axes deliver it.
  \item The angle scan shows $2/9$ exactly at $72°$; the $n$-fold series gives
    $2/9$ exclusively at $n = 5$ (at $n=3$ one gets $2/5$, at $144°$ one gets
    $4/9$).
  \item Of the six fivefold axes, three give $2/9$, three give $4/9$; the
    embedding selects the nearest axis and hence $2/9$. That is a discrete
    binary choice, not a free parameter.
\end{itemize}

\textbf{[B]} The same redistribution also delivers the second quantity: the total
leak $p_0 + p_2 = (7-3\varphi)/9 = 0{.}2384$ is the parameter-free value of the
coupling $\delta$ and agrees with the $\delta^* = 0{.}2389$ back-computed from
$\theta$ to $0{.}18\,\%$. Angle \emph{and} amplitude therefore arise from a single
fivefold redistribution; the earlier separate treatment as two harmonics was too
narrow a view.

\textbf{[K]} Thus two independent paths coincide exactly: the phenomenological
Koide angle (from the masses, without geometry) and the geometric redistribution
(from $A_5$, without masses and without $2/9$ input) both give $2/9$. That is a
convergence finding. $2/9$ is an invariant of the translation between torus
geometry and spectral representation -- it belongs to the common structure, not to
one representation, analogously to $\hbar$ and $c$ being conversion factors and
not ontological primitives.

\textbf{[B]} The connection to the dynamic channel closes here: the fivefold
rotation $R_5$ sets a phase $\pi/2$ -- precisely the value $\chi = \pi/2$ that
marks the one distinguishing channel above. The geometric source and the dynamic
location are the same.

\section{Verification Script}

\begin{itemize}
  \item $\theta$-independence of $Q$ (exact, for arbitrary angles), the
    elimination chain through the three blind channels, and the contingency test
    $\theta^*(\delta)$ with the proof that $2/9$ lies undistinguished in the
    achieved range:
    \texttt{python/A\_Serie\_Skripte/a120\_theta.py}
\end{itemize}

\section{Symbol Glossary}

Symbols used throughout the entire A-series are explained in A010.
Specific to this document:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\begin{tabular}{lp{9cm}}
\toprule
Symbol & Meaning \\
\midrule
$\theta = 2/9$ & Geometric fixed-point angle; dynamic locus on $T^4$ \\
$p_0 = 2/9$ & Exact $\theta$ value as $C_3$-in-$A_5$ identity \\
$\Omega_\text{res}$ & Resonance frequency of the $\theta$-mode \\
$\Delta\omega$ & Frequency spacing to the next mode \\
\bottomrule
\end{tabular}}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Open Questions}

\textbf{First, the value $2/9$ is derived, not open.} It follows exactly and
parameter-free from the icosahedral redistribution and independently coincides
with the phenomenological Koide angle. The earlier classification as structurally
unjustified is thereby superseded.

\textbf{Second, $\delta$ is not free.} It is the total leak $(7-3\varphi)/9$ of
the same redistribution that carries $\theta$. The contingency impression arose
solely from treating $\delta$ as a free parameter; the geometry fixes it.

\textbf{Third, one derivation edge remains open -- and is precisely named.} The
explicit mechanism connecting the geometric redistribution weights
$(2/9,\,(5-3\varphi)/9,\,(2+3\varphi)/9)$ with the physical mass ratios has not
been written out. This bridge need not run via Koide; it can be led directly
through the masses or the mode structure. That is the subject of further work --
and explicitly not an objection to the convergence finding, but the next stage.

\textbf{Fourth, the underlying doubling structure $A_5$ is presupposed.} The value
$2/9$ is exact within the established icosahedral doubling; whether this doubling
itself necessarily follows from the three stipulations of A020 or enters as an
additional structure is the remaining structural question -- one that goes beyond
the five-fold counting but no longer touches the value $2/9$.

\section{Supersedes}

This document subsumes: Dok.~291 (dynamic locus), Dok.~293 (icosahedral approach),
Dok.~286 (dynamic sector), Dok.~290 (magnitude/phase, insofar as concerning
$\theta$). Incorporated: P42, P35.

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
