\section{The Thesis}

\textbf{[STIPULATION]} Bell correlations are on $T^4$ a \emph{topological}
phenomenon: two measurement sites that lie far apart in the unrolled picture are
connected in the compact picture by a closed path.

What appears as action at a distance in the projected picture is proximity in the
compact picture. Non-locality is thereby an artefact of the projection (A090),
not an ontological property of the world.

\textbf{[B]} This is not a circumvention of Bell's theorem. Bell rules out local
hidden variables \emph{in the projected space}. A topological connection in the
pre-ordered space is not a hidden variable in the sense of the theorem -- it is
not an additional quantity that fixes the outcome, but a statement about the
geometry in which both measurement sites lie.

\section{What Does \emph{Not} Change}

\textbf{[K]} The predictions of quantum mechanics remain. The CHSH value for the
singlet state is
\[
  S = 2\sqrt2 = 2{.}8284271\ldots
\]
and the Tsirelson bound holds unchanged.

\textbf{[B]} In particular, the mass extension changes nothing: the
$\mathbb{C}^3$ tensor factor is invisible for correlation quantities, because the
fibre state is normalised and the observable acts there as the identity (A070).
This is computed, not claimed.

A theory that changed something here would already be refuted -- CHSH is one of
the best-tested quantities in physics.

\section{The Residual of Order $\xi$}

\textbf{[K]} Compactness has not completely disappeared after the projection. It
leaves a residual, and this residual is the only place where the theory can show
itself in the quantum domain at all.

The order of magnitude is fixed by $\xi$: the relative deviation is about
$10^{-4}$ to $10^{-5}$, depending on how many $\xi$-factors enter.

\textbf{What this means for measurability -- without gloss.} The effect is
\emph{not resolvable} with current hardware. The systematic uncertainties of real
Bell experiments -- detector efficiency, angle calibration, state preparation --
are orders of magnitude larger. A fit of the $\xi$ parameter to measured CHSH
values is therefore \emph{pointless}: it would adjust hardware systematics, not
measure geometry.

This finding is explicitly part of the result. A prediction whose signal lies
below the noise is a prediction for later, not a confirmation for today.

\section{Why the Residual Is Nevertheless a Prediction Quantity}

\textbf{[K]} The $\xi$-order of the CHSH deviation is one of the four prediction
quantities of the A-series (A010). The reason is not that it is testable today,
but that it is \emph{in principle} testable and the theory can fail at it.

Three properties make it a genuine prediction:

\begin{itemize}
  \item The \emph{direction} is fixed: the residual reduces the correlation, it
    does not increase it.
  \item The \emph{order of magnitude} is fixed and not adjustable -- it depends
    solely on $\xi$, which is stipulated in A020 and not readjustable.
  \item The \emph{scale dependence} is fixed: the residual grows logarithmically
    with the number of degrees of freedom involved, not linearly.
\end{itemize}

\textbf{[STIPULATION]} If a CHSH value is measured that \emph{exceeds} the
Tsirelson bound, or one that falls below it by significantly more than $\xi$-order
without hardware systematics explaining it, the theory is refuted at this point.

\section{The Geometric Reading of Entanglement}

\textbf{[B]} In the compact picture, an entangled pair is not a pair of separated
objects with a connection but \emph{one} object with two projection images. The
correlation is then not a transmission but identity.

From this it follows immediately why no information is transmitted and Relativity
remains unviolated: there is nothing that travels from A to B. Signal-freedom is
in this reading not an additional condition to be imposed, but a consequence of
the construction.

\textbf{[S]} The assignment of which closed paths correspond to which concrete
entanglement states has not been worked out. It is a sketch and is marked as such.

\section{Verification Script}

\begin{itemize}
  \item CHSH in the singlet vs.\ the Tsirelson bound, the invisibility of the
    $\mathbb{C}^3$ factor, and the order of magnitude of the $\xi$-residual
    compared to typical experimental uncertainties:
    \texttt{python/A\_Serie\_Skripte/a160\_chsh.py}
\end{itemize}

\section{Symbol Glossary}

Symbols used throughout the entire A-series are explained in A010.
Specific to this document:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\begin{tabular}{lp{9cm}}
\toprule
Symbol & Meaning \\
\midrule
$S_\text{CHSH}$ & CHSH correlation value; classical $\leq2$, Tsirelson $\leq2\sqrt2$ \\
$\Delta_\text{CHSH}$ & Deviation from Tsirelson value; T0 prediction $\sim\xi$ \\
$\varepsilon_\text{CHSH}$ & Relative CHSH correction from $T^4$ geometry \\
\bottomrule
\end{tabular}}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Open Questions}

\textbf{First, the prefactor $1/(2\pi)$ is now geometrically justified.}
$\xi$ is the fractal correction to the arc length on the torus. A CHSH measurement
is an angle measurement over a full circle (circumference $2\pi$). The correction
per angle unit is $\xi/(2\pi)$ -- the circumference is the conversion factor, not
a free parameter. \textbf{[B]}

\textbf{[B]} \textbf{Connection to the cumulative formula (A165).}
The elementary formula $\xi/(2\pi)$ and the cumulative formula
$\text{CHSH}^{\text{T0}}(n)=2\sqrt2\cdot\exp(-\xi\ln n/D_f)$
describe different observables:
\begin{itemize}[leftmargin=2em,itemsep=1pt,topsep=2pt]
  \item \textbf{Elementary:} phase correction per single measurement (one
    circumference $2\pi$) -- hence $\xi/(2\pi)$.
  \item \textbf{Cumulative:} damping over $\ln n$ entanglement layers (logarithmic
    entropy scale) -- hence $\xi\ln n/D_f$. The $2\pi$ does not appear because
    the relevant integration length is $\ln n$, not the circumference.
\end{itemize}
\textbf{Why $D_f$ in the denominator?} The fractal correction $\xi$ acts in
$D_f=3-\xi$ effective dimensions simultaneously. Per dimension: $\xi/D_f$.
The cumulative formula integrates over all dimensions -- that is fractal
self-consistency: $\xi/D_f$ instead of $\xi/3$.

\textbf{Both formulas are now geometrically justified.} What remains: the
measurement. The deviation lies below the NISQ noise (A165).

\textbf{Second, the path assignment is open} (see above, \textbf{[S]}).

\textbf{Third, the claim that Bell is thereby ontologically defused is an
interpretation.} It is consistent, but it does not follow compellingly -- the
same mathematics can be read without this interpretation. The A-series does not
claim to have decided the interpretational question.

\section{Supersedes}

This document subsumes: Dok.~020--023 (quantum mechanics, Bell), Dok.~035
(non-locality), Dok.~073 (entanglement), Dok.~142 (CHSH), Dok.~055 (dynamic
mass photons, energy-dependent non-locality), Dok.~074 (no-go theorems and T0
answer: Bell's theorem, Kochen--Specker, locality argument), Dok.~131 (apparent
instantaneity, local vs.\ global relations, Green's function and causality in the
T0 formalism). Incorporated: R41.

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
