\section{The Unit}

\textbf{[K]} The elementary information unit of this theory is the
\emph{winding quantum}
\[
  \Delta w = 1 .
\]

It is the smallest difference between two winding classes on $T^4$. Half a
winding quantum does not exist -- the fundamental group
$\pi_1(T^4)\cong\mathbb{Z}^4$ is integer-valued (A030).

\textbf{[B]} Three properties follow immediately, and they are the reason why
this choice is to be preferred over any cell-based definition:

\begin{itemize}
  \item \textbf{integer-valued} -- no arbitrary fineness;
  \item \textbf{coordinate-free} -- independent of origin, orientation, and
    parametrisation;
  \item \textbf{energy-independent} -- the unit is the same at every scale,
    because it is topological, not metric.
\end{itemize}

The last property is the strongest. An information unit that depended on the
energy would not be a unit but a scale choice.

\section{Why No Unit Cells}

\textbf{[B]} The obvious alternative -- dividing space into cells and counting
information -- fails at the same objections listed in A030: origin, orientation,
coordinate dependence, and an entropy that depends on an arbitrary partition.

For the winding quantum all these objections are empty, because a winding class
has no location. It is the property of a closed path, not of a region. And the
torus is boundaryless, $\partial T^4=\emptyset$ -- a surface-based definition is
likewise excluded because no surface is distinguished.

\section{Magnitude and Phase}

\textbf{[K]} The mass operator splits into two channels (A070, A120): magnitudes
and phases of the spectral coefficients. For the concept of information the
separation is essential.

\textbf{[B]} A magnitude spectrum fixes the phase only up to an all-pass factor.
There is therefore information that is \emph{in principle} not visible in the
magnitude channel -- the proof stands in A120, where it is shown that $\theta$
is captured by no symmetric, counting functional.

\textbf{[STIPULATION]} From this follows a booking rule for the whole series: a
statement that uses only magnitudes can make no claim about phase information --
neither its existence nor its absence.

\section{The Connection to Landauer}

\textbf{[B]} The Landauer principle links the erasure of one bit to a minimum
energy $k_B T\ln 2$. In the language of this theory this is a statement of the
\emph{translation layer}: it contains $k_B$ and $T$, two quantities that are
bridge and dress by A080.

The winding quantum lies beneath it. It is the topological unit; the Landauer
energy is what it costs in a particular thermal dress.

\textbf{[B]} \textbf{The derivation.} On the 4-torus
$\pi_1(T^4)\cong\mathbb Z^4$: the first homotopy group is $\mathbb Z^4$, each
direction carries discrete winding numbers. Erasing a bit corresponds to the
transition $\Delta w = 1$ -- a change of winding number by one in one direction.
This transition is irreversible (type-II loss, A090): the winding number is a
topological invariant; its loss cannot be undone without expenditure of energy.

The energy expenditure follows from the thermodynamic dress of this topological
transition. A system in thermal equilibrium at temperature $T$ must for an
irreversible bit transition dissipate at least entropy $\Delta S = k_B \ln 2$
(two states, one erased). The minimum energy is:
\[
  E_L = T\cdot\Delta S = k_B T\ln 2.
\]
The winding quantum $\Delta w=1$ is the geometric carrier of this step; the
Landauer energy is its thermodynamic dress. Beneath: a topological transition.
Above: a thermal energy amount.

\textbf{[K]} \textbf{Limits.} The derivation presupposes that the bit transition
may be identified with the winding quantum -- that is the physical claim that is
not reduced further. The Landauer energy $k_BT\ln2$ is a lower bound; actual
erasure operations cost more. Whether exactly $\Delta w=1$ is the only possibility
to erase a bit is the second open question (see below).

\section{The Reversal Test}

\textbf{[B]} The projection chain (A090) is lossless in one direction and not in
the other. For the concept of information this means: the question ``how much
information is lost?'' has an answer only for type I and type II; for type III
the answer is zero.

In unrolling (type I) the loss can be exactly named -- it is the winding number,
specifically one integer per direction. This is the only place in the series where
an information loss can be \emph{exactly} quantified, and it is, because the lost
quantity is integer-valued.

\section{Verification Script}

\begin{itemize}
  \item Integer-valuedness, coordinate-freedom, and scale-independence of $\Delta w$;
    countercheck that a cell-based entropy depends on the partition and a spectral
    one does not:
    \texttt{python/A\_Serie\_Skripte/a180\_windungsquant.py}
\end{itemize}

\section{Symbol Glossary}

Symbols used throughout the entire A-series are explained in A010.
Specific to this document:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\begin{tabular}{lp{9cm}}
\toprule
Symbol & Meaning \\
\midrule
$S_L = k_B\ln 2$ & Landauer energy; minimum cost per erased bit \\
$\Delta w$ & Winding change; topological discreteness of information change \\
$I_\text{max}$ & Maximum information at given energy \\
$E_L = k_BT\ln 2$ & Landauer bound at temperature $T$ \\
\bottomrule
\end{tabular}}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Open Questions}

\textbf{First, the derivation presupposes that bit transition and winding quantum
may be identified.} That is the core physical claim; it is not reduced further.
The derivation is carried out in A180 (above), but the claim that exactly
$\Delta w=1$ carries a bit is a stipulation -- not forced by the topology alone.

\textbf{Second, it has not been shown that $\Delta w=1$ is the \emph{only}
invariant unit.} Shown is that it is invariant and that cell-based alternatives
are not. That is less.

\textbf{Third, an entropy formula is missing.} This series contains no written-out
entropy as a function of the spectrum -- only the finding that such a function would
automatically be invariant. That is a programme, not a result.

\section{Supersedes}

This document subsumes: Dok.~243, 255, 257 (information), Dok.~290
(magnitude/phase), Dok.~301 (winding quantum), Dok.~302 (unit cells and
partition invariance).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
