\section{The Thesis}

\textbf{[STIPULATION]} The Standard Model is in this theory not a competing
framework but the \emph{decompactified projection} of the compact structure.

What in the Standard Model appears as a list of independent inputs -- masses,
couplings, mixing angles -- are in this reading projection images of a structure
with fewer degrees of freedom.

\section{What the Projection Explains}

\textbf{[B]} Three features of the Standard Model become, in this reading,
consequences and not assumptions:

\textbf{The number three.} Three generations follow from the $Z_3$ structure
(A030, A110). In the Standard Model it is an observation without reason.

\textbf{The hierarchy.} The orders of magnitude of the lepton masses follow the
$\xi$-ladder (A100), at the per cent level. In the Standard Model the Yukawa
couplings are free parameters without ordering among themselves.

\textbf{The form of the mass relation.} The Koide relation $Q=2/3$ is an operator
condition, not coincidence (A110). In the Standard Model it has no standing.

\section{What the Projection Does Not Explain}

\textbf{[STIPULATION]} This section is the longer one, and that is the honest
finding.

\textbf{The gauge group -- three convergent arguments.}

\textbf{[B] Argument 1: Charge quantisation from torus flux.}
The electric charge arises from topologically quantised flux lines through the
torus: $\Phi=n\cdot h/e$ with $n\in\mathbb{Z}$. The quantisation is topologically
protected -- the torus has two non-contractible loops (toroidal and poloidal), the
flux through them is invariant under continuous deformations. $U(1)_\text{EM}$
follows from the torus topology, not from a postulated gauge symmetry.

\textbf{[B] Argument 2: Colour charge from linking number.}
The colour charge of QCD arises from the topological linking (linking number) of
exactly three flux threads around the torus. Three colours (red, green, blue) =
three threads: $SU(3)_C$ is topologically forced by the triple-linking structure
of $T^4/\mathbb{Z}_3$.

\textbf{[S] Argument 3: $SU(27)$ group chain decomposition.}
From $27=3^3$ ($\mathbb{Z}_3$-torus) follows the chain
$SU(27)\supset SU(9)^3\supset SU(3)^9\supset SU(3)\times SU(2)\times U(1)$.
This makes the SM gauge group the canonical subgroup of the symmetry breaking.

\textbf{What is still missing:} Arguments 1 and 2 deliver $U(1)$ and $SU(3)$
from the torus topology. $SU(2)_L$ follows from the chiral projection (A095).
What is not written out: an explicit mapping of the torus topology to the covariant
derivatives $D_\mu = \partial_\mu + igA_\mu^a T^a$ -- i.e.\ the transition from
the topological charge structure to the gauge Lagrangian
$-\tfrac14 F_{\mu\nu}^a F^{a\,\mu\nu}$.

\textbf{The coupling constants.} Their values and their running are not the
subject of the A-series. For $\alpha$ the status is clarified in A130:
calibrated, not derived.

\textbf{The mixing matrices.} CKM and PMNS do not appear.

\textbf{The Higgs sector -- consistency check near proof.} A complete 1-loop
EFT-matching calculation (carried out in the legacy corpus) derives:
\[
  \xi = \frac{\lambda_h^2 v^2}{16\pi^3 m_h^2}
\]
with $\lambda_h=m_h^2/(2v^2)$, $v=246\,\text{GeV}$, $m_h=125{.}09\,\text{GeV}$.
Numerically: $\xi_\text{EFT}=1{.}303\times10^{-4}$, deviation from
$\xi_0=4/30000$ only $2{.}3\,\%$. The $16\pi^3$ structure is the natural result
of the 1-loop suppression and NDA normalisation -- no fitting.

\textbf{[S]} \textbf{Two restrictions that together are decisive.}

\textbf{First}, the EFT calculation delivers a lepton-specific $\xi$
($\xi_e\approx6{.}7\times10^{-14}$, $\xi_\mu\approx2{.}9\times10^{-9}$), not the
universal $\xi_0$. The numerically close value $\xi_\text{EFT}\approx1{.}303\times10^{-4}$
is the value for a reference fermion at $\mu=m_h$ in the $\overline{\text{MS}}$
scheme.

\textbf{Second, the $2{.}3\,\%$ deviation is structurally expected} -- from two
independent reasons that act together:

\textbf{(a) Unrolled SI values.} The formula
$\xi_\text{EFT}=m_h^2/(64\pi^3 v^2)$ contains $v=246\,\text{GeV}$ and
$m_h=125{.}09\,\text{GeV}$ -- SI measured values in the $\overline{\text{MS}}$
scheme, scheme-dependent and only at 1-loop level. A $2{.}3\,\%$ deviation
corresponds to a $1{.}1\,\%$ deviation in $v$, which lies within the theoretical
uncertainty of 1-loop matchings (typically $1$--$5\,\%$ without NNLO corrections).

\textbf{(b) Fractal corrections are not cleanly separable in $v$.} The measured
VEV $v=246\,\text{GeV}$ absorbs all SM quantum corrections -- the fractal torus
structure $D_f=3-\xi$ is not separately visible therein but is implicitly
contained in the measurement and mixed with the SM loops. The EFT matching in
flat space with integer dimension $D=3$ cannot cleanly extract $K_\text{frak}=(1-100\xi)$,
leading to a systematic inaccuracy. Numerically:
$\xi_\text{EFT}/K_\text{frak}^{3/2}\approx1{.}330\times10^{-4}$, deviation from
$\xi_0$ only $0{.}3\,\%$ -- but that is a post-hoc correction, not a proof.

In short: the deviation is structurally expected, because two different description
levels -- flat perturbative QFT and fractal torus geometry -- do not see the same
effective $v$ value.

\textbf{$\xi_\text{EFT}$ must therefore not be used to calculate $\alpha$ or
$E_0$.} That would be a circularity trap: one would run SI measured values ($v$,
$m_h$) through the FFGFT formulas and count the result as confirmation, even
though the SI values themselves carry the deviation. The formulas of the A-series
use exclusively $\xi_0=4/30000$.

$\xi_\text{EFT}$ is a Wilson coefficient (scheme- and scale-dependent);
$\xi_0$ is the geometric ratio $L_0/\ell_P$ (scheme-independent). That both agree
to $2{.}3\,\%$ -- in a calculation using SI measured values with built-in
theoretical uncertainty -- is the consistency finding. No more, but also no less.

\textbf{[B]} The balance reads: the theory explains the \emph{ordering} of the
fermion sector and not the gauge sector. That is a partial statement, and
presenting it as an explanation of the Standard Model would be an overreach.

\section{Why the Projection Loses Information}

\textbf{[B]} According to A090, the spatial projection (type II) is not
reversible. From this it follows that the Standard Model \emph{cannot} fully
reproduce the compact structure -- regardless of how precisely one measures it.

This is testable, though difficult: what does not completely disappear in the
projection leaves a residual of order $\xi$, and the four prediction quantities
of the series are precisely these residuals (A090, A210).

\section{Verification Script}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Numerical verification of projection-chain steps and mass ratios from
    A090/A100:
    \texttt{python/A\_Serie\_Skripte/a090\_proj.py} (shared with A090).
\end{itemize}

\section{Open Questions}

\textbf{First, the gauge sector is completely missing.} Without it the claim that
the Standard Model is a projection is untested for the largest part of the
Standard Model.

\textbf{Second, the projection mapping is not written out.} There is in this
series no explicit mapping from $T^4/Z_3$ to the fields of the Standard Model --
only the claim that it exists, and examples in the fermion sector.

\textbf{Third, the statement in its present form is not falsifiable.} As long as
the mapping is missing, the thesis can be neither confirmed nor refuted. It is a
programme.

\section{Supersedes}

This document subsumes: Dok.~019 (Standard Model), Dok.~097 (QFT), Dok.~141
(SM parameters), Dok.~298 (SM as projection).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
