\section{How the Theory Can Fail}

\textbf{[STIPULATION]} A theory that cannot fail at anything says nothing. The
A-series therefore carries exactly four quantities at which it can be refuted.
They are ratios or structural statements -- never pure absolute values, since
absolute values are bookkeeping (A080, A130). The first, the $\tau$-mass, is the
sharpest: a genuine prediction of a measurable value, because the ratio structure
of the leptons binds so tightly.

That there are only four is not a lack of courage, but a consequence of the
projection chain (A090): only few quantities survive the projection from the
compact structure into the observed world. What disappears in the projection is
not measurable -- not through ineptitude, but structurally.

\section{The Four Prediction Quantities}

\textbf{[K]} \textbf{First: the $\tau$-mass.}
\[
  m_\tau^\text{pred} = 1776{.}968\ \text{MeV},
\]
from $(m_e, m_\mu)$ and the structural numbers $(\sqrt2, 2/9)$ (A110). Against
PDG $1776{.}86\pm0{.}12$ that is $+0{.}90\,\sigma$. A measurement to $0{.}05$ MeV
decides: if the value lands near $\approx 1776{.}97$, the pair $(\sqrt2, 2/9)$ is
confirmed to $10^{-5}$; significantly below, it is refuted. This is the sharpest
point of the series and its actual prediction core: the theory \emph{does} predict
the \textbf{lepton masses}. Unlike $\alpha$ or $G$, here a numerical value stands
\emph{before} the measurement -- no bookkeeping, no anchor choice, but a genuine
prediction, because the ratio structure forces the third mass from two.

\textbf{[K]} \textbf{Second: the $\xi$-order of the CHSH deviation.} The Bell
value falls short of the Tsirelson bound by a residual of order $\xi$, i.e.\
$10^{-4}$ to $10^{-5}$ (A160). Direction fixed (reduction), order of magnitude
fixed (not adjustable), scaling fixed (logarithmic). Not resolvable today; a CHSH
value above the bound or significantly below without hardware explanation refutes
the theory.

\textbf{[K]} \textbf{Third: the fractal dimension.}
\[
  D_f = 3 - \xi = 2{.}99986667 .
\]
A geometric structure with a measurably different dimension from $3$ in exactly
this size -- or its absence where the theory requires it -- decides. $D_f$ is
$\xi$ in geometric dress; the deviation from $3$ \emph{is} $\xi$.

\textbf{[K]} \textbf{Fourth: the fundamental length as anchor point.} The
definition
\[
  L_0 = \xi\,\ell_P
\]
places the fundamental length of the theory in relation to the Planck length.
Below this sub-Planck scale the theory makes no statement (A130). $L_0$ is the
lower bound of validity of the relative description; a structure that showed
$\xi$-ratios even below it would speak against it.

\textbf{The numerical value is an anchor matter, not a test.} $L_0 = \xi\,\ell_P$
is the \emph{only} anchor point at which the theory is bound to an absolute scale
-- and like any anchor, it can be set differently depending on one's viewpoint
(against the Planck length, against the Planck time, against $1/\xi$). \emph{Which
anchor} is chosen is convention; falsifiable is solely the $\xi$-scaling: that the
boundary lies at $\xi$ times the Planck scale and not at another power.

\textbf{The numerical value itself does, however, require care -- it is not
arbitrary.} At the standard anchor (Planck length):
\[
  L_0 = \xi\,\ell_P = \tfrac{4}{30000}\cdot 1{.}616\cdot10^{-35}\,\text{m}
       = 2{.}155\cdot10^{-39}\,\text{m}.
\]
An occasionally appearing value $5{.}39\cdot10^{-39}$ m is \emph{not} a valid
anchor variant but a transcription error: the mantissa $5{.}391$ is that of the
Planck \emph{time} ($t_P = 5{.}391\cdot10^{-44}$ s), and the value implies
$\xi = 3{.}34\cdot10^{-4}$ instead of $4/30000 = 1{.}333\cdot10^{-4}$ -- a
factor $2{.}5$ too large. Convention is the \emph{choice} of anchor; the
numerical value at a given anchor is not.

\section{Why They Must Be Ratios}

\textbf{[B]} All four are dimensionless or traceable to $\xi$. This is no
coincidence but a principle: only ratios are intrinsic (A080). An absolute value
-- e.g.\ ``$G = 6{.}674\cdot10^{-11}$'' -- is bound to a unit choice and can
neither confirm nor refute the theory, because it depends on the scale that is
itself an input.

That is why $\alpha$ is not on the list, even though A130 treats it in detail:
its numerical value is bookkeeping. And that is why the $\tau$-mass is on it,
even though it is a mass: what is tested is not its absolute value but the
\emph{ratio} that $(\sqrt2, 2/9)$ forces between the three lepton masses.

\section{What Is Not a Test Quantity}

\textbf{[STIPULATION]} Explicitly \emph{not} counted as falsification:

The agreement of $\alpha$ with $1/137$ (bookkeeping, A130). The numerical value
of $G$ (bookkeeping, A145). The ladder ratios at the per cent level (too coarse,
check points not predictions, A100). The neutrino sector (not testable, A150).
The thesis ``SM is a projection'' as long as the mapping is missing (A190).

This honesty belongs to falsifiability: listing as a test quantity something one
cannot sharply test simulates testability.

\section{Verification Script}

\begin{itemize}
  \item The four prediction quantities with value, comparison quantity, and
    decision criterion; and the demonstration that each is dimensionless or
    traceable to $\xi$:
    \texttt{python/A\_Serie\_Skripte/a210\_prognosegroessen.py}
\end{itemize}

\section{Open Questions}

\textbf{First, three of the four are not sharply measurable today.} Only the
$\tau$-mass is within reach of running experiments. The other three are
\emph{in principle} testable, but not yet in practice. That is honest to name.

\textbf{Second, the completeness of the list is not proved.} That exactly four
quantities survive the projection is an inventory (A090), not a derivation. A
fifth is not excluded.

\section{Supersedes}

This document collects the test quantities from A090, A110, A120, A130, A160 and
presents them as a closed list. It subsumes: Dok.~292 ($\tau$-prediction),
Dok.~142 (CHSH), Dok.~101 ($L_0$, $D_f$), and the falsification and no-go
statements from Dok.~249, Dok.~074 (no-go), and Dok.~193. Incorporated: R52
(numerical value of $L_0$ at the standard anchor corrected; $5{.}39\cdot10^{-39}$ m
rejected as transcription error).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
