\section{Purpose: Residuals in One Place}

\textbf{[STIPULATION]} Every document of the series closes with ``Open
Questions''. This document collects these residuals in one place, so that the
open frontier of the theory is visible as a whole -- not scattered, not glossed over.

A residual is not a weakness to be hidden. It is the edge at which work continues.
A theory without named open points is either finished or dishonest; this one is neither.

\textbf{Note:} This edition reflects the state after the A-series extension
2026-07 (Blocks 0--3 complete, A095 and A192 new, several points raised or
closed). Points previously listed as open but since closed are no longer carried here.

\section{Closed Points (Since Last Edition)}

\textbf{[K]} The following points were open in earlier editions of A230 and have
been closed in this session:

\begin{itemize}[leftmargin=2em,itemsep=3pt,topsep=3pt]
  \item \textbf{$g_R=0$ from torus projection.} Was [S]. Now [B]: the Fourier
    projector $P_+$ annihilates the $|1,-1\rangle$ state algebraically;
    $g_R=\langle0|H|0\rangle=0$ follows from the kernel of $P_+$ (A095).
  \item \textbf{CHSH prefactor $\xi/(2\pi)$.} Was unexplained. Now [B]:
    $2\pi$ is the circumference of the unit circle; the phase correction per
    measurement is $\xi/(2\pi)$ (A160).
  \item \textbf{Cumulative CHSH formula $\text{CHSH}^{\text{T0}}(n)$.} Now [B]:
    $\xi\ln n/D_f$ integrates over $D_f$ fractal dimensions; $2\pi$ is absent
    because the relevant integration length is $\ln n$, not the circumference (A160).
  \item \textbf{Gauge sector $U(1)$ and $SU(3)$.} Was fully open. Now [B]:
    $U(1)_\text{EM}$ from flux quantisation $\Phi=n\cdot h/e$ on the torus;
    $SU(3)_C$ from linking number of three threads ($\dim(su(3))=8$ geometrically
    proved). $SU(2)_L$ from chiral projection (A095). Open edge: covariant
    derivatives $D_\mu$ not written out (A192).
  \item \textbf{Higgs-EFT 2.3\% deviation.} Now explained [S]: SI values are
    scheme-dependent (1-loop) and fractal corrections in $v$ not separable.
    $\xi_\text{EFT}/K_\text{frak}^{3/2}\approx1{.}330\times10^{-4}$, residual
    only 0.3\,\% -- but post-hoc correction, not proof (A190).
  \item \textbf{Gravitational quantisation.} Was a demand. Now declared:
    not required; $G=\xi^2/(4m_\text{char})$ is intrinsic (A140, A142).
  \item \textbf{$\xi$-proof demand.} Was open. Now declared: no proof possible
    or necessary; $\xi$ is a fundamental parameter with five plausibility
    reasons (A015).
\end{itemize}

\section{The One Large Open Point}

\textbf{[STIPULATION]} Above everything stands a residual that generates several
others: the \emph{measurement process} is not modelled (A090).

Which compact direction is unrolled and which becomes space is deferred to the
measurement process and not resolved there. From this follow the openness of the
unrolled direction (A060), the interpretational openness of Bell (A160), and the
question of what distinguishes the observer as an embedded object (A090). Whoever
closes this one point closes several.

\section{Residuals of the Foundation (A020--A090)}

\textbf{[STIPULATION]} \textbf{Absolute scale (A020, A085, A100, A130).}
The reduction to one dimension is derived; what size this dimension has is not.
The same gap appears as the order of magnitude of $\xi$ (A020), as the
calibration of $E_0$ (A130), as the bridge constant $v$ (A100) -- one gap in
several guises, not several gaps.

\textbf{[STIPULATION]} \textbf{Factor 100 in $K_\text{frak}$ (A040).}
Any integer factor closes the Pythagorean comma equally well; $100$ is
consistency, not necessity.

\textbf{[STIPULATION]} \textbf{Non-closure quantity $\delta$ (A050).}
The recursion cannot fix it; free.

\textbf{[S]} \textbf{$\mathbb{C}^3$ fibre and generations (A070).}
The assignment is interpretation, not derivation.

\textbf{[STIPULATION]} \textbf{Holographic completeness type II (A090).}
Whether type-II loss is exactly reconstructible from boundary data is open.

\textbf{[STIPULATION]} \textbf{Why $P_+$ and not $P_-$ (A095).}
$g_R=0$ is now [B]; why nature selects $P_+$ (orientation argument) remains [S].

\section{Residuals of the Sectors (A100--A192)}

\textbf{[STIPULATION]} \textbf{$\theta=2/9$ (A120).} Geometric source
$C_3\subset A_5$ known as a second witness; derivation from the stipulations is
missing. Empirically sharp to seven places, structurally contingent.

\textbf{[STIPULATION]} \textbf{Ladder exponents $p_i$ (A100).}
Geometric sequence $p_{n+1}=\tfrac23p_n$ established [K] for leptons and Up-type
quarks (up to Charm); for Top ($p_t=-1/3$) and Down-type ($\Delta p=-1/2$) the
geometric justification is missing.

\textbf{[STIPULATION]} \textbf{$r=\sqrt2$ as stipulation (A110).}
Algebraic consequence: $Q=2/3$. No derivation from $\xi$ alone.

\textbf{[STIPULATION]} \textbf{$\kappa=4$ in $E_0=e^2$ (A130).}
Whether the four follows from $\dim(T^4)$ or is an entry point remains open.

\textbf{[STIPULATION]} \textbf{Characteristic mass in $G$ (A145).}
$G=\xi^2/(4m_\text{char})$: $m_\text{char}$ not uniquely fixed. Gravitational
dynamics and inverse-square law completely missing (A140).

\textbf{[STIPULATION]} \textbf{Quark sector (A150, A075).}
No counterpart to the circulant level; Hopf algebra and Feynman rules for
interactions missing.

\textbf{[STIPULATION]} \textbf{Neutrino sector (A150).} Not testable.

\textbf{[S]} \textbf{CHSH $\xi$-residual measured (A160, A165).}
IBM Heron r2 (May 2026) confirms Bell violation ($S=2{.}74$); device-to-device
variation $\sim1{.}4\,\%$ exceeds $\xi$ effect by factor~1400. Not resolvable
in principle with NISQ hardware.

\textbf{[S]} \textbf{Path assignment of entanglement (A160).}
Which closed paths correspond to which entanglement states: sketch.

\textbf{[S]} \textbf{Landauer connection (A180).}
$\Delta w=1\leftrightarrow k_BT\ln2$: connection justified [B], but that
$\Delta w=1$ is the \emph{only} invariant unit has not been shown.

\textbf{[STIPULATION]} \textbf{Gauge sector (A190, A192).}
$U(1)$ and $SU(3)$ from torus topology [B]; $SU(2)_L$ from chiral projection [B].
Open edge: covariant derivatives $D_\mu=\partial_\mu+igA_\mu^aT^a$ not written
out; coupling constants $g_s$, $g_w$, $e$ not from $\xi$; Higgs mechanism
$SU(2)\times U(1)\to U(1)$ not from torus topology; CKM/PMNS missing.

\textbf{[STIPULATION]} \textbf{Block-3 additions.} Exponent $41/4$ in A265
calibrated to $H_0$, not derived. $\alpha=1$ stipulation (A267) worked out for
EM only. Mass-free Dirac formulation (A263) for free fields only.

\section{Findings for the Correction Register}

\textbf{[STIPULATION]} For booking in Dok.~190 (author's responsibility):

\textbf{Symbol collision $\kappa$:} Mass exponent $\kappa=7$ (Dok.~009, correct)
vs.\ energy-scale exponent (Dok.~101, erroneously $7$ instead of $4$). In
Dok.~101, $\kappa=7$ with $E_0\approx33{.}12$ gives $1/\alpha=6{.}84$; correct
is $\kappa=4$, $E_0=e^2$.

\textbf{$\alpha$ labelling:} ``Derivation'' (Dok.~011, 043) to be refined to
``calibration / SI bookkeeping''; substance correct (A130).

\section{What the Residual Picture Shows}

\textbf{[B]} Since the last edition the picture has shifted: the gauge sector is
no longer fully open but at [B] level for $U(1)$ and $SU(3)$; chirality has been
raised from [S] to [B]; the CHSH prefactor is geometrically justified. The two
large construction sites remain -- measurement process and complete gauge sector
-- but the gauge-sector site has shrunk.

The pattern is stable: a load-bearing core (geometry, units, lepton ratios, three
gauge groups topologically), two large construction sites (measurement process,
covariant derivatives and coupling constants), and a series of smaller declared
stipulations.

\section{Open Questions}

\textbf{First, the collection is as complete as the sources.} A230 bundles the
residuals of the other documents; an open point not named there is also missing here.

\textbf{Second, this document does not weight.} Exception: the measurement process
is explicitly the largest; all others stand without ranking (A200).

\textbf{Third, ``open'' is not ``unsolvable''.} The list says where the theory is
incomplete, not whether the gaps are closable.

\section{Supersedes}

This document collects the ``Open Questions'' sections of all A-documents (state:
A-series extension 2026-07). It generates no new statements, but bundles existing
ones and records points closed since the last edition.

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
