\section{Purpose: The External Boundary}

\textbf{[STIPULATION]} The A-series describes \emph{one} theory. It stands
alongside other frameworks -- the Standard Model, General Relativity, and various
independent works. This document draws the boundary: what the series claims, what
it does not, and how it relates to established frameworks.

The purpose is demarcation, not comparison. The series does not appear as a
competitor that refutes something; it appears as a reordering that reads the same
things differently.

\section{On the Standard Model}

\textbf{[B]} The series \emph{contradicts} the Standard Model at no tested point.
The CHSH value remains $2\sqrt2$ (A160), the masses agree within their tolerances
(A100, A110), the constants are the same in a different notation (A130).

\textbf{[STIPULATION]} What it adds is an ordering: three generations from
$Z_3$, the mass hierarchy from $\xi$, the Koide relation as an operator condition
(A190). What it adds beyond the fermion sector: $U(1)_\text{EM}$ from flux quantisation
and $SU(3)_C$ from linking number are derived from the torus topology [B] (A192).
What is missing: covariant derivatives, coupling constants, CKM/PMNS -- the
operational gauge sector is not written out (A190, A192). The series is therefore
not a replacement of the Standard Model but an attempt to justify its fermion and
gauge sectors -- the latter topologically established but not fully executed.

The formula connections on which everything rests are those of the Standard Model
and SI metrology; the series computes within them, it does not replace them (A130).

\section{On General Relativity}

\textbf{[STIPULATION]} The series gives $G$ an expression from $\xi$ (A145) and
argues that the quantum gravity problem does not arise in its form (A140). But it
delivers \emph{no} field equations and does not reproduce the classical
gravitational dynamics.

It therefore stands not in competition with General Relativity but beneath it: it
says something about the \emph{constant} $G$, nothing about the \emph{dynamics}
that Relativity describes. Where Relativity is a theory of gravitation, the series
is at this point a programme.

\section{On Independent Frameworks}

\textbf{[STIPULATION]} In the vicinity of the theory there exist further
independent works -- among others on icosahedral selection structures, on
projector-based memory models, and on golden-ratio-based approaches. The A-series
does not treat these as parts of itself. Detailed comparisons stand where they
belong: in independent comparison documents outside this series, not in the
canonical FFGFT text.

\textbf{[B]} Where such a work shares a structure -- for example the
$\varphi$-icosahedral object in which $2/9$ appears forward (A120) -- that is a
\emph{point of contact}, not evidence. A shared object does not confirm a number;
it only shows that two frameworks stand at the same point. The series records such
points of contact for what they are, not as derivations.

\textbf{[STIPULATION]} This restraint is methodological. Supporting a thesis
through agreement with a second, likewise unproved framework shifts the burden of
proof rather than bearing it. The A-series rests on its own stipulations and their
consequences, not on external frameworks.

\section{What the Demarcation Is Not}

\textbf{[B]} The external boundary is not a valuation. That the series does not
treat the gauge sector does not make the Standard Model superior and the series
inferior -- they address different questions. That the series gives no field
equations does not make it wrong, but incomplete at a named point (A140).

Demarcation means: saying what one speaks about and what one does not. This is the
prerequisite for the series' claims to be testable at all -- one must know against
what to measure them.

\section{Verification Script}

This document contains no computational statements -- it draws conceptual
boundaries to external frameworks. A numerical verification script is not
applicable.

\section{Open Questions}

\textbf{First, the relation to the gauge sector is unresolved.} As long as the
projection mapping is missing (A190), it is not decided whether the gauge sector
\emph{could} follow from the geometry or whether it stands beside it.

\textbf{Second, the points of contact with independent frameworks have not been
evaluated.} That several frameworks stand at $2/9$ or the $\varphi$-icosahedron
is noted, but not examined as to whether a common deeper structure lies behind it.

\section{Supersedes}

This document demarcates the series from external frameworks. It subsumes the
corresponding parts of Dok.~019 (Standard Model), Dok.~127 (gravitation),
Dok.~293 (icosahedral point of contact). The detailed framework comparisons
(Dok.~246, 251, 252, 269, 271, 272) remain independent and are \emph{not}
incorporated into the series.

\section{Use of AI Tools}

This document was created with the assistance of AI tools. The questions,
stipulations, and all substantive decisions come from the author; the tools
formulate, compute, and create verification scripts.
Responsibility for content and errors rests entirely with the author.
Full wording of the rules in A010.
