\section{Purpose}

\textbf{[STIPULATION]} This document treats three structural ``ugliness'' of the
Standard Model and their T0 explanation: (1) chirality of the weak interaction,
(2) gravitation as a separate tensor term, (3) absence of magnetic monopoles.
In all three cases FFGFT provides a geometric explanation from the energy field
$E_\text{field}(x,t)$ and the parameter $\xi$. Methodological restriction: parts
of the derivation are still in development; what counts as proof and what as sketch
is explicitly marked.

\section{Chirality: Left-Handedness of the Weak Interaction}

\textbf{[B]} In the Standard Model the exclusive left-handedness of the weak
interaction is an input. In FFGFT it has a geometric basis that follows from
half-integrality on the torus.

\textbf{Half-integrality and inside/outside asymmetry.} Spin-$\tfrac12$ follows
from the winding number $w=n_\phi/n_\theta=\tfrac12$ (winding (1,1) on $T^4$,
720° symmetry). The decisive consequence: the torus has an \emph{inside and
outside} with different effective couplings. The electric field on the outside
points topologically fixed inward (electron) or outward (positron) -- the direction
is prescribed by the winding geometry, not freely choosable.

\textbf{[B]} After the projection $T^4\to\mathbb{R}^3\times\mathbb{R}_t$ (A090),
inner and outer coupling appear as different chiral states. The projection is not
symmetric: the compact topology selects one coupling direction. Left-handed coupling
is the outer perspective, right-handed the inner perspective -- and the weak
interaction couples exclusively to the projected outer state.

\textbf{[S]} \textbf{What has not yet been carried out.} The qualitative mechanism
is clear: half-integrality $\Rightarrow$ inside/outside asymmetry $\Rightarrow$
chiral projection. What is missing: an explicit computation showing that $g_R=0$
(not $g_R=-g_L$) follows from this projection. That is the open quantitative
edge -- not the basic idea.

\section{Gravitation as Field Gradient}

\textbf{[S]} In the SM gravitation is a separate tensor field ($G_{\mu\nu}$). In
FFGFT gravitation is the gradient of the same energy field that also describes
particle masses. The nonlinear field equation:
\[
  \Box E_\text{field} + \xi\,E_\text{field}^3 = 0.
\]

\textbf{[K]} \textbf{Equivalence in the weak field.} For $E_\text{field}=E_0(1+h)$
with small perturbation $h$, the field equation linearises to a form that is
equivalent to the linearised Einstein equation. The full covariant tensor
formulation $g_{\mu\nu}(E_\text{field})$ with Riemann and Ricci tensors is worked
out in the legacy corpus. This is a \textbf{[K]} result: equivalence in the weak
field is shown; completeness of the equivalence in the strong field is not at
proof level.

\section{Magnetic Monopoles}

\textbf{[S]} Magnetic monopoles are absent in the SM; their absence is unexplained.
In FFGFT they are topological excitations of the energy field and satisfy the Dirac
quantisation condition $q_e q_m = 2\pi n\hbar$. Their rarity is a consequence of
the high energy threshold $\sim E_P/\xi\approx7{.}5\times10^3\,E_P$ -- far beyond
any currently achievable energy.

\textbf{[S]} \textbf{Status.} The topological argument is plausible; a direct
proof that the T0 energy-field monopole exactly satisfies (and not merely
reproduces) the Dirac quantisation condition is not fully worked out.

\section{Objection-Refutation Table}

\textbf{[K]} Standard objections and their status in FFGFT:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\setlength\tabcolsep{4pt}
\begin{tabular}{p{5.5cm}lp{5cm}}
\toprule
Objection & Status & Comment \\
\midrule
Dimensional inconsistency & Refuted & Normalisation with $E_P$, $L_0$ shown \\
No GR equivalence & Partial & Weak field rigorous; strong field sketch \\
Missing nonlinearity & Refuted & $E^3$ term present, Lagrangian shown \\
No covariance & Refuted & Tensor $g_{\mu\nu}$ constructed \\
Monopole problem & Sketch & Topological interpretation, threshold plausible \\
No renormalisability & Refuted & $[E^4]=4$, renormalisable \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Position in the A-Series}

\textbf{[B]} The chirality question is worked out in A095: the inside/outside
topology of the torus and the chiral projection connect half-integrality (A263)
with the left-handedness of the weak coupling geometrically.

\textbf{[B]} The gravitation-as-field-gradient thesis is related to A142 (time-field
Lagrange): there gravitation is derived from the time field; here from the energy
field. Both approaches need to be checked for consistency -- this has not yet been done.

\section{Verification Script}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Chirality phase difference for left/right-handers; weak-field linearisation;
    monopole threshold from $E_P/\xi$:
    \texttt{python/A\_Serie\_Skripte/a264\_asymmetrie.py}
\end{itemize}

\section{Open Questions}

\textbf{Open quantitative edge: $g_R=0$ from the projection.}
The mechanism half-integrality $\Rightarrow$ inside/outside asymmetry $\Rightarrow$
chiral projection is geometrically clear. What is still missing: the explicit
computation showing that the weak coupling of the projected inner state is exactly
zero -- and not merely smaller than the outer coupling. That is a quantitative task,
not a conceptual one.

\textbf{Gravitation in the strong field is not at proof level.} The weak-field
equivalence is shown; the full nonlinear equivalence is missing.

\textbf{The connection to the projection chain (A090) is not worked out.} Whether
the weak interaction follows from the decompactification is open.

\section{Supersedes}

This document subsumes: Dok.~143 (chirality from energy-field rotation, gravitation
as field gradient, magnetic monopoles as topological excitations, field equation
$\Box E+\xi E^3=0$, covariant tensor), Dok.~144 (objection-refutation table,
renormalisability, SM as effective low-energy theory). \emph{Not} taken over:
excluded applications from Dok.~143/144 ($\Lambda_\text{cosmo}$ value, tension
parameter).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. Responsibility
for content and errors rests with the author. Full wording of the rules in A010.
