\section{Purpose}

\textbf{[STIPULATION]} This document develops three related theses:

\textbf{(1) Redshift as a static geometry effect.} In FFGFT $z$ arises not from
space expansion but from energy loss of the photon in the $\xi$-field along the
light path: $1+z=e^{\xi x}$.

\textbf{(2) Achromaticity.} The mechanism is purely geometric -- it stretches all
wavelengths equally. Earlier presentations of chromatic T0 redshift in the corpus
are recorded as a correction in the correction programme.

\textbf{(3) The SI anchor of the sector.} Both FFGFT and the Standard Model need
an empirical anchor for the transition from natural units to measurable SI
quantities in cosmology. In FFGFT this anchor is the ratio $m_ec^2/k_BT_\text{CMB}$
-- a measured number, not pure geometry. The SM has the analogue: $H_0$ in km/s/Mpc
presupposes $c$, $k_B$, and the megaparsec definition, which are themselves
historical SI conventions.

\section{The Static Redshift}

\textbf{[B]} A photon loses energy linearly with distance travelled in the static
$\xi$-field:
\[
  \frac{dE}{dx} = -\xi\,E
  \;\Rightarrow\;
  E(x) = E_0\,e^{-\xi x}.
\]
The redshift:
\[
  \boxed{\;1+z = e^{\xi x},\qquad z\approx\xi\,x\;\text{ (small }z\text{)}\;}
\]
No scale factor $a(t)$, no Big Bang, no expanding space. Light travel time to an
object with redshift $z$:
\[
  \tau(z) = \frac{\ln(1+z)}{H_0^\text{T0}}.
\]
The function grows without bound -- there is no Big Bang ceiling.

\textbf{[K]} \textbf{Comparison with the Hubble law.} For small $z$: $z\approx\xi x$.
Hubble law: $z=H_0 d/c$. Identification: $H_0=\xi c$. The T0 formulation uses
the Hubble energy $E_H=E_0\cdot\xi^{41/4}$, from which
$H_0^\text{T0}=E_H/\hbar\approx66{.}2\,$km/s/Mpc ($-1{.}9\,\%$ vs.\ Planck).
The exponent $41/4$ is not derived from $\xi$ alone -- that is the named open
point.

\section{Achromaticity: Correction of the Earlier Presentation}

\textbf{[B]} The mature FFGFT mechanism is \emph{fractal path elongation}: the
path through the recursive time geometry is stretched by a factor that depends
solely on the distance -- not on the wavelength of the photon. Hence $1+z=e^{\xi x}$
holds for \emph{all} wavelengths with the same factor.

\textbf{[K]} \textbf{Physical reason.} A \emph{geometric} stretch factor acts on
wavelength and pulse duration in the same ratio -- just as gravitational redshift
and standard cosmological redshift are achromatic. A wavelength-dependent term
would arise only from a dispersive medium effect, not from pure geometry.

\textbf{[K]} \textbf{Consequence.} The observed cosmological redshift is achromatic
to high precision -- FFGFT gets this right. The earlier presentation of chromatic
T0 redshift in earlier versions of the legacy corpus is superseded; the correction
is recorded as a correction entry.

\section{The SI Anchor: Where the Circularity Sits}

\textbf{[B]} This is the methodologically most important section. FFGFT derives
$H_0$ from $\xi$ and $E_0$. The derivation ends with:
\[
  H_0^\text{T0} = \frac{E_H}{\hbar},
  \qquad E_H = E_0\cdot\xi^{41/4}.
\]
Apparently a pure $\xi$-derivation. But $E_0=\sqrt{m_em_\mu}=7{.}398\,$MeV is
a \emph{measured} quantity (A130), and the transition to km/s/Mpc needs $\hbar$
and the megaparsec definition -- both SI conventions.

\textbf{[K]} \textbf{The remaining anchor.} After cancelling the $\hbar c$ factors
(which appear in both length scales $L_\xi$ and $\bar\lambda_e$) what remains is:
\[
  \boxed{\;\frac{m_ec^2}{k_BT_\text{CMB}} = 2{.}176\times10^9\;}
\]
Here $c^2$ (mass $\to$ energy) and $k_B$ (kelvin $\to$ energy) sit -- that is a
ratio of two \emph{measured} quantities: electron rest energy to CMB temperature.
The bridge formula is thus geometry form ($K_\text{geo}\cdot\xi^{41/4}$) \textbf{times}
SI anchor ($m_ec^2/k_BT_\text{CMB}$) -- not a pure geometry identity.

\textbf{[B]} \textbf{Where the exponent changes.} The same ratio sits in the
exponent itself: referenced to the Planck scale instead of $E_0$, the exponent
becomes $63/4=41/4+11/2$, where $11/2$ encodes the SI scale conversion
$\ell_P\leftrightarrow E_0$. The factor never disappears -- it only changes location.

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{lll}
\toprule
Reference scale & Exponent & SI factor explicit as \\
\midrule
$E_0$ (electron/CMB) & $41/4$ & Ratio $m_ec^2/k_BT_\text{CMB}$ \\
$\ell_P$ (Planck)    & $63/4 = 41/4+11/2$ & Additional exponent $11/2$ \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{The SM Has the Same Problem}

\textbf{[B]} The Standard Model gives $H_0$ in km/s/Mpc. This unit presupposes:
$c$ (speed of light in km/s), the megaparsec definition
($1\,\text{Mpc}=3{.}0857\times10^{22}\,\text{m}$, historically from parallaxes),
$k_B$ for temperature measurements, and the SI 2019 reform that fixes $c$, $\hbar$,
$k_B$, and $e$ by definition. These quantities are not independent of one another
-- the measurement chain is self-referential.

\textbf{[B]} Concretely: $T_\text{CMB}=2{.}7255\,$K (Fixsen 2009) is linked to
energy via $k_B$; $H_0\approx67{.}4\,$km/s/Mpc is linked to a length via $c$ and
Mpc; the ratio $m_ec^2/k_BT_\text{CMB}$ connects particle physics with cosmology
-- and this ratio has no place in the SM basic theory. The SM calls it a
measurement; FFGFT attempts to understand it from $\xi$, and comes closer, but
not all the way (the exponent $41/4$ is missing).

\textbf{[S]} \textbf{The honest comparison.} Both frameworks -- $\Lambda$CDM and
FFGFT -- need an empirical anchor for cosmology that lies outside the theoretical
core. In the SM that is $H_0$ itself (a measurement, not a derivation). In FFGFT
it is $m_ec^2/k_BT_\text{CMB}$ plus the not-yet-derived exponent $41/4$. FFGFT
is one step further here -- but not yet completely parameter-free.

\section{Cosmological Degeneracy}

\textbf{[K]} FFGFT and $\Lambda$CDM are \emph{observationally degenerate} on the
standard tests: both reproduce the same fluxes, angular sizes, and time dilations.
The key points:

\textbf{Supernova time dilation:} DES measures $b=1{.}003\pm0{.}011$ (White et al.\ 2024,
Dark Energy Survey, MNRAS). The fractal path elongation stretches wavelength
\emph{and} pulse duration in the same ratio $\Rightarrow b=1$. The test only
excludes non-dilating tired light ($b=0$) -- FFGFT predicts $b=1$ and is not
affected.

\textbf{Hubble tension:} In FFGFT $H_0$ is not an expansion rate but the geometric
energy-loss coefficient. Different measurement methods probe different scales;
systematic variations are geometrically expected. The tension $67{.}4$
(Planck 2018) vs.\ $73{.}0\,$km/s/Mpc (SH0ES) is not a fundamental problem in FFGFT.

\textbf{[S]} \textbf{Honest situation.} The degeneracy cuts both ways: the data
\emph{fit} FFGFT (no wrong prediction), but they do not \emph{force} it. The case
for FFGFT rests on parsimony (no $\Lambda$, no dark energy) and on the $\xi$-derivation
of the constants -- not on a single discriminator.

\section{Verification Script}

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item Numerical verification: $1+z=e^{\xi x}$, achromaticity (same stretch
    factor for $\lambda_1\neq\lambda_2$), SI anchor $m_ec^2/k_BT_\text{CMB}$,
    exponent table $41/4$ vs.\ $63/4$:
    \texttt{python/A\_Serie\_Skripte/a265\_rotverschiebung.py}
\end{itemize}

\section{Symbol Glossary}

Symbols used throughout the entire A-series are explained in A010.
Specific to this document:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small\begin{tabular}{lp{9cm}}
\toprule
Symbol & Meaning \\
\midrule
$z$ & Cosmological redshift; $1+z=\lambda_\text{obs}/\lambda_\text{emit}$ \\
$E_H = E_0\cdot\xi^{41/4}$ & Hubble energy in FFGFT \\
$H_0^\text{T0}\approx66{.}2\,$km/s/Mpc & FFGFT value of the Hubble constant \\
$\tau(z) = \ln(1+z)/H_0^\text{T0}$ & Light travel time in FFGFT \\
$m_ec^2/k_BT_\text{CMB}$ & Empirical SI anchor of the cosmological sector \\
\bottomrule
\end{tabular}}
\renewcommand{\arraystretch}{1.0}
\end{center}

\section{Open Questions}

\textbf{The exponent $41/4$ is not derived from $\xi$ alone.} It is calibrated to
the measured $H_0$. As long as it is missing, FFGFT in the cosmological sector is
not parameter-free.

\textbf{The anchor $m_ec^2/k_BT_\text{CMB}$ needs a geometric explanation.} Why
precisely the ratio of electron rest energy to CMB temperature appears as the
natural transition is an open structural question.

\textbf{BAO and CMB peaks have not yet been derived from FFGFT.} The degeneracy
claim presupposes that the same angular scales are reproducible; the proof in
FFGFT's own formalism is outstanding.

\section{Supersedes}

This document subsumes: Dok.~026 (static redshift as geometric path elongation,
FEM simulation, Hubble energy $E_H=E_0\xi^{41/4}$, derivation
$H_0\approx66{.}2\,$km/s/Mpc), Dok.~280 (static redshift, achromaticity as
correction K6, $z\to$time as $\Lambda$CDM transfer, cosmological degeneracy,
no Big Bang), Dok.~279 (Casimir--$H_0$ bridge formula, SI anchor
$m_ec^2/k_BT_\text{CMB}$, exponent $41/4$ vs.\ $63/4$, location of SI factor).

\section{Use of AI Tools}

This document was created with the assistance of AI tools. Responsibility
for content and errors rests with the author. Full wording of the rules in A010.
