\chapter{Explanation of Quantum Mechanical Phenomena in Fractal T0 Geometry  Narrative Version of FFGFT}


\section*{Explanation of Quantum Mechanical Phenomena in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter explains central quantum phenomena such as interference, entanglement, and tunnelling from the dynamics of the fractal vacuum field — without ontological superposition.
	
	\subsection*{Mathematical Foundation}
	
	Quantum mechanics is based on wave functions and superposition. In the FFGFT, these emerge as mathematical constructs from the phase and amplitude of the vacuum field \(\Phi = \rho e^{i\theta}\), regulated by \(\xi = \frac{4}{3} \times 10^{-4}\). There is no ontological superposition of real states — the vacuum field is always deterministic.
	
	\subsection*{Double-Slit Interference}
	
	The interference pattern arises from the phase difference:
	
	\begin{equation}
		\Delta \theta = \theta_1 - \theta_2.
	\end{equation}
	
	The intensity at the screen:
	
	\begin{equation}
		I \propto 1 + \cos(\Delta \theta).
	\end{equation}
	
	The cosine term generates the interference pattern — classical wave from global vacuum phase.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\Delta \theta] = \text{dimensionless}.
	\end{equation}
	
	\subsection*{Entanglement}
	
	Entangled particles share phase:
	
	\begin{equation}
		\theta_{12} = \theta_1 + \theta_2 = \text{constant}.
	\end{equation}
	
	The sum of the phases is fixed — measurement on one fixes the phase locally, but the field was already globally coherent. There is no instantaneous signal transmission, but pre-existing fractal non-locality.
	
	\subsection*{Tunnelling Effect}
	
	Under the barrier:
	
	\begin{equation}
		P \approx \exp\left( -2 \kappa d \right), \quad \kappa = \sqrt{2m(V-E)} / \hbar \cdot (1 + \xi \ln(d/l_0)).
	\end{equation}
	
	The exponential decay arises from phase accumulation under the barrier, with fractal correction \(\xi \ln(d/l_0)\) for non-locality.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\kappa] = \si{1/m}.
	\end{equation}
	
	\subsection*{Fractal Coherence}
	
	Correlation function:
	
	\begin{equation}
		C(\Delta x) = \xi \ln(\Delta x / l_0).
	\end{equation}
	
	Logarithmic coherence enables interference over large distances — without ontological superposition.
	
	\subsection*{Comparison Standard QM – FFGFT}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard QM} & \textbf{FFGFT (T0)} \\
			\hline
			Postulates & Emergent from phase \\
			Wave-particle duality & Amplitude-phase separation \\
			Collapse & Deterministic dynamics \\
			No gravity & Unified \\
			Ontological superposition & Mathematical construct \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The FFGFT explains quantum phenomena as dynamics of the vacuum phase \(\theta\): interference from path phases, entanglement from global coherence, tunnelling from non-locality. The wave function \(\psi\) is a purely mathematical construct for describing probabilities — not an ontological reality. There is no instantaneous action or retrocausality. Everything parameter-free from \(\xi\), unifies QM with gravity.
