\chapter{Lepton and Neutron Lifetimes in Fractal T0 Geometry}


	
	\subsection*{Brief Introduction}
	
	This chapter covers two aspects of particle lifetimes: (1)~The lifetime ratio \(\tau_\mu/\tau_\tau\) of charged leptons, which FFGFT derives with \(0.19\%\) accuracy from geometric parameters (Doc~160), and (2)~the neutron lifetime discrepancy, to which FFGFT offers a qualitative perspective.
	
	
	\subsection*{Part I: Lepton Lifetime Ratio (Doc~160)}
	
	\subsubsection*{Basic Formula}
	
	The ratio of muon to tau lifetime follows from Fermi theory:
	
	\begin{equation}
		\frac{\tau_\mu}{\tau_\tau} = \left(\frac{m_\tau}{m_\mu}\right)^5 \cdot \frac{f_{\tau \to e}}{f_{\mu \to e}} \cdot \frac{1}{BR(\tau \to e \nu \bar\nu)}
	\end{equation}
	
	where \(f\) denotes phase space corrections and \(BR\) the branching ratio. The fifth power of the mass ratio originates from the \(G_F^2 m^5\) scaling of the weak decay width.
	
	\subsubsection*{Phase Space Corrections}
	
	The function \(f(x) = 1 - 8x + 8x^3 - x^4 - 12x^2 \ln x\) with \(x = (m_\text{daughter}/m_\text{mother})^2\) yields:
	
	\begin{align}
		f_{\mu \to e} &= 0.999813, \quad f_{\tau \to e} = 0.999999, \quad f_{\tau \to \mu} = 0.972560.
	\end{align}
	
	\subsubsection*{T0 Determination of the Hadronic Rate}
	
	The key FFGFT contribution is the geometric determination of the hadronic branching ratio \(R_\text{had} = \Gamma_\text{had}/\Gamma_e\):
	
	\begin{equation}
		\boxed{R_\text{had} = N_{c,\text{eff}} \cdot K_\text{frak} = \left(3 + \frac{D \cdot \xi^{1/4}}{2}\right) \cdot \frac{144}{125} = 3.642}
	\end{equation}
	
	Experimentally: \(R_\text{had}^\text{exp} = 3.636\). \textbf{Deviation: \(+0.16\%\).}
	
	The three components:
	
	\begin{itemize}
		\item \textbf{Strong coupling constant:} \(\alpha_s(m_\tau) = D \cdot \xi^{1/(D+1)} = 3 \cdot \xi^{1/4} = 0.3224\) (\(-2.3\%\) from experiment, within \(0.5\sigma\)). The prefactor \(D = N_c = 3\) corresponds to colour charges as spatial winding dimensions of the torus, the exponent \(1/(D+1) = 1/4\) to dilution across all spacetime dimensions.
		\item \textbf{Effective colour factor:} \(N_{c,\text{eff}} = 3 + \alpha_s/2 = 3.161\)
		\item \textbf{Fractal correction factor:} \(K_\text{frak} = 144/125 = 1.152\) — identical to the factor in the Koide mass formula and the \(g\)-\(2\) bridge (Ch.~24)
	\end{itemize}
	
	\subsubsection*{Result}
	
	\begin{equation}
		\frac{\tau_\mu}{\tau_\tau}\bigg|_\text{T0} = \left(\frac{m_\tau}{m_\mu}\right)^5 \cdot \frac{f_{\tau e}}{f_{\mu e}} \cdot \left(1 + \frac{f_{\tau\mu}}{f_{\tau e}} + R_\text{had}\right) = 7\,553\,123
	\end{equation}
	
	Experimentally: \(7\,567\,689\). \textbf{Deviation: \(-0.19\%\).}
	
	\begin{center}
		\small
		\begin{tabular}{lccc}
			\textbf{Quantity} & \textbf{T0} & \textbf{Experiment} & \textbf{Deviation} \\
			\hline
			\(\alpha_s(m_\tau)\) & 0.3224 & \(0.330 \pm 0.014\) & \(-2.3\%\) \\
			\(\tau_\mu/\tau_\tau\) & 7\,553\,123 & 7\,567\,689 & \(-0.19\%\) \\
			\(\tau_\tau\) & \(2.908 \times 10^{-13}\) s & \(2.903 \times 10^{-13}\) s & \(+0.17\%\) \\
			\(BR(\tau \to e)\) & \(17.81\%\) & \(17.82\%\) & \(-0.05\%\) \\
			\(BR(\tau \to \text{had})\) & \(64.87\%\) & \(64.79\%\) & \(+0.12\%\) \\
			\(R_\text{had}\) & 3.642 & 3.636 & \(+0.16\%\) \\
		\end{tabular}
	\end{center}
	
	All predictions agree with experiment to better than \(0.4\%\). Inputs: only \(\xi = 4/30000\) and experimental lepton masses.
	
	\subsubsection*{What \(K_\text{frak}\) Absorbs}
	
	The factor \(K_\text{frak} = 144/125\) from torus geometry implicitly encodes the electroweak corrections (\(S_\text{EW} = 1.019\)), CKM unitarity (\(|V_{ud}|^2 + |V_{us}|^2 = 0.998\)), and higher-order QCD corrections in a single geometric ratio. The SM calculation with the full perturbative series gives \(R_\tau^\text{SM} = 3.662\) (\(+0.73\%\)), while the T0 formula yields \(3.642\) (\(+0.16\%\)).
	
	
	\subsection*{Part II: Neutron Lifetime Discrepancy}
	
	\subsubsection*{The Problem}
	
	The free neutron lifetime differs by measurement method: bottle experiments yield about \SI{879.5}{\second}, beam experiments about \SI{888.0}{\second} — a difference of roughly \SI{8.5}{\second} (\(\sim 1\%\)).
	
	\subsubsection*{Qualitative FFGFT Perspective}
	
	\textbf{Important caveat:} The technical reference documents contain no quantitative treatment of the neutron lifetime discrepancy. The following discussion is a qualitative consideration within the FFGFT framework.
	
	In FFGFT, the vacuum field \(\Phi = \rho(x,t)e^{i\theta(x,t)}\) is dynamic and in principle environment-dependent. In confined systems (bottle), boundary conditions could slightly modify the local vacuum structure, potentially affecting the effective weak decay rate. This idea is qualitatively plausible — the vacuum amplitude near material surfaces could be altered by fractal boundary conditions.
	
	However, a consistent quantitative derivation is lacking:
	
	\begin{itemize}
		\item The \(\beta\)-decay is governed by the weak interaction (\(G_F\)), not by an energy barrier
		\item The coupling between vacuum structure and weak decay rate would need to proceed via modification of \(G_F\) or the phase space function — this mechanism is not developed in the reference documents
		\item The observed discrepancy of \(\sim 1\%\) has a magnitude near \(\xi^{1/2} \approx 0.012\), which is suggestive but does not constitute a complete derivation
	\end{itemize}
	
	\subsubsection*{Status}
	
	The neutron lifetime discrepancy remains an open problem, both in the Standard Model and in FFGFT. Alternative explanations include experimental systematics, dark decay channels, or sterile neutrinos. FFGFT offers an interesting perspective (environment-dependent vacuum structure) that requires rigorous development.
	
	\subsection*{Conclusion}
	
	FFGFT demonstrates its predictive power most impressively for lepton lifetimes: the ratio \(\tau_\mu/\tau_\tau\) is derived with \(0.19\%\) accuracy from \(\xi\) and the universal factor \(K_\text{frak} = 144/125\) — without free parameters and with the same geometric factor appearing in the Koide formula and \(g\)-\(2\) bridge. The neutron lifetime discrepancy remains as qualitative motivation for future research.


