\chapter{The Neutrino Mass Problem in Fractal T0 Geometry}


	
	\subsection*{Brief Introduction}
	
	This chapter presents the speculative FFGFT hypothesis for neutrino masses: neutrinos as ``nearly massless photons'' with double \(\xi\) suppression. The approach is cosmologically compatible but stands in tension with standard oscillation data. The reference documents (Doc~007, 047) are transparent in this assessment.
	
	\subsection*{Neutrinos as Nearly Massless Photons}
	
	The FFGFT hypothesis is based on a geometric analogy: neutrinos behave like photons with two suppression factors --- ``nearly massless'' and ``weakly interacting'':
	
	\begin{equation}
		\boxed{m_\nu = \frac{\xi^2}{2} \cdot m_e = \frac{(4/30000)^2}{2} \cdot 0.511\text{ MeV} = 4.54\text{ meV}}
	\end{equation}
	
	The double \(\xi\) suppression simultaneously gives the velocity deviation:
	
	\begin{equation}
		v_\nu = c \cdot \left(1 - \frac{\xi^2}{2}\right) \approx 0.9999999911 \cdot c, \quad \Delta v/c = 8.89 \times 10^{-9}.
	\end{equation}
	
	
	\subsection*{Cosmological Compatibility}
	
	The T0 prediction satisfies all experimental upper bounds:
	
	\begin{center}
		\small
		\begin{tabular}{lcc}
			\textbf{Bound} & \textbf{Experiment} & \textbf{T0} \\
			\hline
			\(m_{\nu_e}\) & \(< 0.8\) eV (KATRIN) & 4.54 meV \\
			\(\Sigma m_\nu\) & \(< 0.12\) eV (Planck) & 13.6 meV \\
			\(\Sigma m_\nu\) & \(< 0.07\) eV (DESI+Planck) & 13.6 meV \\
		\end{tabular}
	\end{center}
	
	The T0 prediction lies at 11--20\% of the cosmological upper bounds.
	
	\subsection*{Koide Extension: Quasi-Degenerate Spectrum}
	
	Doc~007 extends the basic hypothesis through a Koide-like perturbation with \(\delta \approx \xi^{1/3} \approx 0.051\), producing a quasi-degenerate spectrum:
	
\begin{equation}
	\begin{aligned}
		m_1 &\approx 4.20\text{ meV},\quad 
		m_2 \approx 4.54\text{ meV}, \\
		m_3 &\approx 5.12\text{ meV},\quad 
		\Sigma m_\nu = 13.86\text{ meV.}
	\end{aligned}
\end{equation}
	
	\textbf{Note on the Koide quotient:} For a quasi-degenerate spectrum, the Koide quotient \(Q = \Sigma m / (\Sigma\sqrt{m})^2\) converges to \(1/3\), not \(2/3\). The T0 neutrino masses yield \(Q_\nu \approx 0.334\), confirming this mathematical behaviour. The value \(Q = 2/3\) of charged leptons requires strongly hierarchical masses.
	
	\subsection*{Tension Point: Oscillation Data}
	
	\textbf{This is the central challenge of the hypothesis.} The experimental mass splittings require significantly larger masses than the T0 prediction:
\begin{center}
	\small
	\begin{tabular}{lccc}
		& \textbf{Experiment} & \textbf{T0 (Koide)} & \textbf{Faktor} \\
		\hline
		\(\Delta m^2_{21}\) 
		& \(7.53 \times 10^{-5}\) eV\(^2\) 
		& \(2.97 \times 10^{-6}\) eV\(^2\) 
		& 25\(\times\) \\
		\(\Delta m^2_{32}\) 
		& \(2.44 \times 10^{-3}\) eV\(^2\) 
		& \(5.60 \times 10^{-6}\) eV\(^2\) 
		& 435\(\times\) \\
	\end{tabular}
\end{center}
	
	The minimum mass sums from oscillation data are:
	
	\begin{itemize}
		\item Normal hierarchy: \(\Sigma m_\nu \geq 58\) meV
		\item Inverted hierarchy: \(\Sigma m_\nu \geq 100\) meV
		\item T0 prediction: \(\Sigma m_\nu = 14\) meV --- factor 4--7 too small
	\end{itemize}
	
	FFGFT addresses this tension through the hypothesis that oscillations are caused by geometric phases rather than mass differences. This mechanism is speculative and not experimentally confirmed.
	
	\subsection*{Geometric Oscillation Hypothesis}
	
	The T0 hypothesis postulates equal masses for all flavours with geometric phase factors as the oscillation mechanism:
	
\begin{equation}
	\begin{aligned}
		\phi_{\text{geo}, i} 
		&\propto f(n, \ell, j) \cdot \frac{L}{E} \cdot \frac{1}{T_x}, \\
		T_x &= \frac{1}{m_\nu} 
		\approx 220\text{ eV}^{-1} 
		\approx 1.45 \times 10^{-13}\text{ s}
	\end{aligned}
\end{equation}
	
	with \(f(n,\ell,j) = n^6/\ell^3\) (or 1 for \(\ell = 0\)):
	
	\begin{center}
		\small
		\begin{tabular}{lcccc}
			\textbf{Flavour} & \(n\) & \(\ell\) & \(j\) & \(f(n,\ell,j)\) \\
			\hline
			\(\nu_e\) & 1 & 0 & 1/2 & 1 \\
			\(\nu_\mu\) & 2 & 1 & 1/2 & 64 \\
			\(\nu_\tau\) & 3 & 2 & 1/2 & 91.125 \\
		\end{tabular}
	\end{center}
	
	\textbf{Warning:} This approach contradicts the established theory that oscillations require \(\Delta m^2_{ij} \neq 0\). It is purely hypothetical.
	
	\subsection*{Comparison Standard Model -- FFGFT}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard Model} & \textbf{FFGFT (T0)} \\
			\hline
			Masses free (Yukawa) & \(m_\nu = \xi^2/2 \cdot m_e\) (no free parameter) \\
			Seesaw mechanism & Double \(\xi\) suppression \\
			\(\Delta m^2 \neq 0\) for oscillations & Geometric phases (speculative) \\
			Three mass spectra possible & Quasi-degenerate enforced \\
			Majorana/Dirac open & Not determined \\
		\end{tabular}
	\end{center}
	
	\subsection*{Experimental Tests}
	
	\begin{itemize}
		\item \textbf{KATRIN upgrade:} Sensitivity \(\sim 0.2\) eV (still too coarse for T0 masses)
		\item \textbf{Euclid/DESI:} \(\Sigma m_\nu\) sensitivity \(\sim 0.02\) eV --- could test T0 prediction (\(0.014\) eV)
		\item \textbf{Supernova neutrinos:} \(\Delta v/c \sim 10^{-8}\) potentially measurable
		\item \textbf{Falsification:} Measurement of \(\Sigma m_\nu > 0.03\) eV with simultaneously confirmed \(\Delta m^2\) would exclude the T0 hypothesis
	\end{itemize}
	
	\subsection*{Conclusion}
	
	The FFGFT neutrino hypothesis has an elegant structure: a single formula \(m_\nu = \xi^2/2 \cdot m_e\) without free parameters that is cosmologically compatible. However, it stands in considerable tension with experimental oscillation data (\(\Sigma m_\nu\) factor 4--7 too small) and requires an unconfirmed geometric oscillation mechanism. The reference documents (Doc~007, 047) are transparent in this assessment and mark the approach as speculative.


