
	
	\chapter{The Koide Mass Formula in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter examines the empirical Koide formula within the FFGFT framework and shows how the exponent structure of particle masses establishes a natural connection to the \(g\)-\(2\) anomaly.
	
	\subsection*{The Koide Relation}
	
	The Koide relation connects the masses of the three charged leptons:
	
	\begin{equation}
		Q = \frac{m_e + m_\mu + m_\tau}{(\sqrt{m_e} + \sqrt{m_\mu} + \sqrt{m_\tau})^2} \approx \frac{2}{3}.
	\end{equation}
	
	Experimentally, \(Q = 0.6666605\), a deviation of only \(6 \times 10^{-6}\) from \(2/3\). This relation is unexplained in the Standard Model.
	
	\textbf{Unit check (Koide ratio):}
	\[
	[Q] = \frac{\si{\kilo\gram}}{(\si{\kilo\gram^{1/2}})^2} = \text{dimensionless}.
	\]
	
	\subsection*{T0 Motivation: Exponent Structure}
	
	In FFGFT, lepton masses follow an exponent hierarchy (Doc~007):
	
	\begin{equation}
		m_i \propto \xi_0^{p_i}, \quad p_i = \left(\frac{3}{2},\; 1,\; \frac{2}{3}\right).
	\end{equation}
	
	The step size between generations is \(\Delta p = 1/3 = 1/D\) — the inverse spatial dimension. This regular structure motivates why \(Q \approx 2/3\): the exponent spacings are geometrically uniform.
	
	\textbf{Important caveat:} The Koide relation \(Q = 2/3\) is an empirical observation. FFGFT \emph{motivates} it through the \(1/3\) step size of the exponent hierarchy but does not provide a closed analytical derivation that exactly proves \(Q = 2/3\). A complete derivation would require the eigenvector representation of the flavour mixing matrix (Doc~007), which is beyond the scope of this chapter.
	
	\subsection*{Eigenvector Representation}
	
	The masses of charged leptons follow the Koide relation via eigenvector representation (Doc~007, Brannen 2005):
	
	\begin{equation}
		\begin{pmatrix}
			\sqrt{m_e} \\
			\sqrt{m_\mu} \\
			\sqrt{m_\tau}
		\end{pmatrix}
		= \mathbf{U} \cdot \begin{pmatrix}
			m_1 \\
			m_2 \\
			m_3
		\end{pmatrix},
	\end{equation}
	
	where \(\mathbf{U}\) is the unitary flavour mixing matrix (CKM/PMNS analogue). The \(Q = 2/3\) property follows from the structure of \(\mathbf{U}\).
	
	\subsection*{Small Deviations from Fractality}
	
	Fractal perturbations \(\delta_i \approx \xi \cdot \Delta k\) shift the phases minimally:
	
	\begin{equation}
		\Delta Q \approx \xi^2 \sum_i (\delta_i / \theta_0)^2 \approx 10^{-8} \ to \ 10^{-7}.
	\end{equation}
	
	This tiny correction lies within the current measurement uncertainty of \(\pm 10^{-5}\).
	
	\subsection*{Extension to Other Particles}
	
	Analogous relations hold for up-quarks (with strong coupling):
	
	\begin{equation}
		Q_{\text{up}} \approx \frac{2}{3} + \xi \cdot \alpha_s(\mu).
	\end{equation}
	
	For neutrinos (Doc~007): \(Q_\nu \approx 2/3\) with \(\Delta Q_\nu < 1\%\), directly linked to the PMNS mixing. Future precision measurements can test these.
	
	\subsection*{Comparison with Other Approaches}
	
	\begin{center}
		\small
		\resizebox{\textwidth}{!}{%
			\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
				\textbf{Other Models} & \textbf{FFGFT (T0)} \\
				\hline
				Numerical fits only & Exponent hierarchy with \(\Delta p = 1/3\) \\
				Additional parameters & Motivated by \(\xi\) and spatial dimension \\
				Leptons only & Extendable to quarks/neutrinos \\
				No justification & Eigenvector representation + fractal perturbation \\
			\end{tabular}%
		}
	\end{center}
	
	\subsection*{Conclusion on the Koide Formula}
	
	FFGFT motivates the Koide formula through the exponent structure \(p = 3/2,\; 1,\; 2/3\) with the regular step size \(\Delta p = 1/3 = 1/D\). The complete derivation requires the eigenvector representation of the flavour mixing matrix. The fractal perturbation through \(\xi\) generates corrections \(\Delta Q \sim 10^{-8}\), consistent with experimental accuracy.
	
	\subsection*{Bridge from Masses to \(g\)-\(2\)}
	
	The same \(1/3\) step size reappears in the \(g\)-\(2\) anomaly hierarchy (Doc~018). The fractal corrections to the anomalous magnetic moments of leptons read \(\Delta a_\ell = 4\pi/f^{p_\ell}\) with the same exponents \(p_\mu = 5/3\), \(p_\tau = 4/3\) (\(\Delta p = 1/3\)). This yields the \textit{exact} ratio:
	
	\begin{equation}
		\frac{\Delta a(\tau - \mu)}{\Delta a(\mu - e)} = f^{1/3} - 1 \approx 18.57
	\end{equation}
	
	\textit{This ratio is mathematically exact because the geometric projection factor \(k_{\text{geom}}\) cancels completely — it depends only on \(f = \xi^{-1} = 7500\).}
	
	From the mass formulas follows \(m_\tau/m_\mu = (125/144) \cdot f^{1/3}\), from the \(g\)-\(2\) formulas \(\Delta a(\tau{-}e)/\Delta a(\mu{-}e) = f^{1/3}\). Combination yields the \textbf{bridge formula} (Doc~018):
	
	\begin{equation}
		\boxed{\frac{\Delta a(\tau{-}e)}{\Delta a(\mu{-}e)} = \frac{144}{125} \cdot \frac{m_\tau}{m_\mu}}
	\end{equation}
	
	\textit{The \(g\)-\(2\) ratio is determined directly by the mass ratio. No \(\alpha\), no \(k_{\text{eff}}\), no \(K_{\text{frak}}\) — everything cancels. This is the purest form of the mass formula-\(g\)-\(2\) connection.}
	
	Applied to experimental values, the bridge formula yields a parameter-free prediction:
	
	\begin{equation}
		a_\tau^{\text{T0}} = a_e^{\text{exp}} + \frac{144}{125} \cdot \frac{m_\tau}{m_\mu} \cdot \Delta a(\mu{-}e)^{\text{exp}} \approx 1.282 \times 10^{-3}
	\end{equation}
	
	\textit{For comparison: the Standard Model calculates \(a_\tau^{\text{SM}} = 1.177 \times 10^{-3}\). The difference lies in the ratio \(\Delta a(\tau{-}e)/\Delta a(\mu{-}e)\): T0 predicts \(19.4\), SM predicts \(2.8\) — a factor of~7, clearly testable at Belle~II.}
	
	In T0, \(g\)-\(2\) predictions are primarily about \textbf{ratios}:
	\begin{itemize}[leftmargin=*]
		\item \textbf{Absolute values:} \(\sim 2\%\) deviation (ideal formula), \(\sim 0.01\%\) with fractal correction
		\item \textbf{Ratio \(\Delta a(\tau{-}\mu)/\Delta a(\mu{-}e)\):} Exactly \(= f^{1/3} - 1\), parameter-independent
		\item \textbf{Bridge to masses:} \(\Delta a(\tau{-}e)/\Delta a(\mu{-}e) = (144/125) \cdot m_\tau/m_\mu\), parameter-independent
	\end{itemize}
	


