\chapter{Ron Folman's T³ Quantum Gravity Experiment in the Fractal T0 Geometry  Narrative Version of FFGFT}


	
	\subsection*{Brief Introduction}
	
	This chapter shows how the T³ experiment interprets the observed T$^3$ scaling as a natural consequence of the fractal vacuum phase -- a testable in principle but experimentally extremely challenging signal.
	
	\subsection*{Mathematical Foundation}
	
	The experiment observes a gravitational phase shift that scales proportionally to \(g T^3\). This \(T^3\) dependence is a natural consequence in the FFGFT of the fractal vacuum phase, regulated by \(\xi = \frac{4}{3} \times 10^{-4}\).
	

	
	\subsection*{The T³ Experiment – What Is Measured?}
	
	In an atom interferometer, the wave packet of an atom is split, the two parts experience different gravitational potentials, and thereby accumulate a relative phase. Classically, one expects a phase shift proportional to \(T^2\), because the path separation \(\Delta z\) grows quadratically with time:
	
	\begin{equation}
		\Delta z(t) = \frac{1}{2} g t^2.
	\end{equation}
	
	The classical phase arises from the energy difference \(m g \Delta z\), integrated over time \(T\):
	
	\begin{equation}
		\Delta \phi_{\text{class}} = \frac{m g \Delta z T}{\hbar} \propto T^3 \quad (\text{only in certain config.}).
	\end{equation}
	
	However, the experiment robustly shows \(T^3\), indicating a deeper structure.
	
	\subsection*{Fractal Vacuum Phase as the Cause}
	
	The vacuum phase \(\theta(x)\) varies spatially. Its gradient couples to gravity:
	
	\begin{equation}
		\partial_i \theta \propto \xi \cdot \frac{g_i}{c^2}.
	\end{equation}
	
	This gradient is proportional to the local acceleration but scaled by the small factor \(\xi\), as the fractality damps the coupling.
	
	The accumulated phase along a path is the time integral of the local phase:
	
	\begin{equation}
		\phi(t) = \int_0^t \theta(x^i(t')) \, dt'.
	\end{equation}
	
	For two paths with vertical separation \(\Delta z(t) = \frac{1}{2} g t^2\), the difference is:
	
	\begin{equation}
		\Delta \phi = \int_0^T \left[ \theta(z + \Delta z(t')) - \theta(z) \right] dt'.
	\end{equation}
	
	The Taylor expansion of the phase around the reference position z describes how the phase changes with height:
	
	\begin{equation}
		\theta(z + \Delta z) = \theta(z) + (\partial_z \theta) \Delta z + \frac{1}{2} (\partial_z^2 \theta) (\Delta z)^2 + \text{ higher terms}.
	\end{equation}
	
	The first term (linear in \(\Delta z\)) grows quadratically with time, the second (quadratic in \(\Delta z\)) quartically.
	
	% FIXED ALIGN ENVIRONMENT - Simplified approach

	
	\[
	\begin{aligned}
		\Delta \phi &= (\partial_z \theta) \int_0^T \frac{1}{2} g t^2 \, dt' + \frac{1}{2} (\partial_z^2 \theta) \int_0^T \left(\frac{1}{2} g t^2\right)^2 \, dt' + \cdots \\
		&= (\partial_z \theta) \cdot \frac{g T^3}{6} + (\partial_z^2 \theta) \cdot \frac{g^2 T^5}{40} + \text{ higher terms}.
	\end{aligned}
	\]
	
	Taking the fractal normalization into account, the leading \(T^3\) term arises directly from the linear phase gradient -- precisely the observed scaling.
	
	\subsection*{Higher Corrections and Experimental Assessment}
	
	The fractal structure generates a series of higher-order terms:
	
	\begin{equation}
		\Delta \phi = \xi \frac{g T^3}{6} + \xi^{3/2} \frac{g^2 T^5}{40} a_\xi + \xi^2 \frac{g^3 T^7}{336} + \cdots
	\end{equation}
	
	\textbf{Honest assessment of measurability:} The fractal phase gradient is \(\partial_z \theta = \xi \cdot g/c^2 \approx 1.5 \times 10^{-20}\) m\(^{-1}\). For a typical interferometer time \(T = 2\) s, this yields a phase shift of \(\Delta\phi \approx 10^{-19}\) rad -- approximately 13 orders of magnitude below the current detection threshold of \(\sim 10^{-6}\) rad. Even at \(T = 1000\) s (space experiment), \(\Delta\phi \approx 10^{-11}\) rad remains extremely challenging.
	
	The \(T^3\) scaling observed in the experiment can also be explained within standard QM through specific interferometer configurations. The FFGFT offers a \textit{structural} explanation -- the \(T^3\) dependence follows naturally from the fractal phase gradient -- but the coefficient is so small that direct detection of the \(\xi\) contribution is not possible with current technology.
	
	\subsection*{Comparison with Standard Theory}
	
	\begin{center}
		\begin{tabular}{p{0.42\textwidth}p{0.42\textwidth}}
			\textbf{Standard QM + GR} & \textbf{FFGFT (T0)} \\
			\midrule
			Mostly expects \(T^2\) & Fundamental \(T^3\) \\
			\(T^3\) only in special cases & \(T^3\) always through phase \\
			No intrinsic constant & Coefficient through \(\xi\) \\
			No systematic higher terms & Predictable \(\xi^{3/2} T^5\) correction \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The T³ experiment exhibits a scaling that appears in the FFGFT as a natural consequence of the fractal phase gradient. The \(T^3\) dependence follows directly from the time-mass duality. Direct detection of the \(\xi\) coefficient is not possible with current technology (\(\Delta\phi \approx 10^{-19}\) rad at \(T = 2\) s), but represents a testable signal in principle -- particularly for future space-based interferometers with very long free-fall times.



