\chapter{Planck Units and Universal Constants in Fractal T0 Geometry}


	
	\subsection*{Brief Introduction}
	
	This chapter derives the Planck units and all fundamental constants from the fractal geometry of the vacuum field — regulated by \(\xi = \frac{4}{3} \times 10^{-4}\).
	
	\subsection*{Mathematical Foundation}
	
	The Planck units mark the scale where quantum gravity effects become important. In the FFGFT, they emerge from the fractal structure, with no singularities or divergences.
	
	\subsection*{Fundamental T0 Length \(L_0\)}
	
	The minimal sub-Planck length scale is the fundamental T0 length:
	
	\begin{equation}
		\boxed{L_0 = \xi \cdot l_P = \frac{4}{3} \times 10^{-4} \times 1.616 \times 10^{-35} \text{ m} = 2.155 \times 10^{-39} \text{ m}}
	\end{equation}
	
	\(L_0\) is the scale of spacetime granulation -- the absolute floor of physics below which no defined spacetime geometry exists. It is about 7500 times smaller than the Planck length.
	
	\subsection*{Planck Length as Emergent Quantity}
	
	The Planck length is a derived quantity in FFGFT:
	
	\begin{equation}
		\ell_P = \frac{L_0}{\xi} = L_0 \cdot \xi^{-1}.
	\end{equation}
	
	The derivation chain reads: \(\xi \to G \to l_P\), not the other way round. The Planck scale marks the transition from the fractal sub-Planck structure to classical physics.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\ell_P] = \si{m}.
	\end{equation}
	
	\subsection*{Planck Mass}
	
	Planck mass:
	
	\begin{equation}
		m_P = \rho_0 \cdot L_0^3 \cdot \xi^{-3}.
	\end{equation}
	
	The density \(\rho_0\) in volume \(L_0^3\), amplified by \(\xi^{-3}\).
	
	\subsection*{Planck Time}
	
	Planck time:
	
	\begin{equation}
		t_P = \frac{\ell_P}{c} = \frac{L_0}{c \cdot \xi}.
	\end{equation}
	
	Directly from length and speed of light. Analogously, \(T_0 = \xi \cdot t_P\) defines the minimal time scale.
	
	\subsection*{Emergence of \(G\), \(\hbar\), \(c\)}
	
	Gravitational constant:
	
	\begin{equation}
		G = \frac{\hbar c}{m_P^2} \cdot \xi^2.
	\end{equation}
	
	Weakness through \(\xi^2\).
	
	All constants reduce to \(\xi\), \(L_0\), \(\rho_0\), \(c\).
	
	\subsection*{Comparison Standard -- FFGFT}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard} & \textbf{FFGFT (T0)} \\
			\hline
			Planck units arbitrary & Emergent from \(\xi\) \\
			19 free constants & Reduced to \(\xi\) \\
			No hierarchy & Geometrically explained \\
			Ad-hoc & Parameter-free \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The FFGFT derives Planck units and all universal constants from the fractal scale \(\xi\). The fundamental T0 length \(L_0 = \xi \cdot l_P \approx 2.155 \times 10^{-39}\,\)m is the sub-Planck scale of spacetime granulation. The hierarchy problems disappear — everything is a geometric consequence of a single parameter.



