\documentclass[11pt,a4paper,openany]{book}

% Essential packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[a4paper,margin=2.5cm]{geometry}
\usepackage{lmodern}

% Math and physics packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{physics}
\usepackage{siunitx}

% Graphics and tables
\usepackage{graphicx}
\usepackage[table,xcdraw]{xcolor}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{tcolorbox}
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{float}

% Document formatting
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{newunicodechar}

% Additional packages
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{braket}
\usepackage{breakurl}
\usepackage{cancel}
\usepackage{caption}
\usepackage{cite}
\usepackage{csquotes}
\usepackage{doi}
\usepackage{forest}
\usepackage{gensymb}
\usepackage{hyphenat}
\usepackage{listings}
\usepackage{mdframed}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{pdflscape}
\usepackage{ragged2e}
\usepackage{setspace}
\usepackage{slashed}
\usepackage{tabularx}
\usepackage{textcomp}
\usepackage{textgreek}
\usepackage{upgreek}
\usepackage{url}

% Color definitions
\definecolor{blue}{rgb}{0,0,1}
\definecolor{boxgray}{RGB}{240,240,240}
\definecolor{deepblue}{RGB}{0,0,127}
\definecolor{deepgreen}{RGB}{0,127,0}
\definecolor{deepred}{RGB}{191,0,0}
\definecolor{t0blue}{RGB}{0,102,204}
\definecolor{t0green}{RGB}{0,153,0}
\definecolor{t0orange}{RGB}{255,152,0}
\definecolor{t0purple}{RGB}{102,0,204}
\definecolor{t0red}{RGB}{204,0,0}
\definecolor{t0yellow}{RGB}{255,204,0}

% Geometry and settings
\pgfplotsset{compat=1.18}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,calc}

% Theorem environments
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{example}{Example}[section]

% Custom commands
\newcommand{\kB}{k_{\text{B}}}
\newcommand{\degree}{^\circ}

% Headers and footers
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\leftmark}
\fancyhead[R]{T0 Theory}
\fancyfoot[C]{\thepage}

\begin{document}

\maketitle
\tableofcontents

%==============================
% Automatisch generierte Kapitel:

%%------------------------------
\input{chapters_en/T0_Grundlagen_En_ch}

%%------------------------------
\input{chapters_en/T0_Modell_Uebersicht_En_ch}

%%------------------------------
\input{chapters_en/T0_tm-erweiterung-x6_En_ch}

%%------------------------------
\input{chapters_en/T0_Teilchenmassen_En_ch}

%%------------------------------
\input{chapters_en/T0_Neutrinos_En_ch}

%%------------------------------
\input{chapters_en/T0_xi-und-e_En_ch}

%%==============================
% Globales Literaturverzeichnis
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
		
		\bibitem{pdg2024}
		Particle Data Group Collaboration (2024). 
		\textit{Review of Particle Physics}. 
		Progress of Theoretical and Experimental Physics, 2024(8), 083C01.
		\url{https://pdg.lbl.gov}
		
		\bibitem{flag2024}
		Aoki, Y., et al. (FLAG Collaboration) (2024). 
		\textit{FLAG Review 2024 of Lattice Results for Low-Energy Constants}. 
		arXiv:2411.04268.
		\url{https://arxiv.org/abs/2411.04268}
		
		\bibitem{fermilab_muon_g2}
		Abi, B., et al. (Muon g-2 Collaboration) (2021). 
		\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
		Physical Review Letters, 126, 141801.
		
		\bibitem{peskin_schroeder}
		Peskin, M. E., \& Schroeder, D. V. (1995). 
		\textit{An Introduction to Quantum Field Theory}. 
		Addison-Wesley.
		
		\bibitem{weinberg_qft}
		Weinberg, S. (1995). 
		\textit{The Quantum Theory of Fields, Vol. I--III}. 
		Cambridge University Press.
		
		\bibitem{griffiths_particle}
		Griffiths, D. (2008). 
		\textit{Introduction to Elementary Particles}. 
		Wiley-VCH.
		
		\bibitem{mandl_shaw}
		Mandl, F., \& Shaw, G. (2010). 
		\textit{Quantum Field Theory (2nd ed.)}. 
		Wiley.
		
		\bibitem{srednicki_qft}
		Srednicki, M. (2007). 
		\textit{Quantum Field Theory}. 
		Cambridge University Press.
		
		\bibitem{t0_fundamentals}
		Pascher, J. (2024). 
		\textit{T0-Theory: Foundations of Time-Mass Duality}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_fine_structure}
		Pascher, J. (2024). 
		\textit{T0-Theory: The Fine Structure Constant}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_neutrinos}
		Pascher, J. (2024). 
		\textit{T0-Theory: Neutrino Masses and PMNS Mixing}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_github}
		Pascher, J. (2024--2025). 
		\textit{T0-Time-Mass-Duality Repository}. 
		GitHub.
		\url{https://github.com/jpascher/T0-Time-Mass-Duality}
		
		\bibitem{lattice_qcd_review}
		Kronfeld, A. S. (2012). 
		\textit{Twenty-first Century Lattice Gauge Theory: Results from the QCD Lagrangian}. 
		Annual Review of Nuclear and Particle Science, 62, 265--284.
		
		\bibitem{neutrino_mixing_pdg}
		Particle Data Group Collaboration (2024). 
		\textit{Neutrino Masses, Mixing, and Oscillations}. 
		PDG Review 2024.
		\url{https://pdg.lbl.gov/2024/reviews/rpp2024-rev-neutrino-mixing.pdf}
		
		\bibitem{higgs_discovery}
		ATLAS and CMS Collaborations (2012). 
		\textit{Observation of a New Particle in the Search for the Standard Model Higgs Boson}. 
		Physics Letters B, 716, 1--29.
		
		\bibitem{Brannen2005}
		C. P. Brannen, ``Estimate of neutrino masses from Koide's relation'', \textit{arXiv:hep-ph/0505028} (2005).
		\url{https://arxiv.org/abs/hep-ph/0505028}
		
		\bibitem{Brannen2006}
		C. P. Brannen, ``Koide Mass Formula for Neutrinos'', \textit{arXiv:0702.0052} (2006).
		\url{http://brannenworks.com/MASSES.pdf}
		
		\bibitem{PhaseVectors2025}
		Anonymous, ``The Koide Relation and Lepton Mass Hierarchy from Phase Vectors'', \textit{rXiv:2507.0040} (2025).
		\url{https://rxiv.org/pdf/2507.0040v1.pdf}
		
		\bibitem{PDG2025}
		Particle Data Group, ``Review of Particle Physics'', \textit{Phys. Rev. D} \textbf{112} (2025) 030001.
		\url{https://pdg.lbl.gov/2025/}
\end{thebibliography}

\end{document}
