\documentclass[12pt,a4paper]{book}
\input{../../../T0_preamble_shared_En.tex}

\title{Fundamental Fractal-Geometric Field Theory (FFGFT): A Unified Physics from a Single Number\\[0.5em]
	\large Part 1: Core Documents}
\author{}
\date{}

\begin{document}
	
	\begin{center}
		\vspace*{2cm}
		{\Huge\textbf{FFGFT: Time-Mass Duality}}\\[1cm]
		{\Large Part 1: Core Documents}\\[2cm]
	\end{center}
	
	\frontmatter
	\pagestyle{empty}
	
	\mainmatter
	\pagestyle{plain}
	
	\tableofcontents
	\listoftables
	
	% Unified Introduction
	\chapter*{Introduction: In Search of the Deepest Secrets}
	\addcontentsline{toc}{chapter}{Introduction}
	
	Physics faces seven great mysteries – fundamental questions that challenge our understanding of the universe. Why does time have a direction? How does mass arise? What is the nature of quantum reality? This book invites you on a fascinating journey to these secrets and shows how the **Fundamental Fractal-Geometric Field Theory (FFGFT)** – formerly known as the T0 theory of time-mass duality – provides a unified framework to connect these seemingly unrelated puzzles.
	
	The FFGFT starts from a bold assumption: time and mass are two sides of the same coin, dual to each other like wave and particle in quantum mechanics. From this simple but profound insight – mathematically expressed through a single dimensionless constant \(\xi = \frac{4}{3} \times 10^{-4}\) – emerge answers to questions that have occupied physicists for decades.
	
	Imagine you're trying to understand a complex machine. Traditional physics examines each component separately. FFGFT, however, reveals that many of these apparently separate parts are actually different manifestations of the same underlying mechanism.
	
	This insight has concrete, experimentally testable consequences and is distinguished by its elegance: instead of adding new particles or dimensions, FFGFT derives diverse phenomena from a single principle.
	
	You don't need to be a professional physicist to follow this journey. We explain technical concepts in everyday language and use mathematics only where it truly illuminates the ideas.
	
	Each chapter stands on its own – read them in order or jump to topics that interest you. Some sections are more technical; feel free to skim them and focus on the conceptual explanations.
	
	\textbf{The seven mysteries we explore}
	
	1. **The Nature of Time** – "Three Clocks" thought experiment and resolution of classical paradoxes.  
	2. **The Origin of Mass** – Alternative to the Higgs mechanism from time relationships.  
	3. **Quantum Reality and Geometry** – Connection between quantum world and spacetime curvature.  
	4. **Cosmic Structures** – Origin of galaxies and voids.  
	5. **Statistical Physics of Time** – Time as a statistical phenomenon.  
	6. **Chance and Determination** – New paths between chaos and predetermination.  
	7. **The Cosmic Mystery of the CMB Dipole** – Hints at the fundamental nature of space.
	
	\textbf{Bonus: The Fractal Nature of Time} – Time as a fractal pattern.
	
	These chapters are a look behind the curtain of reality. FFGFT shows that the deepest secrets of physics are interwoven and emerge from a single principle.
	
	Welcome to the exploration of the seven mysteries of physics – and the theory that connects them.
	



% Part 1: Core T0 Documents (matching Teil1 structure)

% 1. Introduction and Summary (instead of Introduction and Journey)
\input{../en_chapters_new/001a_T0_Book_Abstract_En_ch}

% 3. Fundamentals
\input{../en_chapters_new/003_T0_Grundlagen_v1_En_ch}

% 4. Model Overview
\input{../en_chapters_new/004_T0_Modell_Uebersicht_En_ch}

% 5. Time-Mass Extension (Final Fractal Mass Formulas)
\input{../en_chapters_new/005_T0_tm-erweiterung-x6_En_ch}

% 6. Particle Masses
\input{../en_chapters_new/006_T0_Teilchenmassen_En_ch}

% 7. Neutrinos
\input{../en_chapters_new/007_T0_Neutrinos_En_ch}

% 8. Xi and e
\input{../en_chapters_new/008_T0_xi-und-e_En_ch}

% 9. Xi Origin (Mass Scaling Exponent)
\input{../en_chapters_new/009_T0_xi_ursprung_En_ch}

% 10. Energy
\input{../en_chapters_new/010_T0_Energie_En_ch}

% 11. Fine Structure Constant
\input{../en_chapters_new/011_T0_Feinstruktur_En_ch}

% 12. Gravitational Constant
\input{../en_chapters_new/012_T0_Gravitationskonstante_En_ch}

% 13. SI Units
\input{../en_chapters_new/013_T0_SI_En_ch}

% 14. Natural to SI
\input{../en_chapters_new/014_T0_nat-si_En_ch}

% 15. Natural Units Systematics
\input{../en_chapters_new/015_NatEinheitenSystematik_En_ch}

% 16. Complete Calculations
\input{../en_chapters_new/016_T0_Vollstaendige_Berchnungen_En_ch}

% 17. Anomalous Magnetic Moments
\input{../en_chapters_new/017_T0_Anomale_Magnetische_Momente_En_ch}

% 17. Lagrangian
\input{../en_chapters_new/019_T0_lagrndian_En_ch}

% 18. g-2 Anomaly
\input{../en_chapters_new/018_T0_Anomale-g2-9_En_ch}

% 19. QM-QFT-RT
\input{../en_chapters_new/020_T0_QM-QFT-RT_En_ch}

% 20. QAT
\input{../en_chapters_new/021_T0_QAT_En_ch}

% 21. QFT-ML Addendum
\input{../en_chapters_new/022_T0-QFT-ML_Addendum_En_ch}

% 22. Bell Tests
\input{../en_chapters_new/023_Bell_En_ch}

% 23. Networks
\input{../en_chapters_new/024_T0_netze_En_ch}

% 24. Cosmology
\input{../en_chapters_new/025_T0_Kosmologie_En_ch}

% 25. Geometric Cosmology
\input{../en_chapters_new/026_T0_Geometrische_Kosmologie_En_ch}

% 26. MNRAS Analysis
\input{../en_chapters_new/027_T0_Analyse_MNRAS_Widerlegung_En_ch}

% 27. Seven Questions
\input{../en_chapters_new/028_T0_7-fragen-3_En_ch}

% 28. Three Clocks
\input{../en_chapters_new/029_T0_threeclock_En_ch}

% 29. Penrose
\input{../en_chapters_new/030_T0_penrose_En_ch}

% 30. g-2 Extension
\input{../en_chapters_new/031_T0_g2-erweiterung-4_En_ch}

% 31. Inversion
\input{../en_chapters_new/032_T0_umkehrung_En_ch}

% 32. T0 vs Synergetics
\input{../en_chapters_new/033_T0-Theory-vs-Synergetics_En_ch}

% 33. QM Optimization
\input{../en_chapters_new/034_T0_QM-optimierung_En_ch}

% 34. Quantum Mechanics
\input{../en_chapters_new/035_QM_En_ch}

% 35. Peratt
\input{../en_chapters_new/036_T0_peratt_En_ch}

% 36. Hannah (Mizohata-Takeuchi)
\input{../en_chapters_new/037_Hannah_En_ch}

% 37. Markov Chains
\input{../en_chapters_new/038_Markov_En_ch}

% 38. CMB Dipoles
\input{../en_chapters_new/039_Zwei-Dipole-CMB_En_ch}

% 39. Summary
\input{../en_chapters_new/081_Zusammenfassung_En_ch}

\end{document}
