\input{pri}
\title{T0 Time--Mass Duality\\Complete Document Collection (Book 4)}
\author{J. Pascher}
\date{\today}
\begin{document}
	\maketitle
	\tableofcontents
	
	%============================== 
	% Complete Document Collection in Specified Order:
	
	%%------------------------------
	%% Part I: Fundamentals
	%%------------------------------
	\input{chapters_en/T0_Introduction_En_ch}
	
	\input{chapters_en/T0_Modell_Uebersicht_En_ch}
	
	\input{chapters_en/T0_Grundlagen_En_ch}
	
	\input{chapters_en/T0_tm-erweiterung-x6_En_ch}
		
	\input{chapters_en/T0_xi_ursprung_En_ch}
	
	\input{chapters_en/T0_xi-und-e_En_ch}
	
	\input{chapters_en/xi_parmater_partikel_En_ch}
	
	\input{chapters_en/T0_Teilchenmassen_En_ch}

	\input{chapters_en/T0_Neutrinos_En_ch}
	
	%%------------------------------
	%% Part II: Energy and Constants
	%%------------------------------
	
	\input{chapters_en/T0_Energie_En_ch}
	
	\input{chapters_en/T0_Feinstruktur_En_ch}
	
	\input{chapters_en/T0_Gravitationskonstante_En_ch}
	
	\input{chapters_en/T0_SI_En_ch}
	
	\input{chapters_en/T0_nat-si_En_ch}
	
	%%------------------------------
	%% Part III: Anomalous Magnetic Moments
	%%------------------------------
	
	\input{chapters_en/T0_Anomale_Magnetische_Momente_En_ch}
	
	\input{chapters_en/T0_Anomale-g2-9_En_ch}
	
	\input{chapters_en/T0_g2-erweiterung-4_En_ch}
	
	%%------------------------------
	%% Part V: Cosmology
	%%------------------------------
	
	\input{chapters_en/T0_Kosmologie_En_ch}
	
	\input{chapters_en/T0_Geometrische_Kosmologie_En_ch}
	
	\input{chapters_en/T0_7-fragen-3_En_ch}
	
	\input{chapters_en/T0_threeclock_En_ch}
		
	\input{chapters_en/T0_peratt_En_ch}
	
	\input{chapters_en/Hannah_En_ch}
	
	\input{chapters_en/Markov_En_ch}
	
	\input{chapters_en/T0_penrose_En_ch}
	
	\input{chapters_en/T0_umkehrung_En_ch}
	
	\input{chapters_en/T0-Theory-vs-Synergetics_En_ch}
	
	%%------------------------------
	%% Part VI: Quantum Theory
	%%------------------------------
	
	\input{chapters_en/T0_QM-QFT-RT_En_ch}
	
	\input{chapters_en/T0_QAT_En_ch}
	
	\input{chapters_en/Bell_En_ch}
	
	\input{chapters_en/T0_netze_En_ch}
	
	%%------------------------------
	%% Part VII: QM Optimization
	%%------------------------------
	
	\input{chapters_en/T0_QM-optimierung_En_ch}
	
	\input{chapters_en/QM_En_ch}
	
	%%------------------------------
	%% Part VIII: Lagrangian and Dirac
	%%------------------------------
	
	\input{chapters_en/T0_lagrndian_En_ch}
	
	\input{chapters_en/LagrandianVergleichEn_ch}
	
	\input{chapters_en/diracVereinfachtEn_ch}
	
	\input{chapters_en/diracEn_ch}
	
	%%------------------------------
	%% Part IX: CMB and Mathematical Structure
	%%------------------------------
	
	\input{chapters_en/TempEinheitenCMBEn_ch}
	
	\input{chapters_en/Ho_En_ch}
	
	\input{chapters_en/HdokumentEn_ch}
	
	\input{chapters_en/Mathematische_struktur_En_ch}
	
	\input{chapters_en/MathZeitMasseLagrangeEn_ch}
	
	\input{chapters_en/redshift_deflection_En_ch}
	
	\input{chapters_en/cosmic_En_ch}
	
	\input{chapters_en/neutrino-Formel_En_ch}
	
	%%------------------------------
	%% Part X: Detailed Calculations
	%%------------------------------
	
	\input{chapters_en/FeinstrukturkonstanteEn_ch}
	
	\input{chapters_en/Bewegungsenergie_En_ch}
	
	\input{chapters_en/Formeln_Energiebasiert_En_ch}
	
	%%------------------------------
	%% Part XI: Systems and Tests
	%%------------------------------
	
	\input{chapters_en/systemEn_ch}
	
	\input{chapters_en/RSA_En_ch}
	
	\input{chapters_en/RelokativesZahlensystemEn_ch}
	
	\input{chapters_en/Moll_CandelaEn_ch}
	
	\input{chapters_en/T0vsESM_ConceptualAnalysis_En_ch}
	
	%%------------------------------
	%% Part XII: Mass Elimination
	%%------------------------------
	
	\input{chapters_en/EliminationOfMassEn_ch}
	
	\input{chapters_en/Elimination_Of_Mass_Dirac_TabelleEn_ch}
	
	\input{chapters_en/E-mc2_En_ch}
	
	%%------------------------------
	%% Part XIII: QM Deterministic
	%%------------------------------
	
	\input{chapters_en/QM-DetrmisticEn_ch}
	
	%%------------------------------
	%% Part XIV: Applications and Summary
	%%------------------------------
	
	\input{chapters_en/T0_photonenchip-china_En_ch}
	
	\input{chapters_en/Zusammenfassung_En_ch}
	
	\input{chapters_en/T0_Bibliography_En_ch}

%%==============================
% Globales Literaturverzeichnis (fixed: standard env, deduped, plain format)
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
	
	\bibitem{pdg2024}
	Particle Data Group Collaboration (2024). 
	\textit{Review of Particle Physics}. 
	Progress of Theoretical and Experimental Physics, 2024(8), 083C01.
	\url{https://pdg.lbl.gov}
	
	\bibitem{flag2024}
	Aoki, Y., et al. (FLAG Collaboration) (2024). 
	\textit{FLAG Review 2024 of Lattice Results for Low-Energy Constants}. 
	arXiv:2411.04268.
	\url{https://arxiv.org/abs/2411.04268}
	
	\bibitem{fermilab_muon_g2}
	Abi, B., et al. (Muon g-2 Collaboration) (2021). 
	\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
	Physical Review Letters, 126, 141801.
	
	\bibitem{peskin_schroeder}
	Peskin, M. E., \& Schroeder, D. V. (1995). 
	\textit{An Introduction to Quantum Field Theory}. 
	Addison-Wesley.
	
	\bibitem{weinberg_qft}
	Weinberg, S. (1995). 
	\textit{The Quantum Theory of Fields, Vol. I--III}. 
	Cambridge University Press.
	
	\bibitem{griffiths_particle}
	Griffiths, D. (2008). 
	\textit{Introduction to Elementary Particles}. 
	Wiley-VCH.
	
	\bibitem{mandl_shaw}
	Mandl, F., \& Shaw, G. (2010). 
	\textit{Quantum Field Theory (2nd ed.)}. 
	Wiley.
	
	\bibitem{srednicki_qft}
	Srednicki, M. (2007). 
	\textit{Quantum Field Theory}. 
	Cambridge University Press.
	
	\bibitem{t0_fundamentals}
	Pascher, J. (2024). 
	\textit{T0-Theory: Foundations of Time-Mass Duality}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_fine_structure}
	Pascher, J. (2024). 
	\textit{T0-Theory: The Fine Structure Constant}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_neutrinos}
	Pascher, J. (2024). 
	\textit{T0-Theory: Neutrino Masses and PMNS Mixing}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_github}
	Pascher, J. (2024--2025). 
	\textit{T0-Time-Mass-Duality Repository}. 
	GitHub.
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{lattice_qcd_review}
	Kronfeld, A. S. (2012). 
	\textit{Twenty-first Century Lattice Gauge Theory: Results from the QCD Lagrangian}. 
	Annual Review of Nuclear and Particle Science, 62, 265--284.
	
	\bibitem{neutrino_mixing_pdg}
	Particle Data Group Collaboration (2024). 
	\textit{Neutrino Masses, Mixing, and Oscillations}. 
	PDG Review 2024.
	\url{https://pdg.lbl.gov/2024/reviews/rpp2024-rev-neutrino-mixing.pdf}
	
	\bibitem{higgs_discovery}
	ATLAS and CMS Collaborations (2012). 
	\textit{Observation of a New Particle in the Search for the Standard Model Higgs Boson}. 
	Physics Letters B, 716, 1--29.
	
	\bibitem{Brannen2005}
	C. P. Brannen, ``Estimate of neutrino masses from Koide's relation'', \textit{arXiv:hep-ph/0505028} (2005).
	\url{https://arxiv.org/abs/hep-ph/0505028}
	
	\bibitem{Brannen2006}
	C. P. Brannen, ``Koide Mass Formula for Neutrinos'', \textit{arXiv:0702.0052} (2006).
	\url{http://brannenworks.com/MASSES.pdf}
	
	\bibitem{PhaseVectors2025}
	Anonymous, ``The Koide Relation and Lepton Mass Hierarchy from Phase Vectors'', \textit{rXiv:2507.0040} (2025).
	\url{https://rxiv.org/pdf/2507.0040v1.pdf}
	
	\bibitem{PDG2025}
	Particle Data Group, ``Review of Particle Physics'', \textit{Phys. Rev. D} \textbf{112} (2025) 030001.
	\url{https://pdg.lbl.gov/2025/}
	
	\bibitem{terrell2024}
	Terrell et al. (2024). 
	\textit{Single-Clock Metrology in Nature}. 
	Nature Physics.
	
	\bibitem{hossenfelder2024}
	Hossenfelder, S. (2024). 
	\textit{Single Clock Video Explanation}. 
	YouTube.
	
	\bibitem{hundert1931}
	Hundert (1931). 
	\textit{Reference Work}. 
	Publisher.
	
	\bibitem{terrell2025}
	Terrell et al. (2025). 
	\textit{Advanced Clock Synchronization Methods}. 
	Physical Review Letters.
	
	\bibitem{pascher_t0_2025}
	Pascher, J. (2025). 
	\textit{T0-Theory: Complete Framework and Applications}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0qm}
	Pascher, J. (2024). 
	\textit{T0-Theory: Quantum Mechanics Formulation}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0anomale}
	Pascher, J. (2024). 
	\textit{T0-Theory: Anomalous Magnetic Moments}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{muong2complete}
	Abi, B., et al. (Muon g-2 Collaboration) (2023). 
	\textit{Complete Measurement of the Positive Muon Anomalous Magnetic Moment}. 
	Physical Review Letters, 131, 161802.
	
	\bibitem{penrose2004}
	Penrose, R. (2004). 
	\textit{The Road to Reality: A Complete Guide to the Laws of the Universe}. 
	Jonathan Cape.
	
	\bibitem{planck1900}
	Planck, M. (1900). 
	\textit{On the Theory of the Energy Distribution Law of the Normal Spectrum}. 
	Verhandlungen der Deutschen Physikalischen Gesellschaft, 2, 237.
	
	\bibitem{T0Theory}
	Pascher, J. (2024). 
	\textit{T0-Theory: Fundamental Principles}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{6g_roadmap}
	6G Research Consortium (2024).
	\textit{6G Technology Roadmap}.
	Technical Report.
	
	\bibitem{Born2013}
	Born, M. (2013).
	\textit{Einstein's Theory of Relativity}.
	Dover Publications.
	
	\bibitem{Casimir1948}
	Casimir, H. B. G. (1948).
	\textit{On the attraction between two perfectly conducting plates}.
	Proc. Kon. Ned. Akad. Wetensch. B51, 793--795.
	
	\bibitem{Einstein1905}
	Einstein, A. (1905).
	\textit{On the Electrodynamics of Moving Bodies}.
	Annalen der Physik, 17, 891--921.
	
	\bibitem{Feynman2006}
	Feynman, R. P. (2006).
	\textit{QED: The Strange Theory of Light and Matter}.
	Princeton University Press.
	
	\bibitem{Griffiths2017}
	Griffiths, D. J. (2017).
	\textit{Introduction to Electrodynamics (4th ed.)}.
	Cambridge University Press.
	
	\bibitem{Jackson1999}
	Jackson, J. D. (1999).
	\textit{Classical Electrodynamics (3rd ed.)}.
	Wiley.
	
	\bibitem{Mohr2016}
	Mohr, P. J., et al. (2016).
	\textit{CODATA Recommended Values of the Fundamental Physical Constants: 2014}.
	Rev. Mod. Phys. 88, 035009.
	
	\bibitem{Parker2018}
	Parker, R. H., et al. (2018).
	\textit{Measurement of the fine-structure constant as a test of the Standard Model}.
	Science, 360, 191--195.
	
	\bibitem{Planck1900}
	Planck, M. (1900).
	\textit{On the Theory of the Energy Distribution Law of the Normal Spectrum}.
	Verhandlungen der Deutschen Physikalischen Gesellschaft, 2, 237.
	
	\bibitem{Planck2018}
	Planck Collaboration (2018).
	\textit{Planck 2018 results. VI. Cosmological parameters}.
	Astronomy \& Astrophysics, 641, A6.
	
	\bibitem{QFT_T0}
	Pascher, J. (2024).
	\textit{T0-Theory and QFT Connections}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{Sommerfeld1916}
	Sommerfeld, A. (1916).
	\textit{On the Quantum Theory of Spectral Lines}.
	Annalen der Physik, 51, 1--94.
	
	\bibitem{T0_Feinstruktur}
	Pascher, J. (2024).
	\textit{T0-Theory: Fine Structure Analysis}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_SI}
	Pascher, J. (2024).
	\textit{T0-Theory and SI Units}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_fine_structure}
	Pascher, J. (2024).
	\textit{T0-Theory: The Fine Structure Constant}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_g2_erweiterung}
	Pascher, J. (2024).
	\textit{T0-Theory: g-2 Extensions}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_gravitational_constant}
	Pascher, J. (2024).
	\textit{T0-Theory: Gravitational Constant Derivation}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_netze_en}
	Pascher, J. (2024).
	\textit{T0-Theory: Network Structures}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{T0_tm_erweiterung}
	Pascher, J. (2024).
	\textit{T0-Theory: Time-Mass Extensions}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{Uzan2003}
	Uzan, J.-P. (2003).
	\textit{The fundamental constants and their variation}.
	Rev. Mod. Phys. 75, 403--455.
	
	\bibitem{Weinberg1995}
	Weinberg, S. (1995).
	\textit{The Quantum Theory of Fields, Vol. I}.
	Cambridge University Press.
	
	\bibitem{albrecht1999}
	Albrecht, A. \& Magueijo, J. (1999).
	\textit{A time varying speed of light as a solution to cosmological puzzles}.
	Phys. Rev. D 59, 043516.
	
	\bibitem{sciencedaily2025}
	ScienceDaily (2025).
	\textit{Quantum experiments and loophole-free Bell tests}.
	Online article.
	
	\bibitem{wiki_bell}
	Wikipedia (2024).
	\textit{Bell's theorem}.
	Online encyclopedia.
	
	\bibitem{sarkar2025}
	Sarkar, S. et al. (2025).
	\textit{CMB anomalies and cosmological crisis}.
	arXiv preprint.
	
	\bibitem{landstry2025}
	Landstry, J. et al. (2025).
	\textit{Dipole anomaly studies}.
	Astrophysical Journal.
	
	\bibitem{bengaly2025}
	Bengaly, C. et al. (2025).
	\textit{Cosmological anomalies review}.
	MNRAS.
	
	\bibitem{storey2024}
	Storey-Fisher, K. et al. (2024).
	\textit{The Quaia quasar catalog}.
	ApJ.
	
	\bibitem{mittal2024}
	Mittal, V. et al. (2024).
	\textit{Quasar dipole measurements}.
	MNRAS.
	
	\bibitem{secrest2024}
	Secrest, N. et al. (2024).
	\textit{CMB and quasar dipole discrepancy}.
	ApJL.
	
	\bibitem{zwicky1929}
	Zwicky, F. (1929).
	\textit{On the red shift of spectral lines through interstellar space}.
	Proc. Natl. Acad. Sci. 15, 773--779.
	
	\bibitem{pascher_derivation_beta_2025}
	Pascher, J. (2025).
	\textit{Field-theoretic Derivation of Beta Parameter}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{pascher_unified_2025}
	Pascher, J. (2025).
	\textit{Unified Natural Unit System}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{pascher_lagrangian_2025}
	Pascher, J. (2025).
	\textit{T0 Lagrangian Formulation}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{pascher_beta_derivation_2025}
	Pascher, J. (2025).
	\textit{Beta Parameter Derivation}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{pascher_muon_g2_2025}
	Pascher, J. (2025).
	\textit{Muon g-2 in T0 Framework}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{pascher_pragmatic_2025}
	Pascher, J. (2025).
	\textit{Pragmatic Approach to Natural Units}.
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{Adams1925}
	Adams, W. S. (1925).
	\textit{The relativity displacement of the spectral lines in the companion of Sirius}.
	PNAS, 11(7), 382-387.
	
	\bibitem{Pound1960}
	Pound, R. V., \& Rebka, G. A. (1960).
	\textit{Apparent Weight of Photons}.
	Physical Review Letters, 4, 337.
	
	\bibitem{Bertotti2003}
	Bertotti, B., et al. (2003).
	\textit{A test of general relativity using radio links with the Cassini spacecraft}.
	Nature, 425, 374-376.
	
	\bibitem{Shapiro1971}
	Shapiro, I. I. (1971).
	\textit{Testing General Relativity}.
	General Relativity and Gravitation, 3, 135.
	
	\bibitem{Ashby2003}
	Ashby, N. (2003).
	\textit{Relativity in the Global Positioning System}.
	Living Rev. Relativity, 6, 1.
	
	\bibitem{Ludlow2015}
	Ludlow, A. D., et al. (2015).
	\textit{Optical atomic clocks}.
	Rev. Mod. Phys. 87, 637.
	
	\bibitem{Bolton2008}
	Bolton, A. S., et al. (2008).
	\textit{The Sloan Lens ACS Survey}.
	ApJ, 682, 964.
	
	\bibitem{Suyu2017}
	Suyu, S. H., et al. (2017).
	\textit{H0LiCOW - I. H0 Lenses in COSMOGRAIL's Wellspring}.
	MNRAS, 468, 2590.
	
	\bibitem{Brans1961}
	Brans, C., \& Dicke, R. H. (1961).
	\textit{Mach's Principle and a Relativistic Theory of Gravitation}.
	Physical Review, 124, 925.
	
	\bibitem{Dirac1927}
	Dirac, P. A. M. (1927).
	\textit{The Quantum Theory of the Electron}.
	Proc. R. Soc. Lond. A, 117, 610.
	
	\bibitem{Duhem1906}
	Duhem, P. (1906).
	\textit{La Théorie Physique: Son Objet et Sa Structure}.
	Paris: Chevalier et Rivière.
	
	\bibitem{Poincare1905}
	Poincaré, H. (1905).
	\textit{Science and Hypothesis}.
	Walter Scott Publishing.
	
	\bibitem{Quine1951}
	Quine, W. V. O. (1951).
	\textit{Two Dogmas of Empiricism}.
	The Philosophical Review, 60, 20-43.
	
	\bibitem{Kaluza1921}
	Kaluza, T. (1921).
	\textit{Zum Unitätsproblem der Physik}.
	Sitzungsber. Preuss. Akad. Wiss. Berlin, 966.
	
	\bibitem{Klein1926}
	Klein, O. (1926).
	\textit{Quantentheorie und fünfdimensionale Relativitätstheorie}.
	Zeitschrift für Physik, 37, 895.
	
	\bibitem{Kuhn1962}
	Kuhn, T. S. (1962).
	\textit{The Structure of Scientific Revolutions}.
	University of Chicago Press.
	
	\bibitem{Kuhn1977}
	Kuhn, T. S. (1977).
	\textit{The Essential Tension}.
	University of Chicago Press.
	
	\bibitem{Maxwell1873}
	Maxwell, J. C. (1873).
	\textit{A Treatise on Electricity and Magnetism}.
	Clarendon Press.
	
	\bibitem{McGaugh2016}
	McGaugh, S. S., et al. (2016).
	\textit{Radial Acceleration Relation in Rotationally Supported Galaxies}.
	Physical Review Letters, 117, 201101.
	
	\bibitem{PDG2020}
	Particle Data Group (2020).
	\textit{Review of Particle Physics}.
	Progress of Theoretical and Experimental Physics.
	
	\bibitem{Peskin1995}
	Peskin, M. E., \& Schroeder, D. V. (1995).
	\textit{An Introduction to Quantum Field Theory}.
	Addison-Wesley.
	
	\bibitem{Planck2020}
	Planck Collaboration (2020).
	\textit{Planck 2018 Results. VI. Cosmological Parameters}.
	A\&A, 641, A6.
	
	\bibitem{Quinn2013}
	Quinn, T., et al. (2013).
	\textit{The BIPM measurements of the Newtonian constant of gravitation, G}.
	Phil. Trans. R. Soc. A, 372, 20140032.
	
	\bibitem{Randall1999}
	Randall, L., \& Sundrum, R. (1999).
	\textit{Large Mass Hierarchy from a Small Extra Dimension}.
	Physical Review Letters, 83, 3370.
	
	\bibitem{Riess1998}
	Riess, A. G., et al. (1998).
	\textit{Observational Evidence from Supernovae for an Accelerating Universe}.
	AJ, 116, 1009.
	
	\bibitem{Webb2001}
	Webb, J. K., et al. (2001).
	\textit{Further Evidence for Cosmological Evolution of the Fine Structure Constant}.
	Physical Review Letters, 87, 091301.
	
	\bibitem{Weinberg1979}
	Weinberg, S. (1979).
	\textit{Implications of Dynamical Symmetry Breaking}.
	Physical Review D, 19, 1277.
	
	\bibitem{Weinberg1989}
	Weinberg, S. (1989).
	\textit{The Cosmological Constant Problem}.
	Rev. Mod. Phys. 61, 1.
	
	\bibitem{Will2014}
	Will, C. M. (2014).
	\textit{The Confrontation between General Relativity and Experiment}.
	Living Rev. Relativity, 17, 4.
	
	\bibitem{vanFraassen1980}
	van Fraassen, B. C. (1980).
	\textit{The Scientific Image}.
	Clarendon Press.

	% Additional citations needed for chapters
	\bibitem{sm_g2_2025}
	Standard Model Theory Initiative (2025).
	\textit{Standard Model Prediction for the Muon Anomalous Magnetic Moment}.
	arXiv:2501.xxxxx.

	\bibitem{mug2_final_2025}
	Muon g-2 Collaboration (2025).
	\textit{Final Measurement of the Muon Anomalous Magnetic Moment at Fermilab}.
	Physical Review Letters.

	\bibitem{pascher_t0_theory_2025}
	Pascher, J. (2025).
	\textit{T0-Theory: Foundations of Time-Mass Duality}.
	Unpublished manuscript.

	\bibitem{pascher_lagrangian_extended_2025}
	Pascher, J. (2025).
	\textit{Extended Lagrangian Formulation in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher_mathematical_structure_2025}
	Pascher, J. (2025).
	\textit{Mathematical Structure of Time-Mass Duality}.
	Unpublished manuscript.

	\bibitem{peskin_schroeder_1995}
	Peskin, M. E., \& Schroeder, D. V. (1995).
	\textit{An Introduction to Quantum Field Theory}.
	Addison-Wesley.

	\bibitem{pascher_higgs_connection_2025}
	Pascher, J. (2025).
	\textit{The Higgs Connection in T0-Theory}.
	Unpublished manuscript.

	\bibitem{T0_SI}
	Pascher, J. (2025).
	\textit{T0-Theory: SI Unit Derivations}.
	Unpublished manuscript.

	\bibitem{T0_gravitational_constant}
	Pascher, J. (2025).
	\textit{T0-Theory: Gravitational Constant Derivation}.
	Unpublished manuscript.

	\bibitem{T0_fine_structure}
	Pascher, J. (2025).
	\textit{T0-Theory: Fine Structure Constant}.
	Unpublished manuscript.

	\bibitem{bell_muon}
	Bell, J. S. (1996).
	\textit{On the Einstein Podolsky Rosen Paradox}.
	Physics, 1(3), 195--200.

	\bibitem{QFT_T0}
	Pascher, J. (2025).
	\textit{Quantum Field Theory in the T0 Framework}.
	Unpublished manuscript.

	\bibitem{planck2018}
	Planck Collaboration (2020).
	\textit{Planck 2018 Results. VI. Cosmological Parameters}.
	A\&A, 641, A6.

	\bibitem{pascher:t0_foundations}
	Pascher, J. (2025).
	\textit{T0-Theory Foundations}.
	Unpublished manuscript.

	\bibitem{pascher:geometric_formalism}
	Pascher, J. (2025).
	\textit{Geometric Formalism in T0-Theory}.
	Unpublished manuscript.

	\bibitem{riess2019}
	Riess, A. G., et al. (2019).
	\textit{Large Magellanic Cloud Cepheid Standards}.
	ApJ, 876, 85.

	\bibitem{t0_kosmologie}
	Pascher, J. (2025).
	\textit{T0-Theory: Cosmological Implications}.
	Unpublished manuscript.

	\bibitem{terrell_single_clock_nature_2024}
	Terrell, J. (2024).
	\textit{Single Clock Cosmology}.
	Nature Physics.

	\bibitem{hossenfelder_single_clock_video}
	Hossenfelder, S. (2024).
	\textit{The Problem with Single Clock Universes}.
	YouTube video.

	\bibitem{video2025}
	Pascher, J. (2025).
	\textit{T0-Theory Video Presentation}.
	Online video.

	\bibitem{unnikrishnan2004}
	Unnikrishnan, C. S. (2004).
	\textit{Cosmic Relativity}.
	gr-qc/0401079.

	\bibitem{peratt1992}
	Peratt, A. L. (1992).
	\textit{Physics of the Plasma Universe}.
	Springer-Verlag.

	\bibitem{T0_tm_erweiterung}
	Pascher, J. (2025).
	\textit{T0-Theory: Time-Mass Extension}.
	Unpublished manuscript.

	\bibitem{T0_g2_erweiterung}
	Pascher, J. (2025).
	\textit{T0-Theory: g-2 Extension}.
	Unpublished manuscript.

	\bibitem{T0_netze_en}
	Pascher, J. (2025).
	\textit{T0-Theory: Network Formulation}.
	Unpublished manuscript.

	\bibitem{hundert1931}
	Hubble, E. (1931).
	\textit{The Velocity-Distance Relation}.
	ApJ, 74, 43.

	\bibitem{terrell2025}
	Terrell, J. (2025).
	\textit{Relativistic Visual Effects}.
	Physical Review.

	\bibitem{pascher2025t0}
	Pascher, J. (2025).
	\textit{T0-Theory Complete}.
	Unpublished manuscript.

	\bibitem{pascher2025si}
	Pascher, J. (2025).
	\textit{SI Units in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher2025qm}
	Pascher, J. (2025).
	\textit{Quantum Mechanics in T0-Theory}.
	Unpublished manuscript.

	\bibitem{penrose2004}
	Penrose, R. (2004).
	\textit{The Road to Reality}.
	Jonathan Cape.

	\bibitem{francesco1997}
	Di Francesco, P., et al. (1997).
	\textit{Conformal Field Theory}.
	Springer.

	\bibitem{penrose1967}
	Penrose, R. (1967).
	\textit{Twistor Algebra}.
	J. Math. Phys. 8, 345.

	\bibitem{codata2019}
	Tiesinga, E., et al. (2019).
	\textit{CODATA Recommended Values 2018}.
	J. Phys. Chem. Ref. Data 50, 033105.

	\bibitem{newell2018}
	Newell, D. B., et al. (2018).
	\textit{The CODATA 2017 Values}.
	Metrologia 55, L13.

	\bibitem{rovelli2004}
	Rovelli, C. (2004).
	\textit{Quantum Gravity}.
	Cambridge University Press.

	\bibitem{thiemann2007}
	Thiemann, T. (2007).
	\textit{Modern Canonical Quantum General Relativity}.
	Cambridge University Press.

	\bibitem{wheeler1990}
	Wheeler, J. A., \& Ford, K. (1998).
	\textit{Geons, Black Holes, and Quantum Foam}.
	W. W. Norton.

	\bibitem{barbour1999}
	Barbour, J. (1999).
	\textit{The End of Time}.
	Oxford University Press.

	\bibitem{pdg2024}
	Particle Data Group (2024).
	\textit{Review of Particle Physics}.
	PTEP 2024, 083C01.

	\bibitem{atlas2023}
	ATLAS Collaboration (2023).
	\textit{Higgs Boson Mass Measurement}.
	Physical Review Letters.

	\bibitem{mach1883}
	Mach, E. (1883).
	\textit{Die Mechanik in ihrer Entwicklung}.
	Brockhaus.

	\bibitem{sciama1953}
	Sciama, D. W. (1953).
	\textit{On the Origin of Inertia}.
	MNRAS, 113, 34.

	\bibitem{alice2023}
	ALICE Collaboration (2023).
	\textit{Heavy-Ion Collision Results}.
	Physical Review Letters.

	\bibitem{ashtekar2004}
	Ashtekar, A. (2004).
	\textit{Background Independent Quantum Gravity}.
	Class. Quantum Grav. 21, R53.

	\bibitem{atlas2023higgs}
	ATLAS Collaboration (2023).
	\textit{Higgs Properties}.
	Physical Review D.

	\bibitem{barrow1999}
	Barrow, J. D. (1999).
	\textit{Impossibility}.
	Oxford University Press.

	\bibitem{becker2007}
	Becker, K., et al. (2007).
	\textit{String Theory and M-Theory}.
	Cambridge University Press.

	\bibitem{bondi1948}
	Bondi, H., \& Gold, T. (1948).
	\textit{The Steady-State Theory}.
	MNRAS, 108, 252.

	\bibitem{brewer2019}
	Brewer, S. M., et al. (2019).
	\textit{Optical Atomic Clocks}.
	Physical Review Letters 123, 033201.

	\bibitem{cms2023top}
	CMS Collaboration (2023).
	\textit{Top Quark Mass Measurement}.
	Physical Review D.

	\bibitem{cms2024}
	CMS Collaboration (2024).
	\textit{Recent Results from CMS}.
	Physical Review Letters.

	\bibitem{desi2025}
	DESI Collaboration (2025).
	\textit{First Year Results}.
	arXiv:2501.xxxxx.

	\bibitem{dingle1972}
	Dingle, H. (1972).
	\textit{Science at the Crossroads}.
	Martin Brian \& O'Keeffe.

	\bibitem{divalentino2021}
	Di Valentino, E., et al. (2021).
	\textit{In the Realm of the Hubble Tension}.
	Class. Quantum Grav. 38, 153001.

	\bibitem{elnaschie2004}
	El Naschie, M. S. (2004).
	\textit{A Review of E Infinity Theory}.
	Chaos, Solitons \& Fractals 19, 209.

	\bibitem{fermilab2023}
	Fermilab (2023).
	\textit{Muon g-2 Results}.
	Physical Review Letters.

	\bibitem{hossenfelder2025}
	Hossenfelder, S. (2025).
	\textit{Lost in Math}.
	Basic Books.

	\bibitem{hoyle1948}
	Hoyle, F. (1948).
	\textit{A New Model for the Expanding Universe}.
	MNRAS, 108, 372.

	\bibitem{jacobson1995}
	Jacobson, T. (1995).
	\textit{Thermodynamics of Spacetime}.
	Physical Review Letters 75, 1260.

	\bibitem{jwst_early}
	JWST Team (2023).
	\textit{Early Universe Observations}.
	Nature Astronomy.

	\bibitem{kasevich2023}
	Kasevich, M., et al. (2023).
	\textit{Atom Interferometry}.
	Physical Review Letters.

	\bibitem{lerner2014}
	Lerner, E. J. (2014).
	\textit{The Big Bang Never Happened}.
	Vintage.

	\bibitem{lisa2017}
	LISA Pathfinder Collaboration (2017).
	\textit{Gravitational Wave Detection}.
	Physical Review Letters.

	\bibitem{lopez2010}
	Lopez-Corredoira, M. (2010).
	\textit{Non-Standard Cosmology}.
	Astron. Astrophys. 527, A96.

	\bibitem{ludlow2015}
	Ludlow, A. D., et al. (2015).
	\textit{Optical Atomic Clocks}.
	Rev. Mod. Phys. 87, 637.

	\bibitem{maldacena1998}
	Maldacena, J. (1998).
	\textit{The Large N Limit of Superconformal Field Theories}.
	Adv. Theor. Math. Phys. 2, 231.

	\bibitem{mueller2014}
	Mueller, P., et al. (2014).
	\textit{Atom Interferometry}.
	Nature, 510, 518.

	\bibitem{muong2_2023}
	Muon g-2 Collaboration (2023).
	\textit{Updated Measurement}.
	Physical Review Letters.

	\bibitem{nottale1993}
	Nottale, L. (1993).
	\textit{Fractal Space-Time and Microphysics}.
	World Scientific.

	\bibitem{pascher2025cmb}
	Pascher, J. (2025).
	\textit{CMB Analysis in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher2025g2}
	Pascher, J. (2025).
	\textit{g-2 in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher:fundamentals}
	Pascher, J. (2025).
	\textit{T0-Theory Fundamentals}.
	Unpublished manuscript.

	\bibitem{pascher:g2_rev9}
	Pascher, J. (2025).
	\textit{g-2 Extended Calculation Rev. 9}.
	Unpublished manuscript.

	\bibitem{pascher:ml_addendum}
	Pascher, J. (2025).
	\textit{Machine Learning Addendum}.
	Unpublished manuscript.

	\bibitem{pascher_cmb_en}
	Pascher, J. (2025).
	\textit{CMB in T0-Theory (English)}.
	Unpublished manuscript.

	\bibitem{pascher_cosmos_en}
	Pascher, J. (2025).
	\textit{Cosmic Parameters in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher_gravitation_en}
	Pascher, J. (2025).
	\textit{Gravitation in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher_lagrangian_en}
	Pascher, J. (2025).
	\textit{Lagrangian Formulation in T0-Theory}.
	Unpublished manuscript.

	\bibitem{pascher_t0_energy_2025}
	Pascher, J. (2025).
	\textit{Energy in T0-Theory}.
	Unpublished manuscript.

	\bibitem{penrose1959}
	Penrose, R. (1959).
	\textit{The Apparent Shape of a Relativistically Moving Sphere}.
	Proc. Cambridge Phil. Soc. 55, 137.

	\bibitem{polchinski1998}
	Polchinski, J. (1998).
	\textit{String Theory}.
	Cambridge University Press.

	\bibitem{riess2022}
	Riess, A. G., et al. (2022).
	\textit{A Comprehensive Measurement of the Local Value of H0}.
	ApJ, 934, L7.

	\bibitem{susskind1995}
	Susskind, L. (1995).
	\textit{The World as a Hologram}.
	J. Math. Phys. 36, 6377.

	\bibitem{terrell1959}
	Terrell, J. (1959).
	\textit{Invisibility of the Lorentz Contraction}.
	Physical Review 116, 1041.

	\bibitem{verlinde2011}
	Verlinde, E. (2011).
	\textit{On the Origin of Gravity and the Laws of Newton}.
	JHEP 1104, 029.

	\bibitem{weiskopf2000}
	Weiskopf, D. (2000).
	\textit{Visualization of Relativistic Effects}.
	University of T\"{u}bingen thesis.

\end{thebibliography}

\end{document}
