\documentclass[11pt,a4paper,openany]{book}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx}
\usepackage[unicode,pdfencoding=auto,hypertexnames=false]{hyperref}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{siunitx}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{tikz}
\usepackage[most]{tcolorbox}
\tcbset{colback=white,colframe=black,arc=2pt,boxrule=0.5pt}
\tikzset{
  t0blue/.style={draw=blue,fill=blue!10},
  t0red/.style={draw=red,fill=red!10},
  t0green/.style={draw=green!50!black,fill=green!10},
  t0orange/.style={draw=orange,fill=orange!10},
}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage{adjustbox}
\usepackage{xcolor}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\pagestyle{fancy}
\setlength{\headheight}{28pt}

\newcommand{\checkmarkx}{\checkmark}
\newcommand{\warningx}{\textbf{!}}

% Makros aus Einzel-Dokumenten (Fallback-Definitionen)
\newcommand{\mytimes}{\times}
\newcommand{\myapprox}{\approx}
\newcommand{\mysim}{\sim}
\newcommand{\myomega}{\omega}
\newcommand{\mypi}{\pi}
\newcommand{\myrightarrow}{\rightarrow}
\newcommand{\mypropto}{\propto}
\newcommand{\deltafield}{\delta\phi}
\newcommand{\xipar}{\xi}
\newcommand{\lambdah}{\lambda_h}

% Additional macros used in chapter files
\newcommand{\Kfrak}{K_{\text{frak}}}  % Fractal correction factor
\newcommand{\Dfrak}{D_f}              % Fractal dimension
\newcommand{\betapar}{\beta}          % T0 beta parameter
\newcommand{\alphapar}{\alpha}        % T0 alpha parameter
\newcommand{\Efield}{E}               % Energy field
% Note: checkmarkxa/warningxa are variants used in auto-generated chapter files
\newcommand{\checkmarkxa}{\checkmark}
\newcommand{\warningxa}{\textbf{!}}

% Einfache abstract-Umgebung für Kapitel:
\newenvironment{abstract}{%
  \begin{center}\bfseries Abstract\end{center}\small
}{\par}

\title{T0 Time--Mass Duality\\Unified English Book}
\author{J. Pascher}
\date{\today}

\begin{document}

\maketitle
\tableofcontents

%==============================
% Automatisch generierte Kapitel:

%%------------------------------
\input{chapters_en/T0_Grundlagen_En_ch}

%%------------------------------
\input{chapters_en/T0_Modell_Uebersicht_En_ch}

%%------------------------------
\input{chapters_en/T0_tm-erweiterung-x6_En_ch}

%%------------------------------
\input{chapters_en/T0_Teilchenmassen_En_ch}

%%------------------------------
\input{chapters_en/T0_Neutrinos_En_ch}

%%------------------------------
\input{chapters_en/T0_xi-und-e_En_ch}

%%==============================
% Globales Literaturverzeichnis
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
		
		\bibitem{pdg2024}
		Particle Data Group Collaboration (2024). 
		\textit{Review of Particle Physics}. 
		Progress of Theoretical and Experimental Physics, 2024(8), 083C01.
		\url{https://pdg.lbl.gov}
		
		\bibitem{flag2024}
		Aoki, Y., et al. (FLAG Collaboration) (2024). 
		\textit{FLAG Review 2024 of Lattice Results for Low-Energy Constants}. 
		arXiv:2411.04268.
		\url{https://arxiv.org/abs/2411.04268}
		
		\bibitem{fermilab_muon_g2}
		Abi, B., et al. (Muon g-2 Collaboration) (2021). 
		\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
		Physical Review Letters, 126, 141801.
		
		\bibitem{peskin_schroeder}
		Peskin, M. E., \& Schroeder, D. V. (1995). 
		\textit{An Introduction to Quantum Field Theory}. 
		Addison-Wesley.
		
		\bibitem{weinberg_qft}
		Weinberg, S. (1995). 
		\textit{The Quantum Theory of Fields, Vol. I--III}. 
		Cambridge University Press.
		
		\bibitem{griffiths_particle}
		Griffiths, D. (2008). 
		\textit{Introduction to Elementary Particles}. 
		Wiley-VCH.
		
		\bibitem{mandl_shaw}
		Mandl, F., \& Shaw, G. (2010). 
		\textit{Quantum Field Theory (2nd ed.)}. 
		Wiley.
		
		\bibitem{srednicki_qft}
		Srednicki, M. (2007). 
		\textit{Quantum Field Theory}. 
		Cambridge University Press.
		
		\bibitem{t0_fundamentals}
		Pascher, J. (2024). 
		\textit{T0-Theory: Foundations of Time-Mass Duality}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_fine_structure}
		Pascher, J. (2024). 
		\textit{T0-Theory: The Fine Structure Constant}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_neutrinos}
		Pascher, J. (2024). 
		\textit{T0-Theory: Neutrino Masses and PMNS Mixing}. 
		Unpublished manuscript, HTL Leonding.
		
		\bibitem{t0_github}
		Pascher, J. (2024--2025). 
		\textit{T0-Time-Mass-Duality Repository}. 
		GitHub.
		\url{https://github.com/jpascher/T0-Time-Mass-Duality}
		
		\bibitem{lattice_qcd_review}
		Kronfeld, A. S. (2012). 
		\textit{Twenty-first Century Lattice Gauge Theory: Results from the QCD Lagrangian}. 
		Annual Review of Nuclear and Particle Science, 62, 265--284.
		
		\bibitem{neutrino_mixing_pdg}
		Particle Data Group Collaboration (2024). 
		\textit{Neutrino Masses, Mixing, and Oscillations}. 
		PDG Review 2024.
		\url{https://pdg.lbl.gov/2024/reviews/rpp2024-rev-neutrino-mixing.pdf}
		
		\bibitem{higgs_discovery}
		ATLAS and CMS Collaborations (2012). 
		\textit{Observation of a New Particle in the Search for the Standard Model Higgs Boson}. 
		Physics Letters B, 716, 1--29.
		
		\bibitem{Brannen2005}
		C. P. Brannen, ``Estimate of neutrino masses from Koide's relation'', \textit{arXiv:hep-ph/0505028} (2005).
		\url{https://arxiv.org/abs/hep-ph/0505028}
		
		\bibitem{Brannen2006}
		C. P. Brannen, ``Koide Mass Formula for Neutrinos'', \textit{arXiv:0702.0052} (2006).
		\url{http://brannenworks.com/MASSES.pdf}
		
		\bibitem{PhaseVectors2025}
		Anonymous, ``The Koide Relation and Lepton Mass Hierarchy from Phase Vectors'', \textit{rXiv:2507.0040} (2025).
		\url{https://rxiv.org/pdf/2507.0040v1.pdf}
		
		\bibitem{PDG2025}
		Particle Data Group, ``Review of Particle Physics'', \textit{Phys. Rev. D} \textbf{112} (2025) 030001.
		\url{https://pdg.lbl.gov/2025/}
\end{thebibliography}

\end{document}
