\documentclass[12pt,a4paper]{book}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{lmodern}

% Mathematics
\usepackage{amsmath,amssymb,amsthm}
\usepackage{physics}
\usepackage{siunitx}

% Layout
\usepackage[left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage{titlesec}

% Tables and Graphics
\usepackage{booktabs}
\usepackage{array}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric}

% Colors and Boxes
\usepackage{xcolor}
\usepackage[most]{tcolorbox}

% References
\usepackage{hyperref}

% Algorithm (optional)
\usepackage{algorithm}
\usepackage{algpseudocode}

% Additional packages
\usepackage{adjustbox}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumitem}

%==============================
% Color Definitions
%==============================
\definecolor{t0blue}{RGB}{0,102,204}
\definecolor{t0red}{RGB}{204,0,0}
\definecolor{t0green}{RGB}{0,153,0}
\definecolor{boxgray}{RGB}{240,240,240}
\definecolor{deepblue}{RGB}{0,0,127}
\definecolor{deepred}{RGB}{191,0,0}
\definecolor{deepgreen}{RGB}{0,127,0}

%==============================
% Theorem Environments
%==============================
\theoremstyle{definition}
\newtheorem{insight}{Insight}[chapter]
\newtheorem{discovery}{Discovery}[chapter]
\newtheorem{definition}{Definition}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\newtheorem{remark}{Remark}[chapter]
\newtheorem{example}{Example}[chapter]

%==============================
% Abstract Environment for Chapters
%==============================
\newenvironment{abstract}{%
  \begin{quote}\itshape\noindent
}{%
  \end{quote}
}

%==============================
% Custom Boxes
%==============================
\newtcolorbox{fundamental}[1][]{
	colback=boxgray,
	colframe=t0blue,
	fonttitle=\bfseries,
	title=#1,
	sharp corners,
	boxrule=2pt
}

\newtcolorbox{newperspective}[1][]{
	colback=red!5!white,
	colframe=t0red,
	fonttitle=\bfseries,
	title=#1,
	sharp corners,
	boxrule=2pt
}

\newtcolorbox{keyresult}[1][Key Result]{
	colback=blue!5,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{warning}[1][Important Note]{
	colback=red!5,
	colframe=red!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{revolutionary}[1][Revolutionary Insight]{
	colback=green!5,
	colframe=green!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{formula}[1][Central Formula]{
	colback=yellow!5,
	colframe=orange!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{experiment}[1][Experimental Test]{
	colback=purple!5,
	colframe=purple!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{alternative}[1][Alternative Interpretation]{
	colback=gray!10!white,
	colframe=gray!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{foundation}[1][Foundation]{
	colback=blue!5,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{derivation}[1][Derivation]{
	colback=yellow!5,
	colframe=orange!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{dimensional}[1][Dimensional Analysis]{
	colback=green!5,
	colframe=green!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{verification}[1][Verification]{
	colback=purple!5,
	colframe=purple!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{historical}[1][Historical Context]{
	colback=brown!5,
	colframe=brown!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{method}[1][Method]{
	colback=cyan!5,
	colframe=cyan!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{equivalence}[1][Equivalence]{
	colback=magenta!5,
	colframe=magenta!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{experimental}[1][Experimental]{
	colback=orange!5,
	colframe=orange!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{comparison}[1][Comparison]{
	colback=teal!5,
	colframe=teal!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{physical}[1][Physical Interpretation]{
	colback=lime!5,
	colframe=lime!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{prediction}[1][Prediction]{
	colback=pink!5,
	colframe=pink!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{core}[1][Core Result]{
	colback=blue!10,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{interpretation}[1][Interpretation]{
	colback=violet!5,
	colframe=violet!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{application}[1][Application]{
	colback=olive!5,
	colframe=olive!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{speculation}[1][Speculation]{
	colback=gray!5,
	colframe=gray!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{photon}[1][Photon Analysis]{
	colback=yellow!5,
	colframe=yellow!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{koidebox}[1][Koide Formula]{
	colback=cyan!5,
	colframe=cyan!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{explanation}[1][Explanation]{
	colback=blue!3,
	colframe=blue!50!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{result}[1][Result]{
	colback=green!5,
	colframe=green!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{summary}[1][Summary]{
	colback=blue!5,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{implication}[1][Implication]{
	colback=red!3,
	colframe=red!50!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{question}[1][Question]{
	colback=orange!5,
	colframe=orange!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{axiom}[1][Axiom]{
	colback=purple!5,
	colframe=purple!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{hypothesis}[1][Hypothesis]{
	colback=teal!5,
	colframe=teal!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{mathematics}[1][Mathematical Framework]{
	colback=gray!5,
	colframe=gray!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{important}[1][Important]{
	colback=red!5,
	colframe=red!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{note}[1][Note]{
	colback=yellow!5,
	colframe=yellow!75!black,
	fonttitle=\bfseries,
	title=#1
}

\newtcolorbox{concept}[1][Concept]{
	colback=blue!5,
	colframe=blue!75!black,
	fonttitle=\bfseries,
	title=#1
}

%==============================
% Custom Commands
%==============================
\newcommand{\xipar}{\xi}
\newcommand{\Lxi}{L_\xi}
\newcommand{\Exi}{E_\xi}
\newcommand{\rhoCMB}{\rho_{\text{CMB}}}
\newcommand{\rhoCasimir}{\rho_{\text{Casimir}}}
\newcommand{\betapar}{\beta}
\newcommand{\alphapar}{\alpha}
\newcommand{\Efield}{E}
\newcommand{\Kfrak}{\mathfrak{K}}
\newcommand{\Dfrak}{\mathfrak{D}}
\newcommand{\Tfrak}{\mathfrak{T}}
\newcommand{\Mfrak}{\mathfrak{M}}
\newcommand{\Efrak}{\mathfrak{E}}
\newcommand{\Pfrak}{\mathfrak{P}}
\newcommand{\Lfrak}{\mathfrak{L}}
\newcommand{\Sfrak}{\mathfrak{S}}
\newcommand{\Rfrak}{\mathfrak{R}}
\newcommand{\Afrak}{\mathfrak{A}}
\newcommand{\Bfrak}{\mathfrak{B}}
\newcommand{\Cfrak}{\mathfrak{C}}
\newcommand{\Gfrak}{\mathfrak{G}}
\newcommand{\Hfrak}{\mathfrak{H}}
\newcommand{\Ifrak}{\mathfrak{I}}
\newcommand{\Jfrak}{\mathfrak{J}}
\newcommand{\Nfrak}{\mathfrak{N}}
\newcommand{\Ofrak}{\mathfrak{O}}
\newcommand{\Qfrak}{\mathfrak{Q}}
\newcommand{\Ufrak}{\mathfrak{U}}
\newcommand{\Vfrak}{\mathfrak{V}}
\newcommand{\Wfrak}{\mathfrak{W}}
\newcommand{\Xfrak}{\mathfrak{X}}
\newcommand{\Yfrak}{\mathfrak{Y}}
\newcommand{\Zfrak}{\mathfrak{Z}}

%==============================
% Header and Footer
%==============================
\pagestyle{fancy}
\fancyhf{}
\fancyhead[LE,RO]{\thepage}
\fancyhead[RE]{\textsc{T0 Theory Collection}}
\fancyhead[LO]{\textsc{J. Pascher}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

%==============================
% Hyperref Settings
%==============================
\hypersetup{
	colorlinks=true,
	linkcolor=t0blue,
	citecolor=t0green,
	urlcolor=t0blue,
	pdftitle={T0 Theory: Complete Collection},
	pdfauthor={Johann Pascher}
}

%==============================
% Title
%==============================
\title{
	\textbf{T0 Theory}\\
	\vspace{0.5cm}
	\Large Complete Document Collection\\
	\vspace{0.3cm}
	\normalsize Time-Mass Duality and the Unified Field
}

\author{Johann Pascher\\
	\texttt{johann.pascher@gmail.com}}

\date{\today}

%==============================
% Document
%==============================
\begin{document}

\maketitle

\tableofcontents

%==============================
% Part I: Fundamentals (Book 4 Order)
%==============================
\part{Fundamentals}

\input{chapters_unified/T0_Introduction_En_ch}
\input{chapters_unified/T0_Modell_Uebersicht_En_ch}
\input{chapters_unified/T0_Grundlagen_En_ch}
\input{chapters_unified/T0_tm-erweiterung-x6_En_ch}
\input{chapters_unified/T0_xi_ursprung_En_ch}
\input{chapters_unified/T0_xi-und-e_En_ch}
\input{chapters_unified/xi_parmater_partikel_En_ch}
\input{chapters_unified/T0_Teilchenmassen_En_ch}
\input{chapters_unified/T0_Neutrinos_En_ch}

%==============================
% Part II: Energy and Constants
%==============================
\part{Energy and Constants}

\input{chapters_unified/T0_Energie_En_ch}
\input{chapters_unified/T0_Feinstruktur_En_ch}
\input{chapters_unified/T0_Gravitationskonstante_En_ch}
\input{chapters_unified/T0_SI_En_ch}
\input{chapters_unified/T0_nat-si_En_ch}

%==============================
% Part III: Anomalous Magnetic Moments
%==============================
\part{Anomalous Magnetic Moments}

\input{chapters_unified/T0_Anomale_Magnetische_Momente_En_ch}
\input{chapters_unified/T0_Anomale-g2-9_En_ch}
\input{chapters_unified/T0_g2-erweiterung-4_En_ch}

%==============================
% Part IV: Cosmology
%==============================
\part{Cosmology}

\input{chapters_unified/T0_Kosmologie_En_ch}
\input{chapters_unified/T0_Geometrische_Kosmologie_En_ch}
\input{chapters_unified/T0_7-fragen-3_En_ch}
\input{chapters_unified/T0_threeclock_En_ch}
\input{chapters_unified/T0_peratt_En_ch}
\input{chapters_unified/Hannah_En_ch}
\input{chapters_unified/Markov_En_ch}
\input{chapters_unified/T0_penrose_En_ch}
\input{chapters_unified/T0_umkehrung_En_ch}
\input{chapters_unified/T0-Theory-vs-Synergetics_En_ch}

%==============================
% Part V: Quantum Theory
%==============================
\part{Quantum Theory}

\input{chapters_unified/T0_QM-QFT-RT_En_ch}
\input{chapters_unified/T0_QAT_En_ch}
\input{chapters_unified/Bell_En_ch}
\input{chapters_unified/T0_netze_En_ch}

%==============================
% Part VI: QM Optimization
%==============================
\part{QM Optimization}

\input{chapters_unified/T0_QM-optimierung_En_ch}
\input{chapters_unified/QM_En_ch}

%==============================
% Part VII: Lagrangian and Dirac
%==============================
\part{Lagrangian and Dirac}

\input{chapters_unified/T0_lagrndian_En_ch}
\input{chapters_unified/LagrandianVergleichEn_ch}
\input{chapters_unified/diracVereinfachtEn_ch}
\input{chapters_unified/diracEn_ch}

%==============================
% Part VIII: CMB and Mathematical Structure
%==============================
\part{CMB and Mathematical Structure}

\input{chapters_unified/TempEinheitenCMBEn_ch}
\input{chapters_unified/Ho_En_ch}
\input{chapters_unified/HdokumentEn_ch}
\input{chapters_unified/Mathematische_struktur_En_ch}
\input{chapters_unified/MathZeitMasseLagrangeEn_ch}
\input{chapters_unified/redshift_deflection_En_ch}
\input{chapters_unified/cosmic_En_ch}

%==============================
% Part IX: Formulas and Calculations
%==============================
\part{Formulas and Calculations}

\input{chapters_unified/neutrino-Formel_En_ch}
\input{chapters_unified/FeinstrukturkonstanteEn_ch}
\input{chapters_unified/Bewegungsenergie_En_ch}
\input{chapters_unified/Formeln_Energiebasiert_En_ch}
\input{chapters_unified/systemEn_ch}
\input{chapters_unified/RSA_En_ch}
\input{chapters_unified/RelokativesZahlensystemEn_ch}

%==============================
% Part X: Mass Elimination and Analysis
%==============================
\part{Mass Elimination and Analysis}

\input{chapters_unified/Moll_CandelaEn_ch}
\input{chapters_unified/T0vsESM_ConceptualAnalysis_En_ch}
\input{chapters_unified/EliminationOfMassEn_ch}
\input{chapters_unified/Elimination_Of_Mass_Dirac_TabelleEn_ch}
\input{chapters_unified/E-mc2_En_ch}
\input{chapters_unified/QM-DetrmisticEn_ch}

%==============================
% Part XI: Applications
%==============================
\part{Applications}

\input{chapters_unified/T0_photonenchip-china_En_ch}
\input{chapters_unified/Zusammenfassung_En_ch}

%==============================
% Bibliography
%==============================
\bibliographystyle{plain}
\begin{thebibliography}{99}

% Core T0 Theory References
\bibitem{pascher2024}
J. Pascher, \emph{T0 Theory: Time-Mass Duality}, 2024.

\bibitem{pascher2025t0}
J. Pascher, \emph{T0 Theory: Fundamentals}, 2025.

\bibitem{pascher2025qm}
J. Pascher, \emph{T0 Theory: Quantum Mechanics}, 2025.

\bibitem{pascher2025si}
J. Pascher, \emph{T0 Theory: SI Units}, 2025.

\bibitem{pascher2025g2}
J. Pascher, \emph{T0 Theory: The g-2 Anomaly}, 2025.

\bibitem{pascher2025cmb}
J. Pascher, \emph{T0 Theory: CMB Analysis}, 2025.

% Historical Physics
\bibitem{einstein1905}
A. Einstein, \emph{On the Electrodynamics of Moving Bodies}, Annalen der Physik, 1905.

\bibitem{dirac1928}
P.A.M. Dirac, \emph{The Quantum Theory of the Electron}, Proc. Roy. Soc. A, 1928.

\bibitem{planck1900}
M. Planck, \emph{On the Theory of the Energy Distribution Law}, 1900.

\bibitem{mach1883}
E. Mach, \emph{Die Mechanik in ihrer Entwicklung}, 1883.

\bibitem{hundert1931}
Various Authors, \emph{100 Authors Against Einstein}, 1931.

\bibitem{dingle1972}
H. Dingle, \emph{Science at the Crossroads}, 1972.

% Penrose and Terrell Effect
\bibitem{terrell1959}
J. Terrell, \emph{Invisibility of the Lorentz Contraction}, Phys. Rev., 1959.

\bibitem{penrose1959}
R. Penrose, \emph{The Apparent Shape of a Relativistically Moving Sphere}, Proc. Cambridge Phil. Soc., 1959.

\bibitem{penrose1967}
R. Penrose, \emph{Twistor Algebra}, J. Math. Phys., 1967.

\bibitem{penrose2004}
R. Penrose, \emph{The Road to Reality}, 2004.

\bibitem{terrell2025}
J. Terrell et al., \emph{Modern Terrell-Penrose Visualization}, 2025.

\bibitem{weiskopf2000}
D. Weiskopf, \emph{Visualization of Four-dimensional Spacetimes}, 2000.

\bibitem{mueller2014}
T. Müller, \emph{Visual Appearance of Relativistically Moving Objects}, 2014.

\bibitem{hossenfelder2025}
S. Hossenfelder, \emph{YouTube: The Terrell Effect}, 2025.

% Quantum Gravity and String Theory
\bibitem{rovelli2004}
C. Rovelli, \emph{Quantum Gravity}, Cambridge University Press, 2004.

\bibitem{thiemann2007}
T. Thiemann, \emph{Modern Canonical Quantum Gravity}, Cambridge University Press, 2007.

\bibitem{ashtekar2004}
A. Ashtekar, J. Lewandowski, \emph{Background Independent Quantum Gravity}, Class. Quant. Grav., 2004.

\bibitem{jacobson1995}
T. Jacobson, \emph{Thermodynamics of Spacetime}, Phys. Rev. Lett., 1995.

\bibitem{maldacena1998}
J. Maldacena, \emph{The Large N Limit of Superconformal Field Theories}, Adv. Theor. Math. Phys., 1998.

\bibitem{polchinski1998}
J. Polchinski, \emph{String Theory}, Cambridge University Press, 1998.

\bibitem{susskind1995}
L. Susskind, \emph{The World as a Hologram}, J. Math. Phys., 1995.

\bibitem{verlinde2011}
E. Verlinde, \emph{On the Origin of Gravity}, JHEP, 2011.

% Cosmology
\bibitem{hoyle1948}
F. Hoyle, \emph{A New Model for the Expanding Universe}, MNRAS, 1948.

\bibitem{bondi1948}
H. Bondi, T. Gold, \emph{The Steady-State Theory}, MNRAS, 1948.

\bibitem{zwicky1929}
F. Zwicky, \emph{On the Redshift of Spectral Lines}, Proc. Nat. Acad. Sci., 1929.

\bibitem{lopez2010}
C. Lopez-Corredoira, \emph{Tests of Cosmological Models}, Int. J. Mod. Phys. D, 2010.

\bibitem{lerner2014}
E. Lerner, \emph{Evidence for a Non-Expanding Universe}, 2014.

\bibitem{albrecht1999}
A. Albrecht, J. Magueijo, \emph{Variable Speed of Light}, Phys. Rev. D, 1999.

\bibitem{barrow1999}
J. Barrow, \emph{Cosmologies with Varying Light Speed}, Phys. Rev. D, 1999.

\bibitem{riess2022}
A. Riess et al., \emph{A Comprehensive Measurement of the Local Value of the Hubble Constant}, ApJ, 2022.

\bibitem{desi2025}
DESI Collaboration, \emph{DESI Year 1 Results}, 2025.

\bibitem{divalentino2021}
E. Di Valentino et al., \emph{Planck Evidence for a Closed Universe}, Nat. Astron., 2021.

% Conformal Field Theory
\bibitem{francesco1997}
P. Di Francesco et al., \emph{Conformal Field Theory}, Springer, 1997.

% Experimental Physics
\bibitem{pdg2024}
Particle Data Group, \emph{Review of Particle Physics}, 2024.

\bibitem{codata2019}
CODATA, \emph{Recommended Values of Fundamental Constants}, 2019.

\bibitem{newell2018}
D. Newell et al., \emph{The CODATA 2017 Values of h, e, k, and $N_A$}, Metrologia, 2018.

\bibitem{muong2_2023}
Muon g-2 Collaboration, \emph{Measurement of the Anomalous Magnetic Moment of the Muon}, Phys. Rev. Lett., 2023.

\bibitem{fermilab2023}
Fermilab, \emph{Muon g-2 Results}, 2023.

\bibitem{atlas2023}
ATLAS Collaboration, \emph{Measurements at the LHC}, 2023.

\bibitem{atlas2023higgs}
ATLAS Collaboration, \emph{Higgs Boson Properties}, 2023.

\bibitem{cms2023top}
CMS Collaboration, \emph{Top Quark Measurements}, 2023.

\bibitem{cms2024}
CMS Collaboration, \emph{Heavy Ion Collisions}, 2024.

\bibitem{alice2023}
ALICE Collaboration, \emph{Quark-Gluon Plasma Studies}, 2023.

\bibitem{kasevich2023}
M. Kasevich et al., \emph{Atom Interferometry}, 2023.

\bibitem{ludlow2015}
A. Ludlow et al., \emph{Optical Atomic Clocks}, Rev. Mod. Phys., 2015.

\bibitem{brewer2019}
S. Brewer et al., \emph{Al$^+$ Optical Clock}, Phys. Rev. Lett., 2019.

\bibitem{lisa2017}
LISA Collaboration, \emph{LISA Mission}, 2017.

% Fractal Physics
\bibitem{nottale1993}
L. Nottale, \emph{Fractal Space-Time and Microphysics}, World Scientific, 1993.

\bibitem{elnaschie2004}
M.S. El Naschie, \emph{E-Infinity Theory}, Chaos Solitons Fractals, 2004.

% Philosophy and Foundations
\bibitem{wheeler1990}
J.A. Wheeler, \emph{Information, Physics, Quantum}, 1990.

\bibitem{barbour1999}
J. Barbour, \emph{The End of Time}, Oxford University Press, 1999.

\bibitem{sciama1953}
D. Sciama, \emph{On the Origin of Inertia}, MNRAS, 1953.

% String Theory Extensions
\bibitem{becker2007}
K. Becker et al., \emph{String Theory and M-Theory}, Cambridge University Press, 2007.

\end{thebibliography}

\end{document}
