\documentclass[11pt,a4paper,openany]{book}

% Standardized preamble - T0_Book1a_En.tex
\input{T0_preamble_En}

\begin{document}
	
	% Your document content here...
	

% Globales Literaturverzeichnis (fixed: standard env, deduped, plain format)
\chapter*{References}
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
	
	\bibitem{pdg2024}
	Particle Data Group Collaboration (2024). 
	\textit{Review of Particle Physics}. 
	Progress of Theoretical and Experimental Physics, 2024(8), 083C01.
	\url{https://pdg.lbl.gov}
	
	\bibitem{flag2024}
	Aoki, Y., et al. (FLAG Collaboration) (2024). 
	\textit{FLAG Review 2024 of Lattice Results for Low-Energy Constants}. 
	arXiv:2411.04268.
	\url{https://arxiv.org/abs/2411.04268}
	
	\bibitem{fermilab_muon_g2}
	Abi, B., et al. (Muon g-2 Collaboration) (2021). 
	\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
	Physical Review Letters, 126, 141801.
	
	\bibitem{peskin_schroeder}
	Peskin, M. E., \& Schroeder, D. V. (1995). 
	\textit{An Introduction to Quantum Field Theory}. 
	Addison-Wesley.
	
	\bibitem{weinberg_qft}
	Weinberg, S. (1995). 
	\textit{The Quantum Theory of Fields, Vol. I--III}. 
	Cambridge University Press.
	
	\bibitem{griffiths_particle}
	Griffiths, D. (2008). 
	\textit{Introduction to Elementary Particles}. 
	Wiley-VCH.
	
	\bibitem{mandl_shaw}
	Mandl, F., \& Shaw, G. (2010). 
	\textit{Quantum Field Theory (2nd ed.)}. 
	Wiley.
	
	\bibitem{srednicki_qft}
	Srednicki, M. (2007). 
	\textit{Quantum Field Theory}. 
	Cambridge University Press.
	
	\bibitem{t0_fundamentals}
	Pascher, J. (2024). 
	\textit{T0-Theory: Foundations of Time-Mass Duality}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_fine_structure}
	Pascher, J. (2024). 
	\textit{T0-Theory: The Fine Structure Constant}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_neutrinos}
	Pascher, J. (2024). 
	\textit{T0-Theory: Neutrino Masses and PMNS Mixing}. 
	Unpublished manuscript, HTL Leonding.
	
	\bibitem{t0_github}
	Pascher, J. (2024--2025). 
	\textit{T0-Time-Mass-Duality Repository}. 
	GitHub.
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{lattice_qcd_review}
	Kronfeld, A. S. (2012). 
	\textit{Twenty-first Century Lattice Gauge Theory: Results from the QCD Lagrangian}. 
	Annual Review of Nuclear and Particle Science, 62, 265--284.
	
	\bibitem{neutrino_mixing_pdg}
	Particle Data Group Collaboration (2024). 
	\textit{Neutrino Masses, Mixing, and Oscillations}. 
	PDG Review 2024.
	\url{https://pdg.lbl.gov/2024/reviews/rpp2024-rev-neutrino-mixing.pdf}
	
	\bibitem{higgs_discovery}
	ATLAS and CMS Collaborations (2012). 
	\textit{Observation of a New Particle in the Search for the Standard Model Higgs Boson}. 
	Physics Letters B, 716, 1--29.
	
	\bibitem{Brannen2005}
	C. P. Brannen, ``Estimate of neutrino masses from Koide's relation'', \textit{arXiv:hep-ph/0505028} (2005).
	\url{https://arxiv.org/abs/hep-ph/0505028}
	
	\bibitem{Brannen2006}
	C. P. Brannen, ``Koide Mass Formula for Neutrinos'', \textit{arXiv:0702.0052} (2006).
	\url{http://brannenworks.com/MASSES.pdf}
	
	\bibitem{PhaseVectors2025}
	Anonymous, ``The Koide Relation and Lepton Mass Hierarchy from Phase Vectors'', \textit{rXiv:2507.0040} (2025).
	\url{https://rxiv.org/pdf/2507.0040v1.pdf}
	
	\bibitem{PDG2025}
	Particle Data Group, ``Review of Particle Physics'', \textit{Phys. Rev. D} \textbf{112} (2025) 030001.
	\url{https://pdg.lbl.gov/2025/}
	
	\bibitem{casimir1948}
	Casimir, H. B. G. (1948). \textit{On the attraction between two perfectly conducting plates}.
	Proc. K. Ned. Akad. Wet. \textbf{51}, 793.
	
	\bibitem{pdg_2024}
	Particle Data Group (2024). \textit{Review of Particle Physics}.
	Prog. Theor. Exp. Phys. \textbf{2024}, 083C01.
	
	\bibitem{pascher_t0_2025}
	Pascher, J. (2025). \textit{T0 Theory: Foundations and Extensions}.
	HTL Leonding Internal Manuscript.
	
	\bibitem{pascher_xi_parameter_2025}
	Pascher, J. (2025). \textit{Mathematical Analysis of the $\xi$ Parameter in T0 Theory}. 
	Present work - markdown analysis.
	
	\bibitem{pascher_simplified_dirac_2025}
	Pascher, J. (2025). \textit{Simplified Dirac Equation in T0 Theory: From Complex 4x4 Matrices to Simple Field Node Dynamics}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/diracVereinfachtEn.pdf}
	
	\bibitem{pascher_universal_lagrangian_2025}
	Pascher, J. (2025). \textit{Simple Lagrangian Revolution: From Standard Model Complexity to T0 Elegance}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/LagrandianVergleichEn.pdf}
	
	\bibitem{pascher_system_2025}
	Pascher, J. (2025). \textit{The T0 Revolution: From Particle Complexity to Field Simplicity}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/systemEn.pdf}
	
	\bibitem{pascher_higgs_derivation_2025}
	Pascher, J. (2025). \textit{Field-Theoretic Derivation of the $\xi$ Parameter in Natural Units}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/DerivationVonBetaEn.pdf}
	
	\bibitem{pascher_geometry_dependent_2025}
	Pascher, J. (2025). \textit{Geometry-Dependent $\xi$ Parameters and Electromagnetic Corrections}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Ho_EnergieEn.pdf}
	
	\bibitem{pascher_deterministic_qm_2025}
	Pascher, J. (2025). \textit{Deterministic Quantum Mechanics via T0-Energy Field Formulation}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QM-DetrmisticEn.pdf}
	
	\bibitem{pascher_mass_elimination_2025}
	Pascher, J. (2025). \textit{Elimination of Mass as Dimensional Placeholder in the T0 Model}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/EliminationOfMassEn.pdf}
	
	\bibitem{planck1900}
	M. Planck, \textit{Zur Theorie des Gesetzes der Energieverteilung im Normalspektrum}, Verhandlungen der Deutschen Physikalischen Gesellschaft 2, 237-245 (1900).
	
	\bibitem{planck1906}
	M. Planck, \textit{Vorlesungen über die Theorie der Wärmestrahlung}, Johann Ambrosius Barth, Leipzig, 1906.
	
	\bibitem{hartree1957}
	D. R. Hartree, \textit{The Calculation of Atomic Structures}, John Wiley \& Sons, New York, 1957.
	
	\bibitem{weinberg1995}
	S. Weinberg, \textit{The Quantum Theory of Fields, Vol. 1}, Cambridge University Press, 1995.
	
	\bibitem{peskin1995}
	M. E. Peskin and D. V. Schroeder, \textit{An Introduction to Quantum Field Theory}, Addison-Wesley, 1995.
	
	\bibitem{misner1973}
	C. W. Misner, K. S. Thorne, and J. A. Wheeler, \textit{Gravitation}, W. H. Freeman and Company, 1973.
	
	\bibitem{jackson1998}
	J. D. Jackson, \textit{Classical Electrodynamics}, 3rd edition, John Wiley \& Sons, 1998.
	
	\bibitem{pascher_t0_length_2025}
	J. Pascher, \textit{Beyond the Planck Scale: The T0 Length in Quantum Gravity}, March 24, 2025.
	
	\bibitem{muong2_fermilab_2021}
	Muon g-2 Collaboration (2021). 
	\textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. 
	Phys. Rev. Lett. \textbf{126}, 141801.
	
	\bibitem{sm_g2_2025}
	Lattice QCD Collaboration (2025). \textit{Updated Hadronic Vacuum Polarization Contribution to Muon g-2}. Phys. Rev. D \textbf{112}, 034507.
	
	\bibitem{mug2_final_2025} 
	Muon g-2 Collaboration (2025). \textit{Final Results from the Fermilab Muon g-2 Experiment}. Nature Phys. \textbf{21}, 1125--1130.
	
	\bibitem{pascher_t0_theory_2025}
	Pascher, J. (2025). 
	\textit{T0-Time-Mass Duality: Fundamental Principles and Experimental Predictions}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{pascher_lagrangian_extended_2025}
	Pascher, J. (2025). 
	\textit{Extended Lagrangian Density with Time Field for Explaining the Muon g-2 Anomaly}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/CompleteMuon_g-2_AnalysisDe.pdf}
	
	\bibitem{pascher_mathematical_structure_2025}
	Pascher, J. (2025). 
	\textit{Mathematical Structure of T0-Theory: From Complex Standard Model Physics to Elegant Field Unification}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Mathematische_struktur_En.tex}
	
	\bibitem{pascher_higgs_connection_2025}
	Pascher, J. (2025). 
	\textit{Higgs-Time Field Connection in T0-Theory: Unification of Mass and Temporal Structure}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/LagrandianVergleichEn.pdf}
	
	\bibitem{T0_SI}
	Pascher, J. (2025). \textit{T0\_SI - THE COMPLETE CONCLUSION: Why the SI Reform 2019 Unwittingly Implemented the $\xi$-Geometry}, T0 Series v1.2, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_SI_En.pdf}
	
	\bibitem{QFT_T0}
	Pascher, J. (2025). \textit{QFT - Quantum Field Theory in the T0 Framework}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QFT_T0_En.pdf}
	
	\bibitem{Fermilab2025}
	E. Bottalico et al., Final Muon g-2 Result (127 ppb Precision), Fermilab, 2025. 
	\url{https://muon-g-2.fnal.gov/result2025.pdf}
	
	\bibitem{CODATA2025}
	CODATA 2025 Recommended Values ($g_e = -2.00231930436092$). 
	\url{https://physics.nist.gov/cgi-bin/cuu/Value?gem}
	
	\bibitem{BelleII2025}
	Belle II Collaboration, Tau Physics Overview and g-2 Plans, 2025. 
	\url{https://indico.cern.ch/event/1466941/}
	
	\bibitem{T0_Calc}
	Pascher, J. (2025). \textit{T0 Calculator}, T0 Repo, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/html/t0_calc.html}
	
	\bibitem{T0_gravitational_constant}
	Pascher, J. (2025). \textit{T0\_Gravitational Constant - Extended with Full Derivation Chain}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_GravitationalConstant_En.pdf}
	
	\bibitem{T0_fine_structure}
	Pascher, J. (2025). \textit{The Fine Structure Constant Revolution}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_FineStructure_En.pdf}
	
	\bibitem{T0_ratio_absolute}
	Pascher, J. (2025). \textit{T0\_Ratio Absolute - Critical Distinction Explained}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Ratio_Absolute_En.pdf}
	
	\bibitem{Hierarchy}
	Pascher, J. (2025). \textit{Hierarchy - Solutions to the Hierarchy Problem}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Hierarchy_En.pdf}
	
	\bibitem{Fermilab2023}
	T. Albahri et al., Phys. Rev. Lett. 131, 161802 (2023). 
	\url{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.131.161802}
	
	\bibitem{Hanneke2008}
	D. Hanneke et al., Phys. Rev. Lett. 100, 120801 (2008). 
	\url{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.100.120801}
	
	\bibitem{DELPHI2004}
	DELPHI Collaboration, Eur. Phys. J. C 35, 159--170 (2004). 
	\url{https://link.springer.com/article/10.1140/epjc/s2004-01852-y}
	
	\bibitem{bell_muon}
	Pascher, J. (2025). \textit{Bell-Muon - Connection between Bell Tests and Muon Anomaly}, T0 Series, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Bell_Muon_En.pdf}
	
	\bibitem{CODATA2022}
	CODATA 2022 Recommended Values.
	
	\bibitem{pascher_t0_foundations_2025}
	Pascher, J. (2025). \textit{T0 Time-Mass Duality: Fundamental Principles}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{pascher_wilson_coefficients_2025}
	Pascher, J. (2025). \textit{Complete Derivation of the Higgs Mass and Wilson Coefficients}. 
	T0 Theory Documentation.
	
	\bibitem{pascher_dirac_simplified_2025}
	Pascher, J. (2025). \textit{Simplified Dirac Equation in T0 Theory}. 
	T0 Theory Documentation.
	
	\bibitem{pascher_qft_extended_2025}
	Pascher, J. (2025). \textit{T0 Quantum Field Theory: Complete Mathematical Extension}. 
	T0 Theory Documentation.
	
	\bibitem{weinberg_qft1}
	Weinberg, S. (1995). \textit{The Quantum Theory of Fields, Volume 1: Foundations}. 
	Cambridge University Press.
	
	\bibitem{nielsen_chuang}
	Nielsen, M. A. and Chuang, I. L. (2010). \textit{Quantum Computation and Quantum Information}. 
	Cambridge University Press.
	
	\bibitem{bell1964}
	Bell, J. S. (1964). \textit{On the Einstein Podolsky Rosen paradox}. 
	Physics, 1(3), 195--200.
	
	\bibitem{aspect1982}
	Aspect, A., Dalibard, J., and Roger, G. (1982). \textit{Experimental test of Bell's inequalities using time-varying analyzers}. 
	Physical Review Letters, 49(25), 1804--1807.
	
	\bibitem{particle_data_group_2022}
	Particle Data Group (2022). \textit{Review of Particle Physics}. 
	Prog. Theor. Exp. Phys. \textbf{2022}, 083C01.
	
	\bibitem{planck_collaboration_2020}
	Planck Collaboration (2020). \textit{Planck 2018 results. VI. Cosmological parameters}. 
	Astron. Astrophys. \textbf{641}, A6.
	
	\bibitem{ligo_collaboration_2016}
	LIGO Scientific Collaboration (2016). \textit{Observation of Gravitational Waves from a Binary Black Hole Merger}. 
	Phys. Rev. Lett. \textbf{116}, 061102.
	
	\bibitem{t0theory} 
	Pascher, J. \textit{T0 Time-Mass Duality Theory}. 
	GitHub Repository, 2025.
	
	\bibitem{qat} 
	Jacob, B. et al. \textit{Quantization and Training of Neural Networks for Efficient Integer-Arithmetic-Only Inference}. 
	CVPR, 2018.
	
	\bibitem{physicsai}
	Carleo, G. et al. \textit{Machine learning and the physical sciences}. 
	Reviews of Modern Physics, 2019.
	
	\bibitem{iyq2025}
	International Year of Quantum (2025). \emph{About IYQ}. \url{https://quantum2025.org/about/}.
	
	\bibitem{nobel2025}
	Reuters (2025). \emph{Trio win Nobel for quantum physics in action}. October 7.
	
	\bibitem{decision2025}
	The Quantum Insider (2025). \emph{New Research on QM Decision-Making}. October 25.
	
	\bibitem{keysight2025}
	Keysight (2025). \emph{Joy of Quantum: IYQ Principles}. September 22.
	
	\bibitem{sciencedaily2025}
	ScienceDaily (2025). \emph{Physicists just built a quantum lie detector}. October 7.
	
	\bibitem{wiki_bell}
	Wikipedia (2025). \emph{Bell's Theorem}. \url{https://en.wikipedia.org/wiki/Bell%27s_theorem}.
	
	\bibitem{pascher_t0}
	Pascher, J. (2025). \emph{T0 Series: Masses, Neutrinos, g-2}. GitHub.
	
	\bibitem{T0_tm_erweiterung}
	Pascher, J. (2025). \textit{T0 Time-Mass Extension: Fractal Corrections in QFT}. T0-Repo, v2.0.
	
	\bibitem{T0_g2_erweiterung}
	Pascher, J. (2025). \textit{g-2 Extension of the T0 Theory: Fractal Dimensions}. T0-Repo, v2.0.
	
	\bibitem{T0_Feinstruktur}
	Pascher, J. (2025). \textit{Derivation of the Fine-Structure Constant in T0}. T0-Repo, v1.4.
	
	\bibitem{t0_basics}
	Pascher, J. (2025). 
	\textit{T0-Theory: Fundamental Principles}. 
	T0 Document Series, Document 1.
	
	\bibitem{t0_gravitationalconstant}
	Pascher, J. (2025). 
	\textit{T0-Theory: Gravitational Constant}. 
	T0 Document Series, Document 3.
	
	\bibitem{t0_particlemasses}
	Pascher, J. (2025). 
	\textit{T0-Theory: Particle Masses}. 
	T0 Document Series, Document 4.
	
	\bibitem{cmb_verification_script}
	Pascher, J. (2025). 
	\textit{T0-Model Casimir-CMB Verification Script}. 
	GitHub Repository. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{cosmic_document}
	Pascher, J. (2025). 
	\textit{T0-Theory: Cosmic Relations}. 
	Project Documentation. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{heisenberg1927}
	Heisenberg, W. (1927). 
	\textit{On the Perceptual Content of Quantum Theoretical Kinematics and Mechanics}. 
	Zeitschrift für Physik, 43(3-4), 172--198.
	
	\bibitem{planck2020}
	Planck Collaboration (2020). 
	\textit{Planck 2018 results. VI. Cosmological parameters}. 
	Astronomy \& Astrophysics, 641, A6.
	
	\bibitem{lamoreaux1997}
	Lamoreaux, S. K. (1997). 
	\textit{Demonstration of the Casimir force in the 0.6 to 6 $\mu$m range}. 
	Physical Review Letters, 78(1), 5--8.
	
	\bibitem{riess2022}
	Riess, A. G., et al. (2022). 
	\textit{A Comprehensive Measurement of the Local Value of the Hubble Constant}. 
	The Astrophysical Journal Letters, 934(1), L7.
	
	\bibitem{weinberg1989}
	Weinberg, S. (1989). 
	\textit{The cosmological constant problem}. 
	Reviews of Modern Physics, 61(1), 1--23.
	
	\bibitem{peebles2003}
	Peebles, P. J. E. (2003). 
	\textit{The Lambda-Cold Dark Matter cosmological model}. 
	Proceedings of the National Academy of Sciences, 100(8), 4421--4426.
	
	\bibitem{einstein1917}
	Einstein, A. (1917). 
	\textit{Cosmological Considerations on the General Theory of Relativity}. 
	Sitzungsberichte der Königlich Preußischen Akademie der Wissenschaften, 142--152.
	
	\bibitem{hubble1929}
	Hubble, E. (1929). 
	\textit{A relation between distance and radial velocity among extra-galactic nebulae}. 
	Proceedings of the National Academy of Sciences, 15(3), 168--173.
	
	\bibitem{friedmann1922}
	Friedmann, A. (1922). 
	\textit{On the Curvature of Space}. 
	Zeitschrift für Physik, 10(1), 377--386.
	
	\bibitem{pascher_t0_foundations}
	J. Pascher, \textit{T0-Theory: Summary of Findings}, T0-Document Series, Nov. 2025.
	
	\bibitem{pascher_geometric_formalism}
	J. Pascher, \textit{The Geometric Formalism of T0 Quantum Mechanics}, T0-Document Series, Nov. 2025.
	
	\bibitem{riess2019}
	A. G. Riess, S. Casertano, W. Yuan, L. M. Macri, D. Scolnic, \textit{Large Magellanic Cloud Cepheid Standards for a 1\% Determination of the Hubble Constant}, The Astrophysical Journal, 876(1), 85, 2019.
	
	\bibitem{nathan2024}
	E. Nathan, A. Hees, H. W. R. W. Z. Yan, \textit{Does the Hubble tension eclipse the Solar System?}, Monthly Notices of the Royal Astronomical Society, 544(1), 975-983, 2024.
	
	\bibitem{pascher_geometric_cosmology}
	J. Pascher, \textit{T0 Cosmology: Redshift as a Geometric Path Effect in a Static Universe}, T0-Document Series, Nov. 2025.
	
	\bibitem{hossenfelder2025}
	Sabine Hossenfelder, ``The Top 10 Physics Paradoxes and Unsolved Problems'', YouTube-Video, 2025. 
	\url{https://www.youtube.com/watch?v=MVu_hRX8A5w}
	
	\bibitem{hossenfelder2006}
	Sabine Hossenfelder, ``Top Ten Unsolved Questions in Physics'', Backreaction Blog, 2006. 
	\url{http://backreaction.blogspot.com/2006/07/top-ten.html}
	
	\bibitem{hossenfelder2019}
	Sabine Hossenfelder, ``Good Problems in the Foundations of Physics'', Backreaction Blog, 2019. 
	\url{http://backreaction.blogspot.com/2019/01/good-problems-in-foundations-of-physics.html}
	
	\bibitem{koide1981}
	Yoshio Koide, ``A Charm-Tau Mass Formula'', Progress of Theoretical Physics, Vol. 66, p. 2285, 1981.
	
	\bibitem{koide1982}
	Yoshio Koide, ``On the Mass of the Charged Leptons'', Progress of Theoretical Physics, Vol. 69, p. 1823, 1983.
	
	\bibitem{brannen2005}
	Carl Brannen, ``The Lepton Masses'', arXiv:hep-ph/0501382, 2005. 
	\url{https://brannenworks.com/MASSES2.pdf}
	
	\bibitem{koide2005}
	L. Stodolsky, ``The strange formula of Dr. Koide'', arXiv:hep-ph/0505220, 2005.
	
	\bibitem{fine_tuning2017}
	Don Page, ``Fine-Tuning'', Stanford Encyclopedia of Philosophy, 2017. 
	\url{https://plato.stanford.edu/entries/fine-tuning/}
	
	\bibitem{barnes2014}
	Luke A. Barnes, ``Fine-Tuning of Particles to Support Life'', Cross Examined, 2014. 
	\url{https://crossexamined.org/fine-tuning-particles-support-life/}
	
	\bibitem{abbott2015}
	H. G. B. Casimir, ``Can Compactifications Solve the Cosmological Constant Problem?'', arXiv:1509.05094, 2015.
	
	\bibitem{milgrom1983}
	Mordehai Milgrom, ``A modification of the Newtonian dynamics as a possible alternative to the hidden mass hypothesis'', Astrophysical Journal, Vol. 270, p. 365, 1983.
	
	\bibitem{banik2021}
	Indranil Banik et al., ``The origin of the MOND critical acceleration scale'', arXiv:2111.01700, 2021.
	
	\bibitem{guth1981}
	Alan H. Guth, ``Inflationary universe: A possible solution to the horizon and flatness problems'', Physical Review D, Vol. 23, p. 347, 1981.
	
	\bibitem{espinosa2018}
	J. R. Espinosa et al., ``Cosmological Aspects of Higgs Vacuum Metastability'', arXiv:1809.06923, 2018.
	
	\bibitem{bednyakov2011}
	V. A. Bednyakov et al., ``On the metastability of the Standard Model vacuum'', arXiv:hep-ph/0104016, 2001.
	
	\bibitem{particle_data_group2024}
	Particle Data Group, ``Review of Particle Physics'', PDG 2024. 
	\url{https://pdg.lbl.gov/}
	
	\bibitem{codata2022}
	CODATA, ``Fundamental Physical Constants'', 2022. 
	\url{https://physics.nist.gov/cuu/Constants/}
	
	\bibitem{t0_kosmologie}
	Johann Pascher, ``T0-Theory: Cosmology – Static Universe and $\xi$-Field Manifestations'', T0 Document Series, Document 6, 2025. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{desi2025}
	DESI Collaboration. (2025). Baryon Acoustic Oscillations DR2. \emph{MNRAS}, submitted.
	
	\bibitem{divalentino2021}
	Di Valentino, E., et al. (2021). In the realm of the Hubble tension. \emph{Class. Quantum Grav.}, 38, 153001.
	
	\bibitem{hoyle1948}
	Hoyle, F. (1948). A New Model for the Expanding Universe. \emph{MNRAS}, 108, 372.
	
	\bibitem{bondi1948}
	Bondi, H., \& Gold, T. (1948). The Steady-State Theory. \emph{MNRAS}, 108, 252.
	
	\bibitem{zwicky1929}
	Zwicky, F. (1929). On the redshift of spectral lines. \emph{PNAS}, 15(10), 773.
	
	\bibitem{lerner2014}
	Lerner, E. J. (2014). Surface brightness data contradict expansion. \emph{Astrophys. Space Sci.}, 349, 625.
	
	\bibitem{lopez2010}
	López-Corredoira, M. (2010). Angular size test on expansion. \emph{Int. J. Mod. Phys. D}, 19, 245.
	
	\bibitem{albrecht1999}
	Albrecht, A., \& Magueijo, J. (1999). Time varying speed of light. \emph{Phys. Rev. D}, 59, 043516.
	
	\bibitem{barrow1999}
	Barrow, J. D. (1999). Cosmologies with varying light speed. \emph{Phys. Rev. D}, 59, 043515.
	
	\bibitem{rovelli2004}
	Rovelli, C. (2004). Quantum Gravity. Cambridge University Press.
	
	\bibitem{thiemann2007}
	Thiemann, T. (2007). Modern Canonical Quantum General Relativity. Cambridge University Press.
	
	\bibitem{ashtekar2004}
	Ashtekar, A., \& Lewandowski, J. (2004). Background independent quantum gravity. \emph{Class. Quantum Grav.}, 21, R53.
	
	\bibitem{polchinski1998}
	Polchinski, J. (1998). String Theory. Cambridge University Press.
	
	\bibitem{becker2007}
	Becker, K., Becker, M., \& Schwarz, J. H. (2007). String Theory and M-Theory. Cambridge University Press.
	
	\bibitem{mach1883}
	Mach, E. (1883). The Science of Mechanics. La Salle: Open Court.
	
	\bibitem{sciama1953}
	Sciama, D. W. (1953). On the origin of inertia. \emph{MNRAS}, 113, 34.
	
	\bibitem{wheeler1990}
	Wheeler, J. A. (1990). Information, physics, quantum. In: Zurek, W. (Ed.), Complexity, Entropy, and Physics of Information.
	
	\bibitem{barbour1999}
	Barbour, J. (1999). The End of Time. Oxford University Press.
	
	\bibitem{cms_atlas}
	ATLAS Collaboration (2012). \textit{Observation of a new particle in the search for the Standard Model Higgs boson}. Phys. Lett. B \textbf{716}, 1--29.
	
	\bibitem{python_fractions}
	Python Software Foundation. (2023). \textit{fractions --- Rational numbers}. Python 3.9 Documentation.
	
	\bibitem{pollard1975}
	Pollard, J. M. (1975). A Monte Carlo method for factorization. \textit{BIT Numerical Mathematics}, 15(3), 331--334.
	
	\bibitem{fermat1643}
	Fermat, P. de (1643). \textit{Methodus ad disquirendam maximam et minimam}. Historical source.
	
	\bibitem{knuth1997}
	Knuth, D. E. (1997). \textit{The art of computer programming, volume 2: Seminumerical algorithms}. Addison-Wesley.
	
	\bibitem{cohen2007}
	Cohen, H. (2007). \textit{Number theory volume I: Tools and diophantine equations}. Springer Science \& Business Media.
	
	\bibitem{shor1994}
	Shor, P. W. (1994). Algorithms for quantum computation: discrete logarithms and factoring. \textit{Proceedings 35th Annual Symposium on Foundations of Computer Science}, 124--134.
	
	\bibitem{higgs1964}
	Higgs, P. W. (1964). Broken symmetries and the masses of gauge bosons. \textit{Physical Review Letters}, 13(16), 508--509.
	
	\bibitem{weinberg1967}
	Weinberg, S. (1967). A model of leptons. \textit{Physical Review Letters}, 19(21), 1264--1266.
	
	\bibitem{gelfand1963}
	Gelfand, I. M., \& Fomin, S. V. (1963). \textit{Calculus of variations}. Prentice-Hall.
	
	\bibitem{arnold1989}
	Arnold, V. I. (1989). \textit{Mathematical methods of classical mechanics}. Springer-Verlag.
	
	\bibitem{evans2010}
	Evans, L. C. (2010). \textit{Partial differential equations}. American Mathematical Society.
	
	\bibitem{shannon1948}
	Shannon, C. E. (1948). A mathematical theory of communication. \textit{Bell System Technical Journal}, 27(3), 379--423.
	
	\bibitem{lenstra1993}
	Lenstra, A. K., \& Lenstra Jr, H. W. (Eds.). (1993). \textit{The development of the number field sieve}. Springer-Verlag.
	
	\bibitem{nielsen_chuang2010}
	Nielsen, M. A., \& Chuang, I. L. (2010). \textit{Quantum computation and quantum information}. Cambridge University Press.
	
	\bibitem{riemannian_geometry}
	Lee, J. M. (2018). \textit{Introduction to Riemannian manifolds}. Springer.
	
	\bibitem{variational_calculus}
	Kot, M. (2014). \textit{A first course in the calculus of variations}. American Mathematical Society.
	
	\bibitem{pde_stability}
	Strikwerda, J. C. (2004). \textit{Finite difference schemes and partial differential equations}. SIAM.
	
	\bibitem{computational_complexity}
	Sipser, M. (2012). \textit{Introduction to the theory of computation}. Cengage Learning.
	
	\bibitem{information_theory}
	Cover, T. M., \& Thomas, J. A. (2012). \textit{Elements of information theory}. John Wiley \& Sons.
	
	\bibitem{Jackson1999}
	Jackson, J. D. (1999). \textit{Classical Electrodynamics} (3rd ed.). John Wiley \& Sons.
	
	\bibitem{Feynman1985}
	Feynman, R. P. (1985). \textit{QED: The Strange Theory of Light and Matter}. Princeton University Press.
	
	\bibitem{Weinberg1995}
	Weinberg, S. (1995). \textit{The Quantum Theory of Fields, Volume 1: Foundations}. Cambridge University Press.
	
	\bibitem{Planck1906}
	Planck, M. (1906). Vorlesungen über die Theorie der Wärmestrahlung. Leipzig: J.A. Barth.
	
	\bibitem{Maxwell1865}
	Maxwell, J. C. (1865). A Dynamical Theory of the Electromagnetic Field. \textit{Philosophical Transactions of the Royal Society}, 155, 459-512.
	
	\bibitem{CODATA2018}
	CODATA Task Group on Fundamental Constants (2019). CODATA Recommended Values of the Fundamental Physical Constants: 2018. \textit{Rev. Mod. Phys.}, 91, 025009.
	
	\bibitem{deutsch1985}
	Deutsch, D. (1985). Quantum theory, the Church-Turing principle and the universal quantum computer. \textit{Proceedings of the Royal Society A}, 400(1818), 97--117.
	
	\bibitem{cms2012}
	CMS Collaboration (2012). Observation of a new boson at a mass of 125 GeV with the CMS experiment at the LHC. \textit{Physics Letters B}, 716(1), 30--61.
	
	\bibitem{codata2018}
	Tiesinga, E., et al. (2021). CODATA recommended values of the fundamental physical constants: 2018. \textit{Reviews of Modern Physics}, 93(2), 025010.
	
	\bibitem{kochen_specker1967}
	Kochen, S. and Specker, E. P. (1967). The problem of hidden variables in quantum mechanics. \textit{Journal of Mathematics and Mechanics}, 17(1), 59--87.
	
	\bibitem{clauser_horne1974}
	Clauser, J. F. and Horne, M. A. (1974). Experimental consequences of objective local theories. \textit{Physical Review D}, 10(2), 526--535.
	
	\bibitem{pusey_barrett_rudolph2012}
	Pusey, M. F., Barrett, J., and Rudolph, T. (2012). On the reality of the quantum state. \textit{Nature Physics}, 8(6), 475--478.
	
	\bibitem{hardy1993}
	Hardy, L. (1993). Nonlocality for two particles without inequalities for almost all entangled states. \textit{Physical Review Letters}, 71(11), 1665--1668.
	
	\bibitem{greenberger_horne_zeilinger1989}
	Greenberger, D. M., Horne, M. A., and Zeilinger, A. (1989). Going beyond Bell's theorem. \textit{Bell's Theorem, Quantum Theory and Conceptions of the Universe}, 69--72.
	
	\bibitem{superdeterminism_review}
	Brans, C. H. (1988). Bell's theorem does not eliminate fully causal hidden variables. \textit{International Journal of Theoretical Physics}, 27(2), 219--226.
	
	\bibitem{t_hooft_deterministic}
	't Hooft, G. (2016). \textit{The Cellular Automaton Interpretation of Quantum Mechanics}. Springer.
	
	\bibitem{palmer_superdeterminism}
	Palmer, T. N. (2020). The invariant set postulate: A new geometric framework for the foundations of quantum theory and the role played by gravity. \textit{Proceedings of the Royal Society A}, 476(2243), 20200319.
	
	\bibitem{t0_deterministic_qm}
	T0 Theory Documentation. \textit{Deterministic Quantum Mechanics via T0-Energy Field Formulation}.
	
	\bibitem{t0_lagrangian}
	T0 Theory Documentation. \textit{Simple Lagrangian Revolution: From Standard Model Complexity to T0 Elegance}.
	
	\bibitem{bell_test_loopholes}
	Larsson, J. Å. (2014). Loopholes in Bell inequality tests of local realism. \textit{Journal of Physics A: Mathematical and Theoretical}, 47(42), 424003.
	
	\bibitem{freedom_of_choice}
	Scheidl, T. et al. (2010). Violation of local realism with freedom of choice. \textit{Proceedings of the National Academy of Sciences}, 107(46), 19708--19713.
	
	\bibitem{t0_elimination_mass}
	T0 Model Analysis. \textit{Elimination of Mass as Dimensional Placeholder in the T0 Model: Towards True Parameter-Free Physics}. Internal Document (2025).
	
	\bibitem{t0_beta_derivation}
	T0 Model Analysis. \textit{Field-Theoretic Derivation of the $\beta_T$ Parameter in Natural Units}. Internal Document (2025).
	
	\bibitem{t0_verification_table}
	T0 Model Analysis. \textit{T0 Model Calculation Verification: Scale Ratios vs. CODATA/Experimental Values}. Internal Document (2025).
	
	\bibitem{planck_units}
	Planck, M. (1899). \textit{Über irreversible Strahlungsvorgänge}. Sitzungsberichte der Königlich Preußischen Akademie der Wissenschaften zu Berlin.
	
	\bibitem{natural_units}
	Weinberg, S. (1995). \textit{The Quantum Theory of Fields, Volume I: Foundations}. Cambridge University Press.
	
	\bibitem{si_units}
	Bureau International des Poids et Mesures. (2019). \textit{The International System of Units (SI), 9th edition}. BIPM.
	
	\bibitem{pascher_derivation_2025}
	Pascher, J. (2025). \textit{Field-Theoretic Derivation of the $\beta_T$ Parameter in Natural Units ($\hbar = c = 1$)}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/DerivationVonBetaEn.pdf}
	
	\bibitem{pascher_units_2025}  
	Pascher, J. (2025). \textit{Natural Unit Systems: Universal Energy Conversion and Fundamental Length Scale Hierarchy}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/NatEinheitenSystematikEn.pdf}
	
	\bibitem{pascher_dirac_2025}
	Pascher, J. (2025). \textit{Integration of the Dirac Equation in the T0 Model: Updated Framework with Natural Units}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/diracEn.pdf}
	
	\bibitem{planck_1899}
	Planck, M. (1899). \textit{Über irreversible Strahlungsvorgänge}. Sitzungsberichte der Königlich Preußischen Akademie der Wissenschaften zu Berlin, 5, 440-480.
	
	\bibitem{wheeler_1955}
	Wheeler, J. A. (1955). \textit{Geons}. Physical Review, 97(2), 511-536.
	
	\bibitem{weinberg_1989}
	Weinberg, S. (1989). \textit{The cosmological constant problem}. Reviews of Modern Physics, 61(1), 1-23.
	
	\bibitem{einstein1905}
	Einstein, A. (1905). \textit{Does the inertia of a body depend upon its energy content?} Annalen der Physik, 18, 639--641.
	
	\bibitem{michelson1887}
	Michelson, A. A. and Morley, E. W. (1887). \textit{On the relative motion of the Earth and the luminiferous ether}. American Journal of Science, 34, 333--345.
	
	\bibitem{pascher_derivation_beta_2025}
	Pascher, J. (2025). \textit{Field-Theoretic Derivation of the $\beta_T$ Parameter in Natural Units}. T0 Model Documentation.
	
	\bibitem{pascher_ratio_physics_2025}
	Pascher, J. (2025). \textit{Pure Energy T0 Theory: The Ratio-Based Revolution}. T0 Model Documentation.
	
	\bibitem{lorentz1904}
	Lorentz, H. A. (1904). \textit{Electromagnetic phenomena in a system moving with any velocity smaller than that of light}. Proceedings of the Royal Netherlands Academy of Arts and Sciences, 6, 809--831.
	
	\bibitem{weinberg1972}
	Weinberg, S. (1972). \textit{Gravitation and Cosmology}. John Wiley \& Sons.
	
	\bibitem{pascher_h0_energy_2025}
	Pascher, J. (2025). \textit{Pure Energy Formulation of $H_0$ and $\kappa$ Parameters in the T0 Model Framework}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Ho_EnergieEn.pdf}
	
	\bibitem{pascher_elimination_mass_2025}
	Pascher, J. (2025). \textit{Elimination of Mass as Dimensional Placeholder in the T0 Model: Towards True Parameter-Free Physics}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/EliminationOfMassEn.pdf}
	
	\bibitem{pascher_mol_candela_2025}
	Pascher, J. (2025). \textit{T0 Model: Universal Energy Relations for Mol and Candela Units - Complete Derivation from Energy Scaling Principles}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Moll_CandelaEn.pdf}
	
	\bibitem{pascher_lagrangian_comparison_2025}
	Pascher, J. (2025). \textit{Simple Lagrangian Revolution: From Standard Model Complexity to T0 Elegance}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/LagrandianVergleichEn.pdf}
	
	\bibitem{pascher_verification_table_2025}
	Pascher, J. (2025). \textit{T0 Model Verification: Scale Ratio-Based Calculations vs. CODATA/Experimental Values}. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Elimination_Of_Mass_Dirac_TabelleEn.pdf}
	
	\bibitem{dirac_original_1928}
	Dirac, P. A. M. (1928). \textit{The Quantum Theory of the Electron}. Proc. R. Soc. London A \textbf{117}, 610.
	
	\bibitem{muong2_experiment_2021}
	Muon g-2 Collaboration (2021). \textit{Measurement of the Positive Muon Anomalous Magnetic Moment to 0.46 ppm}. Phys. Rev. Lett. \textbf{126}, 141801.
	
	\bibitem{higgs_mechanism_1964}
	Higgs, P. W. (1964). \textit{Broken Symmetries and the Masses of Gauge Bosons}. Phys. Rev. Lett. \textbf{13}, 508--509.
	
	\bibitem{weinberg_qft_1995}
	Weinberg, S. (1995). \textit{The Quantum Theory of Fields, Volume 1: Foundations}. Cambridge University Press.
	
	\bibitem{schrodinger1926}
	Schrodinger, E. (1926). Quantisation as a Problem of Proper Values. \textit{Annalen der Physik}, 79, 361--376.
	
	\bibitem{dirac1928}
	Dirac, P.A.M. (1928). The Quantum Theory of the Electron. \textit{Proceedings of the Royal Society A}, 117, 610--624.
	
	\bibitem{grover1996}
	Grover, L.K. (1996). A fast quantum mechanical algorithm for database search. \textit{Proceedings of the 28th Annual ACM Symposium on Theory of Computing}, 212--219.
	
	\bibitem{einstein_mass_energy_1905}
	Einstein, A. (1905). \textit{Ist die Trägheit eines Körpers von seinem Energieinhalt abhängig?} Ann. Phys. \textbf{17}, 639--641.
	
	\bibitem{t0sicomplete}
	Pascher, J. (2025). \textit{The Complete Closure of T0-Theory: From $\xi$ to the SI Reform 2019}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_SI_En.pdf}
	
	\bibitem{t0grundlagen}
	Pascher, J. (2025). \textit{T0 Grundlagen / T0 Foundations}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Grundlagen_en.pdf}
	
	\bibitem{hdokument}
	Pascher, J. (2025). \textit{H-Dokument: Complete T0 Framework Master Document}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/HdokumentEn.pdf}
	
	\bibitem{t0energie}
	Pascher, J. (2025). \textit{T0-Energie: Comprehensive Energy-Based Formulation}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0-Energie_En.pdf}
	
	\bibitem{system}
	Pascher, J. (2025). \textit{System: Complete T0 System Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/systemEn.pdf}
	
	\bibitem{zusammenfassung}
	Pascher, J. (2025). \textit{Zusammenfassung / Summary: Comprehensive Overview Document}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Zusammenfassung_En.pdf}
	
	\bibitem{t0ratiovsabsolute}
	Pascher, J. (2025). \textit{T0 Ratio vs. Absolute: The Role of Fractal Correction in T0 Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_verhaeltnis-absolut_En.pdf}
	
	\bibitem{t0unifiedreport}
	Pascher, J. (2025). \textit{T0 Unified Report: Calculator Results for Masses and Constants}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_unified_report.pdf}
	
	\bibitem{mathzeitmasse}
	Pascher, J. (2025). \textit{Mathematical Foundations of Time-Mass Duality with Lagrangian Formalism}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/MathZeitMasseLagrangeEn.pdf}
	
	\bibitem{mathstruktur}
	Pascher, J. (2025). \textit{Mathematische Struktur / Mathematical Structure Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Mathematische_struktur_En.pdf}
	
	\bibitem{eliminationmass}
	Pascher, J. (2025). \textit{Elimination of Mass: Mathematical Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/EliminationOfMassEn.pdf}
	
	\bibitem{eliminationdiractabelle}
	Pascher, J. (2025). \textit{Elimination of Mass in Dirac Equation: Tables}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Elimination_Of_Mass_Dirac_TabelleEn.pdf}
	
	\bibitem{eliminationdiraclag}
	Pascher, J. (2025). \textit{Elimination of Mass in Dirac Lagrangian}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Elimination_Of_Mass_Dirac_LagEn.pdf}
	
	\bibitem{lagrandianvergleich}
	Pascher, J. (2025). \textit{Lagrangian Comparison: From Complexity to Elegance}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/LagrandianVergleichEn.pdf}
	
	\bibitem{lagrandianeinfach}
	Pascher, J. (2025). \textit{Simplified Lagrangian Density in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/lagrandian-einfachEn.pdf}
	
	\bibitem{notwendigkeitzweilagrange}
	Pascher, J. (2025). \textit{Necessity of Two Lagrangians in T0 Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Notwendigkeit_zwei_lagrange_En.pdf}
	
	\bibitem{formelnenergie}
	Pascher, J. (2025). \textit{Complete Energy-Based Formula Collection}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Formeln_Energiebasiert_En.pdf}
	
	\bibitem{dirac}
	Pascher, J. (2025). \textit{Dirac Equation in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/diracEn.pdf}
	
	\bibitem{diracvereinfacht}
	Pascher, J. (2025). \textit{Simplified Dirac: From Matrices to Fields}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/diracVereinfachtEn.pdf}
	
	\bibitem{t0feinstruktur}
	Pascher, J. (2025). \textit{T0 Fine Structure: Mathematical Derivation of the Fine Structure Constant}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Feinstruktur_En.pdf}
	
	\bibitem{e137}
	Pascher, J. (2025). \textit{Comprehensive Analysis of the Number 137}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/137_En.pdf}
	
	\bibitem{feinstrukturkonstante}
	Pascher, J. (2025). \textit{Extended Fine Structure Constant Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/FeinstrukturkonstanteEn.pdf}
	
	\bibitem{musicalspiral}
	Pascher, J. (2025). \textit{Musical Spiral and the Number 137}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/musical-spiral-137-En.pdf}
	
	\bibitem{t0teilchenmassen}
	Pascher, J. (2025). \textit{T0 Particle Masses: Systematic Mass Calculation of All Fermions}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Teilchenmassen_En.pdf}
	
	\bibitem{teilchenmassen}
	Pascher, J. (2025). \textit{Comprehensive Particle Mass Calculations}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/teilchenmmassen_En.pdf}
	
	\bibitem{xiparameter}
	Pascher, J. (2025). \textit{Xi Parameter and Particle Physics}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/xi_parmater_partikel_En.pdf}
	
	\bibitem{t0neutrinos}
	Pascher, J. (2025). \textit{T0 Neutrinos: Special Treatment of Neutrino Physics}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Neutrinos_En.pdf}
	
	\bibitem{neutrinoformel}
	Pascher, J. (2025). \textit{Neutrino Formula Developments}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/neutrino-Formel_En.pdf}
	
	\bibitem{t0anomale}
	Pascher, J. (2025). \textit{T0 Anomalous Magnetic Moments: Solution to Muon g-2 Anomaly}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Anomale_Magnetische_Momente_En.pdf}
	
	\bibitem{muong2complete}
	Pascher, J. (2025). \textit{Complete Muon g-2 Analysis: $0.05\sigma$ Agreement with Experiment}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/CompleteMuon_g-2_AnalysisEn.pdf}
	
	\bibitem{muong2fractal}
	Pascher, J. (2025). \textit{Fractal Approach to Muon g-2 Anomaly}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/CompleteMuon_g-2_fraktal_En.pdf}
	
	\bibitem{detailierteleptonen}
	Pascher, J. (2025). \textit{Detailed Formulas for Lepton Anomalies}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/detailierte_formel_leptonen_anemal_En.pdf}
	
	\bibitem{bellmuon}
	Pascher, J. (2025). \textit{Bell Tests and Muon Anomaly Connection}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/bell-myon.pdf}
	
	\bibitem{t0gravitationskonstante}
	Pascher, J. (2025). \textit{T0 Gravitational Constant: Detailed Gravitational Calculations}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Gravitationskonstante_En.pdf}
	
	\bibitem{gravitationskonstante}
	Pascher, J. (2025). \textit{Geometric Determination of Gravitational Constant}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/gravitationskonstante_En.pdf}
	
	\bibitem{t0kosmologie}
	Pascher, J. (2025). \textit{T0 Cosmology: Cosmological Applications of T0 Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_Kosmologie_En.pdf}
	
	\bibitem{cosmic}
	Pascher, J. (2025). \textit{Cosmic: Extended Cosmological Applications}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/cosmic_En.pdf}
	
	\bibitem{hubble}
	Pascher, J. (2025). \textit{Hubble Constant Analysis in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Ho_En.pdf}
	
	\bibitem{tempcmb}
	Pascher, J. (2025). \textit{CMB in Static $\xi$-Universe: Temperature Units}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/TempEinheitenCMBEn.pdf}
	
	\bibitem{redshift}
	Pascher, J. (2025). \textit{Wavelength-Dependent Redshift and Deflection}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/redshift_deflection_En.pdf}
	
	\bibitem{instantan}
	Pascher, J. (2025). \textit{Apparently Instantaneous Effects in T0 Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/scheinbar_instantan_En.pdf}
	
	\bibitem{t0qmqftrt}
	Pascher, J. (2025). \textit{T0 QM-QFT-RT: Complete Quantum Field Theory in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_QM-QFT-RT_En.pdf}
	
	\bibitem{qft}
	Pascher, J. (2025). \textit{Quantum Field Theory in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QFT_En.pdf}
	
	\bibitem{qmdeterministic}
	Pascher, J. (2025). \textit{Deterministic Quantum Mechanics in T0}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QM-DetrmisticEn.pdf}
	
	\bibitem{qmdeterministicp}
	Pascher, J. (2025). \textit{Deterministic vs Probabilistic Quantum Mechanics}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QM-Detrmistic_p_En.pdf}
	
	\bibitem{qmtesten}
	Pascher, J. (2025). \textit{Testing Quantum Mechanics in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/QM-testenEn.pdf}
	
	\bibitem{dynmassephotonen}
	Pascher, J. (2025). \textit{Dynamic Mass and Non-Local Photons}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/DynMassePhotonenNichtlokalEn.pdf}
	
	\bibitem{derivationbeta}
	Pascher, J. (2025). \textit{Derivation of Beta Parameter from Field Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/DerivationVonBetaEn.pdf}
	
	\bibitem{parameterherleitung}
	Pascher, J. (2025). \textit{Parameter Derivation Methods}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/parameterherleitung_En.pdf}
	
	\bibitem{resolving_alfa}
	Pascher, J. (2025). \textit{Resolving the Constants: $\alpha = 1$}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/ResolvingTheConstantsAlfaEn.pdf}
	
	\bibitem{relzahlensystem}
	Pascher, J. (2025). \textit{Relative Number System in T0}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/RelokativesZahlensystemEn.pdf}
	
	\bibitem{nateinheiten}
	Pascher, J. (2025). \textit{Natural Units Systematics}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/NatEinheitenSystematikEn.pdf}
	
	\bibitem{parametersystem}
	Pascher, J. (2025). \textit{Parameter System Dependencies}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/ParameterSystemdipendentEn.pdf}
	
	\bibitem{mollcandela}
	Pascher, J. (2025). \textit{Mol and Candela Units in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Moll_CandelaEn.pdf}
	
	\bibitem{zeit}
	Pascher, J. (2025). \textit{Time Analysis in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Zeit_En.pdf}
	
	\bibitem{zeitkonstant}
	Pascher, J. (2025). \textit{Time Constant Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Zeit-konstant_En.pdf}
	
	\bibitem{bewegungsenergie}
	Pascher, J. (2025). \textit{Kinetic Energy in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Bewegungsenergie_En.pdf}
	
	\bibitem{emc2}
	Pascher, J. (2025). \textit{E=mc²: Reinterpretation in T0 Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/E-mc2_En.pdf}
	
	\bibitem{amperlow}
	Pascher, J. (2025). \textit{Low Energy Ampere Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/Amper_Low_En.pdf}
	
	\bibitem{t0threeclocken}
	Pascher, J. (2025). \textit{Single-Clock Metrology and Three-Clock Experiment in the T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_threeclock_En.pdf}
	
	\bibitem{t0vsesm}
	Pascher, J. (2025). \textit{T0 vs Extended Standard Model: Conceptual Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0vsESM_ConceptualAnalysis_En.pdf}
	
	\bibitem{hierarchie}
	Pascher, J. (2025). \textit{Hierarchy Problem Solutions in T0}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/hirachie_En.pdf}
	
	\bibitem{nogo}
	Pascher, J. (2025). \textit{No-Go Theorems Analysis}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/NoGoEn.pdf}
	
	\bibitem{t0netze}
	Pascher, J. (2025). \textit{T0 Network Theory}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/T0_netze_En.pdf}
	
	\bibitem{rsa}
	Pascher, J. (2025). \textit{RSA Analysis in T0 Framework}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/RSA_En.pdf}
	
	\bibitem{rsatest}
	Pascher, J. (2025). \textit{RSA Testing Procedures}. HTL Leonding, Austria. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/RSAtest_En.pdf}
	
	\bibitem{t0repository}
	Pascher, J. (2025). \textit{T0-Time-Mass-Duality: Complete Framework Repository}. GitHub Repository. 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality}
	
	\bibitem{t0website}
	Pascher, J. (2025). \textit{Interactive T0 Framework Exploration}. Interactive Website. 
	\url{https://jpascher.github.io/T0-Time-Mass-Duality/}
	
	\bibitem{chipx}
	CHIPX-Touring Quantum, ''Scalable Photonic Quantum Chip,'' World Internet Conference 2025.
	
	\bibitem{t0qm}
	J. Pascher, ''Geometrischer Formalismus der T0-Quantenmechanik,'' T0-Repo v1.0 (2025). 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/raw/main/2/pdf/T0_QM-optimierung_De.pdf}.
	
	\bibitem{t0qat}
	J. Pascher, ''T0-QAT: $\xi$-Aware Quantization,'' T0-Repo v1.0 (2025). 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/raw/main/2/pdf/T0_QAT_De.pdf}.
	
	\bibitem{koide}
	J. Pascher, ''Koide-Formel in T0,'' T0-Repo v1.0 (2025). 
	\url{https://github.com/jpascher/T0-Time-Mass-Duality/raw/main/2/pdf/T0_koideformel_De.pdf}.
	
	\bibitem{quantenjahr25}
	Leichsenring, H. (2025). Steht die Quantentechnologie 2025 am Wendepunkt. Der Bank Blog; DPG (2025). 2025 – Das Jahr der Quantentechnologien. LP.PRO - Technologieforum Laser Photonik.
	
	\bibitem{qant_nps}
	Q.ANT (2025). Photonic Computing für effiziente KI und HPC. Pressemitteilungen Q.ANT.
	
	\bibitem{tfln_foundry}
	TraderFox (2024). Quantencomputing 2025: Die Revolution steht kurz bevor. Markets.
	
	\bibitem{phoquant}
	Fraunhofer IOF (2025). Quantencomputer mit Photonen (PhoQuant). PRESSEINFORMATION.
	
	\bibitem{flexible_wafer}
	Mechanically-flexible wafer-scale integrated-photonics fabrication. Nature Scientific Reports, 2024. 
	\url{https://www.nature.com/articles/s41598-024-61055-w}.
	
	\bibitem{lithium_tantalate}
	Lithium tantalate photonic integrated circuits for volume manufacturing. Nature, 2024. 
	\url{https://www.nature.com/articles/s41586-024-07369-1}.
	
	\bibitem{fabrication_heterogeneous}
	Fabrication of heterogeneous LNOI photonics wafers. ScienceDirect, 2023. 
	\url{https://www.sciencedirect.com/science/article/abs/pii/S0169433223003422}.
	
	\bibitem{on_chip_lithium}
	Fabrication of on-chip single-crystal lithium niobate waveguide. ScienceDirect, 2025. 
	\url{https://www.sciencedirect.com/science/article/abs/pii/S0030399224016062}.
	
	\bibitem{integration_microelectronic}
	The integration of microelectronic and photonic circuits on a single wafer. ScienceDirect, 2024. 
	\url{https://www.sciencedirect.com/science/article/pii/S2589965124000540}.
	
	\bibitem{6g_roadmap}
	European Commission (2025). 6G Networks in Europe. Shaping Europe's Digital Future.
	
	\bibitem{thz_epfl}
	Benea-Chelmus, C. et al. (2025). 6G Mobile Communications Are Getting Closer – Revolutionary Chip Enables Optical and Electronic Data Processing. Leadersnet; Nature Communications (Publication).
	
	\bibitem{hhi_6g}
	Fraunhofer HHI (2025). Berlin 6G Conference 2025; Fraunhofer HHI (2025). Photonics West 2025.
	
	\bibitem{analog_optical}
	Analog optical computing: principles, progress, and prospects. ScienceDirect, 2025. 
	\url{https://www.sciencedirect.com/science/article/abs/pii/S0030399225018110}.
	
	\bibitem{recurrent_photonics}
	Integrated photonic recurrent processors. SPIE, 2025. 
	\url{https://www.spiedigitallibrary.org/journals/advanced-photonics/volume-7/issue-5/054003/Integrated-photonic-recurrent-processors/10.1117/1.AP.7.5.054003.full}.
	
	\bibitem{photonics_ai}
	Photonics for sustainable AI. Nature, 2025. 
	\url{https://www.nature.com/articles/s42005-025-02300-0}.
	
	\bibitem{differential_optical}
	All-optical analog differential operation... De Gruyter, 2025. 
	\url{https://www.degruyter.com/document/doi/10.1515/nanoph-2024-0540/html}.
	
	\bibitem{optical_advantages}
	Harnessing optical advantages in computing: a review. Frontiers, 2024. 
	\url{https://www.frontiersin.org/journals/physics/articles/10.3389/fphy.2024.1379051/full}.
	
	\bibitem{rf_photonics}
	RF Signal Filtering. (Placeholder reference for the table entry).
	
\end{thebibliography}

\end{document}