This book tells a story. It is the story of an idea that begins with a simple question: \emph{What happens when you follow the conventions of physics to their logical conclusion?}

In May 2019, the international community of metrologists took a historic step. They redefined the base units of the International System of Units~(SI) --- no longer through physical artefacts like the prototype kilogram in a Parisian vault, but through fundamental constants of nature. The speed of light~$c$, the Planck constant~$\hbar$, the elementary charge~$e$, and the Boltzmann constant~$k_B$ were fixed to exact values. Nature itself became the standard.

This step was revolutionary --- and yet not revolutionary enough. The reform set a direction without following it to its logical end. If we choose natural constants as our standard, why not \emph{all} of them? Why not the fine-structure constant~$\alpha$ as well?

The answer this book develops is astonishing: Setting $\alpha = 1$ --- a convention historically anticipated by George Johnstone Stoney~(1874) and the Heaviside-Lorentz system --- unfolds from this single choice a complete picture of physics. Not as speculative theory, but as geometric necessity.

From $\alpha = 1$ follows a single geometric parameter: $\xi = \tfrac{4}{3} \times 10^{-4}$. From $\xi$ follow the masses of all elementary particles, the gravitational constant, the Planck length, the structure of spacetime. A single measured value --- the fine-structure constant~$\alpha \approx 1/137.036$ --- suffices to reconstruct the entire edifice of physics.

That sounds too good to be true. This book shows, step by step, why it works nonetheless.

The path leads from the SI reform through time-mass duality~($T \cdot m = 1$) to the Adapted Dynamic Vacuum Field Theory~(FFGFT/DVFT), in which the universe appears as a four-dimensional torsion crystal --- infinite, bounded, and free of singularities. It leads through fractal corrections and brain-fold topologies to experimental predictions testable with current technology. And it leads finally to philosophical questions: about determinism and consciousness, about the limits of mathematics and the nature of reality.

The book is intended for all who are willing to question familiar assumptions. It presupposes a basic understanding of physical concepts but strives for a narrative style that makes the line of reasoning accessible. The mathematical details can be found in the individual technical documents listed in the appendix (Chapter~\ref{ch:dokverz}) and freely available on GitHub.

\begin{flushright}
\textit{Johann Pascher}\\
\textit{Linz, February 2026}
\end{flushright}
