\epigraph{If you know exactly one number, you know them all.}{}

This chapter traces the path by which the entire edifice of physics is reconstructed from the single measured value~$\alpha$. It is a cascade of derivations in which each step follows necessarily from the one before.

\section{Step 1: From $\alpha$ to $\xsi$}


\begin{figure}[ht]
\centering
\begin{tikzpicture}[
  box/.style={draw, rounded corners=3pt, minimum width=4.5cm, minimum height=0.7cm,
              text centered, fill=#1, font=\small},
  arr/.style={-{Stealth[length=2.5mm]}, thick, blue!50!black}
]
\node[box=orange!15] (alpha) at (0,0) {$\alpha \approx 1/137.036$};
\node[box=yellow!15] (xi) at (0,-1.3) {$\xi = 4/30000$};
\node[box=green!10] (masses) at (-3,-2.6) {Particle masses};
\node[box=green!10] (G) at (3,-2.6) {$G$, Planck length};
\node[box=blue!10] (torus) at (-3,-3.9) {Torus geometry};
\node[box=blue!10] (Kfrak) at (3,-3.9) {$K_{\text{frak}} = 0.9867$};
\node[box=red!8] (cosmo) at (0,-5.2) {Cosmology, CMB, $T \cdot m = 1$};
\draw[arr] (alpha) -- (xi);
\draw[arr] (xi) -- (masses);
\draw[arr] (xi) -- (G);
\draw[arr] (xi) -- (torus);
\draw[arr] (xi) -- (Kfrak);
\draw[arr] (masses) -- (cosmo);
\draw[arr] (G) -- (cosmo);
\draw[arr] (torus) -- (cosmo);
\draw[arr] (Kfrak) -- (cosmo);
\node[font=\footnotesize\itshape, text=orange!70!black] at (3.5,0) {sole measurement};
\node[font=\footnotesize\itshape, text=red!60!black] at (3.5,-5.2) {everything follows};
\end{tikzpicture}
\caption{The derivation cascade: from the single measured value $\alpha$, via $\xi$, the entire edifice of physics follows --- particle masses, gravitational constant, torus geometry, fractal corrections, and cosmology.}
\label{fig:ableitungskette}
\end{figure}
The fine-structure constant~$\alpha \approx 1/137.036$ is the sole empirical input. In the T0 theory it stands in a precise relation to the geometric parameter~$\xsi$:
\begin{equation}
\alpha = \xsi \cdot \left(\frac{E_0}{1\,\text{MeV}}\right)^2
\end{equation}
where $E_0 = \sqrt{m_e \cdot m_\mu}$ is the characteristic energy scale of the lepton masses. Inverting yields:
\begin{equation}
\xsi = \frac{\alpha}{(E_0/1\,\text{MeV})^2} = \frac{4}{3} \times 10^{-4} = \frac{4}{30000}
\end{equation}

The value $4/30000$ is no coincidence. It has a direct geometric interpretation: $30000/4 = 7500$ is the winding number of the fundamental torus, and $f = 7500 = 2^2 \times 3 \times 5^4$ possesses, with its~36 divisors, an ideal symmetry structure for resonances.

\section{Step 2: From $\xsi$ to the Particle Masses}

The masses of the elementary particles are not free parameters --- they are $\xsi$-quantisations. The three lepton masses follow from:
\begin{align}
m_e &\propto \xsi^{n_e} \cdot f^{k_e} \\
m_\mu &\propto \xsi^{n_\mu} \cdot f^{k_\mu} \\
m_\tau &\propto \xsi^{n_\tau} \cdot f^{k_\tau}
\end{align}
with integer exponents $n_i$ and $k_i$ determined by the resonance structure of the torus. The three generations (electron, muon, tau) correspond to three different resonance modes of the same geometric object.

The result: all lepton masses, all quark masses, the three neutrino masses --- $m_{\nu_e} \approx 9.1$~meV, $m_{\nu_\mu} \approx 1.9$~meV, $m_{\nu_\tau} \approx 18.0$~meV, each determined by a characteristic \emph{double-$\xsi$ suppression} with generation-specific quantum numbers ---, the Higgs VEV ($v \approx 246.7$~GeV with $0.2\%$ accuracy), and the masses of the $W$ and $Z$ bosons all follow from $\xsi$ and the torsion geometry.

Remarkably, the Koide formula --- an empirical relation between the three lepton masses that had been regarded as an unexplained mystery for decades --- emerges as a mathematical consequence of~$\xsi$. The key lies in the exponent structure $p = 3/2,\; 1,\; 2/3$: the step size between generations is $\Delta p = 1/3 = 1/D$ --- the inverse spatial dimension. The same $1/3$ step size reappears in the $g$-$2$ anomaly hierarchy, establishing a direct bridge between the mass spectrum and anomalous magnetic moments (cf.\ \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/158_T0_Koide-zu-g2-1_En.pdf}{Doc.~158}).

\section{Step 3: From $\xsi$ to Gravitation}

The gravitational constant is not a fundamental quantity in the T0 theory. It is derivable:
\begin{equation}
G = \frac{\xsi^2}{4\,\mchar} \times C_{\text{conv}} \times \Kfrak
\end{equation}
where $\mchar = m_e$ is the characteristic mass, $C_{\text{conv}}$ the unit conversion factor, and $\Kfrak \approx 0.9867$ the fractal correction factor.

The famous ``weakness'' of gravity --- the fact that $G \approx 10^{-11}$ in SI units is tiny --- thus has a simple explanation: $G$ scales as $\xsi^2 \approx 10^{-8}$, and $\xsi$ itself is small because spacetime is almost perfectly three-dimensional.

\section{Step 4: The Planck Scale}

The Planck length follows from~$\xsi$ and the electron mass. In natural units ($c = \hbar = 1$), where mass has dimension $[\text{length}]^{-1}$:
\begin{equation}
\lP = \frac{\xsi}{2\sqrt{m_e}} \qquad \text{(in natural units)}
\end{equation}

In SI units this becomes $\lP = \xsi\hbar/(2c\sqrt{m_e})$, reproducing the experimental value $\lP \approx 1.616 \times 10^{-35}$~m.

Below this lies the sub-Planck scale $L_0 = \xsi \cdot \lP$, at which the discrete crystal structure of spacetime becomes visible. The fact that $\lP$ calculated from $\xsi$ agrees exactly with $\lP$ calculated from the measured~$G$ is no coincidence --- both describe the same geometric reality.

\section{Circularity-Freeness of the Derivation}

A critical point: is this derivation chain circular? No. The logical flow is strictly unidirectional:
\begin{enumerate}
\item \textbf{Sole input:} $\alpha$ (or equivalently: the mass ratio $m_e/m_\mu$)
\item \textbf{Geometric derivation:} $\alpha \to \xsi \to$ all masses $\to G \to \lP \to c$
\item \textbf{Verification:} the derived values agree with experimental ones
\end{enumerate}

The SI constants ($c$, $\hbar$, $e$, $k_B$, $G$) are, in this picture, not independent quantities. They are different windows onto \emph{one} geometric reality. The circularity often attributed to the SI system --- that constants are defined through other constants --- dissolves because there is only \emph{one} fundamental parameter.

\begin{kerngedanke}
The entire derivation chain is not speculation but a mathematical cascade: each step is connected by equations that are verifiable. The sole empirical input is $\alpha$. Everything else is geometry and algebra.
\end{kerngedanke}
