\epigraph{Mass is not the opposite of lightness. Mass is the opposite of time.}{}

\section{The Core Axiom}


\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=0.9]
  \draw[->] (0,0) -- (5.5,0) node[right] {$m$};
  \draw[->] (0,0) -- (0,5.5) node[above] {$T$};
  \draw[very thick, blue!70!black, domain=0.25:5, samples=100]
    plot (\x, {1/\x});
  \node[blue!70!black, font=\large] at (3.8,1.8) {$T \cdot m = 1$};
  \fill[red!70!black] (0.5,2) circle (3pt) node[right, font=\small] {~Neutron: high $m$, slow $T$};
  \fill[green!60!black] (2,0.5) circle (3pt) node[above right, font=\small] {Neutrino: low $m$, fast $T$};
  \fill[orange!80!black] (1,1) circle (3pt) node[above right, font=\small] {$m=T=1$ (Planck unit)};
  \draw[<->, thick, red!50!black, dashed] (0.5,2) -- (2,0.5)
    node[midway, above right, font=\footnotesize\itshape] {duality};
\end{tikzpicture}
\caption{Time-mass duality $T \cdot m = 1$ as a hyperbola: every particle sits on the same curve. Heavy particles have slow internal time, light particles fast.}
\label{fig:tm_duality}
\end{figure}
At the heart of the T0 theory stands an equation of compelling simplicity:
\begin{equation}
\Tfield \cdot \mfield = 1
\label{eq:tm_duality}
\end{equation}

Time and mass are not independent. They are \emph{dual} to each other --- two perspectives on the same physical reality. Where the mass is higher, local time passes more slowly. Where less mass is present, clocks tick faster. Not as an effect, not as a consequence of some theory --- but as the \emph{definition} of what time and mass actually are.

\section{Why This Is Not a Postulate}

One might object: ``That is just an axiom you have chosen.'' But equation~(\ref{eq:tm_duality}) \emph{follows} from the ratio-based system. If we work in a framework where:
\begin{itemize}
\item $\alpha = 1$ (electromagnetic coupling normalised),
\item all ratios are defined relatively,
\item energy is the sole fundamental field (cf.\ Chapter~\ref{ch:ffgft}),
\end{itemize}
then there is no room for an independent time definition. Time \emph{must} be inverse to mass, because both are expressions of the same underlying energy dynamics.

\section{What the Duality Means}

The consequences are far-reaching:

\subsection{Time Dilation Becomes Geometric}

In general relativity, time dilation is an effect of spacetime curvature. In T0 it is something simpler: where there is more mass, time is \emph{by definition} slower. Gravitational redshift, GPS corrections, the Hafele-Keating experiments --- all follow directly from $T \cdot m = 1$, without the detour through the metric of a curved space.

\subsection{Mass Becomes Dynamic}

In standard physics the mass of a particle is a constant --- a parameter ``given'' to the particle, for instance by the Higgs mechanism. In T0, mass is a local field: $\mfield = 1/\Tfield$. It can vary, fluctuate, evolve. The Higgs field in this picture is not a separate mechanism (cf.\ \href{https://github.com/jpascher/T0-Time-Mass-Duality/blob/main/2/pdf/052_EliminationOfMass_De.pdf}{Doc.~052}, 053) but a description of the mass distribution in the vacuum field.

\subsection{The Three Perspectives}

The duality can be read in three equivalent ways:
\begin{align}
\text{Everything is } &\textbf{Energy:} \quad E \text{ as the fundamental field} \\
\text{Everything is } &\textbf{Mass:} \quad m = E/c^2 = 1/T \\
\text{Everything is } &\textbf{Time:} \quad T = 1/m
\end{align}

None of these perspectives is ``more correct'' than the others. If one chooses energy as the foundation, mass and time are derived shadows. If one chooses time, mass and energy become frequencies. If one chooses mass, time and energy are reciprocals and products.

This is not a weakness of the theory --- it is its strength. There is no privileged foundation. The duality $T \cdot m = 1$ says: both sides are on equal footing.

\begin{kerngedanke}
Time-mass duality is not a hypothesis to be believed or rejected. It is the logical consequence of a system that sets all constants to one and works solely with ratios. In such a system \emph{there is no other possibility} than that time and mass are inverse to each other.
\end{kerngedanke}
