\documentclass[11pt,a4paper]{article}
\input{T0_preamble_local_En.tex}

\title{\textbf{Triangle--Matrix Reduction Theorem}\\
\large A geometric bridge structure between FFGFT and related formulations\\[2mm]
\normalsize Document 206 of the \emph{Fundamental Fractal Geometric Field Theory} series}
\author{Johann Pascher\\
\small Independent Researcher, Upper Austria, Austria\\[1mm]
\small ORCID: \href{https://orcid.org/0009-0000-6518-4064}{0009-0000-6518-4064}\\
\small \href{mailto:johann.pascher@gmail.com}{johann.pascher@gmail.com}}
\date{8 May 2026}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We formulate and prove the \emph{Triangle--Matrix Reduction Theorem}: every consistent geometric description of physical structures that falls into the same scale regime as FFGFT can be mapped onto two equivalent representations --- a Z\textsubscript{3} triangle connection and a 3\,$\times$\,3 matrix algebra. The bridge relation between these representations is \(\det(A) = 1 - \xi\), from which the fractal dimension \(D_f = 3 - \xi\) follows as a spectral quantity in linear order.

We test the theorem against six concrete bridges to formulations by other researchers: Austin (\(D = 3 + \varepsilon\)), Tekermen (UIFT openness), Phillips (Self-Dual C-25), Porter (\(\Lambda\)-linear), Chekanov-Hakan (trigonometric spectra), and Moseley (ITR \(\nu_M\)). Five bridges confirm the theorem algebraically or structurally; one (Moseley) reveals a regime separation that is not a contradiction but a clarification of the domains of validity.

We explicitly check against the temptation of numerology: an apparent fit for \(\Omega_\Lambda = 0.6889\) is identified by a filter test as non-theoretical and is not booked as a proof. We add a methodological section on the circularity of cosmological reference data --- \(\Omega_\Lambda\) is determined within the \(\Lambda\)CDM framework (dark matter, standard inflation, FRW expansion) and is not a model-independent observable.

The honest balance: The reduction theorem is robust for intrinsic theory quantities. Cosmological observables such as \(\Omega_\Lambda\) require an FFGFT-native evaluation pipeline applied to raw data before a direct quantitative comparison becomes meaningful.

All proofs are reproducibly executed in thirteen attached Python scripts.
\end{abstract}

\tableofcontents

\clearpage
\input{dok206_dreieck_matrix_reduktion_En_ch.tex}

\end{document}
