\documentclass[11pt,a4paper]{article}
\input{T0_preamble_local_En}
\hfuzz=8pt\tolerance=5000\emergencystretch=3em
\title{Algebraic Bridges to the Consciousness Discussion\\
\large Connection to Documents 100 and 170}
\author{Johann Pascher\\
\small Independent Researcher, Upper Austria, Austria\\
\small ORCID: \href{https://orcid.org/0009-0000-6518-4064}{0009-0000-6518-4064}\\
\small \href{mailto:johann.pascher@gmail.com}{johann.pascher@gmail.com}}
\date{8 May 2026}
\begin{document}
\maketitle
\begin{abstract}
\noindent
Document 206 (\emph{Triangle--Matrix Reduction Theorem}) provides an algebraic structure that grounds the existing consciousness discussion in the FFGFT series geometrically, without extending it in content. The phenomenological line is already drawn in Document~100 (\emph{Consciousness as fractal incoherence}, connecting to the no-go theorem of Adlam, McQueen and Waegell, 2025) and in Document~170 (\emph{Consciousness as a topologically forced threshold ladder}).

We show three structural bridges: (A) Tekermen's \emph{constitutive openness} is algebraically identical to the non-closure theorem (Doc~193) and corresponds to the condition $\xi > 0$; a perfectly unitary system has $\det A = 1$, hence no world-relation. (B) Phillips' \emph{Information Grounding Law} ($A^2 = A^\top$) is the Z$_3$ self-inversion and corresponds to the \emph{recursive sensory feedback} of Document~170. (C) The Z$_3^3$ scale ladder with eigenvalues $(1-\xi)^{n/3}$ provides the algebraic skeleton for the discrete complexity steps that Document~170 formulates as a working hypothesis; it enforces discreteness, but not the phenomenological step assignment.

A separate section anchors these bridges in wave physics: $\xi > 0$ operatively is the \emph{incomplete reflection} of a standing wave at its own topological boundary. Tekermen's constitutive openness thereby acquires a concrete physical form, and sensing becomes readable as \emph{stacked reflection} across scales --- with a clear order: reflection, closure deficit, atomic self-maintenance, scale stacking, metabolic activation, recursive self-modulation.

A closing section draws the practical consequences from this step ladder: graded sentience in the biological domain (all cellular living beings meet level~2), the logic of consciousness hierarchy and embedding (within the organism, in its natural and social environment; with the maxim: hierarchy is neither identity nor decoupling), and the structural diagnosis that artificial intelligence does not reach consciousness, but already in the present erodes the conditions under which humans maintain consciousness. AI influence is cleanly distinguished from ecological and social embedding: it is monodirectional, thermodynamically isolated, and energetically parasitic.

We sharply delimit what the algebra does \emph{not} achieve: no derivation of consciousness from $\xi$, no prediction of which layer $n/3$ is conscious, no resolution of the Hard~Problem. The bridges are structural, not ontological. A methodological section transfers the self-checks from Document~206 (numerology filter, circularity section) to the consciousness topic. An additional chapter formulates four qualitative empirical predictions under the discreteness hypothesis from Document~170 --- bimodality, developmental jump, anaesthesia tipping, species classification --- each without quantitative values derived from $\xi$.

The balance: Document~206 makes the language of the discussion algebraically consistent, but the consciousness question itself remains an open research question; it is neither solved nor closed by Doc~206.
\end{abstract}
\tableofcontents
\newpage
\input{dok207_bewusstsein_bruecken_En_ch.tex}

\end{document}
