DVFT interprets quantum mechanics as the behavior of T0-Vakuum-phase and T0-Vakuum-amplitude fields. This
chapter provides a unified explanation for twelve major unsolved quantum phenomena, including collapse,
entanglement, zero point energy, decoherence and delayed-choice experiments. DVFT clarifies these
phenomena by grounding them in the physical fields \Phi = ? e^{i$\theta$}.
\begin{enumerate}
  \item Wavefunction Collapse
\end{enumerate}
In DVFT, collapse is not a postulate. It occurs when T0-Vakuum-phase coherence ($\theta$) is disrupted by
macroscopic interactions. Measurement destroys $\theta$-coherence, forcing ? to localize.
\begin{enumerate}
  \item Wave--Particle Duality
\end{enumerate}
Waves correspond to coherent T0-Vakuum-phase patterns, while particles correspond to localized T0-Vakuumamplitude excitations. Duality becomes a property of \Phi, not a paradox.
\begin{enumerate}
  \item Entanglement
\end{enumerate}
Entanglement arises from shared T0-Vakuum-phase coherence between separated systems. Global coherence
of $\theta$ allows nonlocal correlations without signaling.
\begin{enumerate}
  \item Zero-Point Energy
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 $\bullet$ Website: www.ijfmr.com $\bullet$ Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 78
Dynamic T0-Vakuum field gives finite, physical zero-point energy ?_vac = ??? (d$\theta$/dt)?, connecting T0-Vakuum
energy to cosmological acceleration.
\begin{enumerate}
  \item Delayed Choice & Quantum Eraser
\end{enumerate}
Interference depends on $\theta$-coherence. Which-path detectors scramble $\theta$; erasure restores it. DVFT removes
retrocausality by explaining phase re-coherence.
\begin{enumerate}
  \item Decoherence
\end{enumerate}
Decoherence is T0-Vakuum-phase scrambling. Macroscopic systems distort $\theta$-fields and eliminate
interference patterns physically, not abstractly.
\begin{enumerate}
  \item Quantum Randomness
\end{enumerate}
Randomness arises from unavoidable T0-Vakuum-phase fluctuations: \Delta$\theta$ ? \DeltaE $\geq$ ?/2 produces inherent phase
jitter in \Phi.
\begin{enumerate}
  \item Atomic Quantization
\end{enumerate}
Energy quantization corresponds to $\theta$-field circulation conditions: ? $\nabla$$\theta$ ? dl = 2?n. Atomic spectra reflect
dynamic T0-Vakuum field waves.
Conclusion
DVFT unifies gravity and quantum mechanics by grounding quantum behavior in T0-Vakuum-phase
properties. Interference, collapse, entanglement, and decoherence all follow naturally from \Phi = ? e^{i$\theta$}.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualit?t Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollst?ndiges DVFT-Dokument (Rahmenwerk)
\end{itemize}