% ==============================================================================
% Teil1_En.tex – Angepasst für einheitliches Buchlayout (wie Teil1a_De.tex)
% Version: 1.0 (angepasst an deutsche Buchversion)
% Author: Johann Pascher
% Date: 2026
% ==============================================================================

\documentclass[11pt,openright,twoside]{book}
\input{../../../T0_preamble_shared-ebook_En.tex}  % Verwende die neue englische Buch-Preamble (siehe unten)


\title{Fundamental Fractal-Geometric Field Theory (FFGFT):\\
	A Unified Physics from a Single Number\\[0.5em]
	\large Part 1: Core Documents}
\author{Johann Pascher}
\date{}

\begin{document}
% RESET alle Zähler am Anfang
\setcounter{section}{0}
\setcounter{subsection}{0}
\setcounter{subsubsection}{0}
\setcounter{paragraph}{0}

% Tiefe für Nummerierung und TOC
\setcounter{secnumdepth}{1}  % Nur Sections nummerieren
\setcounter{tocdepth}{1}     % Nur Sections im TOC	
\begin{center}
	\vspace*{2cm}
	{\Huge\textbf{Fundamental Fractal-Geometric Field Theory (FFGFT) or T0 Theory: Time-Mass Duality}}\\[1cm]
	{\Large Part 1: Core Documents}\\[2cm]
\end{center}
	
	\frontmatter
	\pagestyle{empty}
	
	\mainmatter
	\pagestyle{plain}
	
	\tableofcontents
	%\listoftables
	
% Unified Introduction for All Parts
\chapter*{Introduction: In Search of the Deepest Mysteries}
\addcontentsline{toc}{chapter}{Introduction}

Physics faces seven great mysteries – fundamental questions that challenge our understanding of the universe. Why does time have a direction? How does mass arise? What is the nature of quantum reality? This book invites you on a fascinating journey to explore these mysteries and shows how **Fundamental Fractal-Geometric Field Theory (FFGFT)** – formerly known as the T0 Theory of Time-Mass Duality – provides a unified framework to connect these seemingly disparate puzzles.

FFGFT starts from a bold assumption: time and mass are two sides of the same coin, dual to each other like wave and particle in quantum mechanics. From this simple yet profound insight – mathematically expressed through a single dimensionless constant \(\xi = \frac{4}{3} \times 10^{-4}\) – emerge answers to questions that have occupied physicists for decades.

Imagine trying to understand a complex machine. Traditional physics examines each component separately. FFGFT, however, reveals that many of these seemingly separate parts are different manifestations of the same underlying mechanism.

This insight has concrete, experimentally verifiable consequences and is distinguished by its elegance: instead of adding new particles or dimensions, FFGFT derives diverse phenomena from a single principle.

You don't need to be a professional physicist to follow this journey. We explain technical concepts in everyday language and use mathematics only where it illuminates the ideas.

Each chapter stands on its own – read in sequence or jump to topics that interest you. Some sections are more technical; feel free to skip them and focus on the conceptual explanations.

\textbf{The Seven Mysteries We Explore}

1. **The Nature of Time** – Thought experiment "Three Clocks" and solutions to classical paradoxes.  
2. **The Origin of Mass** – Alternative to the Higgs mechanism from temporal relationships.  
3. **Quantum Reality and Geometry** – Connection between the quantum world and spacetime curvature.  
4. **Cosmic Structures** – Formation of galaxies and voids.  
5. **Statistical Physics of Time** – Time as a statistical phenomenon.  
6. **Chance and Determination** – New paths between chaos and predetermination.  
7. **The Cosmic Mystery of the CMB Dipole** – Clues to the fundamental structure of space.

\textbf{Bonus: The Fractal Nature of Time} – Time as a fractal pattern.

These chapters offer a glimpse behind the curtain of reality. FFGFT reveals that the deepest mysteries of physics are interwoven and emerge from a single principle.

Welcome to the exploration of the seven mysteries of physics – and the theory that connects them.
	% Part 1: Core T0 Documents (wie in Teil1a_De.tex)
	
	\input{../en_chapters_new/001a_T0_Book_Abstract_En_ch}
	\input{../en_chapters_new/003_T0_Grundlagen_v1_En_ch}
	\input{../en_chapters_new/004_T0_Modell_Uebersicht_En_ch}
	\input{../en_chapters_new/006_T0_Teilchenmassen_En_ch}
	\input{../en_chapters_new/007_T0_Neutrinos_En_ch}
	\input{../en_chapters_new/008_T0_xi-und-e_En_ch}
	\input{../en_chapters_new/009_T0_xi_ursprung_En_ch}
	\input{../en_chapters_new/010_T0_Energie_En_ch}
	\input{../en_chapters_new/011_T0_Feinstruktur_En_ch}
	\input{../en_chapters_new/012_T0_Gravitationskonstante_En_ch}
	\input{../en_chapters_new/013_T0_SI_En_ch}
	\input{../en_chapters_new/014_T0_nat-si_En_ch}
	\input{../en_chapters_new/015_NatEinheitenSystematik_En_ch}
	\input{../en_chapters_new/016_T0_Vollstaendige_Berchnungen_En_ch}
	\input{../en_chapters_new/019_T0_lagrndian_En_ch}
	\input{../en_chapters_new/020_T0_QM-QFT-RT_En_ch}
	\input{../en_chapters_new/021_T0_QAT_En_ch}
	\input{../en_chapters_new/022_T0-QFT-ML_Addendum_En_ch}
	\input{../en_chapters_new/023_Bell_En_ch}
	\input{../en_chapters_new/024_T0_netze_En_ch}
	\input{../en_chapters_new/025_T0_Kosmologie_En_ch}
	\input{../en_chapters_new/026_T0_Geometrische_Kosmologie_En_ch}
	\input{../en_chapters_new/027_T0_Analyse_MNRAS_Widerlegung_En_ch}
	\input{../en_chapters_new/028_T0_7-fragen-3_En_ch}
	\input{../en_chapters_new/029_T0_threeclock_En_ch}
	\input{../en_chapters_new/030_T0_penrose_En_ch}
	\input{../en_chapters_new/032_T0_umkehrung_En_ch}
	\input{../en_chapters_new/033_T0-Theory-vs-Synergetics_En_ch}
	\input{../en_chapters_new/034_T0_QM-optimierung_En_ch}
	\input{../en_chapters_new/035_QM_En_ch}
	\input{../en_chapters_new/036_T0_peratt_En_ch}
	\input{../en_chapters_new/037_Hannah_En_ch}
	\input{../en_chapters_new/038_Markov_En_ch}
	\input{../en_chapters_new/039_Zwei-Dipole-CMB_En_ch}
	\input{../en_chapters_new/081_Zusammenfassung_En_ch}
	%\input{../en_chapters_new/072_QM-Detrmistic_p_En_ch.tex}
\end{document}