% =============================================================================
% INTRODUCTION TO VOLUME 4: NEWER DOCUMENTS AND EXTENSIONS — PART I
% (Vol. 4 of 5; continued in Vol. 5)
% =============================================================================

\section*{Fourth Volume of the Document Collection}

This fourth volume continues the collection of individual documents on T0
theory / FFGFT. As in the three preceding volumes, the documents are
standalone works produced at different points in the theory's development.
Unlike Volumes 1--3, which carry thematically closed emphases (foundations,
Lagrangian/QFT, cosmology/consciousness), this volume gathers the documents
that arose or were added after the original three-volume conception, as well
as a few earlier works that had not been included in the first three volumes.

\subsection*{Vol.~4 of 5 --- Split}

Because of the Kindle volume limit (max.\ 550 pages per volume), the
documents added since the original three-volume conception are distributed
over \emph{two} volumes:

\begin{itemize}
\item \textbf{Volume 4 (this volume):} 37 documents -- supplementary
      individual documents, time and numerical predictions,
      consciousness/photonics, and the early torus and L$_0$ derivations
      up to Doc.~184 (p-bit).
\item \textbf{Volume 5:} 37 documents -- from Doc.~185 (Embedding Cost)
      onwards: late torus geometry, FFGFT field theory, Hilbert-space
      bridge, layers and information formalism, recent clarifications
      including the epistemic self-positioning in Doc.~262.
\end{itemize}

The split follows a natural content boundary: up to and including Doc.~184,
the theory is developed on Layer~1 (compact $T^4$, correction-free
description in natural units); from Doc.~185 onwards, the Layer-1 /
Layer-2 distinction is used as an explicit descriptive grid.

\subsection*{Character of this Volume}

Volume 4 is broad in scope: it contains extensions to classical topics (Bell
tests, asymmetry, Lagrangian), a connected series of numerical predictions
(Koide, g-2, lepton lifetime, $H_0$ ratio, $\mathrm{LiNbO}_3$ dispersion
matched to 16 significant digits), a series on photonics and qubit states,
and the fundamental geometry and L$_0$ derivations.

\subsection*{Four-Part Organisation}

The 37 documents are arranged in numerical order and divided into four
thematic parts:

\begin{itemize}
\item \textbf{Part I --- Supplementary Documents to Volumes 1--3}:
      earlier works not included in the first three volumes (introductions,
      asymmetry, simplified Lagrangian, Bell follow-ups, scramblons).
\item \textbf{Part II --- Time, Cosmology and Numerical Predictions}:
      arrow of time, $H_0$ ratio, Casimir, Koide-to-g-2 bridge, lepton
      lifetime ratios, harmonic structure on the torus, Ising machine
      analogy, UV catastrophe, 't Hooft CAI, $\mathrm{LiNbO}_3$ geometry,
      periodic table.
\item \textbf{Part III --- Consciousness, Photonics and Qubit Series}:
      T0 and consciousness, string-theory connection, quantum dot, spin
      and qubit states, Shor's algorithm, spin stability, pairs and photons.
\item \textbf{Part IV --- Early Torus and L$_0$ Derivations}: L$_0$
      derivation, justification of the torus geometry, maximum scale of
      the universe, Willow processor, p-bit.
\end{itemize}

\subsection*{Status and Updates}

All documents in this collection carry the May 2026 status. The chapters
contained in Volumes 1--3 have been reviewed for the new edition and
corrected where appropriate --- in particular the hardware-validation
correction in Doc.~147 §\,8 in Volume~2, and the updates to the follow-up
documents Doc.~022, Doc.~035, Doc.~148 and Doc.~202.
