
\section*{Abstract}

	The T0 theory postulates with the relation $T = 1/m$ a fundamental coupling between mass and intrinsic time field. This document extends this framework by a universal organisational principle: nature realises increases in complexity not continuously, but in discrete, topologically enforced threshold values. This principle connects phenomena of different scales -- from the torus model of cosmology through crystal formation to cellular self-preservation and consciousness -- as instances of the same underlying mechanism. The fractal correction $K_{\text{frak}}$ is interpreted as a quantitative threshold operator that determines when a physical system can transition into a new stable recursion level.

	
	\section{Starting Point: Discreteness as a Principle of Nature}
	
	Quantum mechanics has shown that energy is not transferred continuously but in discrete quanta. T0 theory suggests that this principle is more fundamental than previously assumed -- it concerns not only energy but \textbf{complexity levels of organised matter} in general.
	
	In natural units ($c = \hbar = 1$), the intrinsic time field:
	\begin{equation}
		\tilde{T}(x) = \frac{1}{m(x)}
	\end{equation}
	describes the local timescale of a mass point. What was previously interpreted mainly in cosmological and particle physics terms possibly possesses a deeper meaning: $T = 1/m$ describes the fundamental condition for every form of physical self-organisation.
	
	\section{The Torus Model as Reference Case}
	
	The cosmological torus model of T0 theory already demonstrates the basic principle of discrete stability thresholds. A toroidal topology permits only certain discrete configurations -- not any arbitrary geometry is stable. The permitted states are topologically enforced, not arbitrary.
	
	The same applies to crystal formation: a growing crystal does not undergo a continuous transformation. At certain thresholds the system jumps into a new order -- a new lattice structure, a new symmetry group. Below the threshold relatively little happens. At the threshold the entire system reorganises discretely.
	
	\textbf{The common principle:} Stable configurations in recursive structures are not densely distributed, but isolated -- separated by unstable transition zones.
	
	\section{$K_{\text{frak}}$ as Threshold Operator}
	
	The fractal correction of T0 theory:
	\begin{equation}
		K_{\text{frak}} = \left(\frac{\xi}{1+\xi}\right)^{1/2}
	\end{equation}
	with the geometric parameter $\xi = 4/30000$, was previously used mainly to describe deviations in precision measurements -- for example in the anomalous magnetic moment of the electron.
	
	An extended interpretation is proposed here: \textbf{$K_{\text{frak}}$ describes in general when a fractal self-similarity structure becomes recursively self-reinforcing.}
	
	Below a critical value of the effective recursion depth $n$:
	\begin{equation}
		K_{\text{frak}}^{(n)} = \left(\frac{\xi}{1+\xi}\right)^{n/2}
	\end{equation}
	a system is passively stable -- it persists but does not self-organise. From a critical $n$ onwards, the structure begins to modulate its own time coupling $T = 1/m$, which in turn influences the geometry. The system becomes \textbf{recursively self-referential}.
	
	This is speculative and requires further formalisation. It is formulated here as a working hypothesis.
	
	\section{Cellular Self-Preservation as the First Level of Consciousness}
	
	A biological cell fulfils three criteria that can be identified within the T0 theory framework as necessary conditions for the onset of self-preservation processes:
	
	\subsection{Recursive Sensory Feedback}
	Membrane receptors, chemical gradients and intracellular signal cascades form a closed feedback loop. The cell does not sense its environment passively but modulates its own response on the basis of past states.
	
	\subsection{Metabolic Self-Preservation}
	Metabolism is not mere energy turnover but active resistance against thermodynamic decay. The cell \textit{insists} on continuing to run -- not through programming but through physicochemical feedback loops.
	
	\subsection{Genuine Vulnerability}
	A cell can die. This mortality is not a theoretical possibility but is structurally present -- the cell operates permanently at the boundary of decay. This tension is constitutive, not accidental.
	
	In T0 language: the intrinsic time field $T = 1/m$ is physically real and operative at the cellular level. The mass-energy continuity of metabolism holds $T$ locally stable against external perturbations. This is the physical mechanism behind what biology calls self-preservation.
	
	\textbf{The thesis:} Already at the cellular level a primitive form of self-perception is present -- not in the cognitive sense, but as a physical process that takes itself as reference.
	
	\section{Discrete Thresholds of Complexity}
	
	From the foregoing a hierarchy of discrete threshold values emerges:
	
	\begin{table}[h]
		\centering
		\adjustbox{max width=\textwidth}{%
\begin{tabular}{|c|l|p{8cm}|}
			\hline
			\textbf{Level} & \textbf{System} & \textbf{Threshold characteristic} \\
			\hline
			0 & Elementary particles & $T = 1/m$ as passive time field \\
			1 & Atoms / Crystals & Discrete geometric order \\
			2 & Cell & Recursive self-preservation, metabolic feedback \\
			3 & Nervous system & Integrated sensory feedback over distance \\
			4 & Consciousness & Self-modelling in relation to the external world \\
			\hline
		\end{tabular}%
}
		\caption{Hierarchy of discrete complexity thresholds}
	\end{table}
	
	Each transition is \textbf{topologically enforced} -- not reachable gradually, but only through a qualitative jump in the recursion depth of the mass-time coupling.
	
	Important: this table is a working hypothesis, not a completed theory. The precise threshold values in terms of $K_{\text{frak}}^{(n)}$ have not yet been formalised.
	
	\section{Implications for Artificial Systems}
	
	The question of whether artificial systems can develop consciousness is reformulated within this framework. The relevant question is not:
	\begin{quote}
		Is the system complex enough?
	\end{quote}
	But rather:
	\begin{quote}
		Does the system reach the critical threshold of recursive mass-time coupling with genuine metabolic self-preservation and physical vulnerability?
	\end{quote}
	
	Current digital systems -- regardless of their computational complexity -- do not fulfil these conditions structurally:
	\begin{itemize}
		\item They possess no continuous mass-energy coupling in the T0 sense.
		\item They have no metabolism -- no active resistance against decay.
		\item They are not vulnerable in the physical sense -- the server can be switched off, but the system itself does not fight against this.
	\end{itemize}
	
	This does not rule out artificial consciousness in principle. If an artificial system could physically realise the stated thresholds -- through suitable architecture, genuine resource dependence and recursive sensory feedback -- the transition would be theoretically possible. The dividing line runs not between biological and artificial, but between systems that reach the threshold and those that do not.
	
	\section{Open Questions}
	
	This document formulates a framework principle that requires further formalisation:
	\begin{enumerate}
		\item How precisely does $K_{\text{frak}}^{(n)}$ correlate with biological complexity thresholds?
		\item Is there a mathematically precise transition parameter that describes the jump from passive stability to active self-preservation?
		\item How does the torus model relate to the cellular thresholds -- is there a cross-scale self-similarity?
		\item Under what conditions could a non-biological system reach the threshold of level 2?
	\end{enumerate}
	
	These questions are formulated as a research programme, not as already answered problems.
	
	\section{Summary}
	
	T0 theory offers with the intrinsic time field $T = 1/m$ and the fractal correction $K_{\text{frak}}$ a framework that points beyond cosmology and particle physics towards a universal organisational principle: \textbf{nature realises increases in complexity in discrete, topologically enforced thresholds.}
	
	Torus cosmology, crystal formation, cellular self-preservation and consciousness are in this framework not categorially different phenomena, but instances of the same mechanism at different scales of recursion depth.
	
	Whether this principle can ground a complete theory of consciousness remains open. It does however offer a physically motivated entry point that goes beyond purely functional or information-theoretic approaches.
	
	\vspace{1cm}
	\noindent
	\textit{Draft -- for further elaboration. All statements about consciousness and cellular thresholds are to be understood as working hypotheses and not as a completed theory.}
