% ============================================================
% Content: Stability as Ground State
% The Permanent Magnet as Macroscopic Proof
% of Discrete Spin Stability in the FFGFT Framework
% March 2026
% ============================================================

% Dirac notation
\providecommand{\ket}[1]{\left|#1\right\rangle}
\providecommand{\bra}[1]{\left\langle#1\right|}
\providecommand{\braket}[2]{\left\langle#1\middle|#2\right\rangle}

% ============================================================
\section{The Uncomfortable Question}
\label{sec:uncomfortable-question}
% ============================================================

Every textbook on quantum mechanics states:
An electron exists in genuine superposition
$\alpha\ket{\uparrow} + \beta\ket{\downarrow}$ ---
simultaneously in both spin states,
until a measurement collapses the state.

On every refrigerator there is a permanent magnet.

Between these two facts lies a contradiction
that standard theory never explicitly resolves.

\begin{significance}[The central question of this document]
If a single, isolated electron exists in genuine superposition
of both spin states ---
why do then billions of electrons
in the permanent magnet \emph{never} show collective superposition,
but always unambiguous, stable alignment?

And conversely:
What does the permanent magnet --- an everyday object,
not a laboratory experiment --- tell us about the nature of spin?
\end{significance}

% ============================================================
\section{What the Permanent Magnet Really Shows}
\label{sec:permanent-magnet}
% ============================================================

A permanent magnet is not a mysterious quantum phenomenon.
It is the \textbf{macroscopic sum of spin alignments}.

Every electron in a ferromagnet (iron, nickel, cobalt)
has a spin --- and thus a magnetic moment.
The \textbf{exchange interaction} (Doc.~174,
section on Method~4) forces neighbouring spins
into parallel alignment: all up, or all down.
This is energetically more favourable than random distribution.

This collective alignment forms \textbf{Weiss domains} ---
macroscopic regions of coherent spin order.
In the permanent magnet, these domains are permanently
aligned and frozen by an external field.

\begin{keyresult}[What the permanent magnet directly proves]
\textbf{1. Spin has preferred, stable alignments.}\\
Up and down are not equivalent alternatives ---
they are geometrically distinguished states.
The field \emph{wants} to be in one of them.

\textbf{2. This stability is macroscopically robust.}\\
A refrigerator magnet maintains its alignment
at room temperature, in an environment with $10^{23}$
thermally fluctuating neighbouring atoms ---
for years, without decohering.

\textbf{3. Superposition never occurs collectively.}\\
No permanent magnet ever shows a state
that is simultaneously north and south.
Nature chooses. Always.
\end{keyresult}

% ============================================================
\section{Standard Theory and Its Explanation}
\label{sec:standard}
% ============================================================

Standard theory explains the macroscopic absence
of superposition through \textbf{decoherence}:
The interaction with the environment destroys superposition
so quickly that it is practically unobservable.

This is technically correct --- but it is a
\textbf{post-hoc explanation}, not a prediction.

\begin{important}[The structural weakness of the decoherence explanation]
Standard theory postulates:
\begin{enumerate}
  \item A single electron exists in genuine superposition.
  \item Decoherence through the environment destroys this superposition
    practically immediately for macroscopic systems.
\end{enumerate}

This does explain \emph{why} we see no macroscopic
superposition --- but it reverses the physical
order of events:

\textbf{It begins with superposition as the ground state}
and then explains why this ground state is always immediately
destroyed.

\textbf{FFGFT reverses this:}
Stability is the ground state.
Superposition is the limited, fragile exception ---
with measurable timescales and a geometric cause.

The question is not only mathematical --- it is physical:
which description is the more natural one?
\end{important}

% ============================================================
\section{Superposition is Fragile --- The Experimental Evidence}
\label{sec:fragility}
% ============================================================

The measured coherence times from Doc.~174
tell an unambiguous story:

\begin{center}
\resizebox{\textwidth}{!}{%
\begin{tabular}{lrrrl}
\toprule
\textbf{System} & \textbf{$T_1$} & \textbf{$T_2$} &
\textbf{Temperature} & \textbf{Remark} \\
\midrule
Exciton (CdSe QD)    & $\sim 1$\,ns  & $\sim 10$\,ps  & 4\,K  &
  Superposition lasts picoseconds \\
Electron spin (GaAs) & $\sim 1$\,ms  & $\sim 10$\,ns  & mK    &
  Superposition lasts nanoseconds \\
Electron spin (Si)   & $> 1$\,s      & $\sim 10$\,ms  & mK    &
  Superposition lasts milliseconds \\
Nuclear spin (P:Si)  & $> 1$\,s      & $> 100$\,ms    & mK    &
  Best known system \\
\textbf{Permanent magnet} & \textbf{Years} & \textbf{---} &
  \textbf{300\,K} & \textbf{Stability without cooling} \\
\bottomrule
\end{tabular}
}
\end{center}

The table shows a clear trend:
the more isolated the system from the disturbing influence of the environment,
the longer superposition is maintained ---
but it \emph{always} lasts only a limited time.

\begin{keypoint}[Superposition is never the stable ground state]
Not a single experimental system shows
superposition as a durably stable state.
Even in the best qubit system (nuclear spin P:Si at mK)
superposition decays after seconds.

The permanent magnet --- without cooling, without isolation ---
maintains its stable spin state for years.

This is not coincidence. This is physics:
\textbf{Stability is energetically preferred.
Superposition is metastable.}
\end{keypoint}

% ============================================================
\section{The Single Electron: Superposition or Unknown State?}
\label{sec:single-electron}
% ============================================================

Here lies the actual conceptual core.

Standard theory claims: a single, isolated electron
exists in genuine superposition
$\alpha\ket{\uparrow} + \beta\ket{\downarrow}$
until measurement.

The FFGFT position is more precise:

\begin{foundation}[FFGFT: Superposition vs.\ epistemic ignorance]
A single electron has at every moment a
\textbf{definite torsion configuration} ---
either spin-up or spin-down.

What we describe as superposition $\alpha\ket{\uparrow} + \beta\ket{\downarrow}$
is \textbf{epistemic ignorance} about this
definitive state --- not ontological simultaneity.

The proof comes from QND measurement (Doc.~174,
Faraday rotation): a spin state can be measured repeatedly
without changing it, and \emph{always} yields the same result.
This is only possible if the state \emph{before measurement}
exists definitively.

\textbf{If the electron were truly in superposition,}
a QND measurement would yield random results at each repetition.
It does not.
\end{foundation}

The apparent superposition arises in the description ---
when we mathematically describe a prepared system before
the readout interaction.
It is a state description under ignorance,
not a physical double-state.

% ============================================================
\section{The Bridge: From Single Spin to Permanent Magnet}
\label{sec:bridge}
% ============================================================

The transition from quantum to classical magnetism
is in FFGFT no puzzle --- it is the same mechanism,
only at different scales.

\begin{center}
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{3cm}p{4cm}p{4cm}p{3cm}}
\toprule
\textbf{Level} & \textbf{System} & \textbf{FFGFT description}
& \textbf{Stability} \\
\midrule
Single spin &
  Electron in QD &
  One stable torsion configuration; up or down &
  $T_1 > 1$\,s (P:Si) \\[6pt]
Spin pair &
  Two coupled QDs &
  Two torsions; exchange interaction prefers parallel alignment &
  $J(t)$ controllable \\[6pt]
Domain &
  Weiss domain ($10^{15}$ spins) &
  Collective torsion order; energetically more stable than disorder &
  Stable at 300\,K \\[6pt]
\textbf{Permanent magnet} &
  Macroscopic body &
  Frozen global torsion alignment &
  \textbf{Stable for years} \\
\bottomrule
\end{tabular}
}
\end{center}

Each level is the same physics --- stable torsion configurations,
collectively reinforced by exchange interaction.
No step in this chain requires genuine superposition.
Every step requires \textbf{geometric precision and
energetic stability}.

\begin{foundation}[FFGFT: Permanent magnet as macroscopic resonator]
In FFGFT the permanent magnet is not a special case ---
it is the natural macroscopic limiting case
of the resonator principle from Doc.~173.

A single quantum dot at $\xi$-level $N \approx 8$:
two stable torsion configurations, metastable intermediate states.

A permanent magnet:
$\sim 10^{22}$ resonators forced by exchange interaction
into the same stable torsion configuration.
The collective field reinforces stability --- instead of destroying it
(decoherence), the coupling acts here as a
stability amplifier.

The boundary between quantum mechanics and classical magnetism
is in FFGFT no categorical boundary ---
it is a quantitative transition along the $\xi$-hierarchy.
\end{foundation}

% ============================================================
\section{What Standard Theory Leaves Unanswered}
\label{sec:unanswered}
% ============================================================

The standard presentation of spin in textbooks and
popular science texts has a structural problem:
it begins with the abstract (Hilbert space, spinor, collapse)
and then explains everyday life (permanent magnet) as a limiting case.

In doing so it overlooks a simple observation:

\begin{significance}[The simplest description of spin]
The permanent magnet exists.
It shows that spin is a \textbf{spatial orientation} ---
discrete, stable, real.

This is the most intuitive representation of spin:
not an abstract state vector in Hilbert space,
but a physical orientation in space
that is macroscopically measurable, stable and everyday.

Quantisation (only up or down, nothing in between)
follows from the geometry of the resonator --- as derived in Doc.~173.
It is not a postulate, but a geometric consequence.

The apparent superposition is an epistemic description
under ignorance --- not a physical double-state.
The permanent magnet shows daily which state is fundamental:
the stable, aligned one --- not the superposed one.
\end{significance}

% ============================================================
\section{Consequences for Quantum Information}
\label{sec:qi-consequences}
% ============================================================

This view has direct consequences for the understanding
of quantum computers.

The standard view: a qubit is powerful because it is in superposition.
Decoherence is the enemy of superposition and must be combated.

The FFGFT view: a qubit is powerful because it is a
\textbf{precisely controllable torsion configuration}.
Decoherence is not the destruction of a miracle ---
it is the system returning to its energetically stable
ground state. This is normal, not pathological.

\begin{keypoint}[Decoherence as return to the ground state]
In FFGFT, decoherence is not a failure of the system ---
it is proof that the stable spin state is real and
energetically preferred.

The permanent magnet does not decohere.
The qubit decoheres in milliseconds.
The difference is not the physics ---
the difference is the \textbf{isolation from the coupling}
that enforces the stable alignment.

A quantum computer does not fight against the nature of spin ---
it fights against the spin's tendency to return to its natural
stability before the computation is finished.
This is an engineering problem, not a foundational problem.
\end{keypoint}

% ============================================================
\section{Summary}
\label{sec:summary-178}
% ============================================================

\begin{conclusionBox}[Conclusion: The Permanent Magnet as Witness]
The permanent magnet is the simplest and most convincing
argument for the FFGFT view of spin:

\textbf{1. Spin has stable, preferred alignments.}\\
Up and down are geometrically distinguished states ---
not arbitrary measurement outcomes.

\textbf{2. Collective superposition does not exist.}\\
Billions of electrons always choose one alignment.
Never both simultaneously. Never.

\textbf{3. Superposition is fragile --- stability is robust.}\\
Coherence times range from picoseconds (exciton) to
seconds (nuclear spin) --- always limited, always finite.
The permanent magnet maintains its state for years.

\textbf{4. The decoherence explanation reverses the physics.}\\
Standard theory begins with superposition as the ground state
and then explains why it always immediately disappears.
FFGFT begins with stability as the ground state ---
superposition is the finite, measurably fragile exception.

\textbf{5. QND measurement confirms determinism.}\\
Repeated Faraday measurements always yield the same result ---
the spin state was definite \emph{before} measurement.

In FFGFT language:
Spin-up and spin-down are two stable torsion configurations.
The permanent magnet is their macroscopic collective realisation.
Superposition is a metastable intermediate torsion ---
real on short timescales, but never the fundamental ground state.

\textbf{The simplest description of spin does not begin in
Hilbert space --- it begins at the refrigerator.}
\end{conclusionBox}

% ============================================================

\begin{thebibliography}{99}

% --- Permanent magnetism and ferromagnetism ---
\bibitem{Heisenberg1928}
Heisenberg, W.
\textit{Zur Theorie des Ferromagnetismus.}
Z.\ Phys.\ \textbf{49}, 619--636 (1928).

\bibitem{Weiss1907}
Weiss, P.
\textit{L'hypothèse du champ moléculaire et la propriété ferromagnétique.}
J.\ Phys.\ Théor.\ Appl.\ \textbf{6}, 661--690 (1907).

% --- Exchange interaction and spin lattice ---
\bibitem{Loss1998}
Loss, D.\ \& DiVincenzo, D.\,P.
\textit{Quantum computation with quantum dots.}
Phys.\ Rev.\ A \textbf{57}, 120--126 (1998).

\bibitem{Petta2005}
Petta, J.\,R.\ et al.
\textit{Coherent manipulation of coupled electron spins in semiconductor
quantum dots.}
Science \textbf{309}, 2180--2184 (2005).

% --- Decoherence and coherence times ---
\bibitem{Veldhorst2014}
Veldhorst, M.\ et al.
\textit{An addressable quantum dot qubit with fault-tolerant control-fidelity.}
Nature Nanotechnol.\ \textbf{9}, 981--985 (2014).

\bibitem{Muhonen2014}
Muhonen, J.\,T.\ et al.
\textit{Storing quantum information for 30 seconds in a nanoelectronic device.}
Nature Nanotechnol.\ \textbf{9}, 986--991 (2014).

% --- QND measurement ---
\bibitem{Atature2007}
Atatüre, M.\ et al.
\textit{Observation of Faraday rotation from a single confined spin.}
Nature Phys.\ \textbf{3}, 101--105 (2007).

\bibitem{Delbecq2019}
Delbecq, M.\,R.\ et al.
\textit{Quantum non-demolition measurement of an electron spin qubit.}
Nature Nanotechnol.\ \textbf{14}, 446--450 (2019).

% --- Decoherence theory ---
\bibitem{Zurek2003}
Zurek, W.\,H.
\textit{Decoherence, einselection, and the quantum origins of the classical.}
Rev.\ Mod.\ Phys.\ \textbf{75}, 715--775 (2003).

\bibitem{Joos2003}
Joos, E.\ et al.
\textit{Decoherence and the Appearance of a Classical World in Quantum Theory.}
2nd ed.\ Springer (2003).

% --- Quantum measurement and determinism ---
\bibitem{Grangier1998}
Grangier, P., Levenson, J.\,A.\ \& Poizat, J.\,P.
\textit{Quantum non-demolition measurements in optics.}
Nature \textbf{396}, 537--542 (1998).

\end{thebibliography}
