% ============================================================
% 190_T0_Korrekturen_En_ch.tex
% Errata and Refinements - FFGFT / T0 Time-Mass Duality
% Older documents remain unchanged; this document records
% corrections and refinements.
% Status: 5 May 2026 (with R7, R8: terminology "renormalization")
% Re-translated in full from the current German register (14 June 2026):
%   corrections C1-C5, refinements R1-R39; plain header (the status box
%   no longer fit on one page).
% ============================================================

\section*{Preliminary Note}

\textbf{Status: C1--C6, R1--R40} (R16/R17 partial, R20/R30/R32 open, R29 partial, R31 partially derived, R33 declared, R34 clarified; R35/R36 added; R37 revised; C4 (factor~3) added, C5/R38 after external audit; R39 $H_0$/$R_H$ status clarified; C6 redshift achromatic; R40 absolute values carry correction via bridge constants ($v$/$E_0$/factors), ratios exact; 100 (RG amplification) $\neq$ 3609 (φ-scale recursion, open); coupling backdoor) --- as of 15~June 2026.

The corrections (C1--C3) and refinements (R1--R13) listed in this document
have been incorporated into the respective source documents. The last open
item --- C2 (tau prefactor $r_\tau$) --- was fully completed on 27~May 2026:
besides the items reported on 26~May in Doc.~016, Doc.~046 and Doc.~116, this
also affected remaining \emph{derived} values in Doc.~046~DE (energy
$18{,}8 \to 18{,}0$~meV) as well as the entire \textbf{English} parallel
version of Docs.~016, 046 and 116, which had not yet been updated on 26~May.
For details and the target state see the section ``Status of incorporation''
under C2.

This document is retained as a historical archive. For $r_\tau$ the value
$25/9$ recorded here is authoritative.

\medskip

\textbf{Addendum (2~June 2026):} Added and incorporated is \textbf{R14a}
(formulation of the redshift in Doc.~041): implemented in Doc.~041 (DE+EN).

\medskip

\textbf{Addendum (6~June 2026):} Carried over from the CMB work (Doc.~267
Cosmological Degeneracy, Doc.~268 CMB peaks from T$^4$): \textbf{R18}
(ΛCDM/FFGFT as two readings, theoretical not empirical),
\textbf{R20} (absolute cosmological scale: \emph{form} fixed as the $\xi$ ratio $R_H/\ell_P$, the \emph{factor} $41/4$ a declared external calibration from $\Lambda$CDM, not derived, open), \textbf{R29} (peak selection rule,
only \emph{partially} answered -- the factor-3 filter does \emph{not} exclude
$|n|^2=30$), \textbf{R30} (rigorous $C_\ell$ projection; the naive spherical
Bessel sum is \emph{insufficient}, open) and \textbf{R31} (geometric
anharmonicity from the codimension-1 projection -- leading behaviour derived
forward, small residual open). New \textbf{R32} (statements presenting $H_0$ as
FFGFT-derived are to be cleaned up corpus-wide -- noted for now). The
previously separate items \emph{R19} (CMB path lengthening) and \emph{R28}
(exponent for $z_*$) are merged into \textbf{R14a} resp.\ \textbf{R20} and do
not appear as their own rows.

\medskip

\textbf{Addendum (8~June 2026):} New \textbf{R33} -- the magnitude-carrying
factor $5^4$ in $\xi = 1/(3\cdot2^2\cdot5^4)$ is \emph{not} derived forward but
grounded intuitively (harmonic / Euler Tonnetz) resp.\ empirically (Higgs
sector); the \emph{form} ($4/3$, $3$, $2^2$) is forward, the \emph{magnitude}
($5^4$) remains at the intuitive derivation and is openly \emph{declared} as
such. Structural parallel to R20 (form fixed, factor open).

\medskip

\textbf{Addendum (8~June 2026, II):} New \textbf{R34} (dimensional structure).
Doc.~181 presents $D=4$ as ``following necessarily''; clarified: \textbf{3+1
is empirical input} (no theory derives the dimension count). Forward are only
(i) periodicity, (ii) torus-not-sphere ($\pi_1\neq0$), (iii) minimal
sufficiency (4 instead of 5 via the duality $\tilde T m=1$), (iv) the lossless
Hilbert representation (Type~III). At the same time recorded: the SI
conversions are \emph{indispensable} for the exponent structure (\emph{power of
$c$}, power of time) -- $c$ is the space-time bridge ($T^3\leftrightarrow$time),
$\hbar$ the mass-time bridge ($S^1_m$); $c=\hbar=1$ collapses $L,T,M$ and
destroys the powers. The four-circle structure \emph{is} this bookkeeping.
Signature as R20/R33 (structure forward, number input).

\medskip

\textbf{Addendum (10~June 2026):} New \textbf{R37} (use of $\varphi$ in various
documents -- clarification of the levels). Occasion: Doc.~275 shows that
$1/\varphi$ is the fixed point of the $\xi$ damping recursion after
$k^* = \log(\varphi)/\xi \approx 3609$ scale levels. In the process it turned
out that $\varphi$ appears in the corpus in \emph{three different roles} that
must not be conflated. R37 documents this separation and augments the
$\xi^N$/$\varphi^N$ triviality warning (R35) by the role level. Note: R35
($\xi^N$ triviality) and R36 ($R_H$ interpretation) had been declared via the
changelog (Updates 16/17); their table entries were added on 10~June 2026.

\textbf{Addendum (11~June 2026):} New \textbf{C5} (three implementation errors
in the validation script v3 for Doc.~275: point duplicates, seed bug,
detector bias -- all fixed in v4, affected results retracted) and \textbf{R38}
($k^*$ result downgraded from ``fixed point without a free parameter'' to
``pass-through point, R35 applies''; R37 level~(2) revised accordingly). Both
entries go back to the independent audit by P.~Stoychev (IPI list, 11~June
2026) -- the first external audit entry of the register.

\textbf{Addendum (14~June 2026):} New \textbf{R39} (status of $H_0$/$R_H$
clarified). Occasion: Doc.~277. It is clarified that the relation Planck
length$\leftrightarrow R_H$ (exponent $41/4$) follows from \emph{no} framework
out of first principles; $\Lambda$CDM fixes it via the measured $H_0$ (itself
circular, Doc.~267), FFGFT adopts the established value for comparability.
Hence the cosmic scale is a \emph{shared empirical reference point}, not an
FFGFT-specific gap and not an asymmetric disadvantage relative to $\Lambda$CDM
(R20/R32/R36 remain valid but are no longer read as a weakness). The only
remaining open point is the forward derivation of $41/4$ from $\xi$ --
symmetric, since no framework has it; the only model asymmetry is the dark
sector (carried by $\Lambda$CDM alone). At the same time a numbering conflict
was resolved: the v3 script audit (initially recorded as C4 in the addendum of
11~June) is now \textbf{C5}; \textbf{C4} denotes the older factor-3 correction
(Doc.~267/268, 3D observer instead of fractal dispersion), added as a table
row.

\textbf{Addendum (15~June 2026):} New \textbf{C6} (redshift is \emph{achromatic},
not wavelength-dependent). Occasion: Doc.~280 and the finite-element simulation of
the fractal path-lengthening. It corrects the earlier chromatic presentation
($z(\lambda)\propto\lambda$, \enquote{UV stronger than radio}) in Doc.~004, 025,
030, 039, 041, 053, 061, 063, 068, 081. The mature mechanism (geometric
path-lengthening) stretches all wavelengths by the same factor; the observed
cosmological redshift is achromatic, which FFGFT gets right. The earlier
\enquote{wavelength-dependent discriminator} drops out -- it moves to the
\enquote{fits} column (data degeneracy, Doc.~267).

\textbf{Addendum (15~June 2026):} New \textbf{R40} (absolute values carry the
fractal/SI correction via the bridge constants; ratios are exact). In FFGFT only the
\emph{dimensionless ratios} are exact. Absolute values carry the fractal/SI correction
because it is absorbed into the dimensionful \emph{bridge constants}: $v$ (masses
$m=r\,\xi^{p}v$), $E_0=7{,}398$~MeV ($\alpha=\xi E_0^2$) and the factors
$3{,}521\times10^{-2}$/$2{,}843\times10^{-5}$ ($G$; canonical script \texttt{calc\_De.py},
which carries \emph{no} explicit $K$). In ratios $v$/$E_0$/factors cancel
($m_\mu/m_e=206{,}768$, correction-free). Factored out, this correction is
$K_{\text{frak}}=1-100\,\xi\approx0{,}987$ (Doc.~011/012; in Doc.~133 derived from
$D_f$-consistency and an RG run over 17 orders of magnitude -- \emph{not an adjusted
correction}). \textbf{Do NOT confuse two numbers:} the \emph{100} in $K_{\text{frak}}$ is
the RG amplification of the ${\sim}1{,}3\,\%$ correction (Doc.~133); the \emph{3609}
(Doc.~275) is the depth of the ξ-scale recursion $r(k)=\tfrac{D_f}{3}(1-\xi)^k$ at which the
sequence \emph{passes} $1/\varphi$. There $1/\varphi$ is a \emph{passage point, not a fixed
point} (the only fixed point is $0$); since the sequence passes \emph{every} value, 3609 is
unanchored unless $1/\varphi$ is independently motivated (status open, R37). Moreover further
mutual couplings are not excluded ($\Rightarrow$ even ratios are leading order;
\emph{backdoor}): a deviation from the simple rational can always be attributed to an
unmodelled coupling -- ratio tests confirm (Koide $10^{-5}$ at $2/3$) but barely falsify.
Clean falsification only via a \emph{forward}-fixed new prediction ($41/4 \to H_0 \approx
66{,}2$ against the $H_0$ tension).

\textbf{Addendum (2~July 2026):} New \textbf{P41} (redshift drift
Sandage--Loeb checked and not booked: amplitude test not degeneracy-proof at
the shared scale $c/R_H=H_0$, only a conditional shape test) and
\textbf{P42} (lepton sector: one declared reference point $m_\mu/m_e$;
$2/9$ as the rational address of $\theta_{\text{ref}}$, sharpened
prediction $m_\tau=1776.9690$ MeV; occasion: precision analysis Doc.~292).
At the same time the doubly assigned heading \enquote{Refinement~14} was
resolved into \textbf{R14a} (redshift Doc.~041, incl. table row) and
\textbf{R14b} (CMB anharmonicity, covering R29--R31).

\bigskip
This document lists corrections and refinements to already published documents
of the FFGFT series. Older documents are \emph{not} changed. Where a
contradiction exists between an older and a newer document, the version
recorded here is authoritative.

Each entry contains: the affected document and location, the erroneous
expression, the correct expression, and a short justification.

% ============================================================
\section{\texorpdfstring{Correction~1: Prefactor in the Higgs derivation of $\xi$}{Correction 1: Prefactor in the Higgs derivation of xi}}
% ============================================================

\subsection*{Affected document}

Doc.~049 (T0 Lagrangian and Higgs integration), HTML interim version
and older working versions.

\subsection*{Erroneous expression}

\begin{equation}
  \xi \;=\; \frac{\lambda_h^2\, v^2}{64\pi^4\, m_h^2}
  \;\approx\; 1{,}0 \times 10^{-5}
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct expression}

\begin{equation}
  \boxed{
    \xi \;=\; \frac{\lambda_h^2\, v^2}{16\pi^3\, m_h^2}
    \;\approx\; 1{,}33 \times 10^{-4}
  }
  \tag{190.1}
\end{equation}

with the experimental inputs:
\begin{align*}
  m_h      &= 125{,}25\,\text{GeV} \quad \text{(Higgs mass)}, \\
  v        &= 246{,}22\,\text{GeV} \quad \text{(vacuum expectation value)}, \\
  \lambda_h &= \frac{m_h^2}{2v^2} \approx 0{,}129
               \quad \text{(Higgs self-coupling)}.
\end{align*}

\subsection*{Justification}

The prefactor $64\pi^4$ stems from a typo in the early HTML visualization. It
yields $\xi \approx 10^{-5}$, which deviates by an order of magnitude from the
geometrically derived value $\xi = 4/3 \cdot 10^{-4}$ and does not reproduce
the natural constants. The correct prefactor $16\pi^3$ gives
$\xi \approx 1{,}33 \times 10^{-4}$, consistent with the independently
determined value from the proton-electron mass ratio (Doc.~009).

% ============================================================
\section{\texorpdfstring{Correction~2: Tau Yukawa prefactor $r_\tau$}{Correction 2: Tau Yukawa prefactor r-tau}}
% ============================================================

\subsection*{Affected documents}

The prefactor $r_\tau$ appears in several documents. Complete list:
\begin{itemize}
  \item Doc.~116 (Koide formula as a consequence of T0 theory),
        lepton-parameter table.
  \item Doc.~016 (Complete calculations), mass table and
        $r$-parameter list.
  \item Doc.~046 (Particle masses), tau-neutrino row
        (double-$\xi$ construction containing $r_\tau$).
\end{itemize}
Already correctly updated at the time of the first correction were
Docs.~006, 028, 158, 210 as well as the theorem and proof part of Doc.~116.

\subsection*{Erroneous expression}

\begin{equation}
  r_\tau \;=\; \frac{8}{3} \;\approx\; 2{,}667
  \quad \Rightarrow \quad
  m_\tau \approx 1712\,\text{MeV} \quad (-3{,}6\,\% \text{ dev.})
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct expression}

\begin{equation}
  \boxed{r_\tau \;=\; \frac{25}{9} \;\approx\; 2{,}778}
  \quad \Rightarrow \quad
  m_\tau \approx 1783\,\text{MeV} \quad (+0{,}4\,\% \text{ dev.})
  \tag{190.2}
\end{equation}

The lepton masses follow generally from:
\begin{equation}
  m_\ell \;=\; r_\ell \cdot \xi^{p_\ell} \cdot v
  \tag{190.3}
\end{equation}
with the exponents $p_e = 3/2$, $p_\mu = 1$, $p_\tau = 2/3$
(step size $\Delta p = 1/3$) and the vacuum expectation value $v$.

\subsection*{Justification}

$r_\tau = 8/3$ was a remnant from an earlier iteration step. Doc.~158
(Koide-to-g-2 bridge) already uses $r_\tau = 25/9$, which matches the tau mass
numerically. Moreover $25/9 = (5/3)^2$ has a geometric interpretation as the
square of the pure sixth in the natural harmonic series, consistent with the
musical resonance analogy (Doc.~060).

\subsubsection*{Complete corrected prefactor table}

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{lccc}
\hline
\textbf{Lepton} & \textbf{Exponent $p$} & \textbf{Prefactor $r$} & \textbf{$m$ [MeV]}\\
\hline
Electron   & $3/2$  & $4/3$   & $0{,}511$ \\
Muon       & $1$    & $16/5$  & $105{,}7$ \\
Tau        & $2/3$  & $25/9$  & $1783$    \\
\hline
\end{tabular}%
}
} % footnotesize
\end{center}

\subsection*{Status of incorporation (Addendum 26 May 2026)}

A renewed corpus-wide search found \textbf{remaining $8/3$ residues}. The
correction had thus \emph{not been carried through cleanly}; the original entry
named only Doc.~116 as affected and overlooked Docs.~016 and 046.

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{lll}
\hline
\textbf{Document / location} & \textbf{Finding} & \textbf{Target} \\
\hline
Doc.~116, lepton-parameter tab. & $r_\tau = 8/3$ & $25/9$ \\
\quad(contradicts its own theorem) & & \\
Doc.~016, mass tab.\ and $r$-list & $r_\tau = 8/3$ & $25/9$ \\
\quad($m_\tau = 1712{,}1$, $-3{,}64\,\%$) & & ($\approx 1783$, $+0{,}3\,\%$) \\
Doc.~046, tau-neutrino (3 places) & $r = 8/3$ & $25/9$ \\
\quad(param.\ row, double-$\xi$ calc., & & \\
\quad second $\nu$ table; cf.\ Doc.~006) & & \\
\hline
\end{tabular}%
}
} % footnotesize
\end{center}

\noindent\textbf{Carried out on 26~May 2026:} All of the above places were
brought to $25/9$; in Doc.~016 the derived tau mass ($1712{,}1 \to 1783{,}4$~MeV)
and the deviation ($3{,}64 \to 0{,}37\,\%$) were recomputed, in Doc.~046 the
$\xi_{\nu_\tau}$ calculation ($128/27 \to 400/81$, $E = 18{,}8 \to 18{,}0$~meV).
C2 is thereby fully incorporated.

\medskip
\noindent\textbf{Addendum 27~May 2026 (actual extent):} An independent full
check on 27~May found that the incorporation on 26~May was \emph{not} complete.
Two points were still open:
\begin{itemize}
  \item \textbf{Doc.~046 DE} still carried, in the \emph{derived} tables
        (compatibility, method-equivalence and falsification tables), the old
        energy value $18{,}8$~meV as well as the decimal form $r_\tau = 2{,}768$.
        The main calculation ($\xi_{\nu_\tau} = 400/81$) was already correct;
        only the downstream values had not been updated. Corrected to
        $18{,}0$~meV resp.\ $2{,}778$.
  \item The \textbf{English parallel version} of Docs.~016, 046 and 116 had
        \emph{not} been updated at all on 26~May (DE and EN must be
        consistent). Corrected: 016~EN (mass table $8/3 \to 25/9$,
        $1712{,}1 \to 1783{,}4$, $3{,}64 \to 0{,}37\,\%$; $r$-list),
        046~EN (both $\nu_\tau$ rows, $\xi_{\nu_\tau}$ calc.
        $128/27 \to 400/81$, three $E$ values, method equivalence),
        116~EN (tau row $8/3 \to 25/9$).
\end{itemize}
\noindent Corpus-wide residual search afterwards: \textbf{0 remaining $8/3$
places} in 016/046/116 (DE+EN). All four files recompiled (Kindle 6$\times$9).
C2 has been \emph{fully} incorporated since 27~May 2026 --- DE and EN.

% ============================================================
\section{\texorpdfstring{Correction~3: Base formula for $g$-$2$ of the electron}{Correction 3: Base formula for g-2 of the electron}}
% ============================================================

\subsection*{Affected document}

T0-Explorer (HTML visualization), first version; older interim versions
of Doc.~018.

\subsection*{Erroneous expression}

\begin{equation}
  a_e \;=\; \frac{4\pi}{f \cdot k_{\text{geom}}}
  \tag{old -- wrong}
\end{equation}

\subsection*{Correct expression}

\begin{equation}
  \boxed{
    a_e \;=\; \frac{S_3}{f \cdot k_{\text{geom}}}
    \;=\; \frac{2\pi^2}{f \cdot k_{\text{geom}}}
  }
  \tag{190.4}
\end{equation}

with $f = 1/\xi \approx 7500$, $k_{\text{geom}} = (2/\sqrt{\varphi})\cdot\sqrt{2} \approx 2{,}224$
and $S_3 = 2\pi^2 \approx 19{,}74$ (surface of the 4D unit sphere,
i.e.\ of the 3D boundary of the torus).

\subsection*{Justification}

The earlier prefactor $4\pi$ corresponds to the surface of the 2D sphere in 3D
space, not to the geometrically correct 3D surface of the 4D torus.
$S_3 = 2\pi^2$ is the correct value from the torus geometry. The fractal
corrections for muon and tau continue to use $4\pi$:

\begin{align}
  \Delta a_\mu  &= \frac{4\pi}{f^{5/3}}, \tag{190.5}\\
  \Delta a_\tau &= \frac{4\pi}{f^{4/3}}. \tag{190.6}
\end{align}

% ============================================================
\section{Refinement~1: Accuracy of the Koide formula}
% ============================================================

\subsection*{Affected documents}

Doc.~116 (abstract, l.\,14): $\Delta Q < 0{,}00003\,\%$ \\
Doc.~158 (abstract): ``experimentally confirmed to $0{,}001\,\%$''

\subsection*{Correct placement}

The Koide relation
\begin{equation}
  Q \;=\; \frac{m_e + m_\mu + m_\tau}
               {(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2}
  \;=\; \frac{2}{3}
  \tag{190.7}
\end{equation}
is experimentally confirmed to better than $0{,}001\,\%$ (PDG values 2022). The
figure $< 0{,}00003\,\%$ in Doc.~116 refers to the internal consistency of the
T0 formulas, not to the experimental measurement uncertainty. Both statements
are correct in content but are different quantities. In external communication
$0{,}001\,\%$ is the appropriate figure.

\subsection*{Note}

The T0 individual masses agree with experiment to $\sim 1\,\%$; the high
precision of $Q = 2/3$ arises from the specific algebraic structure of the
Koide combination, not from individual mass accuracy.

% ============================================================
\section{\texorpdfstring{Refinement~2: $\hbar$ from the Higgs field -- derivation chain}{Refinement 2: hbar from the Higgs field -- derivation chain}}
% ============================================================

\subsection*{Context}

The Planck constant $\hbar$ is derived differently in various documents. Here
the complete, consistent derivation chain is recorded.

\subsection*{Authoritative derivation chain}

\begin{equation}
  \xi \;=\; \frac{\lambda_h^2 v^2}{16\pi^3 m_h^2}
  \;\longrightarrow\;
  L_0 \;=\; \xi \cdot \ell_P
  \;\longrightarrow\;
  \hbar \;\sim\; \sqrt{\xi}\cdot \ell_P \cdot c
  \tag{190.8}
\end{equation}

The time-mass binding condition provides the physical justification:
\begin{equation}
  T(x,t)\cdot m(x,t) \;=\; 1
  \quad\Longrightarrow\quad
  T \;=\; \frac{\hbar}{m\, c^2}
  \quad\Longrightarrow\quad
  E \;=\; \hbar\omega.
  \tag{190.9}
\end{equation}

$h = 2\pi\hbar$ is thereby \emph{not} a free constant but a geometric
consequence of $\xi$ and $\ell_P$. The numerical SI value
$h \approx 6{,}626 \times 10^{-34}\,\text{J·s}$ is the calibration result of
this relation onto the SI base units.

% ============================================================
\section{\texorpdfstring{Refinement~3: Two $\xi$ parameters -- two different spaces}{Refinement 3: Two xi parameters -- two different spaces}}
% ============================================================

\subsection*{Context}

In Docs.~173--176 (quantum dots, spin qubits, qubit state spaces, Shor
algorithm) two numerically different $\xi$ values appear. Earlier documents did
not keep them consistently separate, which can cause confusion.

\subsection*{Authoritative distinction}

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{2.4cm}p{2.0cm}p{2.4cm}p{3.0cm}}
\toprule
\textbf{Parameter} & \textbf{Value} & \textbf{Domain} & \textbf{Meaning} \\
\midrule
$\xi_0$ \newline (geometric) &
$\dfrac{4}{30000}$ \newline $\approx 1{,}33 \times 10^{-4}$ &
3D geometric space &
length hierarchy of the torus; holds in physical position space \\[6pt]
$\xi_{\text{Higgs}}$ \newline (algebraic) &
$\approx 1{,}04 \times 10^{-5}$ &
number / quantum state space &
algebraic field corrections; Higgs sector; decoherence rates \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\subsection*{Justification}

$\xi_0 = 4/30000$ follows from the torus geometry of physical space (geometric
derivation, independent of SI measurements). $\xi_{\text{Higgs}}$ follows from
the algebraic Higgs field structure and appears in coupling formulas between
quantum states (e.g.\ Bell correlations, $T_2$ hierarchy).

\textbf{The two $\xi$ values are not a contradiction}, but describe
complementary aspects: geometry of space ($\xi_0$) vs.\ algebra of the state
space ($\xi_{\text{Higgs}}$). In external communication it must always be made
clear which parameter is meant.

% ============================================================
\section{\texorpdfstring{Refinement~4: $L_0$ and the Schwarzschild interpretation}{Refinement 4: L0 and the Schwarzschild interpretation}}
% ============================================================

\subsection*{Affected documents}

Older versions of Docs.~180--182 (Lagrangian derivation, torus geometry,
maximal universe scale).

\subsection*{Erroneous approach}

Earlier versions interpreted $L_0 = \xi_0 \cdot \ell_P$ as the Schwarzschild
radius of a fundamental minimal entity. This interpretation was explicitly
discarded in Doc.~182 (2026 revision).

\subsection*{Correct placement}

$L_0$ is exclusively the \textbf{geometric fundamental length} of the FFGFT
torus:
\begin{equation}
  L_0 \;=\; \xi_0 \cdot \ell_P \;\approx\; 2{,}15 \times 10^{-39}\,\text{m}.
  \tag{190.10}
\end{equation}
It defines the lowest scale level of the $\xi$ hierarchy and has \emph{no}
Schwarzschild interpretation. The cosmological Hubble radius $R_H$ is the
system-specific upper bound of the cosmological sector -- not a universal
maximal size. Every scale has its own system-specific upper bound.

\subsection*{Remark: Schwarzschild as a consistency check}

The Schwarzschild connection remains valid as an \textbf{internal consistency
check}: an object with mass $M_0 = \xi_0 \cdot m_P / 2$ would have a
Schwarzschild radius of exactly $L_0$ -- without a free parameter. If $M_0$
matches a scale level of the $\xi$ hierarchy, that is a nontrivial
self-consistency test. The connection is \emph{a probe, not a derivation}.

% ============================================================
\section{Refinement~5: Claim and scope of the mass formulas}
% ============================================================

\subsection*{Context}

Several FFGFT documents describe mass derivations for leptons and other
particles. The claim of these derivations must be communicated clearly.

\subsection*{Authoritative formulation}

The FFGFT mass formulas (e.g.\ $m_\ell = r_\ell \cdot \xi^{p_\ell} \cdot v$)
yield values that agree with experiment to $\sim 1\,\%$. This is \textbf{not a
precision calculation} but a structural proof:

\begin{itemize}
  \item The mass formulas \emph{follow geometrically} from $\xi$ and $v$ --
    they are not fitted.
  \item The remaining $\sim 1\,\%$ deviations reflect measurement
    uncertainties and approximations, not errors of the structure.
  \item Numerically better calculations than the Standard Model are
    \emph{not} claimed.
\end{itemize}

In external texts the following is to be avoided: ``FFGFT computes the masses
exactly.'' Correct is: ``FFGFT \emph{derives} the mass structure from a single
parameter $\xi$ and reproduces the orders of magnitude to $\sim 1\,\%$.''

% ============================================================
\section{Refinement~6: Koide formula only with original values}
% ============================================================

\subsection*{Authoritative rule}

The Koide relation
\begin{equation}
  Q = \frac{m_e + m_\mu + m_\tau}{(\sqrt{m_e}+\sqrt{m_\mu}+\sqrt{m_\tau})^2} = \frac{2}{3}
  \tag{190.11}
\end{equation}
may only be evaluated with experimentally measured masses (PDG values).

\textbf{Not admissible:} inserting the symbolic FFGFT terms
$r_\ell \cdot \xi^{p_\ell} \cdot v$ directly into the formula. The
$\sqrt{m_i}$ operation generates cross terms with mixed $\xi$ powers that are
foreign to the torus structure space. Any such insertion yields
$Q \approx 0{,}6677 \neq 2/3$ and is not a contradiction to the theory but a
category error.

\textbf{Admissible:} evaluate the FFGFT terms numerically (e.g.\
$m_\tau = 1783\,\text{MeV}$) and insert this result into the Koide formula like
a measured value.

\textbf{Mathematical background:} The $r_\ell$ terms are geometric invariants
of their torus modes. The set of admissible pairs $(r_i, p_i)$ is not closed
under multiplication: $r_e \cdot r_\mu = 64/15$ belongs to no torus mode. This
is the non-closure theorem (Doc.~193). The general analysis of the composition
limits is found in Doc.~192.

% ============================================================
\section{\texorpdfstring{Refinement~7: Terminology \enquote{renormalization group} and scale structure}{Refinement 7: Terminology renormalization group and scale structure}}
% ============================================================

\subsection*{Affected documents}

\begin{itemize}
  \item Doc.~005 (T0-tm extension): \enquote{RG flow}, \enquote{renormalization-group factor},
        \enquote{renormalization-group invariance},
        subsection \enquote{renormalization-group treatment}.
  \item Doc.~008 ($\xi$ and $e$): subsection \enquote{modified
        renormalization-group equations}.
  \item Doc.~019 (T0 Lagrangian, older version):
        subsection \enquote{renormalization-group equations}.
  \item Doc.~086 (document overview): \enquote{renormalization group as a flow
        in parameter space}.
  \item Doc.~189 (torus derivation): \enquote{cumulative
        renormalization-group running}.
  \item Doc.~202 (FFGFT field theory, overall), \S 18:
        section title \enquote{The renormalization group}.
\end{itemize}

\subsection*{Previous formulation}

In the documents named, the $\xi_0$-modified scale running of the coupling
\begin{equation}
  \frac{d\alpha}{d\ln\mu}
  = \beta_0\,\alpha^2\!\left(1 + \xi_0\,\ln\tfrac{\mu}{E_0}\right)
  \tag{old -- imprecise}
\end{equation}
and the associated scale dependence are called the \emph{renormalization
group}, at times in immediate proximity to statements that characterize
$\xi_0$ explicitly as a topologically fixed geometric constant.

\subsection*{Refined formulation}

In FFGFT the scale dependence of the coupling is \emph{not} the result of a
renormalization procedure but a direct consequence of the recursion
$\mathcal{R}$ (Doc.~203) on the fractal torus geometry. The correct designation
is therefore:

\begin{equation}
  \boxed{\;
  \begin{aligned}
    &\text{scale structure from the recursion} \\
    &\quad\equiv\; \text{recursive $\alpha$ running via $\mathcal{R}$}
  \end{aligned}
  \;}
  \tag{190.12}
\end{equation}

Concretely:
\begin{itemize}
  \item The term $\xi_0\,\ln(\mu/E_0)$ arises from the iterated application of
        the recursion $\mathcal{R}$ to the mode structure, not from a
        counter-term subtraction.
  \item $\xi_0$ is \emph{not} a fixed point of a $\beta$ function but a
        topologically fixed constant ($\xi_0 = 4/30000$, Doc.~180).
  \item Stability, scale flow and UV finiteness are three aspects of the
        \emph{same} recursive structure -- not separate mechanisms.
\end{itemize}

\subsubsection*{Language convention}

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Avoid} & \textbf{Use} \\
\midrule
renormalization group \newline
{\scriptsize(implies a QFT procedure)} &
  scale structure from the recursion \\[6pt]
RG flow / RG running &
  recursive $\alpha$ running; \newline
  $\mathcal{R}$-induced scale correction \\[6pt]
renormalization-group equations &
  scale equations from $\mathcal{R}$ \\[6pt]
renormalization-group invariance &
  recursive scale invariance \\[6pt]
renormalization-group fixed point &
  fixed point of the recursion: \newline
  $\mathcal{R}(\Phi_*) = \Phi_*$ \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\subsection*{Justification}

The designation \enquote{renormalization group} imports a tool of standard
quantum field theory that rests on a completely different principle: there, UV
divergences are absorbed by a procedure, and the parameters \emph{run} under a
formal scale transformation. In FFGFT neither the divergence problem (cf.\
Doc.~159, \enquote{without artificial renormalization}) nor a free scale
parameter to be absorbed exists. The scale dependence is a \emph{structural
property} of the recursion, not a subsequent adjustment step.

The FFGFT-native view is already correctly formulated in Doc.~159
(\enquote{renormalization as a symptom, not a solution}) and Doc.~189
(\enquote{geometrically determined, not by renormalization}); this refinement
serves the uniform terminology across the older Lagrangian and $\xi$-derivation
series (Docs.~005, 008, 019) as well as across Doc.~202.

The underlying mechanism is worked out in Doc.~203 (recursion operator
$\mathcal{R}$) and Doc.~204 (fractal boundary condition).

% ============================================================
\section{\texorpdfstring{Refinement~8: Terminology \enquote{fractal renormalization}}{Refinement 8: Terminology fractal renormalization}}
% ============================================================

\subsection*{Affected documents}

Docs.~005, 008, 012, 014 (with 19~occurrences the most frequent source),
041, 060, 133, 141, 159, 181.

\subsection*{Previous formulation}

\enquote{Fractal renormalization} is used as an FFGFT-internal term for the
geometric correction factors in the conversion between natural and SI units as
well as for scale-dependent corrections on the fractal torus.

\subsection*{Refined formulation}

Since the word \enquote{renormalization}, even in compound form, carries the
QFT connotation of a subtraction or adjustment procedure, the term is replaced
by context-specific alternatives:

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Context} & \textbf{Authoritative designation} \\
\midrule
unit conversion \newline
natural $\leftrightarrow$ SI \newline
{\scriptsize(esp.\ Doc.~014)} &
  geometric scale adjustment \\[8pt]
scale-dependent corrections \newline on the fractal torus \newline
{\scriptsize(Docs.~133, 159, 181)} &
  fractal correction \newline
  {\scriptsize (matches the title of Doc.~133)} \\[8pt]
general scale transformation \newline by recursion &
  $\mathcal{R}$-induced \newline
  scale correction \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\subsection*{Justification}

The internal term \enquote{fractal renormalization} was meant to set the
procedure clearly apart from QFT renormalization, but it adopts the central
word and with it inevitably the connotation of a \emph{correction procedure}.
In FFGFT it is not a procedure but the direct numerical manifestation of the
fractal geometry. The proposed alternatives avoid this misunderstanding
without new terminology -- both phrasings are already established in the corpus
(Doc.~133 \enquote{fractal correction}; \enquote{geometric scale adjustment}
in the same semantic field as Doc.~014).

% ============================================================
\section{\texorpdfstring{Refinement~9: Column \enquote{symmetry} and the term \enquote{color charge} in the fermion tables}{Refinement 9: Column symmetry and the term color charge in the fermion tables}}
% ============================================================

\subsection*{Affected documents}

\begin{itemize}
  \item Doc.~006 (T0 particle masses), \enquote{universal table of fermions},
        column \enquote{symmetry}.
  \item Doc.~046 (Particle Masses, English parallel version), same table,
        column \enquote{color}.
  \item Doc.~042 ($\xi$ parameter and particles), table
        \enquote{spatial field patterns}, entry
        \enquote{quarks: multi-node bound clusters, confined, color charge}.
  \item Doc.~005 (T0-tm extension), method~2 \enquote{extended fractal method
        with QCD integration}: use of $N_c = 3$, $\alpha_s$,
        $\Lambda_{\text{QCD}}$ as external inputs.
\end{itemize}

\subsection*{Previous formulation}

In the fermion tables of Doc.~006/046 each row carries a column
\enquote{symmetry} with the following entries:
\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{ll}
\toprule
\textbf{Particle} & \textbf{Entry in \enquote{symmetry}} \\
\midrule
electron, muon, tau                  & lepton number \\
$\nu_e$, $\nu_\mu$, $\nu_\tau$       & double-$\xi$ \\
up, charm, strange, top, bottom      & color \\
down                                  & color + isospin \\
\bottomrule
\end{tabular}%
}
}
\end{center}

This mixture combines four different concepts in one column: an FFGFT scaling
class (\enquote{double-$\xi$}), an SM conserved quantity (\enquote{lepton
number}), an SM gauge symmetry (\enquote{color}) and an SM quantum number
(\enquote{isospin}). In addition, the entries \enquote{color charge} in
Doc.~042 and $N_c = 3$ in Doc.~005 suggest that the SM color symmetry
$SU(3)_C$ is an independent component of FFGFT.

\subsection*{Refined formulation}

In FFGFT neither the gauge group $SU(3)_C$ nor a color quantum number exists.
Quark masses follow, just like lepton masses, exclusively from the Yukawa
resonance formula
\begin{equation}
  m_f \;=\; r_f \cdot \xi^{p_f} \cdot v
  \tag{190.13}
\end{equation}
with $r_f$ a rational prefactor and $p_f$ a rational exponent (step size
$\Delta p = 1/3$). This is numerically substantiated by the script
\texttt{calc-resonanz-leiter.py}: all six quarks hit their PDG masses to
$\sim 0{,}3\text{--}3{,}4\,\%$, \emph{without} use of $N_c$, $\alpha_s$,
$\Lambda_{\text{QCD}}$ or a color quantum number.

\subsubsection*{Corrected column structure of the fermion table}

The old column \enquote{symmetry} is replaced by two clearly separated columns:

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{2.4cm}p{3.6cm}p{4.0cm}}
\toprule
\textbf{Particle} & \textbf{FFGFT scaling class}
                  & \textbf{SM correspondence \newline (informative)} \\
\midrule
electron, muon, tau              & single-$\xi$  & lepton number \\
$\nu_e$, $\nu_\mu$, $\nu_\tau$    & double-$\xi$   & lepton number, lepton mixing \\
up, charm, top                   & cluster-$\xi$  & up-type, $T_3 = +1/2$ \\
down, strange, bottom            & cluster-$\xi$  & down-type, $T_3 = -1/2$ \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\textbf{Meaning of the classes:}
\begin{itemize}
  \item \emph{single-$\xi$}: $m = r\,\xi^p\,v$ with $p \in \{2/3, 1, 3/2\}$.
  \item \emph{double-$\xi$}: $m_\nu = r_\nu\,\xi^2\,m_e$
        (additional $\xi$ suppression relative to the charged leptons).
  \item \emph{cluster-$\xi$}: $m = r\,\xi^p\,v$ with the same exponents
        $p \in \{-1/3, 1/2, 2/3, 1, 3/2\}$ as for the leptons, but with
        multi-node binding in the sense of Doc.~049 (cubic self-interaction
        $\lambda_s\,(\delta m_q)^3$).
\end{itemize}

\subsubsection*{Language convention for quarks}

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{4.0cm}p{4.5cm}}
\toprule
\textbf{Avoid} & \textbf{Use} \\
\midrule
\enquote{color charge}\newline
{\scriptsize(implies an SU(3)$_C$ quantum number)} &
  multi-node binding \\[6pt]
\enquote{three colors red/green/blue}\newline
{\scriptsize(SM gauge index)} &
  triple-node cluster \newline
  {\scriptsize (the triplet is geometry, not an $SU(3)$ index)} \\[6pt]
\enquote{$N_c = 3$ colors} &
  $N_{\text{cluster}} = 3$ \newline
  {\scriptsize (geometric node count in the baryon)} \\[6pt]
\enquote{color confinement} &
  cluster binding \newline
  {\scriptsize (cubic self-interaction)} \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\subsection*{Status of Doc.~005, method~2}

Doc.~005 contains two calculation methods:
\begin{itemize}
  \item \emph{Method~1: direct geometric method.} Yukawa form per
        Eq.~(190.13); parameter-free; accuracy $\sim 1\,\%$ for all fermions.
        \textbf{This is the FFGFT method.}
  \item \emph{Method~2: extended fractal method with QCD integration.} Uses
        $N_c$, $\alpha_s$, $\Lambda_{\text{QCD}}$, lattice-QCD calibration and
        ML. \textbf{This is a phenomenological bridge construction} for linking
        to the lattice-QCD literature, not part of the parameter-free FFGFT.
\end{itemize}

In external communication method~1 is to be cited. Method~2 may be used if
explicitly labelled as a \enquote{bridge to lattice QCD} or
\enquote{ML-calibrated extension}.

\subsection*{Justification}

The designations \enquote{color}, \enquote{color charge}, \enquote{$N_c$}
import a concept of standard quantum field theory ($SU(3)_C$ as a gauge
symmetry, three colors, eight gluons, color confinement as a non-perturbative
property). Doc.~049 states explicitly that FFGFT contains none of these
elements: \enquote{what we call ,color' becomes high-energy node-binding
patterns} (Doc.~049, §3.7), with a single cubic interaction term
$\lambda_s\,(\delta m_q)^3$ instead of eight gluon fields.

The script validation (\texttt{calc-resonanz-leiter.py}, \texttt{calc\_De.py})
shows: all quark masses follow from the same Yukawa formula as the leptons. The
column \enquote{symmetry} of the fermion table, by contrast, suggests that
$SU(3)_C$ is a distinguishing property of the quarks within FFGFT -- which is
not the case.

The corrected column structure separates the FFGFT-internal
(\emph{scaling class}) from the informative SM link (\emph{SM correspondence}),
parallel to the separation of \enquote{recursive $\alpha$ running} and
\enquote{renormalization group} in Refinement~7.

% ============================================================
\section{\texorpdfstring{Refinement~10: Logical status of $K = 245$ and the factor $1{,}314$ in Doc.~009}{Refinement 10: Logical status of K = 245 and the factor 1.314 in Doc. 009}}
% ============================================================

\subsection*{Affected document}

Doc.~009 (origin of $\xi$), section \enquote{why $K = 245$ is fundamental},
subsection \enquote{geometric meaning}.

\subsection*{Misleading presentation}

Doc.~009 lists the following derivation chain for $K = 245$:
\begin{itemize}
  \item $\varphi^{12} = 321{,}996$
  \item correction by the fractal structure: $(1-\xi)^2 \approx 0{,}999733$
  \item result: $321{,}996 \times 0{,}999733 \approx 321{,}87$
  \item \enquote{scaling to the mass range}: $321{,}87 / 1{,}314 \approx 245$
\end{itemize}
The factor $1{,}314$ appears without derivation or independent physical
justification.

\subsection*{Correct logical order}

$K = 245$ is \emph{not} derived from $\varphi^{12}$ and $1{,}314$. The correct
logical order is the reverse:

\begin{equation}
  K \;=\; \frac{R_{pe}}{(4/3)^\kappa}
    \;=\; \frac{1836{,}153}{(4/3)^7}
    \;\approx\; 245{,}097
  \tag{190.14}
\end{equation}

$K$ is fixed by the observed proton-electron mass ratio $R_{pe}$ and the
exponent $\kappa = 7$. It is an \emph{empirical anchor}, not a result from
first principles. The factor $1{,}314$ is defined implicitly as
$\varphi^{12} / 245 \approx 1{,}314$ and does not constitute an independent
derivation of $K$.

\subsection*{What remains non-trivial}

The exponent $\kappa = 7$ is the \emph{only integer} for which the complete
e-p-$\mu$ triangle closes simultaneously:
\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{lcc}
\toprule
$\kappa$ & $K \times (4/3)^\kappa$ & agreement with $R_{pe}$ \\
\midrule
6 & 1376{,}6 & $-25\,\%$ \\
7 & 1835{,}4 & $\checkmark\; 0{,}04\,\%$ \\
8 & 2447{,}2 & $+33\,\%$ \\
\bottomrule
\end{tabular}%
}
}
\end{center}
This uniqueness is a real condition, not a tautology. $K = 245$ then follows
from $\kappa = 7$ and the empirical $R_{pe}$.

\subsection*{Corrected formulation for external communication}

\begin{itemize}
  \item \textbf{Avoid:} \enquote{$K = 245$ is derived from first principles;
        no free parameters.}
  \item \textbf{Use:} \enquote{An empirical anchor: $K = 245$, fixed by
        $R_{pe}$ and $\kappa = 7$. From this anchor follow five mass ratios
        with ${<}\,0{,}04\,\%$ accuracy. The $\varphi^{12}$ observation is a
        numerological consistency note, not a derivation.}
\end{itemize}

% ============================================================
\section{\texorpdfstring{Refinement~11: $T_\text{CMB}$ correction factor and $K_\text{frac}$ clarification}{Refinement 11: T\_CMB correction factor and K\_frac clarification}}
% ============================================================

\subsection*{Affected documents}

Doc.~025 (cosmology), Doc.~003 (foundations), Doc.~133 (fractal correction derivation).

\subsection*{Problem A: $K_\text{frac}$ does not close the $T_\text{CMB}$ gap}

Doc.~025 derives:
\begin{equation}
  T_\text{CMB} \;=\; \tfrac{16}{9}\,\xi \;=\; \tfrac{4}{16875}\;\text{eV}
  \;\approx\; 2{,}7507\;\text{K}
  \tag{190.15}
\end{equation}
The measured value is $T_\text{CMB} = 2{,}72548\,\text{K}$ (Planck 2018). The
gap is $\approx 0{,}925\,\%$.

$K_\text{frac} = 1 - 100\xi = 74/75$ (Doc.~133) does \emph{not} close this gap.
Numerically:
\begin{equation}
  \tfrac{16}{9}\,\xi \times K_\text{frac} \;=\; 2{,}714\;\text{K}
  \quad (0{,}42\,\% \text{ below the target value, worse})
  \tag{190.16}
\end{equation}
The required correction factor is $0{,}99083$, achieved by the following
formula:
\begin{equation}
  \boxed{
    T_\text{CMB} \;=\; \tfrac{16}{9}\,\xi\,\Bigl(1 - \tfrac{275}{4}\,\xi\Bigr)
    \;=\; 2{,}725486\;\text{K}
  }
  \tag{190.17}
\end{equation}
Agreement with the measured value: $\Delta = 0{,}0002\,\%$.

The coefficient $275/4 = 68{,}75$ lies close to the tetrahedral number
$68 = 72 - 4$ (Doc.~003, section~0.5), but its derivation as a second-order
correction is not yet formally established. \textbf{This is an open point:} a
geometric derivation of $275/4$ is required. The formula above is a numerically
verified result that still requires a complete justification.

\subsection*{Problem B: two inconsistent $K_\text{frac}$ definitions}

Doc.~003 gives:
\begin{equation}
  K_\text{frac}^\text{(003)} \;=\; 1 - \frac{D_\text{frac} - 2}{68}
  \;=\; 1 - \frac{0{,}94}{68} \;\approx\; 0{,}98530
  \tag{190.18}
\end{equation}
where $D_\text{frac} = 2{,}94$ is given without derivation from $\xi$.

Doc.~133 gives:
\begin{equation}
  K_\text{frac}^\text{(133)} \;=\; 1 - 100\xi \;=\; \tfrac{74}{75}
  \;\approx\; 0{,}98667
  \tag{190.19}
\end{equation}
derived from the cumulative RG running with $D_f = 3 - \xi$.

These values differ by $1{,}37 \times 10^{-3}$ and cannot both be correct. The
\textbf{primary definition} is Doc.~133: $K_\text{frac} = 1 - 100\xi = 74/75$.
The value $D_\text{frac} = 2{,}94$ in Doc.~003 is an independent approximation
not derived from $\xi$; it uses a different (tetrahedral) model. Doc.~003 is to
be understood as a heuristic motivation, not as a defining formula.

\subsection*{Corrected formulation for $T_\text{CMB}$}

\begin{itemize}
  \item \textbf{Avoid:} \enquote{$K_\text{frac}$ closes the $T_\text{CMB}$
        gap.}
  \item \textbf{Use:} \enquote{$T_\text{CMB}$ requires a second-order
        correction $(1 - 275/4\cdot\xi)$ that yields $0{,}0002\,\%$ agreement.
        The geometric origin of $275/4$ is still open.}
\end{itemize}

\subsection*{Addendum: $\Delta\text{CHSH} \approx 10^{-5}$ in Doc.~230}

Doc.~230 claims $\Delta\text{CHSH} \approx 10^{-5}$ as a geometrically
motivated prediction. Doc.~022 gives the formula

\begin{equation}
  \text{CHSH}(N) \;=\; 2\sqrt{2}\cdot\exp\!\left(-\xi\,\frac{\ln N}{D_f}\right)
  \tag{190.20}
\end{equation}

where $N$ is the number of measurement runs. This formula yields
$\Delta\text{CHSH} \approx 5\times10^{-4}$ at $N=73$ (not $10^{-5}$).
$\Delta\text{CHSH}$ grows monotonically with $N$; at $N=2$ (minimum) one
already obtains $\Delta\text{CHSH} \approx 8{,}7\times10^{-5}$. The value
$10^{-5}$ from Doc.~230 is not attainable at any finite $N$ under the Doc.~022
formula.

\textbf{Important distinction} (Onur Teker, May 2026): $\text{CHSH}(N)\to 0$
(correlation vanishes) requires $N\to\infty$ and is a different condition from
$\Delta\text{CHSH}=10^{-5}$ (distance from the Tsirelson bound). Both
conditions confirm that the Doc.~022 formula cannot reproduce the Doc.~230
value. The prediction $\Delta\text{CHSH}\approx 10^{-5}$ requires a separate
derivation or a suppression mechanism that is not yet documented.
\textbf{Open point.}

% ============================================================
\section{\texorpdfstring{Refinement~12: Two different $\Delta\text{CHSH}$ observables in Doc.~022 and Doc.~230}{Refinement 12: Two different CHSH observables}}
% ============================================================

\subsection*{Affected documents}

Doc.~022 (QFT-ML addendum), Doc.~230 (Hilbert-space translation).

\subsection*{The apparent contradiction}

Doc.~022 gives $\Delta\text{CHSH} \approx 5\times10^{-4}$ at $N=73$ via the
formula $\text{CHSH}(N) = 2\sqrt{2}\cdot\exp(-\xi\ln N/D_f)$. Doc.~230 claims
$\Delta\text{CHSH} \approx 10^{-5}$ without derivation. These values differ by
a factor of $\sim50$.

\subsection*{Possible resolution: cumulative vs.\ elementary deviation}

The two values refer to different observables:

\begin{itemize}
  \item \textbf{Doc.~022} describes the \emph{cumulative} deviation over $N$
        measurement runs. It grows monotonically with $N$:
        $\Delta\text{CHSH}(N) \sim \xi\ln(N)/D_f \times 2\sqrt{2}$. This is the
        experimentally relevant quantity for a Bell test with $N$ runs.

  \item \textbf{Doc.~230} plausibly refers to the \emph{elementary} deviation
        per single measurement -- the phase cost of one $\theta_4$ projection
        cycle. The natural candidate is:
        \begin{equation}
          \Delta\text{CHSH}_\text{elem}
          \;=\; \frac{\xi}{2\pi}
          \;\approx\; 2{,}1\times10^{-5}
          \;\approx\; 10^{-5}
          \tag{190.21}
        \end{equation}
        These are the Landauer costs per measurement expressed as a CHSH
        deviation: the $\theta_4$ phase runs through a full $2\pi$ cycle per
        measurement, and each cycle costs $\xi$ in geometric units.
\end{itemize}

The ratio between cumulative and elementary deviation at $N$ runs:
\begin{equation}
  \frac{\Delta\text{CHSH}(N)}{\Delta\text{CHSH}_\text{elem}}
  \;\approx\; N\cdot\frac{2\pi}{D_f}
  \tag{190.22}
\end{equation}
At $N=73$ this gives a factor of $\approx 153$, consistent with the observed
factor of $\sim50$--$100$ between the two values.

\subsection*{Status}

This resolution is a \textbf{working hypothesis}, not a proven derivation. The
identification $\Delta\text{CHSH}_\text{elem} = \xi/(2\pi)$ requires a formal
justification from the T⁴ projection geometry. If confirmed, there is no
contradiction between Doc.~022 and Doc.~230 -- they describe the same physical
effect at different integration scales.

\textbf{Experimental consequence:} The cumulative deviation
$\Delta\text{CHSH}(N) \approx 5\times10^{-4}$ at $N=73$ is within reach of
future loophole-free Bell tests (current resolution $\sim10^{-2}$; required
improvement: factor $\sim20$). The elementary deviation
$\xi/(2\pi) \approx 2\times10^{-5}$ would require single-shot precision beyond
current technology.

% ============================================================
\section{Refinement~13: Bridge formula between $\xi_\text{FFGFT}$ and $\xi_\text{UIFT}$}
% ==============================================================================

\subsection*{Context}

In the IPI discussion (May 2026) Onur Teker (UIFT) writes:
\begin{quote}
$\xi = k_B T_\text{CMB} \ln 2 / (m_e c^2)$, derived from three independent
measurements ($T_\text{CMB}$, $k_B$, $m_e$). This is not a hyperparameter --
it is a prediction.
\end{quote}

This identifies $\xi_\text{UIFT}$ with $\xi_\text{FFGFT} = 4/30000$.
Numerically they differ considerably. This refinement documents the exact
relation.

\subsection*{The key: FFGFT uses eV as the temperature unit}

In FFGFT the natural unit system $\hbar = c = k_B = 1$ holds. Temperatures are
expressed in eV (not in Kelvin):
\begin{equation}
  \resizebox{\textwidth}{!}{$\displaystyle T_\text{CMB}[\text{eV}] \;=\; k_B \cdot T_\text{CMB}[\text{K}] \;=\; k_B \cdot 2{,}72548\,\text{K} \;=\; 2{,}3486 \times 10^{-4}\,\text{eV}$}
  \tag{190.23}
\end{equation}

The FFGFT formula (Doc.~025) then reads -- to first order:
\begin{equation}
  T_\text{CMB}[\text{eV}] \;=\; \frac{16}{9}\,\xi_\text{FFGFT}
  \;=\; 2{,}3704 \times 10^{-4}\,\text{eV}
  \qquad (\Delta = 0{,}93\,\%)
  \tag{190.24}
\end{equation}

and to second order (Doc.~190 R11):
\begin{equation}
  \resizebox{\textwidth}{!}{$\displaystyle T_\text{CMB}[\text{eV}] \;=\; \frac{16}{9}\,\xi_\text{FFGFT} \!\left(1 - \frac{275}{4}\,\xi_\text{FFGFT}\right) \;=\; 2{,}3486 \times 10^{-4}\,\text{eV} \qquad (\Delta = 0{,}0002\,\%)$}
  \tag{190.25}
\end{equation}

\subsection*{Bridge formula}

Inserting (190.24) into Onur's expression (first order):
\begin{align}
  \xi_\text{UIFT}
  &= \frac{k_B\,T_\text{CMB}[\text{K}]\,\ln 2}{m_e c^2}
  = \frac{T_\text{CMB}[\text{eV}]\cdot\ln 2}{m_e c^2 / \text{eV}}
  \notag\\[4pt]
  &= \frac{\dfrac{16}{9}\,\xi_\text{FFGFT}\cdot\ln 2}{m_e c^2/\text{eV}}
  \tag{190.26}
\end{align}

Rearranged:
\begin{equation}
  \boxed{
  \frac{\xi_\text{FFGFT}}{\xi_\text{UIFT}}
  \;=\;
  \frac{m_e c^2/\text{eV}}{\dfrac{16}{9}\cdot\ln 2}
  \;=\;
  \frac{510\,999\,\text{eV}}{1{,}2323\,\text{eV}}
  \;\approx\; 414\,684
  }
  \tag{190.27}
\end{equation}

\subsection*{SI conversion table (reconstructed from Doc.~013, archived version)}

The following table was documented in older versions of Doc.~013 (SI
conversions for the natural FFGFT unit system, since shortened). It is
reproduced here because it is essential for the bridge formula.

\begin{center}
\renewcommand{\arraystretch}{1.4}
{\small
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{5.5cm}p{3.5cm}p{3.5cm}}
\toprule
\textbf{Quantity} & \textbf{Nat. units} & \textbf{SI / eV} \\
\midrule
temperature unit $[T]$ & $= [E]$ & 1 eV $= k_B^{-1}\cdot 1\,\text{eV} = 11{,}604\,\text{K}$ \\
$T_\text{CMB}$ [nat.] & $(16/9)\cdot\xi = 2{,}370\times10^{-4}$ & $2{,}370\times10^{-4}$ eV \\
$T_\text{CMB}$ [K] (Planck 2018) & --- & $2{,}72548$ K \\
$T_\text{CMB}$ [eV] $= k_B\cdot T[\text{K}]$ & --- & $2{,}3486\times10^{-4}$ eV \\
$m_e c^2$ & $= m_e$ (nat.) & $510{,}999$ eV $= 0{,}511$ MeV \\
$k_B$ & $= 1$ (nat.) & $8{,}617\times10^{-5}$ eV/K \\
$\hbar$ & $= 1$ (nat.) & $6{,}582\times10^{-16}$ eV·s \\
$c$ & $= 1$ (nat.) & $2{,}998\times10^{8}$ m/s \\
\bottomrule
\end{tabular}%
}
}
\end{center}

\subsection*{Numerical verification}

\begin{center}
\renewcommand{\arraystretch}{1.35}
{\small
\adjustbox{max width=\textwidth}{%
\begin{tabular}{p{6cm}p{4cm}p{3cm}}
\toprule
\textbf{Quantity} & \textbf{Value} & \textbf{Unit} \\
\midrule
$\xi_\text{FFGFT} = 4/30000$ & $1{,}3333\times10^{-4}$ & dimensionless \\
$\xi_\text{UIFT} = k_BT_\text{CMB}\ln2/(m_ec^2)$ & $3{,}1858\times10^{-10}$ & dimensionless \\
ratio $\xi_\text{FFGFT}/\xi_\text{UIFT}$ & $418\,521$ & --- \\
scale factor $m_ec^2/(\frac{16}{9}\ln2)$ [eV] & $414\,684$ & --- \\
$T_\text{CMB}$ [K] (Planck 2018) & $2{,}72548$ & K \\
$T_\text{CMB}$ [eV] $= k_B\cdot T_\text{CMB}[\text{K}]$ & $2{,}3486\times10^{-4}$ & eV \\
$(16/9)\cdot\xi$ [eV] (FFGFT 1st order) & $2{,}3704\times10^{-4}$ & eV \\
$(16/9)\cdot\xi(1-275/4\cdot\xi)$ [eV] (R11) & $2{,}3486\times10^{-4}$ & eV \\
$m_ec^2$ & $510\,999$ & eV \\
\bottomrule
\end{tabular}%
}
}
\end{center}

The residual deviation of $0{,}93\,\%$ between the ratio ($418\,521$) and the
scale factor ($414\,684$) is exactly the first-order T\_CMB error -- this
confirms the correctness of the bridge formula.

\subsection*{Physical interpretation}

$\xi_\text{FFGFT}$ and $\xi_\text{UIFT}$ are \textbf{not the same quantity}.
They are connected by a pure SI conversion factor: the ratio of the
relativistic electron energy ($m_ec^2 = 511\,\text{keV}$) to the eV scale of
the FFGFT temperature formula, modulated by $(16/9)\cdot\ln 2$.

The SI conversion table above was present in older versions of Doc.~013
(archived March 2026, Git commit \texttt{f2be9c8}) and has since been
shortened. The explicit statement
$T_\text{CMB}^\text{nat} = k_B \times 2{,}725\,\text{K} = 2{,}35\times10^{-4}\,\text{eV}$
is found verbatim in that version. The reconstruction here restores the
connection between the natural-unit formula and the SI value, which was
implicitly assumed but no longer shown.

The Vopson-Teker experiment measures $\xi_\text{UIFT}$ directly. If confirmed,
that evidences the thermodynamic ground state at $T_\text{CMB}$ -- not
$\xi_\text{FFGFT} = 4/30000$. The geometric derivation of $\xi_\text{FFGFT}$
from $\kappa = 7$ (Doc.~009) is a separate and independent condition.

% ============================================================
\section{\texorpdfstring{Refinement~14a: Redshift in Doc.~041 -- mechanism instead of energy loss}{Refinement 14a: Redshift in Doc. 041 -- mechanism instead of energy loss}}
% ============================================================

\subsection*{Affected document}

Doc.~041 (parameter derivation), table \enquote{Cosmological Parameters},
LEVEL~3 (redshift) -- in particular the description
\enquote{photon energy loss through $\xi$-field}.

\subsection*{Previous formulation}

The cosmological redshift is labelled in the comparison table as
\enquote{photon energy loss through $\xi$-field} -- i.e.\ as an energy loss of
the photon in the $\xi$ field.

\subsection*{Refined formulation}

The physical mechanism is the \textbf{fractal path lengthening}: the geometric
stretching of the propagation path in the $\xi$ field (torsion lattice), as
derived authoritatively in Doc.~026, Doc.~149 and Doc.~182. The dependence on
the path length $d$ (and the wavelength) remains and is consistent with the
fractal path lengthening -- it is \emph{not} a contradiction.

An \enquote{energy loss} of the photon is \textbf{not an independent
mechanism} but an \emph{apparent artifact}: it would arise only if one
erroneously fails to assume the geometric path lengthening. The wording
\enquote{photon energy loss} in Doc.~041 is therefore to be replaced by
\enquote{fractal path lengthening (geometric path stretching)}; the
\enquote{energy loss} may at most be named explicitly as the artifact that
would arise with the path lengthening omitted.

\subsection*{Justification}

The static FFGFT cosmology explains the redshift purely geometrically
(Doc.~182: \enquote{not by an intrinsic energy loss at the photon, but by
geometric stretching of the propagation path}; \emph{tired light} does not
occur). The comparison table in Doc.~041 abbreviates this mechanism to
\enquote{energy loss} and thereby evokes precisely the tired-light connotation
that FFGFT does not intend. The refinement brings Doc.~041 into line with the
authoritative derivation (Doc.~026/149/182) without changing the path-length
dependence.

\subsection*{Status of incorporation}

\emph{Incorporated (as of 2~June 2026).} Implemented in Doc.~041 (DE+EN).

% ============================================================
\section{\texorpdfstring{Refinement~15: Mark cosmological $z$ as a $\Lambda$CDM comparison quantity}{Refinement 15: Mark cosmological z as a LambdaCDM comparison quantity}}
% ============================================================

\subsection*{Affected documents}

Doc.~061 (temperature units/CMB), section \enquote{modified recombination
history} as well as abstract/summary; Doc.~041 (comparison tables $\Lambda$CDM
vs.\ T0).

\subsection*{Previous formulation}

A $z$-dependent recombination calculation ($z_{\text{rec}}^{T0}\approx 1089{,}5$,
$T(z)=T_0(1+z)[\dots]$) stood as \enquote{In T0 theory recombination occurs
at~\dots} -- i.e.\ as an FFGFT-internal quantity. Likewise \enquote{CMB at
$z\approx 1100$} in the abstract/summary.

\subsection*{Refined formulation}

The static $\xi$ universe has \emph{no} cosmological $z$ in the expansion
sense; FFGFT's redshift is fractal path lengthening, not a scale factor.
Therefore $z$ in these calculations is a \textbf{$\Lambda$CDM pipeline
quantity} and is to be marked explicitly as a \emph{comparison calculation},
not as an FFGFT result. In FFGFT the CMB arises through stationary
thermalization in an infinitely old universe, not through decoupling at some
$z$. In Doc.~061 the section is framed accordingly; the abstract/summary places
are changed to \enquote{without decoupling at any $z$}. In Doc.~041 the
$z=1100$ values are marked as \enquote{($\Lambda$CDM)} (they stand in the
$\Lambda$CDM comparison column anyway).

\subsection*{Justification}

Unmarked comparison calculations create the impression of FFGFT-internal
results and violate the standing caution that cosmological pipeline quantities
($H_0$, $z$, $\Lambda_{\text{obs}}$) must not be presented as FFGFT statements
without labeling. The marking restores the separation without removing the
comparison numbers.

\subsection*{Status of incorporation}

\emph{Incorporated (as of 2~June 2026).} Docs.~061 and 041 (DE+EN) marked.
Further unmarked pipeline comparisons in the corpus are to be checked
separately (ongoing).

% ============================================================
\section{\texorpdfstring{Refinement~16: $H_0$ is emergent (decompactified), not fundamental}{Refinement 16: H0 is emergent, not fundamental}}
% ============================================================

\subsection*{Affected documents}

Doc.~026 (geometric cosmology), l.~116/117 DE+EN; with offshoots in Doc.~064
(l.~104) and Doc.~181 (l.~158). \emph{Already correctly implemented in
Doc.~263} (H$_0$ as an emergent, decompactified quantity); the remaining places
are here only \emph{noted}, not yet changed.

\subsection*{Previous formulation (outdated)}

Doc.~026 calls $H_0$ a \enquote{fundamental constant describing the interaction
of light with the geometry of the T0 vacuum}. This formulation stems from an
earlier state that still understood the redshift as an \emph{energy loss} of
light passing through the vacuum (a near-\enquote{tired light} picture).
Doc.~064 (\enquote{measures energy loss in the $\xi$-field}) and Doc.~181
(\enquote{geometric energy loss}) carry the same remnant.

\subsection*{Refined view}

Two independent reasons argue against treating $H_0$ as a fundamental constant:
\begin{itemize}
  \item \textbf{Energy loss is outdated (cf.\ R14a):} The redshift is fractal
        path lengthening, not energy loss. The \enquote{vacuum as a traversed
        medium} is itself already a decompactified description and not part of
        the compactified $T^4$ view.
  \item \textbf{$H_0$ is emergent, not fundamental:} Doc.~016 records that age,
        critical density and Hubble length are \emph{Friedmann concepts without
        a direct T0 counterpart}; Doc.~262, that $\hbar, \varepsilon_0$ become
        \emph{real only upon decompactification}. Since $H_0 = E_H/\hbar$
        contains the (only then real) $\hbar$, $H_0$ does not exist in the
        compactified $T^4$ form. $H_0$ is an emergent quantity of the
        decompactified description; the non-integer exponent $41/4$ is an
        expression of this scale transition, not a fundamental geometry
        constant. (The integer ansatz $n=10$ in Doc.~165 is therefore to be
        viewed with caution -- it forces an emergent transition quantity into a
        compact geometry.)
\end{itemize}

\subsection*{Status of incorporation}

\emph{Partially incorporated (as of 2~June 2026).} Implemented in Doc.~263
(H$_0$ emergent/decompactified). \textbf{Open:} Doc.~026 (DE+EN, l.~116/117) is
a document that is \emph{outdated} in content (energy-loss/vacuum picture) and
requires a more fundamental revision or a labeling as historical; likewise the
offshoots in Doc.~064/181. Noted as a larger construction site.

% ============================================================
\section{\texorpdfstring{Refinement~17: circular/fit-dependent DE-DM relations in Doc.~028}{Refinement 17: circular DE-DM relations in Doc 028}}
% ============================================================

\subsection*{Affected document}

Doc.~028 (\enquote{7 questions}), sections \enquote{Riddle 4: MOND} and
\enquote{Riddle 5: Dark Energy and Dark Matter}. Only \emph{noted}, not yet
changed.

\subsection*{Finding (recomputed)}

\begin{itemize}
  \item \textbf{DE/DM ratio: circular as a \emph{prediction}, admissible as a
        \emph{conversion}.} Doc.~028 gives $\rho_{\text{DE}}/\rho_{\text{DM}} =
        \xi^{\alpha}$ with $\alpha = \ln(2{,}5)/\ln(\xi)$. Inserting this
        $\alpha$ into $\xi^{\alpha}$ yields \emph{exactly $2{,}5$ for any
        $\xi$} (checked with $\xi = 10^{-3}, 10^{-5}, 0{,}5$). \emph{As a
        prediction} from the $\xi$ geometry the relation is thus circular
        (violates Doc.~101). \emph{But:} the target value $2{,}5$
        ($\Omega_\Lambda/\Omega_{\text{DM}}$) is itself not a model-neutral
        measured value but a $\Lambda$CDM pipeline output (standing caution).
        Reading the relation therefore \emph{not} as a prediction but as a
        \emph{conversion factor} between FFGFT geometry and the
        $\Lambda$CDM-$\Omega$ bookkeeping -- analogous to $c$ (meter/second)
        and to $z$ (cf.\ R15) -- the circular calibration via $2{,}5$ is
        \emph{admissible}. \textbf{Limitation:} unlike $c$ (both sides have the
        same real counterpart), the $\Lambda$CDM side with $\rho_{\text{DE}}$
        contains a model artifact ($\Lambda$ does not exist in FFGFT). The
        factor thus translates partly a real quantity (the DM bookkeeping
        $\leftrightarrow$ $\xi$ effect), partly an artifact
        ($\rho_{\text{DE}}$). Therefore: admissible, but \emph{only of limited}
        informativeness -- as far as the $\Lambda$CDM quantity is artifact-free.
  \item \textbf{The MOND scale is fit-dependent.} $a_0/(cH_0) = \xi^{1/4}\cdot K_M$
        gives the measured value $0{,}176$ only with $K_M = 1{,}637$. The
        $\xi^{1/4} = 0{,}1075$ is genuinely from $\xi$; $K_M$ is a \emph{free
        adjustment factor} without derivation. Partially derived, not
        parameter-free.
  \item \textbf{Two incompatible $a_0$ formulas; rotation curve open.} Besides
        Doc.~028, Doc.~201 (§4.3) gives a \emph{different} form:
        $a_0 = c^2\xi/(4\lambda)\approx 1{,}2\times10^{-10}$\,m/s$^2$. This is
        \emph{not reproducible}: for the correct unit (m/s$^2$) $\lambda$ would
        have to be a \emph{length} ($\sim 2{,}5\times10^{22}$\,m), whereas in
        the rest of Doc.~201 $\lambda$ is via $m_T=\lambda/\xi$ an
        \emph{energy/mass} -- the same symbol in two incompatible meanings.
        Without an independent $\lambda$ value, $a_0$ is either undetermined
        or (backward from the measured value) circular; the length scale
        $2{,}5\times10^{22}$\,m corresponds to no known FFGFT scale.
        \emph{Consequence:} both $a_0$ formulas (028: fit-dependent; 201:
        dimensionally inconsistent) do not carry. The \emph{flat rotation
        curve} follows qualitatively as a MOND consequence of the $\xi$
        geometry (static, without DM substance; Doc.~201/145/156), but the
        concrete profile $v(r)$ and the SPARC comparison are \emph{not worked
        out} -- remains open.
\end{itemize}

\subsection*{Delimitation (what remains valid)}

The CMB relations are \emph{not} affected and remain robust:
$T_{\text{CMB}} = \tfrac{16}{9}\xi^2 E_\xi$ and
$|\rho_{\text{Casimir}}|/\rho_{\text{CMB}} = \pi^2/(240\xi) \approx 308$
contain $\xi$ alone, without a subsequently adjusted exponent or fit factor.

\subsection*{Status of incorporation}

\emph{Noted (as of 2~June 2026), not yet changed.} Recommendation: the DE/DM
ratio (Riddle~5) is to be marked \emph{not} as a prediction but as a limited
conversion factor to the $\Lambda$CDM-$\Omega$ bookkeeping (admissible like
$c/z$, but bounded by the $\rho_{\text{DE}}$ artifact); the MOND scale
(Riddle~4) as partially derived with a free $K_M$. The \emph{interpretation} of
the dark sector is settled -- DM is a $\xi$-geometric effect (an artifact of
the $\Lambda$CDM view, like $H_0$ and $z$), DE is eliminated (no $\Lambda$).
\emph{Quantitatively} it remains open: no model-neutrally derived
$\Omega_{\text{DM}}$, no worked-out rotation curve.

% ==============================================================================
\section{\texorpdfstring{Refinement~14b: CMB anharmonicity, forward vs.\ retrodiction, and the $|n|^2=30$ case (R29/R30/R31)}{Refinement 14b: CMB anharmonicity, forward vs retrodiction}}
% ==============================================================================

An explicit forward investigation (Doc.~268, step~17; scripts
\texttt{Dok268\_Skripte/}) clarified the status of the CMB peak sector and
split it into three points.

\textbf{(1) The direction of the inference (R29).}
The earlier presentation created the impression that $\{1,6,14,26\}$ and hence
$\{3,18,42,78\}$ follow forward from the T$^4$ geometry. In fact
$\{1,6,14,26\}$ is obtained by squaring the \emph{measured} CMB ratios
(Doc.~268, step~4). It is a \textbf{retrodiction} (consistency check), not a
parameter-free prediction. The genuine forward maxima of the full T$^4$
spectrum are dense ($|n|^2=3,6,10,14,18,22,26,30,\ldots$).

\textbf{(2) The $|n|^2=30$ case (R29, sharpened by O.~Teker).}
$30=3\cdot10$ satisfies the factor-3 filter, since $|n|^2=10$ is a local
maximum. Thermally one even has
\[
  I(30)=13{,}2 \;>\; I(42)=7{,}6 \;>\; I(78)=1{,}7,
\]
so $30$ ($\ell\approx696$) would be \emph{stronger} than two visible peaks,
yet shows no peak in the CMB (it lies in the trough between peak~2 and~3). The
earlier argument ``strongest local maximum in the range'' fails here. The
selection mechanism is thus \emph{not} provided by the factor~3 alone.
\emph{Open.}

\textbf{(3) The naive $C_\ell$ Bessel projection is insufficient (R30).}
The calculation $C_\ell=\sum_n N_\mathrm{BE}\,|j_\ell(k_\mathrm{obs}D_A)|^2$
does \emph{not} reproduce $\{3,18,42,78\}$; it washes out to a quasi-continuum
dominated by the lowest modes. The earlier R30 formulation (``a feasible
calculation, no fundamental obstacle'') is withdrawn: a physical
source/window function is missing. \emph{Open.}

\textbf{(4) The forward content -- geometric anharmonicity (new, R31).}
Forward, the symmetric T$^4$ resonance generates the \emph{harmonic} backbone
$1:2:3:4:5$ ($k^2_\mathrm{obs}=3n^2$). The CMB is \emph{anharmonic}
($1:2{,}44:3{,}68:5{,}09$). This anharmonicity follows forward and
parameter-free from the codimension-1 projection:
\[
  D_\mathrm{eff}=D_f-1=2-\xi\approx2
  \;\Rightarrow\;
  \nu=\tfrac{D_\mathrm{eff}}{2}-1=-\tfrac{\xi}{2}\approx0
  \;\Rightarrow\;
  J_0\text{ membrane}
  \;\Rightarrow\;
  1:2{,}30:3{,}60:4{,}90,
\]
matching to $\sim5\%$, \emph{without} mode selection. The radial Bessel index
is $\nu=D/2-1$; the anharmonicity is maximal at $D=2$ and vanishes at $D=1$ and
$D=3$. The CMB sits at the dimension of maximal anharmonicity. The match is to
the \emph{flat} membrane ($J_0$), not to the curved 2-sphere (Y$_{\ell m}$,
gives $1:1{,}73:\ldots$, wrong). This is the conceptually clean, forward-directed
statement; it removes the circularity objection because no selection from data
is needed.

\textbf{(5) The residual deviation -- not from $\xi$.}
The best fit lies at $D\approx1{,}86$ (just below 2). A spectral dimension
$d_s<D_f$ would be the obvious source but fails: the FFGFT fractal is too
weakly fractal ($d_w=2+O(\xi)\Rightarrow d_s\approx2$); for $d_s=1{,}86$ one
would need $d_w\approx2{,}15$ ($\sim1000\times\xi$). The deviation is not
derivable from $\xi$ and is of the order of the measurement uncertainty ($J_0$
is consistent with peaks~3,4 within $\sim2\sigma$; only peak~2 at
$\sim4\sigma$). Pointing to an exact value would be number-juggling.
\emph{Open, presumably partly measurement noise.}

\textbf{Consequence.} The defensible core reads: harmonic T$^4$ backbone
(forward) $+$ geometric anharmonicity from the codimension-1 projection
(forward, $\sim5\%$). The ratio match $\{3,18,42,78\}$ is a retrodiction; the
rigorous single-peak selector and the exclusion of $|n|^2=30$ remain open. The
particle sector ($\alpha$, lepton masses, Koide) is \emph{unaffected} by this
-- it rests on direct $\xi$ powers, not on mode counting.

% ==============================================================================
{\scriptsize
\begin{longtable}{p{0.6cm}p{2.4cm}p{5.5cm}p{5.5cm}}
\toprule
\textbf{No.} & \textbf{Doc.} & \textbf{Erroneous / unclear} & \textbf{Correct / refined} \\
\midrule
\endfirsthead
\multicolumn{4}{c}{\scriptsize\emph{(continued)}}\\
\toprule
\textbf{No.} & \textbf{Doc.} & \textbf{Erroneous / unclear} & \textbf{Correct / refined} \\
\midrule
\endhead
\midrule
\multicolumn{4}{r}{\scriptsize\emph{continued on next page}}\\
\endfoot
\bottomrule
\endlastfoot
C1 & 049 (HTML) &
  $\xi = \lambda_h^2 v^2/(64\pi^4 m_h^2)$ &
  $\xi = \lambda_h^2 v^2/(16\pi^3 m_h^2)$ \\[3pt]
C2 & 116 (tab.) &
  $r_\tau = 8/3$ &
  $r_\tau = 25/9$ \\[3pt]
C3 & 018 (Explorer) &
  $a_e = 4\pi/(f \cdot k)$ &
  $a_e = 2\pi^2/(f \cdot k)$ \\[3pt]
C4 & 267 (DE+EN), \newline 268 (DE) &
  factor~3 interpreted as the fractal dimension $D_f$ (\enquote{fractal dispersion relation $k^2_\mathrm{eff}=D_f\,k^2$}, Doc.~051) &
  \textbf{Factor~3 $=$ three observable space dimensions:} the observer measures $k_\mathrm{obs}^2=(n_1^2+n_2^2+n_3^2)/L^2$ (the fourth torus direction is time unfolding). The conformal metric (Doc.~051) cancels for massless particles; the fractal correction (Doc.~204) is $+0{,}69\,\xi k^2\approx10^{-5}$, \emph{not} the factor~3. $D_f=3-\xi$ is consistent with factor~3 but is not its origin. \emph{Done (267 DE+EN, 268 DE), June 2026} \\[3pt]
C5 & 275 (script v3) &
  Three implementation errors in \texttt{ffgft\_hlv\_gap\_v3.py}:
  (a)~the $T^4$ point lattice used $n_3$ only in the acceptance norm, not in
  the position (729 unique out of 2000 points; the $1/d^2$ clamp produced
  $\lambda_\mathrm{max}=2{,}5{\cdot}10^{12}$) -- the result
  \enquote{gap\_CV $=1{,}68$ outside the band} was an artifact;
  (b)~\texttt{hlv\_points(seed)} did not use the seed -- the
  3-seed \enquote{ensemble} was the same calculation three times;
  (c)~the shell detector for target ratios $<1$ was structurally biased
  (minimum error $(1{,}05/c-1)$; a larger sub-1 ratio wins on every
  point set) -- the discrimination $\Delta=0{,}145$ was structural &
  \textbf{All three fixed in v4} (11~June 2026): $T^4$ as kNN in
  genuine 4D coordinates with dimension-matched 4D nulls (result:
  $1{,}329\pm0{,}025$ \emph{inside} the band $[0{,}690,\,2{,}406]$);
  HLV ensemble with $\sigma=0{,}05$ ($0{,}710\pm0{,}008$, in the band);
  the shell detector raises an exception for targets $\leq1$.
  v3 results in Doc.~275 visibly retracted.
  \emph{Audit: P.~Stoychev (IPI), 11~June 2026} \\[3pt]
R1 & 116 / 158 &
  $\Delta Q < 0{,}00003\,\%$ vs.\ $0{,}001\,\%$ &
  both correct; $0{,}001\,\%$ for external use \\[3pt]
R2 & several &
  $\hbar$ as a postulate &
  $\hbar$ follows from $\xi$ via $L_0 = \xi\cdot\ell_P$ \\[3pt]
R3 & 173--176 &
  a single uniform $\xi$ value &
  two parameters: $\xi_0$ (geom.) and $\xi_{\text{Higgs}}$ (alg.) \\[3pt]
R4 & 180--182 &
  $L_0$ as a Schwarzschild radius &
  $L_0$ = geom.\ fundamental length \\[3pt]
R5 & several &
  \enquote{FFGFT computes masses exactly} &
  mass structure from $\xi$; $\sim 1\,\%$ agreement \\[3pt]
R6 & 116 / 158 &
  Koide with FFGFT symbolic expressions &
  Koide only with numerical values (non-closure, Doc.~193) \\[3pt]
R7 & 005, 008, 019, \newline 086, 189, 202 &
  \enquote{renormalization group} as an FFGFT tool &
  scale structure from the recursion $\mathcal{R}$ \\[3pt]
R8 & 005, 008, 012, \newline 014, 041, 060, \newline 133, 141, 159, 181 &
  \enquote{fractal renormalization} as an internal term &
  geometric scale adjustment / fractal correction \\
R9 & 005, 006, 042, \newline 046 &
  column \enquote{symmetry} with \enquote{color}; \newline
  $N_c = 3$ as an external SM input &
  columns \enquote{scaling class} + \enquote{SM correspondence}; \newline
  quarks via $m = r\,\xi^p\,v$ \\[3pt]
R10 & 009 &
  $K = 245$ from $\varphi^{12}/1{,}314$; \newline
  \enquote{no free parameters} &
  $K = R_{pe}/(4/3)^7$: an empirical anchor; \newline
  factor $1{,}314$ defined implicitly, not derived \\[3pt]
R11 & 025, 003, 133 &
  $K_\text{frac}$ closes the $T_\text{CMB}$ gap; \newline
  one definition of $K_\text{frac}$ &
  correct: $(1-275/4\cdot\xi)$, $\Delta=0{,}0002\,\%$; \newline
  Doc.~003 and Doc.~133 use different models \\[3pt]
R12 & 022, 230 &
  $\Delta\text{CHSH} \approx 10^{-5}$ (Doc.~230) vs.\
  $5\times10^{-4}$ at $N=73$ (Doc.~022) &
  two different observables: cumulative (Doc.~022) vs.\ elementary $\xi/(2\pi)$ (Doc.~230);
  $10^{-5}$ unreachable at any finite $N$ from Doc.~022 \\[3pt]
R13 & 013, 025, 061 &
  $\xi_\text{FFGFT} = \xi_\text{UIFT}$; \newline
  SI conversion table missing &
  $\xi_\text{FFGFT}/\xi_\text{UIFT} = m_ec^2/(\frac{16}{9}\ln 2\cdot\text{eV}) \approx 414\,684$; \newline
  table in Doc.~013 (archived) reconstructed \\[3pt]
R14a & 041 &
  redshift as \enquote{photon energy loss through $\xi$-field} &
  fractal path lengthening (geometric path stretching); energy loss only an artifact when the path lengthening is omitted; path-length dependence remains (Doc.~026/149/182); the same path lengthening carries the CMB treatment in Doc.~268 (formerly tracked separately as R19) \\[3pt]
R15 & 061 / 041 &
  cosmological $z$ ($z\approx 1100$, $z_{\text{rec}}\approx 1089{,}5$) unmarked as an FFGFT quantity &
  marked as a $\Lambda$CDM comparison quantity; the static universe has no cosmological $z$; CMB by stationary thermalization \\[3pt]
R16 & 026 / 064 / 181 &
  $H_0$ as a \enquote{fundamental constant} (energy-loss/vacuum picture) &
  $H_0$ is emergent (decompactified), not fundamental; implemented in Doc.~263, Docs.~026/064/181 noted as outdated \\[3pt]
R17 & 028 &
  DE/DM ratio $\xi^{\ln(2{,}5)/\ln\xi}$ as a prediction; MOND with fit factor $K_M$ &
  the DE/DM relation is circular (gives 2.5 for any $\xi$); MOND partially derived ($\xi^{1/4}$ genuine, $K_M$ free); CMB relations unaffected; noted \\[3pt]
R18 & 267 &
  the relation $\Lambda$CDM expansion vs.\ FFGFT time unfolding treated as an empirical question &
  the two pictures are \emph{not} distinguishable through the observed ratios; the decision is theoretical, not empirical (conceptual placement) \\[3pt]
R20 & 267 / 268 &
  absolute cosmological scale ($R_H$, $D_A$, $z_*$) presented as an FFGFT result &
  the \emph{form} is fixed: a dimensionless $\xi$ ratio ($R_H/\ell_P$). The \emph{factor} (exponent $41/4$, $E_H = E_0\,\xi^{41/4}$, Doc.~182) is \emph{not} derived from the T$^4$ geometry and must not be fitted (fitting $=$ retrodiction). FFGFT is not the traditional yardstick; the factor is therefore adopted as a \emph{declared external calibration} from $\Lambda$CDM -- a choice of units, not an adoption of physics -- and inserted with the converged value once the $H_0$ tension ($\sim$67 vs.\ $\sim$73) is resolved; parametrized until then. The imported value does \emph{not} count as FFGFT confirmation. Affects only absolute positions ($\ell_1\approx220$, $z_*\approx875$), not the ratios; the internal forward derivation of the factor remains the goal. \emph{Open} \\[3pt]
R29 & 268 &
  selection rule: why does the CMB show only the subset $\{3,18,42,78\}$ of the T$^4$ peaks? &
  \emph{Only partially answered.} The factor~3 from the 3D projection ($3\cdot\{1,6,14,26\}$) is plausible, but the sequence $\{1,6,14,26\}$ is \emph{read off the data} (Doc.~268, step~4), not produced forward. In particular $|n|^2=30=3\cdot10$ is \emph{not} excluded: $|n|^2=10$ is a local maximum, and thermally $I(30)=13{,}2 > I(42)=7{,}6 > I(78)=1{,}7$ -- so $30$ ($\ell\approx696$) should be a peak, yet sits in a CMB trough. The ``strongest in range'' argument fails. \emph{Open}, sharpened by O.~Teker \\[3pt]
R30 & 268 &
  rigorous justification of the selection mechanism (full $C_\ell$ projection) missing &
  the \emph{naive} spherical Bessel sum $C_\ell=\sum_n N_\mathrm{BE}|j_\ell(k_\mathrm{obs}D_A)|^2$ does \emph{not} reproduce $\{3,18,42,78\}$ -- it washes out to a quasi-continuum dominated by low modes. The earlier formulation ``a feasible calculation, no fundamental obstacle'' was too optimistic: a physical source/window function selecting the peaks is missing. \emph{Open} \\[3pt]
R31 & 268 &
  anharmonicity of the CMB peaks: whence the stretch relative to the harmonic $1:2:3:4:5$? &
  \emph{Leading behaviour derived forward.} Forward, T$^4$ gives the harmonic backbone $1:2:3:4:5$ (symmetric resonance $k^2=3n^2$). The observed anharmonicity $1:2{,}44:3{,}68:5{,}09$ follows from the codimension-1 projection: last-scattering surface $\Rightarrow D_\mathrm{eff}=D_f-1=2-\xi\approx2 \Rightarrow$ Bessel index $\nu=-\xi/2\approx0 \Rightarrow J_0$ membrane $\Rightarrow 1:2{,}30:3{,}60:4{,}90$, matching to $\sim5\%$, parameter-free, without mode selection. The small residual ($D\approx1{,}86$) is \emph{not} derivable from $\xi$ (the spectral dimension of the weakly fractal space stays $\approx2$) and is of the order of the measurement uncertainty. \emph{Partially derived}; remainder open \\[3pt]
R32 & corpus-wide &
  statements presenting $H_0$ or the absolute scale as \emph{derived by FFGFT} &
  follows from R20: $H_0$ is an \emph{imported} external calibration, not derived. All passages presenting $H_0$ as an FFGFT result are to be cleaned up (\enquote{imported/declared} instead of \enquote{derived}). \emph{Noted for now}; corpus-wide cleanup deferred. \emph{Open} \\[3pt]
R33 & 009 / 042 / 181 &
  magnitude factor $5^4$ in $\xi = 1/(3\cdot2^2\cdot5^4)$ presented as \emph{derived} &
  the \emph{form} of $\xi$ is forward: the harmonic $4/3$ (perfect fourth, Doc.~042/159) gives the leading digit, $3$ (space dimensions) and $2^2{=}4$ (spacetime) are read off the geometry. The \emph{magnitude-carrying} factor $5^4{=}625$ ($\to 10^{-4}$), however, is \emph{not} derived forward: it is merely \emph{asserted} (\enquote{emerges from the fractal structure}, Doc.~009; \enquote{encodes the symmetry structure}, Doc.~181 -- there circular via $30000/4$) or the value is \emph{empirical} (Doc.~042: measured from the Higgs sector $1{,}3194\times10^{-4}$, $\sim$1\,\% off the ideal $4/30000$). It remains the \emph{intuitive} (harmonic / Euler Tonnetz) resp.\ empirical grounding of the magnitude; this is openly \emph{declared} as such, not presented as a forward derivation. Structural parallel to R20 (form fixed, factor open), one level deeper. \emph{Declared/noted} \\[3pt]
R34 & 181 / 013 &
  $D=4$ presented as \enquote{following necessarily / not a postulate}; role of the SI conversions for the c-/time-power &
  \emph{3+1 is empirical input} -- no theory derives the dimension count; the earlier \enquote{follows necessarily} claim (Doc.~181) is overstated. Forward are (i) periodicity (divergence-freedom), (ii) torus-not-sphere ($\pi_1\neq0$, stable windings), (iii) \emph{minimal sufficiency} -- 4 instead of a naive 5, because the duality $\tilde T\cdot m=1$ lets one circle carry mass \emph{and} time, (iv) the lossless (bijective) Hilbert representation (Type~III, Doc.~270/206/230). The \emph{bare number} 4 is \emph{not} forced forward (the \enquote{4 from $\xi$} argument in Doc.~181 is circular resp.\ base-dependent). \emph{Connection with the units:} the four-circle structure is at the same time the exponent bookkeeping of the SI conversions -- $c$ = space-time bridge (the three $T^3$ circles against the time direction), $\hbar$ = mass-time bridge ($S^1_m$, $\tilde T m=1$). Hence the SI factors are indispensable for the \emph{power of $c$} and the \emph{power of time}: $c=\hbar=1$ collapses $L,T,M$ to one axis and destroys exactly the exponent structure one wants to read off. $T^4$ (mass reading) and $T^3$+time (time reading) are the same object. Signature as R20/R33: structure/form forward, number input. \emph{Clarified} \\[3pt]
R35 & corpus-wide \newline (esp.\ 182, 250s, \newline scale tables) &
  quantities of the form $X = \xi^N$ resp.\ $X = \varphi^N$ read as FFGFT confirmation; the SI conversion factor ($\ell_P$) partly tacitly absorbed into the $\xi$ exponent &
  \textbf{$\xi^N$ triviality:} \enquote{$X = \xi^N$} is by itself \emph{vacuous}, since any magnitude can be written as a $\xi$ power -- an exponent alone is not a prediction (cf.\ R10, R20, R33: form forward, number input). The SI conversion factor $\ell_P$ must \emph{not} be absorbed into the exponent. \textbf{Finding:} only $L_0/\ell_P = \xi^1$ is exact; $R_H = \ell_P\cdot\xi^{-63/4}$ with $63/4 = 41/4 + 11/2$ -- the corpus $41/4$ is referenced to $E_0$ instead of the Planck scale; the \enquote{nice fractions} are roundings of measured exponents (measured $\approx 15{,}72$ vs.\ $63/4 = 15{,}75$). A $\xi^N$ representation counts as content only if $N$ is derived forward. \emph{Addendum (Doc.~279, 14~June):} the $11/2$ in $63/4=41/4+11/2$ is \emph{not arbitrary} -- it coincides with the forward-derived fine-structure exponent $\alpha=\xi E_0^2=K\,\xi^{11/2}$ (Doc.~011/070, the same $E_0=\sqrt{m_em_\mu}$ as the $41/4$ anchor), to $\sim0{,}5\,\%$ ($E_0/E_\text{Planck}=\xi^{5{,}48}$ vs.\ $5{,}5$). \emph{A conjecture, not evidence}: different reference bases (MeV vs.\ Planck), the identity proven only by $E_0=E_\text{Planck}\,\xi^{11/2}$ forward. The cosmic $41/4$ remains open. \emph{Declared (changelog Update 16), table entry added 10~June 2026} \\[3pt]
R36 & 182 / cosmol.\ \newline sector &
  $R_H$ interpreted as the \enquote{maximal scale} resp.\ size of the universe &
  \textbf{$R_H$ interpretation refined:} $R_H = c/H_0$ is the \emph{Hubble length} -- the local expansion rate expressed as a distance -- \emph{not} the size of the universe and \emph{not} the observable horizon (the latter $\approx 3\,R_H$ in $\Lambda$CDM). The actual universe exceeds $R_H$; only a \emph{lower bound} is measurable. The \enquote{maximal scale} from Doc.~182 is tenable only as the upper scale of the \emph{cosmological torus sector}, not as the extent of the universe. Consistent with R20 ($R_H$ calibration as a declared external input). \emph{Declared (changelog Update 17), table entry added 10~June 2026} \\[3pt]
R37 & 009, 188, 271, \newline 272, 275 &
  $\varphi$ in various documents in various roles: (a)~phenomenological scaling factor between fractal levels (Doc.~188); (b)~substrate geometry of HLV, not FFGFT (Doc.~271); (c)~trivial representation $X=\varphi^N$ as a non-prediction (Doc.~272); (d)~$\varphi^{12}/(1{,}314)$ with an empirical anchor (Doc.~009, R10) &
  \textbf{Three levels clearly separated:}
  \newline
  \textbf{(1) Microscopic -- input:} $\xi = 4/30000$ (fractal dimension). $\varphi$ is \emph{not} active here; $\xi$ and $\varphi$ are different objects.
  \newline
  \textbf{(2) Macroscopic -- revised (see R38):} $1/\varphi \approx 0{,}6180$ is a \emph{pass-through point} of the $\xi$ damping recursion $r(k+1)=r(k)\cdot(1-\xi)$ at $k^* = \log(\varphi)/\xi \approx 3609$ (the only fixed point: $0$). The original derivation claim is downgraded to an open question -- $k^*(c)$ exists for any target $c$, R35 applies (details: R38). The scale interpretation stands: levels with $q=2/3$ internally convergent, no RG steps with factor~2.
  \newline
  \textbf{(3) Particle physics -- output:} $Q_\mathrm{FFGFT}\approx 0{,}6677$ (Koide scalar, Doc.~258) operates only on the lepton-mass scale. Not to be confused with $1/\varphi$.
  \newline
  \textbf{Warning Doc.~272 / R35 / R10:} the warning \enquote{any quantity is writable as $\varphi^N$ -- not a prediction} remains valid -- and, after the revision of 11~June 2026, also \emph{applies to} the $k^*$ result from Doc.~275 (the earlier opposing delimitation here is retracted, see R38). \emph{Declared; level~(2) revised 11~June 2026} \\[3pt]
R38 & 275 &
  $k^* = \log(\varphi)/\xi \approx 3609$ presented as a \enquote{fixed point} result
  \enquote{without a free parameter}; delimitation from the
  $\varphi^N$ triviality (R35) claimed with three arguments &
  \textbf{Status clarification:} (a)~$1/\varphi$ is a \emph{pass-through point},
  not a fixed point -- the only fixed point of $r\mapsto r(1-\xi)$ is $0$.
  (b)~$k^*(c) = [\log c - \log(D_f/3)]/\log(1-\xi)$ exists for
  \emph{any} target $c\in(0,1)$ with identical parameter status:
  $k^*(Q_\mathrm{FFGFT})=3029$, $k^*(1/2)=5198$, $k^*(1/e)=7499$,
  $k^*(\alpha_\mathrm{em})=36899$ -- the free exponent was merely renamed
  $k^*$ and solved for the target. R35 applies in full
  (first corpus-internal self-application of the guardrail).
  (c)~The arithmetic ($r(3609)=0{,}6179940$, error $4{\cdot}10^{-5}$)
  is correct; the observation would gain physical content only through
  an independent fixing of $k^*\approx3609$ (level counting,
  observable) -- currently open.
  \emph{Revised after audit P.~Stoychev, 11~June 2026} \\[3pt]
R39 & 182, 267, 277, \newline corpus-wide ($H_0$/$R_H$) &
  $H_0$/$R_H$ calibration (R20/R36) readable as an FFGFT-specific gap resp.\ as an asymmetric disadvantage relative to $\Lambda$CDM &
  \textbf{$H_0$/$R_H$ status refined (shared reference point, not an FFGFT gap):} the relation Planck length$\leftrightarrow R_H$ (exponent $41/4$, $R_H/L_0 = 6{,}49\times10^{64}$) is derived from first principles by \emph{no} framework -- why the universe is $\sim$\,$10^{60}$ Planck lengths across is predicted by no theory.
  \newline
  $\Lambda$CDM fixes the relation via the \emph{measured} $H_0$ -- itself circular in the sense of the data degeneracy (Doc.~267). FFGFT adopts the established value for comparability and writes it in $\xi$ notation. Hence the cosmic scale is a \emph{shared empirical reference point of both models}, \emph{not} a free parameter and \emph{not} an FFGFT-specific gap.
  \newline
  Reinforcing: in FFGFT $\hbar, c$ are SI conversion and $G$ is derived ($\xi\to\{m_e,\ldots\}\to G\to\ell_P$); a \enquote{measured} dimensional anchor in the standard-physics sense does not even exist here. The earlier picture \enquote{imported/to be cleaned up} (R20/R32) remains correct but is \emph{not} to be read as a weakness relative to $\Lambda$CDM.
  \newline
  \textbf{Remaining open point (symmetric):} solely the \emph{forward derivation} of the exponent $41/4$ from $\xi$ (R20). It is missing -- but it is missing for every framework, not only FFGFT. The only genuine model asymmetry is the \emph{dark sector} ($\Omega_\Lambda, \Omega_\text{dm}$ as free densities), carried by $\Lambda$CDM alone (Doc.~277, cost table). \emph{Declared 14~June 2026} \\
C6 & 004, 025, 030, 039, \newline 041, 053, 061, 063, \newline 068, 081 &
  Cosmological redshift presented as \emph{wavelength-dependent} ($z(\lambda)\propto\lambda$, \enquote{UV stronger than radio}; e.g.\ Doc.~063 $z(\lambda_0)=\tfrac{\xi x}{E_\xi}\lambda_0$; Doc.~061 $\Delta z=0{,}008\ln(\lambda/\lambda_0)$; Doc.~068 $z(\lambda)=z_0(1+\ln(\lambda/\lambda_0))$). &
  \textbf{Redshift is achromatic.} The fractal path-lengthening is purely geometric and stretches \emph{all} wavelengths by the same factor: $1+z=e^{\xi x}$, independent of $\lambda$. A \emph{finite-element simulation} of the geometry yields no wavelength dependence; the leading term $z=\xi x$ is frequency-independent (Doc.~064). The observed cosmological redshift is achromatic -- FFGFT gets this right, and the earlier chromatic \enquote{discriminator} drops out (it moves to the \enquote{fits} column, data degeneracy Doc.~267). Worked out in Doc.~280. \emph{Declared 15~June 2026} \\
R40 & 005, 006, 011, \newline 012, 133, 275 &
  Implicit: from $\xi$ the \emph{absolute values} (masses, $\alpha$, $G$) follow directly and exactly; the \emph{100} in $K_{\text{frak}}$ and the \emph{3609} of the φ-recursion are taken as related/fundamental. &
  \textbf{Only ratios are exact.} Absolute values carry the fractal/SI correction, absorbed into the bridge constants $v$ (masses $m=r\xi^p v$), $E_0=7{,}398$~MeV ($\alpha$) and $3{,}521\times10^{-2}$/$2{,}843\times10^{-5}$ ($G$; \texttt{calc\_De.py}); in ratios they cancel ($m_\mu/m_e=206{,}768$). Factored out $=K_{\text{frak}}=1-100\xi$ (Doc.~011/012; Doc.~133: from $D_f$-consistency + RG over 17 orders, ``not an adjusted correction''). \emph{Keep separate:} \textbf{100} = RG amplification (Doc.~133); \textbf{3609} = depth at which $r(k)=\tfrac{D_f}{3}(1-\xi)^k$ passes the \emph{passage point} $1/\varphi$ (Doc.~275) -- not a fixed point, unanchored unless $1/\varphi$ is independently motivated (open, R37). Further couplings (backdoor) open; clean falsification only via forward prediction ($41/4\to H_0$). \emph{Declared 15~June 2026} \\
P41 & 267, 280, 221 \newline (cosmological sector) &
  Redshift drift (Sandage--Loeb) proposed as a possibly sharp discriminator of static ($1+z=e^{\xi x}$, $\dot z=0$) versus expansion -- a \emph{new} observable rather than a re-reading of the same data, potentially piercing the degeneracy (Doc.~267). &
  \textbf{Checked and not booked (degeneracy risk at the shared scale).} $\Lambda$CDM signal $\Delta v=c\,\dot z\,\Delta t/(1+z)$ over 25 years: $+6$\,cm/s ($z{=}0.5$), sign change at $z_0=1.92$, $-14$\,cm/s ($z{=}4$), $-20$\,cm/s ($z{=}5$); ELT/ANDES order $\sigma\sim2$\,cm/s. The \emph{amplitude} test is not degeneracy-proof: a secular evolution of the phase $\xi x$ at rate $s\approx(0.1$--$0.4)\,H_0$ mimics $\Lambda$CDM, and the natural FFGFT rate is $c/R_H=H_0$ \emph{exactly} -- both models share the scale (P36/P39); moreover the dipole systematic of the Galactic acceleration ($\approx17$\,cm/s over 25\,yr, direction-dependent and subtractable) lies at the same order as the signal. Conditionally sharp remains only the \emph{shape} test: the sign change at $z_0$, i.e.\ the two-band contrast $\Delta v(0.5)-\Delta v(4)\approx+20$\,cm/s, cannot be mimicked by \emph{any} $z$-constant secular channel -- but it requires a corpus-level \emph{advance} commitment to strict staticity ($\dot z=0$) and low-$z$ carriers beyond Lyman-$\alpha$; time horizon $\sim$2 decades. No falsification criterion booked; calculation: \texttt{Werkzeuge\_Skripte/drift\_sandage\_loeb\_check.py}. \emph{Declared 2~July 2026} \\
P42 & 282, 292 \newline (lepton sector) &
  Doc.~282 presented the pair $(\sqrt2,\ 2/9)$ as \emph{two pure numbers without a fit}; the precision analysis (Doc.~292) shows that the circulant with exactly this pair misses $m_\mu/m_e$ by $1.0\cdot10^{-5}$ at a measurement precision of $2.2\cdot10^{-8}$ -- excluded as an exact pair at the pole-mass level ($\sim450\,\sigma$ in the $\mu/e$-precise direction). &
  \textbf{One declared reference point: the ratio $m_\mu/m_e$.} The framework fundamentally keeps the purely theoretical derivation from $\xi$; the lepton sector receives -- analogous to R39 ($H_0$/$R_H$ as shared empirical reference) -- exactly \emph{one} declared reference point: $m_\mu/m_e$ fixes, at structural $r=\sqrt2$ (from $Q=2/3$), the operative angle $\theta_{\text{ref}}=0.2222220471$. The structural number $2/9$ is its \emph{rational address} to seven digits ($|\theta_{\text{ref}}-2/9|=1.75\cdot10^{-7}$), not an exactness claim at the pole-mass level. The $450\,\sigma$ finding thus dissolves in the claim layer. Two delimitations belong to this: \emph{first}, the status of $\xi$ is untouched -- FFGFT claims $\xi$ as forced by the geometry; that dispute is not adjudicated here. \emph{Second}, the lepton masses are in themselves \emph{not an input of the theory}: the structural numbers ($\sqrt2$ from $Q=2/3$, $2/9$ as address) stand on the theory side; the reference point belongs to the \emph{comparison level} -- it locates the geometric relation in the pole-mass/SI data (analogous to R39/R40: shared reference point resp.\ bridge constant) and would not be needed at all without the intent to compare. The honest price therefore lies not in the parameter count of the theory but in the \emph{test balance}: $m_\mu/m_e$ is consumed as anchor and drops out as a test quantity. The gain: the $m_\tau$ prediction becomes input-error-free sharp, $m_\tau = 1776.9690 \pm 0.0001$ MeV ($+0.91\,\sigma$ against PDG $1776.86\pm0.12$; the Belle-II world average decides). For the bridge work (Doc.~291) the question sharpens accordingly: the dynamics must select $\theta_{\text{ref}}$; $2/9$ remains its address and the pre-registered Stage-10 target (orbit resolution $\sim0.1 \gg 10^{-7}$, unaffected). \emph{Declared 2~July 2026} \\
P43 & 006, 011, 292 \newline (\texttt{calc\_De.py}) &
  Open question: whether the $K_{\text{frak}}$-with-$100$ formulas in the calculator \texttt{calc\_De.py} need reworking after the generation-linear finding (Doc.~292, $N_g=g\cdot N_0$). &
  \textbf{No rework; recorded as a note.} Verified: \texttt{calc\_De.py} does \emph{not} use $K_{\text{frak}}=1-100\xi$ explicitly. \emph{(i)}~$\alpha=\xi E_0^2$ with $E_0=7.398$~MeV ($=$ the geometric route-2 value, Doc.~292); since $7.398/7.348=K_{\text{frak}}^{-1/2}$, $K_{\text{frak}}$ is already \emph{absorbed} into the $E_0$ choice ($1/\alpha=137.035$, no separate factor) -- so the computation is already consistent with the two-route picture (Doc.~292), no contradiction. \emph{(ii)}~The masses run through per-particle $(r,p)$ ($m=r\xi^p v$; e/$\mu$/$\tau$ errors $1.18/0.66/0.37\%$) -- \emph{that} is the coarse $\xi$ ladder in which the generation-linear law $N_g=g\cdot N_0$ (Doc.~292) applies. Replacing the $(r,p)$ by $N_g$ would be a gain only after $N_0\approx38.6$ is derived (otherwise fit against fit, P35); until then the $(r,p)$ stand. No falsification/correction entry; the \textbf{100} in $K_{\text{frak}}$ (fixed RG scale, P40) and $N_0$ (per-generation ladder factor) stay separate. \emph{Declared 3~July 2026} \\
 R41 & 284 (cf.\ 270, 249) &
   Doc.~284 (and the private Medin note) framed \enquote{every conversion to SI is itself a measurement} and \enquote{a geometry-specific memory cannot appear in any SI-carrying result} -- too strong. &
   \textbf{The loss is not the SI conversion.} Per Doc.~270 the Type~I duality decompactification $S^1_m\!\to\!\mathbb{R}_t$ ($\tilde{T}\cdot m=1$) is a \emph{mode-preserving embedding} (lossless); compactness survives as the discrete spectrum and as physical observables ($T_\text{rev}$, CHSH$\sim\xi$). The genuinely lossy steps are the \emph{reverse} compactification $\mathbb{R}\!\to\!S^1$, the spatial projections $D3\!\to\!D0$, and -- for a read-out -- the \emph{finite, non-periodic window plus decoherence} (Test~G). FFGFT \emph{does} carry framework-specific SI observables: mass reading (masses/Koide/$g\!-\!2$), CHSH$\sim\xi$, $D_f$, $L_0$ (Doc.~270/249). \emph{Narrowed claim:} the coherence-sector recurrence (back-flow $5{,}125$, Doc.~282) is not \emph{resolvable} on a warm, finite-window SI-time observable such as EEG -- not \enquote{absent from any SI result}. Doc.~284 (DE+EN) aligned accordingly. \emph{Declared 19~June 2026} \\
 R42 & 270 (cf.\ 248) &
   The selection of which $T^4$ circle becomes time was left implicitly open / treated as a bare empirical input. &
   \textbf{Not an open geometric question -- it is the measurement.} In the compact view the four circles are symmetric (no space/time distinction); time is not selected by the geometry but is \emph{relational} -- the symmetry-breaking \emph{is} the measurement (the Type~I decompactification = read-out, Doc.~270/284). The embedded observer experiences one direction as duration (Doc.~248, self-referentiality). Bookkeeping closes with no gap: one-ness of time = signature/predictivity (hyperbolic vs.\ ultrahyperbolic); \emph{which} circle = the measurement / experienced situation; $3{+}1$ = the observer's situation, not a free parameter. New section added to Doc.~270 (DE+EN). \emph{Declared 19~June 2026} \\
 R43 & 285, 283 &
   Doc.~285 first stated the $3$-vs-$6$ relation as ``inequivalent structure / structural fork, not a coordinate artifact.'' &
   \textbf{Corrected to containment.} $C_3<A_5$ ($3$-fold and $5$-fold both permute the same icosahedron, \texttt{recompute\_reconcile.py}) and $T^7=T^4\times T^3$ ($7=4+3$), so $\mathrm{HLV}\supset\mathrm{FFGFT}$ at the group/dimension level -- the models are reconcilable, not incompatible. The $r(\tau)\le1$ result shows only that one cut-and-project map does not interconvert $\sqrt2$ and $2/\sqrt5$. The genuine difference is the \emph{realised protected geometry}: FFGFT protects an independent $3$-fold ($\sqrt2$, Koide $2/3$, confirmed); HLV the $5$-fold ($2/\sqrt5$), and (Doc.~283) $\sqrt2$ is not among HLV's protected directions. Containment makes them compatible without identical. \emph{Declared 19~June 2026} \\
 R44 & 272, 190 (P35), 285 &
   Previously: $\varphi$ had no distinguished role (P35: any quantity is writable as $\xi^N$ \emph{or} $\varphi^N$ -- a cautionary example with no predictive content). &
   \textbf{Sharpened (no contradiction).} $\varphi$ acquires meaning \emph{not} inside FFGFT but as the derived eigenvalue of HLV's $5$-fold / perp sector (golden inflation $\varphi^2=\varphi+1$) -- a marker of the boundary HLV$\setminus$FFGFT. The same crystallographic restriction ($2\cos(2\pi/5)=1/\varphi\notin\mathbb{Z}$) that forbids $\varphi$ in FFGFT assigns it to HLV. P35 stands: $\varphi$ as a fitting base carries no content, $\varphi$ as a symmetry eigenvalue is structure, not a measured scale in an exponent -- $\varphi$ does not become an FFGFT prediction. Dot Theory classification (Doc.~272): $\varphi$ = HLV-side discriminator of the structural nesting, entered as a contestable $O2$ rendering. \emph{Declared 19 June 2026} \\
 R45 & 285, 282--284 &
   Doc.~285 stated the d7 spectrum point too narrowly (read like ``quasicrystal spectrum without information content''). &
   \textbf{Sharpened.} A quasicrystal has two spectra: the \emph{structure / diffraction} spectrum is pure point (sharp Bragg peaks, $\approx21\times$ above a random null, \texttt{quasicrystal\_information.py}) -- that is the information and exactly HLV's substrate-distinguishability (stands); the \emph{energy / Laplacian} spectrum is singular-continuous (no sharp levels) -- hence no masses. P35 caveat is narrow: only fitting \emph{one} target number as $\varphi^N$ is content-free. Honest residual: null-reproducible was the \emph{temporal} over-damped kernel (Doc.~282--284), not the spatial structure. \emph{Declared 19 June 2026} \\
 R46 & 296 (cf.\ 025, 026, 063, 156) &
   Doc.~296 §5 (\enquote{Speculation: unobservable intermediate ranges}) books dark matter/energy as \emph{possible signatures of unobservable intermediate-scale ranges} -- formulated as open speculation. &
   \textbf{Open check-point (not yet processed).} This intermediate-scale formulation potentially runs \emph{counter} to the already established corpus line, which treats dark matter/energy not as an open signature but as a \emph{derived consequence}: Doc.~025 reads dark matter as a $\xi$-field effect and dark energy as \enquote{not required}; Doc.~026/063 hold that the universe does not expand and dark energy becomes superfluous ($H_0$ reinterpreted); Doc.~156 frames the entire observable reality as the projection of a single energy field with static redshift $z \approx \xi\ln(d/\ell_P)$. The \emph{intermediate-scale} mechanism is a different explanatory route from the established $\xi$-field route and is not a load-bearing concern of the framework. To be reconciled in a later revision of Doc.~296: either align the intermediate-scale formulation with the $\xi$-field derivation or mark it explicitly as a subordinate additional consideration. It should also be noted that the observer/projection/emergence core of Doc.~296 is already established in the corpus (Doc.~156) and is not newly introduced there. No correction entry, no rebuild -- booked as an open note. \emph{Declared 6~July 2026} \\
 R47 & 285, 297, 298 \newline (cf.\ 286, 284, 295) &
   R43 booked \enquote{$\mathrm{HLV}\supset\mathrm{FFGFT}$ dimensional} ($D7=D4+3'$-window). Read in the \emph{time sector}, this pure dimension count treated Marcel's spiral-time window as \emph{additional} -- as if it sat \emph{beside} FFGFT's recursion time and enlarged HLV. &
   \textbf{In the time sector: containment, not enlargement.} In unified notation -- both $D6+$time, Marcel as $D6+$spiral-time, FFGFT in Hilbert space as $D6+$recursion-time -- the spiral-time window is not additive but \emph{internal}: a bounded section (window) of the unrolled recursion time. Hence $\mathrm{HLV}\subset\mathrm{FFGFT}$ \emph{in the time sector}. Precisely, Marcel's object is the over-damped $-1/\varphi$ branch (the $3'$-window, Doc.~285/286: carries structure, no mass), \emph{not} the full recursion operator $R$ -- $R$ has two branches, the relevant one ($\varphi$, $D4$, masses, revival $5{.}125$) is FFGFT's. The embedding $\iota$ (Doc.~297, open conjecture) is exactly the map realizing this window as a bounded projection of the compact recursion. \emph{Distinction from R43 (no contradiction):} R43's $\supset$ is the pure \emph{dimension count} (the $3'$-window as additional); R47's $\subset$ is the \emph{derivation content in the time sector} (the window as a section of the named compact whole -- FFGFT supplies the whole, HLV evaluates the section without naming it). Both readings coexist \emph{as long as both are read in the same $D6+$time notation}. \emph{OP8-consistent:} a warm, finite EEG window over a partial turn looks locally Archimedean (Doc.~295) and does not resolve the winding (R41, Doc.~284) -- that U$_3$ adds nothing resolvable over U$_2$ is thus the \emph{prediction} of the window embedding, not a failure. \emph{Open (symmetric):} whether $\iota$ is \emph{forced} (genuine $\mathrm{HLV}\subset\mathrm{FFGFT}$ in the time sector) or merely \emph{allowed} (compatibility) -- forcing test like C3A5-BRIDGE2, on the time axis; $\iota$ remains a conjecture (Doc.~297).    \emph{Declared 8~July 2026} \\
 R48 & 304 (cf.\ 295, 301, 303) &
   Doc.~304 stated the $M_\tau/M_B$ bridge to Marcel's Spiral-Time memory across scattered bookings; the \emph{private covering note} to the first sending overstated (\enquote{real, not a benchmark artefact, unavoidable}). Marcel Krüger (author of the Spiral-Time Hypothesis) asked publicly that the boundary be made visible in the document itself and the bridge labelled a candidate rather than a secured mapping. &
   \textbf{Note withdrawn, document made precise (not repaired).} The overstatement lay solely in the \emph{mail} and was withdrawn without reservation; the document was written throughout from the FFGFT reading and already booked the bridge as restricted. Doc.~304 gained a dedicated section \enquote{Provenance and the limit of the bridge}: \emph{(i)}~two axes -- the $e$-criterion itself is script-verified and derivable from $\xi$ (\emph{proven}, Doc.~295), only the \emph{correspondence} to the operational $M_\tau/M_B$ is unsecured (logically \emph{restricted}, Category~B; empirically \enquote{no benchmark performed}, i.e.\ without an independent, jointly sealed comparison); \emph{(ii)}~the operational $M_\tau/M_B$ definition (recursive access, semantic compression, affective weighting, identity binding, persistent state carry, predictive reuse) is untouched -- curvature-fidelity is an \emph{additional, FFGFT-side} diagnostic candidate, not the separator of that framework, and replaces none of those functions (both directions: $1/n$ texture without bio-functions possible; bio-memory not excluded by failing the $e$-criterion); \emph{(iii)}~symmetry -- neither framework contains, grounds, explains, or subordinates the other, rejection leaves both unchanged; \emph{(iv)}~named provenance ($M_\tau/M_B$, operational $M_B$, v0.3--v0.5 from Marcel Krüger's work; $D(k)$, $e$-criterion, FFGFT interpretation from the FFGFT corpus). The ledger-foreign term \enquote{untested} was avoided; the claim-state remains \emph{restricted (Category~B)}. No FFGFT result changed -- only the framing of the relation to Marcel's objects. \emph{Declared 11~July 2026} \\
 R49 & 304, 305 (cf.\ 295, 303, 272) &
   After R48 the provenance of 304 was deepened: Marcel Krüger asked publicly that the notation adopted from his Spiral-Time work ($M_\tau/M_B$; likewise the sectors U1/U2/U3) be cited at first use --- not only in the provenance section --- and that the FFGFT-side objects optionally receive distinct notation. &
   \textbf{Vocabulary cited, marked as analysis, abstract de-symbolised --- notation not renamed.} A consolidated first-use footnote attributes U1/U2/U3 \emph{and} $M_\tau/M_B$ to Krüger (2026) with the primary source (\texttt{doi:10.5281/zenodo.21302278}) and documented lineage (Medinformatics; Smart Wearable Technology), and records: \emph{FFGFT does not need this distinction} --- a single, curvature-faithful winding; the sectors and the $M_\tau/M_B$ split serve only as an \emph{analysis} of that framework, not as native structure. The Status separates accordingly: the FFGFT-internal core (thesis, linearisation reflex, measurement/projection epistemology) stands on its own, the correspondence is the illustrative, \emph{restricted} overlay. Doc.~305 is booked in its Status as a \emph{script-verified illustration} of Doc.~295 (not an independent finding; the uniform accumulator is a contrast foil from the bridge context, not an FFGFT object). The abstract was recast \emph{narratively without the borrowed symbols}, so that $M_\tau/M_B$ and U1/U2/U3 first appear in the body (attributed). One sentence acknowledges the governance lineage (claim-state ledger / identity check from Stefaan Vossen's \emph{Dot Theory}, co-developed in the IPI, cf.\ Doc.~272; the five-way record of Doc.~303 as the FFGFT-side extension). The \emph{distinct renaming} of the FFGFT objects ($M_{\mathrm{lin}}/M_{\mathrm{curv}}$) was left as an authorial decision, not carried out. No FFGFT result changed --- only citation, framing, and readability. \emph{Declared 11~July 2026} \\
 R50 & 025, 063 (superseded by 306; cf.\ 003, 010, 295, 298, 302) &
   Docs.~025 and~063 justify the absence of a cosmic initial singularity by Heisenberg's energy--time uncertainty relation (\enquote{$\Delta E\cdot\Delta t \ge \hbar/2 = 1/2$ irrefutably proves\ldots}). Three defects: \emph{(M1)}~\textbf{inverted implication} --- a finite $\Delta t$ gives $\Delta E \ge 1/(2\Delta t)$, a \emph{finite} bound, not $\Delta E\to\infty$; the latter follows only from $\Delta t\to 0$. \emph{(M2)}~\textbf{misapplication} --- energy--time uncertainty is not canonical (Pauli: no self-adjoint time operator); its $\Delta t$ is, by Mandelstam--Tamm, an observable's change time, not a cosmic age. \emph{(M3)}~\textbf{breach of style} --- \enquote{irrefutably} is not a ledger term. Overarching: Heisenberg belongs to the \emph{projected} QM level; an argument leaning on it does not leave the projection but circulates within it (Doc.~298). &
   \textbf{Justification replaced, conclusion unchanged.} The conclusion (no singular beginning; a finite core with a minimal scale $L_0$ set by $\xi$) stands. The derivation is replaced by the native chain of \textbf{Doc.~306}: $T\cdot m = 1$, hence with $E=m$, $T\cdot E = 1$ (Doc.~003/010) --- an \emph{equation}, not an inequality; from it $E\to\infty \Leftrightarrow T\to 0$; but FFGFT time carries a minimal, non-vanishing increment $d_1 = 100\,\xi_1 = 1/75$ (from $\xi=4/30000$), so $T$ is bounded below and $E$ bounded above --- an infinite density is \emph{structurally} excluded. In addition the \textbf{boundary question}: $\partial T^4=\emptyset$ (Doc.~302) --- \enquote{what was at $t=0$?} presupposes a boundary a compact torus does not have; the question is not wrongly answered but wrongly posed. Made precise: $D(k)$ \emph{grows} without bound (logarithmically); the singularity-free statement is that $D(k)$ is finite at every \emph{finite} $k$ and diverges nowhere. Docs.~025/063 are \emph{no longer authoritative} for this point --- not refuted, but superseded. Open (historical, not systematic, left unanswered): why the import was made although Doc.~003/010 was available. \emph{Declared 12~July 2026} \\
\end{longtable}
}
