% ==============================================================================
% T0 Theory / FFGFT: Document 270 (Chapter Content, EN)
% Title: Projection Chain T^4 -> T^0 -- Two Types of Dimensional Reduction
% Author: Johann Pascher
% Date: June 2026
% References: Doc. 147, 159, 183, 185, 206, 254, 258, 259, 268
% ==============================================================================

\section*{Abstract}

The reduction of the fundamental 4-torus structure $T^4$ of FFGFT to lower
dimensions is examined as a formal chain $T^4 \to T^3 \to T^2 \to T^1 \to T^0$.
The central claim is that this chain does \emph{not} consist of steps of the
same kind. It splits into two qualitatively distinct operations. The first step
($D4\!\to\!D3$) is not a lossy projection but a \emph{duality decompactification}:
the compact mass dimension $S^1_m$ is unrolled into the non-compact time
direction via the fundamental relation $\tilde{T}\cdot m = 1$. This operation
preserves the mode content; only the direct visibility of compactness survives,
as a discrete spectral signature encoded by the recursion $\xi^n$. The further
steps ($D3\!\to\!D2\!\to\!D1\!\to\!D0$) are genuine geometric projections of
spatial directions: strictly lossy, not reversible, and \emph{not} compensated
by the recursion. The step $D3\!\to\!D2$ is identified as a holographic
projection. The topological identification $t\sim t+R_m$ is shown to be a
physical observable ($T_\text{rev}$, CHSH deviation $\sim\xi$). The downward reduction is contrasted with the
\emph{upward} operation: the bijective representational translation
$T^4 \leftrightarrow$ Hilbert space/matrix (Type~III, Doc.~230/206/231), which is
\emph{lossless} -- precisely because it adds no geometric extra dimensions but
expresses the same 4D content in a higher-dimensional language. The work thereby
resolves the apparent tension between ``projection loses information'' and
``compactified / decompactified'', and classifies geometric downward reduction
against representational upward translation.

% ============================================================================
\section{Motivation: the tension in the question}
% ============================================================================

FFGFT describes fundamental physics on a compact 4-torus $T^4$ with the single
dimensionless parameter $\xi = 4/30000$ and the central relation
$\tilde{T}\cdot m = 1$. The observable world, by contrast, is a
three-dimensional space with time evolution, $\mathbb{R}^3 \times \mathbb{R}_t$.

Three observations on this transition appear to conflict:
\begin{itemize}
  \item[(A)] \textbf{Loss picture.} Every projection $D{\to}D{-}1$ is not
  injective and therefore loses information. The chain $T^4 \to \dots \to T^0$
  is not reversible.
  \item[(B)] \textbf{Compactness picture.} $T^4$ is fully compactified; the
  observable spacetime $\mathbb{R}^3 \times \mathbb{R}_t$ is decompactified.
  \item[(C)] \textbf{Upward picture.} There already exists a \emph{bijective}
  translation of $T^4$ into a higher-dimensional space -- the Hilbert space
  (Doc.~230) -- which is \emph{lossless}.
\end{itemize}

These three pictures cannot be naively superimposed: if the first step were pure
loss (A), no \emph{decompactified} time direction (B) could arise from it, since
forgetting creates no new dimension; and it would remain puzzling how an upward
move (C) can be lossless while the downward move (A) destroys information.

The resolution: there is not one but \emph{three} dimension-changing operations
of \emph{two kinds}. \emph{Geometric} operations (Type~I: mass-time duality;
Type~II: spatial projection) reduce the observable world out of $T^4$; the
\emph{representational} operation (Type~III) translates $T^4$ upward without
loss. The geometric-downward lossy versus representational-upward bijective
move -- this asymmetry is the central result of the work.

% ============================================================================
\section{Structure of $T^4$}
% ============================================================================

\subsection{Decomposition and radius classes}

\begin{definition}[Fundamental torus structure]\label{def:t4}
The fundamental level of FFGFT is the compact 4-torus
\[
  T^4 \;=\; S^1_x \times S^1_y \times S^1_z \times S^1_m ,
\]
with three \emph{spatial} circles $S^1_{x,y,z}$ and one \emph{mass circle}
$S^1_m$. All four components are compact.
\end{definition}

\begin{remark}[The fourth direction as substitute time]\label{bem:struktur}
The fourth torus direction $S^1_m$ is not a mass dimension \emph{alongside} a
separate time, but the \emph{substitute-time direction} itself. Mass and time
are two \emph{readings} of one and the same dimension; the fundamental relation
$\tilde{T}\cdot m = 1$ is the translation dictionary:
\[
  \underbrace{S^1_m \text{ (compact)}}_{\text{mass reading, discrete spectrum}}
  \;\;\xleftrightarrow{\;\;\tilde{T}\cdot m = 1\;\;}\;\;
  \underbrace{\mathbb{R}_t \text{ (open)}}_{\text{time reading, continuous flow}}.
\]
There is no time ``in addition'' to the four directions; time is the
decompact reading of the fourth direction (cf.\ Doc.~185). The two-type
structure depends only on the separation of \emph{small} and \emph{large}
compactification radii and is independent of the labelling.
\end{remark}

The four directions carry two separated radius classes:
\begin{align}
  R_x = R_y = R_z &\;\sim\; R_H
  && \text{(cosmological horizon, ``large'')},\\
  R_m &\;\sim\; \xi \cdot \ell_P
  && \text{(Planck scale, ``small'')}.
\end{align}

\begin{remark}[Status of the two scales]\label{bem:skalen}
$R_H$ here is the \emph{declared external} (imported) cosmological scale,
\emph{not} derived from $\xi$. Intrinsic is only the \emph{form} -- the
large/small radius-class split, equivalently the dimensionless ratio
$R_H/\ell_P$ -- not the absolute \emph{factor} (Doc.~190, P20). The two-type
structure of this document depends only on that class split, not on the
numerical value of $R_H$. Conversely $R_m\sim\xi\ell_P$ sets the \emph{top} of the
KK tower ($1/R_m\sim\xi^{-1}m_P$, trans-Planckian); the observed particle masses
lie further down the ladder via the recursion $\xi^n$ (Doc.~159, 258/259).
\end{remark}

\subsection{Kaluza--Klein reading}

A compact circle of radius $R$ carries a discrete mass tower $m_n \sim n/R$,
$n \in \mathbb{Z}$. The two radius classes therefore generate qualitatively
different physics:

\begin{center}
\begin{tabular}{lll}
\hline
\textbf{Circle} & \textbf{Radius} & \textbf{Mode tower} \\
\hline
$S^1_{x,y,z}$ & $R\sim R_H$ (large) & gap $\sim 1/R_H \approx 0$, quasi-continuous $\Rightarrow$ space \\
$S^1_m$ & $R\sim \xi\ell_P$ (small) & gap huge, discrete and heavy $\Rightarrow$ mass spectrum \\
\hline
\end{tabular}
\end{center}

\begin{proposition}[$\tilde T m = 1$ as compactification relation]\label{prop:tm}
In natural units a compactification radius $R$ has the dimension of a length or
intrinsic time, $\tilde{T}\sim R$, while the generated mass scale is
$m \sim 1/R$. The fundamental relation
\[
  \boxed{\;\tilde{T}\cdot m = 1\;}
\]
is thus structurally the Kaluza--Klein relation for the mass dimension.
\end{proposition}

% ============================================================================
\section{Two types of reduction}
% ============================================================================

The \emph{downward} direction (reduction of $T^4$) proceeds via two geometric
operations, developed here. The lossless \emph{upward} operation (Type~III,
representational translation) follows in Section~8.

\subsection{Type~I: duality decompactification (mass $\to$ time)}

\begin{definition}[Unrolling the mass dimension]\label{def:typeI}
The operation
\[
  S^1_m \;\xrightarrow{\;\text{covering}\;}\; \mathbb{R}_t,
  \qquad p:\mathbb{R}_t \to S^1_m,\;\; t \mapsto e^{2\pi i\, t / R_m},
\]
unrolls the compact mass circle into the non-compact time direction via its
universal cover. It is governed by $\tilde{T}\cdot m = 1$.
\end{definition}

\begin{theorem}[Type~I preserves mode content]\label{satz:typeI}
The unrolling $S^1_m \to \mathbb{R}_t$ is an embedding, not a projection.
Periodic structures on $S^1_m$ lift uniquely into $\mathbb{R}_t$; the function
space on $\mathbb{R}_t$ is strictly larger. No mode content is forgotten;
rather, an additional non-compact direction arises -- time.
\end{theorem}

\begin{beweis}
(Sketch) The universal cover $p:\mathbb{R}\to S^1$ is a local homeomorphism and
surjective. An $R_m$-periodic function on $\mathbb{R}$ corresponds bijectively to
a function on $S^1_m$ (Fourier series, discrete spectrum). The reverse direction
(compactification $\mathbb{R}\to S^1$) is lossy, since non-periodic parts do not
descend. Unrolling therefore proceeds in the \emph{embedding}, not the
projecting, direction.
\end{beweis}

\begin{corollary}[Time as embedding price]
The ``price'' of decompactification is not loss of information but the
appearance of the time direction itself (Doc.~185). What does not remain
directly visible is only the \emph{compactness}: the periodicity of $S^1_m$
appears in the observable not as geometry but indirectly -- as the discrete
structure of the spectrum.
\end{corollary}

\begin{remark}[What ``not totally loss-free'' refers to]\label{bem:residual}
This is not about absolute loss but about \emph{reading-dependent visibility}.
In the mass reading the compactness is manifest -- the spectrum is discrete and
the identification $t \sim t + R_m$ is expressed directly. In the time reading
the same compactness is only \emph{latent}: from continuous time alone the
topological identification is not uniquely reconstructible (the winding remains
ambiguous). The duality guarantees full translatability of the spectrum; the
identification is carried by the time reading only implicitly -- through the
discreteness of the spectrum. This is exactly where $\xi^n$ acts.
\end{remark}

\subsection{Type~II: geometric projection (spatial)}

\begin{definition}[Forgetting a spatial direction]\label{def:typeII}
A projection $\pi:\mathbb{R}^{k}\to\mathbb{R}^{k-1}$ with $\ker(\pi)=\mathbb{R}$
forgets a spatial direction. It is not injective and therefore not invertible.
\end{definition}

\begin{theorem}[Type~II is strictly lossy]\label{satz:typeII}
In a spatial projection $\mathbb{R}^k \to \mathbb{R}^{k-1}$ a full fibre
$\mathbb{R}$ collapses. The information about the forgotten direction is not
contained in the image and cannot be reconstructed without additional data
(boundary conditions, holographic completeness). The recursion $\xi^n$ does
\emph{not} act on this step.
\end{theorem}

\begin{center}
\begin{tabular}{lll}
\hline
 & \textbf{Type~I (mass$\to$time)} & \textbf{Type~II (spatial)} \\
\hline
Operation & unrolling / covering & forgetting / projection \\
Direction & embedding & projecting \\
Mode content & preserved & lost \\
Reversibility & dual/spectral recoverable & not reversible \\
Role of $\xi^n$ & spectral signature & ineffective \\
Residue & compactness only inferred & genuine geometric loss \\
\hline
\end{tabular}
\end{center}

% ============================================================================
\section{The formal chain, step by step}
% ============================================================================

\subsection{Step~1: $D4 \to D3 + \text{time}$ (Type~I)}
\[
  T^4 \;\longrightarrow\; \underbrace{T^3}_{\to\,\mathbb{R}^3}
  \;\times\; \underbrace{\mathbb{R}_t}_{\text{from } S^1_m}.
\]
Step~1 bundles \emph{two} information-preserving operations of \emph{different}
mechanism: (Ia) the \emph{mass circle} unrolls to $\mathbb{R}_t$ via the duality
$\tilde T m=1$ per Theorem~\ref{satz:typeI} (duality decompactification);
(Ib) the three \emph{spatial circles} decompactify through the \emph{limiting
process} of large radii ($R_{x,y,z}\to\infty$ for $r\ll R_H$) to $\mathbb{R}^3$
(limit decompactification). Both are embeddings, not projections; but (Ib) is
\emph{not} a duality step, it is a limit -- see the clarification in
Section~\ref{sec:offen}, point~3.

\textit{Invariant:} $\tilde{T}\cdot m = 1$ (Prop.~\ref{prop:tm}); in the spatial
limit, local flatness.\quad
\textit{Loss:} none in mode content; only the visibility of compactness
(Rem.~\ref{bem:residual}).

\subsection{Step~2: $D3 \to D2$ (Type~II, holographic)}
\[
  \pi_2:\; \mathbb{R}^3 \;\longrightarrow\; \mathbb{R}^2,
  \qquad \ker(\pi_2) = \mathbb{R}\;\;(\text{depth direction}).
\]
\textit{Invariant:} area $A$.\quad
\textit{Holography:} step~2 is mathematically the holographic principle; in the
horizon case the Bekenstein--Hawking bound $S \le A/(4\ell_P^2)$ (cf.\
Doc.~254/268).\quad
\textit{Loss:} genuine depth direction.

\subsection{Step~3: $D2 \to D1$ (Type~II)}
\[
  \pi_3:\; \mathbb{R}^2 \;\longrightarrow\; \mathbb{R},
  \qquad \ker(\pi_3) = \mathbb{R}.
\]
\textit{Invariant:} length $L$.\quad
\textit{Loss:} second spatial direction; no area measure remains.

\subsection{Step~4: $D1 \to D0$ (Type~II, total loss)}
\[
  \pi_4:\; \mathbb{R} \;\longrightarrow\; \{\mathrm{pt}\}.
\]
\textit{Invariant:} only a discrete scalar measure ($n\in\mathbb{Z}$).\quad
\textit{Loss:} the complete geometric structure.

% ============================================================================
\section{Reversibility, precise per type}
% ============================================================================

\begin{theorem}[Reversibility of the full chain]\label{satz:rev}
Let $\Pi = \pi_4\circ\pi_3\circ\pi_2$ be the spatial subchain
$\mathbb{R}^3 \to \{\mathrm{pt}\}$ and $D$ the Type~I operation
$S^1_m \to \mathbb{R}_t$. Then:
\begin{enumerate}
  \item[(i)] $D$ is, as a duality (Fourier/KK), invertible in mode content; the
  winding remains ambiguous. $D$ is ``almost reversible''.
  \item[(ii)] $\Pi$ is not invertible: there is no continuous map
  $\rho:\{\mathrm{pt}\}\to\mathbb{R}^3$ with $\rho\circ\Pi=\mathrm{id}$.
\end{enumerate}
\end{theorem}

\begin{beweis}
(Sketch) (i) follows from Theorem~\ref{satz:typeI}: unrolling is embedding, the
discrete spectrum encodes the full periodic content; only the choice of lift
(winding) is non-unique. (ii) follows from Theorem~\ref{satz:typeII}: each
$\pi_k$ has $\ker = \mathbb{R}\neq\{0\}$. A left inverse would have to
reconstruct the collapsed fibre structure; this information is not present in
the image $\{\mathrm{pt}\}$.
\end{beweis}

\begin{corollary}[Resolution of the initial tension]
Pictures~(A) and~(B) are both correct but concern different operations. The
non-reversibility (A) holds for the \emph{spatial} projections (Type~II). The
decompactification to the time direction (B) is the \emph{embedding} Type~I
step -- it creates a dimension instead of forgetting one. There is no
contradiction.
\end{corollary}

% ============================================================================
\section{Role of the recursion $\xi^n$}
% ============================================================================

The recursion $R:\xi^n \mapsto \xi^{n+1}$ is \emph{not} a universal compensation
for projection losses. Its function is narrowly bounded:
\begin{itemize}
  \item \textbf{Type~I:} $\xi^n$ generates the discrete mass spectrum (particle
  ladder). This spectrum \emph{is} the compact mode content of $S^1_m$, dually
  expressed as time-frequency structure. $\xi^n$ ``fills in'' nothing; it is the
  spectral signature through which the hidden compactness remains recognisable
  (Rem.~\ref{bem:residual}).
  \item \textbf{Type~II:} $\xi^n$ has no effect. Spatial projection losses are
  genuine and untouched by the recursion.
\end{itemize}

\begin{remark}[Correction of a tempting misrepresentation]
A presentation that assigns the recursion a ``compensation strength'' decreasing
monotonically across all four steps (full/partial/weak/none) is misleading. It
presupposes a uniform lossy ladder that does not exist. The recursion belongs
exclusively to the Type~I step.
\end{remark}

% ============================================================================
\section{Overview}
% ============================================================================

\begin{table}[h!]
\centering
\begin{tabular}{lllll}
\hline
\textbf{Step} & \textbf{Operation} & \textbf{Type} & \textbf{Invariant} & \textbf{$\xi^n$} \\
\hline
$D4\to D3{+}t$ & $S^1_m\to\mathbb{R}_t$ (unroll) & I & $\tilde{T}m=1$ & spectral signature \\
$D3\to D2$ & forget space & II & area $A$ & -- \\
$D2\to D1$ & forget space & II & length $L$ & -- \\
$D1\to D0$ & forget space & II & $n\in\mathbb{Z}$ & -- \\
\hline
\end{tabular}
\caption{The chain $T^4 \to T^0$ separated by type.}
\end{table}

\[
\underbrace{T^4 \;\longrightarrow\; \mathbb{R}^3\times\mathbb{R}_t}_{\text{Type I: embedding, almost reversible}}
\;\longrightarrow\;
\underbrace{\mathbb{R}^2 \;\longrightarrow\; \mathbb{R} \;\longrightarrow\; \{\mathrm{pt}\}}_{\text{Type II: projecting, not reversible}}
\]

% ============================================================================
\section{The upward direction: representational translation (Type~III)}
% ============================================================================

The chain so far describes only the \emph{downward} direction (reduction). There
is a counter-direction -- but it is \emph{not} geometric.

\begin{definition}[Type~III: representational translation]\label{def:typeIII}
The operation
\[
  T^4 \;\xleftrightarrow{\;\text{bijective}\;}\; \mathcal{H}
\]
translates the FFGFT mode formalism on $T^4$ into the (infinite-dimensional)
Hilbert space $\mathcal{H}$, or the equivalent matrix algebra (Doc.~230, 206,
231). It is not an approximation but a \emph{bijective structural statement}:
every QM computation is expressible in FFGFT language and vice versa.
\end{definition}

\begin{important}[The dimensional asymmetry]
Downward (geometric) and upward (representational) are different kinds of
operation with \emph{opposite} information properties:
\begin{itemize}
  \item \textbf{Downward (Type~II, geometric):} lossy, not reversible -- a fibre
  collapses (Theorem~\ref{satz:typeII}).
  \item \textbf{Upward (Type~III, representational):} bijective, lossless -- it
  adds \emph{no} physical dimensions but expresses the same 4D content in a
  higher-dimensional \emph{language} in which it fits without reduction.
\end{itemize}
The losslessness follows \emph{precisely from} the representational character --
not from any gain of genuine extra dimensions.
\end{important}

\begin{remark}[No geometrically higher dimensions]
A geometric extension $T^4 \to T^5 \to \dots$ is excluded in FFGFT (Doc.~171):
complexity arises from \emph{fractal depth} ($D_f = 3-\xi$, self-similarity), not
from \emph{more} dimensions. This is the deliberate contrast with string theory
(10/11D, Calabi--Yau, landscape problem). ``Higher'' therefore always means
Type~III (representational) in FFGFT, never geometric.
\end{remark}

FFGFT thus has three dimension-changing operations:

\begin{center}
\begin{tabular}{llll}
\hline
\textbf{Type} & \textbf{Operation} & \textbf{Character} & \textbf{Information} \\
\hline
I & mass\,$\leftrightarrow$\,time ($\tilde T m=1$) & geometric & almost reversible \\
II & spatial projection (down) & geometric & lossy \\
III & $T^4\leftrightarrow\mathcal{H}$/matrix (up) & representational & \textbf{bijective} \\
\hline
\end{tabular}
\end{center}

\noindent
The bijectivity of Type~III is the mirror image of the non-reversibility of
Type~II (Theorem~\ref{satz:rev}): geometrically one loses on reducing,
representationally one loses nothing on translating.

% ============================================================================
\section{Why exactly four circles? Minimal sufficiency, units, and visualization}\label{sec:warumvier}
% ============================================================================

The chain so far (Type~I/II downward, Type~III upward) presupposes the four-circle
structure $T^4 = S^1_{x,y,z}\times S^1_m$. This section answers \emph{why} there
are exactly four -- deliberately \emph{not} as a derivation of the number, but as
\emph{minimal sufficiency}.

\subsection{$3+1$ is input, not derivation}

No theory derives the dimension count of spacetime: the Standard Model and GR
assume $3+1$; string theory fails on uniqueness (landscape problem). FFGFT, too,
\emph{does not derive the 4 forward}; it takes $3+1$ as \emph{empirical input}.
The question is therefore not \enquote{why is the world four-dimensional?} but
\enquote{\emph{given} $3+1$ -- which structure is the minimal one that carries
everything?}.

\subsection{Minimal sufficiency: four instead of five}

\begin{important}[The duality saves one dimension]
Naively one would need \emph{five} building blocks: three for space, one for a
mass spectrum (particles), one for time evolution. The fundamental relation
$\tilde T\cdot m = 1$, however, identifies the \emph{mass reading} and the
\emph{time reading} of \emph{one} dimension (Type~I, Theorem~\ref{satz:typeI}):
the fourth circle $S^1_m$ carries the mass spectrum as its KK tower \emph{and},
decompactified, time. The duality lets \emph{one} circle do the work of two -- so
the naive $5$ collapses to $\mathbf{4}$.
\end{important}

\begin{itemize}
  \item \textbf{Fewer} (only $T^3$): no mass spectrum, no time.
  \item \textbf{Four} ($T^3$ + one dual circle): space, masses \emph{and} time
  from \emph{one} object, without redundancy.
  \item \textbf{More} (a second such circle): a second independent mass tower or a
  second time -- superfluous, without correlate.
\end{itemize}

\noindent
\enquote{Optimal} therefore means \emph{minimal-sufficient}: the smallest
dimension count in which space, the full mass spectrum, and time jointly emerge
from one geometric object.

\subsection{The four circles as units bookkeeping}

The four-circle structure \emph{is} at the same time the exponent bookkeeping of
the SI conversion factors -- each circle type carries its bridge:
\[
  \underbrace{S^1_{x,y,z}}_{\text{space}}
  \;\xrightarrow{\;c\;}\;\text{time},
  \qquad
  \underbrace{S^1_m}_{\text{mass}}
  \;\xrightarrow{\;\hbar\;(\tilde T m=1)\;}\;\text{time}.
\]
$c$ is the space-time bridge of the three spatial circles, $\hbar$ the mass-time
bridge of the mass circle. This is why the SI conversions are \emph{indispensable}
once one wants to determine the exponent structure correctly:

\begin{remark}[Why natural units hide the powers]
Natural units ($c=\hbar=1$) collapse $L$, $T$ and $M$ to \emph{one} axis. This
removes precisely the distinction that carries the exponent structure -- the
independent \emph{power of $c$} resp.\ \emph{of time}. $c$ and $\hbar$ may be set
to $1$ only \emph{after} the exponents have been read off; before that the
information is destroyed. The factors are the scaffolding that keeps the powers
visible -- and easy to handle precisely because their whole role is that
scaffolding without a free parameter. $G$, too, is \emph{derived} -- reconstructed
from $\ell_P$, $c$, $\hbar$, for which it needs only the SI relations
(Docs.~012/056) -- and carries \emph{no} free factor. The only free factor sits
not in a conversion or natural constant but in the \emph{cosmological absolute
scale} $R_H$ (exponent $41/4$; Doc.~190, R20).
\end{remark}

\subsection{The same structure as Hilbert visualization}

The four-circle geometry is also the \emph{faithful} visualization of the
infinite-dimensional Hilbert space (Type~III, Def.~\ref{def:typeIII}) -- two
readings of \emph{the same} bijection:
\begin{itemize}
  \item \textbf{generative/ontological:} $T^4 \to \mathcal{H}$ -- the geometry
  \emph{generates} the algebra (Doc.~206), not the reverse;
  \item \textbf{visualizing/epistemic:} the abstract $\mathcal{H}$ becomes
  intuitable at all only through the $4$D geometry.
\end{itemize}
\enquote{Higher-dimensional} (the $\infty$-dimensional $\mathcal{H}$) does
\emph{not} mean \enquote{more fundamental}: the generative direction is
$T^4 \to \mathcal{H}$. Precisely \emph{because} the $4$D structure is generative
(not a mere picture), the visualization is \emph{exact} -- bijective, not a
cartoon.

\subsection{Summary of the dimension line}

\begin{important}[What \enquote{optimal} means]
$T^4$ resp.\ $T^3+\text{time}$ is the \emph{minimal-sufficient},
\emph{dual-economical} and \emph{Hilbert-faithful} configuration -- \emph{given}
$3+1$. The strength lies in the economy (one dimension saved by
$\tilde T m=1$) and the faithfulness (lossless Hilbert representation), \emph{not}
in a uniqueness of the number. The bare $4$ is input, not a forward result
(Doc.~190, R34) -- the same signature as for the $\xi$-magnitude (R33) and the
cosmological scale (R20): \emph{structure forward, number input}.
\end{important}

% ============================================================================
\section{In the compact view, time is just another circle: the asymmetry is the measurement}\label{sec:zeitkreis}
% ============================================================================

In the compact representation $T^4 = S^1\times S^1\times S^1\times S^1$ all four
circles are identical: dimensionless cyclic coordinates, no signature, no
space/time distinction. Time is written \emph{exactly} as the three spatial
circles; at the compact level the Lorentzian asymmetry does not exist. This is why,
in FFGFT, the time coordinate is simple to write -- it is one circle like the
others. The complication enters only when one leaves the compact picture.

The asymmetry (one time, signature $(3,1)$) appears only under decompactification
(Type~I, Def.~\ref{def:typeI}): exactly one circle -- the mass circle,
$\tilde{T}\cdot m=1$ -- unrolls through its universal cover into non-compact time,
while the other three stay compact (discrete spectrum) or project (space, Type~II).

\emph{Which} circle becomes time is therefore not an intrinsic-geometric fact to be
derived. The geometry is symmetric, and nothing in it should single one direction
out. Time is \emph{relational}: the selection is the measurement itself. The
decompactification \emph{is} the measurement -- the read-out/projection of this
document and of Doc.~284 -- and committing one circle to non-compact, experienced
time is exactly the information-discarding step a measurement performs. The embedded
observer, reading out from the inside (Doc.~248, self-referentiality), experiences
one direction as duration; that experience constitutes the time circle. The
symmetry-breaking is the measurement, not the geometry.

\begin{principle}[The time circle is selected by the measurement]
In the compact view the four circles of $T^4$ are symmetric. Time is not chosen by
the geometry but is relational: the symmetry-breaking \emph{is} the measurement (the
decompactification of Type~I). Three statements then close the bookkeeping with no gap:
\begin{itemize}
  \item \textbf{That there is one time} (not two) is the signature/predictivity
  constraint -- one timelike direction gives hyperbolic field equations with a
  well-posed Cauchy problem; two or more give ultrahyperbolic equations with no
  well-posed initial-value problem.
  \item \textbf{Which circle is time} is fixed by the measurement, i.e.\ by the
  experienced situation of the embedded observer (Doc.~248).
  \item \textbf{That the split is $3{+}1$} is the structure of being an embedded
  observer -- the empirical input of Doc.~190 (P34), read here as the observer's
  situation rather than a free parameter.
\end{itemize}
\end{principle}

The contrast with a non-compactified treatment of time is then sharp. A framework
that writes time as a complicated structure built on already-physical time $t$ (for
instance a spiral-time operator $\psi(t)=t+i\varphi(t)+j\chi(t)$, Doc.~283/284) has
\emph{reified} the result of the measurement into its kinematics, instead of
recognising experienced time as the measurement-induced decompactification of a
symmetric circle. In the compact view that complication is unnecessary: time is one
more circle, and only the read-out turns it into the non-periodic axis we experience.

% ============================================================================
\section{Physical testability of the identification $t\sim t+R_m$}
% ============================================================================

The topological identification $t \sim t + R_m$ is not a mere accompanying
structure of the duality but a physical observable. In the time reading its
period is \emph{exactly} the fundamental revolution time
\[
  T_\text{rev} \;=\; \frac{R_m}{c} \;=\; \frac{\xi\,\ell_P}{c}
  \;\approx\; 7.2\times10^{-48}\,\text{s},
  \qquad
  \Delta\phi \;=\; 2\pi\xi \;\approx\; 8.4\times10^{-4}\ \text{rad/revolution},
\]
so that $t\sim t+R_m$ is identical with $t\sim t+c\,T_\text{rev}$ (Doc.~183/185).
The compactness of the fourth direction \emph{is} the revival time.

\subsection{Two testable readings}
\begin{itemize}
  \item \textbf{Mass reading (mature, quantitative).} The discrete mode spectrum
  generates the particle masses as torus overtones with step $1/D$; from this
  follow Koide, $g\!-\!2$ and the three generations (Doc.~159, 258/259). Here the
  compactness is numerically realised.
  \item \textbf{Time reading (falsifiable, currently below resolution).} The
  periodicity produces a CHSH deviation from the Tsirelson bound of order $\xi$.
  For 73 qubits FFGFT predicts $\Delta \approx 5.4\times10^{-4}$ (resolvable at
  $\sigma\sim10^{-4}$). The hardware test IBM~Heron~r2 (May~2026) confirms the
  Bell violation ($S=2.74$) and the executability of T0 circuits; the $\xi$
  effect, however, lies below current NISQ noise and is not yet resolvable
  (Doc.~147).
\end{itemize}

\subsection{Scaling: linear versus logarithmic}

\begin{important}[Regime dependence of phase accumulation]
A naive \emph{coherent linear accumulation} $r\cdot\Delta\phi$ over $r$
revolutions would yield physically absurd phase drifts (of order
$10^{44}$~rad/s) and contradict working atomic clocks and deep quantum circuits.
The lab-testable prediction therefore scales \emph{logarithmically},
\[
  \delta\phi \;\sim\; \frac{\xi\,\ln(r)}{D_f}
  \;\approx\; 2\times10^{-4} \quad (D_f = 3-\xi),
\]
not linearly. The linear form $r\cdot\Delta\phi$ of Doc.~185 is the
\emph{worst-case bound of the RSA argument} (coherence over $r\approx N$ cycles),
not the lab prediction. This regime separation explains why deep coherent
circuits can run while the RSA factorisation of large keys remains geometrically
protected.
\end{important}

\paragraph{Conclusion.}
$t\sim t+R_m$ is carried in the FFGFT corpus as an observable ($T_\text{rev}$,
CHSH deviation $\sim\xi$): quantitatively confirmed in the mass reading,
falsifiable in the time reading but currently just below experimental
resolution. It is not an unfalsifiable accompanying structure.

% ============================================================================
\section{Classification and open questions}\label{sec:offen}
% ============================================================================

\paragraph{Connections.}
Doc.~185 (Time as the Embedding Price) provides the ontological basis of the
Type~I step; Doc.~268 (holographic projection) and Doc.~254 (area-bound theorem)
the framework for step~2; Doc.~206 (Triangle--Matrix reduction) confirms that
the 4D level is generative; Doc.~147/183 provide the time-side testability. The upward operation (Type~III)
is developed in Doc.~230 (bijective Hilbert-space translation), Doc.~231
(necessary extensions) and Doc.~206 (matrix representation); Doc.~171 justifies
the exclusion of geometrically higher dimensions.

\paragraph{Open points.}
\begin{enumerate}
  \item \textbf{Structural assumption -- confirmed.} The decomposition
  $T^4 = S^1_{x,y,z}\times S^1_m$ with $S^1_m$ as substitute-time direction and
  $\tilde{T}\cdot m = 1$ as translation is fixed (Rem.~\ref{bem:struktur}).
  \item \textbf{Linear/logarithmic scaling.} The linear worst-case bound
  $r\cdot\Delta\phi$ (Doc.~185, RSA regime) and the logarithmic lab prediction
  $\xi\ln(r)/D_f$ (Doc.~147) should be marked explicitly as regime-dependent to
  secure consistency of presentation.
  \item \textbf{Spatial limit -- clarified.} The decompactification
  $S^1_{x,y,z}\to\mathbb{R}^3$ is a \emph{limiting process}
  ($R_{x,y,z}\to\infty$), neither the Type~I duality nor a Type~II projection,
  but a distinct \emph{limit-type} information-preserving operation~(Ib). It is
  therefore carried in Step~1 explicitly apart from the mass-circle duality~(Ia);
  both share the embedding character, not the mechanism.
  \item \textbf{Holographic completeness.} To what extent can the Type~II loss
  at $D3\to D2$ be reconstructed exactly (not just partially) from boundary
  data? Connection to Doc.~254/268.
\end{enumerate}
