% ==============================================================================
% T0 Theory / FFGFT: Document 271 (Chapter Content, EN)
% Title: FFGFT (T0) compared with Helix-Light-Vortex (HLV)
% Author: Johann Pascher
% Date: June 2026
% References: Doc. 190, 206, 230, 268, 270; HLV (Krueger) Zenodo 20596861 / 20275888
% ==============================================================================

\section*{Abstract}
This work places FFGFT (T0, time--mass duality) and the Helix--Light--Vortex programme
(HLV, M.~Krüger) side by side. Both are \emph{layered effective geometric programmes}: they
replace the smooth continuum with a discrete, higher-dimensionally generated substrate, carry a
three-fold (triadic) core motif, read particles as topological objects, root in classical
proportion/harmonic geometry, and share a methodology of recovery limit plus null-model
falsification. We separate \emph{genuine isomorphisms} from \emph{surface analogies}. The central
difference: FFGFT carries \emph{one} dimensionless constant $\xi \approx 1/7500$ with forward
dimensionless predictions (fine-structure constant, Koide relation, lepton mass ratios), whereas
HLV has no $\xi$-analogue but an explicitly reproducible aperiodic substrate together with a
graph-Laplacian testbed against null models. The geometric fork \emph{aperiodic quasicrystal} (HLV)
versus \emph{periodic $T^4$ torus with a fractal correction} (FFGFT) yields a measurable spectral
difference, from which a \emph{distinguishing} prediction is formulated. HLV's
consciousness/biogravimetry layer is explicitly excluded from this physics comparison. As a shared
guardrail we stress the triviality of any representation $X=\varphi^{N}$ or $X=\xi^{N}$: forward
content lies solely in dimensionless ratios that are isolated, predicted, and precise; an absolute
scale remains a calibrated input.

% ============================================================================
\section{Motivation and scope}
% ============================================================================

HLV is now available in a deliberately \emph{conservative}, falsifiable form in two recent
documents: a \enquote{master explanation} (Zenodo 10.5281/zenodo.20596861) and a reproducible
\enquote{6D-to-3D cut-and-project graph testbed} (Zenodo 10.5281/zenodo.20275888). The move made
there -- away from \enquote{spacetime \emph{is} quasicrystalline} towards \enquote{can this
substrate be made explicit, reproducible, and distinguishable from simpler null models?} -- is
methodologically the same turn that FFGFT performed in its corrections register (Doc.~190, notably
the corpus-wide cleanup of the $H_0$ over-claims).

The aim here is a \emph{comparison}, not a merger: to test where the kinship is structurally
load-bearing, where it is merely verbal, and at which point the two programmes must \emph{diverge}
empirically.

% ============================================================================
\section{Common axes (overview)}
% ============================================================================

\begin{center}
\small
\begin{tabular}{@{}p{0.15\linewidth}p{0.40\linewidth}p{0.40\linewidth}@{}}
\hline
\textbf{Axis} & \textbf{FFGFT / T0 (Pascher)} & \textbf{HLV (Krüger)}\\
\hline
Substrate / projection
& compact 4-torus $T^4$ + fractal correction $D_f=3-\xi$; reduction chain $T^4\!\to\!T^0$
& aperiodic quasicrystal via cut-and-project ($\mathbb{Z}^5\!\to\!3$D), golden-ratio/Fibonacci\\
Time structure
& time--mass duality $\tilde T\cdot m=1$; $Z_3$ in the triangle reduction ($\det=1-\xi$)
& triadic spiral time $\psi(t)=t+i\varphi(t)+j\chi(t)$, $i^2=j^2=-1$\\
Particle ontology
& winding quantum numbers on $T^4$; Bell topological, not ontologically nonlocal
& vortices / standing-wave modes of a scalar field $\Psi$ in the lattice\\
Generative core
& \emph{one} dimensionless $\xi\approx 1/7500$
& no $\xi$-analogue; substrate geometry ($\varphi$, Fibonacci)\\
Forward predictions
& $\alpha$, Koide, lepton ratios (dimensionless, isolated)
& deliberately withheld; focus \enquote{is the substrate distinguishable?}\\
Recovery limit
& $\hbar,c,G$ as conversions; $O(\xi)$ lattice dispersion; bridges (with honest negatives)
& must recover QFT/GR in the limit; graph Laplacian vs.\ null models\\
Falsification channel
& mode spectrum ($T^4$): CMB peak \emph{ratios}, $B=1/3$ from $D=4$
& graph-Laplacian spectrum vs.\ null model; vortex benchmarks\\
\hline
\end{tabular}
\end{center}

% ============================================================================
\section{Genuine isomorphisms vs.\ surface analogies}
% ============================================================================

\begin{enumerate}
\item \textbf{Projection from higher dimensions.}
\emph{Resonance:} both read observed 3-space as the projection of a structured, higher-dimensional,
discrete geometry -- HLV via cut-and-project, FFGFT via the explicit chain $T^4\!\to\!T^0$ (Doc.~270).
\emph{But:} \emph{aperiodic} (quasicrystal) versus \emph{periodic} ($T^4$) are different spectral
classes -- see Section~6. The motif is isomorphic, the realisation is not.

\item \textbf{Triadic core motif.}
\emph{Resonance:} HLV's hypercomplex time $\psi=t+i\varphi+j\chi$ sits next to the $Z_3$ structure of
the FFGFT triangle reduction ($\det(A_\xi)=1-\xi$, Doc.~206) and the three operation types of the
reduction chain.
\emph{But:} HLV's triad is a \emph{time algebra}, FFGFT's a \emph{reduction-matrix symmetry}. The
shared \enquote{3} is striking but not yet a proven isomorphism -- a candidate for closer scrutiny,
not an identity.

\item \textbf{Particles as topological objects.}
\emph{Resonance:} HLV vortices / standing modes correspond to FFGFT winding numbers on the torus;
both relocate \enquote{quantum number} into a topological winding of the substrate. In FFGFT this also
renders the Bell correlation as topological (not ontologically nonlocal). Here the kinship is most
likely genuine.

\item \textbf{Harmonic/proportion root.}
\emph{Resonance:} HLV anchors in the golden ratio and Fibonacci; FFGFT in the Euler Tonnetz and the
comma structure of temperament. Same instinct (\enquote{proportion/harmony $\to$ fundamental
geometry}), different constant.

\item \textbf{Methodology.}
\emph{Resonance (strongest):} recovery limit plus null-model falsification. HLV's \enquote{distinguishable
from simpler null models} is exactly the criterion by which FFGFT tested whether, e.g., $63/4$ is
\emph{isolated} or merely one of several \enquote{nice fractions} in a dense candidate field (Doc.~190,
R35).
\end{enumerate}

% ============================================================================
\section{Divergences and complementarity}
% ============================================================================

\begin{itemize}
\item \textbf{Generative core.} FFGFT has a single dimensionless seed $\xi$ and from it \emph{forward}
predictions ($\alpha=\xi\,(E_0/\text{MeV})^2$, Koide, lepton ratios). HLV (in the documents presented)
has no such analogue and deliberately stays at \enquote{is the substrate distinguishable}. $\Rightarrow$
FFGFT brings the seed, HLV the reproducible substrate construction -- complementary, not competing.

\item \textbf{Tool.} HLV's graph-Laplacian testbed against null models is a numerical falsification
machinery that FFGFT could adopt for its own $T^4$ mode spectrum.

\item \textbf{Substrate.} Aperiodic vs.\ periodic + fractal -- a real geometric fork (Section~6).

\item \textbf{Foundational maturity.} HLV has drawn external-review criticism of an under-specified,
non-closed algebra and undefined operators; FFGFT works with a three-layer discipline (core
derivations / algebraically proven bridges / plausibility reductions) and the Hilbert-space bridge
(Doc.~230--232).

\item \textbf{Scope.} HLV includes a consciousness/biogravimetry layer. This is \emph{explicitly
excluded} here: the present comparison concerns only the physical-geometric layers.
\end{itemize}

% ============================================================================
\section{Distinguishing prediction: the spectral fork}
% ============================================================================

The scientifically robust core of the comparison is spectral. A \emph{periodic} substrate ($T^4$)
produces a discrete spectrum with integer mode labels $|n|^2$ and a harmonic, ladder-like structure;
FFGFT reads off dimensionless CMB peak ratios $1 : 2.449 : 3.742 : \dots$, fixed by $D=4$ (curvature
parameter $B=1/3$). An \emph{aperiodic} substrate (quasicrystal), by contrast, typically produces a
hierarchical, gap-rich spectrum (singular-continuous density of states, Cantor-like gap structure)
\emph{without} a simple integer harmonic ladder.

These two signatures are \emph{distinguishable}. Concrete (scale-free) test:
\begin{enumerate}
\item Run HLV's testbed with (a) the quasicrystal \emph{and} (b) a \emph{periodic} lattice null model --
not only randomised nulls. The sharp question is aperiodic-vs-periodic, not discrete-vs-continuum.
\item Report the leading \emph{deviation exponent} in the recovery limit: does the graph-Laplacian
dispersion approach the continuum $\omega\propto|k|$, and is the residual $O(\text{small})$ and
sign-definite? (FFGFT does exactly this with $O(\xi)$ corrections.)
\item Compare scale-free \emph{spectral ratios}: the harmonic $T^4$ ratio spectrum against the
quasicrystal gap spectrum -- and both against data (CMB peaks resp.\ lattice benchmarks). Whichever
ratio spectrum matches observation discriminates the substrates.
\end{enumerate}

% ============================================================================
\section{Shared methodological guardrail}
% ============================================================================

For \emph{both} programmes: every magnitude can be written as $\varphi^{N}$ or $\xi^{N}$; a single
measured scale in an exponent is therefore \emph{not} a prediction. Forward content lies solely in
dimensionless ratios that are simultaneously \emph{isolated}, \emph{predicted}, and \emph{precise}. The
absolute scale (in FFGFT $H_0$/$R_H$ via the fitted exponent $41/4$) remains a calibrated input, not
evidence (Doc.~190, R35). An honest HLV prediction should likewise be a \emph{scale-free} ratio from
the graph-Laplacian spectrum, not an absolute magnitude dressed in $\varphi$.

% ============================================================================
\section{Status and next steps}
% ============================================================================

This work is a structural mapping, not a unification claim. It remains open whether the triadic
resonance is a genuine isomorphism or a coincidence, and whether either substrate matches the
observed mode spectrum better. The obvious next step is a \emph{joint} testbed run: HLV's graph
Laplacian against a periodic null lattice, plus the scale-free ratio comparison with the $T^4$
spectrum. Only then -- falsification before interpretation -- is a statement about the kinship of the
two geometries defensible.

% ============================================================================
\section{Sources}
% ============================================================================

\begin{itemize}
\item M.~Krüger, \emph{A Conservative Master Explanation of the Helix--Light--Vortex Framework},
Zenodo (2026), doi:10.5281/zenodo.20596861.
\item M.~Krüger, \emph{A Reproducible 6D-to-3D Cut-and-Project Graph Testbed for Quasicrystalline
Laplacian Recovery and Vortex Benchmarks}, Zenodo (2026), doi:10.5281/zenodo.20275888.
\item FFGFT: Doc.~190 (corrections register, R35), Doc.~206 (triangle reduction, $Z_3$), Doc.~230--232
(Hilbert-space bridge), Doc.~268 (CMB peaks from $T^4$), Doc.~270 (reduction chain $T^4\!\to\!T^0$).
\end{itemize}
