% ==============================================================================
% T0 Theory / FFGFT: Document 277 (Chapter Content, EN)
% Title: Wave Propagation and Energy -- local conservation, redshift as a
%        change of bookkeeping, and the disappearance of the dark sector in
%        the static T^4 cosmos
% Author: Johann Pascher
% Date: June 2026
% References: Doc. 009 (xi origin), 038 (Markov determinism),
%             166 (Casimir/H0 xi ladder), 182 (maximal scale, calibrated),
%             230 (Hilbert-space translation), 267 (cosmological degeneracy),
%             268 (CMB peaks from T^4), 270 (projection chain T^4 -> T^0),
%             190 (correction register, P35/P36 calibration guardrail)
% External sources: Noether 1918; Poynting 1884; Jackson; MTW; Wald;
%             Breit-Wheeler 1934
% Status: worked-out, source-referenced version of the short note of the same title
% ==============================================================================

% local environment (EN preamble leaves 'warning' for document-local definition)
\newtheorem{warnthm}[theorem]{Warning}

\section*{Abstract}
A propagating wave \emph{always} carries a well-defined, positive energy:
electromagnetically through the Poynting flux, quantized as $E=\hbar\omega$ per
quantum, mechanically through radiation pressure. This document cleanly
separates two levels that are constantly conflated in popular accounts: the
\emph{local} energy balance (always satisfied,
$\partial_t u + \nabla\!\cdot\mathbf S = 0$ resp.\
$\nabla_\mu T^{\mu\nu}=0$) and the \emph{global} balance, which in curved,
time-non-stationary spacetime is not uniquely definable. The widespread
fallacy \enquote{energy is not conserved} (meaning: \emph{destroyed})
mistakes a level of bookkeeping for physical destruction. In the FRW model the
non-definability of total energy follows from the absence of a timelike
Killing field (Noether); it is not a violation of local physics. In the FFGFT
reading $\hbar$ and $c$ are SI conversion factors; the physical content lies in
the dimensionless ratios ($\tilde T\cdot m = 1$). The measured absolute energy
is observer-dependent, the ratio structure invariant. On a \emph{static}
compact 4-torus $T^4$ the time-translation symmetry exists again; by Noether
the total energy is then well-defined and conserved. Redshift thereby becomes a
pure scale- and observer-rebooking rather than metric stretching of space, and
the main motivation for dark energy (accelerated expansion) as well as part of
the motivation for dark matter (CMB peak fit) disappears -- the relevant
structure follows in FFGFT from the $T^4$ geometry and from $\xi$ (Doc.~267/268).
This cosmological conclusion is framed at the status of the degeneracy thesis
(Doc.~267): on the \emph{data} both models are equivalent, on the theoretical
\emph{structure} FFGFT is the more economical reading (no dark sector, global
energy conservation). $R_H$ is here a shared empirical scale reference, not a
free parameter -- not an empirical knock-out of $\Lambda$CDM, but an economy
argument.

% ============================================================================
\section{Framing: why this separation is necessary}
% ============================================================================

The statement \enquote{a wave without energy would not be a wave} is trivially
true and yet the starting point of a stubborn misunderstanding. In the
cosmological discussion the correct technical observation \enquote{in an
expanding universe there is no globally unique total energy} is regularly
turned into the false conclusion \enquote{energy is destroyed}. The two live on
different levels.

\begin{definition}[Two levels of balance]\label{def:levels277}
\begin{description}
  \item[Local balance] The continuity equation of the energy--momentum tensor,
    $\nabla_\mu T^{\mu\nu}=0$, resp.\ in flat space
    $\partial_t u + \nabla\!\cdot\mathbf S = 0$. A statement about \emph{flux}:
    energy vanishes nowhere, it flows. Always satisfied.
  \item[Global balance] The existence of a unique, conserved \emph{total
    energy} of the system. By Noether tied to time-translation symmetry; in
    non-stationary curved spacetimes not uniquely definable.
\end{description}
\end{definition}

\begin{warnthm}[The category error]
\enquote{Globally not uniquely definable} is a statement about the
\emph{bookkeeping level}. \enquote{Physically destroyed} would be a violation
of local physics -- and that never occurs. Equating the two is the actual
error.
\end{warnthm}

This document works out the short note of the same title, substantiates the
individual steps, and embeds them in the corpus: in the units question
(Doc.~166, 182, 230), in the reduction structure (Doc.~270), and in the
cosmological degeneracy (Doc.~267/268).

% ============================================================================
\section{Local energy balance -- always satisfied}
% ============================================================================

\subsection{Electromagnetic field}

For the electromagnetic field the energy density and the Poynting
vector are~\cite{poynting1884,jackson}
\begin{equation}
  u = \frac{\varepsilon_0}{2}\,|\mathbf E|^2
      + \frac{1}{2\mu_0}\,|\mathbf B|^2,
  \qquad
  \mathbf S = \frac{1}{\mu_0}\,\mathbf E\times\mathbf B,
  \label{eq:poynting277}
\end{equation}
with $\mathbf S$ as the energy flux density. The energy continuity equation
reads
\begin{equation}
  \frac{\partial u}{\partial t} + \nabla\!\cdot\mathbf S = -\,\mathbf J\!\cdot\mathbf E,
  \qquad\text{in vacuum}\quad
  \frac{\partial u}{\partial t} + \nabla\!\cdot\mathbf S = 0.
  \label{eq:cont277}
\end{equation}
It is a \emph{local} conservation statement: any decrease of the energy density
at a point is exactly balanced by outflowing flux. Energy vanishes nowhere.

\subsection{Quantization and radiation pressure}

When quantized, each quantum carries
\begin{equation}
  E = \hbar\omega, \qquad
  p = \hbar k = \frac{E}{c}, \qquad
  P_\text{rad} = \frac{S}{c},
  \label{eq:quant277}
\end{equation}
with momentum $p$ and radiation pressure $P_\text{rad}$. As long as the wave
propagates, energy flows -- with measurable flux density, measurable pressure,
measurable photoelectric effect.

\begin{insight}[Operational content]
The local balance is non-negotiable because it is coupled to three independent
measurable quantities: flux density $S$, radiation pressure
$P_\text{rad}=S/c$, and the photoelectric threshold via $E=\hbar\omega$. A
\enquote{propagating wave without energy} would contradict all three.
\end{insight}

% ============================================================================
\section{Redshift: observer-dependent, not a loss into nothing}
% ============================================================================

Under cosmological redshift the measured wavelength scales; a given observer
measures $E = hc/\lambda$ correspondingly smaller. This does \emph{not} mean
that energy disappears, but that the question \enquote{how much energy} is
frame- resp.\ observer-dependent.

\begin{proposition}[Frame dependence of the photon energy]\label{prop:frame277}
The photon energy is the time component of a four-momentum, $E = p^\mu u_\mu$,
i.e.\ the scalar product with the observer's four-velocity $u_\mu$. It is
therefore not an invariant quantity but observer-dependent. An observer
comoving at the time of emission measures the full energy; an observer in
relative motion measures a different value. What remains \emph{invariant} are
ratios (frequency, energy, mass ratios).
\end{proposition}

Energy here is thus a relative, observer-dependent quantity -- not a destroyed
one. This statement is model-independent (it holds in $\Lambda$CDM just as in
FFGFT); what differs between the models is the \emph{interpretation} of $z$
(Section~\ref{sec:cosmo277}).

% ============================================================================
\section{The global fallacy -- Noether precisely}
% ============================================================================

\begin{theorem}[Noether: energy conservation from time-translation symmetry]
\label{thm:noether277}
A globally conserved total energy exists if and only if the spacetime possesses
a timelike Killing field $\xi^\mu$, i.e.\ a time-translation symmetry
$\nabla_{(\mu}\xi_{\nu)}=0$~\cite{noether1918,wald,mtw}.
\end{theorem}

An expanding FRW universe possesses no timelike Killing field, hence no global
time-translation symmetry, hence no uniquely defined global total energy. This
is a statement about the \emph{non-existence of a unique global balance}, not
about physical destruction. Locally,
\begin{equation}
  \nabla_\mu T^{\mu\nu} = 0
  \label{eq:covcons277}
\end{equation}
always holds.

\begin{remark}[Where this usually goes wrong]
The common crude error reads \enquote{energy is simply not conserved} --
meaning destroyed. The correct statement is: in FRW the \emph{global}
bookkeeping is not unique because the symmetry argument of
Theorem~\ref{thm:noether277} does not apply.
Equation~\eqref{eq:covcons277} is unaffected by this.
\end{remark}

% ============================================================================
\section{Absorption: energy is converted, not destroyed}
% ============================================================================

Upon absorption the wave gives up its energy and changes form: photoelectric
effect, heating, above threshold pair production. The kinematics requires a
second partner: a single free photon cannot create a pair because of
simultaneous energy and momentum conservation.
\begin{equation}
  \gamma\gamma \to e^+ e^-
  \quad(\text{Breit--Wheeler}~\cite{breitwheeler1934}),
  \qquad
  \gamma + N \to e^+ e^- + N
  \quad(E \geq 2 m_e c^2).
  \label{eq:pair277}
\end{equation}
Here too the local balance~\eqref{eq:cont277}/\eqref{eq:covcons277} remains
satisfied at all times: the energy changes form, not existence.

% ============================================================================
\section{FFGFT view: energy as a partly unit-bookkeeping quantity}
% ============================================================================

In FFGFT $\hbar$ and $c$ are SI conversion factors, not ontological primitives;
the physical content lies in the dimensionless ratios. The fundamental relation
\begin{equation}
  \tilde T \cdot m = 1
  \qquad(\text{natural units } \hbar = c = 1)
  \label{eq:Tm277}
\end{equation}
makes this explicit: $E \leftrightarrow 1/\tilde T$ and
$m \leftrightarrow 1/\tilde T$.

\begin{insight}[The ratio structure is invariant]
\enquote{How much energy} depends on the unit and observer convention; the
ratio structure (mass, frequency, energy ratios) is invariant. This is exactly
consonant with Proposition~\ref{prop:frame277}: the absolute value of the
measured energy is observer-dependent, the invariant ratios remain.
\end{insight}

In this reading \enquote{light $\to$ matter} is the binding of free phase
(light) into mode content (mass): the energy changes the level of accounting,
not its existence. The representational side of this statement -- that the same
4D content is losslessly translatable between $T^4$ geometry and Hilbert-space
language -- is worked out in Doc.~230; the reduction chain $T^4\to T^0$ with the
duality decompactification of the mass dimension via $\tilde T\cdot m=1$ in
Doc.~270.

\begin{remark}[Unit bookkeeping instead of ontology]
The label \enquote{partly unit-bookkeeping} is to be read precisely: the
\emph{flux} and the \emph{pressure} (Section~3) are operational,
unit-independent facts. What hangs on the convention is solely the assignment
of an absolute value \enquote{energy} to a given mode content -- the choice of
scale in which one counts.
\end{remark}

% ============================================================================
\section{Cosmological consequence: static $T^4$, no dark sector}
\label{sec:cosmo277}
% ============================================================================

FFGFT lives on a compact, \emph{static} 4-torus $T^4$. There is no metric
expansion of space -- and with it the motivation for dark energy ($\Lambda$)
disappears, as does part of the motivation for dark matter. This has an
immediate, simplifying effect on the energy discussion above.

\begin{proposition}[Global energy conservation is restored]
\label{prop:global277}
A static $T^4$ background possesses a timelike time-translation symmetry. By
Theorem~\ref{thm:noether277} the total energy is then well-defined and
conserved. The fallacy in the context of Theorem~\ref{thm:noether277}
(\enquote{no unique global energy}) is a consequence of the \emph{expansion
assumption}; without it one need not retreat to \enquote{globally undefinable}
in the first place.
\end{proposition}

\paragraph{1. Redshift $=$ change of bookkeeping, not stretching of space.}
Without expansion, redshift is not a stretching of the wavelength by growing
space. It is the scale- and observer-rebooking encoded in
$\tilde T\cdot m = 1$~\eqref{eq:Tm277}: the energy and time scale of the distant
source is referenced differently relative to the local standard. The photon
carries its energy throughout (Sections~3); $z$ is the conversion between
source and observer bookkeeping -- exactly the observer-dependent, relative
energy of Proposition~\ref{prop:frame277}, only without the FRW apparatus.

\paragraph{2. No dark sector needed.}
$\Lambda$CDM needs dark energy to drive an accelerated expansion, and dark
matter inter alia to fit the CMB peak structure. If expansion is removed, the
main task of dark energy is gone. The relevant structure -- e.g.\ the position
of the CMB peaks -- follows in FFGFT from the $T^4$ geometry and from $\xi$
instead of from an expansion-plus-dark fit: the peak ratios are derived in
Doc.~268 from the degeneracies $g(|\vec n|^2)$ of the $T^4$ modes, the scale
ladder (Casimir/CMB/$H_0$) in Doc.~166.

\begin{table}[ht]
\centering
\caption{Theoretical cost of the two readings of the \emph{same} data.}
\label{tab:cost277}
\begin{tabular}{@{}lll@{}}
\toprule
 & $\Lambda$CDM pays & FFGFT \\
\midrule
Accelerated expansion & dark energy $\Lambda$ required &
  not needed (no expanding space) \\
CMB peak fit & dark matter, inter alia &
  from $T^4+\xi$ (Doc.~268) \\
Global energy & not conserved (FRW, no Killing field) &
  conserved (Noether, static $T^4$) \\
\enquote{energy disappears} & lives here as a fallacy &
  dissolves \\
\bottomrule
\end{tabular}
\end{table}

\begin{warnthm}[Status: degenerate on the data, asymmetric in cost]\label{warn:degeneracy277}
On the \emph{data} level the models are degenerate (Doc.~267): SNe~Ia, BAO, and
CMB temperature do not distinguish between metric expansion ($\Lambda$CDM) and
fractal time unfolding (FFGFT) -- the same data, two readings. On the
\emph{structure} level, however, the costs are \emph{not} symmetric
(Tab.~\ref{tab:cost277}): $\Lambda$CDM carries dark energy and dark matter as
free components and gives up global energy conservation; FFGFT pays none of
these. Under empirical equivalence, theoretical economy decides -- and there
FFGFT is the more economical reading. This is a parsimony argument (Occam), not
an empirical knock-out of $\Lambda$CDM.
\end{warnthm}

\begin{remark}[$R_H$ is a scale reference, not an input]
$R_H$ \emph{need not} follow from $\xi$ -- it is a scale reference like any
system-specific upper bound $R_\text{Torus}(m)=\hbar/mc$ (Doc.~182). The
relation Planck length$\leftrightarrow R_H$ (exponent $41/4$,
$R_H/L_0 = 6.49\times10^{64}$) is derived from first principles by \emph{no}
framework: why the universe is $\sim$\,$10^{60}$ Planck lengths across is
predicted by no theory. $\Lambda$CDM fixes the relation via the measured $H_0$
-- itself circular in the sense of the degeneracy (Doc.~267); FFGFT adopts the
established value for comparability and writes it in $\xi$ notation (Doc.~190
P35/P36). This is a \emph{shared empirical reference point} of both models, not
a free parameter and not an FFGFT-specific gap. In FFGFT, moreover, $\hbar, c$
are SI conversion and $G$ is derived ($\xi\to\{m_e,\ldots\}\to G\to\ell_P$);
a \enquote{measured} dimensional anchor in the standard-physics sense does not
even exist here. The only asymmetry remains the dark sector, carried by
$\Lambda$CDM alone.
\end{remark}

% ============================================================================
\section{Methodological placement}
% ============================================================================

The \enquote{local vs.\ global} separation introduced in
Definition~\ref{def:levels277} is structurally the same pattern as elsewhere in
the corpus: a deterministic, locally fully determined structure whose global or
absolute accounting depends on the chosen level of resolution or convention
(cf.\ Markov determinism, Doc.~038). The error \enquote{energy is destroyed}
arises when one reads a missing global bookkeeping as a physical statement --
exactly the kind of fallacy the correction register (Doc.~190) is written to
guard against.

\begin{insight}[What this document shows]
(i)~A propagating wave always carries positive energy; (ii)~locally, energy is
always conserved; (iii)~redshift is observer-dependent, not a loss;
(iv)~\enquote{globally non-unique} $\neq$ destroyed; (v)~in a static $T^4$ the
total energy is even globally conserved and $z$ a pure rebooking. On the
\emph{data}, $\Lambda$CDM and FFGFT are degenerate; on the \emph{structure},
FFGFT is the more economical reading (Tab.~\ref{tab:cost277}). The cosmic scale
$R_H$ is a shared empirical reference point, not a free parameter -- the
asymmetry lies solely in the dark sector.
\end{insight}

% ============================================================================
\section{Summary}
% ============================================================================

\begin{itemize}
  \item Propagating wave $\Rightarrow$ always positive energy
        (Poynting~\eqref{eq:poynting277}, $E=\hbar\omega$~\eqref{eq:quant277}).
  \item Locally, energy is always conserved
        ($\partial_t u+\nabla\!\cdot\mathbf S=0$~\eqref{eq:cont277};
        $\nabla_\mu T^{\mu\nu}=0$~\eqref{eq:covcons277}).
  \item Redshift is observer-dependent (Proposition~\ref{prop:frame277}) --
        not a loss into nothing.
  \item No unique global energy (no time symmetry,
        Theorem~\ref{thm:noether277}) $\neq$ energy destroyed.
  \item FFGFT: energy is partly unit bookkeeping; physically it is the ratios
        ($\tilde T\cdot m = 1$~\eqref{eq:Tm277}; Doc.~230/270).
  \item Static $T^4$ cosmos (no expansion): global energy conservation holds
        (Proposition~\ref{prop:global277}), redshift is pure rebooking, the dark
        sector is not needed. Degenerate on the data (Doc.~267/268/166), more
        economical in cost (Tab.~\ref{tab:cost277}); $R_H$ is a shared scale
        reference, not a free parameter -- the asymmetry is solely the dark
        sector.
\end{itemize}

\paragraph{Connections.}
Doc.~270 (projection chain $T^4\to T^0$, duality decompactification via
$\tilde T\cdot m=1$), Doc.~230 (lossless translation $T^4\leftrightarrow$
Hilbert space), Doc.~267 (cosmological degeneracy $\Lambda$CDM vs.\ FFGFT),
Doc.~268 (CMB peaks from $T^4$), Doc.~166 (Casimir/CMB/$H_0$ as a $\xi$ power
ladder), Doc.~182 (maximal scale $R_H$, calibrated), Doc.~190 (correction
register, P35/P36).

\begin{thebibliography}{9}

\bibitem{noether1918}
E.~Noether,
\emph{Invariante Variationsprobleme},
Nachr.\ d.\ König.\ Gesellsch.\ d.\ Wiss.\ zu Göttingen,
Math-phys.\ Klasse (1918) 235--257.

\bibitem{poynting1884}
J.~H.~Poynting,
\emph{On the Transfer of Energy in the Electromagnetic Field},
Phil.\ Trans.\ R.\ Soc.\ Lond.\ \textbf{175} (1884) 343--361.

\bibitem{jackson}
J.~D.~Jackson,
\emph{Classical Electrodynamics}, 3rd ed.,
Wiley (1998), Ch.~6 (Poynting theorem) and Ch.~7.

\bibitem{breitwheeler1934}
G.~Breit, J.~A.~Wheeler,
\emph{Collision of Two Light Quanta},
Phys.\ Rev.\ \textbf{46} (1934) 1087--1091.

\bibitem{mtw}
C.~W.~Misner, K.~S.~Thorne, J.~A.~Wheeler,
\emph{Gravitation},
Freeman (1973), Ch.~25 (Killing fields, conserved quantities).

\bibitem{wald}
R.~M.~Wald,
\emph{General Relativity},
University of Chicago Press (1984), Sec.~C.3 (Killing fields and conservation
laws).

\bibitem{dok270}
J.~Pascher, \emph{Doc.\,270: Projection chain $T^4\to T^0$ -- two types of
dimensional reduction}, FFGFT corpus (2026).

\bibitem{dok230}
J.~Pascher, \emph{Doc.\,230: Translatability FFGFT $\leftrightarrow$
Hilbert-space quantum mechanics}, FFGFT corpus (2026).

\bibitem{dok267}
J.~Pascher, \emph{Doc.\,267: Cosmological degeneracy -- $\Lambda$CDM and FFGFT
as two readings of the same observations}, FFGFT corpus (2026).

\bibitem{dok268}
J.~Pascher, \emph{Doc.\,268: CMB acoustic peaks from the $T^4$ lattice
structure}, FFGFT corpus (2026).

\bibitem{dok166}
J.~Pascher, \emph{Doc.\,166: The Casimir scale as cosmic link -- Casimir
effect, CMB and $H_0$ in a $\xi$ power ladder}, FFGFT corpus (2026).

\bibitem{dok182}
J.~Pascher, \emph{Doc.\,182: Maximal scale of the universe -- $R_H$ as a
calibrated cosmic scale in $\xi$ notation}, FFGFT corpus (2026).

\bibitem{dok190}
J.~Pascher, \emph{Doc.\,190: Correction register FFGFT/T0 (K1--K4, P1--P38),
P35/P36 calibration guardrail}, FFGFT corpus (2026).

\bibitem{dok038}
J.~Pascher, \emph{Doc.\,038: Markov determinism -- deterministic substrate,
statistical description under lacking resolution}, FFGFT corpus (2026).

\bibitem{dok009}
J.~Pascher, \emph{Doc.\,009: Origin of $\xi = 4/30000$}, FFGFT corpus (2026).

\end{thebibliography}
