% ==============================================================================
% T0 Theory / FFGFT: Document 286 (chapter content, EN)
% Title: The dynamic sector -- kinetic energy as a xi-fractal fraction of the
%        static (T~ * m = 1)
% Author: Johann Pascher
% Date: 21 June 2026
% References: Doc. 047, 067, 080, 204, 255, 263, 285.
% Scripts: kinetik_xi_anteil.py
% Character: problem-statement / research-programme document. It records what is
%   fixed, the single data point, the narrowing, and the structural lead -- and
%   marks the open gap explicitly. No claimed derivation.
% ==============================================================================

\section*{Abstract}
Through the duality $\tilde T\cdot m=1$, FFGFT separates two energy types: \emph{static} (rest mass
$=$ topologically frozen winding, the crystallographic Z$_3$ core) and \emph{kinetic} (free; for
massless states the only form, $E=hf$). The static sector is derived and computed (Z$_3$ mass
operator $+$ mass circle; Doc.~285, BD12-XCORE). The dynamic sector is \emph{not}: the derived rule
that computes the kinetic part, via the duality, as a $\xi$-fractal fraction of the static one is
missing. This document is a \emph{problem-statement document} -- it records what is fixed (the
duality places the window in the kinetic sector), the single existing data point (neutrino,
$m_\nu\sim\xi^2/2\,m_e$, as an ansatz), the narrowing of the $\xi$-power to $p=2$, and the structural
lead $m_{\text{window}}=\xi\cdot\omega$. What remains to be derived is marked explicitly as open. Prefixed is the fixed, reversible Hilbert-space foundation (Doc.~282/270/230) the sector sits on; its actual aim is to find, out of the Hilbert space, the complementary description that maps via $D_f=3-\xi$ and $\xi$ onto SI units.

% ==============================================================================
\section{Where the question comes from}
% ==============================================================================
In Doc.~255, $\tilde T\cdot m=1$ enforces two energy types. The rest mass is \emph{static}: a
topologically stable winding number on $T^4$, fixed in the compact picture by the Z$_3$ mass operator
($r=\sqrt2$, $\theta=2/9$). The kinetic energy is \emph{free}; for a massless particle it is the only
form ($E=hf$). \enquote{Mass is frozen kinetic energy.}

Doc.~285 shows that the empty recursion windows ($3'$, $3''$, \dots) carry no \emph{new} masses but
structure; and that a \emph{dynamics} filling a window supplies the \emph{kinetic} type -- a filled
window is photon-/neutrino-like, not a massive triple. There the gap was named: the \emph{derived}
rule computing the kinetic part, via the duality, as a $\xi$-fractal fraction of the static one is
missing. This document takes up exactly that gap. It is the \enquote{further work} on the dynamic
sector announced in Doc.~285.

% ==============================================================================
\section{The fixed foundation: the reversible Hilbert-space basis}
% ==============================================================================
Before developing the dynamic sector, let the fixed foundation it sits on be recorded. The FFGFT QM
translation (Doc.~282) is closed in three pieces:
\begin{enumerate}
  \item \textbf{The unambiguous Hilbert map} (Type~III, Doc.~270): $\mathcal H=L^2(T^4)\otimes
  \mathbb C^3$, states $=$ fiber-valued fields, QM operation $=$ unitary parallel transport,
  entanglement $=$ holonomy around cycles (Doc.~230), three masses $\leftrightarrow(M,r,\theta)$. A
  \emph{bijection} -- fully reversible.
  \item \textbf{The time-free mass form:} mass sits on a separate tensor factor; CHSH $=2\sqrt2$
  stays identical with and without the $\mathbb C^3$ fiber to $4\cdot10^{-16}$ -- no static QM result
  changes. Time is \emph{not computed} here; the reduced dynamics is time-local, unitary, Markovian.
  \item \textbf{The time form:} adds exactly \emph{one} effect -- non-Markovian memory in the reduced
  dynamics (backflow $0\to0.53$, CP-divisibility violated) -- which itself still lies within QM: a
  traced-out unitary bath reproduces it (Doc.~282/283). At the full level, therefore, unitary/reversible.
\end{enumerate}
Reversibility is precise \emph{per type} (Doc.~270): Type~III (Hilbert) fully reversible; Type~I
(mass circle $\to$ time, \enquote{time taken into the space}) \emph{almost} reversible -- lossless in
mode content, only the winding number stays ambiguous; Type~II (spatial projection $D3\!\to\!D0$)
\emph{not} reversible. The only genuine irreversibility is the spatial projection -- the measurement /
decompactification (Doc.~270/284) --, not the time-inclusion. The non-Markovian memory is not a break
of reversibility but the reduced view.

\paragraph{Aim of the dynamic sector.} On this fixed, reversible foundation, the actual task is the
\emph{Hilbert-space extension and its translation}: \emph{another} description \emph{out of the Hilbert space} -- the complementary,
decompactified/projected side that maps computationally, via $D_f=3-\xi$ and $\xi$, onto SI units. The
SI map is exactly the measurement/projection side (Type~I/II), and $D_f$ and $\xi$ are the bridge
quantities (Doc.~270/249/133). The dynamic sector is thus not a departure from the foundation but its
unrolling into measurable units -- and the sought kinetic $\xi$-fraction is one building block of
exactly that unrolling.

% ==============================================================================
\section{What is fixed}
% ==============================================================================
The duality fixes the \emph{placement}, not the size. With $\tilde T=1/\max(m,\omega)$
(Doc.~067, 080), an almost-massless window state has $\omega\gg m$, hence $\tilde T=1/\omega$: the
state sits in the \emph{kinetic} sector. That is secure. So is the conceptual separation:
\begin{center}
\begin{tabular}{lll}
\toprule
 & static & kinetic \\
\midrule
form        & $E_0=mc^2$ (rest)            & $E=hf$ (free) \\
seat        & Z$_3$ core (winding)         & window, when a dynamics runs \\
time        & $\tilde T=1/m$               & $\tilde T=1/\omega$ \\
status      & derived (Doc.~285)           & \emph{open} (this document) \\
\bottomrule
\end{tabular}
\end{center}
A distinction between two kinetic quantities matters: the ordinary kinetic energy of the electron,
$(\gamma-1)mc^2$ (Doc.~080), is \emph{not} $\xi$-suppressed. The $\xi$-fractal fraction sought here
is the \emph{window rest-mass} of an otherwise massless state -- not the kinetic energy of a massive
one.

% ==============================================================================
\section{The single data point: the neutrino}
% ==============================================================================
Doc.~047 treats the neutrino as a \enquote{near-massless photon}: $E^2=(pc)^2+(\sqrt{\xi^2/2}\,
mc^2)^2$, with $v_\nu=c\,(1-\xi^2/2)\approx0.9999999911\,c$ and $m_\nu\sim\tfrac{\xi^2}{2}m_e$.
This is the only existing value for a window rest-mass as a $\xi$-power of a core mass. It is,
however, explicitly an \emph{ansatz} (from the velocity/photon analogy), not \emph{derived} from the
duality. Doc.~204 additionally supplies a $\xi$-correction to the kinetic energy ($+0.69\,\xi_0$).
There are no further data points; in particular, a single value is not enough for the $\Delta m^2$
spectrum.

% ==============================================================================
\section{Narrowing the $\xi$-power: $p=2$}
% ==============================================================================
With the ansatz $m_{\text{window}}=C\cdot\xi^p\cdot m_{\text{ref}}$, tested against the bounds
(reproducing the $\xi^2/2$ value; the photon limit; dimensional consistency; an oscillation floor
$\gtrsim\!\sqrt{\Delta m^2_{\text{atm}}}\approx 49$~meV; a direct kinematic bound $m_\nu\lesssim0.8$~eV (KATRIN, model-independent)),
only $p=2$ is compatible with the meV scale: $p=1$ gives $\mathcal{O}(10\text{--}70)$~eV (far above
the bound), $p\ge3$ falls below every anchor. So $p=2$ is the \emph{unique} order-of-magnitude
compatible power -- a genuine order-of-magnitude bound, not a fit.

\paragraph{Numerology warning.} \emph{Within} $p=2$, the coefficient ($\tfrac12$) and the reference
mass are \emph{not} fixed by the single anchor. Different references land somewhere in the neutrino
window (e.g.\ $\xi^2/2\cdot m_e\approx4.5$~meV, $\xi^2\cdot m_e\approx9$~meV,
$\xi^2/2\cdot\sqrt{m_e m_\mu}\approx65$~meV). This is \emph{not} evidence but the P35 trap:
coefficient and reference need a derivation, not tuning. Computed: \texttt{kinetik\_xi\_anteil.py}.

% ==============================================================================
\section{The structural lead: $m_{\text{window}}=\xi\cdot\omega$}
% ==============================================================================
The Doc.~047 velocity expression $v_\nu=c(1-\xi^2/2)$ is exactly equivalent to a $\xi^1$ relation.
For $m\ll p$ one has $v/c=1-\tfrac12(m/p)^2$; substituting gives $(m/p)^2=\xi^2$, hence
\begin{equation}
m_{\text{window}}=\xi\cdot p\;\;\big(\approx \xi\cdot\omega\ \text{via}\ \tilde T\cdot m=1\big).
\end{equation}
The \enquote{$\xi^2$} in the notation \enquote{mass $=\xi^2/2\cdot m_e$} is thus presumably the
\emph{square image} of a fundamental $\xi^1$ relation: the static rest-mass is $\xi$ times the
kinetic scale. This is the natural anchor for a derivation \emph{via the duality}, because
$\omega=1/\tilde T$ is exactly the duality quantity. The open question therefore shifts from
\enquote{why $\xi^2$?} to \enquote{why $\xi^1$ between rest-mass and kinetic scale, and what sets
$\omega$ absolutely?}.

% ==============================================================================
\section{What remains to be derived}
% ==============================================================================
Three points are explicitly open:
\begin{enumerate}
  \item \textbf{The reference/scale -- largely closed} (next section). The two lab anchors select the
  reference as the \emph{single} FFGFT scale $E_0=\sqrt{m_e m_\mu}$; in its units $\omega/E_0=\xi/2$
  and $m_{\text{window}}/E_0=\xi^2/2$. Residual: the \emph{one} structural statement $\omega=\xi\,E_0$
  (exactly one fractal $\xi$-power).
  \item \textbf{The coefficient.} The factor $\tfrac12$ in $\xi^2/2$ is not derived; possibly it is
  purely the velocity square ($\tfrac12(m/p)^2$), i.e.\ no free factor at all.
  \item \textbf{The spectrum.} A single $\xi$-fractal value sets the \emph{scale}, not the
  \emph{spectrum} ($\Delta m^2_{\text{sol}}$, $\Delta m^2_{\text{atm}}$, mixing angles). That demands
  the specified $T^7$ dynamics (the second open computation, Doc.~285).
\end{enumerate}

% ==============================================================================
\section{Closing the scale question: the lab anchors select $E_0$}
% ==============================================================================
The first open point -- what sets $\omega$ absolutely -- closes further than a free parameter would. In
FFGFT there is only \emph{one} absolute scale; everything else is dimensionless ratios. The question is
therefore not \enquote{which number} but \enquote{which of the existing scales}. With
$m_{\text{window}}=\tfrac{\xi^2}{2}\cdot\text{reference}$, the two \emph{lab} anchors (oscillation floor
$\gtrsim49$~meV; KATRIN $\lesssim0.8$~eV) bracket the reference:
\begin{center}
\begin{tabular}{lccc}
\toprule
reference & $m_{\text{window}}$ & floor $\ge49$~meV & KATRIN $\le0.8$~eV \\
\midrule
$m_e$ & $4.5$~meV & \emph{fails} (too light) & yes \\
$E_0=\sqrt{m_e m_\mu}$ & $65$~meV & yes & yes \\
$M\approx314$~MeV & $2.8$~eV & yes & \emph{fails} \\
$m_\mu$ & $940$~meV & yes & \emph{fails} (too heavy) \\
\bottomrule
\end{tabular}
\end{center}
$m_e$ is too light, $M$ and $m_\mu$ too heavy -- \emph{only} $E_0=\sqrt{m_e m_\mu}$ fits, and that is
exactly the one natural FFGFT scale (Doc.~282, $\lambda_e\lambda_\mu=E_0$). The reference is thus not a
free quantity but the existing scale, selected by the lab.

In units of $E_0$ everything then becomes a pure $\xi$-power times $\tfrac12$:
\begin{equation}
\frac{\omega}{E_0}=\frac{\xi}{2},\qquad \frac{m_{\text{window}}}{E_0}=\frac{\xi^2}{2}.
\end{equation}
No free parameter remains. The $\tfrac12$ is the velocity square ($\tfrac12(m/p)^2$, Doc.~047) --
kinematic, not a tuning factor; its \emph{structural} origin is the AM sideband factor (see the
signal-engineering reading below).

\paragraph{What honestly remains.} The lab window ($49$--$800$~meV) is a factor $\sim$few wide: it
selects the \emph{scale} $E_0$ sharply (excluding the alternatives by orders of magnitude) but does not
pin the exact coefficient by itself. What remains is exactly \emph{one} structural statement,
\begin{equation}
\omega=\xi\,E_0\,,
\end{equation}
-- $E_0$ suppressed by exactly \emph{one} fractal $\xi$-power ($D_f=3-\xi$). This is no longer
\enquote{free scale, self-referential} but a non-circular computation step: $\omega$ as the
$\xi$-suppressed eigenvalue of the connection-Laplacian in the time-extended Hilbert structure
(Doc.~283 §8). It closes the point -- or falsifies it. Computed: \texttt{schliesse\_omega.py}.

% ==============================================================================
\section{The $\xi^1$ mechanism: lifting the zero mode by the dimension deficit}
% ==============================================================================
The remaining residual -- why $\omega=\xi\,E_0$ with exactly \emph{one} $\xi$-power -- has a concrete
mechanism. The connection-Laplacian on $T^4$ has an exact zero mode (the holonomy-flat constant). The
fractal correction $g=\eta(1+\xi f)$ acts as a diagonal potential perturbation and lifts it;
first-order perturbation theory gives
\begin{equation}
\delta\lambda_0 = \xi\,\langle 0|f|0\rangle = \xi\cdot\overline f\,,
\end{equation}
i.e.\ the power $\xi^1$ \emph{precisely when} the correction has a non-vanishing torus average
$\overline f\neq0$; for $\overline f=0$ the first order vanishes and the mode lifts only at $\xi^2$.

$D_f=3-\xi$ is a dimension \emph{deficit} -- a systematic, non-volume-preserving change of the measure
--, hence $\overline f\neq0$. So the power is \emph{one}. Numerically (\texttt{xi1\_eigenwert.py}): the
zero-mode lift scales with $p=0.999$ for a deficit ($\overline f\neq0$) versus $p=1.98$ for a
volume-preserving ripple ($\overline f=0$) -- so the power is not accidental but follows from the
nature of $D_f=3-\xi$.

\paragraph{Status.} The $\xi^1$ power is thus \emph{derived} (zero-mode lift by the dimension deficit),
not asserted. What remains is only the $O(1)$ coefficient -- kinematically the $\tfrac12$ (Doc.~047) --
and confirming that the physical kinetic state is this lifted zero mode. With that, $\omega=\tfrac{\xi}{2}E_0$
is closed up to an $O(1)$ factor -- and that $O(1)$ factor is identified structurally, in the
signal-engineering reading below, as the sideband $\tfrac12$.

% ==============================================================================
\section{The signal-engineering reading: AM sidebands and mode-locking}
% ==============================================================================
FFGFT grew out of communications engineering and the Fourier duality time$\leftrightarrow$frequency
(Doc.~001a); $\tilde T\!\cdot\! m=1$ \emph{is} that duality. In the dynamic sector the same language
yields two concrete statements -- one solid, one a candidate.

\paragraph{The $\tfrac12$ is the AM sideband factor.} The fractal correction $g=\eta(1+\xi f)$ is
formally an amplitude modulation of the carrier with modulation index $\xi$ (Doc.~057: multiplicative
$=$~AM, additive $=$~FM). Marcel's kinetic prefactor $A(t)=1+\varepsilon(t)$, $|\varepsilon|\ll1$, is
the same object ($\xi\leftrightarrow\varepsilon$). For a carrier $\cos(\omega_c t)$ one obtains
necessarily
\begin{equation}
\cos(\omega_c t)\,[1+\xi\cos(\omega_m t)]
=\cos(\omega_c t)+\frac{\xi}{2}\big[\cos((\omega_c{+}\omega_m)t)+\cos((\omega_c{-}\omega_m)t)\big],
\end{equation}
so the sidebands sit at amplitude $\xi/2$. The kinetic scale $\omega=\tfrac{\xi}{2}E_0$ is therefore the
\emph{first AM sideband of the mass carrier $E_0$}: the $\xi$ from the modulation index ($=$~dimension
deficit, previous section), the $\tfrac12$ from the sideband split
($\cos\!\cdot\!\cos=\tfrac12(\text{sum}+\text{difference})$). This unifies the $\xi^1$ power (lifted zero
mode $=$ first sideband) and the $O(1)$ coefficient into \emph{one} mechanism: the $\tfrac12$ is not
inserted kinematically but is structural -- the velocity square ($\tfrac12(m/p)^2$, Doc.~047) is its
kinematic shadow, not its origin.

\paragraph{$\theta=2/9$ as a mode-locking ratio (candidate).} The phase layer of the fork (Doc.~283)
reads: \emph{dynamic operator-phase $R$} (HLV, skew-adjoint, driven by $\dot\phi$) against \emph{fixed
scalar phase $\theta=2/9$} (FFGFT). Locking a dynamic phase onto a fixed rational value is
well-defined in signal engineering: injection locking, i.e.\ Arnold tongues. A driven nonlinear
oscillator locks onto rational rotation numbers $p/q$; the stable plateaus form a devil's staircase.
$\theta=2/9$ would then be the lock plateau of a rational rotation number -- which connects directly to
FFGFT's \emph{winding numbers} $(n_\theta,n_\varphi,n_3,n_4)$ (Doc.~210): a locked rational winding.
Mode-locking \emph{is} a quantization rule -- rational values are the stable fixed points -- exactly the
kind of \enquote{holonomy/fixed-point/quantization rule} the open $\theta$ point demands. The
\emph{open static} $\theta$ input would thereby acquire a \emph{dynamic} origin in the same sector.

\paragraph{What stays a candidate.} The sideband point is solid: it reproduces $\xi/2$ necessarily. The
mode-locking reading is a \emph{mechanism candidate}, not a derivation. There is a tension: small
denominators ($1/2,1/3,2/5$) have the widest tongues, while $2/9$ (denominator~9) would be a narrower
plateau; \emph{why exactly $2/9$} locks is open. But the reframing is productive: \enquote{why this
value?} becomes \enquote{which Arnold tongue, and why is it stable?} -- a testable question about a
driven oscillator, not about a bare number. An honest bound on the candidate: the rotation number $2/9$
is \emph{dimensionless} (cycles), the Koide offset $\theta=2/9$ is a \emph{radian} angle --
$2\pi\cdot2/9=4\pi/9\neq2/9$ --; reading the two as the same is an additional, open assumption, not part
of the computed candidate (cf.\ Doc.~282).

\paragraph{Z$_3$ protection: the denominator is explained, the numerator is not.} The FFGFT mass core is
a Z$_3$ circulant (Doc.~282); if the driving nonlinearity carries this symmetry (invariant under
$\theta\!\to\!\theta+1/3$, i.e.\ only harmonics $k=3,6,9,\dots$), the picture shifts. A structurally
faithful Z$_3$ drive widens the tongues with $3$-power denominators \emph{selectively}: at equal
criticality $1/3$ becomes $24\times$ wider and the whole $9$-family $11$--$12\times$, while the control
tongue $2/5$ (denominator~$5$, not a multiple of $3$) stays \emph{flat} ($0.97\times$) -- the signature
of genuine symmetry protection, not an artefact (\texttt{z3\_modelock\_test.py}). This answers
\enquote{why a denominator-$9$ lock at all}: the Z$_3$ structure of the core; $2/9$ is no longer
absurdly narrow but symmetry-protected robust. \emph{The numerator stays open:} the symmetry protects
the $9$-family jointly ($1/9=2/9=4/9$ identical), it does not single out $2/9$, and $1/3$ stays wider.
The question thus splits cleanly -- \enquote{why $2/9$} $=$ \enquote{why denominator~$9$} (Z$_3$,
settled) $+$ \enquote{why numerator~$2$ in the family} (open, exactly Marcel's BD17A holonomy domain).

\paragraph{The numerator needs a holonomy.} The $9$-family is a Z$_3$ orbit; a single $3$-fold drive is
therefore numerator-blind. The numerator is selected only by a \emph{second} $3$-structure with a
definite relative phase $\phi$ -- a holonomy that lives in the embedding space ($3'$ of the doubling
$6=3\oplus3'$, $T^4\!\to\!T^7$, Doc.~285), not in the core. With two $3$-fold harmonics ($h{=}3,\,h{=}9$)
and a relative phase $\phi$ (not gauge-removable) the degeneracy breaks
(\texttt{z3\_holonomie\_test.py}, bisection): $1/9$ and $4/9$ stay paired, $2/9$ is the singlet that
moves -- for $\phi\in(\pi,2\pi)$ $2/9$ is the \emph{widest} tongue (clearest margin at $\phi=3\pi/2$),
crossover exactly at $\phi=\pi$. \emph{Honestly:} the effect is small ($\sim\!0.5\%$), $\phi$ is free
(FFGFT does not fix it), and the minimal model splits only $2$-against-$1$. But the structural statement
stands: a holonomy \emph{can} select $2/9$, and $2/9$ is exactly the member it acts on. The open
question is thereby precisely shifted -- no longer \enquote{why $2/9$} but \enquote{what locks $\phi$
into the band where $2/9$ wins} -- and that is Marcel's BD17A \enquote{locked holonomy}.

\paragraph{One fractal correction, two orthogonal phases.} Holonomy and time modulation spring from
the \emph{same} fractal correction $g=\eta(1+\xi f)$ -- the driving nonlinearity \emph{is} $f$
(Doc.~051, Doc.~270). One might fear that treating them as independent is inconsistent. The computation
(\texttt{eine\_fraktale\_quelle.py}, $3$-adic Weierstrass function) shows the opposite: they are two
\emph{orthogonal} functionals of $f$. The time phase $A=2\pi\xi\langle f\rangle$ reads the \emph{mean}
$\langle f\rangle$ (the DC part, the dimension deficit, $O(\xi)$); the holonomy
$\phi=\arg\hat f_9-3\arg\hat f_3$ reads the \emph{phases of the $3$-power harmonics} ($O(1)$). The two
are analytically decoupled -- $\langle f\rangle$ is independent of the harmonic phase (numerically to
$2\cdot10^{-16}$), since $\cos(k\theta+\psi)$ has vanishing mean for every $\psi$. The worry is thereby
resolved: neglecting $A$ does not touch $\phi$, they read different Fourier parts of the \emph{same} $f$.
The real consistency lives elsewhere: $A$ and the $\xi^1$ mass lift \emph{both} depend on
$\langle f\rangle$ -- so the time phase is tied to the mass window, not free. And no free lock: a
phase-coherent fractal ($\psi=0$) gives $\phi=0$ (degeneracy), whereas $2/9$ requires $f$'s $3$-power
harmonics to carry a relative phase in $(\pi,2\pi)$ (a ramp $\delta=\pi/2$ per octave hits $\phi=3\pi/2$
exactly, the $2/9$ maximum -- but as a choice, not a derivation). Thus \enquote{what locks $\phi$} is
concretely named: not some arbitrary phase, but the relative phase of the $3$-power harmonics of the
fractal correction $f$ -- the FFGFT-internal target for BD17A.

\paragraph{Demarcation: what is \emph{not} a mechanism here.} Modulation index and lock ratio are
different quantities in different sectors: $\xi=4/30000$ is the fixed AM index in the amplitude sector
(it yields the sideband $\tfrac12$), $2/9$ is a rotation number in the phase sector. The lock ratio is
\emph{not} $\xi$. Any \enquote{derivation} that sets $\xi$ to an $O(1)$ value (such as $1/3$ or
$\tan(\pi/9)\approx0.364$) in order to force $2/9$ has left FFGFT -- $\xi$ is fixed and orders of
magnitude smaller ($\sim\!10^{-4}$). Likewise the open question is the \emph{stability} of the $2/9$
plateau, not an algebra between $\xi$ and $2/9$; and the memory kernel the locking would rest on is the
discrete-spectral, oscillating kernel of Doc.~282 ($\sum_k g_k^2\delta(\omega-\omega_k)$, with
backflow/revivals), not a dispersive all-pass.

% ==============================================================================
\section{Recursion as feedback: loop gain, regimes, discipline}
% ==============================================================================
FFGFT grew out of communications engineering (Doc.~001a), and its recursions are \emph{feedback loops}.
This places the results above in a frame -- and fixes what about them is \emph{free} and what is not.

\paragraph{The loop gain is a $\xi$ quantity -- and fixed.} The magnitude of the loop gain decides the
behaviour. In FFGFT it is geometrically given, not a dial:
\begin{itemize}
\item $|v|<1$ (negative feedback): the loop contracts. The $\xi$-damping recursion
$r(k{+}1)=r(k)(1-\xi)$ (Doc.~275) has gain $1-\xi$, only $\xi$ below one -- hence the enormous, slow
scale tower; it runs to its only fixed point $0$ and merely \emph{passes through} $1/\varphi$ (no
attractor).
\item $|v|=1$ (Barkhausen): marginal sustained oscillation.
\item $|v|>1$ (positive feedback): the loop runs away. The golden $\varphi$ branch ($|\varphi|>1$)
unrolls, the $-1/\varphi$ branch ($|-1/\varphi|<1$) is the overdamped empty window (Doc.~285).
\end{itemize}
Decompactification is exactly this transition: \emph{one} circle tips from the compact (contracting)
into the runaway regime -- the mass circle $\tilde T\cdot m=1$ unrolls to non-compact time (Doc.~270),
and that tipping \emph{is} the measurement.

\paragraph{The phase selects itself.} A feedback loop imposes no phase: the Barkhausen phase condition
closes at the frequency the loop \emph{finds}; in injection locking the lock phase slides within the
lock range (Adler equation). Hence $\theta=2/9$ is to be read as a \emph{self-selected lock ratio}
(rotation number), not as a tightly imposed phase. A \enquote{derivation} that prescribes a fixed phase
$2/9$ and solves backwards for $\xi$ mistakes this self-adjustment (cf.\ the demarcation above).

\paragraph{Two tiers.} Linear and weak ($\xi$ small): first order $=$ the AM sideband $\tfrac12$ (above,
solid); a purely linear loop does not lock. Nonlinear: mode-locking onto rational rotation numbers $=$
the $\theta=2/9$ candidate (above); the lock-range width scales with the feedback strength $\xi$, and
$\xi\sim10^{-4}$ with denominator~9 makes the $2/9$ tongue extremely narrow -- that is the open
stability problem, not a missing piece of algebra.

\paragraph{Negative feedback as equalization.} The fractal correction $g=\eta(1+\xi f)$ (with
$K_{\text{frak}}$/RG, Doc.~133/051) acts as broadband negative feedback that linearizes the bare carrier
and sets $D_f=3-\xi$ -- weak, with no sharp phase alignment required.

\paragraph{Discipline.} This fixes how the tools are to be used \emph{correctly}: (i)~the loop gain
($\xi$, the eigenvalues $\varphi/{-}1/\varphi$) is fixed, never a dial -- forcing a result by setting
$\xi$ is the cardinal error; (ii)~the open questions are always \emph{regime and lock range}
(contracting/marginal/runaway; tongue width), never an algebra \emph{on} the gain; (iii)~the phase is
self-selected, quantized values are lock ratios; (iv)~the regime of the feedback carries the physics --
negative feedback $=$ compact stable scales $+$ equalization, positive feedback $=$
decompactification/measurement.

% ==============================================================================
\section{Relation to the static sector}
% ==============================================================================
The static sector is closed and computed: the Z$_3$ mass operator ($r=\sqrt2$, $\theta=2/9$) plus the
mass circle yields Koide $2/3$, the lepton ratios and -- as a pre-registered, matched-null-tested
declaration -- the BD12-XCORE interface (Doc.~285). The dynamic sector is the \emph{complementary,
open} side: the same parameter $\xi$, but as a \emph{fraction} rather than an \emph{eigenvalue}. A
derivation of $m_{\text{window}}=\xi\cdot\omega$ would move the window-filling dynamics (Doc.~263,
holographic scale projection) from description to computation, and the neutrino-like $3'$ candidate
(Doc.~285) from conditional to derived.

\paragraph{Retrospect: two things both called \enquote{$2/9$}.} It is worth fixing the thread, for
$\theta=2/9$ appears in two roles. (i)~$2/9$ as a \emph{number/input}: the Z$_3$ circulant of the core
uses it and reproduces the leptons (Koide), empirically closed -- it was always there (Doc.~282;
Doc.~285, the \enquote{protected-invariant} row $r=\sqrt2$, $Q=2/3$, $\theta=2/9$). (ii)~$2/9$ as a
\emph{question} (\enquote{why this value}, specifically the numerator): this becomes relevant only with
the dimensional extension. The reason is structural, not a lack of computation: the bare Z$_3$ core is
\emph{numerator-blind} -- $1/9,2/9,4/9$ are a Z$_3$ orbit, and a single compact $3$-structure cannot in
principle answer \enquote{why $2/9$ rather than $1/9$}. The numerator is seen only by a second
$3$-structure with a relative phase $=$ a holonomy $=$ exactly what the extension provides ($3\oplus3'$,
$T^4\!\hookrightarrow\!T^7$). The \enquote{why-$2/9$} question thus has no home in the core; it is by
nature an extension question.

\paragraph{Where this already stands in the corpus.} Three documents already carry the thread.
\textbf{Doc.~285} (dimension bridge) is the extension itself: $\mathrm{HLV}\supset\mathrm{FFGFT}$,
$T^4\hookrightarrow T^7$ ($7=4+3$, the three perp dimensions), the doubling $6=3\oplus3'$
(\enquote{literally}), the fork (FFGFT $3$-fold $\sqrt2$/$Q=2/3$/$\theta=2/9$ against HLV $5$-fold
$2/\sqrt5$/$\varphi$); $\theta=2/9$ sits in the invariant row. \textbf{Doc.~283} (bridge and fork, §8)
introduces $\theta=2/9$ explicitly as a \emph{complex holonomy}, the \enquote{operational consequence of
compactness}, with the phase layer \enquote{dynamic operator-phase $R$ (HLV) against fixed scalar phase
$\theta=2/9$ (FFGFT)} -- there $2/9$ is already a holonomy/extension object, not a bare core number.
\textbf{Doc.~282} is the core that \emph{uses} $2/9$ (leptons), with the honest line \enquote{translation
is not justification} -- the notation \emph{represents} $2/9$ but does not \emph{ground} it.

\paragraph{The fixed point and the conclusion.} Why the static sector is closed \emph{at all}: the
lepton masses sit at a \emph{self-consistent fixed point} -- the mass operator $\Phi_*=\sum_i m_i P_i$ is
the non-trivial fixed point of the recursion $\mathcal R(\Phi_*)=\Phi_*$ (Doc.~203, lepton exponents
$p_e=3/2,\,p_\mu=1,\,p_\tau=2/3$); \emph{that} is why it is exact, not a fitted value. From the lepton
measurements one \emph{reads off} this fixed point (that is the closure); fixed and open separate
cleanly: $Q=2/3$ \emph{is} the operator condition $r=\sqrt2$ (algebraically fixed, Doc.~282),
$\theta=2/9$ is the holonomy (the numerator, open). Hence the conclusion: all the recent work above
(feedback, mode-locking, holonomy test) is \emph{no new arena} but the mechanistic, signal-engineering
version of what $282\to283\to285$ already say structurally -- $2/9$ is a holonomy, and a holonomy lives
in the extension.

\paragraph{Magnitude and phase: why the split is inevitable.} In signal-engineering language the whole
finding collapses to a single, well-known theorem. The mass operator \emph{is} a Z$_3$ circulant, and a
circulant is diagonalized by the DFT -- its eigenvalues are the DFT of its first row. The three lepton
masses are thus literally a \emph{three-point spectrum}: $\sqrt2$ is the \emph{magnitude} of the
spectral coefficients, $\theta=2/9$ their \emph{phase}. The radial/angular conclusion (Doc.~282) is
therefore nothing but \emph{magnitude spectrum versus phase spectrum}: everything determined sits in the
magnitude ($\xi$ as scale, the hierarchy as envelope, $Q=2/3=\sqrt2$ as amplitude ratio, $\langle
f\rangle$ as DC term), everything open in the phase ($\theta$, the holonomy
$\varphi=\arg\hat f_9-3\arg\hat f_3$, the harmonic phases). The deep reason is the theorem itself:
\emph{a magnitude spectrum does not fix the phase spectrum} -- same power, arbitrary shape. \emph{That}
is precisely why $\theta$ resists every FFGFT tool: the recursion $\mathcal R$ is purely real, hence pure
gain, and real gain does not touch the phase. The orthogonality computed above \emph{is}
\enquote{magnitude $\perp$ phase}. From this the FFGFT$\leftrightarrow$HLV division of labour even
becomes a circuit diagram: FFGFT is the \emph{real amplifier stage} (magnitude, hierarchy), HLV's
skew-adjoint $R$ is the \emph{all-pass/phase stage} ($e^{i\varphi}$, magnitude-preserving, rotating only
the phase). A skew-adjoint operation \emph{is} an all-pass. The missing angular principle is the phase
stage -- and the HLV side carries it, not FFGFT. (Limit of the same lens: mode-locking yields a
\emph{rotation number} (dimensionless), $\theta$ a \emph{radian}; $2\pi\cdot2/9\neq2/9$ -- the lens
identifies the \emph{type} correctly, a locked phase, but the literal identification does not close.)

% ==============================================================================
\section{Reproducibility}\label{sec:repro-286}
% ==============================================================================
\texttt{kinetik\_xi\_anteil.py} (numpy-only): narrowing of the $\xi$-power against the bounds, the
duality framing ($\tilde T=1/\max(m,\omega)$), and the finding $p=2$ with the explicitly open
reference/coefficient/spectrum gap. The script claims no derivation; it narrows. \texttt{schliesse\_omega.py}: the lab selection of the reference $E_0$ (table) and the reduction $\omega/E_0=\xi/2$, $m_{\text{window}}/E_0=\xi^2/2$, with the $\xi^1$ remainder as the marked closing point. \texttt{xi1\_eigenwert.py}: the zero-mode lift as $\xi^1$ from the dimension deficit ($p=0.999$ vs $p=1.98$). \texttt{am\_seitenband\_modelock.py}: confirms the sideband ratio $\xi/2$ necessarily (deviation $0\%$) and measures the Arnold-tongue widths on the sine circle map -- $2/9$ locks as a plateau but is $\sim\!12\times$ narrower than $1/3$: candidate, not derivation. \texttt{z3\_modelock\_test.py}: a Z$_3$-symmetric drive (harmonics $=$ multiples of $3$) widens the $3$-power-denominator tongues selectively ($1/3$ by $24\times$, the $9$-family by $11$--$12\times$), while the control $2/5$ stays flat ($0.97\times$) -- the denominator~$9$ is Z$_3$-protected (Doc.~282), the numerator~$2$ stays open. \texttt{z3\_holonomie\_test.py}: two $3$-fold harmonics ($h{=}3,h{=}9$) with a relative phase $\phi$; measured precisely (bisection), $\phi$ breaks the $9$-degeneracy -- $1/9,4/9$ stay paired, $2/9$ moves and is the widest tongue for $\phi\in(\pi,2\pi)$ ($\sim\!0.5\%$, maximum at $\phi=3\pi/2$); $\phi$ free $\Rightarrow$ shifts the open question to the $\phi$-lock (BD17A). \texttt{eine\_fraktale\_quelle.py}: shows computationally ($3$-adic Weierstrass $f$) that the time phase and the holonomy are \emph{orthogonal} functionals of the same fractal correction -- $A=2\pi\xi\langle f\rangle$ reads the mean ($O(\xi)$), $\phi=\arg\hat f_9-3\arg\hat f_3$ the harmonic phases ($O(1)$), $\langle f\rangle$ phase-independent to $2\cdot10^{-16}$; the time phase is tied to the $\xi^1$ mass lift (both $\langle f\rangle$), the holonomy phase stays an independent datum (coherent $\Rightarrow\phi=0$; $\delta=\pi/2$ ramp $\Rightarrow\phi=3\pi/2$).
