%% 299_Einbettung_Iota_En_ch.tex
%% FFGFT -- Doc. 299: The embedding iota -- working document / forcing protocol
%% Author: Johann Pascher
%% Date: July 2026
%% Language: English

\section*{Doc.~299 \quad The Embedding $\iota$ -- Working Document and
Forcing Protocol (HLV time sector $\hookrightarrow$ FFGFT recursion)}

\subsection*{Purpose and scope}

Doc.~297 records the embedding
\begin{equation}
  \iota\colon \text{HLV base object} \;\hookrightarrow\;
  L^2(T^4)\otimes\mathbb{C}^3
\end{equation}
as an open conjecture: structurally plausible, but not constructed. This
document sets up the next clean step (P35) as a \emph{protocol} -- it fixes,
\emph{before} the joint work, the domain, the codomain, the candidate map, the
matched null models, and the decision criterion. It is not a proof and not a
claim about an outcome; it names what would have to count as \emph{forced} and
what as merely \emph{allowed}, so that the later evaluation cannot be adjusted
after the fact.

The frame is the \emph{time sector}. Following the sharpening in the
correction register (Doc.~190, R47), two senses of containment must be kept
apart: \emph{dimensionally}, HLV counts larger ($T^7 = T^4\times T^3$,
$7 = 4+3$; R43); \emph{in content, in the time sector},
$\mathrm{HLV}\subset\mathrm{FFGFT}$, because the HLV spiral-time window is a
bounded section of the unrolled recursion time. In unified notation -- both
$D6 + \text{time}$, HLV as $D6 + \text{spiral-time}$, FFGFT in Hilbert space as
$D6 + \text{recursion-time}$ -- the window is not additive but internal.
$\iota$ is exactly the map that makes this internal section explicit.

That it is a section takes no value from the window (Doc.~298): a sub-model
that evaluates correctly on its scale is not refuted but located. $\iota$
returns to the section the compact whole of which it is the reduction.

\subsection*{Domain: the HLV side}

Doc.~297 (§\enquote{Two HLV spiral-times}) separates two distinct objects,
both of which HLV calls \enquote{spiral-time}. They are separate embedding
candidates and must not be conflated in the protocol.

\textbf{Object A -- the geometric time.} The $A_5$ singlet on the $S^1$
factor of the factorisation $T^7 = T^4\times T^3$ (Doc.~285): decoupled,
separable, without a memory channel. Purely geometric.

\textbf{Object B -- the temporal-dynamic spiral-time.} The triadic operator
$\Psi(t) = (U_1, U_2, U_3)$ with memory channel $U_3$ (Krueger,
Consciousness document, Eq.~7): a bounded window accumulator with a fixed,
sliding window $M_m$; older values actively drop out. In every
representation -- linear, polar, spiral -- the dependency structure is the
same: finite short-term memory with fixed horizon $M_m$, without accumulation
(Doc.~297: the spiral representation is a coordinate choice, not a structural
property).

\subsection*{Codomain: the FFGFT side}

The codomain is the compact recursion in the Hilbert space
$H = L^2(T^4)\otimes\mathbb{C}^3$ (Doc.~230/282, lossless bijection). Three
structural elements are decisive for $\iota$:

\begin{itemize}
  \item \textbf{The memory kernel.} The Fourier transform of the discrete
    spectral density $\sum_k g_k^2\,\delta(\omega-\omega_k)$ (Doc.~283) --
    the full, accumulating memory structure of the recursion.
  \item \textbf{The frozen winding.} In the frozen configuration
    (Doc.~295) the winding closes after exactly $1/(100\,\xi_0) = 75$
    turns; this is the smallest coherent unit of the recursion.
  \item \textbf{The $K_{\text{frak}}$ recursion} $\xi_{n+1} =
    \xi_n(1 - 100\,\xi_n)$: the present state carries the entire history as a
    structural imprint; it generates the log-spiral with ratio $e$
    (Doc.~295). Memory as generative structure, not as storage.
\end{itemize}

\subsection*{The candidate map $\iota$ (two branches)}

Matching the two objects of the domain, $\iota$ has two branches with
different natural locations.

\textbf{$\iota_{\text{geo}}$ (Object A).} The $A_5$ singlet ($S^1$,
decoupled) maps to the $\xi\to 0$ fixed point of the recursion -- the
geometrically separable, most information-poor configuration of the compact
time (constant pitch, winding closes after $75$). It is Archimedean from
geometric factorisation, but carries no ratio $e$ (Doc.~295 §10: blocked on
the $e$-criterion).

\textbf{$\iota_{\text{dyn}}$ (Object B).} The window $U_3$ maps to the
hard-reset kernel with finite support below one turn:
\begin{equation}
  \iota_{\text{dyn}}\colon U_3 \;\hookrightarrow\;
  \bigl\{\,K \in L^2(T^4)\otimes\mathbb{C}^3 \;\big|\;
  K(t-\tau) = 0 \text{ for } t-\tau > M_m\cdot\Delta t,\;
  M_m < 75\,\bigr\}.
\end{equation}
This corresponds to the Markov limit of the memory kernel ($g_k\to 0$,
Doc.~283), sharpened to a bounded window. Both branches are bounded sections
(windows) of the unrolled recursion time; this is exactly the content-level
$\mathrm{HLV}\subset\mathrm{FFGFT}$ of the time sector.

The information hierarchy (Doc.~297) locates the branches:
\begin{equation}
  U_3 \;\subset\; \text{Markov limit} \;\subset\;
  \text{Archimedean} \;\subset\; \text{log-spiral}~(e)
  \;=\; \text{FFGFT core}.
\end{equation}
The geometric singlet lies to the side of this chain (Archimedean from
factorisation, not from accumulation). Each step is more information-poor
than the next; $U_3$ is the poorest.

\subsection*{The forcing question: forced or merely allowed}

The core of the protocol. That a section \emph{exists} into which $U_3$
embeds is weak -- a bounded window operator can be placed into the degenerate
boundary case of any sufficiently rich recursion. The substantive question is
whether the embedding is \emph{forced} or only \emph{allowed}. This is the
same forcing logic as in the C3A5 specificity test (Doc.~293/294),
transferred to the time axis.

\textbf{Forced ($\mathrm{HLV}\subset\mathrm{FFGFT}$ in the time sector,
genuine).} The Markov-limit section of the recursion \emph{necessarily}
coincides with the hard-reset kernel of $U_3$, and an independent invariant
of the section agrees with $U_3$ where generic bounded window operators do
not. $\iota$ is then the unique structural placement.

\textbf{Allowed (mere compatibility).} $\iota$ merely embeds compatibly:
every bounded window operator would sit equally in the degenerate boundary
case, and the match carries no content beyond the definition (P35).

\textbf{Circularity caveat (P35).} $U_3$ is by construction a hard-reset
window. Reading it as the Markov-limit section of the recursion is therefore
initially \emph{definitional}, not an independent confirmation -- just as the
icosahedral object gives icosahedral reference distance zero because it
\emph{is} that object (Doc.~294). The forcing must therefore come from an
\emph{independent} signature that $U_3$ shares with the recursion section
without both being defined by the same construction rule.

\subsection*{Matched nulls (time axis, $\iota_{\text{dyn}}$)}

The forcing is tested against a family of matched null models -- the
temporal counterpart to axis shuffle and generic tight-frames
(Doc.~293/294). It also mirrors Marcel's own OP8 null family (Doc.~297), so
that the instruments interlock:
\begin{itemize}
  \item \textbf{memory-free Markov} -- the baseline that $\iota_{\text{dyn}}$
    predicts in the boundary case;
  \item \textbf{phase-shuffled} and \textbf{time-shuffled} -- destroy
    temporal structure while preserving marginal statistics;
  \item \textbf{coherence-only} and \textbf{information-only} -- isolate
    single channels;
  \item \textbf{generic window operator} -- random $M_m$, random kernel with
    the same support: the direct analogue of \enquote{random rotation axis /
    generic tight-frame};
  \item \textbf{generic ML baseline}.
\end{itemize}
Calibration as in the specificity test: an exact recursion section gives
distance zero, generic window operators lie in a broad band.
$\iota_{\text{dyn}}$ is \emph{forced} exactly when $U_3$ sits at the zero
point where the generic nulls lie in the band; \emph{allowed} when every
window null reaches the same distance.

\subsection*{Matched nulls (geometric branch, $\iota_{\text{geo}}$)}

For the geometric branch the null family is the spatial counterpart --
axis shuffle and generic frames in the sense of Doc.~293/294, here in the
form agreed with the HLV side:
\begin{itemize}
  \item \textbf{random $C_3/A_5$ embeddings} -- the native carrier against
    arbitrarily rotated embeddings of the three-/five-fold structure;
  \item \textbf{alternative projection stars} -- cut stars other than the
    icosahedral one;
  \item \textbf{tetra-/octahedron controls} -- crystallographic point
    groups without five-fold symmetry as a negative control;
  \item \textbf{shuffled $C_3$ bases} -- permuted fiber bases with
    preserved marginal statistics;
  \item \textbf{spectrally matched null carriers} -- carriers with the same
    power spectrum but without the icosahedral axis structure.
\end{itemize}
Calibration as in the $C3A5$ specificity test (Doc.~294): the exact
icosahedral projector gives distance zero to the reference spectrum (all
fifteen angles $63{.}435^\circ$, redistribution $2/9$), generic frames lie
in a broad band (median RMS $\approx 22$). $\iota_{\text{geo}}$ is
\emph{forced} exactly when the native carrier sits at the zero point where
these nulls lie in the band; \emph{allowed} when generic embeddings reach the
same distance.

\medskip\noindent\textbf{Jointly booked architecture.} Both null families
are agreed with the HLV side. Krueger (IOTA-BRIDGE1 v0.1) tests the same
finite proxy question -- a native-$6$D spiral-time-window carrier as a $C_3$
fiber-compatible object in a finite $L^2(T^4)\otimes\mathbb{C}^3$ proxy --
under spectral, $C_3/A_5$, $U_3$ time-window, and screen/information
diagnostics. The claim boundary is tight on both sides: PASS $=$ finite-proxy
$\iota$-forcing candidate (no subset proof, no physics/mass/QFT/GR
derivation); BLOCK $=$ this concrete finite embedding route is narrowed or
blocked.

\subsection*{Decision criterion and falsification}

The pre-registered OP8-Neuro test (Doc.~297) is the outer decision test; the
forcing protocol adds the specificity step:
\begin{enumerate}
  \item \textbf{$M_3$ does not beat the memory-free Markov baseline.} $U_3$
    lies entirely in the degenerate boundary case. $\iota_{\text{dyn}}$
    holds in the Markov limit -- but from this alone follows \emph{allowed},
    not \emph{forced} (every hard-reset window achieves this). The
    specificity run is additionally required for forcing.
  \item \textbf{$M_3$ clearly beats the memory-free Markov baseline.} $U_3$
    carries non-Markov structure (revivals, BLP backflow, oscillating
    kernel, correlations beyond $M_m$). The simple $\iota_{\text{dyn}}$ into
    the Markov limit is \emph{falsified}; a richer embedding higher in the
    hierarchy (towards log-spiral~$e$) is to be constructed.
  \item \textbf{Forcing verdict (independent of 1/2).} A specificity run --
    the time-axis analogue of \texttt{a5\_bridge\_discrimination.py} --
    measures the distance of an \emph{independent} invariant of the recursion
    section to $U_3$ against the matched nulls. Distance zero at $U_3$ and a
    broad band at the window nulls $\Rightarrow$ forced; otherwise allowed.
\end{enumerate}

\subsection*{To be constructed (deliverables)}

\begin{enumerate}
  \item For $\iota_{\text{geo}}$: represent HLV's $\phi$-icosahedral
    projector explicitly as an operator on the $\mathbb{C}^3$ fiber
    ($\in \mathrm{End}(\mathbb{C}^3)$ with $C_3$ invariance; Doc.~297,
    step~1).
  \item For $\iota_{\text{dyn}}$: compute the Markov-limit kernel of the
    recursion ($g_k\to 0$, Doc.~283) and its distance to $U_3$'s hard-reset
    kernel against the matched-null family -- the time-axis analogue of the
    specificity test.
  \item Fix the forcing metric: distance-to-recursion-section, calibrated so
    that an exact section $\to 0$, a generic window $\to$ broad band.
\end{enumerate}
Domain, codomain, and null family are fixed by this document; what remains
open is only the construction of the three artifacts.

\subsection*{Counter-run performed (result, corrected)}

A first version (v0.1) reduced the spiral-time window to a \emph{winding-less}
hard-reset kernel and found it carries no back-flow -- which is near
tautological, since a kernel without winding cannot carry a revival by
construction, and it does not test Marcel's actual object. His object is
defined by a \emph{winding angle} $\theta$ (the pitch of the archimedean
spiral in recursion time); the angle \emph{is} the structure. The corrected
version (\texttt{python/Dok299\_Skripte/ffgft\_299\_iota\_gegenlauf\_winding\_locked.py},
SHA256, seed 20260708) writes $\theta$ explicitly into the kernel,
$k_\theta(s)=e^{-s/\tau}\cos(\theta s)$, $s=0\dots M{-}1$, and sweeps it.
Object and witness stay apart (witness: BLP back-flow $5{.}125$, Doc.~283);
the nulls share the \emph{same} envelope with incoherent phase -- isolating the
contribution of the angle.

\begin{center}\small
\begin{tabular}{lcl}
\hline
Winding $\theta$ & Back-flow & Reading\\
\hline
$0$ (no winding) & $0{.}00$ & Markov limit (in band)\\
$1/\phi \approx 0{.}618$ & $0{.}00$ & in band (allowed)\\
golden angle $\approx 137{.}5^\circ$ & $0{.}159$ & \textbf{above band}\\
phase-shuffled null (q95) & $0{.}076$ & incoherent bound\\
\hline
\end{tabular}
\end{center}

\noindent Once the angle is in the kernel, the answer is no longer fixed by
construction. At most windings the hard reset (finite width $\sim 1/M$) kills
the revival $\Rightarrow$ back-flow in the null band, allowed. At the
\emph{golden angle}, however, it survives the broadening and rises above the
incoherent band ($0{.}159$ vs.\ q95 $0{.}076$); the first threshold is at
$\theta_c\approx 1{.}82$\,rad. The verdict is therefore \textbf{conditional
rather than decided in advance}: allowed if the native carrier's actual winding
$\theta^\ast$ lies below $\theta_c$; forced (and Doc.~297 under tension at that
point) if $\theta^\ast$ sits at the golden angle. $\theta^\ast$ is to be pinned
from the HLV carrier -- marked here as a candidate, not asserted. The absolute
value ($0{.}159$) is small against the witness $5{.}125$ and the test remains a
finite proxy; but \emph{relative to incoherent phase} it is a positive signal
at that winding, not a null result. The earlier unconditional reading (v0.1)
was an artifact of the winding-less reduction.

The geometric branch ($\iota_{\text{geo}}$) is carried along as a discriminant
test: the 15 pairwise axis angles against a \emph{fixed} icosahedral reference
($63{.}435^\circ$), not against axes taken from the carrier. Icosahedral
$\to 0^\circ$, random-star median $21{.}7^\circ$ -- the fixed reference
separates where a self-referential score would pull any star to $\approx 0$.
This is the anti-circularity condition a forcing test in the geometric branch
must meet.

\subsection*{Correction value $K_{\text{frak}}$ from the closure comma}

The rolled-out recursion closes only after $N=1/(100\xi_0)=75$ equal pieces, not
after one turn. The approximation ``one turn closes'' neglects a small factor:
$75$ turns each shortened by $\varepsilon$ give the exact closure,
$75\,(1-\varepsilon)=74$, hence $\varepsilon = 1/75 = 100\,\xi = 0{.}0133\ldots$
(the closure comma; as an angle $2\pi/75 = 4{.}8^\circ$ per turn). The per-step
factor of the scale recursion $\xi_{n+1}=\xi_n(1-100\xi_n)$ is therefore
\[
  K_{\text{frak}} \;=\; 1 - \varepsilon \;=\; 1 - 100\,\xi \;=\; \tfrac{74}{75}
  \;=\; 0{.}9867,
\]
the form the corpus carries throughout (Doc.~133/231/032/285).

Important: $75=1/(100\xi)$ and $K_{\text{frak}}=1-100\xi$ are both just $100\xi$;
the comma \emph{re-expresses} the already-anchored $100\xi$, it does not derive
it. The anchor lies in Doc.~133 (factor $100$ from the RG running,
$K_{\text{frak}}$ fixed by $m_e/m_\mu$ consistency) and in $\xi$ itself
(Higgs/$\alpha$/Koide). Detailed in Doc.~300.

For the projection side (Marcel) a consistency condition follows: \emph{if} his
closed projection is a section of the same recursion, the conversion to the
rolled-out curve carries the independently anchored factor
$K_{\text{frak}}=1-100\xi=74/75$ -- not from the $75$ and not freely chosen.

\subsection*{Status}

Working document and pre-registered forcing protocol (P35). $\iota$ remains a
conjecture (Doc.~297). This document fixes the test architecture before the
joint run, so that the verdict -- forced or allowed -- cannot be shifted after
the fact. The discipline holds symmetrically: it binds even when the outcome
favours FFGFT.
