%% 300_ZweiRollen_Kfrak_En_ch.tex
%% FFGFT -- Doc. 300: Spiral-Time as readout and debounced comparator;
%%                    the shared correction factor K_frak = 1 - 100 xi (74/75)
%% Author: Johann Pascher
%% Date: July 2026
%% Language: English

\section*{Doc.~300 \quad Spiral-Time as readout and debounced comparator ---
and the shared correction factor $K_{\text{frak}} = 1-100\xi$ ($74/75$)}

\subsection*{Occasion and scope}

From the collaboration comes the observation that Spiral-Time is an operator
class with at least two roles: a \emph{readout} (what happens in the signal or
carrier) and a second part deciding whether this readout may count as a stable
transition. This document makes the second role precise in measurement/circuit
terms and assigns the correction factor connecting both sides to its
\emph{actual} origin in the corpus. Scope: category-B finding (genuine
compatibility / candidate overlap), not an HLV-internal derivation, not a
physical validation.

\subsection*{The two roles, made precise}

The first role, the \emph{readout}, is a measured value: the signal at the
$+$input of a comparison. The second role is not an administrative term
(\enquote{governance}) but precisely a \textbf{comparator with hysteresis} ---
a threshold decision whose output carries one bit. Two forms:
\begin{itemize}
  \item \textbf{amplitude hysteresis}: two level thresholds, a dead band on the
    value axis stabilising against noise at the switching point.
  \item \textbf{time hysteresis (debounce)}: the output accepts an edge only if
    it \emph{persists} over a time window. The dead band lies on the time axis.
\end{itemize}
The second role is the time hysteresis. The finite-proxy window ($M=12$,
$\tau=6$) is a weighted debouncer: a transition counts only once it survives
the window. \enquote{Stable transition} is exactly the time hysteresis.

\subsection*{Validity condition: reference from a derivation, not a copy}

A comparator carries information only if the reference at the $-$input comes
from a \emph{different} source than the signal. If both inputs carry the same
quantity, the output is meaningless. This was the circular core of the U3
boundary gate in the first HLV-side implementation: the reference was a copy of
the readout window (\texttt{hard = hlv.copy()}), so the correlation is $1{.}0$
by construction. The FFGFT-side test (Doc.~299) replaces it with a
\emph{derived} witness (BLP back-flow $5{.}125$, Doc.~283), independent of the
object and not reproducible by a hard-reset window. Self-reference is admissible
when closed by a derivation; circular when closed by a copy.

\subsection*{Why \enquote{the same spiral} is not a postulate}

The statement about the correction factor presupposes that the projected HLV
object and the FFGFT recursion are the \emph{same} spiral. This identity is
supported by several independent contact points:
\begin{itemize}
  \item \textbf{$2/9$}: the same redistribution as the output of the
    $Z_3$-circulant diagonalisation --- found, not sought.
  \item \textbf{$D6$ / $\varphi$-icosahedron}: the same object structure,
    $\tau=\varphi$, all fifteen axis angles $\arccos(1/\sqrt5)=63{.}435^\circ$.
  \item \textbf{time}: the spiral-time sector as a bounded section of the
    rolled-out recursion time (R47).
\end{itemize}
$2/9$ and $D6$ are geometric, mutually independent, both found; under this
multiple anchoring \enquote{the same spiral} is the only remaining reading
(category~B).

\subsection*{The closure comma and $K_{\text{frak}}$}

The rolled-out recursion closes only after $N=1/(100\xi_0)=75$ equal pieces
($\xi=4/30000$), not after one turn (Doc.~295/297). The approximation
\enquote{one turn closes} neglects a small factor: $75$ turns each shortened by
$\varepsilon$ give the exact closure, $75\,(1-\varepsilon)=74$, hence
\begin{equation}
  \varepsilon \;=\; \tfrac{1}{75} \;=\; 100\,\xi \;=\; 0{.}0133\overline{3}
  \qquad(\text{as an angle } 2\pi/75 = 4{.}8^\circ \text{ per turn}).
\end{equation}
The per-step factor of the recursion is therefore
\begin{equation}
  K_{\text{frak}} \;=\; 1 - \varepsilon \;=\; 1 - 100\,\xi \;=\; \tfrac{74}{75}
  \;=\; 0{.}9867,
\end{equation}
exactly the form the corpus carries throughout (Doc.~133/231/032/285/018/005).
The reciprocal length-ratio form (shortened piece $\to$ full turn) is
$75/74 = 1{.}0135$.


\subsection*{The actual anchor: not the $75$, but Doc.~133}

The origin of $100\xi$ --- and thus of $75$ \emph{and} $K_{\text{frak}}$ ---
lies one level deeper and is independent:
\begin{itemize}
  \item The \textbf{scale recursion} $\xi_{n+1}=\xi_n(1-100\xi_n)$
    (Doc.~133/275) has per-step factor $K_{\text{frak}}=1-100\xi$;
    $75=1/(100\xi_0)$ is its winding number.
  \item The \textbf{factor $100$} emerges from the RG running of $D_f=3-\xi$
    over $\sim 17$ orders of magnitude (Planck $\to$ electroweak), effectively
    $D_f^{\text{eff}}\approx 2{.}973$ (Doc.~133); geometrically $100=4\cdot 5^2$
    (Doc.~042).
  \item $K_{\text{frak}}$ is \textbf{not arbitrary} but fixed by requiring two
    independent derivations of the mass ratio $m_e/m_\mu$ to agree (Doc.~133,
    \emph{Unique Determination}).
  \item $\xi=4/30000$ itself is anchored via the Higgs relation, $\alpha$ and
    Koide.
\end{itemize}
The closure comma thus \emph{re-expresses} the already-anchored $100\xi$; it
does not derive it. The $75$ is an output of the same recursion, not an
independent anchor.

\subsection*{Consequence for the projection (Marcel)}

The statement to Marcel therefore remains valid, only correctly booked:
\emph{if} his projected, closed turn object is a section of the same recursion
(supported by $2/9$, $D6$, time), then the conversion between his projection and
the rolled-out exact curve carries exactly the per-step factor
$K_{\text{frak}}=1-100\xi=74/75$ (reciprocally $75/74$) --- a factor anchored
\emph{independently} (Doc.~133), not derived from the $75$ and not freely
chosen. It is a consistency condition, not a derivation from the winding
number: if the projection absorbs the comma and the object appears cleanly
closed, $K_{\text{frak}}$ is the conversion re-entering it at the boundary to
the SI level (Doc.~298). The embedding $\iota$ (Doc.~299) is this
$K_{\text{frak}}$ conversion here.

\subsection*{The meshing, not the section}

The qualifier \enquote{a section of the same recursion} is deliberately
indefinite. The $75$ pieces are equivalent under the shared discrete symmetry:
$75 = 3\cdot 5^2$ carries exactly the two anchors that also generate the common
object --- the $Z_3$ threefoldness (the same as in $2/9=2/3^2$) and the
icosahedral fivefoldness (the same $5$ as in $\arccos(1/\sqrt5)$ and in
$100=4\cdot5^2$, Doc.~042). The symmetry maps the pieces onto one another; none
is distinguished.

Hence the question \emph{which} of the $75$ pieces the projected window meets is
not open but moot: a distinguished assignment is precisely what the symmetry
forbids. What is asserted is only the \emph{existence of the meshing} --- that
the closed object sits as a piece of this partition at all, whose angular
structure $D6$ fixes and whose count factors as $3\cdot5^2$ --- not an index
assignment.

For $K_{\text{frak}}$ this is inconsequential, and it is exactly why the
conversion works without identification: $K_{\text{frak}}=1-100\xi$ is the
per-step factor of the partition, the \emph{same} across all $75$ steps
precisely because they are equivalent. It needs no selected piece to be defined;
the mere existence of the meshing suffices for the conversion to the rolled-out
curve to be $1-100\xi$.

\subsection*{Limit and status}

The chain is as strong as its anchoring: $2/9$ and $D6$ are booked as shared
objects (category~B), $K_{\text{frak}}=1-100\xi$ is independently anchored via
Doc.~133. Comma check script:
\texttt{Dok300\_Skripte/ffgft\_300\_kfrak\_schliessungskomma\_pruefung.py};
time-sector counter-run: \texttt{Dok299\_Skripte/ffgft\_299\_iota\_gegenlauf\_winding\_locked.py}.
