%% 301_Information_Umkehrtest_En_ch.tex
%% FFGFT -- Doc. 301: The reversibility test -- information as output, not as a base unit;
%%                    the bit as the ultimate, input-condition-erasing reduction
%% Author: Johann Pascher
%% Date: July 2026
%% Language: English

\section*{Doc.~301 \quad The reversibility test --- information as output, not
as a base unit}

\section{Occasion and scope}

The collaboration produced a stability picture that carries three quantities ---
information, coherence and energy (ICE) --- as equally ranked corners of a
triangle, with a reference at the centre. This document examines what
categorical standing \enquote{information} actually occupies in such a picture.
The finding is directed but not single-level: \emph{information} is not
synonymous with \emph{bit}. The term splits into three levels --- the bit
(comparator output), the description (chosen representation) and the absolute
identity (the complete object itself). As a base unit beside energy, information
qualifies on neither of the two lower levels; it is fundamental only in the
absolute sense, as the topmost identity. The criterion that carries this
classification is reversibility. Scope: a Category-B finding (categorical
classification, no physical derivation, no claim that FFGFT derives a bit). The
result is a sharpening of the reduction principle of Doc.~296 and the comparator
reading of Doc.~300.

\section{The criterion: fundamental means reversible}

A quantity is fundamental exactly when its transformation has no distinguished
direction --- when one can turn it on its head and it still stands. The
touchstone is energy in natural units. Through the relation
\begin{equation}
  \tilde{T}\cdot m = 1
\end{equation}
energy, mass and the dual time are not independent axes but three views of one
quantity:
\begin{equation}
  E \;=\; m \;=\; \frac{1}{\tilde{T}}.
\end{equation}
This transformation is symmetric: one may begin at $E$ and read off $m$, at $m$
and read $\tilde{T}$, at $\tilde{T}$ and read $E$. No side is the primary one,
none is input or output. This is precisely why energy is intrinsic and the
energy scale $E_0$ belongs to the framework natively (Doc.~292): the
transformation discards nothing, each view carries the others fully. Here
reversibility is not an addition but the expression of the fact that nothing is
lost. In SI, $\hbar$ and $c$ re-enter as conversion factors and pull the three
apart; that is the projection, not the core.

\section{Intrinsic and relational}

Not every quantity carries itself. A geometric quantity is \textbf{intrinsic}:
an area, a winding has its value without reference to anything else. A
thermodynamic or informational quantity is \textbf{relational}: entropy is
defined only relative to a coarse-graining, a bit only relative to a
distinguished reference. There is no bit \enquote{as such}. This distinction is
the categorical basis of what follows: intrinsic quantities can be fundamental,
relational ones always presuppose a \emph{with respect to} and therefore cannot
be self-carrying.

\section{The ICE triangle as a comparator}

Read in circuit terms, the ICE picture coincides corner for corner with the
comparator of Doc.~300 --- not by analogy, but as the same object drawn from the
other side. Usable information at the output of a comparison requires three
ingredients and a fourth condition:
\begin{itemize}
  \item \textbf{Energy} --- the signal at the $+$input carries a level; without
    a level there is no comparison.
  \item \textbf{Coherence} --- the signal has phase structure, is not mere
    noise; geometrically the phase on the windings.
  \item \textbf{Reference} --- the $-$input, the threshold against which the
    decision is made; it must come from a \emph{different}, derived source than
    the signal (Doc.~300: reference from derivation, not from a copy).
  \item \textbf{Hysteresis} --- a bare threshold chatters at the switching
    point; a transition counts only once it stands over a dead-band (amplitude
    hysteresis) or persists across a window (time hysteresis, debouncing).
    Without a dead-band the output is meaningless, however clean the energy and
    coherence.
\end{itemize}
\emph{Important:} The ICE triangle contains energy, coherence and reference, but
no declared dead-band. Hysteresis is the fourth condition without which
\enquote{threshold exceeded} does not become \enquote{transition counts}. The
time hysteresis used in the finite proxy implementation is exactly the sliding
window $M_m$ (Doc.~300/297) --- a debouncer, and as such a short-term buffer, not
an accumulating memory.

\section{Information is output, not input}

The comparator thus inverts the order the triangle suggests. Energy, coherence,
reference and hysteresis stand at the \emph{input}. Information is what emerges
at the \emph{output} once those conditions are met: the bit the threshold
decision produces. It is not the ingredient the comparison is built from, but its
result. But a quantity that presupposes the whole apparatus in order to arise
cannot be the base unit the apparatus is made of. This is also why earlier
attempts to anchor a bit as a base unit had to fail: they sought to posit the
output product as an input quantity --- a circularity.

\section{The reversibility test}

The criterion of Section~2, applied to information, comes out negative.
$E$--$m$--$\tilde{T}$ is bidirectional: each view reconstructs the others, because
nothing is discarded. The comparator is \emph{unidirectional}:
\begin{equation}
  \text{signal} + \text{reference} + \text{hysteresis}
  \;\longrightarrow\; \text{bit},
\end{equation}
and this arrow does not reverse. From a bit one does not recover the signal, not
its level, not its phase, not the reference threshold against which the decision
was made. Fundamental quantities are reversible because they preserve;
information is not reversible because it erases. \emph{Fundamental and bit thus
exclude one another not accidentally but by definition}: reversibility demands
that the generating structure remain preserved in the result, and the bit is
precisely the operation that does not preserve it.

\section{The bit as ultimate reduction}

By Doc.~296, every evaluation is a reduction: it leaves out, and precisely by
leaving out it makes a sub-domain evaluable. The bit is the limiting case of this
statement --- the \emph{maximal} reduction. A whole signal course, with its
energy, its phase, its position relative to the threshold, is collapsed to a
single yes/no; less is not possible. And the irreversibility is not an addition
to the reduction, it \emph{is} the reduction: the threshold, the phase, the input
conditions \emph{were} --- at the moment the comparator flips, they are gone. The
bit no longer carries how it came about. It says \enquote{above} or
\enquote{below}, not at which level, not at which phase, not how far from the
reference. Everything that produced the result is no longer contained in the
result --- and therefore there is no way back, because the where-to-return-to is
exactly what the reduction has erased.

\section{The Landauer connection}

This irreversibility is the thermodynamic side of the same matter. Erasing a bit
costs $k_B T \ln 2$ and produces entropy; the direction is built in, because
erasing information produces heat. To reverse the comparator would mean
recovering that entropy, and that is thermodynamically excluded. This explains in
retrospect why anchoring a base-unit bit to thermal motion went so badly in the
prior working state: the attempt bound a directed, reducing quantity to a
reversible base structure; the directions do not match. Not a lack of
calculation, but a categorical incompatibility was the cause.

\section{Three levels of information: bit, description, absolute identity}

The reversibility test separates cleanly, but the boundary does not run at
\enquote{information} wholesale. The term splits into three levels that answer
the test differently.

\emph{First level --- the bit.} The comparator output: reference-dependent,
generated at the output, erasing the input conditions. It fails ---
unidirectional, reducing, the ultimate reduction (see \enquote{The reversibility
test} and \enquote{The bit as ultimate reduction}). A consequence, not a
foundation.

\emph{Second level --- the description.} Information is not the bit but, first,
a \emph{description}: the representation of a state of affairs. Which kind of
description is chosen --- geometric, mathematical, rhetorical --- changes the
representation, not the state of affairs. This is the same line as in
Doc.~297/300: a representation is a choice of coordinates, not a structural
property of the object; different descriptions of the same object are mutually
translatable, but none is the object. And none is ever \emph{complete}: every
description is a projection (Doc.~296), hence a reduction, hence it leaves out. A
complete description would exist only if a projection left nothing out --- and
then it would evaluate nothing. The description therefore also fails the
reversibility test: as a route back to the object no single description is
invertible, because each is incomplete. The descriptions are mutually
translatable, but none reconstructs the whole.

\emph{Third level --- the absolute identity.} Fundamental in the full sense is
the complete object itself alone: the boundaryless $T^4$ object (the core $\xi$
on $T^4$), of which every projection shows only a section. \emph{Information in
the absolute sense} is not a quantity \emph{in} the system and not a single
description, but the complete self-identity of the object with itself, prior to
any projection. Only this level passes the reversibility test --- trivially,
because there is nothing to leave out: there is no \enquote{with respect to},
because there is no external standpoint. This is the topmost identity; to it, and
to it alone, \enquote{information} belongs fundamentally (self-reference,
Doc.~248 §8).

\emph{Important:} The geometric structure of the core --- winding numbers as
topological invariants, carried losslessly --- belongs to the third level, to the
object itself; it is not \enquote{information} in the bit sense. A geometric
\emph{description} of that structure, by contrast, remains second level: a
projection. And the bit read off is first level. The three meanings must not be
conflated. In particular: if anything stands \enquote{above} energy, it is not
the bit but the complete object --- and energy is one of its projections (a
particularly intrinsic one, but a view).

\section{Digitisation: the staircase and its smoothing}

The reason a bit can never carry the whole information is the basic mechanism of
digital technology: analogue-to-digital and digital-to-analogue conversion. A bit
is the 1-bit quantisation --- the coarsest possible staircase, a single
threshold. Any finer staircase with finitely many steps remains categorically the
same object, only at higher resolution.

The torsion winding provides the natural example. The unrolled recursion closes
after exactly $75$ equal segments (Doc.~300/295); decomposing the winding into
these $75$ parts digitises it --- $75$ discrete steps. By DA conversion a
continuous course can be regained from them. But the reconstruction is already
lossy, for two reasons:
\begin{itemize}
  \item Quantisation discards what lay \emph{between} the steps. The continuous
    structure between the $75$ nodes --- the exponentially shrinking steps of the
    log-spiral, the cumulated integral $D(k)$ (Doc.~295) --- is not contained in
    the $75$ values.
  \item The DA converter outputs a staircase, not a smooth curve. One must
    \emph{smooth} the steps (reconstruction filter). But the smoothing is an
    interpolation --- an assumption the filter adds, not information contained in
    the digital value. What lies between the steps is guessed, not recovered.
\end{itemize}
The AD/DA round trip is thus precisely \emph{not} a true inverse but a directed,
lossy process: the reversibility test in circuit form. The lost intermediate
structure is not reconstructed by the smoothing but replaced by a filter
assumption --- the same signature as the bit, whose input conditions
\enquote{were} and no longer stand in the result.

\emph{Important:} Even the \emph{natural} staircase --- $75$, the closure number
--- does not carry the continuum. It is the right number for the closure step,
but not for the continuous course: the full object is richer than any finite
staircase (Doc.~296). No $N$, not even the structurally distinguished $N=75$,
carries the continuum. Placed within the three levels: the bit is the 1-step
quantisation (first level, output); any finite $N$-staircase --- including the
$75$-division --- is a description of finite resolution (second level), finer than
a bit but still lossy, still a projection; the continuous winding, the complete
object, alone carries everything (third level). The smoothing is exactly the
place where the description overlays its incompleteness with an assumption.

\section{Refinement: resonances enforce the quantisation}

The previous section spoke of the \enquote{continuous structure between the
nodes}. This must be sharpened, for on the finest scale the object is not
continuous. The torus is compact, and a compact torus has a \emph{discrete}
spectrum: the resonances on $T^4$ --- the eigenmodes of the $T^4$
connection-Laplacian (Doc.~283) --- enforce a quantisation. In the smallest parts
\emph{not all possibilities are equally weighted}; the resonance structure
singles out particular discrete states. This is exactly why the Standard Model
comes out discrete --- the masses, $\theta=2/9$, the $Z_3$ structure are
resonances, not arbitrary points of a continuum.

From this follows a restriction of the loss argument: there is a \emph{smallest
possible jump}, the quantum set by the resonances. A conversion that goes down to
this smallest jump and meets the resonance structure is \emph{permitted} --- it
is not lossy, because below the jump there are no further states that could be
lost. What lies between a \emph{coarser} staircase is therefore not a continuum
but finer \emph{discrete} resonance structure, and it has a floor.

The reversibility test thus sharpens: loss does not arise from quantisation as
such, but only from a staircase that is \emph{coarser} than the resonances or lies
\emph{across} them --- for instance an arbitrary equal division. A
resonance-faithful conversion down to the smallest jump passes the reversibility
test: it captures the actual discrete structure, not an approximation. The bit
nonetheless remains the ultimate reduction --- a single threshold is coarser than
the resonance floor and does not meet it. And beyond a single scale it still
holds that no description of one scale captures the cross-scale richness of the
full object (Doc.~296). The statement \enquote{the full object is richer than any
finite staircase} is therefore to be read \emph{across scales} --- within a scale,
the resonance-faithful staircase is by contrast the true structure.

\section{Temporal and topological boundarylessness}

Two properties of the absolute identity follow from analysis and topology and are
therefore booked as \emph{consequences}, not as posits.

\emph{No reachable edge of the recursion.} The map
$\xi_{n+1}=\xi_n(1-100\,\xi_n)$ has $\xi=0$ as a fixed point; $\xi_n$ decays
monotonically towards zero but reaches zero in no finite step (Doc.~296). There is
no first and no last step. A \enquote{simplest initial state} --- a scale without
fractal structure, from which the refinement would only begin to grow --- does not
exist: the self-similarity (factor $1/e$ per $2\pi$ turn, the log-spiral) is not a
property that builds up but is already fully present in the map. A structural
beginning would break the scale invariance that defines the recursion --- a
contradiction, not a world-view.

\emph{Time without a markable origin.} Experienced time \emph{is} the cumulated
defect $D(k)=\sum 100\,\xi_n$ (Doc.~295), the integral over
$\delta t = 1/(100\,\xi_n)$. Since the recursion has no first step, $D(k)$ has no
distinguished origin. Time is the recursion, not its container; to seek a
\enquote{beginning of time} would place the recursion at a moment it only
generates.

\emph{No external standpoint.} $T^4$ is compact and boundaryless,
$\partial T^4 = \emptyset$. That is a topological fact, not a posit. From it
follows that there is no standpoint outside the object --- and hence the \enquote{no
with respect to} of the absolute identity: the complete object has no outside
against which to demarcate itself.

Taken together: the absolute identity is boundaryless spatially (no outside,
$\partial T^4=\emptyset$) and temporally (no beginning, no reachable edge of the
recursion) --- the same property in two guises: no standpoint beyond the object.
These statements are derivable from analysis and topology and carry no speculation
marker.

\section{The reflexive case --- what goes beyond the mathematics}

\emph{What follows explicitly goes beyond the mathematics and is booked as
philosophically speculative (P35). These are two interpretive jumps, not
calculations.}

Applying the three levels to FFGFT itself, the framework --- the torus,
$\tilde{T}\cdot m=1$, $\xi$ across all scales --- is a \emph{description} (second
level), necessarily incomplete. This is not a weakness of this framework in
particular but what a description is: no theory is ever its object, each projects
and leaves out. FFGFT says so explicitly, whereas naive realisms behave as though
they were the territory.

\emph{First jump --- the realist posit.} That the resonance-faithful description
traces a \emph{real} object and is not merely a consistent structure is posited,
not proven. The mathematics shows resonance fidelity ($\alpha$ at the measured
value, the masses as eigenmodes, Koide); that fidelity traces reality rather than
mere consistency is the realist wager. The deflationary reader may always say: all
just description, the object a useful fiction. FFGFT's answer is not a proof but the
wager that the resonance-faithful success is better explained by a real object than
by coincidence --- and the only distinctive thing is that the resonance hits make
that wager falsifiable.

\emph{Second jump --- the diagnosis of the Word reflex.} The pull of the
information-as-fundamental idea (\enquote{In the beginning was the Word};
\enquote{it from bit}; the mass-energy-information equivalence) may stem from a deep
cultural reflex: that information is the first substance from which matter follows.
The reversibility test inverts the order: the word is the bit, and the bit is the
last reduction, not the first creation. In the beginning was the geometry (the
object); the word is what one of its scales reads off. This is a cultural-cognitive
hypothesis about \emph{why} the intuition pulls --- not a mathematical statement; the
reversibility test itself remains mathematical.

\emph{Self-projection.} FFGFT is a $T^4$ process describing $T^4$ (Doc.~248 §8):
the description is of the same stuff as the object and is generated by it (the
describing process is itself a $T^4$ process on the cognitive scale). FFGFT is
therefore neither external to the object nor the object, but its
\emph{self-projection} --- the object describing itself on one of its own scales.
Self-reference as an ontological locus, booked as a posit.

Hence the limit of the opening question: \enquote{How much ontological reality does
FFGFT have?} is itself a second-level question --- it presupposes a describing
standpoint that does not exist over against the third level. One cannot ask from
outside how much reality the object has, because there is no outside; one cannot ask
what came before it, because there is no before. At the level of the absolute
identity the question dissolves.

\section{Status}

Categorical classification (Category~B), not a physical derivation step. The
finding places information relative to programmes that posit it as a physical
base quantity (such as a mass-energy-information equivalence): such programmes
treat information as input; the reversibility test shows that the bit is output.
The three levels are to be booked at different temperatures:
\begin{itemize}
  \item \textbf{Bit} --- \emph{proven}: the ultimate, input-condition-erasing
    reduction is irreversible and therefore a consequence, not a base unit
    (reversibility test).
  \item \textbf{Description} --- \emph{structural}: every representation is a
    projection and hence incomplete (reduction principle, Doc.~296); a choice of
    coordinates, not a structural property of the object.
  \item \textbf{Absolute identity} --- \emph{ontological posit}: information in
    the absolute sense is identified with the complete object and is the topmost
    identity (self-reference, Doc.~248 §8). This is posited, not derived.
\end{itemize}
The load-bearing statement in one sentence: \emph{fundamental $\Leftrightarrow$
reversible; bit and single description fail the test (the bit erases, every
description is incomplete), the absolute identity alone passes it --- so
information counts as fundamental only in the absolute sense, as the topmost
identity, and this is in FFGFT the core $\xi$ on $T^4$, not a quantity beside
it}. Connections: Doc.~296 (reduction as the condition of evaluability),
Doc.~300 (comparator, reference, hysteresis), Doc.~283 (discrete resonance
spectrum on $T^4$), Doc.~292 ($E_0$ intrinsic), Doc.~248 §8 (self-reference).
