%% 303_Repraesentationale_Identitaet_En_ch.tex
%% FFGFT -- Doc. 303: Representational identity across role changes;
%%                    a governance layer beneath the claim-state ledger
%% Author: Johann Pascher
%% Date: July 2026
%% Language: English

\section*{Doc.~303 \quad Representational identity across role changes ---
a governance layer beneath the claim-state ledger}

The claim-state ledger asks whether a transition is \emph{earned}: whether an assertion
may be booked as proven, restricted, or blocked. That test is preceded by an earlier
question it does not ask --- whether the object undergoing the transition has kept its
\emph{representational identity}. A role change is not a strength change. The same symbol,
the same number, the same structure can successively occupy different representational
roles --- mathematical object, computational output, candidate physical quantity,
observable, ontological posit --- and it is between those roles that the real, often
unnoticed, shift takes place. This document names that layer, gives two case studies (one
separates the definition (which identifies) from the governance (which
preserves), and proposes an identity-preservation record as a layer prior to the ledger.

\section{Roles, not strengths}

A representational object can occupy at least the following roles within a framework:

\begin{itemize}
\item \emph{mathematical object} --- a quantity within a formal structure, with no
physical attribution;
\item \emph{computational construct / output} --- the deterministic result of a
procedure;
\item \emph{candidate physical quantity} --- an object to which a physical meaning is
\emph{proposed} but not yet secured;
\item \emph{observable} --- a quantity coupled to measurement;
\item \emph{ontological posit} --- a claim about what \emph{is}, beyond derivation and
falsification.
\end{itemize}

These roles are not stronger or weaker versions of the same claim; they are different
\emph{types}. The claim-state ledger sorts assertions by evidential strength (proven /
restricted / blocked); the role question sorts objects by their representational type.
Both axes are needed, and they are orthogonal.

\section{The failure mode: role drift}

The typical error is not the wrong evidential strength but \emph{silent role drift}: the
same numerical or mathematical object changes its type without the change being declared
as such. A number produced as a lattice output is labelled a \enquote{bare} physical
mass, then carried as a candidate observable, and finally treated as an observed value
after a correction still to come. These are four representational roles of the same
numerical object. None of them is inadmissible in itself; what is inadmissible is only to
present the role change as a mere strengthening of the same claim. This is precisely
where disagreement enters quietly --- often long before the evidential question is even
asked.

\section{Case study I (external): one number in four roles}

A numerical object from a discrete lattice model passed, in an IPI discussion, through
four roles: first a \emph{lattice output} (a deterministic computational result), then a
\emph{bare topological mass} (a physical attribution), then a \emph{candidate} for an
observable ratio, and finally an \emph{observable after screening} (under a
reduction mechanism not yet constructed). The progress of the discussion consisted not in
refuting any one of these roles but in \emph{separating} them: once the roles were laid
apart, each could be examined on its own constitutional footing --- the lattice output as
proven, the physical attribution as a definition, the observable as a still-open
transition. Separating the roles was the actual methodological gain, independent of the
fate of the model.

\section{Case study II (internal): the information unit}

The same role drift occurred, in the preparation of the present document series, within
FFGFT itself. The question of the \enquote{minimal information unit} was answered
successively with four different objects: first a \emph{spectral eigenmode} (an object of
the mass operator), then an \emph{area} (the holographic choice of one bit per area
element), then a \emph{counting quantity} of order $1/\xi$, and finally the
\emph{topological winding quantum} $\Delta w = 1$. These four are not stronger and weaker
versions of the same unit; they are four different representational objects that
successively bore the same name. The role change went unnoticed until the identity was
fixed by a \emph{prior, explicit definition}: Doc.~257 fixes the information unit, by
definition, as the winding quantum $\Delta w = 1$ ($\pi_1(T^4) \cong \mathbb{Z}^4$,
scale-universal). Only that identity anchor made the remaining roles legible as what they
are: the area as a lossy projection, the $\ln 2$ as a thermodynamic shadow, the energy
$\hbar c/L$ as a scale-specific projection --- all \emph{derived or projected}
appearances of the one fixed unit, not competing definitions.

\section{Definition identifies, governance preserves}

The lesson from both cases seems at first to be that an \emph{identity anchor} preserves
identity. But that conflates two questions that belong apart --- and the conflation is
exactly the role drift this document describes, now applied to the document itself. There
are two constitutional questions:

\begin{itemize}
\item the \emph{declarative} question --- \emph{what is this object?} --- is answered by a
\emph{definition}. The definition \emph{identifies}: it sets the constitutional reference
point against which any further claim can be checked at all. In FFGFT, $\Delta w = 1$
(Doc.~257) does this: it fixes \emph{what} the information unit is.
\item the \emph{governance} question --- \emph{under what operations does it remain the
same object?} --- is different. A definition sets the initial reference; it does not
\emph{preserve} identity. Identity is preserved only by the governance imposed on
subsequent transitions.
\end{itemize}

In short: \emph{the definition identifies, governance preserves}. The earlier notion of an
\enquote{identity anchor} carried both roles under one name --- definition \emph{and}
preservation mechanism --- and is therefore itself an instance of the drift described
here. It is cleaner to separate them: the definition is the declared reference point;
governance is a distinct layer that records what happens to that reference at each
transition.

\section{The identity-preservation record}

A merely binary check --- same type before and after the transition $\to$ the ledger;
different type $\to$ substitution --- is too coarse. A transition can treat an object's
declared identity in more than two ways, and the governance layer keeps an explicit record
of which: for each transition it records whether it

\begin{itemize}
\item \emph{preserves} --- the same object in the same role;
\item \emph{projects} --- a scale- or coordinate-dependent appearance of the same object,
lossy and not fundamental;
\item \emph{transforms} --- a derivable reshaping that keeps the reference;
\item \emph{substitutes} --- a different object under the same name (undeclared, this is
role drift; declared, it needs its own licence);
\item \emph{bridges} --- a secured mapping onto an object of another framework.
\end{itemize}

Read against FFGFT's own information unit: the winding quantum $\Delta w = 1$ is
\emph{preserved}; energy ($\hbar c/L$) and area are \emph{projections}; the $\ln 2$ is a
\emph{transformation} (the thermodynamic shadow); the earlier wandering eigenmode $\to$
area $\to 1/\xi$ was \emph{substitution} under a retained name, until the definition
(Doc.~257) fixed the reference; and the verification direction FFGFT$\to$HLV is a
\emph{bridge}. The record decides no physics; it only keeps visible, at each step, what
happens to the identity --- before the ledger asks whether the step is earned.

\section{Relation to the ledger}

Three levels are now separated. The \emph{definition} identifies the object
(declaratively). \emph{Governance} preserves its identity across transitions and keeps, in
the preservation record, whether a step preserves, projects, transforms, substitutes, or
bridges. The \emph{claim-state ledger} scores whether a transition is \emph{earned}
(proven / restricted / blocked). Governance is prior to the ledger: it ensures that a
discussion is held about the \emph{same} object before it is held about that object's
evidential strength. All three levels are largely independent of the underlying physics
--- they concern the bookkeeping of representation, not its content --- and gain importance
as independently developed frameworks come to interact. Whether this bookkeeping is kept
informally or through a systematic mechanism does not change its effect: the discussion
shifts away from defending positions and towards localising where assumptions reside, what
has genuinely been derived, and where an object changes its identity.

\section{Status}

This document is a methodological proposal, not a physical derivation. The FFGFT-specific
statements --- the information unit as $\Delta w = 1$, the three levels, the projection
nature of energy and area --- are corpus-supported (Doc.~257, 301, 300); the role taxonomy
and the identity check are constitutional bookkeeping and are booked as such. The second
case study is explicitly self-critical: FFGFT itself required the discipline proposed
here, and the identity anchor $\Delta w = 1$ was recognised as such only in retrospect
(Doc.~257). The occasion of the question --- an objection to elementary cells, the
constitutional framing of the transition problem, and the representational typing of the
objects involved, as developed within the IPI circle (Takayuki Ueda, Stefaan Vossen,
José Tomás Guevara Calderón) --- is gratefully acknowledged. The distinction between
declarative identity (definition) and its preservation by governance, and the five-way
preservation record (preserve / project / transform / substitute / bridge), were sharpened
in exchange with Stefaan Vossen; they are constitutional language made jointly visible,
neither a replacement for nor an adoption of any particular governance programme.
