%% 306_Native_Zeit_Energie_Reziprozitaet_En_ch.tex
%% FFGFT -- Doc. 306: Replacing the Heisenberg import by native time-energy reciprocity
%% Author: Johann Pascher
%% Date: July 2026
%% Language: English

\section*{Doc.~306 \quad Native time--energy reciprocity --- replacing a borrowed justification}

\begingroup\small\noindent
\textbf{Abstract.} Documents~025 and~063 justify the absence of a cosmic initial singularity by
Heisenberg's energy--time uncertainty relation. That justification is here \emph{replaced}, not
refuted: the conclusion (no singular beginning) stands, the derivation is replaced by a native
one. Three defects are named --- an inverted implication (a finite $\Delta t$ yields a
\emph{finite} bound, not $\Delta E\to\infty$), a misapplication (the $\Delta t$ of the relation is
an observable's characteristic change time, not a cosmic age), and a breach of style
(\enquote{irrefutably} is not a ledger term). The replacing chain is native: from $T\cdot m = 1$
(Doc.~003/010), hence $T\cdot E = 1$, it follows that $E\to\infty \Leftrightarrow T\to 0$; but
FFGFT time carries a minimal, non-vanishing increment $d_1 = 100\,\xi_1 = 1/75$, fixed by
$\xi = 4/30000$. $T$ is therefore bounded below and $E$ bounded above --- an infinite density is
structurally excluded. In addition $\partial T^4 = \emptyset$: the question of a
\enquote{beginning} presupposes a boundary that a compact torus does not have. The same chain
determines the black hole: the horizon is the \emph{extremum} --- slowest time $T=T_0$, maximal
concentration $E=1/T_0$, maximal curvature, all finite and well defined --- no singularity, and
hence nothing to repair. The same holds at the other end: $T\cdot m = 1$ has no solution at $m=0$ --- FFGFT knows no \emph{empty} state, only a thinnest one. Both edges are excluded: the dense one is \emph{quantified} from $\xi$ ($T_0=\xi\,t_P$, $E_\text{max}=E_P/\xi$, with exact closure $T_0 E_\text{max}=1$; simultaneously the natural UV cutoff of the field theory), the thin one structurally, but unquantified --- the latter no deficiency but a consequence of $T\cdot m=1$: each system carries its own upper bound $R_\text{Torus}(m)=\hbar/mc$, so the cosmological sector requires its \emph{own} scale.
\par\endgroup

\medskip

\section{What is being replaced}

Docs.~025 and~063 both contain the passage that Heisenberg's uncertainty relation
$\Delta E\cdot\Delta t \ge \hbar/2 = 1/2$ (natural units) \enquote{irrefutably proves} a classical
Big-Bang singularity to be impossible, and infer:
\begin{itemize}
\item a temporal beginning would mean $\Delta t$ finite;
\item this leads to $\Delta E \to \infty$;
\item hence the universe must have existed eternally.
\end{itemize}
The \emph{conclusion} --- no singular beginning, instead a finite core with a minimal scale $L_0$
from $\xi$ --- is retained. The \emph{derivation} is replaced. Three reasons.

\section{Three defects of the borrowed justification}

\paragraph{(M1) Inverted implication.} The inference \enquote{$\Delta t$ finite $\Rightarrow$
$\Delta E \to \infty$} is invalid. From $\Delta E \ge 1/(2\Delta t)$, a \emph{finite} $\Delta t$
yields a \emph{finite} lower bound on $\Delta E$; a beginning a finite time ago would give a tiny,
harmless bound. $\Delta E \to \infty$ follows only from $\Delta t \to 0$, i.e.\ from the
\emph{instant} $t=0$, not from a finite beginning. This is not a slip but a reversed implication.

\paragraph{(M2) Misapplication.} Energy--time uncertainty is not a canonical uncertainty relation.
By Pauli's theorem there is no self-adjoint time operator conjugate to a Hamiltonian bounded
below; the rigorous form (Mandelstam--Tamm) defines
$\Delta t = \Delta A / |\mathrm{d}\langle A\rangle/\mathrm{d}t|$ --- the characteristic
\emph{change time of an observable}, not an elapsed duration. The \enquote{age of the universe} is
not an admissible $\Delta t$ for this relation.

\paragraph{(M3) Breach of style.} \enquote{Irrefutably proves} is a strength of assertion that does
not occur in the FFGFT ledger. The ledger knows \emph{proven} (derived from $\xi$),
\emph{restricted}, and \emph{blocked}; a statement is certified as sufficiently precise to be
decidable, not as irrefutable.

\paragraph{The overarching point.} Heisenberg's relation is not false within the QM framework, but
it is \emph{projected}: it belongs to the description level that FFGFT understands as a projection
from the deeper structure. An argument against the cosmic singularity that leans on it does not
leave the projection --- it circulates within it. This is exactly what Doc.~298 warns of: one does
not exit the projection by importing its theorems.

\section{The replacing native chain}

\paragraph{(1) Exact reciprocity.} The time--mass duality (Doc.~003, cf.\ Doc.~010) reads
\begin{equation}
T \cdot m = 1, \qquad\text{and with } E = m \text{ (natural units)}\quad
\boxed{\,T \cdot E = 1\,}
\end{equation}
This is an \emph{equation}, not an inequality --- a sharper statement than
$\Delta E\cdot\Delta t \ge 1/2$, and a native one.

\paragraph{(2) Time has a minimal increment.} FFGFT time is the cumulated defect of the unrolled
winding,
\begin{equation}
D(k) = \sum_{n\le k} 100\,\xi_n \;\to\; \ln\!\left(1+\tfrac{k}{75}\right),
\qquad \xi_{n+1} = \xi_n\,(1-100\,\xi_n),
\end{equation}
with the first step
\begin{equation}
d_1 = 100\,\xi_1 = 100 \cdot \tfrac{4}{30000} = \tfrac{1}{75}.
\end{equation}
To be precise: $D(k)$ \emph{grows} without bound as $k\to\infty$ (logarithmically). The
singularity-free statement is not \enquote{$D$ never diverges} but: \emph{$D(k)$ is finite at
every finite $k$, and there is no point at which $D$ or its increments diverge.} The first step is
finite and fixed by $\xi$; no time increment is smaller than $d_1$.

\paragraph{(3) The inference.} From $T\cdot E = 1$,
\begin{equation}
E \to \infty \quad\Longleftrightarrow\quad T \to 0 .
\end{equation}
But no state with $T = 0$ exists in FFGFT: time is bounded below by a finite increment fixed by
$\xi$. Hence $E$ is bounded above --- an infinite energy density is \emph{structurally} excluded,
not by a statement about measurement precision. The exact numerical bound depends on the
normalisation and is not asserted here as a number; the structural statement stands without it.

\paragraph{(4) The boundary question.} The torus is compact and boundaryless,
$\partial T^4 = \emptyset$ (Doc.~302; cf.\ Doc.~263, Doc.~296). The question \enquote{what was at
$t=0$?} presupposes a boundary at which a beginning could sit. A compact torus has none. The
question is therefore not wrongly \emph{answered} but wrongly \emph{posed}: it imports the
decompactified projection as ontology. What standard cosmology reads as a singular beginning is
the point at which the \emph{projection} ends --- not the world.

\section{The black hole: an extremum, not a singularity}

The same chain yields the FFGFT statement about black holes --- and it is remarkably
unspectacular: nothing diverges.

From $T\cdot E = 1$ with the lower bound $T \ge T_0$ (the smallest possible time interval, denoted
the same way in the original T0 notation; cf.\ $\Omega(T)=T_0/T$ in Doc.~095) it follows
immediately that
\begin{equation}
E \;\le\; \frac{1}{T_0}.
\end{equation}
The extrema are \emph{quantified} in the corpus and derived from $\xi$. The minimal length
$L_0 = \xi\,\ell_P$ (Doc.~182) yields, via energy--length reciprocity, the cutoff
\begin{equation}
E_\text{max} = \frac{\hbar c}{L_0} = \frac{E_P}{\xi} \approx 7500\,E_P \approx 9.16\times10^{22}\,\text{GeV},
\qquad
T_0 = \xi\, t_P \approx 7.19\times10^{-48}\,\text{s}
\end{equation}
(Doc.~250, Doc.~290). The reciprocity closes \emph{exactly}: $\xi$ cancels,
\begin{equation}
T_0 \cdot E_\text{max} \;=\; (\xi\, t_P)\cdot\frac{E_P}{\xi} \;=\; t_P \cdot E_P \;=\; 1
\qquad\text{(natural units)} .
\end{equation}
This is not a coincidence but the consistency of the construction: $T\cdot E = 1$ holds at the
extrema, not merely in the middle range.

The same cutoff appears in field theory: the fractal torus supplies a \emph{natural UV cutoff} at
$E_P/\xi$, which is why traditional renormalisation is not required in the full FFGFT formulation
(Doc.~019, Doc.~202); the same threshold explains the rarity of magnetic monopoles (Doc.~143). The
Lagrangian does not diverge because the \emph{geometry} supplies the cutoff --- the minimal time is
not a regulator added afterwards, but follows from the structure.

\paragraph{Scales, not totals.} One clarification, without which everything below would be
misread: $T_0$ and $E_\text{max}$ are \emph{scales}, not bounds on totals. $T_0$ is the minimal time
\emph{increment} of the winding; $E_\text{max}$ is the maximal energy \emph{per fundamental cell},
i.e.\ per elementary excitation --- a \emph{cutoff}, and a cutoff always bounds a single mode, never
a sum. The total energy of a composite system may be arbitrarily large: it consists of many cells,
not of denser ones. A macroscopic body is not \emph{one} winding but very many; \enquote{the $T$ of
the Earth} is not a well-posed quantity, and $\hbar/(M c^2)$ for a stellar mass is not a state of
this relation but a misapplication. $T\cdot E = 1$ and its bounds hold \emph{per excitation}, not
per aggregate.

Accordingly, the statement about the black hole concerns \emph{concentration}, not mass: at the
horizon the \emph{local} density reaches the cell cutoff. The \emph{total} mass remains unbounded ---
a larger hole has more cells, not denser ones.

The horizon is therefore the locus at which the extrema are \emph{attained}:
\begin{itemize}
\item the \emph{slowest time}: $T = T_0$, not $T \to 0$;
\item the \emph{maximal energy and mass concentration}: $E = 1/T_0$ \emph{per cell}, finite
(a density, not a total mass);
\item the \emph{maximal curvature}: finite, because it is tied to $E$.
\end{itemize}
Every one of these quantities is well defined. The horizon is not a boundary to something else,
nor a curtain in front of a singularity, but the surface on which time attains its minimum and
concentration its maximum.

One consequence deserves to be stated, because it is easily missed: in FFGFT there is
\emph{nothing to repair}. Models that replace a singular core by a bounce, a transition shell, or
a daughter branch are fixing a defect that FFGFT never produces. This is not a refutation of such
models --- they work within a continuum picture FFGFT does not share --- but the observation that
the question they answer does not arise here. Where the decompactified description says
\enquote{infinite}, the compact one says only: \emph{this is the extremum}.

\section{The other extreme: the thinnest state}

The reciprocity has two ends. One is the horizon; the other is usually called the
\enquote{vacuum} --- and precisely that name misleads.

\paragraph{The apparent circle.} The objection runs: the vacuum is empty; it appears non-empty
only through curvature; but curvature presupposes mass. No mass, no curvature; no curvature,
nothing to fill the emptiness --- the circle closes.

\paragraph{The circle is an import.} It arises from a \emph{causal arrow} that General Relativity
brings with it: $T_{\mu\nu}$ \emph{generates} curvature; mass is cause, curvature effect. In that
picture one must ask \enquote{what is curving here?}, and without mass there is no answer. FFGFT
has no such arrow. $T\cdot m = 1$ is not a cause--effect relation but a \emph{reciprocity}: mass
and temporal curvature are two readings of the same structure; neither generates the other. The
question \enquote{which came first --- mass or curvature?} is as wrongly posed as the question
about $t=0$: it imports a causal structure the compact description does not have. Nothing needs
generating, and the circle dissolves.

\paragraph{Both ends are excluded.} The fundamental relation itself forbids the edges:
\begin{align}
m \to \infty \;&\Rightarrow\; T \to 0 && \text{excluded by } T \ge T_0 \ \ (L_0 = \xi\,\ell_P),\\
m \to 0 \;&\Rightarrow\; T \to \infty && \text{excluded: } T\cdot m = 1 \text{ has no solution at } m=0.
\end{align}
FFGFT therefore knows \emph{no empty state} --- not because something fills it, but because the
theory contains no description of \enquote{nothing}. The torus with its winding \emph{is} the
object; \enquote{empty} would mean \enquote{no winding}, and the winding is what time is.
\enquote{Vacuum} asserts an emptiness that does not exist in this framework; \emph{the thinnest
state} or \emph{the flattest winding} are the apter terms.

\paragraph{The asymmetry, stated honestly.} The two ends are not equally well determined, and this
should not be made to look tidier than it is:
\begin{itemize}
\item The \emph{dense} pole is hard and derived: $T_0$ and $L_0=\xi\,\ell_P$ follow from $\xi$
(Doc.~182: the chain $\xi \to m_e \to G \to \ell_P \to L_0$ depends on $\xi$ alone).
\item The \emph{thin} pole is \emph{structurally excluded but not quantified}. That $m=0$ is
impossible follows from the relation; \emph{how small} $m$ can become does not --- and for a
\emph{structural} reason, not because of a gap in the derivation. Doc.~182: \enquote{The question of
a universal maximal size of the universe is not well posed: every physical scale has its own
system-specific upper bound $R_\text{Torus}(m) = \hbar/mc$.} That is $T\cdot m = 1$ in geometric
form. If each mass carries its own torus radius, the cosmological scale \emph{cannot} follow from
$\xi$ alone: it belongs to its own system and must be set independently. A separate cosmological
scale is therefore \emph{necessary}, not deficient.
\end{itemize}
A wall below, then, and no universal floor above --- but to each system its own horizon.

\paragraph{What P35 concerns --- and what it does not.} Two things must be kept apart. That the
cosmological sector needs its \emph{own} scale is structural and unobjectionable. Writing it as
$E_H = E_0\,\xi^{41/4}$ is not: the exponent $41/4$ is calibrated to $H_0$, not forward-derived, and
the $\xi$-notation suggests a derivation that does not exist (P35/P36; Doc.~182 says so itself;
Doc.~190). The objection concerns the \emph{notation}, not the necessity of the separate scale.


\begin{figure}[htbp]
\centering
\begin{tikzpicture}[x=0.33cm,y=0.245cm]
% --- Achsen ---
\draw[->,thick] (-50,-8) -- (-15,-8) node[below left=2pt] {\small $\log_{10} T\ [\mathrm{s}]$};
\draw[->,thick] (-50,-8) -- (-50,26) node[above left=2pt,rotate=90,anchor=south] {};
\node[rotate=90,anchor=south] at (-52.6,9) {\small $\log_{10} E\ [\mathrm{GeV}]$};
% Ticks x
\foreach \x in {-50,-45,-40,-35,-30,-25,-20} {
  \draw (\x,-8) -- (\x,-8.6) node[below] {\tiny $\x$};
}
% Ticks y
\foreach \y in {-5,0,5,10,15,20,25} {
  \draw (-50,\y) -- (-50.6,\y) node[left] {\tiny $\y$};
}
% --- die Relation: log E = log(hbar) - log T,  log10(hbar[GeV s]) = -24.1816
% erlaubter Ast: von T_0 (logT=-47.14) nach rechts
\draw[very thick,t0blue] (-47.14,22.96) -- (-16,-8.18);
% verbotener Bereich links der Wand
\fill[gray!12] (-50,-8) rectangle (-47.14,26);
\draw[thick,red!70!black,dashed] (-47.14,-8) -- (-47.14,26);
\node[red!70!black,rotate=90,anchor=south,font=\tiny] at (-48.2,6) {forbidden: $T<T_0$};
% --- Endpunkt (die Wand) ---
\fill[red!75!black] (-47.14,22.96) circle (7pt);
\node[right=5pt,font=\scriptsize,red!75!black,align=left] at (-47.14,22.96)
  {\textbf{Endpoint}\\ $T_0=\xi t_P$, $E_{\max}=E_P/\xi$};
% --- elementare Anregungen ---
\foreach \x/\y/\n in {-43.27/19.09/{Planck}, -26.42/2.24/{Top}, -24.15/-0.03/{Proton},
                      -23.21/-0.98/{Muon}, -20.89/-3.29/{Electron}} {
  \fill[t0blue] (\x,\y) circle (5pt);
}
\node[above right=1pt,font=\tiny] at (-43.27,19.09) {Planck};
\node[above right=1pt,font=\tiny] at (-26.42,2.24) {Top};
\node[above right=1pt,font=\tiny] at (-24.15,-0.03) {Proton};
\node[above right=1pt,font=\tiny] at (-23.21,-0.98) {Muon};
\node[above right=1pt,font=\tiny] at (-20.89,-3.29) {Electron};
% --- Asymptote ---
\draw[->,thick,t0blue] (-17,-7.0) -- (-15.6,-8.4);
\node[font=\scriptsize,align=left,anchor=west] at (-24,-6.6)
  {$m\to 0$: never reached\\ (no solution at $m=0$)};
\end{tikzpicture}
\caption{The relation $T\cdot E = 1$ (in SI: $T\cdot E = \hbar$) in doubly logarithmic
coordinates: a \emph{straight line} of slope $-1$. All elementary excitations lie exactly on it ---
none is privileged, and the line has \emph{no middle}. Exactly one point is distinguished: the
\textbf{endpoint} $(T_0,\,E_{\max}) = (\xi t_P,\ E_P/\xi)$, where the curve \emph{stops} --- the wall
that follows from $\xi$. At the other end it continues as an \emph{asymptote} and never arrives
($T\cdot m = 1$ has no solution at $m=0$). The two edges are therefore of different kinds: on the
left an attained endpoint, on the right an unreachable limit. What is plotted are \emph{scales}
(energy per excitation), not total masses; macroscopic bodies do not belong on this axis.}
\label{fig:306_hyperbel}
\end{figure}

\paragraph{And in between --- a projection, not a structure.} It is tempting to arrange the
systems along a common axis, from maximal to minimal mass concentration, and to find oneself in the
middle of it. That axis, however, is an \emph{external view}: it presupposes a standpoint from which
all systems appear side by side. FFGFT has no such standpoint. $T\cdot m = 1$ holds \emph{per
system}; there is no common $T$ against which to plot, and no scale on which a system could locate
itself.

More sharply: we \emph{project ourselves into the middle}. The axis arises with the observer as its
origin --- whoever lays down the measure necessarily stands where the measure begins. The middle is
therefore not a discovery but a positing, and it goes unnoticed because the one who posits and the
one who is located are the same. For the same reason the edges appear \enquote{extreme}: they are
what lies far from the chosen origin. \emph{Extreme} here means \emph{distant}, not
\emph{privileged}.

Intrinsic time is untouched by this --- it is intrinsic. For an electron it is of no consequence
where an outside observer enters it: its winding is the same in the laboratory as near a horizon,
since $T = 1/m$ and $m$ is the same. What differs is only how another system sees it --- a relation
between two, not a property of one. The \enquote{slowest time} at the horizon, too, is a statement
about the comparison, not about the experience.

The projection is therefore not invalid but a \emph{tool}: without a common axis nothing could be
compared, and understanding requires comparison. It is a means of access, not a constituent of the
structure. It is the same move that dissolved the question of $t=0$ and the singularity, applied a
third time --- now to the scale itself. And it is the sharpest form of the self-reference (Doc.~248):
the thought that lays out the order is itself a process within it; it cannot stand outside, but
\emph{locates itself in the act of ordering}.

\section{An observation on the genesis}

It is notable that 025 and 063 already point to $\xi$ in their \emph{result}: the singularity is
said to be \enquote{replaced by a tiny but finite core with minimal length scale $L_0$ (from
$\xi$)}. The answer therefore already came from $\xi$; only the ladder climbed to reach it was
borrowed. Why the import was made although Doc.~003/010 was available is a \emph{historical
question about the genesis of the corpus}, not a systematic one. It is marked as such here and
left unanswered; any answer would be speculation.

\section{Status}

\emph{Correction / replacement.} The conclusion (no singular beginning; a finite core with a
minimal scale set by $\xi$) is unchanged. The justification in Docs.~025 and~063 is \emph{no
longer authoritative} for this point; it is not recorded as refuted, but as superseded by the
native chain.

\emph{Proven (internal to FFGFT).} $T\cdot m = 1$ (Doc.~003/010); $D(k)$ and $d_1 = 1/75$ from
$\xi$ and the recursion (Doc.~295); $\partial T^4 = \emptyset$ (Doc.~302). The inference
$E\to\infty \Leftrightarrow T\to 0$ follows algebraically from the reciprocity; so does the bound
$E\le 1/T_0$ and with it the characterisation of the horizon as an extremum (no singularity). So does the exclusion of $m=0$ (no empty state).

\emph{Quantified (proven).} The extrema of the dense pole are derived from $\xi$ and computed in
the corpus: $T_0 = \xi\,t_P \approx 7.19\times10^{-48}$\,s and $E_\text{max} = \hbar c/L_0 = E_P/\xi
\approx 9.16\times10^{22}$\,GeV (Docs.~182, 250, 290), with the exact closure
$T_0\cdot E_\text{max} = t_P\cdot E_P = 1$. The fractal torus thereby also supplies the natural UV
cutoff of the field theory (Docs.~019/202/143).

\emph{Structural, not deficient.} The \emph{thin} pole remains excluded but unquantified --- and
that is a statement of the structure, not a gap: from $T\cdot m = 1$ it follows that every system
carries its own upper bound $R_\text{Torus}(m) = \hbar/mc$; a universal maximal size is not
meaningfully demanded (Doc.~182). The cosmological sector therefore requires its \emph{own},
independently set scale.

\emph{Open (P35).} Its \emph{notation} remains to be cleaned up: $E_H = E_0\,\xi^{41/4}$ calibrates
the exponent to $H_0$ and dresses a measured quantity in $\xi$-form; that is not a derivation
(P35/P36, Docs.~182/190). The objection concerns the notation, not the necessity of the separate
scale. The connection $R_H \to \ell_1$ remains open (P20, cf.\ Doc.~267); the cosmological
sector as a whole remains the least determined area of the corpus.
