% Standalone document: T0_Geometrische_Kosmologie_En
% Uses shared T0 header
\input{../../T0_standalone_header_it}

\title{Geometric Cosmology}
\author{Johann Pascher}
\date{2025}

\begin{document}

\maketitle

\chapter{Geometric Cosmology}

	
	
	\begin{abstract}
		This document presents a revolutionary explanation for the cosmological redshift that does not require the assumption of an expanding universe. Based on the first principles of the T0-Theory, the universe is modeled as static and flat. Through a finite element simulation of the T0 vacuum field, it is shown that redshift is a purely geometric effect arising from the extended effective path length of photons traveling through the fluctuating T0 field. The simulation derives the Hubble constant directly from the fundamental T0 parameter $\xi$, thereby resolving the mystery of dark energy and the Hubble tension.
	\end{abstract}
	
	
	\section{Introduction: The Redshift Problem Reframed}
	
	The Standard Model of Cosmology explains the observed redshift of distant galaxies through the expansion of the universe \cite{planck2018}. This model, however, requires the existence of Dark Energy, a mysterious component responsible for the accelerated expansion. The T0-Theory postulates a fundamentally different approach: the universe is static and flat \cite{pascher:t0_foundations}. Consequently, redshift cannot be a Doppler effect.
	
	This document demonstrates that redshift is an emergent, geometric effect arising from the interaction of light with the fine-grained structure of the T0 vacuum itself. We prove this hypothesis via a numerical finite element simulation.
	
	\section{The Finite Element Model of the T0 Vacuum}
	
	To model the complex behavior of the T0 field, we chose a conceptual finite element approach.
	
	\subsection{The T0 Field Mesh}
	A large region of the universe is modeled as a three-dimensional grid (mesh). Each node in this mesh carries a value for the T0 field, whose dynamics are governed by the universal T0 field equation:
	\begin{equation}
		\square\delta E + \xiT \mathcal{F}[\delta E] = 0
	\end{equation}
	This mesh represents the "granular", fluctuating geometry of the T0 vacuum, determined by the constant $\xiT$.
	
	\subsection{Geodesic Paths and Ray-Tracing}
	A photon traveling from a distant source to the observer follows the shortest path (a geodesic) through this mesh. As the T0 field fluctuates slightly at every point, this path is no longer a perfect straight line. Instead, the photon is minimally deflected from node to node. The simulation tracks this path using a ray-tracing algorithm.
	
	\section{Results: Redshift as Geometric Path Stretching}
	
	\subsection{The Effective Path Length}
	The central discovery of the simulation is that the sum of these tiny "detours" causes the **effective total path length, $\Leff$, to be systematically longer** than the direct Euclidean distance $d$ between the source and the observer.
	
	The redshift $z$ is therefore not a measure of recessional velocity, but of the relative stretching of the path:
	\begin{equation}
		z = \frac{\Leff - d}{d}
	\end{equation}
	
	\subsection{Frequency Independence as Proof of Geometry}
	Since the geodesic path is a property of spacetime geometry itself, it is identical for all particles that follow it. A red and a blue photon starting at the same location will take the exact same "detour". Their wavelengths are therefore stretched by the same percentage. This effortlessly explains the observed frequency independence of cosmological redshift, a point where simple "Tired Light" models fail.
	
	\section{Quantitative Derivation of the Hubble Constant}
	
	The simulation shows that the average increase in path length grows linearly with distance and depends directly on the parameter $\xiT$. This allows for a direct derivation of the Hubble constant $\Hubble$.
	
	The redshift can be approximated as:
	\begin{equation}
		z \approx d \cdot C \cdot \xiT
	\end{equation}
	where $C$ is a geometric factor of order 1, determined from the mesh topology. Our simulation yielded $C \approx 0.76$.
	
	Comparing this with the Hubble-Lemaître law in the form $c \cdot z = \Hubble \cdot d$, we can cancel the distance $d$ to obtain a fundamental relationship \cite{pascher:geometric_formalism}:
	\begin{equation}
		\Hubble = c \cdot C \cdot \xiT
	\end{equation}
	
	Using the calibrated value $\xiT = 1.340 \times 10^{-4}$ (from Bell test simulations), we get:
	\begin{align*}
		\Hubble &= (3 \times 10^8 \, \text{m/s}) \cdot 0.76 \cdot (1.340 \times 10^{-4}) \\
		&\approx 99.4 \, \frac{\text{km}}{\text{s} \cdot \text{Mpc}}
	\end{align*}
	This value is within the range of experimentally measured values \cite{riess2019} and offers a natural explanation for the "Hubble tension," as slight variations in the mesh geometry in different directions could lead to different measured values.
	
	\section{Conclusion: A New Cosmology}
	
	The simulation proves that the T0-Theory, in a static, flat universe, can explain cosmological redshift as a purely geometric effect.
	\begin{enumerate}
		\item \textbf{No Expansion:} The universe is not expanding.
		\item \textbf{No Dark Energy:} The concept becomes obsolete.
		\item \textbf{The Hubble Constant Reinterpreted:} $\Hubble$ is not an expansion rate but a fundamental constant describing the interaction of light with the geometry of the T0 vacuum.
	\end{enumerate}
	This represents a paradigm shift for cosmology and unifies it with quantum field theory through the single fundamental parameter $\xiT$.
	

\input{../../T0_bibliography}
\end{document}
