\documentclass[12pt,a4paper]{article}
% Die Preamble liegt drei Verzeichnisse höher (../../../)
\input{../../../T0_preamble_shared_En.tex}

\title{\textbf{Chapter 36: Why Quantum Field Theory (QFT) Did Not Become a Theory of Gravity in Fractal T0 Geometry} \\
	\large Narrative Version of FFGFT}
\author{}
\date{}

\begin{document}
	
	\maketitle
	
	\section*{Why Quantum Field Theory (QFT) Did Not Become a Theory of Gravity in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter explains why standard QFT does not make gravity renormalisable and how the FFGFT solves this through fractal regularisation.
	
	\subsection*{Mathematical Foundation}
	
	QFT is successful for the three non-gravitational forces but fails at quantising gravity due to non-renormalisable divergences. In the FFGFT, gravity is an amplitude deformation, regulated by \(\xi = \frac{4}{3} \times 10^{-4}\). There is no instantaneous action — all changes propagate at the speed of light.
	
	\subsection*{Non-Renormalisability in Standard QFT}
	
	The graviton propagator leads to power-divergent loops:
	
	\begin{equation}
		\delta G \propto G^2 \Lambda^4,
	\end{equation}
	
	with UV cutoff \(\Lambda\). The quartic divergence \(\Lambda^4\) makes the theory non-renormalisable — infinite counterterms are needed.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\delta G] = \si{m^{3}/kg/s^{2}}.
	\end{equation}
	
	\subsection*{Fractal Regularisation in FFGFT}
	
	Gravity as amplitude deformation:
	
	\begin{equation}
		\delta \rho = \xi^2 \cdot \rho_0 \cdot \frac{G m^2}{r^2}.
	\end{equation}
	
	The double \(\xi^2\) damping eliminates UV divergences — the fractal cutoff \(\Lambda \sim 1/(l_0 \xi)\) is soft. Changes in \(\delta \rho\) propagate at light speed — no instantaneous action.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\delta \rho] = \text{dimensionless} \cdot \si{kg^{1/2}/m^{3/2}} \cdot \si{m^{3}/kg/s^{2}} \cdot \si{kg^{2}} / \si{m^{2}}.
	\end{equation}
	
	\subsection*{Vacuum Stiffness as Protection}
	
	The stiffness:
	
	\begin{equation}
		B = \rho_0^2 \xi^{-2} \gg \hbar c / l_P^3.
	\end{equation}
	
	The vacuum is extremely stiff — graviton propagation is suppressed, divergences regularised.
	
	\subsection*{Effective Field Theory}
	
	At energies \(E \ll 1/\xi l_0\):
	
	\begin{equation}
		G_{\text{eff}} = G \cdot (1 + \xi^2 (E l_0)^2).
	\end{equation}
	
	Running coupling, but renormalisable through fractal structure.
	
	\subsection*{Comparison QFT – FFGFT}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard QFT} & \textbf{FFGFT (T0)} \\
			\hline
			Graviton renormalisable? No & Yes, fractal \\
			UV divergences & Soft cutoff \\
			Spin-2 field & Amplitude deformation \\
			Planck scale problematic & Regulated by \(\xi\) \\
			Apparently instantaneous & Light speed \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	Standard QFT fails at gravity because it treats amplitude and phase equally. The FFGFT separates them: Gravity deforms amplitude, strongly damped by \(\xi\). Divergences disappear, the theory is renormalisable — a natural quantum gravity from the fractal Time-Mass Duality. There is no instantaneous action — all processes are causal and at light speed.
	
\end{document}
