\documentclass[12pt,a4paper]{article}
% Die Preamble liegt drei Verzeichnisse höher (../../../)
\input{../../../T0_preamble_shared_En.tex}

\title{\textbf{Chapter 33: Derivation of the Pauli Exclusion Principle in Fractal T0 Geometry} \\
	\large Narrative Version of FFGFT}
\author{}
\\date{January 2025}

\begin{document}
	
	\maketitle
	
	\section*{Derivation of the Pauli Exclusion Principle in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter derives the Pauli principle from the topological structure of the vacuum phase field — without an additional spin postulate.
	
	\subsection*{Mathematical Foundation}
	
	The Pauli principle states that two identical fermions cannot occupy the same quantum state. In the FFGFT, this rule arises inevitably from the impossibility of double windings in the vacuum phase \(\theta(x,t)\), regulated by \(\xi = \frac{4}{3} \times 10^{-4}\).
	
	\subsection*{Topological Winding for Fermions}
	
	Fermions correspond to half-integer phase windings:
	
	\begin{equation}
		\theta_f = \pi + 2\pi n + \delta \theta,
	\end{equation}
	
	with \(n\) integer. The offset \(\pi\) makes the wave function antisymmetric under exchange. The small fractal fluctuation \(\delta \theta \approx \xi \cdot \ln(2)\) slightly breaks exact integrality but remains topologically stable.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\theta_f] = \text{dimensionless}.
	\end{equation}
	
	\subsection*{Energy Barrier for Double Occupancy}
	
	The energy of a winding state is quadratic:
	
	\begin{equation}
		E_n = \frac{1}{2} B (2\pi n)^2.
	\end{equation}
	
	The stiffness \(B = \rho_0^2 \xi^{-2}\) makes double windings (\(n=1\) instead of \(n=1/2 + 1/2\)) more energetic by the factor \(\xi^{-2} \approx 5.6 \times 10^6\) — practically impossible at normal temperatures.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[E_n] = \si{J} \cdot (\text{dimensionless})^2 = \si{J}.
	\end{equation}
	
	\subsection*{Antisymmetry from Phase Parity}
	
	The exchange of two fermions corresponds to phase reversal \(\theta \to -\theta\):
	
	\begin{equation}
		\psi_f(1,2) = -\psi_f(2,1).
	\end{equation}
	
	Antisymmetry follows directly from the topological parity of the phase — no additional postulate required.
	
	\subsection*{Bosons as Integer Windings}
	
	Bosons allow multiple occupancy:
	
	\begin{equation}
		\theta_b = 2\pi n, \quad n = 0, 1, 2, \ldots
	\end{equation}
	
	Integer windings are energetically favourable and symmetric.
	
	\subsection*{Fractal Regularisation of Windings}
	
	On the correlation scale:
	
	\begin{equation}
		E_n \approx B (2\pi n)^2 \cdot (l_0 / \xi)^3.
	\end{equation}
	
	The extended volume scaling \((l_0 / \xi)^3\) further strengthens the barrier against Pauli violation.
	
	\subsection*{Comparison with Standard Model}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard Model} & \textbf{FFGFT (T0)} \\
			\hline
			Pauli as postulate & Topological consequence \\
			Spin as intrinsic property & From half-integer winding \\
			Statistics arbitrary & Geometrically determined \\
			No explanation & Parameter-free from \(\xi\) \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The FFGFT derives the Pauli principle from the topological impossibility of double half-integer windings in the vacuum phase. Fermions are necessarily antisymmetric, bosons symmetric — everything emerges deterministically from the fractal geometry of the Time-Mass Duality with \(\xi\).
	
\end{document}




