\documentclass[12pt,a4paper]{article}

% Die Preamble liegt drei Verzeichnisse höher (../../../)
\input{../../../T0_preamble_shared_En.tex}
\title{\textbf{Chapter 26: Solution to the Baryon Asymmetry in Fractal T0 Geometry} \\
	\large Narrative Version of FFGFT}
\author{}
\date{}

\begin{document}
	
	\maketitle
	
	\section*{Chapter 26: Solution to the Baryon Asymmetry in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter resolves the puzzle of the matter-antimatter asymmetry through the intrinsic asymmetry of the fractal vacuum field.
	
	\subsection*{Mathematical Foundation}
	
	The baryon-to-photon ratio \(\eta_B \approx 6 \times 10^{-10}\) remains unexplained in the Standard Model. In the FFGFT, the asymmetry arises from the asymmetry of the vacuum field \(\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)}\), driven by \(\xi = \frac{4}{3} \times 10^{-4}\).
	

	
	\subsection*{Fractal Vacuum Asymmetry}
	
	The vacuum field is intrinsically asymmetric because phase windings \(n\) for matter (+1) and antimatter (-1) have different energies:
	
	\begin{equation}
		E_n = \frac{1}{2} B (2\pi n + \delta \theta)^2.
	\end{equation}
	
	This equation describes the energy of a topological defect in the vacuum phase field. The stiffness \(B = \rho_0^2 \xi^{-2}\) sets the base energy scale, based on the vacuum density \(\rho_0\) and inversely proportional to \(\xi^2\), since smaller \(\xi\) implies a stiffer structure. The term \((2\pi n + \delta \theta)^2\) represents the quadratic dependence on the total phase shift, where \(2\pi n\) is the integer winding part and \(\delta \theta\) is a small fractal fluctuation that prefers positive windings (+n) because \(\delta \theta > 0\) arises from the intrinsic asymmetry of the fractal hierarchy.
	
	\textbf{Unit check:}
	\begin{equation}
		[E_n] = \si{\joule} \cdot (\text{dimensionless})^2 = \si{\joule}.
	\end{equation}
	
	\subsection*{Baryon Asymmetry from Phase Transition}
	
	In the early universe, the phase transition triggers topological windings:
	
	\begin{equation}
		\eta_B = \xi^3 \cdot \frac{l_0^3}{V_{\text{Hubble}}} \cdot \sin(\delta \theta).
	\end{equation}
	
	This formula quantifies the asymmetry as the product of three factors: \(\xi^3\) represents the triple suppression by the fractal hierarchy (each level damps by \(\xi\)), \(l_0^3 / V_{\text{Hubble}}\) the defect density as the ratio of the fundamental correlation volume to the Hubble volume at the transition time, and \(\sin(\delta \theta)\) the sinusoidal CP bias that encodes the preference for matter over antimatter. The sine arises from the periodic nature of the phase, naturally limiting the asymmetry to small values.
	
	\textbf{Unit check:}
	\begin{equation}
		[\eta_B] = \text{dimensionless} \cdot \si{\meter\cubed} / \si{\meter\cubed} \cdot \text{dimensionless} = \text{dimensionless}.
	\end{equation}
	
	\subsection*{CP Violation through Fractality}
	
	The intrinsic CP bias arises from logarithmic phase shift:
	
	\begin{equation}
		\delta \theta_{\text{CP}} \approx \xi \ln(\xi^{-1}) \approx 10^{-3}.
	\end{equation}
	
	This shift accumulates logarithmically over the infinite fractal levels: the logarithm \(\ln(\xi^{-1})\) effectively counts the number of hierarchy levels (since \(\xi < 1\)), multiplied by \(\xi\) as damping per level, yielding a small but non-vanishing asymmetry — exactly the order of magnitude for the observed CP violation.
	
	\textbf{Unit check:}
	\begin{equation}
		[\delta \theta_{\text{CP}}] = \text{dimensionless}.
	\end{equation}
	
	\subsection*{Non-Equilibrium and Sakharov Conditions}
	
	The transition satisfies the Sakharov conditions: baryon number violation through windings, C/CP through bias, non-equilibrium through rapid fractal collapse.
	
	The resulting value:
	
	\begin{equation}
		\eta_B \approx 6 \times 10^{-10}
	\end{equation}
	
	matches observations precisely, as the combination of \(\xi^3 \approx 10^{-12}\), defect density \(\approx 10^{2}\), and \(\sin(\delta \theta) \approx 10^{-1}\) yields the correct order of magnitude.
	
	\subsection*{Comparison with Other Models}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Other Models} & \textbf{FFGFT (T0)} \\
			\hline
			GUT: Proton decay & Low-energy \\
			Leptogenesis: Heavy neutrinos & Pure phase \\
			Electroweak: Strong transition & Instability from \(\xi\) \\
			Ad-hoc parameters & Parameter-free from \(\xi\) \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The FFGFT resolves the baryon asymmetry through fractal windings, CP bias, and non-equilibrium. \(\eta_B \approx 6 \times 10^{-10}\) is a direct prediction from \(\xi\), a geometric necessity of the Time-Mass Duality.
	
\end{document}