\documentclass[12pt,a4paper]{article}
% Die Preamble liegt drei Verzeichnisse höher (../../../)
\input{../../../T0_preamble_shared_En.tex}

\title{\textbf{Chapter 37: Intrinsic Properties of the Vacuum Field in Fractal T0 Geometry} \\
	\large Narrative Version of FFGFT}
\author{}
\\date{1 January 2025}

\begin{document}
	
	\maketitle
	
	\section*{Intrinsic Properties of the Vacuum Field in Fractal T0 Geometry}
	
	\subsection*{Brief Introduction}
	
	This chapter describes the fundamental properties of the vacuum field \(\Phi = \rho e^{i\theta}\) as a fractal, nonlinear medium.
	
	\subsection*{Mathematical Foundation}
	
	The vacuum is not empty but a dynamic field with intrinsic stiffness and non-locality, regulated by \(\xi = \frac{4}{3} \times 10^{-4}\). There is no instantaneous action — all processes are causal.
	
	\subsection*{Amplitude-Phase Separation}
	
	The vacuum field separates into:
	
	\begin{equation}
		\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)}.
	\end{equation}
	
	Amplitude \(\rho\) carries bound states and gravity, phase \(\theta\) free propagation and quantum effects. The separation is fundamental — no wave-particle duality.
	
	\textbf{Unit check:}
	
	\begin{equation}
		[\Phi] = \si{kg^{1/2}/m^{3/2}}.
	\end{equation}
	
	\subsection*{Vacuum Stiffness}
	
	The stiffness against amplitude deformation:
	
	\begin{equation}
		B = \rho_0^2 \xi^{-2}.
	\end{equation}
	
	The factor \(\xi^{-2}\) makes the vacuum extremely stiff — explains gravitational weakness.
	
	\subsection*{Fractal Non-Locality}
	
	Phase correlation:
	
	\begin{equation}
		C(\Delta x) = \xi \ln(|\Delta x|/l_0) + \frac{\xi^2}{2} [\ln(|\Delta x|/l_0)]^2.
	\end{equation}
	
	Logarithmic coherence over scales — global correlations without instantaneous transmission.
	
	\subsection*{Fluctuations}
	
	Typical fluctuations:
	
	\begin{equation}
		\delta \theta \approx \sqrt{\xi \ln(\Delta x / l_0)}, \quad \delta \rho / \rho_0 \approx \xi^2.
	\end{equation}
	
	Phase fluctuates logarithmically, amplitude strongly damped.
	
	\subsection*{Comparison with Standard Vacuum}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard QFT} & \textbf{FFGFT (T0)} \\
			\hline
			Empty vacuum & Dynamic field \\
			Zero-point divergences & Fractal regulated \\
			Ad-hoc cutoff & Natural from \(\xi\) \\
			No geometry & Fractal structured \\
		\end{tabular}
	\end{center}
	
	\subsection*{Conclusion}
	
	The vacuum in the FFGFT is a fractal, complex field with separated amplitude and phase. Stiffness explains gravity, non-locality quantum phenomena — everything deterministic and causal from \(\xi\). No instantaneity, only global coherence.
	
\end{document}




