\maketitle
	
	\section{Chapter 21: Ron Folman's T³ Quantum Gravity Experiment in Fractal T0-Geometry}
	
	The T³ experiment ("T-cubed", Ron Folman et al., 2021–2025) shows in high-precision atom interferometry a gravitational phase shift \(\Delta \phi \propto g T^3\), which deviates from the classical expectation \(T^2\). In the fractal Dynamic Vacuum Field Theory (DVFT) with T0-Time-Mass Duality, this explains a direct measurement of the fractal vacuum phase curvature, derived from the single fundamental parameter \(\xi = \frac{4}{3} \times 10^{-4}\) (dimensionless).
	
	\subsection{Symbol Directory and Units}
	
	\begin{tcolorbox}[title={\textbf{Important Symbols and their Units}}, colback=blue!5!white, colframe=blue!75!black]
		\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.35\textwidth}}
			\textbf{Symbol} & \textbf{Meaning} & \textbf{Unit (SI)} \\
			\hline
			\(\xi\) & Fractal scale parameter & dimensionless \\
			\(\Delta \phi\) & Gravitational phase shift & dimensionless (radian) \\
			\(g\) & Gravitational acceleration & \si{\meter\per\second\squared} \\
			\(T\) & Interferometer time (separation time) & \si{\second} \\
			\(m\) & Atomic mass & \si{\kilo\gram} \\
			\(\hbar\) & Reduced Planck constant & \si{\joule\second} \\
			\(\Delta z\) & Vertical path separation & \si{\meter} \\
			\(\partial_i \theta\) & Gradient of vacuum phase & \si{\per\meter} \\
			\(\theta(z)\) & Vacuum phase at position z & dimensionless (radian) \\
			\(\partial_z \theta\) & Partial derivative of phase with respect to z & \si{\per\meter} \\
			\(\partial_z^2 \theta\) & Second derivative of phase with respect to z & \si{\per\meter\squared} \\
			\(a_\xi\) & Fractal correction constant & dimensionless \\
			\(\mathcal{F}(X)\) & Fractal function correction & dimensionless \\
		\end{tabular}
	\end{tcolorbox}
	
	\textbf{Unit Check (classical phase shift):}
	\begin{align*}
		[\Delta \phi_{\text{class}}] &= \si{\kilo\gram} \cdot \si{\meter\per\second\squared} \cdot \si{\meter} \cdot \si{\second} / \si{\joule\second} = \text{dimensionless (radian)}
	\end{align*}
	Units consistent.
	
	\subsection{The T³ Experiment – Precise Description}
	
	In standard atom interferometry (light-pulse Ramsey-Bordé), a \(\pi/2\)-pulse splits the wave packet, gravitation shifts the paths by \(\Delta z = \frac{1}{2} g T^2\), and a second pulse recombines. The phase is:
	\begin{equation}
		\Delta \phi_{\text{class}} = \frac{m g \Delta z T}{\hbar} = \frac{m g^2 T^3}{2\hbar}
	\end{equation}
	
	However, a deviation is observed that effectively yields \(\Delta \phi \propto T^3\) when the full wave packet dynamics is considered (based on results from 2021–2025).
	
	\textbf{Unit Check:}
	\begin{align*}
		\left[\frac{m g^2 T^3}{\hbar}\right] &= \si{\kilo\gram} \cdot (\si{\meter\per\second\squared})^2 \cdot \si{\second^3} / \si{\joule\second} = \text{dimensionless}
	\end{align*}
	
	\subsection{Detailed Derivation in T0}
	
	In T0, gravitation is a gradient of the vacuum phase:
	\begin{equation}
		g_i = -\xi \cdot \partial_i \theta
	\end{equation}
	
	The phase of an atom along a worldline \(x^i(t)\) accumulates:
	\begin{equation}
		\phi(t) = \int_0^t \theta(x^i(t')) \, dt'
	\end{equation}
	
	For two paths with vertical separation \(\Delta z(t) = \frac{1}{2} g t^2\):
	\begin{equation}
		\Delta \phi = \int_0^T \left[ \theta(z + \Delta z(t')) - \theta(z) \right] dt'
	\end{equation}
	
	Taylor expansion of the phase:
	\begin{equation}
		\theta(z + \Delta z) = \theta(z) + (\partial_z \theta) \Delta z + \frac{1}{2} (\partial_z^2 \theta) (\Delta z)^2 + \mathcal{O}((\Delta z)^3)
	\end{equation}
	
	Inserting \(\Delta z(t) = \frac{1}{2} g t^2\):
	\begin{align}
		\Delta \phi &= \int_0^T \left[ (\partial_z \theta) \cdot \frac{1}{2} g t^2 + \frac{1}{2} (\partial_z^2 \theta) \left(\frac{1}{2} g t^2\right)^2 + \mathcal{O}(t^6) \right] dt' \nonumber \\
		&= (\partial_z \theta) \cdot \frac{1}{2} g \frac{T^3}{3} + \frac{1}{2} (\partial_z^2 \theta) \cdot \frac{1}{4} g^2 \frac{T^5}{5} + \mathcal{O}(T^7) \nonumber \\
		&= \xi g \frac{T^3}{6} + \xi^2 \cdot \frac{g^2 T^5}{40} \cdot (\partial_z^2 \theta) + \mathcal{O}(T^7)
	\end{align}
	
	The leading term is \(\Delta \phi \propto T^3\), with coefficient \(\xi g / 6\) (adjusted for fractal normalization).
	
	\subsection{Higher Corrections and Testability}
	
	Nonlinearities in the fractal function \(\mathcal{F}(X)\) generate higher terms:
	\begin{equation}
		\Delta \phi = \xi \frac{g T^3}{6} + \xi^{3/2} \frac{g^2 T^5}{40} \cdot a_\xi + \xi^2 \frac{g^3 T^7}{336} + \cdots
	\end{equation}
	
	Future experiments with longer \(T\) can measure these corrections and directly determine \(\xi\).
	
	\subsection{Comparison with Standard Quantum Mechanics + GR}
	
	Standard QM+GR expects pure \(T^3\) only under special conditions (full wave packet overlap). T0 predicts \(T^3\) as a fundamental consequence of the vacuum phase, independent of pulse timing.
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Standard QM + GR} & \textbf{T0-Fractal DVFT} \\
			\hline
			\(\Delta \phi \propto T^2\) (classical) & \(\Delta \phi \propto T^3\) (fractal) \\
			Wave packet effects ad-hoc & Structural phase curvature \\
			No intrinsic scale & \(\xi\) sets coefficient \\
			No higher terms & Predictable \(\xi^{3/2} T^5\)-correction \\
		\end{tabular}
	\end{center}
	
	\subsection{Conclusion}
	
	The T³ experiment is a direct measurement of the fractal vacuum phase curvature in T0-theory. The \(T^3\)-scaling is not a coincidence, but proof of the Time-Mass Duality with \(\xi = \frac{4}{3} \times 10^{-4}\). Precise future measurements can calibrate \(\xi\) and test the theory, while deviations from the standard expectation confirm T0.
	
	This interpretation reduces the experiment to an elegant consequence of the dynamic fractal spacetime structure.
