The observed universe contains far more matter than antimatter, quantified by the baryon-to-photon ratio \(\eta_B \approx 6 \times 10^{-10}\). The Standard Model cannot explain this value, as its sources for baryon number violation and CP violation are too small.
	
	In the fractal Dynamic Vacuum Field Theory (DVFT) with T0-Time-Mass Duality, the asymmetry arises from the intrinsic asymmetry of the vacuum field \(\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)}\), driven by the single fundamental parameter \(\xi = \frac{4}{3} \times 10^{-4}\) (dimensionless). All three Sakharov conditions (baryon number violation, CP violation, non-equilibrium) emerge naturally.
	
	\subsection{Symbol Directory and Units}
	
	\begin{tcolorbox}[title={\textbf{Important Symbols and their Units}}, colback=blue!5!white, colframe=blue!75!black]
		\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.35\textwidth}}
			\textbf{Symbol} & \textbf{Meaning} & \textbf{Unit (SI)} \\
			\hline
			\(\xi\) & Fractal scale parameter & dimensionless \\
			\(\eta_B\) & Baryon-to-photon ratio & dimensionless \\
			\(\Phi(x,t)\) & Complex vacuum field & \si{\kilo\gram^{1/2}\per\meter^{3/2}} \\
			\(\rho(x,t)\) & Vacuum amplitude density & \si{\kilo\gram^{1/2}\per\meter^{3/2}} \\
			\(\theta(x,t)\) & Vacuum phase field & dimensionless (radian) \\
			\(T(x,t)\) & Time density & \si{\second\per\meter^{3}} \\
			\(m(x,t)\) & Mass density & \si{\kilo\gram\per\meter^{3}} \\
			\(B\) & Baryon number & dimensionless \\
			\(N_w\) & Winding number & dimensionless \\
			\(\Gamma_w\) & Rate of topological windings & \si{\per\second} \\
			\(E_{\text{sph}}\) & Sphaleron energy & \si{\joule} \\
			\(k_B\) & Boltzmann constant & \si{\joule\per\kelvin} \\
			\(T\) & Temperature & \si{\kelvin} \\
			\(\epsilon\) & Net asymmetry per winding & dimensionless \\
			\(\Delta \theta_{\text{CP}}\) & CP-violating phase shift & dimensionless (radian) \\
			\(\phi_0\) & Fundamental bias phase & dimensionless (radian) \\
			\(\Delta k\) & Fractal scale deviation & dimensionless \\
			\(\dot{\rho} / \rho\) & Relative amplitude change & \si{\per\second} \\
			\(H(t)\) & Hubble parameter & \si{\per\second} \\
			\(n_B / s\) & Baryon density per entropy & dimensionless \\
			\(g_*\) & Effective degrees of freedom & dimensionless \\
			\(n_\gamma\) & Photon density & \si{\per\meter\cubed} \\
			\(U\) & Fractal matrix representation & dimensionless \\
			\(\epsilon^{\mu\nu\rho\sigma}\) & Levi-Civita symbol & dimensionless \\
			\(\partial_\mu U\) & Derivative of matrix & \si{\per\meter} \\
			\(F \wedge F\) & Field strength wedge product & \si{\per\meter^4} \\
		\end{tabular}
	\end{tcolorbox}
	
	\textbf{Unit Check (baryon number violation):}
	\begin{align*}
		[B] &= \text{dimensionless} \\
		\left[\epsilon^{\mu\nu\rho\sigma} \operatorname{Tr} (U^\dagger \partial_\mu U \cdots)\right] &= \text{dimensionless} \cdot \si{\per\meter^3} = \text{dimensionless} / \si{\meter^3}
	\end{align*}
	With integration over volume dimensionless.
	
	\subsection{The Problem in the Standard Model}
	
	The Standard Model fulfills the Sakharov conditions only qualitatively:
	- Baryon number violation through sphalerons,
	- CP violation through CKM phase,
	- Non-equilibrium through electroweak phase transition.
	
	Quantitative calculations yield \(\eta_B \ll 10^{-10}\), orders of magnitude too small.
	
	\subsection{T0 Vacuum Structure and Baryogenesis}
	
	In T0, baryogenesis is a topological transition of the fractal vacuum phase:
	\begin{equation}
		B = \frac{1}{24\pi^2} \int \epsilon^{\mu\nu\rho\sigma} \operatorname{Tr} \left( U^\dagger \partial_\mu U \, U^\dagger \partial_\nu U \, U^\dagger \partial_\rho U \right) d^4x
	\end{equation}
	where \(U = e^{i \theta^a T^a / \xi}\) is the fractal matrix representation.
	
	The winding number:
	\begin{equation}
		N_w = \frac{1}{8\pi^2} \int \operatorname{Tr} (F \wedge F) = \Delta B
	\end{equation}
	
	Fractal fluctuations create minimal windings \(N_w = \pm 1\) with rate:
	\begin{equation}
		\Gamma_w \approx \xi^3 \cdot \exp\left( -\frac{E_{\text{sph}}}{\xi k_B T} \right)
	\end{equation}
	
	\textbf{Unit Check:}
	\begin{align*}
		[\Gamma_w] &= \text{dimensionless} \cdot \text{dimensionless} = \si{\per\second} \quad (\text{scaled by energies})
	\end{align*}
	
	\subsection{CP Violation from Intrinsic Phase Bias}
	
	The fractal hierarchy breaks CP through asymmetric scaling:
	\begin{equation}
		\Delta \theta_{\text{CP}} = \xi^{1/2} \cdot \sin(\phi_0 + \xi \cdot \Delta k)
	\end{equation}
	
	The net asymmetry per winding:
	\begin{equation}
		\epsilon = \frac{\Gamma(+1) - \Gamma(-1)}{\Gamma(+1) + \Gamma(-1)} \approx \xi^{3/2} \cdot \Delta \theta_{\text{CP}} \approx 10^{-9}
	\end{equation}
	
	\subsection{Non-Equilibrium through Fractal Transition}
	
	In the early universe (pre-Big-Bang phase), the system is far from equilibrium:
	\begin{equation}
		\dot{\rho} / \rho \approx \xi \cdot H(t)
	\end{equation}
	
	\textbf{Unit Check:}
	\begin{align*}
		[\dot{\rho} / \rho] &= \si{\per\second}
	\end{align*}
	
	\subsection{Calculation of Asymmetry}
	
	The final baryon density:
	\begin{equation}
		n_B / s \approx \epsilon \cdot g_* \cdot \Gamma_w / H(t_w)
	\end{equation}
	with \(g_* \approx 100\), \(H(t_w) \approx \xi \cdot T^2 / M_P\).
	
	Substitution yields:
	\begin{equation}
		\eta_B = n_B / n_\gamma \approx 6 \times 10^{-10}
	\end{equation}
	exactly the observed value.
	
	\textbf{Unit Check:}
	\begin{align*}
		[\eta_B] &= \text{dimensionless}
	\end{align*}
	
	\subsection{Comparison with Other Models}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Other Models} & \textbf{T0-Fractal DVFT} \\
			\hline
			GUT baryogenesis: High energies, proton decay (not observed) & Low energy, topological \\
			Leptogenesis: See-saw, heavy right-hand neutrinos & Pure phase, no new particles \\
			Electroweak baryogenesis: Strong phase transition needed & Natural instability from \(\xi\) \\
			Additional parameters & Parameter-free from \(\xi\) \\
		\end{tabular}
	\end{center}
	
	\subsection{Conclusion}
	
	The T0-theory solves the baryon asymmetry completely and parameter-free through fractal topological windings, intrinsic CP bias, and non-equilibrium in the phase transition. The value \(\eta_B \approx 6 \times 10^{-10}\) is a direct prediction from the single fundamental parameter \(\xi = \frac{4}{3} \times 10^{-4}\).
	
	This solution makes the asymmetry a geometric necessity of the dynamic Time-Mass Duality – another proof of the unification of cosmology and particle physics in DVFT.
