\maketitle
	
	\section{Chapter 29: The Delayed-Choice Quantum Eraser Experiment in Fractal T0-Geometry}
	
	The **Delayed-Choice Quantum Eraser (DCQE)** experiment (Kim et al., 2000; Walborn et al., 2002) vividly demonstrates quantum complementarity and entanglement. It appears to imply retrocausality: A delayed decision to erase or retain which-path information seemingly influences the interference behavior of a photon in the past. In the fractal **Dynamic Vacuum Field Theory (DVFT)** with **T0-Time-Mass Duality**, this paradox completely resolves. The phenomenon emerges from the global, fractal coherence of the vacuum phase field \(\theta(x,t)\), regulated by the single fundamental parameter \(\xi = \frac{4}{3} \times 10^{-4}\) (dimensionless). There is no retrocausality – merely a nonlocal but causal correlation in the fractal vacuum structure.
	
	In T0, quantum states are excitations of the complex vacuum field \(\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)}\). Photons are pure phase vortices (\(\delta\rho \approx 0\)), whose propagation is guided by gradients of time density \(T(x,t)\) (duality \(T(x,t) \cdot m(x,t) = 1\)). Entanglement is global phase coherence: \(\theta_{\text{signal}} + \theta_{\text{idler}} = \theta_{\text{total}} =\) const.
	
	\subsection{Symbol Directory and Units}
	
	\begin{tcolorbox}[title={\textbf{Important Symbols and their Units}}, colback=blue!5!white, colframe=blue!75!black]
		\begin{tabular}{p{0.3\textwidth}p{0.3\textwidth}p{0.35\textwidth}}
			\textbf{Symbol} & \textbf{Meaning} & \textbf{Unit (SI)} \\
			\hline
			\(\xi\) & Fractal scale parameter & dimensionless \\
			\(\Phi(x,t)\) & Complex vacuum field & \si{\kilo\gram^{1/2}\per\meter^{3/2}} \\
			\(\rho(x,t)\) & Vacuum amplitude density & \si{\kilo\gram^{1/2}\per\meter^{3/2}} \\
			\(\theta(x,t)\) & Vacuum phase field & \si{\radian} (dimensionless) \\
			\(T(x,t)\) & Time density & \si{\second\per\meter^3} \\
			\(\psi(x,t)\) & Effective wave function & dimensionless \\
			\(\Delta\theta\) & Phase perturbation & \si{\radian} \\
			\(l_0\) & Fractal correlation length & \si{\meter} \\
			\(\theta_{\text{total}}\) & Global entangled phase & \si{\radian} \\
			\(\langle \theta(x) \theta(x') \rangle\) & Phase correlation & \si{\radian^2} \\
			\(V\) & Visibility of interference & dimensionless \\
		\end{tabular}
	\end{tcolorbox}
	
	\textbf{Unit check (phase correlation):}
	\begin{align*}
		[\langle \theta \theta \rangle] &= \text{dimensionless} + \text{dimensionless} \cdot \ln(\si{\meter}/\si{\meter}) = \text{dimensionless}
	\end{align*}
	Units are consistent.
	
	\subsection{The Problem of Apparent Retrocausality}
	
	In the standard model of quantum mechanics, DCQE appears paradoxical: The total distribution at signal detector D0 never shows interference. Only with post-selection (correlation with idler detectors) do subsets with interference (erased) or clumping (which-path) occur – even if the idler measurement is delayed.
	
	This leads to misunderstandings about retrocausality. T0 resolves this parameter-free through fractal nonlocality.
	
	\subsection{Description of the Experiment}
	
	Entangled photon pairs from parametric down-conversion (PDC):
	- Signal photon → double slit → detector D0 (movable for scanning).
	- Idler photon → delayed setup with beam splitters and detectors (D1–D4).
	
	Without erasure (which-path detectors): No interference in correlated subsets.  
	With erasure (e.g., beam splitter before detectors): Interference in subsets – delayed choice only classifies the data.
	
	\subsection{Phase Coherence in the T0 Vacuum Structure}
	
	The effective wave function is a phase modulation:
	\begin{equation}
		\psi(x,t) = e^{i \theta(x,t)/\xi},
	\end{equation}
	since photons are pure phase (\(\rho \approx \rho_0\)).
	
	Fractal correlation:
	\begin{equation}
		\langle \theta(x) \theta(x') \rangle = \theta_0 + \xi \cdot \ln(|x - x'| / l_0).
	\end{equation}
	
	\textbf{Unit check:}
	\begin{align*}
		[\xi \cdot \ln(|x-x'|/l_0)] &= \text{dimensionless}
	\end{align*}
	
	For entangled pairs:
	\begin{equation}
		\theta_{\text{signal}}(x) + \theta_{\text{idler}}(x') = \theta_{\text{total}} = \text{constant}.
	\end{equation}
	
	\subsection{Derivation of the Erasure Effect}
	
	Which-path marking disturbs the idler phase:
	\begin{equation}
		\Delta \theta_{\text{idler}} \approx \pi \quad \Rightarrow \quad \Delta \theta_{\text{signal}} \approx \pi \quad (\text{through duality}),
	\end{equation}
	randomizes the phase at D0 → reduced visibility \(V \approx 0\).
	
	Erasure (e.g., 50/50 beam splitter):
	\begin{equation}
		\Delta \theta_{\text{idler}} \approx 0 \quad \Rightarrow \quad \Delta \theta_{\text{signal}} \approx 0,
	\end{equation}
	coherence maintained → \(V \approx 1\) in correlated subsets.
	
	The "delayed choice" only affects post-selection of events – the global phase \(\theta_{\text{total}}\) is always coherent.
	
	Minimal phase uncertainty from fractality:
	\begin{equation}
		\Delta \theta_{\min} \approx \xi^{3/2} \sqrt{\ln(\xi^{-1})} \approx 4.6 \times 10^{-6}.
	\end{equation}
	
	\subsection{Nonlocal Correlation Without Retrocausality}
	
	The correlation is fractally conditioned:
	\begin{equation}
		\Delta \theta_{\text{signal}} \cdot \Delta \theta_{\text{idler}} \geq \xi.
	\end{equation}
	
	This is deterministic and causal – no signal transmission backwards.
	
	\subsection{Comparison with Other Interpretations}
	
	\begin{center}
		\begin{tabular}{p{0.45\textwidth}p{0.45\textwidth}}
			\textbf{Other Interpretations} & \textbf{T0-Fractal DVFT} \\
			\hline
			Copenhagen: Collapse, observer & Deterministic, vacuum-geometric \\
			Many-Worlds: Branching & Unified fractal phase \\
			Retrocausality models: Time travel & No retrocausality needed \\
			Additional assumptions & Parameter-free from \(\xi\) \\
		\end{tabular}
	\end{center}
	
	\subsection{Conclusion}
	
	The DCQE experiment is no longer a paradox in T0-theory: The apparent retrocausality arises from the global, fractal coherence of the vacuum phase field \(\theta(x,t)\). Erasure restores coherence in correlated subsets without changing the past event – merely the classification of data. Everything emerges parameter-free from the single scale parameter \(\xi = \frac{4}{3} \times 10^{-4}\), and unifies quantum entanglement with Time-Mass Duality as a geometric necessity of the dynamic vacuum.
