% Chapter 09: Cosmology, Redshift and CMB
% Corrected: E_H = E0 * xi^(41/4) as Hubble energy
% H0 is SI convention, E_H is the physical quantity

\chapter{Cosmology, Redshift and CMB in Time-Mass Duality}

\section{Introduction}

In the preceding chapters, the microscopic side of time-mass duality was the 
focus: masses, couplings, and quantum phenomena. This chapter shows how the 
same structure affects large-scale cosmological phenomena: redshift, cosmic 
microwave background radiation, and effective quantities such as the Hubble scale.

The key point is: the same parameter $\xipar = \frac{4}{3} \times 10^{-4}$ 
that determines masses and couplings at the particle level also determines 
the cosmological redshift. There is no transition to a different effective 
parameter at large scales -- in a homogeneous, static universe, the same 
$\xipar$ applies everywhere.

\section{Redshift Without Expanding Space}

\subsection{Standard Interpretation}

Standard cosmology interprets the cosmological redshift primarily as a 
consequence of expanding spacetime. A photon's wavelength is stretched 
with the cosmic scale factor $a(t)$:

\begin{equation}
\frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}} = \frac{a(t_{\text{obs}})}{a(t_{\text{emit}})} = 1 + z
\end{equation}

\subsection{Time-Mass Duality Interpretation}

Within the framework of time-mass duality, the observed redshift is 
understood as a consequence of the fractal deep structure of spacetime. A 
photon propagating through the fractal space with $D_f = 3 - \xipar$ 
continuously loses energy to the dynamic vacuum field.

The T0 redshift:

\begin{equation}
z_{\text{T0}} = \int_0^d \xipar(r) \frac{E_\gamma(r)}{E_{\gamma,0}} dr
\end{equation}

For a homogeneous $\xipar$ field, this simplifies to:

\begin{equation}
\boxed{z_{\text{T0}} \approx \xipar \cdot d}
\label{eq:z_T0_linear}
\end{equation}

where $d$ is the distance in megaparsecs. This linear relation is the 
T0 version of the Hubble law.

\section{The Hubble Parameter and the Hubble Energy}

\subsection{$H_0$ as an SI Convention}

$H_0$ is quoted in km/s/Mpc. Substituting 
1~Mpc~$= 3.26 \times 10^6$~ly~$= 3.08 \times 10^{22}$~m, 
metres cancel and a pure frequency remains:

\begin{equation}
H_0 = 67.4\,\text{km/s/Mpc} = 2.18 \times 10^{-18}\,\text{s}^{-1}
\end{equation}

The three representations km/s/Mpc, km/s/ly and s$^{-1}$ are 
\emph{the same thing} -- just different SI units for the same 
ratio (distance or frequency).

\subsection{The Hubble Energy $E_H$ -- a New Quantity}

Multiplying a frequency by $\hbar$ yields an energy 
($E = \hbar\nu$, Planck/Einstein). For $H_0$ we define:

\begin{align}
\text{SI} \to \text{nat.:} \quad & E_H = \hbar \cdot H_0 
\quad\text{(multiply by $\hbar$)} \\
\text{nat.} \to \text{SI:} \quad & H_0 = E_H / \hbar
\quad\text{(divide by $\hbar$)}
\end{align}

$E_H$ is \emph{no longer $H_0$} (frequency) but an energy. 
In natural units ($\hbar = 1$), $E_H$ and $H_0$ are 
numerically identical.

\subsection{T0 Prediction for $E_H$}

T0 theory computes $E_H$ from the fundamental parameters 
$\xipar$ and $E_0$:

\begin{equation}
\boxed{E_H = E_0 \cdot \xipar^{41/4} = 7.398\,\text{MeV} \cdot \xipar^{10.25} = 1.41 \times 10^{-33}\,\text{eV}}
\label{eq:E_H_T0}
\end{equation}

Back-conversion to SI ($H_0 = E_H / \hbar$):

\begin{equation}
H_0^{\text{T0}} = \frac{E_H}{\hbar} = 2.14 \times 10^{-18}\,\text{s}^{-1} = 66.2\,\text{km/s/Mpc}
\end{equation}

\subsection{Comparison with Measurements}

\begin{center}
\begin{tabular}{lrr}
\toprule
Measurement & $H_0$ [km/s/Mpc] & $E_H$ [eV] \\
\midrule
Planck 2018 & $67.4 \pm 0.5$ & $1.44 \times 10^{-33}$ \\
SH0ES 2022 & $73.0 \pm 1.0$ & $1.56 \times 10^{-33}$ \\
T0 ($E_0 \cdot \xipar^{41/4}$) & $66.2$ & $1.41 \times 10^{-33}$ \\
\bottomrule
\end{tabular}
\end{center}

The deviation from the Planck value is $-1.9\%$. The exponent $41/4$ 
requires physical justification from $\xipar$ field theory.

\begin{remark}[Model dependence of the experimental $H_0$]
	The ``experimental'' value $H_0 \approx 70\,$km/s/Mpc is not a 
	model-independent measurement. It is extracted from raw data (redshifts 
	and luminosities of standard candles) under the assumption of an expanding 
	Friedmann universe. In particular:
	\begin{itemize}
	\item The luminosity distance $d_L = d \cdot (1+z)$ presupposes a 
	cosmic scale factor that does not exist in T0.
	\item In T0, the physical distance $d$ is directly measurable, without 
	$(1+z)$ correction.
	\item The model-independent observation is the linear relation 
	$z \propto d$ for small $z$. Its proportionality factor is interpreted 
	differently in different cosmological models.
	\end{itemize}
\end{remark}

\section{CMB Temperature}

The CMB temperature:

\begin{equation}
T_{\text{CMB}} = 2.7255\,\text{K}
\end{equation}

is interpreted in T0 theory as a thermodynamic equilibrium state of the 
$\xipar$ geometry, not as a relic of a Big Bang. The dynamic vacuum field 
$\Phi = \rho e^{i\theta}$ has an intrinsic phase evolution $\dot{\theta} = m 
= 1/T$ (from time-mass duality). The CMB radiation is the thermal equilibrium 
spectrum of this universal vacuum field, whose temperature is determined by the 
geometric parameters $\xipar$ and $f = 7500$.

\section{Static Universe in the 4D Torus}

T0 theory describes a static universe without global expansion. Spacetime 
has the topology $\mathbb{R}^3 \times S^1$, where $S^1$ is the phase 
direction of the vacuum field (not ``time'' in the classical sense, since 
$T \cdot m = 1$ defines time as the inverse of mass).

The universe is ``infinite'' not in the sense of infinite extent, but because 
the torus is closed upon itself -- there is no boundary and no edge. In this 
view:

\begin{itemize}
\item Redshift arises from energy loss in the fractal vacuum field, not from 
expansion
\item The Hubble relation $z = \xipar \cdot d$ is a direct consequence of the 
fractal dimension $D_f = 3 - \xipar$
\item Dark energy is not a separate substance but manifests as an effective 
property of the dynamic vacuum field $\Phi$
\item Large-scale homogeneity follows from the topology of the torus, without 
inflation
\end{itemize}

JWST observations of evolved galaxies at $z > 10$, which appear unexpectedly 
early in the Standard Model, are natural in the T0 picture since the 
development time is unlimited.

\section{Summary}

The cosmological predictions of T0 theory follow directly from $\xipar$:

\begin{itemize}
\item Redshift: $z = \xipar \cdot d$ (energy loss in the vacuum field)
\item Hubble energy: $E_H = E_0 \cdot \xipar^{41/4} = 1.41 \times 10^{-33}\,$eV 
($-1.9\%$ vs Planck)
\item Back-conversion: $H_0 = E_H / \hbar = 66.2\,$km/s/Mpc
\item CMB as equilibrium state of the vacu