% DVFT Chapter 38: Kapitel 38
% Generated from Markdown
% Date: 2025-12-28

\documentclass[12pt,a4paper]{article}

% Include the shared T0 preamble
\input{../../../T0_preamble_shared_De.tex}

\begin{document}

\title{Kapitel 38}
\author{Dynamic Vacuum Field Theory}
\date{2025}
\maketitle


BLACK HOLE AND QUANTUM SINGULARITIES
1. Introduction
This document presents a full, rigorous DVFT (Dynamic vacuum field Curvature Theory) explanation of
why *both* classical gravitational singularities (black holes) and quantum singularities (point particles,
infinite self-energy) cannot exist.
In DVFT, spacetime curvature and inertia emerge from the vacuum amplitude field:
\Phi(x,t) = \rho(x,t) e^{i\theta(x,t)},
with:
• \rho(x,t) – vacuum amplitude (determines inertia and gravitational potential),
• \theta(x,t) – phase field (determines quantum coherence and wave-like behavior).
Gravity emerges from amplitude gradients:
g = −\nabla\rho.
Singularities require \rho \to \infty or \nabla\rho \to \infty. DVFT forbids both because the vacuum has finite stiffness and
inertial density, encoded in the potential U(\rho).
2. Why Singularities Cannot Exist in DVFT: The Vacuum Potential U(\rho)
DVFT postulates the vacuum has a microphysical potential:
U(\rho) = Λ$_0$ + (κ/2)(\rho − \rho$_0$)$^2$ + (\lambda/4)(\rho − \rho$_0$)⁴ + …
where:
• \rho$_0$ is the equilibrium vacuum amplitude,
• κ is the elastic stiffness of the vacuum,
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 84
• \lambda stabilizes large deviations of \rho.
This potential is strongly convex at large |\rho − \rho$_0$|.
Thus, any attempt to compress the vacuum amplitude beyond moderate values requires infinite energy:
U(\rho) \to \infty as |\rho − \rho$_0$| \to \infty.
Therefore:
• \rho cannot diverge,
• \nabla\rho cannot diverge,
• gravitational curvature cannot diverge.
This single microphysical fact eliminates *all* singularities in DVFT.
3. Removal of Quantum Singularities (Electron, Proton, Point Particles)
Quantum field theory treats electrons and quarks as point particles, leading to:
• infinite self-energy,
• divergent Coulomb self-field,
• undefined gravitational field at $r = 0$.
DVFT replaces a point mass with a finite vacuum amplitude deformation:
\delta\rho(x) = G m \int d$^3$x' |ψ(x')|$^2$ / |x − x'|.
This deformation is always finite because:
• |ψ(x)|$^2$ is normalizable,
• convolution with 1/r smooths the field,
• U(\rho) prevents amplitude blow-up.
As a result:
• no particle has infinite self-energy,
• no wavefunction produces a singular potential,
• gravity is well-defined even in superposition.
Thus quantum singularities are eliminated by vacuum microphysics, not by renormalization.
4. Gravitational Field of a Delocalized Electron
An electron with wavefunction ψ(x,t) generates a vacuum amplitude profile:
\rho(x,t) = \rho$_0$ + G m_e \int d$^3$x' |ψ(x',t)|$^2$ / |x − x'|.
When ψ(x,t) spreads due to quantum dispersion, the gravitational field spreads with it:
g(x,t) = −\nabla\rho(x,t).
This ensures:
• gravity is fully compatible with Heisenberg uncertainty,
• gravitational fields have finite width,
• no r \to 0 divergence occurs.
DVFT therefore produces the first consistent microscopic definition of gravity for a single quantum
particle.
5. Removal of Black Hole Singularities
In classical GR, gravitational collapse leads to infinite curvature at $r = 0$.
In DVFT, as matter compresses and raises \rho(x), the vacuum potential U(\rho) rapidly increases. At
sufficiently high density, a phase transition in the vacuum occurs:
• \rho stops increasing (vacuum stiffness prevents divergence),
• \theta becomes phase-locked (coherence inside horizon),
• matter transitions into a high-amplitude vacuum phase state,
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 85
• gravitational field saturates.
Thus the black hole interior is NOT a singularity. It is a region of:
• finite \rho,
• finite \nabla\rho,
• finite energy density,
• vacuum-phase condensate.
The event horizon may still exist, but the spacetime interior remains regular.
6. DVFT Black Hole Interior Structure
DVFT predicts that inside a black hole:
• \rho(r) rises toward a maximum allowed value \rho_max,
• U(\rho) prevents further growth beyond \rho_max,
• curvature saturates,
• matter becomes vacuum-amplitude dominated,
• \theta freezes (phase coherence becomes rigid),
• no divergence in metric-equivalent quantities occurs.
This resembles:
• gravastar-like interiors,
• vacuum condensate cores,
• nonsingular loop quantum gravity solutions,
• but derived *entirely from DVFT microphysics*.
7. The Deep Reason DVFT Removes Both Types of Singularities
DVFT eliminates singularities because spacetime curvature is not fundamental. It is an *emergent
property* of the vacuum amplitude field \rho. If \rho cannot diverge, then curvature cannot diverge. The
vacuum’s elastic potential and finite inertial density are the mechanisms that prevent runaways.
Thus:
• matter cannot collapse to infinite density,
• wavefunctions cannot create divergent potentials,
• curvature cannot become infinite.
This is the first unified mechanism eliminating singularities across classical and quantum domains.
8. Comparison with GR, LQG, and QFT
General Relativity (GR):
• predicts unavoidable singularities (Hawking-Penrose theorems),
• has no internal regulator for curvature.
Loop Quantum Gravity (LQG):
• introduces discrete geometry,
• removes singularities by quantizing spacetime,
• but requires radical nonlocality and lacks experimental grounding.
Quantum Field Theory:
• produces infinite point-particle self-energies,
• resolves them only through renormalization,
• does not address gravitational singularity.
DVFT:
• retains continuum spacetime,
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 86
• derives gravity from a physical vacuum field,
• imposes finite amplitude & stiffness,
• eliminates both self-energy and gravitational singularities,
• without renormalization,
• without quantizing spacetime,
• without modifying quantum mechanics.
DVFT is the simplest and most physically grounded solution among all three.
9. Final Summary
DVFT eliminates singularities through vacuum amplitude dynamics:
1. The vacuum field \Phi = \rho e^{i\theta} has finite stiffness and inertial density.
2. U(\rho) prevents \rho from diverging under collapse.
3. Quantum particles generate finite vacuum amplitude deformations from |ψ|$^2$.
4. Gravity emerges as \nabla\rho, which can never diverge.
5. Black holes contain vacuum-phase condensates, not singularities.
6. No infinite self-energy, no point divergences, no r \to 0 explosion exists.
DVFT therefore provides the first unified, microphysically consistent elimination of:
• black hole singularities,
• quantum point singularities,
• gravitational field singularities.
This positions DVFT as a fundamentally complete framework bridging general relativity and quantum
mechanics.

\end{document}
