% ==============================================================================
% T0/FFGFT Theory: Document 220
% Title: Casimir falsification criteria:
%        Quantitative predictions in the transition region d → L_ξ
% Author: Johann Pascher
% Date: May 2026
% References: Documents 091 (Casimir-CMB), 166 (xi power ladder), 202 (field theory)
% Occasion: P. Austin (Information Physics Institute), falsification request
% ==============================================================================

\section*{Preamble}

This document formulates an experimentally testable falsification
criterion for FFGFT in the Casimir region, in direct response to
the methodological request from P.~Austin (mail of 9~May 2026, IPI
discussion): \emph{\enquote{What scale-dependence or residual differs
from the standard $1/d^4$ form, given that the ordinary $1/d^4$ form
is asymptotically recovered?}}

The answer is quantitative and lies in an experimentally accessible
range where currently no precision measurements exist.

% ==============================================================================
\section{Starting point: what FFGFT confirms}
% ==============================================================================

FFGFT confirms standard Casimir theory throughout the entire range
measured to date. Specifically:

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item \textbf{Decca et al.\ (170--300\,nm, 0.5\,\% accuracy):}
        no measurable FFGFT correction expected.
  \item \textbf{Bressi et al.\ (0.5--3\,$\mu$m):} no measurable
        FFGFT correction expected.
  \item \textbf{Lamoreaux (0.6--6\,$\mu$m):} no measurable
        FFGFT correction expected.
\end{itemize}

In the sub-$\mu$m to few-$\mu$m range, the FFGFT correction falls
off as the fourth power of $(d/L_\xi)$ and is therefore invisible
(see §\ref{sec:prediction}).

\textbf{The falsification criterion lies in the as-yet-unmeasured
range $d \sim L_\xi \approx 100\,\mu$m}, where current torsional
balance experiments (Iannuzzi group) and planned measurements
(Dartmouth, ILL Grenoble) are just beginning to deliver precise
data.

% ==============================================================================
\section{The FFGFT transition function}
\label{sec:prediction}
% ==============================================================================

\subsection{Asymptotic form (established)}

From Doc.~091, the Casimir energy density in the classical region
$d \ll L_\xi$ is:
\begin{equation}
  |\rho_\text{Casimir}(d)|
  \;=\; \frac{\pi^2}{240\,\xi_0}\,\rho_\text{CMB}\,
        \left(\frac{L_\xi}{d}\right)^4
  \;=\; \frac{\pi^2 \hbar c}{240\,d^4},
  \label{eq:casimir-asymptotic}
\end{equation}
with $L_\xi = (\xi_0\hbar c/\rho_\text{CMB})^{1/4} \approx 100.24\,\mu$m
and $\xi_0 = 4/30000$.

This is the standard formula -- exactly what Decca, Bressi, and
Lamoreaux measured, within their accuracy.

\subsection{\texorpdfstring{Transition function for $d \to L_\xi$}{Transition function for d to L_xi}}

In FFGFT, $L_\xi$ is not an arbitrary scale, but the vacuum length
scale at which the Casimir energy density between two plates
coincides with the CMB energy density:
\begin{equation}
  \rho_\text{Casimir}(d = L_\xi)
  \;=\; \frac{\pi^2}{240}\,\rho_\text{CMB}\,\xi_0^{-1}.
\end{equation}
For $d > L_\xi$, the Casimir mechanism (truncation of vacuum modes
between the plates) can no longer operate, since the wavelengths of
the relevant modes would exceed the plate separation.

This implies a \textbf{geometrically motivated transition function}:
\begin{equation}
  \rho_\text{Casimir}^{\,\text{FFGFT}}(d)
  \;=\; \frac{\pi^2 \hbar c}{240\,d^4}
        \cdot \mathcal{F}\!\left(\frac{d}{L_\xi}\right),
  \label{eq:ffgft-form}
\end{equation}
with the dimensionless transition function
\begin{equation}
  \mathcal{F}(x) \;=\; \frac{1}{1 + x^4},
  \qquad x = d/L_\xi.
  \label{eq:transition}
\end{equation}

\subsection{Justification of the form $1/(1+x^4)$}

The choice of this transition function is not arbitrary:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item \textbf{Asymptote $x \to 0$ (i.e., $d \ll L_\xi$):}
        $\mathcal{F} \to 1$, standard $1/d^4$ is reproduced exactly.
  \item \textbf{Asymptote $x \to \infty$ (i.e., $d \gg L_\xi$):}
        $\mathcal{F} \to 1/x^4$, hence $\rho_\text{Casimir} \to
        \rho_\text{CMB}$ constant -- the vacuum between the plates is
        no longer distinguishable from the CMB.
  \item \textbf{Transition point $x = 1$ ($d = L_\xi$):}
        $\mathcal{F}(1) = 1/2$, exactly the crossover between the
        two regimes.
  \item \textbf{Power $4$:} follows from the four-dimensionality of
        the energy-density volume $\hbar c/L^4$ and is consistent
        with the CMB bridge formula from Doc.~091.
\end{itemize}

% ==============================================================================
\section{Quantitative predictions}
\label{sec:numbers}
% ==============================================================================

From (\ref{eq:transition}) the relative deviation from the standard
formula follows:
\begin{equation}
  \Delta(d) \;\equiv\; \frac{\rho_\text{Casimir}^{\,\text{FFGFT}}(d)
                              - \rho_\text{Casimir}^{\,\text{std}}(d)}
                            {\rho_\text{Casimir}^{\,\text{std}}(d)}
  \;=\; \frac{1}{1 + (d/L_\xi)^4} - 1
  \;=\; -\frac{(d/L_\xi)^4}{1 + (d/L_\xi)^4}.
  \label{eq:delta}
\end{equation}

With $L_\xi = 100\,\mu$m, the following numbers result:

\begin{center}
\renewcommand{\arraystretch}{1.3}
{\small
\begin{tabular}{>{\raggedright\arraybackslash}p{1.6cm}>{\raggedright\arraybackslash}p{1.8cm}>{\raggedright\arraybackslash}p{2.4cm}>{\raggedright\arraybackslash}p{2.4cm}}
\toprule
\textbf{$d$} & $(d/L_\xi)^4$ & \textbf{$|\Delta|$} & \textbf{Measurable?} \\
\midrule
100\,nm     & $10^{-12}$              & $10^{-10}\,\%$    & no \\
1\,$\mu$m   & $10^{-8}$               & $10^{-6}\,\%$     & no \\
3\,$\mu$m   & $8.1\!\cdot\!10^{-7}$   & $\sim 10^{-4}\,\%$ & no \\
10\,$\mu$m  & $10^{-4}$               & $\approx 0.01\,\%$ & marginal \\
30\,$\mu$m  & $8.1\!\cdot\!10^{-3}$   & $\approx 0.80\,\%$ & \textbf{yes} \\
50\,$\mu$m  & $0.063$                 & $\approx 5.9\,\%$ & \textbf{yes} \\
70\,$\mu$m  & $0.24$                  & $\approx 19.3\,\%$ & \textbf{yes} \\
100\,$\mu$m & $1.0$                   & $50\,\%$          & \textbf{yes} \\
\bottomrule
\end{tabular}
}
\renewcommand{\arraystretch}{1.0}
\end{center}

\subsection{Three falsification regimes}

\textbf{Regime A: $d < 10\,\mu$m -- confirmation range.}
FFGFT predicts $|\Delta| < 0.01\,\%$. All existing precision
measurements (Decca: 170--300\,nm; Bressi: 0.5--3\,$\mu$m;
Lamoreaux: up to 6\,$\mu$m) lie in this range. \emph{FFGFT does not
contradict any of these experiments.}

\textbf{Regime B: $10\,\mu\text{m} < d < 100\,\mu$m -- falsification range.}
FFGFT predicts a growing, monotonically increasing deviation from
$0.01\,\%$ (at $d=10\,\mu$m) to $50\,\%$ (at $d=L_\xi$). Currently no
precision measurements exist in this range, but the required
sensitivity ($\sim 1\,\%$ at $d=30$--$50\,\mu$m) is achievable with
torsional balance setups (Iannuzzi group, Dartmouth, ILL Grenoble).

\textbf{Regime C: $d \to L_\xi$ -- prediction point.}
At exactly $d = L_\xi$, $\rho_\text{Casimir} = (1/2)\rho_\text{Casimir}^\text{std}$
should be measured, with $L_\xi$ fixed by Doc.~091 to $100.24\,\mu$m.
This is the \emph{sharpest} test: a single measurement point at
$100\,\mu$m with $\sim 5\,\%$ accuracy fixes or refutes the FFGFT
prediction.

% ==============================================================================
\section{Specific falsification criteria}
% ==============================================================================

FFGFT is \textbf{refuted} by any of the following observations:

\begin{enumerate}[leftmargin=2em,itemsep=4pt,topsep=2pt]
  \item \textbf{Sub-$\mu$m range:}
        A Casimir measurement at $d < 1\,\mu$m showing a deviation
        $|\Delta| > 0.1\,\%$ from standard $1/d^4$.
        \emph{Reason:} FFGFT predicts $|\Delta| < 10^{-6}\,\%$ here.

  \item \textbf{Transition range:}
        A precision measurement in the range $30$--$70\,\mu$m
        showing \emph{no} systematic negative deviation of the size
        predicted by (\ref{eq:delta}).
        \emph{Reason:} FFGFT predicts $|\Delta|$ between $1\,\%$ and
        $20\,\%$ here, with definite sign (Casimir force weaker than
        $1/d^4$).

  \item \textbf{Prediction point:}
        A measurement at $d = 100\,\mu$m that does not give
        $\rho_\text{Casimir}(L_\xi) \approx \frac{1}{2}\,
        \rho_\text{Casimir}^\text{std}(L_\xi)$ (within measurement
        accuracy), or yields $L_\xi$ significantly different from
        the value $L_\xi^\text{T0} = 100.24\,\mu$m calculated from
        $\rho_\text{CMB}$.
        \emph{Reason:} The bridge to the CMB (Doc.~091,
        eq.~\ref{eq:cmb_vacuum_relation}) would be broken.

  \item \textbf{Functional form:}
        A systematic deviation of the measured transition function
        from the form $\mathcal{F}(d/L_\xi) = 1/(1 + (d/L_\xi)^4)$
        outside measurement uncertainty.
\end{enumerate}

Each of these criteria is sufficient for refutation of the FFGFT
Casimir prediction. They are mutually \emph{independent}, so
several experiments can test the theory in parallel or sequentially.

% ==============================================================================
\section{What FFGFT does NOT predict}
% ==============================================================================

For methodological clarity:

\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item FFGFT does \emph{not} predict an additional Yukawa-type force
        $\sim e^{-d/\lambda}$. Modifications from extra dimensions
        (Randall-Sundrum, ADD) produce such corrections; FFGFT does
        not. A measured Yukawa term is neither evidence for nor
        against FFGFT.
  \item FFGFT does \emph{not} predict modifications to the thermal
        Casimir correction (Drude vs.\ plasma model debate). The
        FFGFT prediction is orthogonal to that debate and compatible
        with both models.
  \item FFGFT does \emph{not} predict modifications to geometric
        factors (sphere-plate vs.\ plate-plate, Proximity Force
        Approximation). The correction (\ref{eq:transition}) is
        universal in $d/L_\xi$ and should appear identically in
        all geometries.
\end{itemize}

% ==============================================================================
\section{Summary}
% ==============================================================================

FFGFT makes a quantitative, experimentally testable prediction in
the Casimir region:
\begin{equation*}
  \boxed{
    \rho_\text{Casimir}^{\,\text{FFGFT}}(d)
    \;=\; \rho_\text{Casimir}^{\,\text{std}}(d)
          \cdot \frac{1}{1 + (d/L_\xi)^4},
    \qquad L_\xi = 100.24\,\mu\text{m}.
  }
\end{equation*}

The prediction:
\begin{itemize}[leftmargin=2em,itemsep=2pt,topsep=2pt]
  \item is compatible with all existing data in the measured range
        ($d < 10\,\mu$m, confirmation regime, $|\Delta| < 0.01\,\%$);
  \item delivers a measurable, monotonically increasing deviation
        ($0.8$--$50\,\%$) in the range $30$--$100\,\mu$m;
  \item is experimentally accessible with current torsional balance
        technology;
  \item contains no free parameter -- $L_\xi$ is fixed numerically
        through Doc.~091 by $\rho_\text{CMB}$;
  \item is falsifiable on four independent criteria
        (sub-$\mu$m, transition range, prediction point, functional
        form).
\end{itemize}

\textbf{Methodological note.} This prediction is FFGFT-internal.
It follows from the $\xi$-vacuum geometry and the Casimir-CMB
bridge formula (Doc.~091), not from a topological partition or a
recursive survival structure. Whether other IPI strands can
reproduce the same prediction in their own language remains open
and is not a precondition for the validity of the statement.

\textbf{Status.} The prediction stands available for experimental
test. Should existing or upcoming torsional balance data in the
$30$--$100\,\mu$m range become available, they are to be compared
directly with (\ref{eq:transition}).
