\documentclass[11pt,a4paper]{article}

\usepackage{fontspec}
\setmainfont{DejaVu Sans}
\setsansfont{DejaVu Sans}
\setmonofont{DejaVu Sans Mono}[Scale=0.88]
\defaultfontfeatures{Ligatures=TeX}
\usepackage{microtype}
\usepackage{unicode-math}
\setmathfont{Latin Modern Math}[Scale=1.0]
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=2.5cm}

% --- Zeilenumbruch: sauber wie im Harmonikabuch ---
\sloppy
\emergencystretch=3em
\tolerance=2500
\hbadness=10000
\hfuzz=2pt
\clubpenalty=10000
\widowpenalty=10000

\usepackage{amsmath,amssymb}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  urlcolor=blue!50!black,
  pdftitle={Cosmological Redshift in FFGFT - A Brief Summary},
  pdfauthor={Johann Pascher}
}

\title{Cosmological Redshift in FFGFT\\[2pt]
  \large A Brief Summary for the IPI Correspondence}
\author{Johann Pascher\\[2pt]
\small ORCID: \href{https://orcid.org/0009-0000-6518-4064}{0009-0000-6518-4064}\\
\small GitHub: \url{https://github.com/jpascher/T0-Time-Mass-Duality}\\
\small Zenodo (FFGFT v1.0.13): \url{https://zenodo.org/records/20041529}\\
\small DOI: \href{https://doi.org/10.5281/zenodo.20041529}{10.5281/zenodo.20041529}}
\date{May 2026}

\begin{document}
\maketitle

\begin{abstract}
\noindent In FFGFT, cosmological redshift is a geometric path effect, not a Doppler signature of a metric expansion. Photons traverse the fluctuating $\xi$-vacuum along geodesics whose effective path length $L_{\mathrm{eff}}$ is systematically longer than the Euclidean distance $d$, with $z = (L_{\mathrm{eff}} - d)/d$. The Hubble constant becomes a fundamental coupling that follows from the single dimensionless $\xi = 4/30{,}000$:
\[
\frac{\hbar H_0}{m_e c^2} = \frac{\pi}{2}\,\xi^{10} \qquad\Longrightarrow\qquad H_0 \approx 66{,}5\ \text{km/s/Mpc},
\]
parameter-free, within $1{,}3\%$ of the Planck value. This note summarises the FFGFT redshift mechanism, the two equivalent derivations of $H_0$, and the natural resolution of the Hubble tension. Source documents in the FFGFT corpus: Doc~025 (cosmology), Doc~026 (geometric cosmology), Doc~027 (Solar System consistency), Doc~165 ($H_0$ ratio), Doc~166 (Casimir-Hubble bridge).
\end{abstract}

\section{Setting}

FFGFT models the universe as static and flat. The single dimensionless parameter $\xi = 4/30{,}000$ governs the granularity of the $\xi$-vacuum. Photons crossing the vacuum are not carried by an expanding metric but propagate along geodesics that incorporate the small-scale fluctuations of the $\xi$-field. The cumulative effect over cosmological distances is a systematic redshift; over Solar-System distances it is operationally negligible.

\section{Redshift as a Geometric Path Effect}

The central observation, formalised in Doc~026 via a finite-element simulation of the $\xi$-vacuum, is that geodesics through the granular $\xi$-field are not perfect straight lines. The effective path length $L_{\mathrm{eff}}$ is systematically larger than the direct Euclidean distance $d$ between source and observer:
\begin{equation}
z = \frac{L_{\mathrm{eff}} - d}{d}\,,
\label{eq:z_geometric}
\end{equation}
with the linearised approximation
\begin{equation}
z \approx d \cdot C \cdot \xi
\label{eq:z_linear}
\end{equation}
where $C$ is a geometric constant and $\xi$ controls the cumulative path-stretching rate. The redshift is a property of the spacetime geometry itself, not of the relative velocity between source and observer.

\paragraph{Frequency-independence as a structural test.}
A geodesic is a property of the geometry; it does not depend on the photon's frequency. A red and a blue photon emitted from the same source follow the \emph{same} extended path. Their wavelengths are stretched by the same proportional factor. This is in agreement with the observed frequency-independence of cosmological redshift -- a feature that conventional ``tired light'' models fail to reproduce, and that distinguishes the FFGFT geometric mechanism from energy-loss scenarios with a frequency-dependent cross section.

\section{The Hubble Constant as a Fundamental \texorpdfstring{$\xi$}{xi}-Ratio}

Two equivalent FFGFT derivations of $H_0$ are recorded in the corpus.

\paragraph{Doc~165 -- the dimensionless ratio.} The cleanest formulation expresses $H_0$ as a pure ratio between the cosmological and the electron rest-energy scale:
\begin{equation}
\boxed{\;\frac{\hbar H_0}{m_e c^2} = \frac{\pi}{2}\cdot\xi^{10}\;}
\label{eq:h0_ratio}
\end{equation}
Numerically:
\begin{equation}
H_0^{\mathrm{FFGFT}} \approx 66{,}5\ \text{km/s/Mpc} \qquad (\text{Planck: } 67{,}4 \pm 0{,}5,\ \text{deviation } +1{,}3\%).
\end{equation}
The integer exponent $10$ reflects how far the cosmological energy scale lies from the lepton mass scale, measured in $\xi$-units. The geometric prefactor $\pi/2$ originates from the toroidal topology of the $\xi$-time field.

\paragraph{Doc~026 -- the Hubble-energy form.} Equivalently, the Hubble energy is expressed as
\begin{equation}
E_H = E_0\cdot\xi^{41/4} = 1{,}41\times 10^{-33}\,\text{eV}\,, \qquad H_0 = \frac{E_H}{\hbar} \approx 66{,}2\ \text{km/s/Mpc}\,,
\label{eq:EH_026}
\end{equation}
with $E_0 = 7{,}398$~MeV the FFGFT reference energy. The exponent decomposes as
\begin{equation}
\frac{41}{4} = \underbrace{10}_{\text{Doc 165 (}H_0\text{ ratio)}} + \underbrace{\frac{1}{4}}_{\text{Doc 091 (Casimir scale)}}\,,
\end{equation}
linking the Hubble derivation to the Casimir-CMB derivation through one and the same $\xi$.

\paragraph{Reinterpretation.} Both forms agree to better than $1\%$ with each other and with the Planck-scale measurement. In FFGFT, $H_0$ is not an expansion rate. It is a fundamental coupling describing the strength of the photon-vacuum interaction, derived from $\xi$ alone.

\section{The Hubble Tension}

Standard cosmology faces a $\sim 9\%$ discrepancy between early-universe ($H_0 \approx 67{,}4$ km/s/Mpc, Planck CMB) and late-universe ($H_0 \approx 73$ km/s/Mpc, SH0ES distance ladder; H0LiCOW lensing) measurements. Within $\Lambda$CDM this is a structural problem because the expansion rate should be a single universal constant.

In FFGFT the tension dissolves at the conceptual level for three reasons.

\begin{enumerate}\itemsep2pt
\item \textbf{No expansion, no expansion rate.} $H_0$ is not the rate at which space expands. It quantifies the cumulative photon-vacuum interaction. Different measurement methods need not return identical values, and the disagreement between early-universe and late-universe inferences is not by itself a contradiction.

\item \textbf{Method-dependent path probes.} Different probes (CMB acoustic peaks, distance-ladder Cepheids, gravitational lensing time delays) sample different distances and different photon energy regimes. In a granular $\xi$-vacuum, the cumulative coupling effective in each regime can differ systematically. The pattern of early-low / late-high inferred values is what one would expect if $\xi$-coupling depends mildly on the integrated path properties.

\item \textbf{Anisotropy compatibility.} Finite-element simulations of the $\xi$-vacuum (Doc~026) yield small directional variations of the effective coupling, consistent with reported indications of large-scale anisotropy in $H_0$ measurements.
\end{enumerate}

\section{Consistency with Solar-System Data}

A natural concern with any modification of cosmological redshift is its compatibility with high-precision Solar-System tests. FFGFT addresses this directly (Doc~027): the geometric path stretching is a cumulative effect over cosmological distances. Over Solar-System distances (light-hours), the stretching is operationally negligible, and FFGFT predicts \emph{zero} measurable orbital anomalies in the Solar System.

This is a structural difference from modified-gravity approaches to the Hubble tension, several of which were excluded by Nathan et al.~(2024, MNRAS 544, 975) on Solar-System grounds. FFGFT does not modify gravity at Solar-System scales; it reinterprets the cosmological-redshift premise. The Cassini-mission constraints, which exclude many modified-gravity proposals, are therefore automatically satisfied.

\section{Summary of Predictions}

\begin{enumerate}\itemsep2pt
\item Cosmological redshift is a geometric path effect, $z = (L_{\mathrm{eff}}-d)/d$, frequency-independent by construction.
\item $H_0$ follows parameter-free from $\xi = 4/30{,}000$:
\[
\hbar H_0 / (m_e c^2) = (\pi/2)\,\xi^{10} \quad\Longleftrightarrow\quad E_H = E_0\,\xi^{41/4}\,,
\]
yielding $H_0 \approx 66{,}2$ -- $66{,}5$ km/s/Mpc.
\item The Hubble-tension pattern (early-low / late-high) is structurally compatible with FFGFT and does not require additional model components.
\item The Solar-System Cassini constraints are satisfied automatically; no modification of gravity at local scales.
\item The Casimir scale $L_\xi$ and the Hubble constant $H_0$ satisfy an algebraic bridge relation, $L_\xi \cdot H_0/c \propto \xi^{41/4}$ (Doc~166).
\end{enumerate}

\section*{Document references}

\noindent\small\begin{tabular}{ll}
\textbf{Doc 025} & \emph{T0 Cosmology.} Static, eternal universe; CMB as $\xi$-field manifestation; \\
& three alternative interpretations of the redshift mechanism (energy loss, \\
& cumulative gravitation, spacetime geometry). \\[2pt]
\textbf{Doc 026} & \emph{Geometric cosmology.} Finite-element simulation of the $\xi$-vacuum; \\
& redshift as path stretching; derivation of $E_H = E_0\,\xi^{41/4}$; \\
& three-level resolution of the Hubble tension. \\[2pt]
\textbf{Doc 027} & \emph{MNRAS analysis.} Compatibility with Solar-System tests; \\
& comparison with Nathan et al.\ (2024) on modified gravity. \\[2pt]
\textbf{Doc 165} & \emph{The Hubble ratio.} Derivation of $\hbar H_0/(m_e c^2) = (\pi/2)\,\xi^{10}$ \\
& with $H_0 \approx 66{,}5$ km/s/Mpc, parameter-free. \\[2pt]
\textbf{Doc 166} & \emph{Casimir-Hubble bridge.} The decomposition $41/4 = 10 + 1/4$ \\
& and the algebraic relation $L_\xi \cdot H_0/c$. \\
\end{tabular}

\medskip
All documents available at \url{https://github.com/jpascher/T0-Time-Mass-Duality}\\
and as Zenodo release v1.0.13: \url{https://zenodo.org/records/20041529}.

\end{document}
