\documentclass[11pt,a4paper]{article}

\usepackage{fontspec}
\setmainfont{DejaVu Sans}
\setsansfont{DejaVu Sans}
\setmonofont{DejaVu Sans Mono}[Scale=0.88]
\defaultfontfeatures{Ligatures=TeX}
\usepackage{microtype}
\usepackage{unicode-math}
\setmathfont{Latin Modern Math}[Scale=1.0]
\usepackage[english]{babel}
\usepackage{geometry}
\geometry{margin=2.5cm}

% --- Zeilenumbruch: sauber wie im Harmonikabuch ---
\sloppy
\emergencystretch=3em
\tolerance=2500
\hbadness=10000
\hfuzz=2pt
\clubpenalty=10000
\widowpenalty=10000

\usepackage{amsmath,amssymb}
\usepackage{parskip}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  urlcolor=blue!50!black,
  pdftitle={The Primordial Lithium Problem and FFGFT},
  pdfauthor={Johann Pascher}
}

\title{The Primordial Lithium Problem and FFGFT\\[2pt]
  \large A Brief Summary for the IPI Correspondence}
\author{Johann Pascher\\[2pt]
\small ORCID: \href{https://orcid.org/0009-0000-6518-4064}{0009-0000-6518-4064}\\
\small GitHub: \url{https://github.com/jpascher/T0-Time-Mass-Duality}\\
\small Zenodo (FFGFT v1.0.13): \url{https://zenodo.org/records/20041529}\\
\small DOI: \href{https://doi.org/10.5281/zenodo.20041529}{10.5281/zenodo.20041529}}
\date{May 2026}

\begin{document}
\maketitle

\begin{abstract}
\noindent The primordial lithium problem -- the persistent factor 3--4 discrepancy ($4{,}2\sigma$--$5{,}3\sigma$) between Big Bang Nucleosynthesis (BBN) predictions for $^7$Li and observations of metal-poor halo stars (the Spite plateau) -- has resisted resolution for four decades. Standard solution classes (astrophysical depletion, nuclear physics, beyond-Standard-Model physics) all face structural difficulties. Fields (2011) explicitly lists ``large changes to the cosmological framework'' as a possible solution class. FFGFT instantiates that class: in a static, eternal $\xi$-universe there is no primordial nucleosynthesis epoch, and the Spite plateau is not the relic of an expanding-universe event. This note presents the FFGFT position, including a tentative explanation sketch for why D and $^4$He abundances nonetheless agree with BBN+CMB predictions while $^7$Li does not. The explanation is presented as a sketch, not a closed derivation.
\end{abstract}

\section{The Problem in Numbers}

The Big Bang Nucleosynthesis prediction, when fed the WMAP/Planck baryon-to-photon ratio $\eta_{10} = 6{,}23 \pm 0{,}17$, yields:
\begin{align}
\text{D/H}\big|_{\text{BBN+CMB}} &= (2{,}82 \pm 0{,}21) \times 10^{-5} &&\text{(observation: matches)}\\
Y_p(^4\text{He}) &= 0{,}249 \pm 0{,}009 &&\text{(observation: matches)}\\
^{7}\text{Li/H}\big|_{\text{BBN+CMB}} &= (5{,}24^{+0{,}71}_{-0{,}67}) \times 10^{-10} &&\text{(observation: differs)}
\end{align}
The Spite-plateau measurement \cite{spitespite1982,fields2011} of metal-poor halo stars gives
\begin{equation}
^{7}\text{Li/H}\big|_{\text{obs}} = (1{,}23^{+0{,}68}_{-0{,}32}) \times 10^{-10}\,,
\end{equation}
a factor of $2{,}4$--$4{,}3$ below the BBN+CMB prediction, corresponding to $4{,}2\sigma$--$5{,}3\sigma$ \cite{cyburt2008}. Cyburt, Fields and Olive titled their 2008 update ``A Bitter Pill: The Primordial Lithium Problem Worsens'' -- improved nuclear cross-section data \emph{increased} the predicted $^7$Li abundance.

The discrepancy is universal across stellar environments: the Spite plateau has been observed in halo field stars, globular clusters \cite{cyburt2008}, dwarf spheroidals, ultra-faint galaxies, and accreted satellites \cite{borisov2024}. It is not a feature of any one galactic environment.

\section{Standard Solution Classes}

Following Fields (2011), three classes have been pursued:

\paragraph{Astrophysical (stellar depletion).}
The most active current programme \cite{borisov2024} models internal stellar mixing -- atomic diffusion, parametric turbulence, rotation-induced angular momentum transport -- to deplete photospheric $^7$Li by a factor $\sim 3$. The challenge: the Spite plateau is observationally \emph{thin}, with little star-to-star scatter, and is found across very different stellar populations. Universal depletion across these environments is difficult to motivate physically.

\paragraph{Nuclear physics.}
Hypothetical resonances enhancing $^7$Be destruction, e.g.\ $^7$Be$ + ^{3}$He $\to {}^{10}$C$^* \to p + {}^{9}$B \cite{fields2011,hammache2013}, or revised $^3$He$(\alpha,\gamma)^7$Be cross-sections. Recent experimental work has \emph{tightened} the rates and \emph{worsened} the prediction \cite{cyburt2008}.

\paragraph{Beyond Standard Model.}
Decaying SUSY particles, time-varying fundamental constants \cite{uzan2003}, primordial magnetic fields. Constraint: D and $^4$He must remain unperturbed, which leaves a narrow parameter window.

\paragraph{The fourth class.}
Fields (2011) closes his classification with: \emph{``large changes to the cosmological framework used to interpret light element data.''} This category has received less attention but is logically open.

\section{The FFGFT Position}

FFGFT instantiates the fourth class. The cosmological framework is static and eternal, derived from the single dimensionless parameter $\xi = 4/30{,}000$:
\begin{itemize}\itemsep1pt
\item No Big Bang. The Heisenberg time-energy uncertainty argument (Doc 025) precludes a finite-duration cosmological singularity.
\item No expanding spacetime. Cosmological redshift is a geometric path effect through the granular $\xi$-vacuum, not a Doppler signature (Doc 026).
\item No primordial nucleosynthesis epoch. The Spite plateau is therefore \emph{not} the relic of a universe-wide event 13.8 Gyr ago.
\end{itemize}

In this framework, the Spite plateau records the long-term equilibrium $^7$Li abundance produced and maintained by stellar processes (Galactic cosmic-ray spallation, novae, AGB stars, core-collapse supernovae, white-dwarf mergers \cite{borisov2024}) in a quasi-stationary state. The factor 3--4 ``discrepancy'' is then not a discrepancy with reality, but with a prediction that requires an event (BBN) that did not occur in this framework.

The honest follow-up question is: \emph{why do D and $^4$He match BBN+CMB so precisely if there is no BBN?}

\section{Explanation Sketch: Why D and \texorpdfstring{$^4$He}{4He} Match}

What follows is an \emph{explanation sketch}, not a closed derivation. The point is to indicate a plausible mechanism, not to claim that the mechanism is already worked out.

\paragraph{Step 1 -- The CMB is real, but not a relic.}
FFGFT accepts the CMB as a physical phenomenon, but identifies it as a manifestation of the $\xi$-vacuum rather than the redshifted afterglow of a hot early phase. In Doc 091, the CMB energy density is fixed by
\begin{equation}
\rho_{\mathrm{CMB}} = \frac{\xi\,\hbar c}{L_\xi^4}\,, \qquad L_\xi \approx 100{,}24\,\mu\text{m}\,,
\end{equation}
and the CMB temperature follows accordingly. The photon bath that carries the spectrum is real and operative \emph{now}, not just at $z \approx 1100$.

\paragraph{Step 2 -- The baryon-to-photon ratio.}
In standard BBN, light-element yields depend on the single parameter $\eta = n_B/n_\gamma$. In FFGFT, both the photon density (from $\rho_{\mathrm{CMB}}$ and $T_{\mathrm{CMB}}$) and the cosmic baryon density (from continuous stellar processes integrated over an eternal universe) are present-day quantities. Their ratio defines an \emph{effective} $\eta_{\mathrm{eff}}$, which the WMAP/Planck inference correctly extracts from the CMB acoustic peaks -- because the acoustic-peak structure depends only on the present-day $\eta$, not on its history.

The ΛCDM interpretation reads back from this $\eta$ to a primordial $\eta$ via assumed entropy conservation; FFGFT keeps the present-day $\eta$ as a stationary characteristic of the $\xi$-universe.

\paragraph{Step 3 -- Thermal-equilibrium yields.}
For light nuclides whose abundances are governed by \emph{rapid two-body equilibrium reactions in a thermal bath}, the equilibrium abundance is a function of $\eta$ and $T$ alone, not of the history that produced this $(\eta, T)$ pair. The reaction network that determines D and $^4$He abundances under BBN conditions is dominated by such two-body equilibria with strong reverse reactions:
\begin{equation}
p + n \leftrightarrow d + \gamma, \qquad d + d \leftrightarrow {}^3\text{He} + n, \qquad {}^3\text{He} + d \leftrightarrow {}^4\text{He} + p\,, \dots
\end{equation}
If the FFGFT $\xi$-vacuum sustains a $(T_{\mathrm{CMB}}, \eta_{\mathrm{eff}})$ that coincides with the WMAP-inferred values, the same equilibrium abundances follow. This is why D and $^4$He observations agree with BBN+CMB predictions: the predictions describe a \emph{thermal equilibrium}, and the equilibrium is realised in FFGFT for the same ($T, \eta$) by construction. The agreement is not a coincidence; it is a consistency check on the $\xi$-determination of $T_{\mathrm{CMB}}$.

\paragraph{Step 4 -- Why $^7$Li breaks the pattern.}
$^7$Li is the exception because its production-destruction chain has a \emph{slow, non-equilibrium} component:
\begin{enumerate}\itemsep1pt
\item $^7$Li at WMAP $\eta$ is produced predominantly as $^7$Be via $^3$He$(\alpha,\gamma)^7$Be \cite{fields2011}.
\item In standard BBN, $^7$Be then survives the cessation of nuclear reactions and decays to $^7$Li by electron capture on a timescale of $\sim 53$ days -- after BBN has frozen out.
\item In FFGFT, no freeze-out occurs because there is no expansion-driven temperature drop. The $^7$Be population sits in a stationary environment with continuous photon and electron interactions, including channels that destroy $^7$Be on timescales much shorter than its laboratory half-life would suggest.
\end{enumerate}
The BBN calculation assumes a clean $^7$Be $\to {}^7$Li conversion after freeze-out, treating it as bookkeeping. In FFGFT this assumption is invalid: the stationary state allows continuous $^7$Be destruction (via cosmic-ray-induced spallation, energetic photon channels in the $\xi$-vacuum, or stellar incorporation) that the BBN bookkeeping does not account for. The plateau-level $^7$Li abundance is then the stationary attractor of the full network in a static universe, and it is naturally lower than the BBN bookkeeping value.

\paragraph{What this sketch does and does not claim.}
\textit{Does claim:} a structural reason why an equilibrium-dominated nuclide (D, $^4$He) follows the standard prediction while a freeze-out-dependent nuclide ($^7$Li) does not. \textit{Does not claim:} a closed quantitative derivation of the Spite-plateau value from $\xi$. The next step would be to set up the stationary network in the $\xi$-vacuum and compute the attractor for $^7$Li. This is open work, not a finished result.

\section{Summary}

\begin{enumerate}\itemsep2pt
\item The lithium problem is real and standard: factor 3--4, $4{,}2\sigma$--$5{,}3\sigma$, persistent across four decades and many proposed fixes.
\item Astrophysical, nuclear and BSM solutions all face structural challenges; the cosmological-framework alternative (Fields 2011) remains open.
\item FFGFT instantiates the cosmological-framework alternative: no Big Bang, no primordial nucleosynthesis epoch, the Spite plateau is a stationary stellar-equilibrium feature.
\item The agreement of D and $^4$He with BBN+CMB is not coincidental but a consistency check: equilibrium abundances depend on $(T, \eta)$ alone, and FFGFT fixes both via $\xi$-geometry.
\item $^7$Li differs because its abundance depends on a freeze-out assumption that is invalid in a static universe; the stationary attractor lies below the BBN bookkeeping value.
\item The quantitative derivation of the FFGFT $^7$Li attractor is open work; this note presents the explanation as a sketch.
\end{enumerate}

\section*{References}

\noindent\small
\begin{thebibliography}{99}
\bibitem{spitespite1982} Spite, M.\ \& Spite, F.\ (1982). \emph{Abundance of lithium in unevolved halo stars and old disk stars.} A\&A 115, 357.
\bibitem{nollett1997} Nollett, K.M., Lemoine, M.\ \& Schramm, D.N.\ (1997). \emph{Big Bang Nucleosynthesis in the new cosmology.} arXiv:astro-ph/9612197.
\bibitem{dring1997} Möring \emph{et al.} (1997). \emph{Reaction rate measurements relevant to BBN $^7$Li production.} ApJ.
\bibitem{cyburt2008} Cyburt, R.H., Fields, B.D.\ \& Olive, K.A.\ (2008). \emph{A Bitter Pill: The Primordial Lithium Problem Worsens.} arXiv:0808.2818.
\bibitem{dunkley2009} Dunkley, J.\ \emph{et al.} (2009). \emph{Five-Year WMAP Observations: Bayesian Estimation of CMB Polarization Maps.} arXiv:0803.0586.
\bibitem{fields2011} Fields, B.D.\ (2011). \emph{The Primordial Lithium Problem.} Annual Reviews of Nuclear and Particle Science. arXiv:1203.3551.
\bibitem{hammache2013} Hammache, F.\ \emph{et al.} (2013). \emph{High-energy direct measurement of the $^7$Be$(p,\gamma)^8$B reaction at LUNA.} arXiv:1312.0894.
\bibitem{uzan2003} Uzan, J.-P.\ (2003). \emph{The fundamental constants and their variation: observational status and theoretical motivations.} arXiv:hep-ph/0205340.
\bibitem{borisov2024} Borisov, S., Charbonnel, C., Prantzos, N., Dumont, T.\ \& Palacios, A.\ (2024). \emph{A coherent view of Li depletion and angular momentum transport to explain the Li plateau.} A\&A. arXiv:2403.15534.
\end{thebibliography}

\medskip
\noindent\emph{FFGFT source documents: Doc 025 (T0 Cosmology, $\xi$-field universe and CMB), Doc 026 (geometric cosmology, $H_0$ and the redshift mechanism), Doc 091 (Casimir-CMB relation, $L_\xi$). All available at \url{https://github.com/jpascher/T0-Time-Mass-Duality} and Zenodo v1.0.13: \url{https://zenodo.org/records/20041529}.}

\end{document}
