% ============================================================
% Content: Shor's Algorithm without Qubit Registers ---
% the photonic perspective
% in the FFGFT framework
% Revised March 2026
% Builds on Doc.~173--175
% ============================================================

\providecommand{\ket}[1]{\left|#1\right\rangle}
\providecommand{\bra}[1]{\left\langle#1\right|}
\providecommand{\braket}[2]{\left\langle#1\middle|#2\right\rangle}

\section{Shor's Algorithm without Qubit Registers ---
  the Photonic Perspective}
\label{sec:shor-photon}
% ============================================================

\begin{significance}[Central thesis of this document]
\textbf{Photonically everything is realisable.}

Every step of Shor's algorithm ---
superposition, modular exponentiation,
quantum Fourier transformation, measurement ---
can be physically executed by a photonic system at
room temperature.

Not as a simulation, not as an approximation,
but as a \textbf{direct physical realisation}:
the light \emph{is} the superposition,
the MZI network \emph{is} the Fourier transformation,
the interference \emph{is} the period search.

From the FFGFT perspective this statement is mathematically
precisely formulable:
the FFGFT field equation on a sub-Planck lattice
describes exactly the physical process
that delivers the period $r$ as a resonance frequency.

\medskip
\textbf{What is not possible:}
Simulating this field equation on a conventional
digital computer ---
the matrix problem is $N \times N$ in size,
hence unsolvable for RSA-relevant $N$.

\medskip
\textbf{What this means:}
The photonic system solves the problem
not through computation, but through physics ---
exactly as a lens does not compute a Fourier transformation
but \emph{is} one.
\end{significance}

The quantum computer is often justified by Shor's algorithm
for factorisation --- the only known algorithm with a genuine
exponential quantum advantage over classical methods.

From the FFGFT perspective, the qubit register for Shor is
not the most natural way ---
the natural level is the photonic one.

% ============================================================
\subsection{What Shor Really Does: Only One Quantum Step}
% ============================================================

Shor's algorithm splits into two fundamentally different parts:

\textbf{Part 1 --- classical:}
Choose random $a$, compute $\gcd(a, N)$,
extract factors from the found period.
Ordinary arithmetic --- no quantum computing needed.

\textbf{Part 2 --- the only quantum step:}
Find the \textbf{period} $r$ of the function
$f(x) = a^x \bmod N$.
For this the quantum Fourier transformation (QFT)
is employed, which transforms the superposition state:
\begin{equation}
  \ket{\psi_3} \;=\;
  \frac{1}{\sqrt{M}}\sum_{j=0}^{M-1} \ket{jr + \ell}
\end{equation}
into sharp peaks at $y \approx s \cdot 2^n / r$
--- from which $r$ is extracted via continued fractions.

\begin{keyresult}[The core: period search is a wave operation]
The only step in Shor that is exponentially
more efficient than classical search is
the period search via QFT.
Everything else is classical arithmetic.

The QFT itself is a \textbf{Fourier transformation}:
it finds periodicities through
\textbf{coherent interference} ---
constructive amplification at the period frequencies,
destructive cancellation of all others.

This is not a discrete computational procedure.
This is a \textbf{wave operation} ---
and wave operations are the natural domain
of photonic systems, not qubit registers.

An essential difference:
The qubit register delivers at each measurement
a single probabilistic result ---
the period appears only through
\textbf{averaging over many runs}.

A photonic interference system delivers
the complete intensity pattern \emph{in one run}
directly as a physical quantity ---
no probabilistic averaging needed.
\end{keyresult}

% ============================================================
\subsection{The QFT is a Wave Operation ---
  Photonic Systems Realise It Physically}
% ============================================================

A Fourier transformation through coherent interference
is exactly what every wave system does by nature.

A \textbf{lens} performs an optical
Fourier transformation --- in the time
light takes to pass through it.
No register, no gate, no cooling.

A \textbf{grating spectrometer} decomposes light
into its frequency components through physical
interference --- this is a physical
Fourier analysis that instantly makes periodicities
in the light field visible.

An \textbf{MZI network} with $n$ stages implements
geometrically an $n$-point Fourier transformation ---
the phase relations between the paths correspond
exactly to the twiddle factors $e^{2\pi i jk/n}$ of the QFT.

\begin{foundation}[FFGFT: QFT as physical interference of torsion waves ---
  mathematical formulation]
In FFGFT the QFT is not an abstract unitary matrix
on a qubit register ---
it is the natural dynamics of a wave system.

\textbf{The mathematical formulation:}

The photonic torsion field $\Psi(\mathbf{x}, t)$
in the waveguide satisfies the FFGFT wave equation:
\begin{equation}
  \label{eq:photon-wave}
  \left[\nabla^2 - \frac{1}{c^2}\partial_t^2
  + \xi \cdot K(\mathbf{x})\right]\Psi = 0,
\end{equation}
where $K(\mathbf{x})$ encodes the crystal geometry of the
MZI network.

The stationary solutions of this equation are
exactly the eigenmodes of the QFT ---
the twiddle factors $e^{2\pi i jk/n}$
appear as natural phase relations
between the modes of the waveguide.

\textbf{What this means:}
This equation is \emph{not simulable on a conventional
digital computer} ---
the state space problem is exponentially large.
But it is \emph{physically exactly solvable}:
the photonic system solves it by
relaxing into the equilibrium state.

This is naturally given at the $\xi$ level $N \approx 9$
(photonic resonator, eV scale, room temperature) ---
the torsion waves interfere collectively in the crystal geometry
of the waveguide.

A qubit register at $\xi$ level $N \approx 8$
(mK, spin qubits) \emph{emulates} this process
digitally through gate operations ---
a detour via a colder, more fragile level
to do something the warmer level does directly.
\end{foundation}

% ============================================================
\subsection{The MZI Network: Photonic QFT is Principally Fully Realisable}
\label{sec:mzi-qft}
% ============================================================

\begin{keypoint}[Photonic QFT: principally complete]
A photonic realisation of Shor's QFT step
is \textbf{principally fully possible} ---
not as a simulation, but as a direct physical
evaluation through wave interference.

The MZI network realises the quantum Fourier transformation
in the time light takes to traverse the network ---
at room temperature, without cooling, without qubit register.

The only open problem is the \textbf{input preparation}:
the modular exponentiation $f(x) = a^x \bmod N$
must be encoded for all $x$ simultaneously in the light signal.
Precisely for this the eigenvalue problem (Section~\ref{sec:ffgft-eigen})
is the proposed solution.
\end{keypoint}

The quantum Fourier transformation computes:
\begin{equation}
  F(k) \;=\; \sum_{x=0}^{N-1} f(x)\cdot W_N^{kx},
  \quad W_N = e^{2\pi i/N}.
\end{equation}
The factors $W_N^{jk} = e^{2\pi i jk/N}$ are called
\textbf{twiddle factors} --- they describe
phase rotations by angle $2\pi jk/N$.

In an \textbf{MZI network} (Mach-Zehnder interferometer)
exactly this phase rotation is physically realised:
the light is split by a beam splitter into two paths.
Through changing the optical path length
(phase shifter, piezo, refractive index modulation)
one path experiences the delay $\Delta\phi = 2\pi jk/N$
relative to the other.

The outputs of the MZI correspond exactly to the
\textbf{butterfly operations} of the classical FFT
(Cooley-Tukey algorithm): two input waves are
mixed, multiplied by the twiddle factor and
distributed to two outputs. An $n$-stage MZI network
cascades these operations --- the total network
computes a $2^n$-point FFT in the time light
traverses the network.

\begin{foundation}[FFGFT: MZI network as torsion wave QFT]
In FFGFT every phase rotation by $\Delta\phi$
is a rotation of the torsion configuration
by the same angle in the transverse plane.

The MZI network does not \emph{emulate} the mathematics
of the QFT --- it \emph{is} physically a QFT:
the phase relations between the paths are
the twiddle factors, the beam splitters are
the butterfly operations, and the coherence
of the light ensures the superposition.

At the $\xi$ level $N \approx 9$ (photonic, eV scale)
this operation is thermally stable at room temperature ---
in contrast to the digital emulation at level $N \approx 8$
(spin qubit, meV scale, mK cooling mandatory).

The qubit register emulates digitally what the MZI network
directly does physically --- a detour via a
fragile, cold level for an operation that the
warmer level naturally masters.
\end{foundation}

\subsection{\texorpdfstring{What the MZI Network Does \emph{Not} Solve}{What the MZI Network Does Not Solve}}

The MZI network realises the QFT --- but only for
a \emph{known, complete} input vector.

The actual bottleneck in Shor is the
evaluation of $f(x) = a^x \bmod N$ for all
$x = 0 \ldots 2^n-1$ simultaneously.
A $2^n$ input vector does not exist as a
physical light signal --- it would first have to be
computed, which costs $O(N)$.

The eigenvalue problem (Section~\ref{sec:ffgft-eigen})
is the attempt to circumvent this hurdle too:
not computing all $f(x)$, but reading off the period
as a resonance frequency of the potential.

% ============================================================
\subsection{\texorpdfstring{FFGFT-Shor: $\xi$ Resonance Replaces the QFT}{FFGFT-Shor:  Resonance Replaces the QFT}}
% ============================================================

Doc.~147 develops a FFGFT-Shor algorithm
that replaces the QFT through direct \textbf{$\xi$-resonance search}:

\begin{equation}
  \text{Resonance}(r) \;=\;
  \frac{\exp(-\xipar \cdot r^2 / \Dfrak)}
       {|a^r \bmod N - 1| + 1}.
\end{equation}

Strong resonance at an $r$ means
$a^r \equiv 1 \pmod{N}$ ---
the sought $r$ is found.

\subsection{Why No Qubit Register is Needed ---
  and What Registers Can Still Do}

\begin{foundation}[FFGFT: Shor is a wave interference problem,
  not a discrete state problem]
The period $r$ of $a^x \bmod N$ is a property of the
\emph{entire function} $f : x \mapsto a^x \bmod N$ ---
not of an individual value $f(x_0)$.

It is a \textbf{global spectral property}:
the frequency with which the function returns to the value~1.

A discrete computational machine that evaluates $f(x)$
sequentially needs $O(r)$ steps to find the period ---
exponential in the problem size.

A wave system that encodes $f(x)$ simultaneously
for all $x$ (as amplitude, phase, or intensity)
can extract the period through coherent interference
in a single pass --- regardless of the value of $r$.

That is exactly what the QFT in the qubit register does ---
but the qubit register is not the only way.
A photonic MZI network does the same, at room temperature,
without cooling, without qubit coherence.
\end{foundation}

\begin{important}[Two problems for QC, one for photonics]
\textbf{Qubit register:}
\begin{itemize}
  \item Problem 1: Decoherence in mK environment, error correction required
  \item Problem 2: Modular exponentiation expensive ($O(n^3)$ gates)
  \item Advantage: Complete quantum parallelism in one system
\end{itemize}

\textbf{Photonic MZI network:}
\begin{itemize}
  \item Problem 1 solved: room temperature, no decoherence
  \item Problem 2 open: input preparation for $f(x)$ for all $x$
  \item Advantage: QFT directly, without gates, in one light pass
\end{itemize}
\end{important}

\begin{keypoint}[Quantum computer is no better calculator]
The quantum computer does not compute faster by
having faster bits --- it computes differently:
through quantum parallelism, superposition and interference.

The photonic system is an even more direct realisation:
it does not \emph{compute} the interference ---
it \emph{is} interference.
The period $r$ appears as a physical resonance,
not as a numerical result.
\end{keypoint}

% ============================================================
\section{FFGFT-FFT as Eigenvalue Problem ---
  the Sub-Planck Lattice}
\label{sec:ffgft-eigen}
% ============================================================

\subsection{From Summation to Resonance Problem}

The standard Shor algorithm computes:
\begin{equation}
  \text{QFT}: \quad \ket{x} \;\mapsto\;
  \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} e^{2\pi i xk/N}\ket{k}.
\end{equation}

The FFGFT reformulation replaces this by an eigenvalue problem:
instead of transforming a state vector,
the period is sought as the eigenfrequency of a
tight-binding Hamiltonian:

\begin{equation}
  \label{eq:t0-discrete}
  -\frac{\Psi_{n+1} - 2\Psi_n + \Psi_{n-1}}{\ell_0^2}
  + \frac{E^2}{\hbar^2 c^2}
  \left(1 - \xi \cdot \frac{a^n \bmod N}{N}\right)\Psi_n
  = E\,\Psi_n,
  \quad n \in \mathbb{Z}.
\end{equation}

\begin{keypoint}[Fundamental change of problem class]
The standard QFT transforms:
\textbf{State vector} $\to$ \textbf{frequency space}.

The FFGFT formulation asks:
at which energies does the potential
$V(n) = -\xi \cdot (a^n \bmod N)/N$
have \textbf{localised eigenstates}?

This is not a computational problem ---
it is a \textbf{spectroscopic measurement problem}.
\end{keypoint}

\subsection{The Sub-Planck Scale Makes the Potential Consistently Discrete}

On the sub-Planck lattice with $\ell_0 = \xipar \cdot \lP \approx 2 \times 10^{-39}$\,m
the lattice is fine enough to represent every jump of
$a^n \bmod N$ without information loss.

\begin{foundation}[Sub-Planck scale: discreteness as strength]
What appears as a problem in the continuum ---
the jumps of $a^x \bmod N$ ---
becomes on the discrete lattice a
\textbf{coupling matrix of a tight-binding model}:
\begin{equation}
  H_{mn} =
  -\frac{1}{\ell_0^2}
  \bigl(\delta_{m,n+1} + \delta_{m,n-1} - 2\delta_{m,n}\bigr)
  + \frac{E^2}{\hbar^2 c^2}
  \!\left(1 - \xi \cdot \frac{a^n \!\bmod N}{N}\right)
  \!\delta_{m,n}.
\end{equation}

This is a \textbf{tight-binding Hamiltonian}
with a quasiperiodic potential ---
a model class well understood in solid-state physics
(Anderson localisation, Hofstadter butterfly).

The ``jumpiness'' of $a^n \bmod N$ corresponds to
a pseudorandom potential.
The question shifts from
``Do the eigenvalues exist?''
to
``Are the eigenstates localised at the right energies?'' ---
a question of \textbf{Anderson localisation}.
\end{foundation}

\subsection{The Open Conjecture}
\label{sec:ffgft-conjecture}

\begin{keyresult}[FFGFT-FFT conjecture (open)]
For every $N = p \cdot q$ and every $a$
coprime to $N$, there exists $\xi > 0$
and a lattice constant $\ell_0 \ll \lP$,
such that the discrete eigenvalue problem
(Eq.~\ref{eq:t0-discrete})
has localised eigenstates
at $E = 2\pi\hbar c \cdot k/r$ if and only if
$r$ is the order of $a$ modulo $N$.

\medskip
\textbf{Status:} Unproven.
This conjecture is mathematically precisely formulable
but not yet proven or refuted.
It is not simulable on a classical computer
(the matrix problem is $N \times N$ in size),
but physically realisable in a
FFGFT torsion field on sub-Planck scale.
\end{keyresult}

\subsection{What the Formulation Achieves --- and What Not}

\begin{important}[Honest assessment]
\textbf{What this formulation achieves:}\\
It gives the FFGFT-FFT idea a mathematically precise form.
It connects the number-theoretic problem
(order of $a$ modulo $N$)
with a physical resonance problem
(localised eigenstates of a tight-binding model).
It is basis-system independent and
not reliant on floating-point artefacts.\\[6pt]

\textbf{What this formulation does not achieve:}\\
It does not prove that the eigenstates are localised at the
right energies.
It is not more efficient on a classical computer
than brute-force period search ---
the Hamiltonian problem is just as large
as the original.
The sub-Planck scale makes the problem more consistent,
but not simpler.\\[6pt]

\textbf{The real contribution:}\\
A physical realisation --- a FFGFT torsion field
that physically solves Eq.~(\ref{eq:t0-discrete}) ---
would solve the problem in the time the field
takes to find its equilibrium state.
This is not an algorithmic optimisation,
but a change of realisation substrate.
Just as an optical spectrometer performs a Fourier transformation
at the speed of light ---
not through algorithm, but through physics.
\end{important}

% ============================================================
\section{Empirical Findings: What the Test Programmes Show}
\label{sec:empirical}
% ============================================================

Parallel to the mathematical formulation, four
interactive test programmes were developed and run
(BigInt-exact, no float artefacts).
All programmes are publicly accessible at:

\begin{center}
\url{https://github.com/jpascher/T0-Time-Mass-Duality/tree/main/2/html}
\end{center}

\begin{description}
  \item[\texttt{t0\_shor\_bigint.html}]
    BigInt-corrected Shor simulator ---
    exact modular arithmetic for arbitrary $N$,
    comparison FFGFT period search vs.\ classical trial division,
    benchmark with 10 test cases from $N=15$ to $N \approx 10^{18}$.

  \item[\texttt{t0\_shor\_hypothesis.html}]
    $\xi$-basis hypothesis test ---
    compares $\xi$-optimal bases with random bases
    on period minimality, statistical test over many $N$
    with win rate and median ratio $r_\text{random}/r_\xi$.

  \item[\texttt{t0\_xi\_num\_algebraisch.html}]
    $\xi_\text{num} = \lambda(N)/N$ distribution analysis ---
    cluster analysis over 200 semiprime $N$,
    comparison with FFGFT level hierarchy $\xipar^k$.

  \item[\texttt{t0\_primzahl\_periodizitaet.html}]
    Prime gaps, residue class patterns, $p{-}1$ smoothness
    and autocorrelation of the gap sequence ---
    four tests on the period structure of the primes themselves.
\end{description}

% ============================================================
\subsection{Finding 1: \texorpdfstring{$\xi_\text{num}$}{xi\_num} is Algebraic,
  not Geometric}
% ============================================================

The quantity $\xi_\text{num}(N) = \lambda(N)/N$
shows over 200 random semiprime $N$
three to five accumulation points:

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{rrl}
\toprule
$\xi_\text{num}$ & Share & Cause \\
\midrule
$\approx 1/2$ & 55\,\% & $\gcd(p-1,\,q-1) = 2$ \\
$\approx 1/4$ & 14\,\% & $\gcd(p-1,\,q-1) = 4$ \\
$\approx 1/6$ & 13\,\% & $\gcd(p-1,\,q-1) = 6$ \\
$\approx 1/12$ & 6\,\% & $\gcd(p-1,\,q-1) = 12$ \\
\bottomrule
\end{tabular}%
}
} % footnotesize
\end{center}

This is the harmonic series --- not a
FFGFT resonance structure, but the
\textbf{divisor structure of even numbers}.
All primes $> 2$ are odd,
so $p-1$ and $q-1$ are always even.
The $\gcd$ is always a multiple of~2.

\begin{keypoint}[$\xi_\text{num}$ is structurally different
  from $\xipar$]
$\xipar = 4/30000$ comes from the
3D tetrahedron geometry of physical space.

$\xi_\text{num}(N) = \lambda(N)/N$ comes from the
algebraic divisor structure of the prime factors of $N$.

Both are dimensionless and hierarchically structured ---
but they describe different structures.
The analogy is \emph{structural}, not \emph{parametric}.
\end{keypoint}

% ============================================================
\subsection{Finding 2: Primes Have No Global Period}
% ============================================================

The autocorrelation of prime gaps up to $2 \times 10^5$
shows no significant periodic structure ---
the gaps behave approximately like
uncorrelated noise, consistent with the
Riemann hypothesis.

What primes \emph{do} have:
\begin{itemize}
  \item \textbf{Symmetry structure} (Dirichlet):
    uniform distribution over all residue classes
    coprime to $m$ mod~$m$ --- no accumulation,
    but symmetry.
  \item \textbf{Characteristic gap distribution}:
    $\sim$73\,\% of all prime gaps are multiples
    of~6, because all primes $> 3$ lie on $6k \pm 1$.
  \item \textbf{Individual $\gcd$ structure}:
    Each prime pair $(p, q)$ has its own
    $\gcd(p-1, q-1)$ that determines $\lambda(N)$.
\end{itemize}

\begin{foundation}[FFGFT: Three spaces --- three different $\xi$ roles]
FFGFT distinguishes three mathematically different spaces,
in each of which a different $\xi$ parameter acts.
These are \textbf{not contradictions}, but complementary
descriptions of different aspects of the same theory:

\begin{center}
\resizebox{\textwidth}{!}{%
\begin{tabular}{p{2.5cm}p{2.2cm}p{3.5cm}p{4cm}}
\toprule
\textbf{Space} & \textbf{Parameter} & \textbf{Domain} & \textbf{Example} \\
\midrule
\textbf{Geometric 3D space}
(torus geometry) &
$\xipar \approx 1.333 \times 10^{-4}$ &
Length levels $L_N$; couplings between spatial scales &
Quantum dot scale $N \approx 8$; transistor boundary \\[8pt]
\textbf{Number space / algebra}
($\mathbb{Z}/N\mathbb{Z}$, Higgs sector) &
$\xi_\text{Higgs} \approx 1.038 \times 10^{-5}$ &
Algebraic field corrections; quantum state space;
Bell correlations; decoherence rates &
IBM hardware validation; $T_2$ hierarchy \\[8pt]
\textbf{Number-theoretic space}
($\mathbb{Z}/N\mathbb{Z}$ for primes) &
\emph{no universal parameter} &
Individual $\gcd(p-1,q-1)$ structure per prime pair;
no global $\xi$ &
Shor: period $r$ is $N$-specific \\
\bottomrule
\end{tabular}
}
\end{center}

\textbf{Consequence for Shor's algorithm:}
$\xipar$ applies to spatial resonances in physical position space ---
it cannot provide a universal shortcut for period search in
$\mathbb{Z}/N\mathbb{Z}$, because this space
carries no metric structure that $\xipar$ generated.
$\xi_\text{Higgs}$ applies to the algebraic field structure ---
it appears in the FFGFT-FFT formulation (Section~\ref{sec:ffgft-eigen})
as a damping factor of the eigenvalue equation, not as a period shortcut.

\textbf{Structural analogy remains:}
All three spaces know hierarchies and resonances,
all are basis-system independent ---
but at different levels with different parameters.
\end{foundation}

% ============================================================
\subsection{Finding 3: Why FFGFT Cannot Directly Form
  a Better FFT}
% ============================================================

A global $\xi$ that accelerates period search
does not exist --- because the primes carry no
global resonance parameter.

Why FFT is not directly translatable:
FFT requires a complete known data set.
Evaluating $f(x) = a^x \bmod N$ for all $x = 0 \ldots 2^n$
explicitly costs $O(N)$ --- the advantage would be gone.

The analogue superposition in a physical system
(wave field, photonic MZI network) solves this problem ---
but only if the system evaluates the function $f(x)$
\emph{physically}, not algorithmically.

\begin{important}[The core of the problem]
The bottleneck in Shor is not the
Fourier transformation --- it is the
\textbf{parallel evaluation of $f(x) = a^x \bmod N$
for exponentially many $x$}.

Classical FFT: all $f(x)$ must be known ---
$O(N)$ effort, unsolvable for RSA.

Quantum computer: prepares $\sum_x |x\rangle|f(x)\rangle$
in $O(n^3)$ steps --- through quantum parallelism.

FFGFT eigenvalue problem: does not ask for $f(x)$ for all $x$,
but: at which energies does the potential
$V(x) = -\xi \cdot f(x)/N$ have stable resonances?
That is a different question --- and possibly
one that a physical torsion field
answers directly, without explicit evaluation.
\end{important}

% ============================================================
\section{Worked Example: \texorpdfstring{$N=15$, $a=7$}{N=15, a=7} in the FFGFT View}
\label{sec:example-n15}
% ============================================================

\subsection{Classical Part: Resonance Strength}

Sought: smallest $r$ with $7^r \equiv 1 \pmod{15}$.

The FFGFT resonance strength evaluates each candidate:
\begin{equation}
  \text{Res}(r) \;=\;
  \frac{\exp(-\xipar \cdot r^2 / \Dfrak)}
       {|a^r \bmod N - 1| + 1}.
\end{equation}

\begin{center}
{\footnotesize
\adjustbox{max width=\textwidth}{%
\begin{tabular}{rrrl}
\toprule
$r$ & $7^r \bmod 15$ & Denominator & Resonance strength \\
\midrule
1 & 7  & $|7-1|+1 = 7$  & 0.14 \\
2 & 4  & $|4-1|+1 = 4$  & 0.25 \\
3 & 13 & $|13-1|+1 = 13$& 0.07 \\
\textbf{4} & \textbf{1}  & $|1-1|+1 = \mathbf{1}$  & \textbf{1.00} \\
\bottomrule
\end{tabular}%
}
} % footnotesize
\end{center}

At $r = 4$ the resonance peaks maximally ---
the period is found.

\subsection{Factor Extraction}

With $r = 4$ (even):
\begin{align}
  x &= 7^{r/2} \bmod 15 = 7^2 \bmod 15 = 49 \bmod 15 = 4, \\
  \gcd(x-1,\,15) &= \gcd(3,\,15) = \mathbf{3}, \\
  \gcd(x+1,\,15) &= \gcd(5,\,15) = \mathbf{5}.
\end{align}
$15 = 3 \times 5$ --- correct.

\subsection{FFGFT Eigenvalue Perspective}

In a physical realisation
(torsion field on sub-Planck lattice)
the system would simultaneously ``feel'' the entire potential
$V(n) = -\xipar \cdot (7^n \bmod 15)/15$ ---
not sequentially for $r = 1, 2, 3, 4$.
The resonance at $r = 4$ corresponds to a
localised eigenstate of the
tight-binding Hamiltonian.

% ============================================================
\section{Anderson Localisation: How the Field ``Freezes'' the Period}
\label{sec:anderson-detail}
% ============================================================

Anderson localisation explains the mechanism
behind the FFGFT-FFT conjecture.

\textbf{The pseudorandom potential:}
$V(n) = a^n \bmod N$ is deterministic but
locally jumpy --- like a disordered solid-state lattice.
Waves propagating through such disorder
are scattered at the jumps.

\textbf{Destructive interference almost everywhere:}
At most energies $E$ the scattered waves cancel each other ---
the wave cannot propagate stably.

\textbf{Constructive interference at $E_k \propto k/r$:}
Only at resonance frequencies that exactly match the
hidden period $r$ of the potential
does constructive interference occur ---
the eigenstate \emph{localises}.

\begin{foundation}[Anderson localisation as period search]
The wave function $\Psi_n$ concentrates
on a finite region and forms a
standing pattern --- the period is
``frozen'' into the system.

The physical system does not compute sequentially
$O(N)$ steps --- it ``locks'' into the
energetically most stable state
that physically represents the solution.

On the sub-Planck scale ($\ell_0 \approx 2 \times 10^{-39}$\,m)
the lattice is fine enough to interpret the jumps of
$a^n \bmod N$ not as errors but as
\textbf{geometric information}.
\end{foundation}

% ============================================================
\section{Connection to the Riemann Zeta Function}
\label{sec:zeta}
% ============================================================

\subsection{Pólya-Hilbert Conjecture}

The \textbf{Pólya-Hilbert conjecture} states:
the non-trivial zeros of $\zeta(s)$
are the eigenvalues of a self-adjoint
operator $\mathcal{H}$ --- the
``Riemann Hamiltonian''.

No natural physical system has been found so far
that generates this spectrum.

\subsection{FFGFT Candidate on Sub-Planck Lattice}

FFGFT proposes:
on the sub-Planck scale the fractal
spacetime structure ($\Dfrak = 2.999867$)
generates exactly those boundary conditions that the
Riemann operator needs.

The potential $V(n) = a^n \bmod N$ behaves
like a chaotic quantum system ---
and the energy levels of chaotic systems
statistically follow the same distributions
as the spacings of the zeros of $\zeta(s)$
(Montgomery-Odlyzko law).

\begin{keyresult}[Spectral connection: period and primes]
If the FFGFT eigenvalue problem and the
Riemann zeta function are based on the same
physical resonance principle, it follows:

\textbf{Factorisation is not a combinatorial
search problem} --- it is a
\textbf{spectroscopic measurement problem}.

One would not have to write a programme,
but measure the resonance frequency of a physical
spatial region modulated with the potential $V(n)$.
The period $r$ --- and thus the prime factors ---
appear as spectral lines.

\medskip
\textbf{Status:} This connection is
mathematically precisely formulable
(via the tight-binding Hamiltonian
and the Montgomery-Odlyzko law)
but not yet proven.
It is the open research question
of this document --- precisely formulated in
Section~\ref{sec:ffgft-conjecture}.
\end{keyresult}

\subsection{Why We Cannot Directly Measure This}

Thermal noise and the coarse spacetime structure
at the Planck scale ``smear'' the
fine resonances.
Only below the Planck scale ---
at $\ell_0 = \xipar \cdot \lP \approx 2 \times 10^{-39}$\,m ---
is the lattice fine enough to map the jumps
of the modulo function without information loss.

At this scale nature performs the QFT
``continuously'' --- as natural dynamics
of a wave system that makes periodicities
visible through coherent interference.

\begin{conclusionBox}[Overall balance Doc.~176]
\textbf{What is photonically fully realisable:}\\
Every step of Shor's algorithm is physically
executable by a photonic system at room temperature.
The FFGFT field equation~(\ref{eq:photon-wave})
describes this process mathematically exactly.
The MZI network \emph{is} the QFT, not its simulation.
The feedforward problem is an open engineering question,
not a physical prohibition.\\[6pt]

\textbf{What is not possible on a conventional computer:}\\
Simulating the FFGFT field equation on a digital computer.
The state space problem is exponential --- precisely why
it needs a physical system that solves the equation
by \emph{being} it.\\[6pt]

\textbf{What the test programmes show:}\\
A global $\xi$ parameter that accelerates period search
does not exist --- the period is
determined by $\gcd(p-1, q-1)$, not by
an external resonance. The FFGFT $\xi$ scan is
classical and insufficient for RSA-relevant $N$.\\[6pt]

\textbf{The open mathematical question:}\\
The FFGFT-FFT as an eigenvalue problem (tight-binding Hamiltonian
on sub-Planck lattice) is mathematically precisely formulated
but not yet proven --- specified in
Section~\ref{sec:ffgft-conjecture},
connection to the zeta function in Section~\ref{sec:zeta}.
\end{conclusionBox}

\begin{thebibliography}{99}

\bibitem{Shor1994}
Shor, P.\,W.
\textit{Algorithms for quantum computation: discrete logarithms and factoring.}
In \textit{Proc.\ 35th Annual Symp.\ on Foundations of Computer Science (FOCS)},
124--134 (IEEE, 1994).

\bibitem{Shor1997}
Shor, P.\,W.
\textit{Polynomial-time algorithms for prime factorization and discrete
logarithms on a quantum computer.}
SIAM J.\ Comput.\ \textbf{26}, 1484--1509 (1997).

\bibitem{Griffiths1996}
Griffiths, R.\,B. \& Niu, C.-S.
\textit{Semiclassical Fourier transform for quantum computation.}
Phys.\ Rev.\ Lett.\ \textbf{76}, 3228--3231 (1996).

\bibitem{Knill2001}
Knill, E., Laflamme, R. \& Milburn, G.\,J.
\textit{A scheme for efficient quantum computation with linear optics.}
Nature \textbf{409}, 46--52 (2001).

\bibitem{Reck1994}
Reck, M. et al.
\textit{Experimental realization of any discrete unitary operator.}
Phys.\ Rev.\ Lett.\ \textbf{73}, 58--61 (1994).

\bibitem{Prevedel2007}
Prevedel, R. et al.
\textit{High-speed linear optics quantum computing using active feed-forward.}
Nature \textbf{445}, 65--69 (2007).

\bibitem{NIST2024}
National Institute of Standards and Technology (NIST).
\textit{Post-Quantum Cryptography Standards.}
FIPS 203--205 (2024). \url{https://csrc.nist.gov/pubs}

\bibitem{Fowler2012}
Fowler, A.\,G. et al.
\textit{Surface codes: towards practical large-scale quantum computation.}
Phys.\ Rev.\ A \textbf{86}, 032324 (2012).

\bibitem{Anderson1958}
Anderson, P.\,W.
\textit{Absence of diffusion in certain random lattices.}
Phys.\ Rev.\ \textbf{109}, 1492--1505 (1958).

\bibitem{Montgomery1973}
Montgomery, H.\,L.
\textit{The pair correlation of zeros of the zeta function.}
Analytic Number Theory, Proc.\ Sympos.\ Pure Math.\ \textbf{24},
181--193 (AMS, 1973).

\bibitem{Berry1999}
Berry, M.\,V. \& Keating, J.\,P.
\textit{The Riemann zeros and eigenvalue asymptotics.}
SIAM Rev.\ \textbf{41}, 236--266 (1999).

\bibitem{Hofstadter1976}
Hofstadter, D.\,R.
\textit{Energy levels and wave functions of Bloch electrons in rational
and irrational magnetic fields.}
Phys.\ Rev.\ B \textbf{14}, 2239--2249 (1976).

\end{thebibliography}
