% ============================================================
%  Dok 255 | Information as Topologically Frozen
%           Kinetic Energy
%  Chapter content EN
% ============================================================

\title{Information as Topologically Frozen Kinetic Energy\\[0.4em]
\large Landauer's Principle and Vopson's Equivalence as Consequences\\
of \(T^4\) Geometry in FFGFT}
\author{Johann Pascher}
\date{May 2026}
\maketitle

\begin{abstract}
In the time-mass duality (FFGFT), the foundational relation is
\(\tilde{T} \cdot m = 1\),
where \(\tilde{T} = 1/m\) is the time variable dual to mass \(m\)
on the 4D identification torus \(T^4\).
This relation enforces a natural twofold division of energy:
static energy as topologically enclosed kinetic energy
(winding numbers on \(T^4\)) and free kinetic energy
(motion through \(T^4\)).
From this division it follows without additional postulates
that information is topologically frozen kinetic energy.
Landauer's principle \cite{Landauer1961} and Vopson's
mass-information equivalence \cite{Vopson2019}
are derived as geometric consequences of the \(T^4\) structure,
not as independent postulates.
The quantisation of information follows from the discreteness
of the winding numbers.
We work in natural units with \(c = \hbar = k_B = 1\)
unless stated otherwise.
\end{abstract}

\tableofcontents
\newpage

% ------------------------------------------------------------
\section{Starting Point: Two Energy Types in \(\tilde{T} \cdot m = 1\)}
% ------------------------------------------------------------

The foundational relation of FFGFT \cite{Pascher2026},
\begin{equation}
  \tilde{T} \cdot m = 1,
\end{equation}
couples the time variable \(\tilde{T} = 1/m\) dual to mass \(m\)
on the 4D identification torus \(T^4\).
This structure gives rise to two qualitatively distinct forms of energy:

\paragraph{Static energy.}
Energy bound to rest mass: \(E_0 = mc^2\).
It corresponds to topologically stable winding numbers on \(T^4\) --
geometric invariants preserved without interaction.
This energy is not statistical; it is a discrete topological state.
It does not contribute to thermodynamic entropy as long as the
topology remains intact.

\paragraph{Dynamic kinetic energy.}
Free kinetic energy -- for massless particles (photons) the only
energy form \(E = hf\), for massive particles the contribution
beyond the rest mass.
This energy is statistically distributable and exchanges
with thermodynamic systems.

The \textbf{photon} is the limiting case:
no rest mass, no winding number for mass, purely kinetic,
purely statistical. It is the natural carrier of Shannon information
in the sense of Wheeler \cite{Wheeler1990}.

% ------------------------------------------------------------
\section{Mass as Topologically Frozen Kinetic Energy}
% ------------------------------------------------------------

\subsection{The Core Thesis}

Before any mass formation, only kinetic energy exists.
Mass arises when kinetic energy is enclosed by the \(T^4\) topology
into a stable winding structure.

\begin{center}
\emph{Mass is topologically frozen kinetic energy.}
\end{center}

\paragraph{Definition of winding number.}
Let \(\gamma\) be a closed path on \(T^4\).
The winding number \(w \in \mathbb{Z}\) is the integer homotopy class
\([\gamma] \in \pi_1(T^4) \cong \mathbb{Z}^4\).
Mass corresponds to a stable combination of such winding numbers.
In FFGFT, all leptons carry specific winding exponents \(p_i\)
that follow from the geometry of \(T^4\) \cite{Pascher2026}.

\subsection{Visualisation: Free and Frozen Kinetics}

\begin{figure}[htbp]
\centering
\begin{adjustbox}{max width=\textwidth}
\begin{tikzpicture}[
  node distance=1.0cm,
  every node/.style={font=\small},
  box/.style={draw, rounded corners=4pt, minimum width=2.4cm,
              minimum height=1.0cm, align=center, fill=blue!8},
  massbox/.style={draw, rounded corners=4pt, minimum width=2.4cm,
                  minimum height=1.0cm, align=center, fill=orange!15},
  arr/.style={-{Stealth[length=6pt]}, thick},
  redarr/.style={-{Stealth[length=6pt]}, thick, red!70!black},
]

\node[box] (kin) {Free kinetic\\energy\\(statistical)};
\node[massbox, right=1.6cm of kin] (top) {Topological\\enclosure\\(winding \(w\))};
\node[massbox, right=1.6cm of top] (mass) {Rest mass /\\Information\\(static)};

\draw[arr] (kin) -- node[above,font=\footnotesize]{Freeze} (top);
\draw[arr] (top) -- node[above,font=\footnotesize]{Store} (mass);
\draw[redarr, bend right=35] (mass) to
  node[below,font=\footnotesize,red!70!black]{Erase: \(E_L = k_BT\ln 2\)}
  (kin);

\node[below=0.5cm of kin, font=\footnotesize, text=blue!70!black]
  {Photon: always here};
\node[below=0.5cm of mass, font=\footnotesize, text=orange!80!black]
  {Electron: here + left};

\end{tikzpicture}
\end{adjustbox}
\caption{Energy division in FFGFT.
  Free kinetic energy (blue) can be transferred into static
  mass/information (orange) through topological enclosure.
  Erasure (red arrow) releases the frozen energy as heat --
  Landauer's principle.
  The photon remains permanently in the kinetic sector.}
\label{fig:energy}
\end{figure}

\subsection{Analogy: Standing Wave}

A standing wave on a string is kinetic -- the string vibrates.
Yet the pattern appears static.
Analogously, the rest mass of an electron is the standing wave
of a topologically enclosed oscillation on \(T^4\).
The \enquote{stillness} of the rest mass is the stillness of the
pattern, not of the substance.

\subsection{The Higgs Mechanism in This Picture}

In the Standard Model, the Higgs mechanism imparts mass to particles
through symmetry breaking. In the \(T^4\) language, this corresponds
to the selection of stable topological sectors: kinetic energy is
enclosed in winding structures.
The FFGFT relation \(\xi = \lambda_h^2 v^2 / (16\pi^3 m_h^2)\)
is the algebraic expression of this geometric selection process --
not its replacement.

% ------------------------------------------------------------
\section{Information as Topological Enclosure}
% ------------------------------------------------------------

If mass is topologically frozen kinetic energy, then for information:

\begin{center}
\renewcommand{\arraystretch}{1.4}
\adjustbox{max width=\textwidth}{%
\begin{tabular}{lll}
\toprule
\textbf{Operation} & \textbf{Geometric} & \textbf{Energetic} \\
\midrule
Create  & Winding number \(w \to w\pm1\) & Freeze kinetic energy \\
Store   & \(w = \mathrm{const}\)         & Maintain topology \\
Erase   & \(w \to 0\)                    & Release \(E_L = k_BT\ln2\) \\
\bottomrule
\end{tabular}%
}
\end{center}

\paragraph{Definition of information content.}
The information content \(I(\gamma)\) of a topological state \(\gamma\)
is the minimum number of bits required to specify its winding class
\([\gamma] \in \mathbb{Z}^4\).
\(I\) is an integer.
Shannon entropy arises as the statistical expectation value over
ensembles of such states -- analogous to temperature as the mean
over discrete kinetic energies.

% ------------------------------------------------------------
\section{Landauer's Principle from \(T^4\) Geometry}
% ------------------------------------------------------------

\subsection{The Classical Principle}

Landauer (1961) showed that erasing one bit irreversibly dissipates
heat to the environment \cite{Landauer1961}:
\begin{equation}
  E_L = k_B T \ln 2 \quad \text{per bit.}
  \label{eq:landauer}
\end{equation}
This was experimentally confirmed by Bérut et al.\ (2012)
using a colloidal particle in a double-well potential \cite{Berut2012}.

\subsection{Geometric Derivation}

Let a minimal topological distinction on \(T^4\) be given by two
states with winding number difference \(\Delta w = 1\).
The corresponding frozen kinetic energy is
\(E_0 = \Delta w \cdot \epsilon_0\) with a fundamental energy
quantum \(\epsilon_0\).

At thermal equilibrium at temperature \(T\), the Boltzmann factor
governs the probability of dissolving this distinction.
The energy released is not less than \(k_B T \ln 2\),
since this is the minimum work required at temperature \(T\)
to irreversibly erase a binary distinction (from the second law).

The \(T^4\) topology enforces \(\epsilon_0 = k_B T \ln 2\):
the frozen kinetic energy of a minimal winding difference is the same
physical quantity as the minimal erasure work from the second law --
two expressions for the same quantity, not a new assumption.
Landauer's principle is thus a geometric consequence --
not an independent thermodynamic postulate.

% ------------------------------------------------------------
\section{Vopson's Mass-Information Equivalence as a Consequence}
% ------------------------------------------------------------

Vopson (2019) derived empirically from Landauer's principle
the mass-information equivalence \cite{Vopson2019}:
\begin{equation}
  M_I = \frac{k_B T \ln 2}{c^2} \quad \text{per bit.}
  \label{eq:vopson}
\end{equation}
In the \(T^4\) language, \(M_I\) is the mass corresponding to
a minimal topological winding difference \(\Delta w = 1\)
at temperature \(T\).

\textbf{Vopson discovered empirically what FFGFT explains geometrically.}
The derivation hierarchy is:
\begin{equation}
  T^4\text{-topology} \;\longrightarrow\;
  \Delta w = 1 \;\longrightarrow\;
  E_L = k_B T \ln 2 \;\longrightarrow\;
  M_I = E_L / c^2.
\end{equation}

% ------------------------------------------------------------
\section{Quantisation of Information}
% ------------------------------------------------------------

Winding numbers on \(T^4\) are discrete integers
(\(\pi_1(T^4) \cong \mathbb{Z}^4\)).
This immediately implies:

\begin{itemize}
  \item Information is naturally quantised --
        not as a convention but as a topological necessity.
  \item The minimal information unit is \(\Delta w = 1\)
        (one winding change in one of the four torus directions).
  \item The spatial scale of this minimal unit is the
        fundamental length of FFGFT:
        \begin{equation}
          L_0 = \xi \cdot l_P \approx 2.15 \times 10^{-39}\,\text{m},
        \end{equation}
        where \(\xi = 4/3 \times 10^{-4}\) is the universal geometric
        parameter and \(l_P\) is the Planck length.
        \(L_0\) is thus the smallest physically meaningful
        granularity of information in FFGFT -- below this scale
        no topological distinction is possible.
  \item Continuous Shannon entropy arises as a statistical
        average over discrete topological states.
\end{itemize}

% ------------------------------------------------------------
\section{The Photon as the Limiting Case}
% ------------------------------------------------------------

The photon is the only massless state in the FFGFT spectrum that
carries no topological winding structure for mass.
It therefore remains permanently in the kinetic sector
(cf.\ Fig.~\ref{fig:energy}).

\begin{itemize}
  \item The photon is the natural carrier of Shannon information
        (\enquote{It from Bit} \cite{Wheeler1990}).
  \item Photonic information cannot be frozen into rest mass
        without interaction with massive matter.
  \item The speed of light \(c\) limits the transmission rate
        of free kinetic information -- as a geometric consequence
        of \(T^4\), not as a postulate.
\end{itemize}

% ------------------------------------------------------------
\section{Connection to the Distinguishability Framework}
% ------------------------------------------------------------

Haskins (2026, submitted to Foundations of Physics \cite{Haskins2026})
describes an emergence hierarchy:
\begin{align*}
C_a\Psi = 0 \;&\to\; \text{multiplicity} \;\to\;
\text{distinguishability collapse} \\
&\to\; \text{equivalence structure} \;\to\;
\text{coarse-graining projection} \\
&\to\; \text{degeneracy structure} \;\to\;
\text{structural entropy ordering.}
\end{align*}

In the \(T^4\) language, the distinguishability collapse can be
interpreted as the moment when two kinetic states fall into the
same winding class through topological enclosure -- becoming
indistinguishable. The constraint condition \(C_a\Psi = 0\) then
selects the topologically stable sectors on \(T^4\).

\textbf{This connection is an interpretive bridge, not a derivation.}
A formal correspondence between Haskins' constraints and the
\(T^4\) winding numbers is the subject of further work.

% ------------------------------------------------------------
\section{Summary}
% ------------------------------------------------------------

\begin{enumerate}
  \item \(\tilde{T} \cdot m = 1\) enforces two energy types:
        topologically enclosed (static) and free (kinetic).
  \item Mass is topologically frozen kinetic energy.
  \item Information is frozen kinetic energy in topological form
        (\(\Delta w = 1\) = 1 bit).
  \item Landauer's principle follows geometrically from the
        Boltzmann factor for winding dissolution;
        \(E_L = k_BT\ln 2\) is not a postulate.
  \item Vopson's equivalence \(M_I = k_BT\ln2/c^2\) is a direct
        consequence -- Vopson discovered empirically what FFGFT explains.
  \item Quantisation of information follows from
        \(\pi_1(T^4)\cong\mathbb{Z}^4\).
  \item The photon is the limiting case: purely kinetic, purely
        statistical, natural information carrier.
\end{enumerate}

\bigskip
\noindent
\textbf{Methodological classification:}
This derivation constitutes a bridge (algebraically demonstrable
from \(\tilde{T}\cdot m=1\) and the \(T^4\) topology).
What it achieves: Landauer and Vopson are not independent postulates.
What it does not achieve: an experimental distinction from other theories
that reproduce the same equations.
Specific predictions would be needed for that (e.g.\ deviations at
very low temperatures or in strong gravitational fields).

\bigskip
\noindent
\textbf{Integration in the corpus.}
Doc.~257 refines the derivation given here as a special case of the
thermodynamic scale: the winding quantum \(\Delta w = 1\) is the
scale-universal unit of information, while the associated energy
\(E_\text{bit}(L) = \hbar c/L\) is scale-specific
(cf.\ also Doc.~184, energy hierarchy \(E_N = \hbar c/L_N\)).
Landauer's \(E_L = k_B T \ln 2\) is the special case at the
temperature--length scale on which these two quantities coincide.
Doc.~261 places the energy bipartition used here (frozen/free)
within the broader static/dynamic demarcation: the topologically
frozen side lives on the static layer~1 (compact \(T^4\), winding
numbers); the free kinetic side belongs to the dynamic layer~2
(arrow time, embedding price \(c,\hbar,\varepsilon_0\)).

\bigskip
\begin{flushright}
\textit{Johann Pascher, Upper Austria, May 2026}
\end{flushright}

% ------------------------------------------------------------
\begin{thebibliography}{99}

\bibitem{Landauer1961}
R.~Landauer,
\textit{Irreversibility and heat generation in the computing process},
IBM Journal of Research and Development \textbf{5}(3), 183--191 (1961).

\bibitem{Berut2012}
A.~Bérut, A.~Arakelyan, A.~Petrosyan, S.~Ciliberto,
R.~Dillenschneider, E.~Lutz,
\textit{Experimental verification of Landauer's principle linking
information and thermodynamics},
Nature \textbf{483}, 187--189 (2012).

\bibitem{Vopson2019}
M.\,M.~Vopson,
\textit{The mass-energy-information equivalence principle},
AIP Advances \textbf{9}(9), 095206 (2019).

\bibitem{Wheeler1990}
J.\,A.~Wheeler,
\textit{Information, physics, quantum: The search for links},
in W.~Zurek (ed.), \textit{Complexity, Entropy, and the Physics
of Information}, Addison-Wesley, 3--28 (1990).

\bibitem{Haskins2026}
D.~Haskins,
\textit{Admissibility-constrained distinguishability and the emergence
of coarse-grained structure},
Foundations of Physics (submitted, 2026).

\bibitem{Pascher2026}
J.~Pascher,
\textit{Fundamental Fractal-Geometric Field Theory (FFGFT) --
T0 Time-Mass Duality},
Zenodo, DOI: 10.5281/zenodo.20474821 (2026).

\end{thebibliography}
