% ============================================================
%  Dok 258 | The Recurrence of 2/3:
%           Koide Projectors, FFGFT Ladder and ε-Deformation
%  Chapter content EN
% ============================================================

\title{The Recurrence of \(2/3\):\\[0.4em]
\large Koide Projectors, Complement Step,\\
FFGFT Ladder and \(D = 3+\varepsilon\) Deformation}
\author{Johann Pascher\\[0.3em]
\small In dialogue with P.~Austin,
\textit{A Purely Algebraic Short Note on the Repeated Appearance of 2/3}
(May 2026)}
\date{May 2026}
\maketitle

\begin{abstract}
At exactly \(D = 3\), three distinct mathematical structures yield the
value \(2/3\): the Koide equal-projector condition \(A = B\) between
democratic and orthogonal projection components,
the complement step \(1 - 1/D\),
and the geometric FFGFT lepton ladder with ratio \(q = 2/3\).
A \(D = 3+\varepsilon\) deformation separates the three roads.
This document shows:
(i) the FFGFT ladder is geometric, not arithmetic;
(ii) the exponent step is tied to the integer topological \(D=3\),
not to the fractal dimension \(D_f\);
(iii) the FFGFT ladder predicts \(Q \approx 0.6677\)
(\(0.16\,\%\) below \(2/3\)) without Koide input --
the exact experimental value \(Q = 2/3\) confirms the exponent structure
from an independent direction.
\end{abstract}

\tableofcontents

\section*{Notation}
\addcontentsline{toc}{section}{Notation}

\begin{center}
\renewcommand{\arraystretch}{1.4}
\adjustbox{max width=\textwidth}{%
\begin{tabular}{ll}
\toprule
\textbf{Symbol} & \textbf{Meaning} \\
\midrule
\(\xi = 4/30000\) & Fundamental FFGFT parameter \cite{Pascher2026} \\
\(v = 246.22\,\text{GeV}\) & Higgs vacuum expectation value \\
\(m_i = r_i\,\xi^{p_i}\,v\) & FFGFT mass formula \cite{PascherDok006} \\
\(r_i\) & Rational prefactors of the leptons \\
\(p_i\) & Rational exponents of the leptons \cite{PascherDok051} \\
\(D = 3\) & Topological (integer) spatial dimension of \(T^4\) \\
\(D_f^{\,\text{space}} = 3-\xi\) & Fractal spatial dimension (local metric) \cite{Pascher2026} \\
\(D_f^{\,\text{eff}} \approx 2.973\) & Effective fractal dimension (scale flow) \\
\(K_{\text{frak}}\) & Fractal correction \(= (D_f^{\,\text{eff}}/3)^{D_f^{\,\text{eff}}/2}\) \\
\(x_i = \sqrt{m_i}\) & Square-root lepton mass \\
\(u = (1,1,1)^T\) & Democratic unit vector \\
\(P = uu^T/3\) & Democratic projector \\
\(P^\perp = I - P\) & Residual projector \\
\(A = x^TPx\) & Democratic quadratic component \\
\(B = x^TP^\perp x\) & Residual quadratic component \\
\(Q\) & Koide quantity \(= (A+B)/(3A)\) \cite{Koide1983} \\
\(\Delta_K = 3Q-2\) & Koide residual diagnostic \\
\(\xi_{\text{Koide}}\) & Value of \(\xi\) for exact \(Q = 2/3\) \\
\(\alpha\) & Fine-structure constant \\
\bottomrule
\end{tabular}%
}
\end{center}

\newpage

% ------------------------------------------------------------
\section{Starting Point: Three Roads to \(2/3\)}
% ------------------------------------------------------------

At exactly \(D = 3\), several independent principles produce the same
numerical value:
\begin{equation}
  1 - \frac{1}{D} = \frac{2}{3}, \qquad
  \frac{2}{D} = \frac{2}{3}, \qquad
  \frac{1}{2}\!\left(1 + \frac{1}{D}\right) = \frac{2}{3}.
\end{equation}
The useful instrument for distinguishing them is the formal deformation
\(D = 3+\varepsilon\): principles that coincide at \(D = 3\) separate under
this continuation.

The following table summarises the three continuations:

\begin{center}
\renewcommand{\arraystretch}{1.5}
\adjustbox{max width=\textwidth}{%
\begin{tabular}{lll}
\toprule
\textbf{Principle} & \textbf{Formula} & \textbf{Expansion at \(D=3+\varepsilon\)} \\
\midrule
Koide equal-projector & \(\dfrac{2}{D}\)
  & \(\dfrac{2}{3} - \dfrac{2\varepsilon}{9} + O(\varepsilon^2)\) \\[6pt]
Complement step & \(1 - \dfrac{1}{D}\)
  & \(\dfrac{2}{3} + \dfrac{\varepsilon}{9} + O(\varepsilon^2)\) \\[6pt]
Interval midpoint & \(\dfrac{1}{2}\!\left(1+\dfrac{1}{D}\right)\)
  & \(\dfrac{2}{3} - \dfrac{\varepsilon}{18} + O(\varepsilon^2)\) \\
\bottomrule
\end{tabular}%
}
\end{center}

The roads separate at first order -- the complement step rises,
the Koide equilibrium road and the interval midpoint fall.

% ------------------------------------------------------------
\section{The Koide Relation as a Projector Statement}
% ------------------------------------------------------------

For the charged leptons define \(x_i = \sqrt{m_i}\) and write the Koide
quantity as
\begin{equation}
  Q = \frac{\sum_i m_i}{\left(\sum_i \sqrt{m_i}\right)^2}
    = \frac{x^Tx}{(u^Tx)^2},
  \quad u = (1,1,1)^T.
\end{equation}
With the democratic projector \(P = uu^T/3\) and residual projector
\(P^\perp = I - P\):
\[
  A = x^TPx = \frac{(u^Tx)^2}{3}, \quad B = x^TP^\perp x,
  \quad Q = \frac{A+B}{3A}.
\]
The Koide value \(Q = 2/3\) is equivalent to the
\textbf{equal-projector condition} \(A = B\):
the square-root mass vector splits into a democratic and a residual
component of equal quadratic weight.

Under formal \(D\)-dimensional extension with \(Q_D = 2/D\):
\begin{equation}
  Q_{3+\varepsilon} = \frac{2}{3+\varepsilon}
  = \frac{2}{3} - \frac{2\varepsilon}{9} + O(\varepsilon^2)
  \quad \text{(descending)}.
\end{equation}

% ------------------------------------------------------------
\section{The FFGFT Ladder is Geometric, not Arithmetic}
\label{sec:ladder}
% ------------------------------------------------------------

The canonical charged-lepton parameters in FFGFT
\cite{Pascher2026,PascherDok006} are:
\begin{equation}
  (r_e,\, r_\mu,\, r_\tau) = \left(\tfrac{4}{3},\, \tfrac{16}{5},\, \tfrac{25}{9}\right),
  \qquad
  (p_e,\, p_\mu,\, p_\tau) = \left(\tfrac{3}{2},\, 1,\, \tfrac{2}{3}\right),
\end{equation}
with \(m_i = r_i\,\xi^{p_i}\,v\), \(\xi = 4/30000\),
\(v = 246\,\text{GeV}\) (Higgs vacuum value).

The exponents \(\bigl(\tfrac{3}{2}, 1, \tfrac{2}{3}\bigr)\) do
\emph{not} form a uniform \(1/3\) ladder -- the gaps are
\(p_e - p_\mu = 1/2\) and \(p_\mu - p_\tau = 1/3\).
The resolution: the ladder is \textbf{geometric} with constant ratio
\(q = 2/3\):
\begin{equation}
  p_{n+1} = \frac{2}{3}\,p_n, \qquad
  \frac{3}{2} \xrightarrow{\times 2/3} 1 \xrightarrow{\times 2/3} \frac{2}{3}.
\end{equation}
The unequal differences \(1/2\) and \(1/3\) are \emph{consequences} of a
constant ratio, not independent rules.

\paragraph{Two equivalent readings.}
\begin{itemize}
  \item \textbf{Ratio reading.} \(q = 2/3\) is the inverse of the
        tetrahedral geometry factor \(3/2\). The same number that orders
        the ladder is, numerically, the Koide value.
  \item \textbf{Complement reading.} At the \(\mu\to\tau\) rung
        \(p_\tau = 1 - 1/D = 2/3\) with \(D=3\).
        This places FFGFT on the complement-step road --
        \emph{not} on the equal-projector road \(2/D\).
\end{itemize}

The electron at \(p_e = 3/2 = 1 + 1/(D-1)\) is a half-integer rung --
a geometric midpoint between winding levels (the spin-winding contribution
\cite{PascherDok051}), not a full winding step. That is the structural origin of the \(1/2\) gap.

% ------------------------------------------------------------
\section{Topological \(D=3\) versus the Fractal Dimension}
\label{sec:df}
% ------------------------------------------------------------

FFGFT carries two derived fractal dimensions:
\begin{equation}
  D_f^{\,\text{space}} = 3 - \xi \approx 2.9998667
  \quad\text{(local metric; GRB time-of-flight)},
\end{equation}
\begin{align*}
  D_f^{\,\text{eff}} &\approx 2.973\\
  &\quad\text{(cumulative scale flow, Planck to electroweak)}.
\end{align*}
Both are derived, not assumed.

\paragraph{Why no \(\xi/9\) correction reaches the Koide quantity.}
The Koide quantity \(Q\) is a pure mass \emph{ratio}. Every scale-dependent
factor -- the vacuum value \(v\), the fractal correction
\(K_{\text{frak}} = (D_f^{\,\text{eff}}/3)^{D_f^{\,\text{eff}}/2}\),
and any \(D_f\)-level shift -- is common to all three leptons and cancels
in \(Q\). Fractal corrections attach to \emph{absolute} scales, never to
ratios.

The exponent step is therefore tied to the integer, topological \(D=3\).
The shift \(2/3 - \xi/9\) from the \(D_f\) road is a real effect on
absolute predictions; it simply does not enter \(Q\).

% ------------------------------------------------------------
\section{Forced or Merely Fitted? An Honest Answer}
% ------------------------------------------------------------

\subsection*{What is structurally forced}

The mass \emph{ratios} are not fitted. Two points:
\begin{itemize}
  \item \(m_\mu/m_e\) follows two independent roads that agree:
        geometrically from the ladder
        (\(\tfrac{12}{5}\,\xi^{-1/2} \approx 207.8\))
        and fractally via \(K_{\text{frak}}\) (\(\approx 206.8\)).
        The agreement fixes \(K_{\text{frak}}\) uniquely --
        a consistency test, not a fit.
  \item In the compact representation the coefficients are not free
        rationals: they are constructed so that \(\alpha\) cancels
        exactly. The rationals are \(\alpha\)-geometric invariants.
\end{itemize}

\subsection*{What the ladder does not force}

The ladder does not force the equal-projector condition \(A = B\) exactly.
Inserting the FFGFT masses into the Koide formula gives \cite{PascherDok192}:
\begin{equation}
  Q_{\text{FFGFT}} \approx 0.6677,
  \qquad
  \Delta_K = 3Q_{\text{FFGFT}} - 2 \approx +0.003
\end{equation}
(0.16\,\% below the exact value \(2/3\)).

The reason is structural: the Koide denominator
\(\bigl(\sum\sqrt{m_i}\bigr)^2\) generates cross-terms with exponents
\begin{equation}
  \xi^{5/4}, \quad \xi^{13/12}, \quad \xi^{5/6},
\end{equation}
none of which is a multiple of \(1/3\). They lie \emph{outside} the FFGFT
structure space \(\{p\} \subset \tfrac{1}{3}\mathbb{Z}\).
Exact \(Q = 2/3\) would require
\(\xi_{\text{Koide}} \approx 1.372\times10^{-4}\), about \(2.9\,\%\) larger.

\textbf{The honest position:}
The ladder \emph{predicts} \(Q\) to \(0.16\,\%\) from
\((r_i, p_i, \xi)\) with no Koide input.
The exact experimental \(Q = 2/3\) then \emph{confirms} the exponent
structure from an independent direction -- neither fitted into FFGFT nor
algebraically forced by it. The small residual lies precisely where the
cross-term analysis predicts.

% ------------------------------------------------------------
\section{The Explicit Map FFGFT \texorpdfstring{\(\to\)}{→} Koide}
% ------------------------------------------------------------

The three structures -- the Koide projector form, the FFGFT \(\xi\)-ladder,
and Paul's 24-cell rank split\footnote{%
P.~Phillips (IPI correspondence, May 2026 \cite{Phillips2026}) postulates a
\(24\)-dimensional mediation space with an involution \(J\),
\(J^2 = I\), whose projectors \(P_\pm = (I \pm J)/2\) have ranks
\(\operatorname{rank}(P_-) = 16\) and \(\operatorname{rank}(P_+) = 8\).
This yields the ratios \(8/24 = 1/3\) and \(16/24 = 2/3\)
as a pure rank statement, independent of masses or exponents.
The geometric motivation is the regular 24-cell polytope (24 vertices
in \(\mathbb{R}^4\)) whose symmetry group \(F_4\) admits a natural
\(8+16\) splitting of the weight space.
A formal map to FFGFT quantities has not yet been established.} --
are three distinct primitive objects.
A relation between them must be exhibited by a map, not by a shared numeral.

The FFGFT-to-Koide map is:
\begin{equation}
  (r_i, p_i, \xi)
  \;\longmapsto\;
  x_i = \sqrt{r_i}\,\xi^{p_i/2}\,\sqrt{v}
  \;\longmapsto\;
  (A, B)
  \;\longmapsto\;
  Q_{\text{FFGFT}} = \frac{\sum_i r_i\,\xi^{p_i}}
  {\bigl(\sum_i \sqrt{r_i}\,\xi^{p_i/2}\bigr)^2}.
\end{equation}
Since \(\sqrt{v}\) cancels, the map is explicit and trigonometry-free.

The \(\Delta_K\) discriminator:
\begin{equation}
  \Delta_K = 3Q_{\text{FFGFT}} - 2 = \frac{B}{A} - 1 \approx +0.003
\end{equation}
confirms that the ladder road and the equal-projector road meet near \(2/3\)
and separate -- exactly as the \(\varepsilon\)-deformation predicts.

% ------------------------------------------------------------
\section{Summary}
% ------------------------------------------------------------

\begin{enumerate}
  \item At \(D = 3\) three roads converge to \(2/3\);
        the \(D = 3+\varepsilon\) deformation separates them.
  \item The FFGFT ladder
        \(\bigl(\tfrac{3}{2}, 1, \tfrac{2}{3}\bigr)\)
        is geometric with ratio \(q = 2/3\);
        the unequal gaps \(1/2\) and \(1/3\) are consequences.
  \item FFGFT lies on the complement road
        \(p_\tau = 1 - 1/D\), not on the equal-projector road \(2/D\).
  \item Fractal corrections (\(D_f\)) cancel in \(Q\);
        the step is tied to topological \(D = 3\).
  \item The ladder predicts \(Q \approx 0.6677\)
        (\(0.16\,\%\)) without Koide input;
        the residual arises from cross-term exponents outside
        \(\tfrac{1}{3}\mathbb{Z}\).
  \item Exact \(Q = 2/3\) would require
        \(\xi_{\text{Koide}} \approx 1.372\times10^{-4}\);
        the agreement is a confirmation, not a fit.
\end{enumerate}

\bigskip
\noindent
\textbf{Methodological classification:}
The algebraic derivations in Sections~\ref{sec:ladder}--\ref{sec:df}
are bridges (directly from the ladder structure and torus topology).
The connection to Paul's 24-cell rank split is a plausibility sketch;
a formal map requires further elaboration.

\bigskip
\begin{flushright}
\textit{Johann Pascher, Upper Austria, May 2026}
\end{flushright}

\begin{thebibliography}{99}

\bibitem{Phillips2026}
P.~Phillips,
\textit{IPI correspondence: 24-dimensional mediation space and
\(1/3 + 2/3\) rank split},
unpublished private communication, IPI group (May 2026).

\bibitem{Austin2026}
P.~Austin,
\textit{A Purely Algebraic Short Note on the Repeated Appearance of 2/3:
Koide, Projectors, Complements, FFGFT, and \(n+\varepsilon\) Deformation},
IPI correspondence (May 2026).

\bibitem{Koide1983}
Y.~Koide,
\textit{A fermion-boson composite model of quarks and leptons},
Physics Letters B \textbf{120}(1--3), 161--165 (1983).

\bibitem{PascherDok006}
J.~Pascher,
\textit{Dok.~006 -- Fundamental Parameter Table of FFGFT},
in: FFGFT corpus, Zenodo DOI: 10.5281/zenodo.20474821 (2026).

\bibitem{PascherDok051}
J.~Pascher,
\textit{Dok.~051 -- Spin-winding contribution and electron exponent
\(p_e = 3/2\)},
in: FFGFT corpus, Zenodo DOI: 10.5281/zenodo.20474821 (2026).

\bibitem{PascherDok192}
J.~Pascher,
\textit{Dok.~192 -- Koide analysis: \(Q_{\text{FFGFT}} \approx 0.6677\)
and non-closure theorem},
in: FFGFT corpus, Zenodo DOI: 10.5281/zenodo.20474821 (2026).

\bibitem{Pascher2026}
J.~Pascher,
\textit{Fundamental Fractal-Geometric Field Theory (FFGFT) --
T0 Time-Mass Duality},
Zenodo, DOI: 10.5281/zenodo.20474821 (2026).

\end{thebibliography}
