% ============================================================
%  Static Geometry and the SI Projection
%  Why natural units require no fractal corrections
%  Chapter content EN
%  Sourced: Dok. 011, 012, 013, 014, 015, 041, 044, 116, 133, 193, 258
% ============================================================

\title{Dok.~261 — Static Geometry and the SI Projection:\\
Why Natural Units Require No Fractal Corrections}
\author{Johann Pascher}
\date{May 2026}
\maketitle

\begin{center}
\textit{Context: Dok.~011 (fine structure), Dok.~013/014 (SI \& natural units),
Dok.~116 (Koide), Dok.~133 (fractal correction)} \\[2pt]
\textit{FFGFT archive: DOI 10.5281/zenodo.20474821}
\end{center}

\tableofcontents
\newpage

%=============================================================
\section{Setting}
%=============================================================

The 2019 SI reform fixed four constants ($c$, $\hbar$, $e$, $k_B$) to exact values
and thereby turned most dimensionful quantities into mere unit definitions. What
remains as \emph{genuine} empirical input are the dimensionless constants -- above
all the fine-structure constant $\alpha$, whose value is still measured after the
reform ($\mu_0$, $\varepsilon_0$ and $\alpha$ remained measured quantities). FFGFT
derives these dimensionless inputs as well, from the single parameter
$\xipar = \tfrac{4}{3}\times 10^{-4}$.

This document collects the conversion machinery compactly
(Tables~\ref{tab:si-fixiert-en}--\ref{tab:xi-inputs-en}) and then establishes one
central point: \emph{as long as one stays in natural units and pure ratios, the
description is static and relative and requires no fractal corrections.} The
fractal corrections appear only upon projection to absolute SI values.

%=============================================================
\section{Compactified time: static and complete --- the arrow makes it dynamic}
\label{sec:rahmen}
%=============================================================

This section sets the frame above all the others: whether a quantity appears
static or dynamic depends solely on the \emph{status of the time direction} -- not
on the number of dimensions.

The full FFGFT geometry is the 4-torus $T^4 = T^3 \times S^1$, in which time is a
\emph{compact} direction -- the time-winding $S^1$ (Dok.~230). In this full view
time is a closed loop, on equal footing with the three spatial windings; there is
no flowing ``now'' and no arrow. The description is purely relational: winding
numbers and dimensionless ratios. This is \emph{layer~1} of Dok.~241 -- the level
on which FFGFT makes its fundamental statements.

On this layer everything appears static, yet nothing is lost. The theory's fractal
recursion is not absent here but \emph{frozen}: a ratio such as
$m_\mu/m_e \approx 206.768$ is the end product of a recursion that has come to rest
in this number -- just as the golden ratio $\varphi$ does not stand \emph{beside}
the Fibonacci sequence but \emph{is} its limit (Dok.~241). What is missing on
layer~1 is not the fractality but its visible motion.

\begin{prinzip}
\textbf{Static is not incomplete.} In the compact $T^4$ (time as a winding) the
description carries all invariant content -- as frozen fixed points of fractal
recursions. The transition to dynamics adds no content; it merely sets the
recursion into visible motion.
\end{prinzip}

Dynamics arises through \emph{decompactification}: when the time-winding $S^1$ is
unrolled into the open arrow $t$ -- geometrically the step $T^4 \to T^3$ that
``loses the time-winding'' (Dok.~230) -- three spatial directions plus one
directed time remain: the observed 3+1 world. What singles out this one direction
as an arrow is the fundamental $\xipar$ asymmetry that ``enables all evolution
processes'' (Dok.~078). Only now does the recursion run visibly: processes unfold,
phase accumulates, and the \emph{embedding correction} becomes explicit -- the
``price'' of which Dok.~185 speaks.

With this, everything that follows falls into one picture. The bridge from the
static layer~1 to the dynamic 3+1 world -- \emph{layer~2}, the SI translation
(Dok.~241) -- is carried by exactly $c$, $\hbar$, $\varepsilon_0$. That is why
these constants become real only here (Section~\ref{sec:dyn-konstanten}), and why
$G$ and $\alpha$ too are not static fundamental quantities but dynamic couplings
(Section~\ref{sec:G-alpha}). The only static fundamental quantity remains
$\xipar$; everything else is either a frozen $\xipar$ fixed point (layer~1) or its
visibly moving projection (layer~2).

A clarification so that ``complete'' is not misread: it means \emph{contains all
invariant content}, not \emph{the dynamics is unreal}. For the observer embedded in
the arrow, the time-flow is operationally real. The clean statement is: the
compact $T^4$ picture is complete in content; the dynamics is its real but
content-neutral internal perspective.

Finally, the arc back to retrocausality closes. On the $T^4$ with the time-winding
intact, a closed timelike curve is merely a winding of the time-loop, and
entanglement appears as a \emph{topological connection} (Dok.~230) -- static
geometry. Only after decompactification into 3+1 arrow-time does the same geometry
look like backward causation or nonlocality. The apparent exoticism of the
retrocausal is thus an artifact of the dynamic internal view, not of the geometry.

%=============================================================
\section{The constants fixed by the SI reform}
%=============================================================

\begin{table}[htbp]
  \centering
  \caption{The constants fixed by the 2019 SI reform (the ``machinery'').
           They carry no physics, only scale, and become~$1$ in natural units.}
  \label{tab:si-fixiert-en}
  \adjustbox{max width=\textwidth}{%
\begin{tabular}{llll}
    \toprule
    Constant & Value (exact since 2019) & defines & natural units \\
    \midrule
    $c$     & $299\,792\,458$ m/s                          & metre   & $=1$ \\
    $\hbar$ & $1{.}054\,571\,817\ldots\times10^{-34}$ J\,s & kg      & $=1$ \\
    $e$     & $1{.}602\,176\,634\times10^{-19}$ C           & ampere  & charge unit \\
    $k_B$   & $1{.}380\,649\times10^{-23}$ J/K              & kelvin  & $=1$ \\
    \bottomrule
  \end{tabular}%
}
\end{table}

%=============================================================
\section{Quantity conversion in natural units}
%=============================================================

\begin{table}[htbp]
  \centering
  \caption{Quantity conversion in natural units ($\hbar=c=k_B=1$): all
           dimensionful quantities become powers of energy.}
  \label{tab:nat-umrechnung-en}
  {\small
  \adjustbox{max width=\textwidth}{%
\begin{tabular}{lccl}
    \toprule
    Quantity & SI dimension & $[\hbar=c=k_B=1]$ & back to SI \\
    \midrule
    Energy        & J        & $E$            & base \\
    Mass          & kg       & $E$            & $\times\,S_{\mathrm{T0}}$ \ (via $c^{-2}$) \\
    Momentum      & kg\,m/s  & $E$            & $\times\,c^{-1}$ \\
    Length        & m        & $E^{-1}$       & $\ell[\mathrm{fm}]=197{.}327/E[\mathrm{MeV}]$ \\
    Time          & s        & $E^{-1}$       & $t[\mathrm{s}]=6{.}582\times10^{-22}/E[\mathrm{MeV}]$ \\
    Temperature   & K        & $E$            & $T[\mathrm{K}]=E[\mathrm{eV}]/(8{.}617\times10^{-5})$ \\
    Charge (Gauss)& C        & dimensionless  & $e=\sqrt{\alpha}\approx0{.}0854$ \\
    \bottomrule
  \end{tabular}%
}}

  \medskip
  \footnotesize
  The conversion to SI runs through the \emph{single} mass scale
  $S_{\mathrm{T0}} = 1\,\mathrm{MeV}/c^2 = 1{.}782662\times10^{-30}$~kg (Dok.~013/014);
  the length factor is $\hbar c/S_{\mathrm{T0}} = 1{.}973\times10^{-13}$~m, i.e.\ the
  $197$\,MeV\,fm of the $\hbar c=1$ column expressed in T0 language.\par\smallskip
  In T0 units the charge unit is chosen ($e=\sqrt{4\pi\varepsilon_0\hbar c}$) so that
  the \emph{written} value is $\alpha=1$ (Dok.~044) -- a convention, not a physical
  intervention. The physical invariant $\alpha\approx1/137$ is reconstructed from
  $\xipar$ (Table~\ref{tab:xi-inputs-en}).
\end{table}

%=============================================================
\section{The dimensionless inputs and their derivation from $\xipar$}
%=============================================================

\begin{table}[htbp]
  \centering
  \caption{The surviving dimensionless inputs of physics and their derivation from
           the single parameter $\xipar=\tfrac{4}{3}\times10^{-4}$. All relations
           are sourced.}
  \label{tab:xi-inputs-en}
  {\footnotesize\setlength{\tabcolsep}{4pt}
  \adjustbox{max width=\textwidth}{%
\begin{tabular}{lccl}
    \toprule
    Invariant & Standard physics & FFGFT relation (from $\xipar$) & Source \\
    \midrule
    $\xipar$           & ---            & $=\tfrac{4}{3}\times10^{-4}=4/30000$ & Dok.~013 \\
    $\alpha$ (SI)      & $1/137{.}036$  & $\xipar\,(\Ezero/1\,\mathrm{MeV})^2$\,$^{\dagger}$ & Dok.~011 \\
    Lepton masses      & measured       & $m=r\,\xipar^{\,p}\,v$ & Dok.~116, 006 \\
    \quad exponents    &                & $(p_e,p_\mu,p_\tau)=(\tfrac{3}{2},\,1,\,\tfrac{2}{3})$ & Dok.~116 \\
    \quad ratios       &                & $(r_e,r_\mu,r_\tau)=(\tfrac{4}{3},\,\tfrac{16}{5},\,\tfrac{25}{9})$ & Dok.~116 \\
    Koide $Q$          & $0{.}66666$    & $=\tfrac{2}{3}$ \ (consequence of the $\xipar$ exponents) & Dok.~116, 258 \\
    $\sin^2\theta_W$   & $0{.}2312$     & $\dfrac{1-\sqrt{1-4\alpha_W}}{4}$,\ \ $\alpha_W=\sqrt{\xipar}$ & Dok.~041 \\[0.6em]
    $\theta_{13}$      & $8{.}57^\circ$ & $\arcsin\!\big(\xipar^{1/3}\big)$ & Dok.~041 \\
    $G$                & measured       & $\dfrac{\xipar^2}{4m_e}\,\Kfrak$,\ \ $\Kfrak=1-100\xipar\approx0{.}9867$ & Dok.~012, 133 \\
    \bottomrule
  \end{tabular}%
}}

  \medskip
  \footnotesize
  $^{\dagger}$\,$\alpha=\xipar\,(\Ezero/1\,\mathrm{MeV})^2$ is the \emph{leading order},
  with $\Ezero=\sqrt{m_e\,m_\mu}=7{.}398$\,MeV.
  CODATA precision is reached through the fractal correction product
  $\displaystyle\prod_{n=1}^{137}\!\big(1+\delta_n\,\xipar\,(4/3)^{\,n-1}\big)$.
  These corrections are \textbf{not free assumptions}: $\Kfrak=1-100\xipar$ is uniquely
  fixed by the scale flow from the Planck to the electroweak scale
  ($D_f^{\,\mathrm{space}}=3-\xipar$, Dok.~133, ``$D_f$ is uniquely determined --
  not freely choosable''), and the rational ladder ratios $r_i$ are
  $\alpha$-geometric invariants (Dok.~258), structurally inaccessible to any
  after-the-fact fitting (non-closure theorem, Dok.~193).
\end{table}

%=============================================================
\section{Static geometry: why natural units are correction-free}
%=============================================================

As long as physics is expressed in natural units and pure ratios, its description
is \emph{static} and \emph{relational}: only dimensionless ratios occur, no
absolute anchors and no scale dependence. At this level the FFGFT quantities are
exact geometric invariants of $\xipar$ -- and no fractal correction is required.

\begin{principle}
\textbf{Principle.} In natural units FFGFT is purely relational. The dimensionless
structural relations -- mass ratios, mixing angles, the Koide quantity -- are
static geometric invariants of $\xipar$. They contain no fractal corrections.
\end{principle}

The clearest example is the Koide quantity: $Q=\tfrac{2}{3}$ follows exactly from
the exponents $(p_e,p_\mu,p_\tau)=(\tfrac{3}{2},1,\tfrac{2}{3})$ and the ratios
$(r_e,r_\mu,r_\tau)=(\tfrac{4}{3},\tfrac{16}{5},\tfrac{25}{9})$ -- with no
additional parameter and no fractal correction (Dok.~116). Likewise the ladder
ratios $r_i$, the exponents $p_i$, the Weinberg structure and $\theta_{13}$ are
exact functions of $\xipar$ alone. None of these relations needs an absolute
scale, an $\Ezero$ in MeV, or a conversion factor.

Where, then, do the fractal corrections arise? Only at the \emph{SI projection} --
where an absolute scale is fixed. $\Kfrak=1-100\xipar$ is not a correction to the
geometry but the cumulative effect of the scale flow from the Planck to the
electroweak scale (Dok.~133): a property of mapping the geometry onto an absolute
energy ruler. Likewise the fractal correction product
$\prod_n(1+\delta_n\,\xipar\,(4/3)^{n-1})$ appears only when the leading relation
$\alpha=\xipar(\Ezero/1\,\mathrm{MeV})^2$ is brought to CODATA precision in absolute
SI values.

An important delimitation: these projection factors are nonetheless \emph{not}
free parameters. $\Kfrak$ is uniquely fixed by the scale flow (Dok.~133), the
rational ratios are $\alpha$-geometric invariants (Dok.~258), and the non-closure
theorem (Dok.~193) blocks any after-the-fact adjustment. They are derived
projection factors, not assumed fits.

\begin{result}
\textbf{Conclusion.} The fractal corrections are the price of the absolute
projection, not a defect of the geometry. As long as one stays in natural units
and ratios, the description is static, relative and correction-free; the
corrections appear exclusively at the transition to absolute SI values -- and even
there they are uniquely determined by $\xipar$ and the scale structure.
\end{result}

%=============================================================
\section{Dynamic reality of the constants: $c$, $\hbar$, $\varepsilon_0$ in the time-flow}
\label{sec:dyn-konstanten}
%=============================================================

The previous section showed that the static $\xipar$-geometry is correction-free.
The remaining question is \emph{when} the constants $c$, $\hbar$ and
$\varepsilon_0$ acquire physical reality at all. The answer follows from the same
split, viewed from the other side: these constants are not properties of the
geometry at rest but the conversion rates it adopts as soon as it is embedded in a
real, time-extended process.

FFGFT distinguishes two times here (Dok.~078): the intrinsic, characteristic scale
$\tilde T$ of the duality $\tilde T\cdot m=1$, which governs discrete system
properties, and the overarching continuous time-flow (the ``arrow time'' $t$) in
which systems exist and processes unfold. The duality concerns the intrinsic
scale, not the time-flow itself. Only in the time-flow -- when a timeless identity
is physically \emph{realized} -- does what Dok.~185 calls the \emph{embedding
price} arise: realizing a static mathematical fact as a process costs real time.
$c$, $\hbar$ and $\varepsilon_0$ are the exchange rates of this embedding price.

\begin{erkenntnis}
\textbf{Embedding price.} A timeless $\xipar$-relation is a static fact. Its
physical realization as a process in arrow-time costs time -- and $c$, $\hbar$,
$\varepsilon_0$ are exactly the rates that quantify this price (Dok.~185).
\end{erkenntnis}

In detail:

\textbf{$c$} is not a fundamental law of nature but a dynamic ratio $L/T$
(Dok.~134). Statically, energy and mass are the same number ($E=m$, $c=1$, length
$\equiv$ time); $c$ does not appear at all. As soon as something propagates, $c$
becomes the traversal rate of the $T^4$ geometry -- the full form $E=mc^2$, the
dispersion $E^2=(pc)^2+(mc^2)^2$, the light cone. $c$ is real as the rate at which
the geometry is traversed in time.

\textbf{$\hbar$} is the exchange rate between geometric winding and accumulated
real time. Statically, phase is a dimensionless winding number on the torus
($\hbar=1$). In the time-flow the phase $e^{-iEt/\hbar}$ accumulates; $\hbar$ is
the rate at which the geometric winding becomes visible as oscillation,
interference and decay. In the field form $T_{\text{field}}\cdot E_{\text{field}}=1$
(Dok.~020) this is the transition from the intrinsic scale to observable dynamics.

\textbf{$\varepsilon_0$} is the vacuum's response to time-varying fields.
Statically it is absorbed into the charge-unit convention $\alpha=1$. Dynamically
it becomes real via $c=1/\sqrt{\varepsilon_0\mu_0}$: $\varepsilon_0$ and $\mu_0$
resonate dually (vacuum as a resonant medium, Dok.~043/044), and their product
\emph{is} the propagation of light in time. $\varepsilon_0$ is real as the
impedance of the vacuum to the temporal field flow.

The consequence for particle physics is a sharp dividing line:

\begin{prinzip}
\textbf{Demarcation.} \emph{Dimensionless, static} quantities (mass ratios,
mixing angles, $\sin^2\theta_W$, Koide $Q=2/3$) live entirely in the
$\xipar$-geometry -- without $c$, $\hbar$, $\varepsilon_0$ and without fractal
correction. \emph{Absolute, time-extended} quantities (lifetimes, decay rates,
cross sections, oscillation frequencies, propagators) exist only in the time-flow,
require $c$, $\hbar$, $\varepsilon_0$ to be real, and thereby inherit the SI
projection ($S_{\mathrm{T0}}$, $\Kfrak$).
\end{prinzip}

This is concretely testable: a lifetime \emph{ratio} (two processes, $\hbar$
cancels) is derivable cleanly from $\xipar$ alone (cf.~Dok.~160); an \emph{absolute}
lifetime carries the dynamic constants and the projection factors. The demarcation
thus predicts which quantities FFGFT delivers sharply and correction-free and
which must pass through the projection.

A closing ontological clarification: ``real'' here means \emph{operationally real
in the dynamic regime}, not \emph{ontologically fundamental}. The geometry
($\xipar$, $T^4$, $\tilde T\cdot m=1$) is primary; $c$, $\hbar$, $\varepsilon_0$
are the real conversion rates the timeless web of ratios adopts once it becomes
process-like. They are the SI shadows of embedding the static geometry into the
time-flow.

%=============================================================
\section{Consequence: $G$ and $\alpha$ are not static fundamental constants}
\label{sec:G-alpha}
%=============================================================

Exactly the same demarcation applies to the two quantities traditionally regarded
as fundamental constants: the gravitational constant $G$ and the fine-structure
constant $\alpha$. Both are \emph{coupling constants} -- they quantify the
strength of an interaction. And a coupling strength is the clearest case of a
dynamic quantity: it describes a process and it \emph{runs} with scale.

\textbf{$\alpha$.} Structurally $\alpha$ is not a free input but derived from
$\xipar$: $\alpha=\xipar\,(\Ezero/1\,\mathrm{MeV})^2$ (Dok.~011,
cf.~Table~\ref{tab:xi-inputs-en}). Operationally, however,
$\alpha=e^2/(4\pi\varepsilon_0\hbar c)$ -- built from exactly the embedding
constants $\varepsilon_0$, $\hbar$, $c$ -- and it \emph{runs} with energy
($\alpha(Q^2)$). This running is nothing other than the scale flow that also
generates the fractal correction product
$\prod_n(1+\delta_n\,\xipar\,(4/3)^{n-1})$. Thus $\alpha$ is neither fundamental
(it follows from $\xipar$) nor static (it lives in the scale/time-flow).

\textbf{$G$.} In natural units $G=1$ (Dok.~012). The SI value follows from
$\xipar$: $G=\dfrac{\xipar^2}{4m_e}\,\Kfrak$ -- thereby containing the projection
factor $\Kfrak=1-100\xipar$, which is itself a scale-flow effect (Dok.~133). The
equivalent Planck form $G=\ell_{\mathrm P}^2 c^3/\hbar$ (Dok.~012/127) shows it
even more directly: $G$ is expressed through $c^3/\hbar$, i.e.\ through the
dynamic constants themselves. $G$ is thus doubly projected -- via $\Kfrak$ and via
$c$, $\hbar$ -- and measures the strength of the gravitational interaction, a
process. $G$ too is neither fundamental nor static.

\begin{result}
\textbf{Conclusion.} The only static fundamental quantity is $\xipar$. $G$ and
$\alpha$ are not fundamental, static constants but \emph{dynamic couplings}:
derived from $\xipar$, dressed with the embedding constants $c$, $\hbar$,
$\varepsilon_0$ and clothed by scale-flow factors ($\Kfrak$, the fractal product).
Like $c$, $\hbar$, $\varepsilon_0$, they become real only in the time-flow. The
apparent fundamentality of $G$ and $\alpha$ is a consequence of the measurement
convention, not a foundation.
\end{result}

%=============================================================
\section{The demarcation from the Lagrangian viewpoint}
%=============================================================

The static/dynamic split of this document is not a reading of
Tables~\ref{tab:si-fixiert-en}--\ref{tab:xi-inputs-en} but the architecture of the
Lagrangian extension itself. The tables only summarize what the Lagrangian already
carries.

\textbf{Two densities as a necessity.} Dok.~095 shows that FFGFT requires two
complementary Lagrangian densities -- not by style but from the scale hierarchy.
The simplified
\[
  \mathcal{L}_{\mathrm{T0}} = \varepsilon\,(\partial\,\delta E)^2,
  \qquad \varepsilon = \xipar\,E^2
\]
carries pure $\xipar$ structure (layer~1); the extended Standard-Model density with
T0 corrections carries the dynamics (layer~2). Both are, as Dok.~095 stresses,
``mathematical descriptions ... not nature itself''. The demarcation is thus a
corollary of the two densities, not an interpretive overlay.

\textbf{The cut runs term by term.} The full decomposition (Dok.~067) separates
derivative from mass terms:
\[
  \mathcal{L}_{\text{time}} = \sqrt{-g}\Big[\tfrac{1}{2}\,g^{\mu\nu}\partial_\mu T\,\partial_\nu T - V(T)\Big],
  \qquad
  \mathcal{L}_{\text{gauge}} = \sqrt{-g}\big(-\tfrac{1}{4}F_{\mu\nu}F^{\mu\nu}\big),
\]
\[
  \mathcal{L}_\psi = \sqrt{-g}\,\Omega^4(T)\big(i\bar\psi\gamma^\mu\partial_\mu\psi - m\,\bar\psi\psi\big).
\]
The \emph{derivative terms} ($\partial_\mu$, $\sqrt{-g}$ with the metric,
$-\tfrac14 F^2$) carry the dynamics -- and, in dimensional form, $c$ (via the
metric) and $\hbar$ (via the kinetic normalization). The \emph{mass/potential
terms} ($V(T)$, $m\bar\psi\psi$) are static. The Euler-Lagrange step that turns
these into equations of motion \emph{is} the decompactification into arrow-time of
Section~\ref{sec:rahmen}.

\textbf{$\alpha$ and $G$ in the Lagrangian.} The gauge coupling sits in the
covariant derivative $D_\mu = \partial_\mu + ieA_\mu$ (Dok.~019) -- so $\alpha$ is
structurally a derivative (dynamic) term, not a static parameter. And gravity is
not inserted but \emph{emergent}: Dok.~049 shows it arises automatically from
$\mathcal{L} = \varepsilon\,(\partial\,\delta m)^2$, and Dok.~180 derives $G$ in
step~4 of a self-consistency chain directly from $\xipar$ -- $\xipar$, $L_0$ and
$G$ are not postulated but follow from the self-consistency of the Lagrangian.

\begin{result}
\textbf{Field-theoretic origin.} The demarcation of
Sections~\ref{sec:rahmen}, \ref{sec:dyn-konstanten} and \ref{sec:G-alpha} is a
consequence of the Lagrangian extension: the two densities (Dok.~095) are layers~1
and~2; the cut between derivative and mass terms (Dok.~067) is the static/dynamic
cut; $\alpha$ lives in the covariant derivative (Dok.~019); $G$ emerges from
$\xipar$ (Dok.~049/180). The tables are the SI summary, not the source of proof.
\end{result}
