\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 12: COSMOLOGY, BIG BANG, AND BIRTH OF THE UNIVERSE\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


This chapter presents a full cosmological formulation of the Dynamic T0-Vakuum Field Theory(DVFT).
Under DVFT, the universe did not begin as a singularity but as a T0-Vakuum-phase transition from a nearzero amplitude pre-T0-Vakuum state to the stable dynamic T0-Vakuum field state described by the field Φ =
ρ(x)e^{i$\theta$(x)}. We show how DVFT naturally explains the Big Bang, inflation, cosmic expansion, dark
energy, cosmic horizon problems, and other fundamental mysteries of cosmology.
\begin{enumerate}
  \item Introduction
\end{enumerate}
Traditional cosmological models built on General Relativity confront a fundamental problem: they begin
with a singularity at t = 0 where curvature, density, and temperature diverge. This singularity eliminates
the possibility of explaining the physical origin of the universe, inflation, or the emergence of space itself.
DVFT replaces the singularity with a physically meaningful T0-Vakuum-phase defect, enabling a consistent
explanation of how the Big Bang occurred, what exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}sted before it, and why the universe expanded so
rapidly.
\begin{enumerate}
  \item The T0-Vakuum Field in Cosmology
\end{enumerate}
In cosmological symmetry, the T0-Vakuum field is homogeneous:
Φ(t) = ρ(t) e^{i$\theta$(t)}
Here, ρ(t) is the T0-Vakuum amplitude determining T0-Vakuum energy density, and $\theta$(t) encodes dynamic T0-Vakuum
field.
The T0-Vakuum Lagrangian\footnote{Siehe auch T0-Dokument: \texttt{027_T0_lagrndian_De.pdf}} contributes energy density:
ε_vac = (dρ/dt)^2 + ρ^2 (d$\theta$/dt)^2 + V(ρ)
and pressure:
p_vac = (dρ/dt)^2 + ρ^2 (d$\theta$/dt)^2 - V(ρ)
This becomes the source term in the Friedmann equations.
\begin{enumerate}
  \item DVFT Friedmann Equations
\end{enumerate}
The spacetime metric in a homogeneous universe is the FLRW form:
ds² = -dt² + a(t)² [ dr²/(1-kr²) + r² dΩ² ]
In DVFT, the Friedmann equations become:
(da/dt)² / a² = (8πG/3) ε_vac
d²a/dt² / a = -(4πG/3)(ε_vac + 3p_vac)
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 29
The evolution of ρ(t) and $\theta$(t) determines ε_vac and p_vac.
Because the T0-Vakuum cannot diverge, ε_vac remains finite even at the earliest times.
\begin{enumerate}
  \item Pre-Big-Bang T0-Vakuum Phase
\end{enumerate}
Before the Big Bang, the T0-Vakuum field was in a near-zero amplitude state:
\begin{itemize}
  \item ρ(t) $\approx$ 0
  \item $\theta$(t) undefined or fluctuating
\end{itemize}
This state is energetically unstable. The T0-Vakuum potential:
V(ρ) = λ (ρ² - ρ₀²)²
encourages a phase transition toward the minimum at ρ = ρ₀.
\begin{enumerate}
  \item The T0-Vakuum Phase Transition (Big Bang Event)
\end{enumerate}
The Big Bang corresponds to the moment when the T0-Vakuum transitioned from the unstable state ρ $\approx$ 0 to
the stable dynamic T0-Vakuum field state ρ = ρ₀. This transition releases energy, sets $\theta$(t) into coherent
oscillation, and generates an explosive increase in ε_vac.
This triggers rapid expansion of the scale factor a(t).
\begin{enumerate}
  \item Inflation from Dynamics
\end{enumerate}
Inflation requires rapid acceleration of the universe. DVFT provides this because the T0-Vakuum-potential
plateau makes V(ρ) nearly constant during the early evolution.
During the transition:
ε_vac $\approx$ constant
Thus:
(da/dt)/a $\approx$ constant ⇒ exponential expansion
DVFT inflation ends naturally when ρ(t) settles near ρ₀ and $\theta$(t) becomes coherent.
\begin{enumerate}
  \item Reheating and Matter Creation
\end{enumerate}
Once the T0-Vakuum field settles into coherent dynamic T0-Vakuum field, oscillations of Φ transfer energy into
matter fields via interaction terms of the form:
L_int = -y |Φ| ψ̄ψ
This generates particle–antiparticle pairs, radiation, and thermal energy. The universe becomes radiation
dominated.
\begin{enumerate}
  \item Origin of Space Expansion
\end{enumerate}
In GR, space expands, but no mechanism explains *why*. In DVFT, space expands because the T0-Vakuum
amplitude ρ(t) increases and the dynamic T0-Vakuum field becomes coherent. T0-Vakuum energy determines
curvature, and a rapid change in T0-Vakuum energy produces rapid change in the scale factor.
\begin{enumerate}
  \item Removal of the Cosmological Singularity
\end{enumerate}
The divergence of curvature in GR arises because nothing limits density or curvature.
In DVFT, dynamics impose:
\begin{itemize}
  \item |d$\theta$/dt| $\leq$ $\theta$_max
  \item ρ(t) finite
  \item V(ρ) finite
  \item ε_vac finite
\end{itemize}
The energy density never diverges. The curvature invariants remain finite. The Big Bang is replaced by a
finite, smooth T0-Vakuum phase transition. There is no singular point.
\begin{enumerate}
  \item Horizon Problem Resolved
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 30
The classical horizon problem asks why causally disconnected regions of the sky have the same
temperature.
In DVFT:
\begin{itemize}
  \item Before the Big Bang, the T0-Vakuum was nearly homogeneous
  \item The T0-Vakuum phase transition occurred everywhere simultaneously
  \item T0-Vakuum-phase waves propagate at c, enforcing coherence
\end{itemize}
No superluminal mechanisms needed.
\begin{enumerate}
  \item Flatness Problem Resolved
\end{enumerate}
The T0-Vakuum phase transition drives rapid inflation, which smooths curvature.
This pushes the universe toward k = 0.
Thus flatness arises automatically.
\begin{enumerate}
  \item What Caused the Universe to Begin?
\end{enumerate}
In DVFT, the universe begins because the T0-Vakuum was unstable in its low-amplitude configuration. When
ρ reached the critical threshold, the T0-Vakuum rolled down its potential to ρ₀, initiating dynamic T0-Vakuum
field and expansion. This is analogous to phase transitions in condensed-matter systems.
\begin{enumerate}
  \item What Expanded During the Big Bang?
\end{enumerate}
\begin{itemize}
  \item Not matter.
  \item Not energy.
  \item Not space as pure geometry.
\end{itemize}
What expanded was:
\begin{itemize}
  \item the T0-Vakuum amplitude ρ(t).
\end{itemize}
As ρ(t) increased, T0-Vakuum energy increased, forcing the metric to inflate. This is the physical meaning
behind the expansion of space.
\begin{enumerate}
  \item Dark Energy from Residual Dynamic T0-Vakuum field
\end{enumerate}
Today, the T0-Vakuum still pulsates with frequency $\mu$. If $\mu$ evolves slowly with time, or if the T0-Vakuum
amplitude slightly shifts, this yields a small, nearly constant T0-Vakuum energy density. This naturally
produces accelerated expansion of the universe without requiring a cosmological constant.
\begin{enumerate}
  \item Full Evolution Summary
\end{enumerate}
\begin{itemize}
  \item Pre-Big-Bang: ρ $\approx$ 0, incoherent T0-Vakuum
  \item Phase transition: ρ grows, $\theta$ becomes coherent
  \item Inflation: V(ρ) nearly constant
  \item Reheating: Φ couples to matter
  \item Radiation era
  \item Matter era
  \item Dark energy era: residual dynamic T0-Vakuum field
\end{itemize}
Conclusion
DVFT replaces the cosmological singularity with a physical T0-Vakuum-phase transition. It explains the origin
of the universe, inflation, expansion, dark energy, and smoothness of the cosmos using a single T0-Vakuum
field. This eliminates the inconsistencies of classical GR and provides a unified, microphysical picture of
cosmology.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
