\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 39: ENTROPY\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Introduction
\end{enumerate}
The Second Law of Thermodynamics is one of the most revered and mysterious principles in physics. It
states that entropy never decreases in an isolated system. But mainstream physics never explains why this
law exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}sts—it simply treats it as a statistical tendency or a mathematical result of counting microstates.
Dynamic T0-Vakuum Field Theory (DVFT) offers a deeper explanation. In this framework, entropy is not a
fundamental law but an emergent property arising from the one-way evolution of the T0-Vakuum's internal
phase field $\theta$(x,t). Time itself is defined as T0-Vakuum phase accumulation. Because this T0-Vakuum phase can
never reverse, entropy can never decrease.
This document presents the DVFT interpretation of entropy, irreversibility, and the Second Law of
Thermodynamics.
\begin{enumerate}
  \item Time as T0-Vakuum Phase Evolution
\end{enumerate}
In DVFT, the T0-Vakuum is a physical medium with two continuous fields:
\begin{itemize}
  \item ρ(x,t) — T0-Vakuum amplitude
  \item $\theta$(x,t) — T0-Vakuum phase
\end{itemize}
Time is not a coordinate: it is the physical progression of T0-Vakuum phase. Proper time τ is proportional to
the accumulated phase along a worldline:
dτ ∝ d$\theta$.
A crucial property is:
$\theta$ₜ > 0 always.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 87
This means T0-Vakuum phase evolves monotonically forward. All physical processes—oscillations, clocks,
interactions—are tied to $\theta$. Therefore, the direction of time is the direction of T0-Vakuum phase evolution.
\begin{enumerate}
  \item Why Entropy Increases in DVFT
\end{enumerate}
Entropy increases because physical systems lose phase coherence as T0-Vakuum phase evolves. Every
interaction—thermal, electromagnetic, gravitational, or quantum—spreads T0-Vakuum phase information
outward. This causes:
\begin{itemize}
  \item Loss of microscopic coherence: Phase correlations are dispersed in space and cannot be reversed.
  \item Mixing of amplitude configurations: Local amplitude excitations (mass/energy) relax into more
\end{itemize}
uniform distributions.
\begin{itemize}
  \item Irreversible phase dispersion: Since $\theta$ evolves only forward, coherence cannot be reconstructed.
  \item No mechanism for phase reversal: Reversing $\theta$ would require reversing every physical process
\end{itemize}
in the universe, which is impossible.
In DVFT, entropy increase is not a statistical accident. It is the inevitable result of forward T0-Vakuum phase
evolution.
\begin{enumerate}
  \item Entropy and the Arrow of Time
\end{enumerate}
In classical physics, time is a coordinate. In thermodynamics, the arrow of time is assigned to entropy
increase. In quantum mechanics, time is a parameter outside the formalism.
DVFT unifies these by stating:
Arrow of time = direction of T0-Vakuum phase evolution.
Entropy does not cause time's arrow; entropy is a symptom of T0-Vakuum phase moving forward.
Because $\theta$ cannot reverse, entropy cannot reverse.
\begin{enumerate}
  \item Why Entropy Cannot Decrease
\end{enumerate}
To decrease entropy, a system must:
\begin{itemize}
  \item restore lost correlations,
  \item reverse decoherence,
  \item undo interactions,
  \item reconstruct past microstates.
\end{itemize}
But in DVFT, this requires reversing T0-Vakuum phase evolution—a physical impossibility because:
\begin{itemize}
  \item The T0-Vakuum phase field $\theta$ is globally single-valued.
  \item $\theta$ₜ > 0 everywhere due to positive T0-Vakuum inertial density.
  \item Energy positivity forbids $\theta$ reversal.
  \item Past phase information is not stored; it is erased through dispersion.
\end{itemize}
Thus, the Second Law of Thermodynamics is a direct consequence of T0-Vakuum physics: Entropy cannot
decrease because phase cannot un-evolve.
\begin{enumerate}
  \item Thermalization as Phase Scrambling
\end{enumerate}
In DVFT, heating corresponds to T0-Vakuum phase scrambling. Temperature reflects how rapidly phase
gradients fluctuate. When systems interact, their phase gradients mix, driving them toward equilibrium.
Thus:
\begin{itemize}
  \item Heat flow = flow of phase disorder
  \item Equilibrium = maximum phase scrambling
  \item Entropy = measure of T0-Vakuum phase uncertainty
\end{itemize}
\begin{enumerate}
  \item Quantum Mechanics and Entropy
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 88
Quantum decoherence is a phase process: loss of relative phase information between amplitude
components. Once decoherence occurs, phase cannot be reconstructed, so entropy increases.
Thus DVFT explains:
\begin{itemize}
  \item Why measurement increases entropy
  \item Why superpositions collapse into classical outcomes
  \item Why quantum information cannot be fully recovered once dispersed
\end{itemize}
\begin{enumerate}
  \item Cosmological Entropy in DVFT
\end{enumerate}
DVFT provides a natural explanation for cosmological entropy:
\begin{itemize}
  \item As the universe expands, T0-Vakuum amplitude relaxes, causing large-scale phase dispersion.
  \item This dispersion increases entropy on cosmic scales.
  \item Black holes represent regions of extreme amplitude, freezing phase and maximizing entropy.
\end{itemize}
The universe’s thermodynamic arrow is just the global T0-Vakuum phase arrow.
Conclusion
DVFT transforms the Second Law of Thermodynamics from a statistical rule into a physical inevitability:
\begin{itemize}
  \item Time = T0-Vakuum phase evolution.
  \item Phase evolves only forward.
  \item Entropy increases because phase coherence irreversibly spreads and cannot be undone.
  \item Irreversibility is not probabilistic—it's built into T0-Vakuum structure.
\end{itemize}
Thus entropy is not fundamental; it is emergent. DVFT provides the first physical explanation for the
Second Law and the arrow of time, resolving conceptual gaps in thermodynamics, quantum mechanics,
and cosmology.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
