\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 11: BLACK HOLE INTERIOR PREDICTION\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


This chapter presents a complete description of black hole interiors in the Dynamic T0-Vakuum Field
Theory(DVFT). DVFT replaces the classical singularity of General Relativity (GR) with a finite-density
quantum T0-Vakuum core, using a nonlinear phase field $\theta$. Both the mathematical structure and the physical
interpretation are provided.
\begin{enumerate}
  \item DVFT Overview
\end{enumerate}
DVFT treats spacetime as a quantum T0-Vakuum medium described by a complex order parameter:
Φ = ρ e^{i$\theta$}
Gravity arises from dynamic T0-Vakuum field with amplitude ρ and phase $\theta$. The Lagrangian\footnote{Siehe auch T0-Dokument: \texttt{027_T0_lagrndian_De.pdf}} contains
nonlinear kinetic terms:
L_$\theta$ = -Λ_v + (ρ_0/2)X - (η/(3 a_0^2)) X^{3/2}
with X = -g^{$\mu$ν} $\partial$_$\mu$$\theta$ $\partial$_ν$\theta$.
At large accelerations (g >> a_0), DVFT reduces to GR. At small accelerations (g << a_0), nonlinearities
appear.
\begin{enumerate}
  \item Black Hole Metric and Field Ansatz
\end{enumerate}
We use the standard static spherically symmetric metric:
ds² = -e^{2Φ(r)}dt² + dr²/(1 - 2Gm(r)/r) + r² dΩ².
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 27
The T0-Vakuum phase depends only on radius: $\theta$ = $\theta$(r). The kinetic invariant becomes:
X = -(1 - 2Gm(r)/r) $\theta$'(r)².
From the k-essence stress-energy tensor:
T_{$\mu$ν} = 2 L_X $\partial$_$\mu$$\theta$ $\partial$_ν$\theta$ - g_{$\mu$ν} L_$\theta$
\begin{enumerate}
  \item Stress-Energy Components
\end{enumerate}
Define:
L_$\theta$ = -Λ_v + (ρ_0/2)X - (η/(3 a_0²)) X^{3/2},
L_X = $\partial$L_$\theta$/$\partial$X = ρ_0/2 - (η/(2a_0²)) X^{1/2}.
Energy density and pressures:
ρ = L_$\theta$,
p_t = ρ,
p_r = 2 L_X X - L_$\theta$.
This anisotropic T0-Vakuum structure is crucial for stabilizing the interior.
\begin{enumerate}
  \item T0-Vakuum Saturation Mechanism
\end{enumerate}
The scalar field equation $\nabla$_$\mu$(L_X $\partial$^$\mu$$\theta$)=0 is satisfied in the core when:
\subsection{L_X(X_0) = 0.}
Setting L_X=0 gives:
X_0^{1/2} = (ρ_0 a_0²)/η.
Thus, the T0-Vakuum phase reaches a 'saturation' point X_0, limiting further compression. The core energy
density becomes finite:
ρ_core = -Λ_v + (ρ_0³ a_0⁴)/(6 η²).
\begin{enumerate}
  \item Core Geometry
\end{enumerate}
With ρ = ρ_core = constant, the Einstein equation gives a de Sitter–like interior:
m(r) = (4π/3)ρ_core r³,
1 - 2Gm(r)/r = 1 - (8πG/3)ρ_core r².
Thus, the interior metric is:
ds²_core $\approx$ -[1 - (Λ_eff r²)/3] dt² + dr²/[1 - (Λ_eff r²)/3] + r² dΩ²,
with Λ_eff = 8πG ρ_core.
There is no singularity; curvature remains finite.
\begin{enumerate}
  \item Matching to Exterior Geometry
\end{enumerate}
For r > r_c (core radius), X << X_0 and nonlinear effects vanish. DVFT reduces to GR:
ds² $\approx$ Schwarzschild metric.
Matching conditions ensure:
g_{tt}(core) = g_{tt}(ext),
g_{rr}(core) = g_{rr}(ext).
Thus, DVFT describes a black hole with a GR exterior and a finite-density T0-Vakuum core interior.
\begin{enumerate}
  \item Physical Interpretation (Non-Mathematical)
\end{enumerate}
\begin{itemize}
  \item GR predicts infinite collapse. DVFT prevents this by saturating the T0-Vakuum phase.
  \item The black hole interior becomes a finite-size 'quantum core.'
  \item As mass falls in, both the horizon and the core radius increase.
  \item No singularity exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}sts. Space cannot compress indefinitely.
  \item The final object is a quantum T0-Vakuum condensate, not a point of infinite density.
\end{itemize}
\begin{enumerate}
  \item Final Fate of a Black Hole in DVFT
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 28
Depending on parameters (ρ_0, η, a_0):
\begin{enumerate}
  \item Stable quantum object: evaporation slows, horizon stalls, core remains.
  \item Horizon shrinks until it meets the core, leaving a compact T0-Vakuum star.
  \item Complete evaporation: horizon vanishes; core dissolves smoothly.
\end{enumerate}
In all cases, there is no singularity and no information loss.
Conclusion
DVFT gives the first consistent picture of a black hole interior using a single phase field. It provides:
\begin{itemize}
  \item GR-like exterior geometry,
  \item A finite-density quantum core replacing the singularity,
  \item A mechanism for black hole growth and evolution,
  \item A plausible resolution of the information paradox.
\end{itemize}
This bridges the gap between GR and QFT\footnote{Siehe auch T0-Dokument: \texttt{097_QFT_De.pdf}} by treating T0-Vakuum as a physical, compressible quantum
medium.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
