\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 41: INTRINSIC PROPERTIES OF THE VACUUM FIELD\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Introduction
\end{enumerate}
This document compiles the intrinsic numerical parameters of the T0-Vakuum field in DVFT (Dynamic
T0-Vakuum field Curvature Theory). Unlike conventional physics, where T0-Vakuum constants such as α, ε₀, ħ,
c, and even cosmological density appear as disconnected inputs, DVFT unifies them under the dynamics
of a single complex T0-Vakuum field:
Φ(x,t) = ρ(x,t) e^{i$\theta$(x,t)}
Here:
\begin{itemize}
  \item ρ(x,t) is the T0-Vakuum amplitude (inertial density, gravitational stiffness).
  \item $\theta$(x,t) is the T0-Vakuum phase (quantum coherence, charge, CP violation).
\end{itemize}
The constants governing ρ and $\theta$ define the mechanical, electromagnetic, and quantum structure of spacetime itself. This document consolidates their values and shows how they relate to observable physics.
\begin{enumerate}
  \item Fundamental DVFT T0-Vakuum Parameters
\end{enumerate}
DVFT introduces the following intrinsic T0-Vakuum parameters:
\begin{enumerate}
  \item B – T0-Vakuum phase stiffness
  \item ρ₀ – Inertial T0-Vakuum density
  \item K₀ – Amplitude stiffness of the T0-Vakuum
  \item ($\partial$$\theta$/$\partial$x) – Fundamental phase gradient corresponding to one unit of electric charge
\end{enumerate}
These determine all quantum, electromagnetic, and gravitational behavior emerging from Φ.
\begin{enumerate}
  \item Phase Stiffness B (Calibrated from α)
\end{enumerate}
The fine-structure constant α is expressed in DVFT as:
α = (B / ħ c) ($\partial$$\theta$/$\partial$x)²
Choosing the phase gradient associated with one unit charge as:
|$\partial$$\theta$/$\partial$x| $\approx$ 2π / λ_C, λ_C = ħ / (m_e c) $\approx$ 3.86 $\times$ 10⁻¹³ m,
gives:
|$\partial$$\theta$/$\partial$x| $\approx$ 1.63 $\times$ 10¹³ m⁻¹.
Using α_exp = 1/137.036, the resulting T0-Vakuum phase stiffness is:
B $\approx$ 8.7 $\times$ 10⁻⁵⁵ (unit depends on normalization of Lagrangian\footnote{Siehe auch T0-Dokument: \texttt{027_T0_lagrndian_De.pdf}}).
Interpretation:
\begin{itemize}
  \item B measures how hard it is to twist the T0-Vakuum phase $\theta$.
  \item This same B must be used for electromagnetism, neutrino masses, baryogenesis, and quantum
\end{itemize}
coherence.
\begin{enumerate}
  \item Inertial T0-Vakuum Density ρ₀
\end{enumerate}
ρ₀ is taken from the effective mass-equivalent density of dark energy:
ρ₀ $\approx$ 6 $\times$ 10⁻²⁷ kg/m³.
This represents the intrinsic inertial content of the T0-Vakuum amplitude ρ, which couples directly to
gravitational behavior.
\begin{enumerate}
  \item Amplitude Stiffness K₀ (via c = $\sqrt$(K₀/ρ₀))
\end{enumerate}
DVFT identifies the speed of light with the ratio of amplitude stiffness to inertial density:
c² = K₀ / ρ₀ → K₀ = ρ₀ c².
Substituting ρ₀ $\approx$ 6$\times$10⁻²⁷ kg/m³ and c $\approx$ 3$\times$10⁸ m/s gives:
K₀ $\approx$ 5.4 $\times$ 10⁻¹⁰ J/m³.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 92
This value is close to the observed dark-energy density, suggesting a deep relationship between T0-Vakuum
elasticity and cosmic acceleration.
\begin{enumerate}
  \item Fundamental Phase Gradient (Unit Charge)
\end{enumerate}
For a unit electric charge, the T0-Vakuum phase winds by 2π over a microscopic radius taken to be the electron
Compton wavelength:
λ_C = ħ / (m_e c) $\approx$ 3.86 $\times$ 10⁻¹³ m.
Thus:
|$\partial$$\theta$/$\partial$x|_e $\approx$ 2π / λ_C $\approx$ 1.63 $\times$ 10¹³ m⁻¹.
This gradient defines the microscopic "twist" of the T0-Vakuum phase corresponding to one unit of electric
charge.
\begin{enumerate}
  \item Derived DVFT Quantities
\end{enumerate}
Once B, ρ₀, K₀, and |$\partial$$\theta$/$\partial$x| are set, DVFT determines a wide range of T0-Vakuum properties:
\begin{itemize}
  \item Speed of Light:
\end{itemize}
c = $\sqrt$(K₀/ρ₀) $\approx$ 3 $\times$ 10⁸ m/s.
\begin{itemize}
  \item Fine-Structure Constant:
\end{itemize}
α = (B / ħ c)($\partial$$\theta$/$\partial$x)² → α $\approx$ 1/137 (by calibration).
\begin{itemize}
  \item Deep-Field Acceleration Scale (galactic regime):
\end{itemize}
a₀ $\approx$ c² / L_*,
where L_* is the cosmic coherence length (~Hubble radius).
This gives the correct MOND-like acceleration scale ~1$\times$10⁻¹⁰ m/s².
\begin{itemize}
  \item Neutrino Mass Scale:
\end{itemize}
m_ν ∝ B ($\partial$$\theta$/$\partial$x)² evaluated at long coherence scales, yielding naturally small masses: 0.01–0.05 eV.
\begin{itemize}
  \item Quantum Coherence Length of T0-Vakuum:
\end{itemize}
L_coh $\approx$ $\sqrt$(ħ / B),
which becomes extremely large due to tiny B, enabling phase coherence across cosmological distances.
\begin{itemize}
  \item Dark-Energy Behavior:
\end{itemize}
U(ρ₀) $\approx$ K₀ ∼ 10⁻¹⁰ J/m³,
matching observed T0-Vakuum energy density.
\begin{enumerate}
  \item Why Using a Single B Everywhere Is Consistent
\end{enumerate}
B must be universal because:
\begin{itemize}
  \item $\theta$ is a universal phase field in DVFT.
  \item All quantum phenomena (charge, CP violation, coherence, neutrino masses, photon propagation,
\end{itemize}
baryogenesis) arise from the same $\theta$-dynamics.
\begin{itemize}
  \item A single stiffness constant ensures unification, just as ħ and c apply universally in conventional
\end{itemize}
physics.
This allows DVFT to coherently explain:
\begin{itemize}
  \item Quantum mechanics
  \item Electromagnetism
  \item Neutrino behavior
  \item Deep-field gravity
  \item Dark energy
  \item Early-universe CP asymmetry
\end{itemize}
all through the same T0-Vakuum field.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 93
\begin{enumerate}
  \item Summary of Intrinsic T0-Vakuum Parameters
\end{enumerate}
DVFT T0-Vakuum Parameter Sheet:
\begin{itemize}
  \item Phase stiffness:
\end{itemize}
B $\approx$ 8.7 $\times$ 10⁻⁵⁵
\begin{itemize}
  \item Inertial T0-Vakuum density:
\end{itemize}
ρ₀ $\approx$ 6 $\times$ 10⁻²⁷ kg/m³
\begin{itemize}
  \item Amplitude stiffness:
\end{itemize}
K₀ $\approx$ 5.4 $\times$ 10⁻¹⁰ J/m³
\begin{itemize}
  \item Fundamental phase gradient for one charge:
\end{itemize}
|$\partial$$\theta$/$\partial$x|_e $\approx$ 1.63 $\times$ 10¹³ m⁻¹
\begin{itemize}
  \item Coherence length:
\end{itemize}
L_coh $\approx$ $\sqrt$(ħ/B) → enormous (cosmic-scale)
\begin{itemize}
  \item Deep-field acceleration:
\end{itemize}
a₀ $\approx$ 10⁻¹⁰ m/s²
\begin{itemize}
  \item Speed of light:
\end{itemize}
c = $\sqrt$(K₀/ρ₀)
Together, these define the intrinsic mechanical, electromagnetic, quantum, and gravitational structure of
the DVFT T0-Vakuum.
Conclusion
The numerical T0-Vakuum parameters in DVFT are consistent with known electromagnetic, quantum, and
cosmological observations. By fixi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}ng B from α and anchoring ρ₀ and K₀ in cosmology, the entire quantum
and gravitational framework emerges from a single unified T0-Vakuum field Φ = ρ e^{i$\theta$}.
These parameters provide the first coherent numerical foundation for a theory that unifies:
\begin{itemize}
  \item Special relativity
  \item Quantum mechanics
  \item Electromagnetism
  \item Neutrino physics
  \item Baryogenesis
  \item Dark energy
  \item Galactic dynamics (without dark matter)
\end{itemize}
within one field-based T0-Vakuum framework.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
