\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{FFGFT Kapitel 35: QUANTUM PHENOMENA EXPLAINED\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{31. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


FFGFT interprets quantum mechanics as the behavior of T0-Vakuum-phase and T0-Vakuum-amplitude fields. This
chapter provides a unified explanation for twelve major unsolved quantum phenomena, including collapse,
entanglement, zero point energy, decoherence and delayed-choice experiments. FFGFT clarifies these
phenomena by grounding them in the physical fields Φ = ρ e^{i$\theta$}.
\begin{enumerate}
  \item Wavefunction Collapse
\end{enumerate}
In FFGFT, collapse is not a postulate. It occurs when T0-Vakuum-phase coherence ($\theta$) is disrupted by
macroscopic interactions. Measurement destroys $\theta$-coherence, forcing ψ to localize.
\begin{enumerate}
  \item Wave–Particle Duality
\end{enumerate}
Waves correspond to coherent T0-Vakuum-phase patterns, while particles correspond to localized T0-Vakuumamplitude excitations. Duality becomes a property of Φ, not a paradox.
\begin{enumerate}
  \item Entanglement
\end{enumerate}
Entanglement arises from shared T0-Vakuum-phase coherence between separated systems. Global coherence
of $\theta$ allows nonlocal correlations without signaling.
\begin{enumerate}
  \item Zero-Point Energy
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 78
Dynamic T0-Vakuum field gives finite, physical zero-point energy ε_vac = ρ₀² (d$\theta$/dt)², connecting T0-Vakuum
energy to cosmological acceleration.
\begin{enumerate}
  \item Delayed Choice & Quantum Eraser
\end{enumerate}
Interference depends on $\theta$-coherence. Which-path detectors scramble $\theta$; erasure restores it. FFGFT removes
retrocausality by explaining phase re-coherence.
\begin{enumerate}
  \item Decoherence
\end{enumerate}
Decoherence is T0-Vakuum-phase scrambling. Macroscopic systems distort $\theta$-fields and eliminate
interference patterns physically, not abstractly.
\begin{enumerate}
  \item Quantum Randomness
\end{enumerate}
Randomness arises from unavoidable T0-Vakuum-phase fluctuations: Δ$\theta$ · ΔE $\geq$ ħ/2 produces inherent phase
jitter in Φ.
\begin{enumerate}
  \item Atomic Quantization
\end{enumerate}
Energy quantization corresponds to $\theta$-field circulation conditions: ∮ $\nabla$$\theta$ · dl = 2πn. Atomic spectra reflect
dynamic T0-Vakuum field waves.
Conclusion
FFGFT unifies gravity and quantum mechanics by grounding quantum behavior in T0-Vakuum-phase
properties. Interference, collapse, entanglement, and decoherence all follow naturally from Φ = ρ e^{i$\theta$}.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_FFGFT-alles\_De.pdf} -- Vollständiges FFGFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
