\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 38: BLACK HOLE AND QUANTUM SINGULARITIES\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Introduction
\end{enumerate}
This document presents a full, rigorous DVFT (Dynamic T0-Vakuum field Curvature Theory) explanation of
why *both* classical gravitational singularities (black holes) and quantum singularities (point particles,
infinite self-energy) cannot exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}st.
In DVFT, spacetime curvature and inertia emerge from the T0-Vakuum amplitude field:
Φ(x,t) = ρ(x,t) e^{i$\theta$(x,t)},
with:
\begin{itemize}
  \item ρ(x,t) – T0-Vakuum amplitude (determines inertia and gravitational potential),
  \item $\theta$(x,t) – phase field (determines quantum coherence and wave-like behavior).
\end{itemize}
Gravity emerges from amplitude gradients:
g = −$\nabla$ρ.
Singularities require ρ → $\infty$ or $\nabla$ρ → $\infty$. DVFT forbids both because the T0-Vakuum has finite stiffness and
inertial density, encoded in the potential U(ρ).
\begin{enumerate}
  \item Why Singularities Cannot Exist in DVFT: The T0-Vakuum Potential U(ρ)
\end{enumerate}
DVFT (als effektive phänomenologische Schicht von T0) postuliert the T0-Vakuum has a microphysical potential:
U(ρ) = Λ₀ + (κ/2)(ρ − ρ₀)² + (λ/4)(ρ − ρ₀)⁴ + …
where:
\begin{itemize}
  \item ρ₀ is the equilibrium T0-Vakuum amplitude,
  \item κ is the elastic stiffness of the T0-Vakuum,
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 84
\begin{itemize}
  \item λ stabilizes large deviations of ρ.
\end{itemize}
This potential is strongly convex at large |ρ − ρ₀|.
Thus, any attempt to compress the T0-Vakuum amplitude beyond moderate values requires infinite energy:
U(ρ) → $\infty$ as |ρ − ρ₀| → $\infty$.
Therefore:
\begin{itemize}
  \item ρ cannot diverge,
  \item $\nabla$ρ cannot diverge,
  \item gravitational curvature cannot diverge.
\end{itemize}
This single microphysical fact eliminates *all* singularities in DVFT.
\begin{enumerate}
  \item Removal of Quantum Singularities (Electron, Proton, Point Particles)
\end{enumerate}
Quantum field theory treats electrons and quarks as point particles, leading to:
\begin{itemize}
  \item infinite self-energy,
  \item divergent Coulomb self-field,
  \item undefined gravitational field at r = 0.
\end{itemize}
DVFT replaces a point mass with a finite T0-Vakuum amplitude deformation:
δρ(x) = G m $\int$ d³x' |ψ(x')|² / |x − x'|.
This deformation is always finite because:
\begin{itemize}
  \item |ψ(x)|² is normalizable,
  \item convolution with 1/r smooths the field,
  \item U(ρ) prevents amplitude blow-up.
\end{itemize}
As a result:
\begin{itemize}
  \item no particle has infinite self-energy,
  \item no wavefunction produces a singular potential,
  \item gravity is well-defined even in superposition.
\end{itemize}
Thus quantum singularities are eliminated by T0-Vakuum microphysics, not by renormalization.
\begin{enumerate}
  \item Gravitational Field of a Delocalized Electron
\end{enumerate}
An electron with wavefunction ψ(x,t) generates a T0-Vakuum amplitude profile:
ρ(x,t) = ρ₀ + G m_e $\int$ d³x' |ψ(x',t)|² / |x − x'|.
When ψ(x,t) spreads due to quantum dispersion, the gravitational field spreads with it:
g(x,t) = −$\nabla$ρ(x,t).
This ensures:
\begin{itemize}
  \item gravity is fully compatible with Heisenberg uncertainty,
  \item gravitational fields have finite width,
  \item no r → 0 divergence occurs.
\end{itemize}
DVFT therefore produces the first consistent microscopic definition of gravity for a single quantum
particle.
\begin{enumerate}
  \item Removal of Black Hole Singularities
\end{enumerate}
In classical GR, gravitational collapse leads to infinite curvature at r = 0.
In DVFT, as matter compresses and raises ρ(x), the T0-Vakuum potential U(ρ) rapidly increases. At
sufficiently high density, a phase transition in the T0-Vakuum occurs:
\begin{itemize}
  \item ρ stops increasing (T0-Vakuum stiffness prevents divergence),
  \item $\theta$ becomes phase-locked (coherence inside horizon),
  \item matter transitions into a high-amplitude T0-Vakuum phase state,
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 85
\begin{itemize}
  \item gravitational field saturates.
\end{itemize}
Thus the black hole interior is NOT a singularity. It is a region of:
\begin{itemize}
  \item finite ρ,
  \item finite $\nabla$ρ,
  \item finite energy density,
  \item T0-Vakuum-phase condensate.
\end{itemize}
The event horizon may still exist, but the spacetime interior remains regular.
\begin{enumerate}
  \item DVFT Black Hole Interior Structure
\end{enumerate}
DVFT predicts that inside a black hole:
\begin{itemize}
  \item ρ(r) rises toward a maximum allowed value ρ_max,
  \item U(ρ) prevents further growth beyond ρ_max,
  \item curvature saturates,
  \item matter becomes T0-Vakuum-amplitude dominated,
  \item $\theta$ freezes (phase coherence becomes rigid),
  \item no divergence in metric-equivalent quantities occurs.
\end{itemize}
This resembles:
\begin{itemize}
  \item gravastar-like interiors,
  \item T0-Vakuum condensate cores,
  \item nonsingular loop quantum gravity solutions,
  \item but derived *entirely from DVFT microphysics*.
\end{itemize}
\begin{enumerate}
  \item The Deep Reason DVFT Removes Both Types of Singularities
\end{enumerate}
DVFT eliminates singularities because spacetime curvature is not fundamental. It is an *emergent
property* of the T0-Vakuum amplitude field ρ. If ρ cannot diverge, then curvature cannot diverge. The
T0-Vakuum’s elastic potential and finite inertial density are the mechanisms that prevent runaways.
Thus:
\begin{itemize}
  \item matter cannot collapse to infinite density,
  \item wavefunctions cannot create divergent potentials,
  \item curvature cannot become infinite.
\end{itemize}
This is the first unified mechanism eliminating singularities across classical and quantum domains.
\begin{enumerate}
  \item Comparison with GR, LQG, and QFT\footnote{Siehe auch T0-Dokument: \texttt{097_QFT_De.pdf}}
\end{enumerate}
General Relativity (GR):
\begin{itemize}
  \item predicts unavoidable singularities (Hawking-Penrose theorems),
  \item has no internal regulator for curvature.
\end{itemize}
Loop Quantum Gravity (LQG):
\begin{itemize}
  \item introduces discrete geometry,
  \item removes singularities by quantizing spacetime,
  \item but requires radical nonlocality and lacks experimental grounding.
\end{itemize}
Quantum Field Theory:
\begin{itemize}
  \item produces infinite point-particle self-energies,
  \item resolves them only through renormalization,
  \item does not address gravitational singularity.
\end{itemize}
\subsection{Dvft:}
\begin{itemize}
  \item retains continuum spacetime,
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 86
\begin{itemize}
  \item derives gravity from a physical T0-Vakuum field,
  \item imposes finite amplitude & stiffness,
  \item eliminates both self-energy and gravitational singularities,
  \item without renormalization,
  \item without quantizing spacetime,
  \item without modifying quantum mechanics.
\end{itemize}
DVFT is the simplest and most physically grounded solution among all three.
\begin{enumerate}
  \item Final Summary
\end{enumerate}
DVFT eliminates singularities through T0-Vakuum amplitude dynamics:
\begin{enumerate}
  \item The T0-Vakuum field Φ = ρ e^{i$\theta$} has finite stiffness and inertial density.
  \item U(ρ) prevents ρ from diverging under collapse.
  \item Quantum particles generate finite T0-Vakuum amplitude deformations from |ψ|².
  \item Gravity emerges as $\nabla$ρ, which can never diverge.
  \item Black holes contain T0-Vakuum-phase condensates, not singularities.
  \item No infinite self-energy, no point divergences, no r → 0 explosion exists.
\end{enumerate}
DVFT therefore provides the first unified, microphysically consistent elimination of:
\begin{itemize}
  \item black hole singularities,
  \item quantum point singularities,
  \item gravitational field singularities.
\end{itemize}
This positions DVFT as a fundamentally complete framework bridging general relativity and quantum
mechanics.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
