\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 43: FUNDAMENTAL AXIOMS AND CONSTANTS\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Core Axi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}oms of the Dynamic T0-Vakuum Field Theory (DVFT)
\end{enumerate}
Axiom 1 — The T0-Vakuum Is a Physical Medium
The T0-Vakuum is not empty. It is a structured, dynamic T0-Vakuum field Φ continuum with an amplitude ρ and
phase $\theta$ undergoes intrinsic Dynamic T0-Vakuum field, and matter acts as a local perturbation that modifies
this Dynamic T0-Vakuum field. The resulting phase and amplitude gradients propagate at light speed,
imprinting curvature onto spacetime.
Axiom 2 — All Forces and Particles Emerge from T0-Vakuum Structure
Gauge interactions and gravity originate from the geometry and dynamics of the T0-Vakuum fields. Particles
are stable, localized excitations—either dynamic or topological—in these fields.
Axiom 3 — Light Is a Phase Wave of the T0-Vakuum
Photons correspond to phase oscillations $\theta$(x) of the T0-Vakuum. Their propagation speed is set by the ratio
of T0-Vakuum stiffness to inertial density.
Axiom 4 — Lorentz Invariance Emerges from T0-Vakuum Uniformity
Uniform values of K₀ and ρ₀ across the T0-Vakuum ensure that all observers measure the same wave speed c.
Lorentz symmetry reflects the symmetry of the T0-Vakuum itself.
Axiom 5 — Gravity and Mass Arise from T0-Vakuum Amplitude Φ
Local variations in Φ determine inertial response and generate spacetime curvature. Massive particles
require Φ excitation; photons do not.
Axiom 7 — T0-Vakuum Constants K₀ and ρ₀ Are Fundamental
Electromagnetic constants ε₀ and $\mu$₀ are not fundamental. They appear as effective parameters describing
how EM probes T0-Vakuum properties. The true constants are K₀ and ρ₀, which determine c.
\begin{enumerate}
  \item Fundamental Constants of DVFT
\end{enumerate}
\begin{itemize}
  \item K₀ — T0-Vakuum Stiffness Constant
  \item Resistance of T0-Vakuum phase to spatial distortion.
  \item Fundamental.
  \item ρ₀ — T0-Vakuum Inertial Density Constant
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 97
\begin{itemize}
  \item Resistance to temporal acceleration of the T0-Vakuum phase.
  \item Fundamental.
  \item c — Speed of Light
  \item Derived from T0-Vakuum constants: c = $\sqrt$(K₀ / ρ₀).
  \item Φ₀ — T0-Vakuum Amplitude (VEV)
  \item Determines gravitational coupling and T0-Vakuum energy scale.
  \item ε₀ — Electric Permittivity (Emergent)
  \item Effective: ε₀ $\approx$ ρ₀.
  \item $\mu$₀ — Magnetic Permeability (Emergent)
  \item Effective: $\mu$₀ $\approx$ 1 / K₀.
  \item ħ — Quantum of Action
  \item Fundamental quantum constant.
  \item G — Newton’s Gravitational Constant
  \item Couples T0-Vakuum energy to curvature.
\end{itemize}
\begin{enumerate}
  \item Structural Relationships Among Constants
  \item Speed of Light:
\end{enumerate}
c = $\sqrt$(K₀ / ρ₀)
\begin{enumerate}
  \item Electromagnetic Constants:
\end{enumerate}
ε₀ = ρ₀ (effective)
$\mu$₀ = 1/K₀ (effective)
\begin{enumerate}
  \item Gravitational–T0-Vakuum Relation:
\end{enumerate}
G relates Φ₀-driven energy density to curvature.
\begin{enumerate}
  \item Mass Generation:
\end{enumerate}
m ∝ coupling $\times$ Φ₀
These show how classical constants emerge from deeper T0-Vakuum properties.
Conclusion: DVFT as a First-Principles Framework
DVFT redefines physics from the ground up by treating the T0-Vakuum itself as the foundational physical
entity. Rather than postulating constants like c, ε₀, and $\mu$₀, DVFT derives them from intrinsic T0-Vakuum
constants K₀ and ρ₀.
This achieves:
\begin{itemize}
  \item A physical origin for the speed of light,
  \item A unified T0-Vakuum origin for all forces,
  \item A mechanism for mass, curvature, and gauge symmetry breaking,
  \item A coherent interpretation connecting microphysics and cosmology.
\end{itemize}
DVFT proposes a universe where everything—energy, fields, particles, geometry—arises from a single
structured dynamic T0-Vakuum field.
\subsection{References}
\begin{enumerate}
  \item Einstein, A. (1915). Die Feldgleichungen der Gravitation. Sitzungsberichte der Preußischen Akademie
\end{enumerate}
der Wissenschaften (Berlin), 844–847.
\begin{enumerate}
  \item Einstein, A. (1905). Zur Elektrodynamik bewegter Körper. Annalen der Physik, 17, 891–921.
\end{enumerate}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 98
\begin{enumerate}
  \item Einstein, A. (1905). Ist die Trägheit eines Körpers von seinem Energieinhalt abhängig? Annalen der
\end{enumerate}
Physik, 18, 639–641.
\begin{enumerate}
  \item Schwarzschild, K. (1916). Über das Gravitationsfeld eines Massenpunktes nach der Einsteinschen
\end{enumerate}
Theorie. Sitzungsberichte der Königlich Preußischen Akademie der Wissenschaften, 189–196.
\begin{enumerate}
  \item Kerr, R. P. (1963). Gravitational field of a spinning mass as an example of algebraically special metrics.
\end{enumerate}
Physical Review Letters, 11(5), 237–238. https://doi.org/10.1103/PhysRevLett.11.237
\begin{enumerate}
  \item Hawking, S. W. (1975). Particle creation by black holes. Communications in Mathematical Physics,
\end{enumerate}
43, 199–220. https://doi.org/10.1007/BF02345020
\begin{enumerate}
  \item Wald, R. M. (1984). General Relativity. University of Chicago Press.
  \item Misner, C. W., Thorne, K. S., & Wheeler, J. A. (1973). Gravitation. W. H. Freeman.
  \item Carroll, S. M. (2004). Spacetime and Geometry: An Introduction to General Relativity.
\end{enumerate}
Addison‑Wesley.
\begin{enumerate}
  \item Weinberg, S. (1972). Gravitation and Cosmology: Principles and Applications of the General Theory
\end{enumerate}
of Relativity. Wiley.
\begin{enumerate}
  \item Will, C. M. (2014). The Confrontation between General Relativity and Experiment. Living Reviews
\end{enumerate}
in Relativity, 17, 4. https://doi.org/10.12942/lrr-2014-4
\begin{enumerate}
  \item Clifton, T., Ferreira, P. G., Padilla, A., & Skordis, C. (2012). Modified Gravity and Cosmology. Physics
\end{enumerate}
Reports, 513(1), 1–189. https://doi.org/10.1016/j.physrep.2012.01.001
\begin{enumerate}
  \item Planck Collaboration (Aghanim, N., et al.). (2020). Planck 2018 results. VI. Cosmological parameters.
\end{enumerate}
Astronomy & Astrophysics, 641, A6. https://doi.org/10.1051/0004-6361/201833910
\begin{enumerate}
  \item Riess, A. G., Yuan, W., Macri, L. M., et al. (2022). A Comprehensive Measurement of the Local Value
\end{enumerate}
of the Hubble Constant with 1 km s−1 Mpc−1 Uncertainty from the Hubble Space Telescope and the
SH0ES Team. The Astrophysical Journal Letters, 934, L7. https://doi.org/10.3847/2041-8213/ac5c5b
\begin{enumerate}
  \item Freedman, W. L., Madore, B. F., Hatt, D., et al. (2019). The Carnegie‑Chicago Hubble Program. VIII.
\end{enumerate}
An Independent Determination of the Hubble Constant Based on the Tip of the Red Giant Branch. The
Astrophysical Journal, 882, 34.
\begin{enumerate}
  \item Kolb, E. W., & Turner, M. S. (1990). The Early Universe. Addison‑Wesley.
  \item Dodelson, S. (2003). Modern Cosmology. Academic Press.
  \item Mukhanov, V. (2005). Physical Foundations of Cosmology. Cambridge University Press.
  \item Guth, A. H. (1981). Inflationary universe: A possible solution to the horizon and flatness problems.
\end{enumerate}
Physical Review D, 23, 347–356. https://doi.org/10.1103/PhysRevD.23.347
\begin{enumerate}
  \item Linde, A. D. (1982). A New Inflationary Universe Scenario. Physics Letters B, 108(6), 389–393.
\end{enumerate}
https://doi.org/10.1016/0370-2693(82)91219-9
\begin{enumerate}
  \item Penzias, A. A., & Wilson, R. W. (1965). A Measurement of Excess Antenna Temperature at 4080 Mc/s.
\end{enumerate}
The Astrophysical Journal, 142, 419–421. https://doi.org/10.1086/148307
\begin{enumerate}
  \item Smoot, G. F., et al. (1992). Structure in the COBE differential microwave radiometer first-year maps.
\end{enumerate}
The Astrophysical Journal Letters, 396, L1–L5. https://doi.org/10.1086/186504
\begin{enumerate}
  \item Zwicky, F. (1933). Die Rotverschiebung von extragalaktischen Nebeln. Helvetica Physica Acta, 6,
\end{enumerate}
110–127.
\begin{enumerate}
  \item Rubin, V. C., & Ford, W. K. Jr. (1970). Rotation of the Andromeda Nebula from a Spectroscopic
\end{enumerate}
Survey of Emission Regions. The Astrophysical Journal, 159, 379–403.
https://doi.org/10.1086/150317
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 99
\begin{enumerate}
  \item Bosma, A. (1978). The distribution and kinematics of neutral hydrogen in spiral galaxies of various
\end{enumerate}
morphological types. PhD thesis, University of Groningen.
\begin{enumerate}
  \item Navarro, J. F., Frenk, C. S., & White, S. D. M. (1996). The Structure of Cold Dark Matter Halos. The
\end{enumerate}
Astrophysical Journal, 462, 563–575. https://doi.org/10.1086/177173
\begin{enumerate}
  \item Tully, R. B., & Fisher, J. R. (1977). A new method of determining distances to galaxies. Astronomy &
\end{enumerate}
Astrophysics, 54, 661–673.
\begin{enumerate}
  \item McGaugh, S. S., Schombert, J. M., Bothun, G. D., & de Blok, W. J. G. (2000). The Baryonic Tully–
\end{enumerate}
Fisher Relation. The Astrophysical Journal Letters, 533, L99–L102.
\begin{enumerate}
  \item McGaugh, S. S. (2005). The Baryonic Tully–Fisher Relation of Galaxies with Extended Rotation
\end{enumerate}
Curves and the Stellar Mass of Rotating Galaxies. The Astrophysical Journal, 632, 859–871.
\begin{enumerate}
  \item Lelli, F., McGaugh, S. S., & Schombert, J. M. (2016). SPARC: Mass Models for 175 Disk Galaxies
\end{enumerate}
with Spitzer Photometry and Accurate Rotation Curves. The Astronomical Journal, 152, 157.
https://doi.org/10.3847/0004-6256/152/6/157
\begin{enumerate}
  \item Milgrom, M. (1983). A modification of the Newtonian dynamics as a possible alternative to the hidden
\end{enumerate}
mass hypothesis. The Astrophysical Journal, 270, 365–370. https://doi.org/10.1086/161130
\begin{enumerate}
  \item Bekenstein, J. D. (2004). Relativistic gravitation theory for the modified Newtonian dynamics
\end{enumerate}
paradigm. Physical Review D, 70, 083509. https://doi.org/10.1103/PhysRevD.70.083509
\begin{enumerate}
  \item Horndeski, G. W. (1974). Second-order scalar-tensor field equations in a four-dimensional space.
\end{enumerate}
International Journal of Theoretical Physics, 10, 363–384. https://doi.org/10.1007/BF01807638
\begin{enumerate}
  \item Gubitosi, G., Piazza, F., & Vernizzi, F. (2012). The Effective Field Theory of Dark Energy.
\end{enumerate}
arXiv:1210.0201.
\begin{enumerate}
  \item Frusciante, N., & Perenon, L. (2020). Effective Field Theory of Dark Energy: a review. Physics
\end{enumerate}
Reports, 857, 1–63. https://doi.org/10.1016/j.physrep.2020.02.004
\begin{enumerate}
  \item Woodard, R. P. (2015). Ostrogradsky’s theorem on Hamiltonian instability. Scholarpedia, 10(8),
  \item https://doi.org/10.4249/scholarpedia.32243
  \item Motohashi, H., & Suyama, T. (2015). Third order equations of motion and the Ostrogradsky instability.
\end{enumerate}
Physical Review D, 91, 085009. https://doi.org/10.1103/PhysRevD.91.085009
\begin{enumerate}
  \item Langlois, D. (2017). Degenerate Higher‑Order Scalar‑Tensor (DHOST) theories. arXiv:1707.03625.
  \item Ben Achour, J., Crisostomi, M., Koyama, K., Langlois, D., & Noui, K. (2016). Degenerate higher
\end{enumerate}
order scalar-tensor theories beyond Horndeski and disformal transformations. Physical Review D, 93,
\begin{enumerate}
  \item https://doi.org/10.1103/PhysRevD.93.124005
  \item Creminelli, P., & Vernizzi, F. (2017). Dark Energy after GW170817 and GRB170817A. Physical
\end{enumerate}
Review Letters, 119, 251302. https://doi.org/10.1103/PhysRevLett.119.251302
\begin{enumerate}
  \item Ezquiaga, J. M., & Zumalacárregui, M. (2017). Dark Energy after GW170817: dead ends and the road
\end{enumerate}
ahead. Physical Review Letters, 119, 251304. https://doi.org/10.1103/PhysRevLett.119.251304
\begin{enumerate}
  \item Langlois, D., Ezquiaga, J. M., & Zumalacárregui, M. (2018). Scalar-tensor theories and modified
\end{enumerate}
gravity in the wake of GW170817. Physical Review D, 97, 061501(R).
https://doi.org/10.1103/PhysRevD.97.061501
\begin{enumerate}
  \item Abbott, B. P., et al. (LIGO Scientific Collaboration and Virgo Collaboration). (2017). GW170817:
\end{enumerate}
Observation of Gravitational Waves from a Binary Neutron Star Inspiral. Physical Review Letters,
119, 161101. https://doi.org/10.1103/PhysRevLett.119.161101
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 100
\begin{enumerate}
  \item Abbott, B. P., et al. (LIGO Scientific Collaboration and Virgo Collaboration). (2017). Multi-messenger
\end{enumerate}
Observations of a Binary Neutron Star Merger. The Astrophysical Journal Letters, 848, L12–L16.
https://doi.org/10.3847/2041-8213/aa91c9
\begin{enumerate}
  \item Abbott, B. P., et al. (LIGO Scientific Collaboration and Virgo Collaboration). (2019). Tests of General
\end{enumerate}
Relativity with the Binary Black Hole Signals from the LIGO‑Virgo Catalog GWTC‑1. Physical
Review D, 100, 104036. https://doi.org/10.1103/PhysRevD.100.104036
\begin{enumerate}
  \item Eardley, D. M., Lee, D. L., Lightman, A. P., Wagoner, R. V., & Will, C. M. (1973). Gravitational-wave
\end{enumerate}
observations as a tool for testing relativistic gravity. Physical Review Letters, 30, 884–886.
https://doi.org/10.1103/PhysRevLett.30.884
\begin{enumerate}
  \item Nishizawa, A., Taruya, A., Hayama, K., Kawamura, S., & Sakagami, M. (2009). Probing non-tensorial
\end{enumerate}
polarizations of stochastic gravitational-wave backgrounds with ground-based laser interferometers.
Physical Review D, 79, 082002. https://doi.org/10.1103/PhysRevD.79.082002
\begin{enumerate}
  \item Vainshtein, A. I. (1972). To the problem of nonvanishing gravitation mass. Physics Letters B, 39(3),
\end{enumerate}
393–394. https://doi.org/10.1016/0370-2693(72)90147-5
\begin{enumerate}
  \item Babichev, E., & Deffayet, C. (2013). An introduction to the Vainshtein mechanism. Classical and
\end{enumerate}
Quantum Gravity, 30(18), 184001. https://doi.org/10.1088/0264-9381/30/18/184001
\begin{enumerate}
  \item Khoury, J., & Weltman, A. (2004). Chameleon cosmology. Physical Review D, 69, 044026.
\end{enumerate}
https://doi.org/10.1103/PhysRevD.69.044026
\begin{enumerate}
  \item Burrage, C., & Sakstein, J. (2018). Tests of Chameleon Gravity. Living Reviews in Relativity, 21, 1.
\end{enumerate}
https://doi.org/10.1007/s41114-018-0011-x
\begin{enumerate}
  \item Schrödinger, E. (1926). Quantisierung als Eigenwertproblem (Parts I–IV). Annalen der Physik, 79–81
\end{enumerate}
(1926).
\begin{enumerate}
  \item Heisenberg, W. (1927). Über den anschaulichen Inhalt der quantentheoretischen Kinematik und
\end{enumerate}
Mechanik. Zeitschrift für Physik, 43, 172–198. https://doi.org/10.1007/BF01397280
\begin{enumerate}
  \item Born, M. (1926). Zur Quantenmechanik\footnote{Siehe auch T0-Dokument: \texttt{020_T0_QM-QFT\footnote{Siehe auch T0-Dokument: \texttt{097_QFT_De.pdf}}-RT_De.pdf}} der Stoßvorgänge. Zeitschrift für Physik, 37, 863–867.
\end{enumerate}
https://doi.org/10.1007/BF01397477
\begin{enumerate}
  \item von Neumann, J. (1932). Mathematische Grundlagen der Quantenmechanik. Springer (English transl.:
\end{enumerate}
Mathematical Foundations of Quantum Mechanics, Princeton Univ. Press, 1955).
\begin{enumerate}
  \item Sakurai, J. J., & Napolitano, J. (2017). Modern Quantum Mechanics (2nd ed.). Cambridge University
\end{enumerate}
Press.
\begin{enumerate}
  \item Zurek, W. H. (2003). Decoherence, einselection, and the quantum origins of the classical. Reviews of
\end{enumerate}
Modern Physics, 75, 715–775. https://doi.org/10.1103/RevModPhys.75.715
\begin{enumerate}
  \item Joos, E., Zeh, H. D., Kiefer, C., Giulini, D., Kupsch, J., & Stamatescu, I.-O. (2003). Decoherence and
\end{enumerate}
the Appearance of a Classical World in Quantum Theory (2nd ed.). Springer.
https://doi.org/10.1007/978-3-662-05328-7
\begin{enumerate}
  \item Yang, C. N., & Mills, R. L. (1954). Conservation of isotopic spin and isotopic gauge invariance.
\end{enumerate}
Physical Review, 96(1), 191–195. https://doi.org/10.1103/PhysRev.96.191
\begin{enumerate}
  \item Faddeev, L. D., & Popov, V. N. (1967). Feynman diagrams for the Yang–Mills field. Physics Letters
\end{enumerate}
B, 25(1), 29–30. https://doi.org/10.1016/0370-2693(67)90067-6
\begin{enumerate}
  \item Peskin, M. E., & Schroeder, D. V. (1995). An Introduction to Quantum Field Theory. Addison‑Wesley.
  \item Weinberg, S. (1995). The Quantum Theory of Fields, Vol. I: Foundations. Cambridge University Press.
  \item Clay Mathematics Institute. (2000–present). Yang–Mills existence and mass gap (Millennium Prize
\end{enumerate}
Problem). https://www.claymath.org/millennium/yang-mills-the-maths-gap/
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 101
\begin{enumerate}
  \item Jaffe, A. (2000). Quantum Yang–Mills Theory (CMI Millennium Prize Problem description; Jaffe–
\end{enumerate}
Witten). Clay Mathematics Institute. (PDF commonly circulated as “yangmills.pdf”).
\begin{enumerate}
  \item Sakharov, A. D. (1967). Violation of CP invariance, C asymmetry, and baryon asymmetry of the
\end{enumerate}
universe. JETP Letters, 5, 24–27.
\begin{enumerate}
  \item Penrose, R. (1996). On Gravity’s role in Quantum State Reduction. General Relativity and Gravitation,
\end{enumerate}
28, 581–600. https://doi.org/10.1007/BF02105068
\begin{enumerate}
  \item Diósi, L. (1989). Models for universal reduction of macroscopic quantum fluctuations. Physical
\end{enumerate}
Review A, 40, 1165–1174. https://doi.org/10.1103/PhysRevA.40.1165
\begin{enumerate}
  \item Bassi, A., Lochan, K., Satin, S., Singh, T. P., & Ulbricht, H. (2013). Models of wave-function collapse,
\end{enumerate}
underlying theories, and experimental tests. Reviews of Modern Physics, 85, 471–527.
https://doi.org/10.1103/RevModPhys.85.471
\begin{enumerate}
  \item Arndt, M., & Hornberger, K. (2014). Testing the limits of quantum mechanical superpositions. Nature
\end{enumerate}
Physics, 10, 271–277. https://doi.org/10.1038/nphys2863
\begin{enumerate}
  \item Marletto, C., & Vedral, V. (2017). Gravitationally Induced Entanglement between Two Massive
\end{enumerate}
Particles is Sufficient Evidence of Quantum Effects in Gravity. Physical Review Letters, 119, 240402.
https://doi.org/10.1103/PhysRevLett.119.240402
\begin{enumerate}
  \item Margalit, Y., Dobkowski, O., Zhou, Z., et al. (2021). Realization of a complete Stern–Gerlach
\end{enumerate}
interferometer: Toward a test of quantum gravity. Science Advances, 7(22), eabg2879.
https://doi.org/10.1126/sciadv.abg2879
\begin{enumerate}
  \item Roura, A. (2020). Gravitational Redshift in Quantum-Clock Interferometry. Physical Review X, 10,
  \item https://doi.org/10.1103/PhysRevX.10.021014
  \item Dobkowski, O., Trok, B., Skakunenko, P., et al. (2025). Observation of the quantum equivalence
\end{enumerate}
principle for matter-waves. arXiv:2502.14535.
\begin{enumerate}
  \item This paper positions Dynamic T0-Vakuum Field Theory (DVFT) as a transformative approach to unifying
\end{enumerate}
general relativity, quantum mechanics, and cosmology by reimagining space as a dynamic T0-Vakuum
field that has amplitude and phase. This intrinsic dynamic T0-Vakuum field behavior open a new
theoretical and observational possibilities for understanding the universe’s structure and force

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
