\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{FFGFT Kapitel 5: PROBLEMS IN GENERAL RELATIVITY\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{31. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


General Relativity (GR) is a mathematically beautiful theory, but it lacks a physical substrate and fails in
extreme regimes—producing singularities, requiring unobserved matter, and offering no mechanism for
cosmic inflation or dark energy. The Fundamental Fractal-Geometric Field Theory (FFGFT) replaces these gaps by
modeling spacetime as a dynamic T0-Vakuum field. This chapter summarizes the major problems of GR and
how FFGFT provides deeper, physical, and internally consistent solutions.
The exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}stence of a dynamic T0-Vakuum field introduces a dynamical character to spacetime itself. Though
$\Phi$vac breaks global time-translation symmetry at the solution level, the underlying Lagrangian\footnote{Siehe auch T0-Dokument: \texttt{027_T0_lagrndian_De.pdf}} remains
Lorentz invariant. Every observer perceives $\Phi$vac as the same dynamic T0-Vakuum field state in their frame
of reference.
\begin{enumerate}
  \item Origin of the Curvature
\end{enumerate}
The T0-Vakuum field carries energy–momentum. Its stress–energy tensor directly enters Einstein's equation.
Thus, curvature is caused by the T0-Vakuum’s internal dynamics. Curvature is not a mysterious property of
geometry but a macroscopic field response to dynamic T0-Vakuum field distortions. FFGFT derives curvature
from dynamics. Distorted dynamic T0-Vakuum field carries stress–energy:
T$\mu$ν($\Phi$) = $\partial$$\mu$$\Phi$* $\partial$ν$\Phi$ + $\partial$$\mu$$\Phi$ $\partial$ν$\Phi$* − g$\mu$ν(…)
Phase gradients δ$\theta$ propagate at light speed, modifying T$\mu$ν($\Phi$). Einstein's GR equation then becomes:
G$\mu$ν = 8πG ( T$\mu$ν (m) + T$\mu$ν($\Phi$))
The gravitational potential is emergent from the T0-Vakuum phase pattern. Thus, curvature is the macroscopic
imprint of dynamic T0-Vakuum field structure. Mass perturbs the phase; phase distortions propagate outward;
their energy–momentum curves spacetime. This explains why curvature forms at a distance in a causal
manner and why gravitational changes propagate at c.
\begin{enumerate}
  \item Curvature Without Physical Cause
\end{enumerate}
GR states that curvature is determined by the Einstein equation G_{$\mu$ν} = 8πGT_{$\mu$ν}, but it does not
explain what actually curves. FFGFT explains curvature as the stress–energy of the dynamic T0-Vakuum field,
where phase gradients $\partial$$\theta$ create gravitational curvature. Dynamics provides a physical mechanism for
gravity.
\begin{enumerate}
  \item Black Hole Singularity Resolution
\end{enumerate}
Classical GR predicts singularities where curvature diverges to infinity. Such infinities signal a breakdown
of the theory. In FFGFT, the T0-Vakuum field $\Phi$ cannot support infinite phase gradients due to nonlinear
saturation in its potential V(|$\Phi$|²). As a collapsing object approaches the classical singularity, the T0-Vakuum
amplitude ρ decreases while the phase gradient $\partial$$\theta$ increases but never diverges. The phase reaches a
saturation limit determined by T0-Vakuum stiffness, preventing infinite curvature:
|$\partial$$\theta$| < $\theta$max
The center of a black hole becomes a phase defect of $\Phi$ rather than a point of infinite density. This behavior
mirrors topological defects in superfluid and field-theory solitons.
Thus, FFGFT naturally resolves singularities by replacing them with finite-energy T0-Vakuum-phase defects,
maintaining causality and finiteness of curvature.
FFGFT introduces field dynamics that restrict infinitely large gradients by physical T0-Vakuum stiffness.
\begin{enumerate}
  \item Big Bang Singularity Resolution
\end{enumerate}
GR cannot describe the origin of the universe because the Big Bang is a singularity. FFGFT replaces it with
a T0-Vakuum phase transition from ρ $\approx$ 0 to ρ₀, producing inflation, reheating, and the origin of space and time
without infinities.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 14
\begin{enumerate}
  \item No Explanation for Inflation
\end{enumerate}
GR needs an ad-hoc inflation field. FFGFT naturally generates inflation from the T0-Vakuum potential V(ρ)
and the intrinsic phase $\theta$(t). Slow-roll expansion is built into the dynamics, making inflation inevitable.
\begin{enumerate}
  \item Dark Matter Problem
\end{enumerate}
GR requires unseen matter to explain galaxy rotation curves, lensing, and cluster masses. FFGFT explains
these effects through long-range T0-Vakuum-phase distortions which create additional curvature, producing
dark-matter-like behavior without introducing new particles.
\begin{enumerate}
  \item Dark Energy
\end{enumerate}
GR’s cosmological constant problem arises from a mismatch of 120 orders of magnitude. FFGFT attributes
dark energy to residual dynamic T0-Vakuum field energy, ε_vac = ρ₀²$\theta$̇² + V(ρ₀), providing a natural physical
source of accelerated expansion.
\begin{enumerate}
  \item No Mechanism for Expansion of Space
\end{enumerate}
GR describes expansion mathematically but does not explain why it occurs. FFGFT explains expansion
through T0-Vakuum amplitude growth ρ(t) controls the scale factor a(t). Space expands because the T0-Vakuum
evolves.
\begin{enumerate}
  \item Why Gravity is Always Attractive
\end{enumerate}
GR postulates attraction but does not explain it. FFGFT explains attraction through T0-Vakuum phase tension:
mass distorts phase gradients, and objects move along paths minimizing T0-Vakuum energy.
Conclusion
FFGFT resolves every major theoretical limitation of General Relativity by introducing a dynamic T0-Vakuum
field whose amplitude and phase structure create curvature, remove singularities and explain cosmic
expansion.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_FFGFT-alles\_De.pdf} -- Vollständiges FFGFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
