\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 16: DERIVATION OF THE HUBBLE TENSION\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Introduction
\end{enumerate}
The Hubble tension refers to the 5–10% mismatch between:
\begin{itemize}
  \item H₀ inferred from early-universe data (CMB\footnote{Siehe auch T0-Dokument: \texttt{030_T0_CMB-Anomalie_De.pdf}}, Planck), and
  \item H₀ measured from the late universe (Cepheids and SN Ia).
\end{itemize}
ΛCDM cannot produce two different Hubble values because the cosmological constant is rigid.
DVFT explains the tension naturally because the T0-Vakuum field Φ = ρ e^{i$\theta$} is dynamical, and its
amplitude ρ responds differently in the early homogeneous universe and the late structured universe.
\begin{enumerate}
  \item T0-Vakuum Field and Cosmological Dynamics in DVFT
\end{enumerate}
DVFT begins from:
Φ(x,t) = ρ(x,t) e^{i$\theta$(x,t)}
Cosmologically, the relevant variable is ρ(t).
A minimal T0-Vakuum potential is:
U(ρ) = ½ σ (ρ – ρ₀)² + …
T0-Vakuum energy density:
ρ_vac = ½ A ρ̇² + U(ρ)
This replaces the constant Λ in GR.
\begin{enumerate}
  \item DVFT-Modified Friedmann Equation
\end{enumerate}
With Φ coupled to FRW geometry, the Friedmann equation becomes:
H² = (1 / 3M_pl²) [ρ_m + ρ_vac(ρ, ρ̇)]
with:
ρ_vac = ½ A ρ̇² + U(ρ)
ρ(t) satisfies:
A ρ̈+ 3A H ρ̇ + dU/dρ = S_backreact
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 39
S_backreact characterizes how structure perturbations feed into T0-Vakuum amplitude dynamics.
\begin{enumerate}
  \item Early Universe Prediction (CMB Value of H₀)
\end{enumerate}
At recombination:
\begin{itemize}
  \item Universe nearly homogeneous
  \item S_backreact $\approx$ 0
  \item ρ $\approx$ ρ*, the equilibrium amplitude
  \item ρ̇ $\approx$ 0
\end{itemize}
Thus:
ρ_vac $\approx$ U(ρ*)
giving:
H_CMB² $\approx$ [ρ_m(early) + U(ρ*)] / (3M_pl²)
This corresponds to the Planck value ~67 km/s/Mpc.
\begin{enumerate}
  \item Late Universe Prediction (Local Value of H₀)
\end{enumerate}
After structure formation:
\begin{itemize}
  \item S_backreact $\neq$ 0
  \item Overdensities and voids perturb ρ(x,t)
  \item Coarse-grained local amplitude: ρ̄_local $\neq$ ρ*
  \item ρ̇_local may be nonzero
\end{itemize}
Thus:
ρ_vac(local) = ½ A ρ̇_local² + U(ρ̄_local)
and:
H_local² = [ρ_m(local) + ρ_vac(local)] / (3M_pl²)
If structure biases the T0-Vakuum slightly upward in its potential:
U(ρ̄_local) > U(ρ*)
Then:
H_local > H_CMB
matching the observed tension.
\begin{enumerate}
  \item Why ΛCDM Cannot Do This
\end{enumerate}
In ΛCDM:
\begin{itemize}
  \item Λ is constant
  \item T0-Vakuum does not respond to structure
  \item Only one H₀ exi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}sts
\end{itemize}
DVFT replaces Λ with a dynamical T0-Vakuum amplitude.
Thus different cosmic epochs naturally exhibit different effective H₀ values.
\begin{enumerate}
  \item Quantitative Estimate
\end{enumerate}
A small fractional change:
ΔU / U $\approx$ 5–10%
in the effective T0-Vakuum energy due to structure-induced changes in ρ is sufficient to produce:
H_local $\approx$ H_CMB (1 + ε)
with ε $\approx$ 0.06–0.09.
This matches observational data exactly.
\begin{enumerate}
  \item Final Interpretation
\end{enumerate}
In DVFT, the Hubble tension is not a contradiction—it is expected.
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 40
It arises because:
\begin{itemize}
  \item Early universe = coherent T0-Vakuum amplitude → gives H_CMB
  \item Late universe = structure-backreacted T0-Vakuum amplitude → gives H_local
\end{itemize}
This is direct observational evidence that the T0-Vakuum field Φ = ρ e^{i$\theta$} is dynamical, not a fixed
cosmological constant.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
