\documentclass[12pt,a4paper]{article}

\input{../T0_preamble_shared_De.tex}

\title{DVFT Kapitel 17: ALTERNATIVE TO GR + ΛCDM\\
\large Angepasst an T0 Zeit-Masse-Dualitätstheorie}

\author{Originalkonzept: Satish B. Thorwe\\
Angepasst an T0-Theorie: Johann Pascher}

\date{27. December 2025}

\begin{document}

\maketitle

\tableofcontents

\newpage


\begin{enumerate}
  \item Introduction
\end{enumerate}
This document explains, in a rigorous and logically complete manner, why the Dynamic T0-Vakuum Field
Theory(DVFT) eliminates the need for the cosmological constant, invalidates inflation, removes the
foundations of ΛCDM, and supersedes all geometric or metric-based cosmological frameworks derived
from General Relativity (GR).
\begin{enumerate}
  \item The Cosmological Constant as the Central Failure of Modern Cosmology
\end{enumerate}
The mismatch between Λ predicted by Quantum Field Theory and Λ inferred from cosmology is ~10^120
— the largest discrepancy in the history of physics.
This alone indicates:
\begin{itemize}
  \item ΛCDM cannot be fundamental,
  \item GR + Λ is an effective approxi\footnote{Siehe auch T0-Dokument: \texttt{009_T0_xi_ursprung_De.pdf}}mation, not a physical theory,
  \item the T0-Vakuum cannot be a geometric entity.
\end{itemize}
The cosmological constant problem is not a puzzle — it is evidence that the underlying ontology is
incorrect.
\begin{enumerate}
  \item Why All Current Cosmological Models Fail
\end{enumerate}
General Relativity (GR):
\begin{itemize}
  \item offers no physical explanation for Λ,
  \item requires dark matter,
  \item requires inflation,
  \item predicts singularities,
  \item cannot quantize gravity.
\end{itemize}
Inflationary models:
\begin{itemize}
  \item were invented solely to fix GR's horizon and flatness problems,
  \item have no physical T0-Vakuum origin,
  \item require finely tuned potentials,
  \item introduce unobservable fields.
\end{itemize}
Quantum Field Theory T0-Vakuum:
\begin{itemize}
  \item predicts T0-Vakuum energy density 120 orders too large,
  \item cannot include gravitation consistently.
\end{itemize}
Modified gravity (MOND, f(R), TeVeS):
\begin{itemize}
  \item work only at galactic scales,
  \item break at cosmological scales,
  \item lack microphysical interpretation.
\end{itemize}
String/LQG cosmologies:
\begin{itemize}
  \item generate no definite predictions,
  \item require vast model freedom,
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 41
\begin{itemize}
  \item cannot explain Λ or dark energy.
\end{itemize}
These failures arise because all frameworks assume either:
\begin{itemize}
  \item ❌ geometry is fundamental (GR),
  \item ❌ quantum fields sit on geometry (QFT\footnote{Siehe auch T0-Dokument: \texttt{097_QFT_De.pdf}}).
\end{itemize}
Both assumptions are incorrect if the T0-Vakuum is physical.
\begin{enumerate}
  \item DVFT Replaces the Cosmological Constant with T0-Vakuum Amplitude Dynamics
\end{enumerate}
DVFT defines the T0-Vakuum as a physical field:
Φ = ρ e^{i$\theta$},
with a T0-Vakuum potential:
U(ρ) = (1/2) σ (ρ - ρ₀)².
Cosmic acceleration arises from relaxation of the T0-Vakuum amplitude ρ, not from any constant Λ.
Thus:
\begin{itemize}
  \item Λ is not fundamental,
  \item Λ is not constant,
  \item Λ is an artifact of misinterpreting U(ρ) geometrically.
\end{itemize}
This removes the cosmological constant problem completely.
DVFT does not solve Λ — it replaces the concept entirely.
\begin{enumerate}
  \item DVFT Explains CMB\footnote{Siehe auch T0-Dokument: \texttt{030_T0_CMB-Anomalie_De.pdf}} Uniformity Without Inflation
\end{enumerate}
GR cannot explain CMB temperature uniformity; inflation was invented to repair this.
DVFT predicts:
\begin{itemize}
  \item an initially coherent T0-Vakuum phase $\theta$,
  \item uniform amplitude ρ across all space,
  \item no distinct “regions” before expansion.
\end{itemize}
Therefore:
\begin{itemize}
  \item the entire early universe shared a single T0-Vakuum state,
  \item temperature uniformity was intrinsic,
  \item no horizon problem exists.
\end{itemize}
CMB uniformity is direct empirical support for DVFT's T0-Vakuum ontology.
\begin{enumerate}
  \item DVFT Explains Galaxy Rotation Without Dark Matter
\end{enumerate}
DVFT deep-field equation:
g² = a₀ g_N
naturally reproduces flat rotation curves and the baryonic Tully–Fisher relation:
v_c⁴ = G M_b a₀.
No dark matter halos are required.
Dark matter appears only when the T0-Vakuum is incorrectly modeled using GR's geometry instead of DVFT's
amplitude-phase structure.
\begin{enumerate}
  \item DVFT Predicts Cosmic Acceleration Without Λ
\end{enumerate}
Since expansion is driven by U(ρ), not Λ:
\begin{itemize}
  \item acceleration is dynamical, not constant,
  \item de Sitter space is not fundamental,
  \item observed late-time acceleration matches DVFT predictions,
  \item no fine-tuned cosmological constant is required.
\end{itemize}
International Journal for Multidisciplinary Research (IJFMR)
E-ISSN: 2582-2160 ● Website: www.ijfmr.com ● Email: editor@ijfmr.com
IJFMR250664112 Volume 7, Issue 6, November-December 2025 42
\begin{enumerate}
  \item DVFT Provides Yang–Mills Mass Gap Automatically
\end{enumerate}
The Yang–Mills Mass Gap emerges from T0-Vakuum phase stiffness B:
m_gap² ∼ B ρ₀².
No other theory provides a natural physical origin for the mass gap.
This is strong evidence for DVFT’s T0-Vakuum-field structure.
\begin{enumerate}
  \item DVFT Eliminates Big Bang and Black Hole Singularities
\end{enumerate}
Because ρ saturates at a maximum value, singularities cannot occur.
Instead:
\begin{itemize}
  \item Big Bang = release of stored amplitude energy,
  \item Black hole core = finite-density T0-Vakuum-amplitude saturation,
  \item no divergences in curvature,
  \item no undefined geometry.
\end{itemize}
This is impossible in GR but automatic in DVFT.
\begin{enumerate}
  \item DVFT Unifies All Interactions
\end{enumerate}
DVFT unifies:
\begin{itemize}
  \item gravity ($\nabla$ρ),
  \item electromagnetism ($\nabla$$\theta$),
  \item weak and strong interactions (phase topology),
  \item quantum mechanics ($\theta$-coherence),
  \item cosmology (U(ρ)),
\end{itemize}
from the single T0-Vakuum field Φ = ρ e^{i$\theta$}.
This replaces both GR and QFT as fundamental theories.
Conclusion
DVFT provides:
\begin{itemize}
  \item physical T0-Vakuum ontology,
  \item automatic solutions to cosmological inconsistencies,
  \item removal of Λ,
  \item natural explanation for CMB uniformity,
  \item galaxy curves without dark matter,
  \item acceleration without cosmological constant,
  \item singularity elimination,
  \item unification of all forces.
\end{itemize}
Therefore:
The cosmological constant problem, inflation problem, dark matter hypothesis, and GR-based cosmology
collectively point to a single conclusion:
DVFT is the only cosmological theory that remains consistent with all observations and solves all
foundational problems simultaneously. Thus DVFT stands not as an alternative, but as the fundamental
cosmological theory.

\section{Referenzen zu T0-Dokumenten}

Dieses Kapitel steht in Zusammenhang mit folgenden T0-Dokumenten im Repository \texttt{2/pdf/}:

\begin{itemize}
  \item \texttt{002\_T0\_Grundlagen\_De.pdf} -- T0 Zeit-Masse-Dualität Grundlagen
  \item \texttt{004\_T0\_Energie\_De.pdf} -- T0 Energiefeld-Theorie
  \item \texttt{009\_T0\_xi\_ursprung\_De.pdf} -- Ursprung des geometrischen Parameters $\xi$
  \item \texttt{201\_DVFT-alles\_De.pdf} -- Vollständiges DVFT-Dokument (Rahmenwerk)
\end{itemize}

\end{document}
