% Chapter file: 047_neutrino-Formel_En_ch.tex
% Source: 047_neutrino-Formel_En.tex
% No preamble, no headers/footers, no page numbers

% \chapter{\Huge\textbf{T0 Model: Unified Neutrino Formula Structure}}

\begin{abstract}
		This document presents a mathematically consistent formula structure for neutrino calculations within the T0 model, based on the hypothesis of equal masses for all flavor states (\(\nu_e, \nu_\mu, \nu_\tau\)). The neutrino mass is derived from the photon analogy (\(\frac{\xipar^2}{2}\)-suppression), and oscillations are explained by geometric phases based on \( T_x \cdot m_x = 1 \), with quantum numbers (\(n, \ell, j\)) determining phase differences. A plausible target value for the neutrino mass (\(m_\nu = 15 \text{ meV}\)) is derived from empirical data (cosmological constraints). The T0 model is based on speculative geometric harmonies without empirical support and is highly likely to be incomplete or incorrect. Scientific integrity requires a clear distinction between mathematical correctness and physical validity.
	\end{abstract}
	

	\section{Preamble: Scientific Integrity}
	
	\begin{warning}
		\textbf{CRITICAL LIMITATION:} The following formulas for neutrino masses are \textbf{speculative extrapolations} based on the untested hypothesis that neutrinos follow geometric harmonies and all flavor states have equal masses. This hypothesis has \textbf{no empirical basis} and is highly likely to be incomplete or incorrect. The mathematical formulas are nonetheless internally consistent and error-free.
		
		\vspace{0.5cm}
		\textbf{Scientific Integrity Requires:}
		\begin{itemize}
			\item Honesty about the speculative nature of predictions
			\item Mathematical correctness despite physical uncertainty
			\item Clear separation between hypotheses and verified facts
		\end{itemize}
	\end{warning}
	
	\section{Neutrinos as ''Near-Massless Photons'': The T0 Photon Analogy}
	
	\begin{speculation}
		\textbf{Fundamental T0 Insight:} Neutrinos can be understood as ''damped photons.''
		
		The remarkable similarity between photons and neutrinos suggests a deeper geometric kinship:
		\begin{itemize}
			\item \textbf{Speed:} Both propagate at nearly the speed of light
			\item \textbf{Penetration:} Both have extreme penetration capabilities
			\item \textbf{Mass:} Photon is exactly massless, neutrino is nearly massless
			\item \textbf{Interaction:} Photon interacts electromagnetically, neutrino interacts weakly
		\end{itemize}
	\end{speculation}
	
	\subsection{Photon-Neutrino Correspondence}
	
	\begin{important}
		\textbf{Physical Parallels:}
		\begin{align}
			\text{Photon:} \quad &E^2 = (pc)^2 + 0 \quad \text{(perfectly massless)} \\
			\text{Neutrino:} \quad &E^2 = (pc)^2 + \left(\sqrt{\frac{\xipar^2}{2}} m c^2\right)^2 \quad \text{(nearly massless)}
		\end{align}
		
		\textbf{Speed Comparison:}
		\begin{align}
			v_\gamma &= c \quad \text{(exact)} \\
			v_\nu &= c \times \left(1 - \frac{\xipar^2}{2}\right) \approx 0.9999999911 \times c
		\end{align}
		
		The speed difference is only \(8.89 \times 10^{-9}\) -- practically unmeasurable!
	\end{important}
	
	\subsection{Double \(\xipar\)-Suppression from Photon Analogy}
	
	\begin{formula}
		\textbf{T0 Hypothesis:} Neutrino = Photon with Geometric Double Damping
		
		If neutrinos are ''near-photons,'' two suppression factors arise:
		\begin{itemize}
			\item \textbf{First \(\xipar\) Factor:} ''Near massless'' (like a photon, but not perfect)
			\item \textbf{Second \(\xipar\) Factor:} ''Weak interaction'' (geometric coupling)
			\item \textbf{Result:} \(m_\nu \propto \frac{\xipar^2}{2}\), consistent with the speed difference \(v_\nu = c \times \left(1 - \frac{\xipar^2}{2}\right)\)
		\end{itemize}
		
		\textbf{Interaction Strength Comparison:}
		\begin{align}
			\sigma_\gamma &\sim \alpha_{\text{EM}} \approx \frac{1}{137} \\
			\sigma_\nu &\sim \frac{\xipar^2}{2} \times G_F \approx 8.888888 \times 10^{-9}
		\end{align}
		
		The ratio \(\sigma_\nu/\sigma_\gamma \sim \frac{\xipar^2}{2}\) confirms the geometric suppression!
	\end{formula}
	
	\section{Neutrino Oscillations}
	
	\begin{important}
		\textbf{Neutrino Oscillations:} Neutrinos can change their identity (flavor) during flight -- a phenomenon known as neutrino oscillation. A neutrino produced as an electron neutrino (\(\nu_e\)) can later be detected as a muon neutrino (\(\nu_\mu\)) or tau neutrino (\(\nu_\tau\)) and vice versa.
		
		In standard physics, this behavior is described by the mixing of mass eigenstates (\(\nu_1, \nu_2, \nu_3\)) connected to flavor states (\(\nu_e, \nu_\mu, \nu_\tau\)) via the PMNS matrix (Pontecorvo-Maki-Nakagawa-Sakata):
		\begin{align}
			\begin{pmatrix}
				\nu_e \\ \nu_\mu \\ \nu_\tau
			\end{pmatrix}
			=
			U_{\text{PMNS}}
			\begin{pmatrix}
				\nu_1 \\ \nu_2 \\ \nu_3
			\end{pmatrix},
		\end{align}
		where \(U_{\text{PMNS}}\) is the mixing matrix.
		
		Oscillations depend on mass differences \(\Delta m^2_{ij} = m_i^2 - m_j^2\) and mixing angles. Current experimental data (2025) provide:
		\begin{align}
			\Delta m^2_{21} &\approx 7.53 \times 10^{-5} \text{ eV}^2 \quad \text{[Solar]} \\
			\Delta m^2_{32} &\approx 2.44 \times 10^{-3} \text{ eV}^2 \quad \text{[Atmospheric]} \\
			m_\nu &> 0.06 \text{ eV} \quad \text{[At least one neutrino, 3}\sigma\text{]}
		\end{align}
		
		\textbf{Implications for T0:}
		\begin{itemize}
			\item The T0 model postulates equal masses for flavor states (\(\nu_e, \nu_\mu, \nu_\tau\)), implying \(\Delta m^2_{ij} = 0\), which is incompatible with standard oscillations.
			\item To explain oscillations, the T0 model uses geometric phases based on \( T_x \cdot m_x = 1 \), with quantum numbers (\(n, \ell, j\)) determining phase differences.
		\end{itemize}
	\end{important}
	
	\subsection{Geometric Phases as Oscillation Mechanism}
	
	\begin{speculation}
		\textbf{T0 Hypothesis: Geometric Phases for Oscillations}
		
		To reconcile the hypothesis of equal masses (\(m_{\nu_e} = m_{\nu_\mu} = m_{\nu_\tau} = m_\nu\)) with neutrino oscillations, it is speculated that oscillations in the T0 model are caused by geometric phases rather than mass differences. This is based on the T0 relation:
		\[
		T_x \cdot m_x = 1,
		\]
		where \(m_x = m_\nu = 4.54 \text{ meV}\) is the neutrino mass, and \(T_x\) is a characteristic time or frequency:
		\[
		T_x = \frac{1}{m_\nu} = \frac{1}{4.54 \times 10^{-3} \text{ eV}} \approx 2.2026 \times 10^2 \text{ eV}^{-1} \approx 1.449 \times 10^{-13} \text{ s}.
		\]
		
		The geometric phase is determined by the T0 quantum numbers (\(n, \ell, j\)):
		\[
		\phi_{\text{geo}, i} \propto f(n, \ell, j) \cdot \frac{L}{E} \cdot \frac{1}{T_x},
		\]
		where \(f(n, \ell, j) = \frac{n^6}{\ell^3}\) (or 1 for \(\ell = 0\)) are the geometric factors:
		\begin{align}
			f_{\nu_e} &= 1, \\
			f_{\nu_\mu} &= 64, \\
			f_{\nu_\tau} &= 91.125.
		\end{align}
		
		\textbf{Calculated Phase Differences:}
		\begin{align}
			\phi_{\nu_e} &\propto 1 \cdot \frac{L}{E} \cdot \frac{1}{T_x}, \\
			\phi_{\nu_\mu} &\propto 64 \cdot \frac{L}{E} \cdot \frac{1}{T_x}, \\
			\phi_{\nu_\tau} &\propto 91.125 \cdot \frac{L}{E} \cdot \frac{1}{T_x}.
		\end{align}
		
		These phase differences could cause oscillations between flavor states without requiring different masses. The exact form of the oscillation probability requires further development but remains highly speculative.
		
		\textbf{WARNING:} This approach is purely hypothetical and lacks empirical confirmation. It contradicts the established theory that oscillations are caused by \(\Delta m^2_{ij} \neq 0\).
	\end{speculation}
	
	\section{Fundamental Constants and Units}
	
	\subsection{Base Parameters}
	
	\begin{formula}
		\textbf{T0 Base Constants:}
		\begin{align}
			\xipar &= \frac{4}{3} \times 10^{-4} \approx 1.333333 \times 10^{-4} \quad \text{[dimensionless]} \\
			\frac{\xipar^2}{2} &= \frac{\left(\frac{4}{3} \times 10^{-4}\right)^2}{2} \approx 8.888888 \times 10^{-9} \quad \text{[dimensionless]} \\
			v &= 246.22 \text{ GeV} \quad \text{[Higgs VEV]} \\
			\hbar c &= 0.19733 \text{ GeV·fm} \quad \text{[Conversion constant]} \\
			T_x &= \frac{1}{4.54 \times 10^{-3} \text{ eV}} \approx 2.2026 \times 10^2 \text{ eV}^{-1} \approx 1.449 \times 10^{-13} \text{ s} \quad \text{[T0 Mass]}
		\end{align}
	\end{formula}
	
	\subsection{Unit Conventions}
	
	\begin{important}
		\textbf{Consistent Unit Hierarchy:}
		\begin{align}
			\text{Standard:} &\quad \text{GeV} \\
			\text{Submultiples:} &\quad 1 \text{ eV} = 10^{-9} \text{ GeV} \\
			&\quad 1 \text{ meV} = 10^{-12} \text{ GeV} = 10^{-3} \text{ eV} \\
			\text{Masses:} &\quad m[\text{GeV}/c^2] = E[\text{GeV}]/c^2 \approx E[\text{GeV}] \text{ (natural units)} \\
			\text{Time:} &\quad 1 \text{ eV}^{-1} \approx 6.582 \times 10^{-16} \text{ s}
		\end{align}
	\end{important}
	
	\section{Charged Lepton Reference Masses}
	
	\subsection{Precise Experimental Values (PDG 2024)}
	
	\begin{experimental}
		\textbf{Verified Particle Masses:}
		\begin{align}
			m_e &= 0.51099895000 \times 10^{-3} \text{ GeV} = 510.99895 \text{ keV} \\
			m_\mu &= 105.6583745 \times 10^{-3} \text{ GeV} = 105.6583745 \text{ MeV} \\
			m_\tau &= 1776.86 \times 10^{-3} \text{ GeV} = 1.77686 \text{ GeV}
		\end{align}
		
		\textbf{Unit Conversion to eV:}
		\begin{align}
			m_e &= 510998.95 \text{ eV} = 510998950 \text{ meV} \\
			m_\mu &= 105658374.5 \text{ eV} \\
			m_\tau &= 1776860000 \text{ eV}
		\end{align}
	\end{experimental}
	
	\section{Neutrino Quantum Numbers (T0 Hypothesis)}
	
	\subsection{Postulated Quantum Number Assignment}
	
	\begin{speculation}
		\textbf{Hypothetical Neutrino Quantum Numbers:}
		\begin{align}
			\nu_e: &\quad n=1, \ell=0, j=1/2 \quad \text{[Ground state neutrino]} \\
			\nu_\mu: &\quad n=2, \ell=1, j=1/2 \quad \text{[First excitation]} \\
			\nu_\tau: &\quad n=3, \ell=2, j=1/2 \quad \text{[Second excitation]}
		\end{align}
		
		\textbf{Role of Quantum Numbers:}
		The quantum numbers do not affect neutrino masses (since \(m_{\nu_e} = m_{\nu_\mu} = m_{\nu_\tau}\)) but determine the geometric factors \(f(n, \ell, j)\), which govern the oscillation phases.
		
		\textbf{WARNING:} These assignments are purely speculative and lack experimental basis.
	\end{speculation}
	
	\subsection{Geometric Factors}
	
	\begin{formula}
		\textbf{T0 Geometric Factors:}
		\begin{align}
			f(n,\ell,j) &= \frac{n^6}{\ell^3} \quad \text{for } \ell > 0 \\
			f(1,0,j) &= 1 \quad \text{for } \ell = 0 \text{ (special case)}
		\end{align}
		
		\textbf{Calculated Values:}
		\begin{align}
			f_{\nu_e} &= f(1,0,1/2) = 1 \\
			f_{\nu_\mu} &= f(2,1,1/2) = \frac{2^6}{1^3} = 64 \\
			f_{\nu_\tau} &= f(3,2,1/2) = \frac{3^6}{2^3} = \frac{729}{8} = 91.125
		\end{align}
	\end{formula}
	
	\section{Neutrino Mass Formula}
	
	\subsection{T0 Hypothesis: Equal Masses with Geometric Phases}
	
	\begin{speculation}
		\textbf{T0 Hypothesis: Equal Neutrino Masses with Geometric Phases}
		
		The T0 model postulates that all flavor states (\(\nu_e, \nu_\mu, \nu_\tau\)) have the same mass:
		\[
		m_{\nu_e} = m_{\nu_\mu} = m_{\nu_\tau} = m_\nu = 4.54 \text{ meV}.
		\]
		The mass is derived from the photon analogy:
		\[
		m_\nu = \frac{\xipar^2}{2} \times m_e = \left(8.888888 \times 10^{-9}\right) \times (0.51099895 \times 10^{-3} \text{ GeV}) = 4.54 \text{ meV}.
		\]
		
		To explain oscillations, a geometric mechanism is postulated based on the T0 relation:
		\[
		T_x \cdot m_x = 1, \quad m_x = 4.54 \text{ meV}, \quad T_x \approx 2.2026 \times 10^2 \text{ eV}^{-1} \approx 1.449 \times 10^{-13} \text{ s}.
		\]
		
		The oscillation phases are determined by geometric factors \(f(n, \ell, j)\):
		\[
		\phi_{\text{geo}, i} \propto f_{\nu_i} \cdot \frac{L}{E} \cdot \frac{1}{T_x},
		\]
		where \(f_{\nu_e} = 1\), \(f_{\nu_\mu} = 64\), \(f_{\nu_\tau} = 91.125\).
		
		\textbf{Rationale:}
		\begin{itemize}
			\item The mass \(4.54 \text{ meV}\) is consistent with the cosmological constraint (\(\Sigma m_\nu = 0.01362 \text{ eV} < 0.07 \text{ eV}\)).
			\item Geometric phases enable oscillations without mass differences, supporting the equal-mass hypothesis.
			\item This hypothesis is highly speculative and lacks empirical confirmation.
		\end{itemize}
	\end{speculation}
	
	\begin{formula}
		\textbf{Formula:} \(m_{\nu_i} = 4.54 \text{ meV}\)
		
		\textbf{Total Mass:}
		\[
		\Sigma m_\nu = 3 \times 4.54 \text{ meV} = 13.62 \text{ meV} = 0.01362 \text{ eV}
		\]
		
		\textbf{Comparison with Plausible Target Value:}
		\begin{itemize}
			\item \(\nu_e, \nu_\mu, \nu_\tau\): \(4.54 \text{ meV}\) vs. \(15 \text{ meV}\) (Agreement: \(30.3\%\))
			\item \(\Sigma m_\nu\): \(13.62 \text{ meV}\) vs. \(45 \text{ meV}\) (Deviation: Factor \(\approx 3.30\))
		\end{itemize}
	\end{formula}
	
	\begin{warning}
		\textbf{CRITICAL FINDING:} The hypothesis of equal masses with geometric phases is incompatible with experimental oscillation data (\(\Delta m^2_{21} \approx 7.53 \times 10^{-5} \text{ eV}^2\), \(\Delta m^2_{32} \approx 2.44 \times 10^{-3} \text{ eV}^2\)), as it implies \(\Delta m^2_{ij} = 0\). The geometric approach is purely speculative and requires further theoretical and experimental validation.
	\end{warning}
	
	\section{Plausible Target Value Based on Empirical Data}
	
	\subsection{Derivation from Measurements}
	
	\begin{experimental}
		\textbf{Plausible Target Value:}
		The T0 model postulates equal masses for all flavor states (\(\nu_e, \nu_\mu, \nu_\tau\)). Thus, a single target value for the neutrino mass \(m_\nu\) is derived based on empirical data (as of 2025):
		\begin{itemize}
			\item Cosmological Constraint: \(\Sigma m_\nu = 3 m_\nu < 0.07 \text{ eV} \implies m_\nu < 23.33 \text{ meV}\).
			\item Oscillation Data: \(\Delta m^2_{21} \approx 7.53 \times 10^{-5} \text{ eV}^2\), \(\Delta m^2_{32} \approx 2.44 \times 10^{-3} \text{ eV}^2\), typically requiring different masses. The T0 model bypasses this via geometric phases.
			\item Plausible Target Value: \(m_\nu \approx 15 \text{ meV}\), lying between the solar (\(8.68 \text{ meV}\)) and atmospheric scales (\(50.15 \text{ meV}\)) and satisfying the cosmological constraint:
			\[
			\Sigma m_\nu = 3 \times 15 \text{ meV} = 45 \text{ meV} = 0.045 \text{ eV} < 0.07 \text{ eV}.
			\]
		\end{itemize}
		
		\textbf{Rationale:}
		\begin{itemize}
			\item The target value is consistent with the cosmological constraint and lies within the order of magnitude of oscillation data.
			\item The equal-mass hypothesis is supported by geometric phases, distinguishing the T0 model from standard physics.
			\item The value is plausible but not directly measured, as flavor masses are mixtures of eigenstates.
			\item The T0 mass (\(4.54 \text{ meV}\)) is below the target value (\(30.3\%\)) but also cosmologically consistent.
		\end{itemize}
	\end{experimental}
	
	\section{Experimental Comparison}
	
	\subsection{Current Experimental Upper Limits (2025)}
	
	\begin{experimental}
		\textbf{Experimental Limits:}
		\begin{align}
			m_{\nu_e} &< 0.45 \text{ eV} \quad \text{[KATRIN, 90\% CL]} \\
			m_{\nu_\mu} &< 0.17 \text{ MeV} \quad \text{[Muon decay, indirect]} \\
			m_{\nu_\tau} &< 18.2 \text{ MeV} \quad \text{[Tau decay, indirect]} \\
			\Sigma m_\nu &< 0.07 \text{ eV} \quad \text{[DESI+Planck, 95\% CL]} \\
			\Delta m^2_{21} &\approx 7.53 \times 10^{-5} \text{ eV}^2 \quad \text{[Solar]} \\
			\Delta m^2_{32} &\approx 2.44 \times 10^{-3} \text{ eV}^2 \quad \text{[Atmospheric]} \\
			m_\nu &> 0.06 \text{ eV} \quad \text{[At least one neutrino, 3}\sigma\text{]}
		\end{align}
	\end{experimental}
	
	\subsection{Safety Margins for T0 Hypothesis}
	
	\begin{longtable}[c]{@{}lcc@{}}
		\caption{Safety Margins of the T0 Hypothesis Against Experimental Limits} \\
		\toprule
		\textbf{Parameter} & \textbf{T0 Mass (\(4.54 \text{ meV}\))} & \textbf{Target Value (\(15 \text{ meV}\))} \\
		\midrule
		\endfirsthead
		\toprule
		\textbf{Parameter} & \textbf{T0 Mass (\(4.54 \text{ meV}\))} & \textbf{Target Value (\(15 \text{ meV}\))} \\
		\midrule
		\endhead
		$m_{\nu_e}$ vs 0.45 eV & 99200× & 30× \\
		$m_{\nu_\mu}$ vs 0.17 MeV & 3.74E7× & 11333× \\
		$m_{\nu_\tau}$ vs 18.2 MeV & 4.01E9× & 1.21E6× \\
		\midrule
		$\Sigma m_\nu$ vs 0.07 eV & 5.14× & 1.56× \\
		$\Sigma m_\nu$ vs 0.06 eV & 4.41× & 1.33× \\
		\bottomrule
	\end{longtable}
\normalsize
	
	\begin{important}
		\textbf{T0 Hypothesis:}
		\begin{itemize}
			\item The T0 mass (\(4.54 \text{ meV}\)) is consistent with cosmological constraints (\(\Sigma m_\nu = 0.01362 \text{ eV} < 0.07 \text{ eV}\)) and lies below the target value (\(15 \text{ meV}\), \(30.3\%\)).
			\item Geometric phases (\(T_x \cdot m_x = 1\)) provide a speculative mechanism for oscillations but are incompatible with standard oscillations.
			\item Physical Rationale: The mass is based on \(\frac{\xipar^2}{2}\)-suppression, consistent with the speed difference \(v_\nu = c \times \left(1 - \frac{\xipar^2}{2}\right)\).
		\end{itemize}
	\end{important}
	
	\section{Consistency Checks and Validation}
	
	\subsection{Dimensional Analysis}
	
	\begin{formula}
		\textbf{Dimensional Consistency:}
		\begin{align}
			[\xipar] &= 1 \quad \checkmark \text{ dimensionless} \\
			[m_e] &= \text{GeV} \quad \checkmark \text{ energy/mass} \\
			\left[\frac{\xipar^2}{2} \times m_e\right] &= \text{GeV} \quad \checkmark \text{ energy/mass} \\
			[f_{\nu_i}] &= 1 \quad \checkmark \text{ dimensionless} \\
			[m_\nu] &= \text{eV} \quad \checkmark \text{ (fixed mass)} \\
			[T_x] &= \text{eV}^{-1} \quad \checkmark \text{ (time)}
		\end{align}
		All formulas are dimensionally consistent.
	\end{formula}
	
	\subsection{Mathematical Consistency}
	
	\begin{important}
		\textbf{Consistency of the Hypothesis:}
		\begin{itemize}
			\item The formula \(m_\nu = \frac{\xipar^2}{2} \times m_e = 4.54 \text{ meV}\) is physically grounded in the photon analogy and consistent with the speed difference.
			\item Geometric phases based on \(f(n, \ell, j)\) and \(T_x \cdot m_x = 1\) provide a speculative mechanism for oscillations.
			\item No free parameters except \(\xipar\), simplifying the theory.
		\end{itemize}
	\end{important}
	
	\subsection{Experimental Validation}
	
	\begin{experimental}
		\textbf{Validation Status (as of 2025):}
		\begin{itemize}
			\item The T0 mass (\(4.54 \text{ meV}\)) satisfies cosmological constraints (\(\Sigma m_\nu = 0.01362 \text{ eV} < 0.07 \text{ eV}\)) and is close to the target value (\(15 \text{ meV}\), \(30.3\%\)).
			\item Incompatible with standard oscillations (\(\Delta m^2_{ij} = 0\)), but geometric phases offer a speculative workaround.
			\item The target value (\(15 \text{ meV}\)) is consistent with cosmological constraints but not directly measured.
		\end{itemize}
	\end{experimental}
	
	\section{Conclusion}
	
	\begin{important}
		\textbf{Summary and Outlook:}
		\begin{itemize}
			\item The T0 model postulates equal neutrino masses (\(m_\nu = 4.54 \text{ meV}\)) based on the photon analogy (\(\frac{\xipar^2}{2} \times m_e\)), consistent with the speed difference (\(v_\nu = c \times \left(1 - \frac{\xipar^2}{2}\right)\)).
			\item Geometric phases based on \(T_x \cdot m_x = 1\) and quantum numbers (\(f_{\nu_e} = 1\), \(f_{\nu_\mu} = 64\), \(f_{\nu_\tau} = 91.125\)) speculatively explain oscillations without mass differences.
			\item The plausible target value (\(m_\nu = 15 \text{ meV}\)) is derived from empirical data (cosmological constraint) and lies within the order of magnitude of oscillation data but is not directly measured.
			\item The T0 mass (\(4.54 \text{ meV}\)) is reasonably close to the target value (\(30.3\%\)), satisfies cosmological constraints, but is incompatible with standard oscillations.
			\item The T0 model remains speculative, relying on geometric harmonies without empirical basis.
			\item Future experiments (2025–2030, e.g., KATRIN upgrade, DESI, Euclid) could further test or refute the T0 hypothesis, particularly the geometric oscillation mechanism.
			\item Scientific integrity requires clearly communicating the speculative nature of the T0 model and awaiting further tests.
		\end{itemize}
	\end{important}

